### 2020-09-14 paper/coverletter/coverletter.tex
Startd paper

\documentclass[11pt, a4paper, sans, colorlinks, linkcolor=True]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{black}
\usepackage{ragged2e}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[left=1in, right=1in, bottom=0.5in, top=0.5in]{geometry}
%\addtolength{\topmargin}{-.875in}
\pagenumbering{gobble}
\usepackage{setspace}

%Personal Details
\name{Oliver James}{Hall}
\title{Coverletter}
\address{School of Physics and Astronomy\\ University of Birmingham, Edgbaston}{B15 2TT, Birmingham}{United Kingdom}
\email{ojhall94@gmail.com}
\homepage{https://www.ojhall94.github.io}

\begin{document}
\definecolor{links}{HTML}{3f28bd}
\hypersetup{urlcolor=links}
\recipient{\ }{\ }
\date{\today}
\opening{Dear Nature Astronomy editors,}
\makelettertitle
\justify
\vspace{-0.5cm}

We have written a paper where we use asteroseismology -- the study of oscillating stars -- to gain a new understanding of stellar rotational evolution in stars like the Sun. Using a novel ensemble of asteroseismic rotation, we provide very strong evidence of the existence of the much-debated theory of weakened magnetic braking. This represents a major leap forward for the field of stellar rotational evolution, using rotation measurements independent of those used to first propose the theory, and including older, inactive stars. We think it would be a good fit for your journal, and hope you agree. We have provided a concise summary below.\\

As cool main sequence stars like the Sun grow older, their rotation slows down as magnetic winds carry away angular momentum. The study of this age-rotation relationship, called gyrochronology, provides much potential for measuring stellar age from a star’s rotation, down to 10\% [1]. However gyrochronology has major problems for older stars. A 2016 study, published in Nature, used ages determined through asteroseismology to show that stars older than the Sun appeared to stop losing angular momentum [2]. This effect, which deeply complicates the use of gyrochronology for older stars, was dubbed “weakened magnetic braking”.

{\hskip 1em}Since it was initially proposed, the idea of weakened magnetic breaking has received widespread attention from the stellar astrophysics community. Whether this phenomenon  actually takes place on the main sequence is currently uncertain. Stellar rotation is typically measured by looking at star spots on the surface. Since older, inactive stars show fewer spots, a lack of slow rotation rates on the main sequence may in fact be a selection effect, and not a physical reduction in angular momentum loss [3].

{\hskip 1em}Our study solves this lack of rotation rates for inactive stars by measuring rotation using asteroseismology. Modes of oscillation will rotationally shift in frequency due to a star’s spin, allowing us to measure rotation independent of activity. Asteroseismic rotation has been shown to be a good proxy for surface rotation (something we re-confirm in our paper). In fact you might even consider it to be more fundamental than spot rotation.

{\hskip 1em}In our study, we measured inclination angles and seismic rotation of 91 main sequence stars. These measurements form the largest legacy catalogue of seismic rotation to date, as well as the largest sample of surface rotation of inactive main sequence stars until the launch of PLATO. We compared these new rotation rates to models of stellar rotational evolution, and found that our ensemble overwhelmingly favoured a model where weakened magnetic braking took place. By demonstrating that weakened magnetic braking is needed using seismic rotation for a sample that includes inactive stars, we open the doors for a new era of understanding of the interactions between age, magnetism and rotation in the Sun and stars like it.\\

We believe this work will interest your diverse readership, for a number of reasons:
\begin{itemize}[leftmargin=1.5em]
\itemsep0em 
\item[--] It uses new data -- the first large ensemble of asteroseismic rotation -- to settle an ongoing problem in gyrochronology and stellar modelling, and represents a major result in the field of stellar rotation.

\item[--] It presents novel techniques, determining stellar rotation from interior sound waves that form modes of oscillation on the surface, and assessing two stellar models simultaneously in a Bayesian mixture model framework.

\item[--] Our rotation catalogue and confirmation of weakened magnetic braking together form an important stepping stone in how late main sequence ages may be determined in the near future. This will be interesting to a wide range of astronomers that are looking to find well-constrained ages of stars (e.g. to study planets, stars, clusters and the Milky Way, as well as to constrain stellar evolutionary theory).

\item[--] The Sun is currently thought to lie close to the boundary where weakened magnetic braking kicks in [2]. Our findings affect the predicted rotational evolution of the Sun, and with it, the Sun’s future levels of activity.
\end{itemize}

The cross-disciplinary nature of our study (asteroseismology and rotational evolution) means we have a wide range of expert referees we can suggest.

\begin{itemize}[leftmargin=1.5em]
\itemsep0em 
\item[--] \href{https://fys.kuleuven.be/ster/staff/conny-aerts}{Conny Aerts} - asteroseismology and statistics. 
\item[--] \href{https://ruthangus.github.io/}{Ruth Angus} - applied gyrochronology and Bayesian statistics
\item[--] \href{https://www2.physics.ox.ac.uk/contacts/people/aigrain}{Suzanne Aigrain} - Bayesian statistics, stellar rotation and gyrochronology. Good knowledge of asteroseismology.
\item[--] \href{https://www.aip.de/Members/sbarnes/dr.-sydney-barnes}{Sydney Barnes}* - stellar rotation and gyrochronology calibration
\item[--] \href{https://www.fgcu.edu/directory/dbuzasi?list=1}{Derek Buzasi}** - theoretical and observational gyrochronology, asteroseismology
\item[--] \href{https://www.unige.ch/sciences/astro/evolution/en/members/patrick-eggenberger/}{Patrick Eggenberger} - asteroseismology, angular momentum transport in stellar interiors
\item[--] \href{https://www.mpg.de/5040011/sonnensystemforschung_wissM7}{Laurent Gizon} - stellar rotation, asteroseismology and asteroseismic modelling
\item[--] \href{https://www.iau.org/administration/membership/individual/6822/}{Marie-Jo Goupil} - stellar evolutionary theory
\item[--] \href{https://www.physastro.iastate.edu/directory/sdk}{Steve Kawaler} - stellar rotational evolution and asteroseismology
\item[--] \href{https://orcid.org/0000-0001-5928-7251}{Nuccio Lanza} - stellar rotation
\item[--] \href{https://astronomy.fas.harvard.edu/people/soren-meiborn}{Soren Meibom} - gyrochronology and surface rotation
\item[--] \href{https://whitedwarf.org/travis/}{Travis Metcalfe}*** - asteroseismology, stellar rotation and stellar activity
\item[--] \href{https://www.stsci.edu/stsci-research/research-directory/david-soderblom}{David Soderblom} - stellar ages and activity
\end{itemize}

* Known to be skeptical of weakened magnetic braking which is in opposition to his own research. Previous encounters as a referee with the authors have been difficult and less than constructive.

** Has provided references for me in the past.

*** Frequently collaborates with the third author on studies of stellar rotational evolution.\\

We hope you enjoy our paper, and that you consider publishing it in your journal. We think it would be an excellent fit, as it uses a new and unique cross-disciplinary analysis to end a long-standing discussion in the field of stellar rotational evolution.

\vspace{0.5cm}

Yours sincerely, \\
\vspace{0.5em}
\includegraphics[scale=0.2]{signature.png} \\ 
\vspace{0.5em}
\textbf{Oliver J. Hall}, on behalf of the authors. \\

References:

{\hskip 1.5em}[1] Meibom et al. (2015), \href{https://www.nature.com/articles/nature14118}{Nature}, 517, 589

{\hskip 1.5em}[2] van Saders et al. (2016), \href{https://www.nature.com/articles/nature16168}{Nature}, 529, 181

{\hskip 1.5em}[3] van Saders et al. (2019), \href{https://iopscience.iop.org/article/10.3847/1538-4357/aafafe}{The Astrophysical Journal}, 872, 128
\end{document}

### 2020-09-14 paper/natastron/paper.tex
Startd paper

\documentclass[12pt]{article}
\setlength{\textwidth}{167mm}
\setlength{\headsep}{0mm}
\setlength{\headheight}{0mm}
\setlength{\textheight}{230mm}
\setlength{\oddsidemargin}{1.6mm}
\setlength{\evensidemargin}{1.6mm}
\setlength{\topmargin}{4.6mm}

\usepackage{chngcntr}
\usepackage{graphicx}
\graphicspath{ {Images/} }

% Astronomical abbreviations (thanks to Dan Huber)
\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
\newcommand{\dnu}{\mbox{$\Delta \nu$}\xspace}
\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
\newcommand{\logg}{\mbox{$\log(g)$}\xspace}
\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
\newcommand{\msun}{\mbox{$\mathrm{M}_{\odot}$}\xspace}
\newcommand{\lsun}{\mbox{$\mathrm{L}_{\odot}$}\xspace}
\newcommand{\mearth}{\mbox{$\mathrm{M}_{\oplus}$}\xspace}
\newcommand{\rsun}{\mbox{$\mathrm{R}_{\odot}$}\xspace}
\newcommand{\kepler}{\emph{Kepler}\xspace}
\newcommand{\tess}{\emph{TESS}\xspace}
\newcommand{\ktwo}{K2\xspace}
\newcommand{\gaia}{\emph{Gaia}\xspace}

\begin{document}
\noindent\textbf{\LARGE{New asteroseismic rotation rates of \emph{Kepler} dwarfs show strong agreement with weakened magnetic braking on the late-age main sequence}}\\

\noindent Oliver J. Hall$^{1,2,3}$ 
	Guy R. Davies$^{2,3}$, 
	Jennifer van Saders$^{4,5,6}$,
	Martin B. Nielsen$^{2,3}$
	Mikkel N. Lund$^{3}$, 
	William J. Chaplin$^{2,3}$, 
	Rafael A. Garc\'ia$^{7, 8}$, 
	Louis Amard$^{9}$,
	Angela A. Breimann$^{9}$, 
	Saniya Khan$^{2,3}$, 
	Victor See$^{9}$, 
	Jamie Tayar$^{4, 10}$
	\\

	% List of institutions
	\noindent $^{1}$ Scientific Support Office, Directorate of Science, European Space Research and Technology Centre (ESA/ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, NL

	\noindent 	$^{2}$ School of Physics and Astronomy, University of Birmingham, Edgbaston, Birmingham, B15 2TT, UK

	\noindent 	$^{3}$ Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, 8000 Aarhus C, Denmark

	\noindent 	$^{4}$ Institute for Astronomy, University of Hawai'i, Honolulu, HI 96822

	\noindent 	$^{5}$ Observatories of the Carnegie Institution for Science, Pasadena, CA 91101

	\noindent 	$^{6}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544

	\noindent 	$^{7}$ IRFU, CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France

	\noindent 	$^{8}$ AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, F-91191 Gif-sur-Yvette, France

	\noindent 	$^{9}$ University of Exeter Department of Physics and Astronomy, Stocker Road, Devon, Exeter, EX4 4QL, UK

	\noindent $^{10}$ Hubble Fellow

\vspace{10mm}

\textbf{Studies using asteroseismic ages and rotation rates from spot modulation have shown that standard age-rotation relations break down roughly half-way through the main sequence lifetime, a phenomenon referred to as weakened magnetic braking. While rotation rates from spot modulation can be difficult to determine for older, less active stars, rotational splitting of asteroseismic oscillation frequencies can provide rotation rates for both active and quiescent stars \cite{adibekyan+2017}.\\
We obtained asteroseismic rotation rates of 91 main sequence stars showing high signal-to-noise modes of oscillation.
Using these new rotation rates, along with effective temperatures, metallicities and seismic masses and ages, we built a hierarchical Bayesian mixture model to determine whether the ensemble more closely agreed with a standard rotational evolution scenario, or one where weakened magnetic braking takes place. The weakened magnetic braking scenario was found to be $98.4\%$ more likely for our stellar ensemble, adding to the growing body of evidence for this stage of stellar rotational evolution. This work represents the largest catalogue of seismic rotation on the main sequence to date, opening up possibilities for more detailed ensemble analysis of rotational evolution with \textit{Kepler}.}

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:
\bibliographystyle{nature}
\bibliography{library.bib} %

\end{document}

### 2020-09-15 paper/natastron/paper.tex
Finished setting up structure

@@
 \graphicspath{ {Images/} }
+\usepackage[symbol]{footmisc}
 
@@
 
-\noindent Oliver J. Hall$^{1,2,3}$ 
+\noindent Oliver J. Hall$^{1,2,3,}$\footnote[1]{Email: \texttt{oliver.hall@esa.int} | Twitter: \texttt{@asteronomer} | GitHub: \texttt{@ojhall94}}
 	Guy R. Davies$^{2,3}$, 
@@
 
-\textbf{Studies using asteroseismic ages and rotation rates from spot modulation have shown that standard age-rotation relations break down roughly half-way through the main sequence lifetime, a phenomenon referred to as weakened magnetic braking.
-While rotation rates from spot modulation can be difficult to determine for older, less active stars, rotational splitting of asteroseismic oscillation frequencies can provide rotation rates for both active and quiescent stars \cite{adibekyan+2017}.\\
+\textbf{Studies using asteroseismic ages and rotation rates from spot modulation have shown that standard age-rotation relations break down roughly half-way through the main sequence lifetime, a phenomenon referred to as weakened magnetic braking \cite{vansaders+2016}.
+While rotation rates from spot modulation can be difficult to determine for older, less active stars, rotational splitting of asteroseismic oscillation frequencies can provide rotation rates for both active and quiescent stars.\\
 We obtained asteroseismic rotation rates of 91 main sequence stars showing high signal-to-noise modes of oscillation.
-Using these new rotation rates, along with effective temperatures, metallicities and seismic masses and ages, we built a hierarchical Bayesian mixture model to determine whether the ensemble more closely agreed with a standard rotational evolution scenario, or one where weakened magnetic braking takes place.
-The weakened magnetic braking scenario was found to be $98.4\%$ more likely for our stellar ensemble, adding to the growing body of evidence for this stage of stellar rotational evolution.
+Using these new rotation rates, along with effective temperatures, metallicities and seismic masses and ages, we built a hierarchical Bayesian mixture model to determine whether the ensemble more closely agreed with a standard rotational evolution scenario, or one where weakened magnetic braking takes place \cite{vansaders+pinsonneault2013}.
+The weakened magnetic braking scennatureario was found to be $98.4\%$ more likely for our stellar ensemble, adding to the growing body of evidence for this stage of stellar rotational evolution.
 This work represents the largest catalogue of seismic rotation on the main sequence to date, opening up possibilities for more detailed ensemble analysis of rotational evolution with \textit{Kepler}.}
@@
 %%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+\section{Introduction} %500 words
+
+\section{Data}
+
+\section{Results}
+
+\section{Discussion}
 
 % The best way to enter references is to use BibTeX:
-\bibliographystyle{nature}
+\bibliographystyle{naturemag}
 \bibliography{library.bib} %
 
+\section*{Acknowledgements}
+
+\section*{Methods}
+
+\section*{Author Contributions}
+
 \end{document}

### 2020-09-16 paper/natastron/paper.tex
Rewrote intro, started on data

--- 2020-09-14 paper/natastron/paper.tex
@@
 
-\textbf{Studies using asteroseismic ages and rotation rates from spot modulation have shown that standard age-rotation relations break down roughly half-way through the main sequence lifetime, a phenomenon referred to as weakened magnetic braking.
-While rotation rates from spot modulation can be difficult to determine for older, less active stars, rotational splitting of asteroseismic oscillation frequencies can provide rotation rates for both active and quiescent stars \cite{adibekyan+2017}.\\
+\textbf{Studies using asteroseismic ages and rotation rates from star spot rotation have shown that standard age-rotation relations break down roughly half-way through the main sequence lifetime, a phenomenon referred to as weakened magnetic braking.
+While rotation rates from spots can be difficult to determine for older, less active stars, rotational splitting of asteroseismic oscillation frequencies can provide rotation rates for both active and quiescent stars.\\
 We obtained asteroseismic rotation rates of 91 main sequence stars showing high signal-to-noise modes of oscillation.
-Using these new rotation rates, along with effective temperatures, metallicities and seismic masses and ages, we built a hierarchical Bayesian mixture model to determine whether the ensemble more closely agreed with a standard rotational evolution scenario, or one where weakened magnetic braking takes place.
+Using these new rotation rates, along with effective temperatures, metallicities and seismic masses and ages, we built a hierarchical Bayesian mixture model to determine whether the ensemble more closely agreed with a standard rotational evolution scenario \cite{vansaders+pinsonneault2013}, or one where weakened magnetic braking takes place \cite{vansaders+2016}.
 The weakened magnetic braking scenario was found to be $98.4\%$ more likely for our stellar ensemble, adding to the growing body of evidence for this stage of stellar rotational evolution.
@@
 %%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+\section{Introduction} %500 words
+Gyrochronology is the study of the relationship between a star's rotation period and its age.
+As a star grows older along the main sequence, magnetic winds will cause it to lose angular momentum, slowing it down.
+Because the loss rate is related to temperature, the rotation period of a young star will rapidly settle on to a plane in age-colour-rotation space \cite{barnes2007}.
+As a result, knowing the rotation and colour of a star provides an avenue to measure it's age, which can otherwise be difficult to come by, enabling more in-depth studies of stellar populations \cite{leiner+2019,claytor+2019}.
+
+Gyrochronology was previously calibrated on stellar clusters, which have well constrained ages, but only up to roughly $2.5\, \rm{Gyr}$ so far \cite{meibom+2015}.
+With the launch of the \textit{Kepler} mission \cite{borucki+2010}, ages of main sequence field stars (i.e.
+not in clusters) became more widely available through asteroseismology, the study of stellar variability \cite{silvaaguirre+2015}.
+When looking at these stars disagreements were found with gyrochronology beyond the middle of their main sequence lifetime, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}.
+It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops, causing stars to keep fast rotation rates that we were not expected in existing gyrochronology relations.
+
+The mechanism by which weakened magnetic braking occurs is  still subject to debate, and may be connected to changes in the magnetic field morphology \cite{reville+2015,garraffo+2016, metcalfe+2019, see+2019}.
+It may also be explained from an observational point of view.
+A large scale survey of stellar rotation rates measured using star spots pointed out a lack of slowly rotating stars older then Sun \cite{mcquillan+2014}.
+As activity reduces with age, older stars with fewer star spots are less likely to have their rotation measured \cite{matt+2015}.
+The point at which the detection probability drops appears to lie at a similar level of activity to that at which the proposed weakened magnetic braking takes place, pitting these two possibilities against one another \cite{vansaders+2019}.
+
+Determining whether weakened magnetic braking is a true phenomenon or a bias in star spot observations requires new data, which can be provided by asteroseismology.
+A star's rotation causes modes of oscillation to split into multiplets, making it possible to measure the rate of rotation by measuring oscillation frequencies \cite{ledoux1951}.
+Asteroseismic rotation is more difficult to obtain than rotation from star spots, but does not require  spots to be visible, meaning that we can measure rotation for quiescent stars that would not have been present in existing catalogues of star-spot rotation.
+Previous studies have shown that asteroseismic rotation rates probe the near-surface of the star, making them comparable to spot rotation rates, and the perfect avenue to explore whether weakened magnetic braking truly takes place \cite{lund+2014, benomar+2015}.
+Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of colours and ages, and evaluate this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one where weakened magnetic braking takes place.
+
+\section{Data}
+
+In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) oscillations for each star, of which the latter have significantly lower signal-to noise.
+Radial oscillations ($\ell = 0$), which are also visible, do not split.
+In this work, we studied a sample of 94 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}.
+
+For the purposes of studying gyrochronology, we wanted to be able to single out stars for which the loss of angular momentum via magnetized winds is the dominant source of rotational evolution.
+Stars with $T_{\rm eff} > 6250\, \rm{K}$ fall beyond the `Kraft' break, which roughly separate stars with large convective envelopes (at lower temperatures) from those with thin ones (high temperatures), at which the efficiency of angular momentum transport is greatly reduced.
+We also wanted to single out stars that have started to evolve onto the sub-giant branch, where the outer envelope begins to expand, making them challenging targets for gyrochronology.
+While there are no identified mixed dipole modes\footnote{In evolved stars, gravity modes propagating in the radiative interior will interfere with non-radial p modes, changing their structure and creating so-called `mixed modes' \cite{bedding+2010}.} in the stars in our sample, indicating an evolved structure, we can still apply a conservative sub-giant classification of stars with $\rm{log(g)} < 4.0\, \rm dex$.
+\cite{garcia+2014}.
+
+Our sample spans surface gravities of $3.8\, \rm{dex} < \rm{log(g)} < 4.6\, \rm{dex}$ and temperatures of $5000\, \rm{K} < T_{\rm eff} <  6700\, \rm{K}.$ Of our full sample of 95 targets, 67 stars fall in the range $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$, which we call main sequence (MS) stars.
+Four targets in our sample have $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$ which we class as potentially being sub-giants (SG stars).
+The remaining 24 stars in our sample have $T_{\rm eff} > 6250\, \rm K$, which we class as being hot main sequence stars.
+
+%% reduce this to two paragraphs., point to Figure 1. Then go straigh to what we did and results. Then discussion with a plot per paragraph, and then copy and paste section 3.
+
+\section{Results}
+ Neither catalogues reported stellar rotation, so we repeated the mode frequency fitting with a model that accounted for this in more detail (see \textbf{\textit{Methods}}).
+
+\section{Discussion}
 
 % The best way to enter references is to use BibTeX:
-\bibliographystyle{nature}
+\bibliographystyle{naturemag}
 \bibliography{library.bib} %
 
+\section*{Acknowledgements}
+
+\section*{Methods}
+
+\section*{Author Contributions}
+
 \end{document}

### 2020-09-16 paper/natastron/paper.tex
Started results

@@
 \usepackage{chngcntr}
+\usepackage{xspace}
 \usepackage{graphicx}
-\graphicspath{ {Images/} }
+\graphicspath{{Images/}}
 \usepackage[symbol]{footmisc}
@@
 Previous studies have shown that asteroseismic rotation rates probe the near-surface of the star, making them comparable to spot rotation rates, and the perfect avenue to explore whether weakened magnetic braking truly takes place \cite{lund+2014, benomar+2015}.
-Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of colours and ages, and evaluate this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one where weakened magnetic braking takes place.
+Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of colours and ages, and evaluate this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one where weakened magnetic braking takes place.\\
 
@@
 Radial oscillations ($\ell = 0$), which are also visible, do not split.
-In this work, we studied a sample of 94 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}.
+In this work, we studied a sample of 95 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}.
+A table of parameters taken from these studies, as well as details on how these were obtained, can be found in \textbf{\textit{Methods}}.
 
-For the purposes of studying gyrochronology, we wanted to be able to single out stars for which the loss of angular momentum via magnetized winds is the dominant source of rotational evolution.
-Stars with $T_{\rm eff} > 6250\, \rm{K}$ fall beyond the `Kraft' break, which roughly separate stars with large convective envelopes (at lower temperatures) from those with thin ones (high temperatures), at which the efficiency of angular momentum transport is greatly reduced.
-We also wanted to single out stars that have started to evolve onto the sub-giant branch, where the outer envelope begins to expand, making them challenging targets for gyrochronology.
-While there are no identified mixed dipole modes\footnote{In evolved stars, gravity modes propagating in the radiative interior will interfere with non-radial p modes, changing their structure and creating so-called `mixed modes' \cite{bedding+2010}.} in the stars in our sample, indicating an evolved structure, we can still apply a conservative sub-giant classification of stars with $\rm{log(g)} < 4.0\, \rm dex$.
-\cite{garcia+2014}.
+We separated our sample into three categories \cite{garcia+2014}: 64 main sequence stars (MS, $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$); 4 potential sub-giant stars (SG, $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$, which may have begun to evolve off the main sequence, complicating their rotational history\footnote{It should be noted that none of these stars have identified mixed dipole modes, which indicate an evolved structure (see \cite{bedding+2010}).}; and 24 `hot' stars (H, $T_{\rm eff} > 6250\, \rm K$), which lie above the Kraft break, the point at which convective envelopes are tenuous, and angular momentum loss becomes inefficient \cite{kraft1967}.
+The sample, which can be seen in Figure \ref{fig:sample}, spans surface gravities of $3.8\, \rm{dex} < \rm{log(g)} < 4.6\, \rm{dex}$, temperatures of $5000\, \textrm{K} < T_{\rm eff} <  6700\, \rm{K}$, and ages from $1$ to $\sim 13\, \rm{Gyr}$.
 
-Our sample spans surface gravities of $3.8\, \rm{dex} < \rm{log(g)} < 4.6\, \rm{dex}$ and temperatures of $5000\, \rm{K} < T_{\rm eff} <  6700\, \rm{K}.$ Of our full sample of 95 targets, 67 stars fall in the range $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$, which we call main sequence (MS) stars.
-Four targets in our sample have $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$ which we class as potentially being sub-giants (SG stars).
-The remaining 24 stars in our sample have $T_{\rm eff} > 6250\, \rm K$, which we class as being hot main sequence stars.
-
-%% reduce this to two paragraphs., point to Figure 1. Then go straigh to what we did and results. Then discussion with a plot per paragraph, and then copy and paste section 3.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\textwidth]{data.pdf}
+	\caption{Our sample of 95 stars from the Kages and LEGACY catalogues coloured by asteroseismic age  \cite{silvaaguirre+2015, silvaaguirre+2017}.
+The dashed lines indicate our classification boundaries: main sequence (circles, $\teff < 6250\, K$, $\logg < 4\, \rm{dex}$), potential sub-giants (squares, $\teff < 6250\, K$, $\logg > 4\, \rm{dex}$), and `hot' stars (triangles, $\teff > 6250\, K$).
+The Sun is shown with the `$\odot$' symbol, and has an age of $4.6\, \rm{Gyr}$ \cite{bonanno+frohlich2015
+		}.
+The solid lines are evolutionary tracks generated using MESA \cite{paxton+2017}, for a metallicity of $Z = 0.01493$ and helium content of $Y = 0.26588$.
+Left to right, they represent masses of $1.5$, $1.25$, $1$ and $0.75\, M_\odot$.
+Vertical errorbars are too small to be visible.}
+	\label{fig:sample}
+\end{figure}
 
 \section{Results}
- Neither catalogues reported stellar rotation, so we repeated the mode frequency fitting with a model that accounted for this in more detail (see \textbf{\textit{Methods}}).
+ The `Kages' and LEGACY catalogues that form our stellar sample both performed detailed asteroseismic frequency fitting, but did not report asteroseismic rotation.
+Here, we repeated the mode frequency fitting with an improved Bayesian model that accounted for rotation in more detail (see \textbf{\textit{Methods}}).
+We fit our model to \kepler power-spectra of 95 stars, which was successful in 94 cases.
+We compared our results with both published and unpublished asteroseismic rotation rates, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with previous work.
+To some degree this was expected, as  for stars viewed near pole-on the power of the split modes of oscillation are extremely small.
+We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we judge our asteroseismic rotation measurements to be robust (for a full justification, see \textit{\textbf{Methods}}).
 

### 2020-09-25 paper/natastron/paper.tex
Chipping away at paper

@@
 \textbf{Studies using asteroseismic ages and rotation rates from star spot rotation have shown that standard age-rotation relations break down roughly half-way through the main sequence lifetime, a phenomenon referred to as weakened magnetic braking.
-While rotation rates from spots can be difficult to determine for older, less active stars, rotational splitting of asteroseismic oscillation frequencies can provide rotation rates for both active and quiescent stars.\\
+While rotation rates from spots can be difficult to determine for older, less active stars, rotational splitting of asteroseismic oscillation frequencies can provide rotation rates for both active and quiescent stars, and so can confirm whether this effect really takes place in older stars.\\
 We obtained asteroseismic rotation rates of 91 main sequence stars showing high signal-to-noise modes of oscillation.
@@
 %%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-\section{Introduction} %500 words
+ %500 words
 Gyrochronology is the study of the relationship between a star's rotation period and its age.
@@
 Because the loss rate is related to temperature, the rotation period of a young star will rapidly settle on to a plane in age-colour-rotation space \cite{barnes2007}.
-As a result, knowing the rotation and colour of a star provides an avenue to measure it's age, which can otherwise be difficult to come by, enabling more in-depth studies of stellar populations \cite{leiner+2019,claytor+2019}.
+As a result, knowing the rotation and colour of a star provides an avenue to measure it's age, which can otherwise be difficult to come by, enabling more in-depth studies of stellar populations and individual stars \cite{leiner+2019,claytor+2019}.
 
@@
 not in clusters) became more widely available through asteroseismology, the study of stellar variability \cite{silvaaguirre+2015}.
-When looking at these stars disagreements were found with gyrochronology beyond the middle of their main sequence lifetime, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}.
-It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops, causing stars to keep fast rotation rates that we were not expected in existing gyrochronology relations.
+When looking at these stars ,disagreements were found with gyrochronology beyond the middle of their main sequence lifetime, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}.
+It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops, causing stars to keep fast rotation rates at old ages, which we would not expected from existing gyrochronology relations.
 
@@
 Determining whether weakened magnetic braking is a true phenomenon or a bias in star spot observations requires new data, which can be provided by asteroseismology.
-A star's rotation causes modes of oscillation to split into multiplets, making it possible to measure the rate of rotation by measuring oscillation frequencies \cite{ledoux1951}.
+A star's rotation causes modes of oscillation to split into multiplets, making it possible to measure the rate of rotation by measuring the splitting between oscillation frequencies \cite{ledoux1951}.
 Asteroseismic rotation is more difficult to obtain than rotation from star spots, but does not require  spots to be visible, meaning that we can measure rotation for quiescent stars that would not have been present in existing catalogues of star-spot rotation.
@@
 
-\section{Data}
-
-In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) oscillations for each star, of which the latter have significantly lower signal-to noise.
+\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) oscillations for each star, of which the latter have significantly lower signal-to noise.
 Radial oscillations ($\ell = 0$), which are also visible, do not split.
@@
 
-We separated our sample into three categories \cite{garcia+2014}: 64 main sequence stars (MS, $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$); 4 potential sub-giant stars (SG, $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$, which may have begun to evolve off the main sequence, complicating their rotational history\footnote{It should be noted that none of these stars have identified mixed dipole modes, which indicate an evolved structure (see \cite{bedding+2010}).}; and 24 `hot' stars (H, $T_{\rm eff} > 6250\, \rm K$), which lie above the Kraft break, the point at which convective envelopes are tenuous, and angular momentum loss becomes inefficient \cite{kraft1967}.
-The sample, which can be seen in Figure \ref{fig:sample}, spans surface gravities of $3.8\, \rm{dex} < \rm{log(g)} < 4.6\, \rm{dex}$, temperatures of $5000\, \textrm{K} < T_{\rm eff} <  6700\, \rm{K}$, and ages from $1$ to $\sim 13\, \rm{Gyr}$.
+We separated our sample into three categories \cite{garcia+2014}: 64 main sequence stars (MS, $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$); 4 potential sub-giant stars (SG, $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$, which may have begun to evolve off the main sequence, complicating their rotational history\footnote{It should be noted that none of these stars have identified mixed dipole modes, which indicate an evolved structure (see \cite{bedding+2010}).}; and 24 `hot' stars (H, $T_{\rm eff} > 6250\, \rm K$), which lie above the Kraft break, the point at which convective envelopes are tenuous, and angular momentum loss through magnetic winds becomes inefficient \cite{kraft1967}.
+The sample, which can be seen in Figure \ref{fig:sample}, spans surface gravities of $3.8\, \rm{dex} < \rm{log(g)} < 4.6\, \rm{dex}$, temperatures of $5000\, \textrm{K} < T_{\rm eff} <  6700\, \rm{K}$, and ages from $1$ to $\sim 13\, \rm{Gyr}$.\\
 
@@
 
-\section{Results}
- The `Kages' and LEGACY catalogues that form our stellar sample both performed detailed asteroseismic frequency fitting, but did not report asteroseismic rotation.
+\textbf{Results of asteroseismic fitting:} The `Kages' and LEGACY catalogues that form our stellar sample both performed detailed asteroseismic frequency fitting, but did not report asteroseismic rotation.
 Here, we repeated the mode frequency fitting with an improved Bayesian model that accounted for rotation in more detail (see \textbf{\textit{Methods}}).
@@
 To some degree this was expected, as  for stars viewed near pole-on the power of the split modes of oscillation are extremely small.
-We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we judge our asteroseismic rotation measurements to be robust (for a full justification, see \textit{\textbf{Methods}}).
+We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we judge our asteroseismic rotation measurements to be robust (for a full justification, see \textit{\textbf{Methods}}).\\
+
+\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two models of rotational evolution: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model').
+The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$ (for details, see \textbf{\textit{Methods}}).
+
+We evaluated our ensemble against both population models simultaneously using a Bayesian mixture model, which treated the data as being drawn from a mixture made from Kernel Density Estimates of both populations, modulated by a mixing parameter $P_{\rm s}$.
+In the limit that $P_{\rm s} \rightarrow 1$, the data are mostly likely drawn from the standard model.
+In the limit $P_{\rm s} \rightarrow 0$, the WMB model is more likely.
+We then this mixture model to our ensemble, accounting for the population distributions in effective temperature ($T_{\rm eff}$), metallicity (\feh), asteroseismic mass ($M$) and age ($t$) and our new rotation periods ($P$).
 

### 2020-09-25 paper/natastron/paper.tex
Added in supplementary materials

@@
 \usepackage{graphicx}
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+\usepackage[ ]{hyperref}
 \graphicspath{{Images/}}
@@
 	% List of institutions
-	\noindent $^{1}$ Scientific Support Office, Directorate of Science, European Space Research and Technology Centre (ESA/ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, NL
+	\noindent $^{1}$ European Space Agency (ESA), European Space Research and Technology Centre (ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, The Netherlands
 
@@
 We separated our sample into three categories \cite{garcia+2014}: 64 main sequence stars (MS, $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$); 4 potential sub-giant stars (SG, $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$, which may have begun to evolve off the main sequence, complicating their rotational history\footnote{It should be noted that none of these stars have identified mixed dipole modes, which indicate an evolved structure (see \cite{bedding+2010}).}; and 24 `hot' stars (H, $T_{\rm eff} > 6250\, \rm K$), which lie above the Kraft break, the point at which convective envelopes are tenuous, and angular momentum loss through magnetic winds becomes inefficient \cite{kraft1967}.
+Our conclusions are largely insensitive to these categorical assignments, and they are intended solely to help explore results category-by-category.
 The sample, which can be seen in Figure \ref{fig:sample}, spans surface gravities of $3.8\, \rm{dex} < \rm{log(g)} < 4.6\, \rm{dex}$, temperatures of $5000\, \textrm{K} < T_{\rm eff} <  6700\, \rm{K}$, and ages from $1$ to $\sim 13\, \rm{Gyr}$.\\
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{data.pdf}
+	\includegraphics[width=0.6\textwidth]{data.pdf}
 	\caption{Our sample of 95 stars from the Kages and LEGACY catalogues coloured by asteroseismic age  \cite{silvaaguirre+2015, silvaaguirre+2017}.
 The dashed lines indicate our classification boundaries: main sequence (circles, $\teff < 6250\, K$, $\logg < 4\, \rm{dex}$), potential sub-giants (squares, $\teff < 6250\, K$, $\logg > 4\, \rm{dex}$), and `hot' stars (triangles, $\teff > 6250\, K$).
-The Sun is shown with the `$\odot$' symbol, and has an age of $4.6\, \rm{Gyr}$ \cite{bonanno+frohlich2015
-		}.
+The Sun is shown with the `$\odot$' symbol, and has an age of $4.6\, \rm{Gyr}$ \cite{bonanno+frohlich2015}.
 The solid lines are evolutionary tracks generated using MESA \cite{paxton+2017}, for a metallicity of $Z = 0.01493$ and helium content of $Y = 0.26588$.
@@
 
+\textbf{Seismic versus surface rotation rates:}\\
+
 \textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two models of rotational evolution: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model').
@@
 In the limit $P_{\rm s} \rightarrow 0$, the WMB model is more likely.
-We then this mixture model to our ensemble, accounting for the population distributions in effective temperature ($T_{\rm eff}$), metallicity (\feh), asteroseismic mass ($M$) and age ($t$) and our new rotation periods ($P$).
+This mixture model was evaluated in a five-dimensional parameter space, accounting for the population distributions in effective temperature ($T_{\rm eff}$), metallicity (\feh), asteroseismic mass ($M$) and age ($t$) and our new rotation periods ($P$).
 
-\section{Discussion}
+We fit our mixture model to the 73 stars in our sample with the best convergence metrics on the asteroseismic mode frequency fitting (see \textbf{\textit{Table 1}}).
+This sample included 22 `hot` stars, 4 potential sub-giants, and 47 main sequence stars.
+We calculated a joint posterior for this sample by multiplying the posterior probabilities obtained for $P_{\rm s}$ for each stars.
+This joint probability can be seen in Figure \ref{fig:gyroresults} in the left-hand plot, and the cumulative probability can be seen in the right-hand plot.
+In both of these plots, their left-hand sides hold 98.4\% of the probability, indicating that the weakened magnetic braking model is preferred.
+When only considering the main sequence stars, which are expected to be driving this distinction, this rises to 99.2\%.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{modelresults.pdf}
+	\caption{Posterior estimates of the mixture model parameter $P_{\rm s}$, broken down by stellar classification.
+A value of $P_{\rm s}$ close to zero indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 1 indicates that the data are more consistent with a standard rotational evolution scenario.
+\textit{Left:} the product of histograms of the posterior estimates for 73 stars, or subsets thereof for different stellar classifications.
+\textit{Right:} the cumulative posterior probability for 73 stars, or subsets thereof for different stellar types.}
+	\label{fig:gyroresults}
+\end{figure}
+
+\textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we made sure to test the same results were obtained using different subsets of the ensemble.
+Figure 3 shows ....
+[metallicity, full sample, biases, asteroseismology, van saders].\\
+
+We leave the reader with the following conclusions:
+\begin{enumerate}
+	\item We found that our ensemble was $98.4\%$ more likely to be drawn from the WMB model than the standard model, for stars evolved under a standard braking law \cite{vansaders+pinsonneault2013}.
+In other words, our asteroseismic observations strongly favour a model of weakened magnetic braking \cite{vansaders+2016}, at a critical Rossby number of $Ro_{\rm{crit}} = 1.97$.
+This work expands upon previous analysis (\cite{vansaders+2019}) by including quiescent stars older than the Sun.
+This conclusion was found to be robust against choice of ensemble members and potentially underestimated asteroseismic systematic uncertainties.
+A comparison to other braking laws \cite{matt+2015} using our asteroseismic ensemble will take place in future work.
+
+	\item We compared our new asteroseismic rotation rates with surface rotation measures from spot modulation.
+Our findings replicate those in similar studies (\cite{nielsen+2015,benomar+2015}), in the sense that we find no statistically significant difference between seismic and spot modulation measures of stellar rotation in our ensemble.
+
+	\item We present new techniques for asteroseismic `peak-bagging' frequency analyses, specifically: expressing well known empirical asteroseismic relations in a hierarchical modeling structure to account for small-scale effects not included in our model (such as acoustic glitches), and replacing uninformative empirical relations with Gaussian Process priors.
+
+	\item The new asteroseismic rotation catalogue presented in this work will act as an entry point for more detailed studies, including comparisons between different braking laws and individually modeled values of stellar rotation at different critical Rossby numbers.
+\end{enumerate}
+
+Finally, in the near future our asteroseismic rotation catalogue will be further complemented; with high-precision surface rotation measurements and atmospheric parameters from spectroscopic surveys such as LAMOST \cite{deng+2012}, 4MOST \cite{dejong+2014} and WEAVE \cite{dalton+2014}; and new asteroseismic measurements of age from the \ktwo and \tess missions.
+With these surveys, large scale ensemble asteroseismology will continue to increase the possibilities for understanding gyrochronology.\\
+
+All analysis performed as part of this work is stored in an online public repository\footnote{\url{https://github.com/ojhall94/malatium}}.\\
+
+\textbf{Software}: \texttt{astropy} \cite{astropycollaboration+2013, astropycollaboration+2018}, \texttt{astroquery} \cite{ginsburg+2019}, \texttt{Lightkurve} \cite{lightkurvecollaboration+2018}, \texttt{corner} \cite{foreman-mackey2016}, \texttt{emcee} \cite{foreman-mackey+2013}, \href{https://docs.daft-pgm.org/}{\texttt{daft}}, \texttt{Stan} \cite{carpenter+2017}, \texttt{PyStan} \cite{vanhoey+2013}, \texttt{iPython} \cite{perez+granger2007}, \texttt{Jupyter Notebooks} \cite{kluyver+2016}, \texttt{numpy}  \cite{vanderwalt+2011}, \texttt{pandas} and \texttt{scipy} \cite{mckinney2010}, \texttt{matplotlib} \cite{hunter2007}, \texttt{seaborn} \cite{waskom+2018}, \texttt{statsmodels} \cite{seabold+perktold2010}, \texttt{PyMC3} \cite{salvatier+2016}, \texttt{theano} \cite{thetheanodevelopmentteam+2016}.\\
+
+\textbf{Acknowledgments}:The authors would like to thank Sean Matt, Ellis Avallone, Alex Dixon, Warrick Ball and Brett Morris for helpful discussions. 
+OJH, GRD and WJC acknowledge the support of the UK Science and Technology Facilities Council (STFC). 
+JvS acknowledges support from the TESS Guest Investigator Program (80NSSC18K18584).
+MBN acknowledges support from the UK Space Agency
+This work has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (CartographY GA. 804752)
+Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement no.: DNRF106). 
+LA, AB and VS acknowledge funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation program (grant agreement No.
+682393 AWESoMeStars).
+AB also acknowledges the support of the College of Engineering, Mathematics and Physical Sciences at the University of Exeter.
+RAG acknowledges the support from the PLATO and GOLF CNES grants.
+JT acknowledges that support for this work was provided by NASA through the NASA Hubble Fellowship grant $\#51424$ awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
+The computations described in this paper were performed using the University of Birmingham's BlueBEAR HPC service.
+This paper includes data collected by the Kepler mission and obtained from the MAST data archive at the Space Telescope Science Institute (STScI).
+Funding for the Kepler mission is provided by the NASA Science Mission Directorate.
+STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5–26555.\\
 
@@
 
-\section*{Acknowledgements}
+\textbf{Author Contributions:} O.J.H.
+led the project, with help from G.R.D., J.V.S., M.B.N and W.J.C..
+J.V.S.
+also led the development of the stellar population models.
+M.N.L., R.A.G.
+and S.K.
+both provided data or stellar models and along with J.T.
+assessed the validity of our asteroseismic results.
+L.A., A.B.
+and V.S.
+provided the assessment of the theoretical implications of the gyrochronology results.
+All authors have contributed to the interpretation of the data and the results, and all discussed and provided comments for all drafts of the paper.
 
-\section*{Methods}
+\textbf{Competing Interests:} The authors declare that they have no competing financial interests.
 
-\section*{Author Contributions}
+\textbf{Correspondence:} Correspondence and requests for materials should be addressed to O.J.H.. (email: oliver.hall@esa.int).
+
+\clearpage
+
+\section*{Supplementary materials}
+\setcounter{tocdepth}{2}
+\tableofcontents
+\section{Asteroseismic Methods}
+\subsection{Asteroseismic Data}
+For our asteroseismic power spectrum data we used the unweighted power spectra from the KASOC pipeline \cite{handberg+lund2014}\footnote{Obtainable from the \href{http://kasoc.phys.au.dk/}{KASOC} webpage.}.
+We did not apply any additional treatment to these data.
+For 16 Cyg A \& B (KIC 12069424 and KIC 12069449) we used the KEPSEISMIC lightcurves \cite{garcia+2011}\footnote{Obtainable from \href{https://archive.
+		stsci.edu/prepds/kepseismic/}{MAST}.}, which have significantly better signal-to-noise for these two stars.
+
+For our sample, we used the asteroseismic ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{silvaaguirre+2015} in the Kages and LEGACY catalogues.
+These ages have been obtained by comparisons of measured oscillation properties to stellar models, accounting for an expanded range of metallicities.
+\texttt{BASTA} is thoroughly compared to four other seismic modelling techniques in \cite{silvaaguirre+2017}.
+While uncertainties found through \texttt{BASTA} are typically higher than for other techniques, only \texttt{BASTA} and \texttt{ASTFIT} \cite[Aarhus STellar Evolution Code]{christensen-dalsgaard2008} recover the radius, mass and age of the Sun, when applied to solar data.
+Although the uncertainties on \texttt{ASTFIT} ages are overall lower, they are not reported in \cite{silvaaguirre+2015} for the Kages sample.
+In order to maintain an internally consistent stellar age sample, we used age results from \texttt{BASTA} for both the Kages and LEGACY samples.
+
+For our stellar masses we used asteroseismic model masses obtained by \texttt{BASTA} reported in Kages and LEGACY, in order to maintain internal consistency with the age measurements.
+We note that age and mass posteriors from \texttt{BASTA} are correlated, but chose not to account for the unpublished correlations in this work.
+As described in the catalogue papers, for Kages stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy reported in \cite{huber+2013a}.
+For LEGACY stars, atmospheric properties were similarly taken from \cite{buchhave+latham2015} for most stars in the catalogue, and complemented by other values from the literature for the remaining stars \cite[see Table 3]{silvaaguirre+2017}.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=.99\textwidth]{Images/modelfit.pdf}
+	\caption{A power spectrum constructed from four years of \kepler observations of 16 Cyg A (KIC 12069424).
+Plotted over the top is the model resulting from the fit to the data described in this work.
+The model implements both the mode frequencies, seen on the right hand side of the plot, and the convective background, the effects of which are seen on the left.
+Low frequencies have been cropped out for clarity.
+\textit{Inset}: A zoom in on a radial (right) and quadrupole (left) ($\ell = 0, 2$) pair of modes.
+The quadrupole mode is split into five components by the star's rotation.
+Due to the star's inclination angle with respect to us, two out of five peaks are more distinct.
+The height and spacing of the mode components is a function of the star's rotational splitting ($0.56\, \mu\rm{Hz}$, equivalent to $P_{\rm rot} = 20.5\, \rm{days}$) and angle of inclination ($45^\circ$).}
+	\label{fig:modelfit}
+\end{figure*}
+
+\subsection{Asteroseismic Model}\label{s:seismo}
+In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background ($B(\nu)$), the oscillations ($O(\nu)$), and the white noise ($W$) in the style of e.g.
+\cite{davies+2015}.
+Our data, observed with \kepler, are also subject to the apodization (attenuation) of signals in the frequency-domain, where we fit our model \cite{chaplin+2011}.
+The apodization in power is given by
+
+\begin{equation}\label{eq:apodization}
+	\eta^2(\nu) = \rm{sinc}^2\left(\frac{\pi}{2}\frac{\nu}{\nu_{\rm nyq}}\right)\, ,
+\end{equation}
+where $\nu_{\rm nyq}$ is the Nyquist frequency for the \kepler short cadence, which was treated as a free parameter in our model to account for gaps in the data.
+Apodization only affects signals with characteristic timescales, meaning that it does not affect the white noise level, only the oscillations and convective background components.
+Given the above, our comprehensive model for the power spectrum is
+
+\begin{equation}\label{eq:model}
+	M(\nu) = W + \eta^2(\nu)[O(\nu) + B(\nu)]\, .
+\end{equation}
+
+\subsubsection{Convective Background}
+To model the convective background we used three Harvey components \cite{harvey1985}, which express the background in power as Lorentzian-like functions centered on zero frequency.
+The Harvey components take the form
+
+\begin{equation}
+	H(\nu, a, b, x) = \frac{4a^2/b}{1 + (2\pi b\nu)^x}\, ,
+\end{equation}
+
+\noindent where $a$ and $b$ are the free parameters in our model, and $x$ is fixed. The three Harvey components together form our background function as
+
+\begin{equation}\label{eq:background}
+	B(\nu) = H(\nu, a, b, x=4) + H(\nu, c, d, x=4) + H(\nu, j, k, x=2)\, ,
+\end{equation}
+
+\noindent where we have labeled parameters for the separate components.
+The $x = 2$ term here contributes to the background at high frequencies, whereas the $x=4$ terms contribute the background at low frequencies.
+
+\subsubsection{Modes of Oscillation}
+Modes of oscillation appear in the power spectrum as Lorentzian peaks \cite{chaplin+basu2017}.
+Due to stellar rotation, each mode with an angular degree of $\ell > 0$ is split into its $(2\ell +1)$ Lorentzian components, labeled by $m$, the azimuthal order.
+For all $\ell=(0,1,2)$ modes identified in \cite{davies+2016,lund+2017} we add a (set of) Lorentzian(s) to our model, building a composite model representing all visible modes.
+The construction of our oscillation model takes the form
+
+\begin{equation}
+	O(\nu) = \sum_n \sum_\ell \sum_{m=-\ell}^\ell \frac{H_{n,\ell,m}}{1 + \frac{4}{\Gamma^2_{n,\ell}}(\nu - \nu_{n,\ell,m})^2}\, ,
+\end{equation}
+
+\noindent where $n$ is the radial order of a mode (i.e.
+the overtone number of the oscillation), $H_{n,\ell,m}$ is the height of the mode, $\Gamma_{n,\ell}$ is the linewidth of the mode (approximated to be equal for all split components at a single $n$ and $\ell$) and $\nu_{n, \ell, m}$ is the frequency of the mode.
+The range of $n$ differs per star depending on how many radial orders were reported in LEGACY or Kages, and the range of $\ell$ depends on how many angular degrees were reported for the corresponding radial order.
+
+\subsubsection{Mode Frequencies and Rotational Splitting}\label{ssec:frequencies}
+The mode frequencies of main sequence stars are described by the asymptotic expression \cite{tassoul1980, vrard+2016}.
+The asymptotic expression defines the locations of the modes as regularly spaced, with structured deviation around \numax, the frequency of maximum oscillation amplitude.
+The expression takes the form
+
+\begin{equation}\label{eq:asymptotic}
+	\nu_{n,\ell,m} = \dnu\left(n + \epsilon + \delta\nu_{0,\ell} + \frac{\alpha}{2}(n - \frac{\numax}{\dnu} + \epsilon)^2\right) + m\nu_{s}\, ,
+\end{equation}
+
+\noindent where \dnu is the large frequency separation between two consecutive radial orders, $\epsilon$ is a a phase offset, $\delta\nu_{0,\ell}$ is the small frequency separation between two oscillation modes of different $\ell$ at the same radial order, $\alpha$ describes the curvature of the spacing around \numax, and $\nu_s$ is the rotational splitting.
+Note that here we have expressed the small separation $\delta\nu_{0,\ell}$ as a fraction of $\dnu$.
+In order to improve the computational efficiency of this analysis, we fixed \dnu to the values reported in LEGACY and Kages.
+
+Instead of calculating mode frequencies directly from Equation \ref{eq:asymptotic} for the model, we treated the individual mode frequencies as parameters as well, drawn from Equation \ref{eq:asymptotic}.
+This is called a `latent parameter' implementation \cite{hogg2012, hall+2019}, as it forms a step between the parameters we want to draw inference on (also called hyperparameters) and our data.
+The parameters $\nu_{n,\ell,m}$ were allowed to vary within an uncertainty $\sigma_{\ell}$, which has a single value for each angular degree and also varied as a free parameter.
+This allowed us to account for small shifts in frequency due to sudden changes in the stellar structure \cite[called acoustic glitches]{mazumdar+2014}.
+The mode frequency latent parameters were drawn from a normal distribution using Equation \ref{eq:asymptotic} as its mean function, as
+
+\begin{equation}
+	\nu_{n, \ell, m} \sim \mathcal{N}(\nu_{n, \ell, m}, \sigma_{\ell})\, ,
+\end{equation}
+
+\noindent where the expression $\nu_{n, \ell, m}$ on the right hand side represents the contents of Equation \ref{eq:asymptotic}, and $\mathcal{N}$ represents a normal distribution with a mean equal to $\nu_{n, \ell, m}$ and a standard deviation equal to $\sigma_{\ell}$.
+The symbol `$\sim$' indicates that the parameters on the left hand side of the equation are drawn from the probability distribution on the right hand side.
+This notation will be used throughout this paper.
+
+\subsubsection{Mode Linewidth}
+The linewidths of asteroseismic p modes vary roughly as a function of mode frequency, and do so slowly relative to \dnu.
+This can be expressed as an empirical relation \cite{davies+2014, appourchaux+2016, lund+2017}.
+However, this relation has six free parameters, none of which are directly relevant to this work.
+Instead of fitting this relation, we chose to employ a more flexible Gaussian Process \cite[GP]{rasmussen+williams2006} to act as a prior on the linewidths.
+This can be considered as us modelling the linewidths as correlated measurements.
+As our GP covariance kernel we used a Squared Exponential Kernel to capture the slight periodicity of linewidth with frequency, as
+
+\begin{equation}\label{eq:gpkernel}
+	K_{i,j} = \rho^2 \exp \left[ -\frac{(n_{\textrm{f}, i} - n_{\textrm{f}, j})^2}{2L^2} \right]\, ,
+\end{equation}
+
+\noindent where $n_{\rm f}$ is the fractional radial order of a given mode.
+For each star, the overtone numbers $n$ were rescaled to be between 0 (for the lowest $n$) and 1 (for the highest $n$)\footnote{Overtones of $\ell = 2$ modes were increased by $1$ to ensure this approximation applied to all modes.}.
+This approximation was used to describe the change in linewidth as a function of frequency without depending on the exact frequencies of the modes.
+$K_{i,j}$ represents an element of the covariance matrix $\underline{K}$, describing the covariance between two values of linewidth at different fractional radial orders.
+The GP kernel has two hyperparameters: $\rho$, which determines the spread of the kernel, and $L$, which determines the length scale in terms of $n_{\rm f}$.
+The length scale was significantly larger than the large frequency separation (\dnu) in all cases, and so we considered the use of fractional radial orders a valid approximation in this model.
+
+A linear function was used for the mean of the GP, as
+
+\begin{equation}\label{eq:gpmean}
+	\mu = m \times n_{\textrm{f}} + c\, ,
+\end{equation}
+where $m$ and $c$ are the slope and intercept of the line. The linewidth latent parameters were then drawn from the multivariate probability distribution
+
+\begin{equation}\label{eq:gammagp}
+	\Gamma \sim \mathcal{N}(\mu, \underline{K})\, ,
+\end{equation}
+
+\noindent where $\Gamma$ represents the linewidths of all the modes in the model. The parameters $m$, $c$ and $\rho$ were marginalised over, whereas $L$ was fixed to a pre-determined value.
+
+\subsubsection{Mode Heights and Angle of Inclination}
+The height in power of each mode, $H_{n, \ell, m}$, varies not only as a function of distance in frequency from \numax, but also due to observation conditions, such as inclination angle and passband.
+In our model, we treated $H_{n, \ell, m}$ as a deterministic parameter, as
+
+\begin{equation}\label{eq:height}
+	H_{n, \ell, m} =  \varepsilon_{\ell, m}(i) \frac{2 (A_{n, \ell})^2}{\pi \Gamma_{n, \ell}}\, ,
+\end{equation}
+
+\noindent where $\varepsilon_{\ell, m}(i)$ modulates the height as a function of inclination angle ($i$) (see below), and $A_{n, \ell}$ and $\Gamma_{n, \ell}$ are the mode amplitude and linewidth respectively for a given radial order and angular degree.
+Instead of modeling and modulating height directly, we instead sampled in amplitude and linewidth.
+This approach mitigates the correlations between height and linewidth in the sampling process \cite{toutain+appourchaux1994}.
+
+As done above for the mode frequencies and linewidths, the mode amplitudes $A_{n,\ell}$ were also treated as latent parameters drawn from a probability distribution governed by hyperparameters.
+We used a Gaussian function $G(\nu)$, centered on $\numax$, so that
+
+\begin{equation}\label{eq:amplitude}
+	G(\nu) = A \times \exp\left[-\frac{(\nu - \numax)^2}{2w^2}\right]\, ,
+\end{equation}
+
+\noindent where $A$ is the amplitude at \numax, and $w$ is the width of the Gaussian, both free parameters in our model. 
+The mode amplitude latent parameters were then drawn from the probability distribution
+
+\begin{equation}
+	A_{n, \ell} \sim \mathcal{N}(G(\nu_{n,\ell}) \times V_\ell, \sigma_{A})\, ,
+\end{equation}
+
+\noindent where $V_\ell$ is a free parameter for the mode visibility of different angular degrees, which should be consistent for all \kepler observations.
+The mode visibility for $V_0$ is fixed at 1, and $V_{1,2}$ are treated as free parameters.
+The parameter $\sigma_{A}$, the uncertainty on the distribution, is also a free parameter, and takes the same value for all amplitudes regardless of angular degree.\\
+
+The angle of inclination of a star with respect to Earth changes the net perturbation by a given mode when integrated across the stellar disc, changing the amplitudes of modes of different azimuthal orders.
+This is a geometric problem, and is expressed by $\varepsilon_{\ell, m}(i)$, which takes the form \cite{gizon+solanki2003}
+
+\begin{equation}\label{eq:legendre}
+	\varepsilon_{\ell, m}(i) = \frac{(\ell - |m|)!}{(\ell + |m|)!}\left[P_\ell^{|m|}(\cos(i))\right]^2\, ,
+\end{equation}
+
+\noindent where $P_\ell^{|m|}$ are associated Legendre functions. For the first three angular degrees, Equation \ref{eq:legendre} takes the form \cite{handberg+campante2011}
+
+\begin{equation}
+	\begin{split}
+		\varepsilon_{0,0}(i) &= 1\, ,\\
+		\varepsilon_{1,0}(i) &= \cos^2(i)\, ,    \\
+		\varepsilon_{1,\pm1}(i) &= \frac{1}{2}\sin^2(i)\, ,\\
+		\varepsilon_{2,0}(i) &= \frac{1}{4}(3\cos^2(i) - 1)^2\, ,\\
+		\varepsilon_{2,\pm1}(i) &= \frac{3}{8}\sin^2(2i)\, ,\\
+		\varepsilon_{2,\pm2}(i) &= \frac{3}{8}\sin^4(i)\, ,
+	\end{split}
+\end{equation}
+
+\noindent where the sum of available components for a single $\ell$ are normalized to one.
+
+\subsubsection{Likelihood Function}\label{sec:like}
+If data have Gaussian noise in the time domain, they will appear in the frequency domain with noise following a $\chi^2$ distribution with two degrees of freedom \cite[$\chi^2_2$ hereafter][]{woodard1984}.
+The noise properties of $\chi^2_2$ distributed data are multiplicative, and require a specific treatment when fitting a model.
+As our frequency bins can be approximated to be independent, we used the likelihood function \cite{anderson+1990},
+
+\begin{equation}
+	\ln p(\mathcal{P} | M) = \sum_{j=0}^{N-1} \left[\ln[M_j(\nu)] + \frac{\mathcal{P}_j}{M_j(\nu)}\right]\, , 
+\end{equation}
+
+\noindent where $\mathcal{P}$ is the power spectral density (and thus our data), and $M(\nu)$ represents our model.
+The subscript $j$ denotes an individual datum, for a total of $N$ data.
+We have omitted the dependence of the model $M(\nu)$ on its parameters, for clarity.
+This equation is functionally equivalent to the evaluation of a gamma distribution of the form $\gamma(\mathcal{P} | 1, \beta)$, where $\beta = 1/M(\nu)$, which is the implementation we used in the sampling process.
+
+\subsubsection{Fitting the convective background}\label{sec:background}
+Fitting the convective background, apodization and white noise component must be done for the full range of the power spectrum in order to be accurately constrained.
+However, fitting a single model to the full range of frequencies is computationally inefficient when we are interested in the modes of oscillation, as these occupy a relatively small range of frequencies.
+
+In order to speed up this process, the background was first fit independently to a subset of our data for each star.
+This subset was created by removing all frequencies within a range $0.1 \times \dnu$ below and above the minimum and maximum mode frequencies reported in LEGACY and Kages.
+For KIC 3427720 we also removed frequencies in the range $90\, \mu\rm{Hz} < \nu < 400\, \mu{\rm{Hz}}$, where there were large peaks not of asteroseismic origin, skewing the background fit.
+
+For each star the model function (see Eq. \ref{eq:model}) was fit, as
+
+\begin{equation}
+	M_{B}(\nu) = W + \eta^2(\nu)B(\nu)\, ,
+\end{equation}
+
+\noindent where $B(\nu)$ is the background model described in Equation \ref{eq:background}.
+The parameter components of our background fit are then $\phi_B = \{\log(a), \log(b), \log(c), \log(d), \log(j), \log(k), W, \nu_{\rm nyq}\}$, where the parameters of the Harvey components were sampled in log space.
+The model was fit to the background data using \texttt{PyStan} \cite{vanhoey+2013}, run for 10,000 iterations on each star\footnote{These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work.}.
+
+\subsubsection{Obtaining First Guesses and Prior Values}
+In order to utilise some of the prior measurements of our targets without using them as hard constraints on our parameters, some of our model equations were fit to LEGACY and Kages data to obtain first guesses and mean values on hyperparameter priors.
+
+For first guesses for parameters in the asymptotic expression, we fit Equation \ref{eq:asymptotic}, \textit{not} including the rotational component $m\nu_s$, to the $\ell = (0, 1, 2)$ mode frequencies reported in LEGACY and Kages for each star, using their reported uncertainties.
+This yielded estimates of $\hat{\epsilon}$, $\widehat{\delta\nu}_{01}$, $\widehat{\delta\nu}_{02}$ and $\hat{\alpha}$, where the hat symbol `\, $\widehat{}$\, ' indicates a prior value (e.g.
+$\hat{\nu}_{\rm max}$ is taken from LEGACY or Kages).
+While not precise, as we did not mitigate any perturbations due to acoustic glitches (sudden changes in interior sound speed, which the latent parameter treatment takes care of in the full model), these rough results act as functional first guesses and prior mean values.
+The relation was fit to each star using PyMC3 \cite{salvatier+2016} using 5000 iterations on 4 chains.
+
+To obtain first guesses for the parameters used to set the GP prior on linewidth, we fit a GP constructed as in Equation \ref{eq:gammagp} to the linewidths of the $\ell = 0$ modes reported in LEGACY.
+Linewidths were not reported for the other angular degrees in LEGACY, but the estimates may be generalised to other $\ell$, as linewidth is a strong function of frequency.
+The relation was fit to each star using PyMC3 using 2500 iterations on 4 chains.
+
+Fitting the LEGACY linewidths yielded rough estimates of $\hat{m}$, $\hat{c}$, $\hat{\rho}$ and $L$ for each star.
+As is noted in Equation \ref{eq:gammagp}, $L$ was fixed to this fit value when fitting our full model to our data.
+For stars in Kages, for which no linewidths were reported, we instead fixed these prior values to $\hat{m} = 1$, $\hat{c} = 0.5$, $\hat{\rho} = 0.1$, and the length scale to $L = 0.3$.
+These values were chosen to reflect those found for the LEGACY stars.
+
+Finally, we obtained prior values for the Gaussian function describing the distribution of mode amplitudes around \numax.
+The mode amplitude of the highest peak in the spectrum was used for the amplitude, which was typically at or near \numax.
+For the width of the Gaussian we used the empirical function \cite{lund+2017}
+
+\begin{equation}
+	\hat{w} = 0.25 \times \numax\, .
+\end{equation}
+
+\noindent For the mode visibilities, we used $\hat{V}_1 = 1.2$ and $\hat{V}_2 = 0.7$, which reflect the results for these parameters reported in the LEGACY catalogue.
+
+\subsubsection{Priors on our Hyperparameters}
+Given our first guesses and measured prior values, we can define the prior probabilities of the hyperparameters on which our model depends. For the mode frequency hyperparameters, these are
+
+\begin{equation}
+	\begin{split}
+		\numax &\sim \mathcal{N}(\hat{\nu}_{\rm max}, 10)\, ,\\
+		\epsilon &\sim \mathcal{N}(\hat{\epsilon}, 1)\, ,\\
+		\alpha &\sim \ln\mathcal{N}(\ln(\hat{\alpha}), 0.01)\, ,\\
+		\delta\nu_{01} &\sim \ln\mathcal{N}(\ln(\widehat{\delta\nu}_{01}), 0.1)\, ,\\
+		\delta\nu_{02} &\sim \ln\mathcal{N}(\ln(\widehat{\delta\nu}_{02}), 0.1)\, ,\\
+		\sigma_{0,1,2} &\sim \mathcal{C}_{1/2}(\beta = 2)\, ,
+	\end{split}
+\end{equation}
+
+\noindent where $\ln\mathcal{N}$ represents a log-Normal distribution and $\mathcal{C}_{1/2}$ represents a half-Cauchy distribution, and other symbols are as described above.
+All three hyperparameters $\sigma_{0,1,2}$ describing the uncertainty on the latent parameters of different angular degree were subject to the same prior.
+
+For the mode linewidths, our hyperparameter priors took the form
+
+\begin{equation}
+	\begin{split}
+		m &\sim \mathcal{N}(\hat{m}, 1)\, ,\\
+		c &\sim \mathcal{N}(\hat{c}, 1)\, ,\\
+		\rho &\sim \ln\mathcal{N}(\ln(\hat{\rho}), 0.1)\, ,\\
+	\end{split}
+\end{equation}
+
+\noindent where the conventions are the same as above. For our mode amplitudes, they took the form
+
+\begin{equation}
+	\begin{split}
+		w &\sim \ln\mathcal{N}(\ln(\hat{w}), 10)\, ,\\
+		A &\sim \ln\mathcal{N}(\ln(\hat{A}), 1)\, ,\\
+		V_1 &\sim \ln\mathcal{N}(\ln(\hat{V}_1), 0.1)\, ,\\
+		V_2 &\sim \ln\mathcal{N}(\ln(\hat{V}_2), 0.1)\, ,\\
+		\sigma_A &\sim \mathcal{C}_{1/2}(\beta = 1)\, .
+	\end{split}
+\end{equation}
+
+As the convective background had already been fit to our data excluding the region where the modes are present, the results from that fit could be used as extremely informative priors on our fit to the region containing the modes, where there is little information present to constrain the background.
+To do so, we modeled the background parameters $\phi_B$ in our full model as being drawn from a multivariate normal distribution as
+
+\begin{equation}
+	\phi_{B}\sim\mathcal{N}(\hat{\phi}_{B},\underline{\Sigma}_{\hat{\phi}_{B}})\, ,
+\end{equation}
+
+\noindent where $\hat{\phi}_B$ are the median values of our posterior distributions from our prior background fit, and $\underline{\Sigma}_{\hat{\phi}_{B}}$ is the full covariance matrix of all the posterior distributions from our prior background fit, taking into account the correlations between the different Harvey components.
+
+Finally, we defined the priors on the rotational parameters: the mode splitting ($\nu_s$), and the inclination angle ($i$).
+In order to give these an appropriate treatment, we made two reparameterizations.
+First, we sampled the projected rotational splitting, $\nu_{\rm{s}}\sin(i)$, which is more efficiently sampled due to the strong correlations between $i$ and $\nu_{\rm s}$ \cite{ballot+2006,ballot+2008a}.
+A prior was applied over this as
+
+\begin{equation}
+	\nu_s\sin(i) \sim \ln\mathcal{N}(\ln(0.75), 0.75)\, ,
+\end{equation}
+
+\noindent where conventions are as above.
+This subjective prior was chosen to reflect that most stars will have a solar-like rotation, with a long tail to allow for the fastest rotators.
+Second, we sampled in $\cos(i)$, and gave this a prior of
+
+\begin{equation}
+	\begin{split}
+		\cos(i) &\sim \mathcal{U}(0, 1)\, ,
+	\end{split}
+\end{equation}
+which is equivalent to stating that probability to observe an inclination angle $i$ is equal to $\sin(i)$.
+Here, the $\mathcal{U}(0,1)$ indicates a uniform prior between 0 and 1.
+Using a uniform prior on $\cos(i)$ allowed us to account for the geometric effect that stars with a large inclination angle with respect to us are more common \cite{chaplin+basu2017}.
+
+\subsubsection{Fitting procedure}
+Using our prior information and model described above, we fit Equation \ref{eq:model} to our data $\mathcal{P}$, using the likelihood function described in Section \ref{sec:like}.
+
+In order to speed up the fitting process, we only applied our model to the region of the power spectrum that contains visible modes of oscillation.
+We created this subset by removing all frequencies outside a range $0.25 \times \Delta\nu$ below and above the minimum and maximum mode frequencies reported in LEGACY and Kages.
+This region overlaps minimally with the data used to fit for our prior information of the convective background (see Section \ref{sec:background}), so that both model fits are independent.
+
+To improve computational efficiency, we reduced the number of oscillation modes being fit in five targets.
+For 16 Cyg A \& B, KIC 7970740 and KIC 8478994, we excluded any modes with a Bayes Factor ($\ln(K)$) of less than 6, as reported in LEGACY \cite{kass+raftery1995,davies+2016,lund+2017}.
+For KIC 8478994, which is reported without a value for $\ln(K)$ in Kages, we only included modes of an overtone number that contained a detection for all of $\ell = (0, 1, 2)$, retaining 5 sets of higher signal-to-noise overtones.
+We do not expect this reduced scope to bias our results, although they may reduce the precision on our measured rotation rates.
+
+We fit our model to our power spectrum data with \texttt{PyMC3}, using 2500 iterations each on 4 chains.
+An example of our model fit to an asteroseismic power spectrum of 16 Cyg A is shown in Figure \ref{fig:modelfit}.
+
+\section{Gyrochronology Methods}\label{s:gyro}
+\subsection{Stellar Models}\label{ssec:models}
+The braking models used in this work have several parameters that inform the rotational evolution.
+These are: a normalization factor to reproduce the solar rotation ($f_k$); a disk locking timescale ($T_{\rm disk}$) and period ($P_{\rm disk}$) which together regulate the stellar angular velocity during the pre-main sequence; the critical angular velocity that marks the transition from saturated (rapidly rotating) to unsaturated (slowly rotating) regimes ($\omega_{\rm crit}$), and the critical Rossby number, above which stars conserve angular momentum ($Ro_{\rm crit}$), mentioned above.
+$T_{\rm disk}$, $P_{\rm disk}$ and $\omega_{\rm crit}$ are calibrated to match the behavior in young open clusters, but have little impact on the rotational evolution beyond $\approx 1\, \rm{Gyr}$ in solar-mass stars.
+Both $f_k$ and $Ro_{\rm crit}$ affect the late-time evolution.
+Both models adopt $\omega_{\rm crit} = 3.4  \times 10^{-5}\, \rm{s}^{-1}$, $P_{\rm disk} = 8.1$, $T_{\rm disk} = 0.28$ and $f_k = 6.6$.
+In the weakened magnetic braking model, $Ro_{\rm crit} = 1.97$.
+For further details, see \cite{vansaders+pinsonneault2013} and \cite{vansaders+2016, vansaders+2019}.
+
+Instead of comparing asteroseismic measurements of age and rotation directly to rotational models of individual stars, we instead compared them to synthetic populations based on rotational models, similar to those presented in \cite{vansaders+2019}, with some adaptations.
+To construct a synthetic population of rotating stars, \cite{vansaders+2019} applied the rotational braking laws described above to a galactic population model.
+Their approach used a TRILEGAL \cite{girardi+2012} Milky-Way simulation of the \kepler field, using the standard population values intended for this purpose from \cite{girardi+2015}.
+Stars from the TRILEGAL simulations were then drawn randomly in bins until they matched observations of stellar parameters of the \kepler field \cite{mathur+2017}.
+This aimed to replicate the \kepler selection effect, by ensuring the TRILEGAL population properties matched those observed in the \kepler field.
+
+We used the same approach here, with two changes.
+First, we updated the distribution of stellar parameters matched to the TRILEGAL populations.
+Instead of \cite{mathur+2017}, we used the \cite{berger+2020} temperatures and luminosities, and 2MASS $K$-band magnitudes as our stellar parameter distributions for the \kepler field, which are more accurate following the use of \gaia DR2 parallaxes \cite{gaiacollaboration+2018}.
+The TRILEGAL simulation was matched to the \cite{berger+2020} sample using a nearest-neighbours approach (as opposed to binning), based on the density of stars on the HR diagram.
+
+Second, we made further changes to account for possible binarity in the the \cite{berger+2020} sample.
+If the first step is performed blindly, blended binaries in the sample cause an overestimation of the number of old stars.
+In order to overcome this, we:
+
+\begin{enumerate}
+	\item blended the TRILEGAL stars with binary companions drawn from a flat mass-ratio distribution, using the binary fraction of \cite{raghavan+2010},
+	\item recalculated the `observed' luminosities and magnitudes assuming that each binary pair was blended, and
+	\item shifted these stars' temperatures following the $g$-$K$ relation presented in \cite{berger+2020}.
+\end{enumerate}
+
+This new distribution was used for the nearest-neighbour matching.
+Once drawn we dropped the binary companion and used the true TRILEGAL properties of those stars.
+For stars where the mass of the companion was $M < 0.4\, M_\odot$, binary contributions were ignored.
+Every binary was assumed to result in a blend, regardless of separation.
+This results in slightly more young stars than reality, because young, blended binary systems contaminate regions of the HR diagram where one expects to find old stars, and the number of blends is overestimated by assuming every binary system is a blend.
+
+Our asteroseismic sample of stars with short cadence observations are subject to additional selection functions not included in the creation of the model populations above.
+We did \textit{not} explicitly account for these asteroseismic selection functions in our model, by design.
+Both the standard and WMB models contain stars with the same fundamental parameters (mass, radius, effective temperature, metallicity) but a different period based on the choice of rotational evolution prescription.
+Applying an asteroseismic selection function that depends on these fundamental parameters \cite{chaplin+2011} would apply an identical prior to both models, therefore providing no net effect on our posterior distribution.
+Additionally, we expected any seismic selection function to be relatively flat (and therefore uninformative) on a star-by-star scale, on which we run our model analysis (as opposed to a population scale, see below).
+
+\subsection{Bayesian Mixture Models}
+In order to determine whether weakened magnetic braking occurs on the main sequence, we compared our sample of seismic age and rotation, along with temperature, metallicity and mass, to the two stellar population models of the \kepler field adapted from \cite{vansaders+2019}, discussed above.
+Both stellar models were evaluated in a Bayesian framework, with the rationale of determining which of the two models (standard or WMB) is most likely to reproduce our observed data.
+Each model sample contained temperature (\teff), mass ($M$), age ($t$), metallicity ($\rm{[Fe/H]}$) and rotation ($P$) information.
+
+In order to draw probabilistic inference about the models, we built a five-dimensional Kernel Density Estimate (KDE) of both model populations using the \texttt{statsmodels} package \cite{seabold+perktold2010}.
+We used a band-width (setting the resolution of the KDE) of $0.02\, M_\odot$ in mass, $10\, \rm K$ in \teff, $0.01\, \rm{dex}$ in $\ln(t)$, $0.01\, \rm{dex}$ in $\rm{[Fe/H]}$ and $0.01\, \rm{dex}$ in $\ln(P)$.
+Note that age and rotation were treated in log space, where the posterior estimates from asteroseismology more closely resemble normal distributions.
+This approach translates the population models to a probability distribution we can use in a Bayesian framework.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.45\textwidth]{pgm_models.pdf}
+	\caption{A probabilistic graphical model (PGM) represented algebraically in Equation \ref{eq:modelll}.
+The shaded circle indicates observed data, and solid black points represent other fixed information, such as the KDEs and observational uncertainties.
+The remaining circles represent parameters.
+The underline indicates that the symbol represents a set of parameters or data.
+Here, $\kappa_{\rm{s}}$ and $\kappa_{\rm WMB}$ represent the KDEs of standard and WMB model populations respectively.
+$P_{\rm{s}}$ is the mixture model weighting factor.
+The latent parameters $\underline{\theta}$, our observations $\underline{\mathcal{D}}$ and their uncertainties $\underline{\sigma_{\mathcal{D}}}$ include temperature (\teff), mass ($M$), log-age ($\ln(t)$), metallicity (\feh) and log-rotation ($\ln(P)$).
+This model is \textit{hierarchical}, as all the latent parameters are drawn from the common probability distribution set by $P_{\rm{s}}$ and described in Equation \ref{eq:mixturell}.}
+	\label{fig:pgm}
+\end{figure}
+
+We evaluated our data against both models simultaneously by treating the data as being drawn from a mixture of both model KDEs.
+In this mixture model structure, the two KDEs were modulated by a weighting factor, $P_{\rm s}$.
+In the limit $P_{\rm s} \rightarrow 1$, the data are most likely drawn from the standard model.
+In the limit $P_{\rm s} \rightarrow 0$, the data are most likely drawn from the WMB model.
+
+The posterior probability of obtaining $P_{\rm s}$ and additional parameters $\theta$ given our data $\mathcal{D}$ is $p(P_{\rm{s}}, \theta | \mathcal{D})$.
+Using Bayes equation, we can express this as:
+
+\begin{equation}\label{eq:modelll}
+	p(P_{\rm{s}}, \theta | \mathcal{D}) \propto p(\mathcal{D} | \theta)\ p(\theta | P_{\rm{s}}, \kappa_{\rm{s}}, \kappa_{\rm{WMB}})\ p(P_{\rm{s}})\, ,
+\end{equation}
+
+\noindent where $\kappa_{\rm{s}}$ and $\kappa_{\rm{WMB}}$ are the KDE functions for the standard and WMB models respectively, and $\theta$ here are parameters, $\theta = \{M, \teff, \ln(t), \feh, \ln(P)\}$.
+As done above for the asteroseismic model, the parameters $\theta$ may be referred to as latent parameters, as they form a step between the parameter we want to infer ($P_{\rm{s}}$) and our data.
+Using this approach allowed our model to properly take into account the observational uncertainties on the data.
+
+The second component on the right hand side of Equation \ref{eq:modelll} describes the probability of obtaining our latent parameters $\theta$ given our KDEs and the mixture model weighting parameter $P_{\rm s}$, and is described by the mixture model
+
+\begin{equation}\label{eq:mixturell}
+	p(\theta | P_{\rm{s}}, \kappa_{\rm{s}}, \kappa_{\rm{WMB}}) = P_{\rm s} \times \kappa_{\rm s}(\theta) + (1 - P_{\rm s}) \times \kappa_{\rm WMB}(\theta)\, ,
+\end{equation}
+
+\noindent where all parameters are as described above.
+This probability function describes a distribution that is a mixture of both KDEs.
+While the KDEs are constant, $P_{\rm s}$ is a free parameter, and so the shape of this distribution can vary.
+The latent parameters $\theta$ are drawn from this distribution, and therefore from some combination of the two stellar models.
+
+The first component in Equation \ref{eq:modelll} describes the likelihood of obtaining the parameters $\theta$ given our data and their observational uncertainty. It takes the form
+
+\begin{equation}
+	p(\mathcal{D} | \theta) = \mathcal{N}(\mathcal{D} | \theta, \sigma_{\mathcal{D}})\, ,
+\end{equation}
+
+\noindent a normal distribution evaluating the latent parameters $\theta$ against the observations, with observational uncertainty $\sigma_{\mathcal{D}}$.
+This approach means that in each parameter space (such as age), the age drawn from the stellar model mixture is entered into the likelihood equation with our static observations.
+The value of this equation (and thus the likelihood) will increase if $\theta$ is closer to the observations, and the mixture model will be modulated in a manner that maximises this probability, inferring whether one stellar model is more likely to produce our data than the other.
+
+The final term, $p(P_{\rm s})$, represents the prior on the mixture model weight, which is uniform between 0 and 1. A visual representation of our model is shown in Figure \ref{fig:pgm}.
+
+Typically, this model would evaluate all stars in our sample against the stellar models simultaneously for a single posterior estimate of $P_{\rm s}$.
+At 95 stars, in 5 parameter spaces, this totals 476 free parameters to marginalise over.
+This is not an issue for Hamiltonian Monte Carlo \cite[HMC]{betancourt+girolami2013}, however the use of KDE functions, over which a probabilistic gradient can not be measured, reduces HMCs effectiveness.
+Alternative Markov Chain Monte Carlo techniques \cite[MCMC]{foreman-mackey+2013} can more efficiently sample the KDE functions, but can not treat the large number of hierarchical parameters.
+To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $P_{\rm s}$, and multiplied these post hoc to obtain a combined posterior.
+This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications (see Section \ref{s:class}), at the expense of the ability to marginalise for a single value of $P_{\rm s}$ directly.
+
+\subsubsection{Fitting procedure}
+The parameter space of the stellar models was reduced before calculating the KDEs.
+These cuts were made in $M$, $\teff$, $\ln(t)$ and \feh, removing any stars in the models that fell more than $3 \times \sigma_{\mathcal{D}}$ outside the observations.
+Our observables $M$, $t$ and $P$ have asymmetric uncertainties from the Bayesian asteroseismic analysis.
+We used the larger of the reported uncertainties on each parameter as $\sigma_{\mathcal{D}}$ in each parameter space.
+
+KIC 6278762 was excluded from this stellar model analysis, because its age fell more than $3\sigma$ outside of the highest age in the stellar models\footnote{This is a metallicity issue, as the oldest stars have metallicities outside the range of the rotational model grids.}, and KICs 7106245 and 8760414 were excluded for the same reason due to low metallicities outside the functional range of the stellar models (-0.99 and -0.92 respectively).
+
+We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{foreman-mackey+2013}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.
+
+After fitting, we took a normalised histogram of the posterior estimate of $P_{\rm s}$ for each star, using 100 bins.
+In this histogram, each bin approximated the value of the posterior function for $P_{\rm s}$.
+The array of 100 bins for all stars were multiplied, resulting in an approximation of the joint posterior probability function for $P_{\rm s}$ given all stars in the ensemble.
+
+\section{Verifying asteroseismic results}
+\subsection{Priors on rotational parameters}
+In our Bayesian analysis, we have placed weakly informative priors on our sampled rotational parameters, $\nu_{\rm s}\sin(i)$ and $\cos(i)$ (see Section \ref{s:seismo}).
+The prior is especially important for the angle of inclination, which is hardest to infer from the data.
+We are able to validate the robustness of our asteroseismic results by confirming that their posterior distributions are data-dominated, and not prior-dominated.
+We can do so by comparing the $68\%$ credible regions of the posterior estimates of $\nu_{\rm s}\sin(i)$ and $i$ against the $68\%$ credible regions of their priors.
+
+A comparison between prior and posterior is shown for 94 stars in $\nu_{\rm s}\sin(i)$, $i$ and $P_{\rm rot}$ in Figure \ref{fig:priors}, arranged by age.
+In the Figure, results with means and error bars that closely resemble the prior distribution can be interpreted as prior-dominated (i.e.
+poorly informed by the data).
+The projected splitting, $\nu_{\rm s}\sin(i)$, is overall well constrained, with only one star appearing prior dominated.
+This is expected, as the projected splitting is what we observe on the star before decoupling inclination and rotation.
+The angle of inclination $i$, sampled as $\cos(i)$, more closely follows the prior distribution in most cases.
+Combining the two, the rotation period $P_{\rm rot}$ has no stars directly corresponding to the effective prior on period, and globally follows a trend with increasing age.
+The three outliers with fast rotation at late ages (KICs 6603624, 8760414 and 8938364) are discussed in more detail in Section \ref{ssec:litcomp}.
+
+The rotation rates as presented in this work are a product of our Bayesian sampling of both projected splitting and angle of inclination.
+As seen in Figure \ref{fig:priors} there are instances where $i$ or $\nu_{\rm s}\sin(i)$ closely resemble the prior (and are therefore prior-dominated).
+There are no cases of this when looking at the resulting period measurements, as they will have been informed by at least one strongly data-driven parameter (judging from Figure \ref{fig:priors}, commonly $\nu_{\rm s}\sin(i)$).
+From this, we conclude that our ensemble of asteroseismic rotation is not strongly dominated by the priors imposed on projected splitting and inclination in our Bayesian analysis.
+
+\subsection{Comparisons to previous studies}\label{ssec:litcomp}
+In order to validate our results, we compared our rotational parameters to those obtained in the literature, as well as those resulting from the work presented in LEGACY and Kages, which were unreported and received through private communication by the authors of the catalogue papers.
+
+Comparisons with LEGACY and Kages are shown in Figure \ref{fig:legacykages} for projected splitting, inclination angle, and rotation period.
+In all three cases we show the fractional difference between the values obtained in this work and those from LEGACY and Kages.
+On the right of Figure \ref{fig:legacykages}, we show the distribution of the fractional differences for the three parameters.
+The projected splitting is in good agreement with both studies, however LEGACY finds slightly lower $\nu_{\rm s}\sin(i)$ for the faster rotators, deviating from our work by over $1\sigma$.
+Neither LEGACY nor Kages used a spatially isotropic prior for the inclination angle in their analyses, instead opting for a uniform prior.
+As posterior estimates of inclination angle are only loosely data-driven, the introduction of an isotropic prior should result in our analysis reporting globally higher inclination angles.
+This effect is seen in the comparisons of both inclination angles and rotation rates for the LEGACY stars, where we find overall lower rotation rates compared to LEGACY for stars at very similar $\nu_{\rm s}\sin(i)$.
+
+A number of stars are excluded from Figure \ref{fig:legacykages} and compared individually as extreme outliers: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have fast rotation rates ($<5\, \rm days$) in Kages, but are found to have a broader spread of rotation rates in this work.
+At similar values for $\nu_{\rm s}\sin(i)$, Kages found much lower inclination angles with highly asymmetrical uncertainties.
+Based on a comparison between the summary statistics of these stars, we conclude that the results found in this work have better marginalised over inclination angle, improving our measure of rotation.
+
+Conversely, KICs 6603624, 8760414 and 8938364 have extremely slow rotation periods in LEGACY, but extremely \textit{fast} ($<3\, \rm {days}$) in this work.
+KICs 8760414 and 8938364 are excluded from the gyrochronology analysis below based on checks for $\hat{R}$ and the number of effective samples.
+Both stars have ages greater than $10\, \rm Gyr$, making their fast rotation rates highly unlikely under any model of rotational evolution.
+The posterior estimate of $P$ for KIC 6603624 is well-defined in our analysis, but with an age of $7.8\, \rm Gyr$, its measured rotation of $1.2\, \rm days$ is also highly unlikely under any model of rotational evolution.
+The LEGACY estimate of rotation is similarly extreme at $378\, \rm days$.
+These three stars have the lowest inclination angles in our sample ($< 10^\circ$), at which point the power in the split components of the seismic modes is so low that it becomes difficult to probe the measure of splitting\footnote{The split components for these stars will have a height roughly 3\% of the central mode.
+For comparison, for the next lowest inclined star at $17^\circ$, this rises to $10\%$.}.
+In cases such as these with lower signal-to-noise, spurious peaks may be interpreted as split components.\\
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{Images/litcomp_alt2.pdf}
+	\caption{Comparisons between posterior estimates of rotational parameters from this work, LEGACY and Kages \cite[private communication]{davies+2016, lund+2017}.
+Fractional differences are plotted against stellar rotation obtained in this work.
+The $\Delta$ indicates the fractional difference betwen thsi work and the literature (i.e.
+stars above the zero-line have higher values in this work).
+The right hand panels the distribution of the fractional differences around the zero line.
+The colour legend is consistent throughout all panels.
+The x-axis units on the right hand panels are equivalent to the y-axis of the left hand panels.
+10 stars have been omitted from this plot and are discussed in more detail in the text: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have extremely low rotation periods in Kages, with high uncertainties.
+Conversely, KICs 6603624, 8760414 and 8938364 have extremely high rotation periods in LEGACY with low uncertainties.
+In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
+	\label{fig:legacykages}
+\end{figure*}
+
+We also compared our asteroseismic estimates of stellar rotation with similar studies in the literature, shown in Figure \ref{fig:literaturecomp}.
+These included: \cite{davies+2015}, a study of the binary solar analogues 16 Cyg A \& B; \cite{nielsen+2015}, which our catalogue shares 5 stars with; and \cite{benomar+2018}, an asteroseismic study of differential rotation with which our catalogue shares 40 targets.
+For the latter, we used their reported splitting value $a_1$, which is equivalent to $\nu_{\rm s}$.
+
+Overall, Figure \ref{fig:literaturecomp} shows no strong disagreements between our asteroseismic measurements for stellar rotation and those from the literature.
+The scatter of the fractional differences lies cleanly around the zero line, with a mean and spread of $0.0_{-15.6}^{+16.4}\, \%$.
+The increase in uncertainty with period is due to more slowly rotating stars being more difficult to constrain using asteroseismology.
+% The agreement within $1\sigma$ here is encouraging, indicating that these independent Bayesian analyses are finding appropriate uncertainties on these rotation measurements.
+
+It is of note that 16 Cyg A, as reported by \cite{davies+2015} was found to be rotating slightly faster in our analysis (deviating within $2\sigma$), despite the fit being performed on the same data.
+We found an inclination angle that is slightly lower than \cite{davies+2015} for 16 Cyg A but a similar projected splitting, which would explain finding a lower value of rotation.
+
+There are three outliers at low period in Figure \ref{fig:literaturecomp}: KICs 6603624, 8760414 and 8938364.
+These are the same targets found to be outliers in a comparison to the LEGACY and Kages measurements (see above), with anomalously fast rotation rates and low inclination angles.
+As these stars represent the lowest inclination angles in our sample, and were found to disagree with two independent studies, we opted to exclude them from the gyrochronology analysis, and to flag the rotation measurements for these three stars presented in this work.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.49\textwidth]{Images/seis_comparison_rot_alt2.pdf}
+	\caption{Fractional differences between posterior estimates of asteroseismic rotation period from this work.
+Literature sources are: \cite{davies+2015} (16 Cyg A \& B), \cite{nielsen+2015} (5 stars) and \cite{benomar+2018} (40 stars).
+We used the reported parameter $a_{1}$ from \cite{benomar+2018}, which represents the rotational splitting in the case of uniform latitudinal rotation in their model.
+The dashed line represents the median of the sample shown, with the dotted lines representing the $15.9^{\rm{th}}$ and $84.1^{\rm{st}}$ percentiles.
+In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
+	\label{fig:literaturecomp}
+\end{figure}
+
+\subsection{Internal vs external rotation}
+Different methods of rotation measurement probe different regions of stars.
+Asteroseismology of main sequence stars probes internal rotation in the near surface layers, where the observed p modes are most sensitive \cite{lund+2014}.
+Measurements of star-spot modulation instead probe the rotation rates of star spots on the surface.
+A distinct difference between rotation rates obtained through these different techniques would hold information about differential rotation (both latitudinal and radial) of near-surface layers, such as those we observe in the Sun \cite{beck2000}.
+
+\cite{nielsen+2015} performed a comparative analysis of 5 Sun-like stars observed with \kepler for which both star-spot modulation and asteroseismic rotation could be measured.
+They found no statistically significant difference between the two techniques.
+
+Similarly, \cite{benomar+2015} performed an analysis on a larger sample of 22 stars.
+In this work they not only considered rotation rates from spots, but also spectroscopic measures of the projected surface rotation $\textrm{v}\sin(i)$, which they found to be more reliable.
+Comparisons with asteroseismic observations again showed no significant radial differential rotation.
+
+With our expanded sample of asteroseismic rotation we can perform a similar analysis, to both validate our sample and probe radial differential rotation.
+Figure \ref{fig:vsinilit} shows a comparison between spectroscopic $\textrm{v}\sin(i)$ measurements as listed in LEGACY and Kages (left) and \cite{benomar+2015} (right).
+In these cases the asteroseismic $\textrm{v}\sin(i)$ has been calculated using our measure of asteroseismic $\nu_s\sin(i)$ and the known asteroseismic radii.
+Three stars (KICs 6603624, 8760414 and 8938364) have been excluded from this figure due to strong disagreements of measured rotation rates with the literature (see Section \ref{ssec:litcomp} above).
+
+For the LEGACY and Kages sample, we find no strong deviation from the 1:1 line except at very low velocities, which is likely due to biases inherent to spectroscopic line broadening measurements \cite{doyle+2014, tayar+2015}.
+For the \cite{benomar+2015} sample stars lie a lot closer to the 1:1 line.
+% , apart from one clear outlier.
+While we find no statistically significant difference between these observations, more in-depth studies of stars furthest away from the bisector in this sample may prove valuable in future work.
+
+Overall, there appears to be a global offset where spectroscopic measurements of projected rotation appear faster than asteroseismic measures.
+Based on the LEGACY and Kages $v\sin(i)$ values, this offset is roughly $18\%$ (i.e.
+spectroscopic projected rotation rates are higher than asteroseismic rates).
+This offset is much smaller ($\sim5\%$) for the \cite{benomar+2015} sample, albeit for far fewer stars.
+These offsets are within the typical disagreement between spectroscopic methods, based on comparisons of projected rotation measurements for red giant stars \cite[see Figure 2]{tayar+2015}, especially at $< 5\, \rm{km\,s^{-1}}$.\\
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{Images/vsini-comparison.pdf}
+	\caption{Comparisons between asteroseismic and spectroscopic measures of projected surface rotation, $\textrm{v}\sin(i)$.
+All asteroseismic (x-axis) values are from this work, all spectroscopic (y-axis) values are from the literature.
+\textit{Left}: comparisons to 81 stars values reported in LEGACY and Kages.
+\textit{Right}: comparisons to 16 stars observed by \cite{benomar+2015}.
+Asteroseismic values are transformed from projected splitting ($\nu_s\sin(i)$) using the asteroseismic radius measurements presented in LEGACY and Kages.
+The solid lines indicate the 1:1 line, while the dash-dotted lines represent the 2:1 and 1:2 lines.}
+	\label{fig:vsinilit}
+\end{figure*}
+
+We also repeated the \cite{nielsen+2015} comparison of asteroseismic rotation rates to surface rotation rates, using surface rotation measurements from \cite{nielsen+2013} and \cite{garcia+2014}.
+Figure \ref{fig:protlit} shows comparisons for 48 stars with rotation rates from both techniques, including 4 from the original \cite{nielsen+2015} sample.
+Rotation from spot-modulation are subject to measuring multiples of the true rotation rate, unlike an asteroseismic analysis \cite{mcquillan+2014}, and therefore some stars may appear at the 2:1 and 1:2 lines on the Figure.
+
+We repeated the analysis in \cite{nielsen+2015} by fitting a line of the form $P_{\rm surf} = m \times P_{\rm seis}$.
+For the purposes of this fit we used the larger of the asymmetrical uncertainties on the seismic rotation from this work.
+In order to avoid biasing the fit due to outliers, we only included stars below the 1.8:1 line.
+
+Our fit found a value of $m = 0.96\pm0.03$, showing a close agreement ($< 2\sigma$) between asteroseismic and surface rotation rates on a population level.
+Of the 40 stars that were part of this analysis, 21 had a median value of $P_{\rm s} < 0.5$ in the gyrochronology analysis.
+We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.
+As we find no statistically significant deviation, we conclude that our asteroseismic ensemble is in agreement with surface rotation measurements of these stars, and can therefore be used to draw inferences about gyrochronology.
+
+The overall agreement within the ensemble between the photometric measures of surface rotation and the asteroseismic rotation rates is in line with previous studies of Sun-like stars \cite{gizon+2013, chaplin+2013, nielsen+2015, benomar+2015}, where different measures of rotation appear indistinguishable.
+Individual deviations from this agreement, as appears to be the case for a number of stars that lie distinctly off the bisector, may warrant a more in-depth analysis, which we leave to future work.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.49\textwidth]{Images/surf-seis-comparison.pdf}
+	\caption{Comparisons between asteroseismic and photometric measures of stellar rotation, for 48 stars.
+Literature values were taken, in order of priority, from: \cite{garcia+2014} and \cite{nielsen+2013} (i.e.
+if a value was reported in \cite{nielsen+2013} and also in \cite{garcia+2014}, the latter was used).
+Stars used in \cite{vansaders+2016} are highlighted.
+The four triangles represent stars included in the original \cite{nielsen+2015} work.
+The solid line indicates 1:1 line, while the dash-dotted lines represent 2:1 and 1:2 lines.
+The shaded region around the 1:1 line is the $1\sigma$ credible interval of the fit to the data, the result of which is shown as the title of the figure.
+Stars that were not included in the fitting process are transparent.}
+	\label{fig:protlit}
+\end{figure}
+
+\section{Verifying consequences for gyrochronology}
+\subsection{Rotational models for different stellar types}
+Of the 73 stars for which posterior probability distributions of $P_{\rm s}$ were obtained, 4 were potential sub-giants, 22 were `hot' stars, and 47 were main sequence stars.
+Different stellar types should hold different amounts of diagnostic information about the standard or WMB models.
+Our `hot' stars should hold little to no information, as they lie above the Kraft break, where traditional gyrochronology relations used to build the stellar models break down (specifically, they do not lose angular momentum with time).
+Similarly, the rotational evolution of sub-giant stars is dominated by envelope expansion, complicating the interpretation of rotation.
+
+Figure \ref{fig:modelresults} shows joint posterior distributions for $P_{\rm s}$ for the three different stellar types, as well as their cumulative distributions.
+Both the  4 sub-giant stars and the 22 `hot' stars marginally prefer the standard model.
+The 47 MS stars on the other hand were most strongly in favour of weakened magnetic braking and dominate the full joint posterior.
+When only considering these stars, $99.2\%$ of the joint probability fell below $P_{\rm{s}} = 0.5$, compared to $98.4\%$ for all 73 stars.
+
+\subsection{Limits of our stellar models}\label{ssec:limits}
+The models presented in \cite{vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$.
+Our sample of 91 stars contained 4 stars with metallicities below $-0.4\, \rm{dex}$, which are shown as shaded symbols in Figure \ref{fig:fullmodels}.
+Of these 4, 3 were included in our final sample of 73 stars used to evaluate our stellar models: KICs 7970740, 8684723 and KIC 9965715.
+All three are classed as MS stars, with metallicities of $-0.54 \pm 0.10$, $-0.42 \pm 0.10$ and $-0.44 \pm 0.18\, \rm {dex}$ respectively, placing them within $3\sigma$ of the metallicity limits of our stellar models.
+KICs 8684723 and 9965715 strongly agree with the WMB model, whereas KIC 7970740 weakly prefers the standard model.
+Excluding these stars was not found to significantly alter the joint posterior distribution shown in Figure \ref{fig:modelresults}.
+
+Recently, \cite{amard+matt2020} compared different rotational evolution models \cite[][of which we use the former in this work]{vansaders+pinsonneault2013,matt+2015} while studying the effect metallicity has on rotation.
+They found that metal-rich stars spin down significantly more effectively than metal poor stars.
+The population of 73 stars used in our stellar model comparisons is roughly centered on a $\rm{[Fe/H]}$ of 0 $\rm dex$, with a spread of $~0.16\, \rm dex$, with no stars significantly above or below $\pm 0.4\, \rm dex$ (as discussed above).
+While differences in stellar rotational evolution as a function of metallicity in this region are still somewhat pronounced, they are much less so than for more metal-rich or poor stars \cite[see Figure 2][]{amard+matt2020}.
+However, for stars with $\feh < 0$, the \cite{matt+2015} model prescription sees stars spin down more slowly than the models used in this work (i.e.
+they will rotate faster at later ages).
+This work only explores the presence of weakened magnetic braking for a single braking law, and a comparison to the \cite{matt+2015} braking model will be explored in a future paper.
+
+When constructing KDEs from our stellar model samples (see Section \ref{s:gyro}), we selected fixed resolutions (or band-widths) for the KDEs.
+In mass, the band-width of $0.02\, M_\odot$, was larger than the uncertainties of 24 of 73 stars used to construct our joint posterior.
+For the stars with the smallest uncertainties, this significantly limits the size of the KDE being evaluated (as subsections of the full stellar models are used to evaluate individual stars, for computational efficiency).
+In order to confirm that these stars do not significantly affect the ensemble's preference towards the WMB model, we recalculated the joint posterior distribution for $P_{\rm s}$, excluding stars with an uncertainty on mass smaller than the KDE band-width.
+While the 24 stars with small uncertainties do favour the WMB model, they do so very weakly, whereas the remaining 49 stars with larger uncertainties strongly favour the WMB model.
+Their removal from the total joint posterior probability does not significantly alter it from the distribution shown in Figure \ref{fig:modelresults}.
+
+\subsection{Systematic uncertainties from asteroseismology}
+In our model analysis, we used asteroseismic mass and age obtained using \texttt{BASTA}, as reported in LEGACY and Kages.
+Asteroseismic properties obtained through stellar models can be subject to systematic errors arising from differences in input physics and choice of stellar models not included in the reported statistical uncertainties.
+A quantification of these different systematic effects can be found in Section 4 of \cite{silvaaguirre+2015}, based on the Kages catalogue.
+Combining their reported median systematic uncertainties due to input physics results in median uncertainties of $20\%$ (up from $14\%)$ on age and $5\%$ (up from $3\%$) on mass for the Kages sample.
+For LEGACY, the median uncertainties are $18\%$ (up from $10\%)$ and $5.6\%$ (up from $4\%$) for age and mass respectively.
+
+In order to check the effect of systematic seismic uncertainties on our results for gyrochronology, we re-ran our model analysis described in Section \ref{s:gyro} after inflating uncertainties on mass and age.
+We increased uncertainties by the fractional difference between the \texttt{BASTA} statistical uncertainties and the median full statistical and systematic uncertainties described above.
+For example, a LEGACY star with a mass of $2.0 \pm 0.5\, M_\odot$ would have its uncertainty inflated by $1.6\%$ of its mass, to $0.53\, M_\odot$.
+
+The results we found by repeating our model analysis with inflated uncertainties on asteroseismic mass and age closely replicated those found in our initial analysis.
+Specifically: subgiants preferred the standard model, and MS stars strongly favoured the WMB model.
+The `hot' stars in this case slightly preferred the WMB model compared to the unaltered ensemble.
+The full joint posterior distribution for 73 stars still strongly favours of the WMB model even with the inflated uncertainties, including when considering only stars on the main sequence, when excluding stars outside the models' metallicity range, and when excluding stars with low uncertainties on mass (see Section \ref{ssec:limits}).
+
+To further test the limits of this analysis, we reran our mixture model fit, this time only shifting the asteroseismic ages younger by the systematic uncertainty, and retaining the statistical uncertainty (i.e.
+the ages of LEGACY and Kages stars were reduced by $8\%$ and $6\%$ respectively).
+In this scenario where all asteroseismic ages are overestimated, `true' fast rotators at young ages would have been mistaken for fast rotators at old ages, suggesting the presence of weakened magnetic braking where none existed.
+Despite the shift in age, the results from this mixture model fit closely matched those found for the unaltered ensemble, finding $95.8\%$ of the total posterior probability to lie below $P_{\rm s} = 0.5$ (as opposed to $98.4\%$ for the unaltered ensemble).
+While the preference for the WMB model is slightly reduced, we conclude that the use of asteroseismic age is valid for the gyrochronology analyses presented in this work.
+
+\subsection{Binaries and Planet Hosts}
+For stars to be good probes of existing gyrochronology relations, their rotational evolution must occur in isolation.
+If a star interacts with a close binary companion (through tides, or a merger) the natural angular momentum loss can be disturbed, causing gyrochronology to mispredict ages \cite{leiner+2019, fleming+2019}.
+Between LEGACY and Kages, we have 8 known binaries.
+
+First, KIC 8379927, KIC 7510397, KIC 10454113 and KIC 9025370 are spectroscopic binaries.
+This does not affect the asteroseismic analysis, but may affect their rotational evolution.
+Of these, KICs 8379927, 7510397 and 9025370 were included in the gyrochronology analysis.
+None of them preferred one model strongly over the other, with all three finding flat posteriors for $P_{\rm s}$.
+% This implies that they are not yet at the Rossby number where weakened magnetic braking is proposed to take place in the models used in this work.
+
+Second, the binary pairs of KIC 9139151 \& 9139163 and 16 Cyg A \& B are individually observed binary components with wide orbital separations, so we do not expect their binarity to have affected their rotational evolution.
+
+While we chose not to account for star-planet tidal interactions in this work, we note that this may also disturb the natural stellar rotational evolution when tidal forces are at play \cite{maxted+2015,gallet+delorme2019, benbakoura+2019}, although this has been disputed by observations of asteroseismic planet hosts \cite{ceillier+2016}.\\
+
+\subsection{Evidence for Weakened Magnetic Braking in the literature}
+Weakened magnetic braking was first proposed by \cite{vansaders+2016}, in response to stars with spot rotation rates faster than expected from gyrochronology at their asteroseismic ages.
+This discrepancy was also indicated at around the same time in other studies of asteroseismic ages of main sequence stars \cite{nielsen+2015, angus+2015, davies+2015}.
+The theory of weakened magnetic braking has been both reinforced by recent studies \cite{metcalfe+egeland2019}, as well as disputed \cite{lorenzo-oliveira+2019}, at least at the critical Rossby number originally proposed.
+
+As a sanity check that the evidence in favour of weakened magnetic braking presented in this work is independently robust, we recreated the joint posterior probability for $P_{\rm s}$, this time looking only at MS stars, and excluding any of the 22 stars that were included in the original \cite{vansaders+2016} sample.
+Of the 47 MS stars used to distinguish between stellar models, 16 were included in the \cite{vansaders+2016} sample.
+Both the 16 \cite{vansaders+2016} stars as well as the remaining MS stars favoured the WMB model, although the \cite{vansaders+2016} stars did so more strongly, not including any stars that favoured the standard model.
+Specifically, when considering only the \cite{vansaders+2016} stars, $96.3\%$ of the total joint probability lay below $P_{\rm s} = 0.5$, compared to $91.7\%$ when considering only those stars \emph{not} included in the \cite{vansaders+2016} study.
+The stars initially used to propose the WMB model are still those most strongly in favour of it even when using asteroseismic rotation rates only.
+% It is encouraging that the inclusion of older, more quiescent stars and the use of asteroseismic rotation rates finds the same conclusion.}
+
+Finally, we comment on the results found by \cite{lorenzo-oliveira+2019}.
+Using spectroscopic rotation measurements of 14 solar twins, compared to grids of stellar models, they found marginal evidence favouring a standard rotational evolution.
+If weakened magnetic braking were to take place, it would most likely be outside the range of their sample, at $Ro_{\rm {crit}} \geq 2.29$, compared to the value of $1.97$ used in this work.
+Our sample does not overlap with theirs, so we can not directly compare to their results.
+However, our work does find statistical agreement between our asteroseismic rotation rates and ages, and a model of weakened magnetic braking at a critical Rossby number of $1.97$.
+While a comparison to models of different Rossby numbers is outside the scope of this study, the LEGACY and Kages rotation sample may facilitate such studies in the future.
+
+% The best way to enter references is to use BibTeX:
+%\bibliographystyle{naturemag}
+%\bibliography{library.bib} %
 

### 2020-09-28 paper/natastron/paper.tex
bla
Done with main body

@@
 
-\textbf{Studies using asteroseismic ages and rotation rates from star spot rotation have shown that standard age-rotation relations break down roughly half-way through the main sequence lifetime, a phenomenon referred to as weakened magnetic braking.
+\textbf{Studies using asteroseismic ages and rotation rates from star spot rotation have indicated that standard age-rotation relations may break down roughly half-way through the main sequence lifetime, a phenomenon referred to as weakened magnetic braking.
 While rotation rates from spots can be difficult to determine for older, less active stars, rotational splitting of asteroseismic oscillation frequencies can provide rotation rates for both active and quiescent stars, and so can confirm whether this effect really takes place in older stars.\\
@@
 Because the loss rate is related to temperature, the rotation period of a young star will rapidly settle on to a plane in age-colour-rotation space \cite{barnes2007}.
-As a result, knowing the rotation and colour of a star provides an avenue to measure it's age, which can otherwise be difficult to come by, enabling more in-depth studies of stellar populations and individual stars \cite{leiner+2019,claytor+2019}.
+As a result, knowing the rotation and colour of a star provides an avenue to measure it's age, to a precision of $\sim 10\%$ for starst most similar to the Sun \cite{meibom+2015}.
+Age can otherwise be difficult to come by, and so gyrochronology enables more in-depth studies of stellar populations and individual stars \cite{leiner+2019,claytor+2019}.
 
@@
 not in clusters) became more widely available through asteroseismology, the study of stellar variability \cite{silvaaguirre+2015}.
-When looking at these stars ,disagreements were found with gyrochronology beyond the middle of their main sequence lifetime, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}.
-It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops, causing stars to keep fast rotation rates at old ages, which we would not expected from existing gyrochronology relations.
+When looking at these stars, disagreements were found with gyrochronology beyond the middle of their main sequence lifetime, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}.
+It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops.
+This would cause stars to keep fast rotation rates at old ages, which we would not expected from existing gyrochronology relations.
 
@@
 As activity reduces with age, older stars with fewer star spots are less likely to have their rotation measured \cite{matt+2015}.
-The point at which the detection probability drops appears to lie at a similar level of activity to that at which the proposed weakened magnetic braking takes place, pitting these two possibilities against one another \cite{vansaders+2019}.
+The point at which the detection probability drops appears to lie at a similar level of activity as when the proposed weakened magnetic braking takes place, pitting these two possibilities against one another \cite{vansaders+2019}.
 
 Determining whether weakened magnetic braking is a true phenomenon or a bias in star spot observations requires new data, which can be provided by asteroseismology.
-A star's rotation causes modes of oscillation to split into multiplets, making it possible to measure the rate of rotation by measuring the splitting between oscillation frequencies \cite{ledoux1951}.
-Asteroseismic rotation is more difficult to obtain than rotation from star spots, but does not require  spots to be visible, meaning that we can measure rotation for quiescent stars that would not have been present in existing catalogues of star-spot rotation.
+A star's rotation causes modes of oscillation to split into multiplets, making it possible to obtain an independent rate of rotation by measuring the splitting between oscillation frequencies \cite{ledoux1951}.
+Asteroseismic rotation is more difficult to obtain than rotation from star spots, but does not require  spots to be visible, meaning that we can measure rotation for older, quiescent stars that would not have been present in existing catalogues of star-spot rotation.
 Previous studies have shown that asteroseismic rotation rates probe the near-surface of the star, making them comparable to spot rotation rates, and the perfect avenue to explore whether weakened magnetic braking truly takes place \cite{lund+2014, benomar+2015}.
-Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of colours and ages, and evaluate this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one where weakened magnetic braking takes place.\\
+Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of colours and ages, and evaluated this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one where weakened magnetic braking takes place.\\
 
@@
 To some degree this was expected, as  for stars viewed near pole-on the power of the split modes of oscillation are extremely small.
-We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we judge our asteroseismic rotation measurements to be robust (for a full justification, see \textit{\textbf{Methods}}).\\
-
-\textbf{Seismic versus surface rotation rates:}\\
+We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we considered our asteroseismic rotation measurements to be robust (for a full justification, see \textit{\textbf{Methods}}).\\
 
 \textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two models of rotational evolution: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model').
-The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$ (for details, see \textbf{\textit{Methods}}).
+The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$ (see \textbf{\textit{Methods}}).
 
-We evaluated our ensemble against both population models simultaneously using a Bayesian mixture model, which treated the data as being drawn from a mixture made from Kernel Density Estimates of both populations, modulated by a mixing parameter $P_{\rm s}$.
+In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting\footnote{Excluding those with a number of effective samples $n_{\rm eff} < 25\%$ and a Gelman-Rubin metric of $\hat{R}>1.1$ \cite{gelman+rubin1992,salvatier+2016}} (see \textbf{\textit{Table 1}}).
+The remaining sample of 73 stars contained 4 potential sub-giants, 22 `hot' stars and 47 main sequence stars.
+Figure \ref{fig:fullsample} shows these stars plotted over the top of both the standard and WMB population models in rotation-temperature space, alongside the stars not used in the gyrochronology analysis (shown without uncertainties).
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{fullsample.png}
+	\caption{Stars for which rotation was measured in this work, plotted over stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution.
+The 21 Stars that were excluded from the gyrochronology analysis are marked with crosses and without uncertainties (see text).
+Circles, squares and triangles denote main sequence, sub-giant, and `hot' stars respectively.
+Stars with a metallicity of $\bigl\lvert \feh \bigl\rvert > 0.4$ are coloured differently (darker), to indicate that they fall outside the functional range of the \cite{vansaders+2019} stellar models.
+Note that only period-temperature space is shown here, but when evaluating between the two model prescriptions we also considered mass, age and metallicity.}
+	\label{fig:fullsample}
+\end{figure*}
+
+We evaluated our ensemble against both population models simultaneously using a Bayesian mixture model, which treated the data as being drawn from a mixture made from Kernel Density Estimates (KDEs) of both populations, modulated by a mixing parameter $P_{\rm s}$.
 In the limit that $P_{\rm s} \rightarrow 1$, the data are mostly likely drawn from the standard model.
@@
 
-We fit our mixture model to the 73 stars in our sample with the best convergence metrics on the asteroseismic mode frequency fitting (see \textbf{\textit{Table 1}}).
-This sample included 22 `hot` stars, 4 potential sub-giants, and 47 main sequence stars.
-We calculated a joint posterior for this sample by multiplying the posterior probabilities obtained for $P_{\rm s}$ for each stars.
-This joint probability can be seen in Figure \ref{fig:gyroresults} in the left-hand plot, and the cumulative probability can be seen in the right-hand plot.
-In both of these plots, their left-hand sides hold 98.4\% of the probability, indicating that the weakened magnetic braking model is preferred.
-When only considering the main sequence stars, which are expected to be driving this distinction, this rises to 99.2\%.
+We fit our mixture model to each star individually, which yields a posterior probability density for the value of $P_{\rm s}$ for that star.
+In order to assess the posterior probability for the full sample, we multiplied the individual posterior probabilities for $P_{\rm s}$.
+This was done for the full ensemble of 73 stars, as well as for the individual stellar types.
+These joint probabilities can be seen in Figure \ref{fig:gyroresults} in the left-hand plot.
+The cumulative probability can be seen in the right-hand plot.
+In both of these plots, the left-hand side hold 98.4\% of the probability\footnote{When performing this analysis on all 91 stars for which seismic rotation was measured, this value is 96.6\%.}, indicating that the weakened magnetic braking model is preferred.
+When only considering the 47 main sequence stars, which are expected to be driving this distinction, this rises to 99.2\%.
+\\
 
@@
 
-\textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we made sure to test the same results were obtained using different subsets of the ensemble.
-Figure 3 shows ....
-[metallicity, full sample, biases, asteroseismology, van saders].\\
+\textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we made sure to test the same results were obtained using different subsets of the ensemble, and when exploring potential biases.
+We found that the joint posterior distribution did not change significantly when excluding stars with a metallicity outside the model range (purple in Figure \ref{fig:fullsample}), or when excluding stars that were included in the original study that proposed the presence of weakened magnetic braking \cite{vansaders+2016}.
+The same was true when repeating the analysis with increased uncertainties on asteroseismic mass and age, or when shifting asteroseismic ages younger by their systematic uncertainties \cite{silvaaguirre+2015, silvaaguirre+2017}.
+Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $P_{\rm s}$.
+For a full discussion of these tests and other biases, see \textbf{\textit{Methods}}.\\
+
+\textbf{Seismic versus surface rotation rates:} Different methods of rotation measurement probe different regions of stars.
+Asteroseismology of main sequence stars probes internal rotation in the near surface layers, where the observed modes of oscillation are most sensitive \cite{lund+2014}.
+Measurements of star spot modulation instead probe the rotation rates of star spots of the surface.
+Previous studies have shown that seismic rotation rates show no statistically significant deviation from spot rotation rates \cite{nielsen+2015, benomar+2015}.
+Finally, we confirm this for our larger sample to ensure that our seismic rotation periods can be reliably used to draw conclusions on the evolution of surface rotation.
+
+Figure \ref{fig:protlit} shows a comparison between 48 stars from our sample for which spot  rotation rates had previously been measured.
+Rotation rates from spot modulation are subject to measuring multiples of the true rotaiton rate, unlike asteroseismic rotation, and so some stars may appear at the 2:1 and 1:2 lines in the Figure.
+We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid outliers (transparent in the Figure).
+Our fit found a value of $m = 0.96 \pm 0.03$, showing a close agreement ($<2\sigma$) between asteroseismic and surface rotation rates on a population level.
+Of the stars used in this comparison, 21 had a median value of $P_{\rm s}$ in the gyrochronology analysis.
+We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.
+This overall agreement between photometric and asteroseismic rotation rates is in line with previous studies of Sun-like stars \cite{gizon+2013, chaplin+2013, nielsen+2015, benomar+2015}, and so we can conclude that our asteroseismic ensemble can reliably be used to draw inferences about gyrochronology.\\
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.6\textwidth]{Images/surf-seis-comparison.pdf}
+	\caption{Comparisons between asteroseismic and photometric measures of stellar rotation, for 48 stars.
+Literature values were taken, in order of priority, from: \cite{garcia+2014} and \cite{nielsen+2013} (i.e.
+if a value was reported in \cite{nielsen+2013} and also in \cite{garcia+2014}, the latter was used).
+Stars used in \cite{vansaders+2016} are highlighted.
+The four triangles represent stars included in the original \cite{nielsen+2015} work.
+The solid line indicates 1:1 line, while the dash-dotted lines represent 2:1 and 1:2 lines.
+The shaded region around the 1:1 line is the $1\sigma$ credible interval of the fit to the data, the result of which is shown as the title of the figure.
+Stars that were not included in the fitting process are transparent.}
+	\label{fig:protlit}
+\end{figure}
 
@@
 \begin{enumerate}
-	\item We found that our ensemble was $98.4\%$ more likely to be drawn from the WMB model than the standard model, for stars evolved under a standard braking law \cite{vansaders+pinsonneault2013}.
-In other words, our asteroseismic observations strongly favour a model of weakened magnetic braking \cite{vansaders+2016}, at a critical Rossby number of $Ro_{\rm{crit}} = 1.97$.
+	\item We found that our ensemble was $98.4\%$ more likely to be drawn from a weakened magnetic braking model than a standard model of rotational evolution \cite{vansaders+pinsonneault2013}, at a critical Rossby number of $Ro_{\rm{crit}} = 1.97$.
 This work expands upon previous analysis (\cite{vansaders+2019}) by including quiescent stars older than the Sun.
 This conclusion was found to be robust against choice of ensemble members and potentially underestimated asteroseismic systematic uncertainties.
-A comparison to other braking laws \cite{matt+2015} using our asteroseismic ensemble will take place in future work.
+A comparison to other braking laws \cite{matt+2015} and other gyrochronology relations using our asteroseismic ensemble will take place in future work.
 
 	\item We compared our new asteroseismic rotation rates with surface rotation measures from spot modulation.
-Our findings replicate those in similar studies (\cite{nielsen+2015,benomar+2015}), in the sense that we find no statistically significant difference between seismic and spot modulation measures of stellar rotation in our ensemble.
+Our findings replicate those in similar studies \cite{nielsen+2015,benomar+2015}, in the sense that we find no statistically significant difference between seismic and spot modulation measures of stellar rotation in our ensemble.
 
@@
 % The best way to enter references is to use BibTeX:
-\bibliographystyle{naturemag}
-\bibliography{library.bib} %
+%\bibliographystyle{naturemag}
+%\bibliography{library.bib} %
 
@@
 
+\section{Results}
+bla bla short shpiel about which values were included and which weren't
+
 \section{Verifying asteroseismic results}
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.49\textwidth]{Images/surf-seis-comparison.pdf}
-	\caption{Comparisons between asteroseismic and photometric measures of stellar rotation, for 48 stars.
-Literature values were taken, in order of priority, from: \cite{garcia+2014} and \cite{nielsen+2013} (i.e.
-if a value was reported in \cite{nielsen+2013} and also in \cite{garcia+2014}, the latter was used).
-Stars used in \cite{vansaders+2016} are highlighted.
-The four triangles represent stars included in the original \cite{nielsen+2015} work.
-The solid line indicates 1:1 line, while the dash-dotted lines represent 2:1 and 1:2 lines.
-The shaded region around the 1:1 line is the $1\sigma$ credible interval of the fit to the data, the result of which is shown as the title of the figure.
-Stars that were not included in the fitting process are transparent.}
-	\label{fig:protlit}
-\end{figure}
-
 \section{Verifying consequences for gyrochronology}
@@
 
-% The best way to enter references is to use BibTeX:
-%\bibliographystyle{naturemag}
-%\bibliography{library.bib} %
+ The best way to enter references is to use BibTeX:
+\bibliographystyle{naturemag}
+\bibliography{library.bib} %
 

### 2020-09-29 paper/natastron/methods.tex
Chpping away

--- 2020-09-25 paper/natastron/paper.tex
@@
-\documentclass[12pt]{article}
-\setlength{\textwidth}{167mm}
-\setlength{\headsep}{0mm}
-\setlength{\headheight}{0mm}
-\setlength{\textheight}{230mm}
-\setlength{\oddsidemargin}{1.6mm}
-\setlength{\evensidemargin}{1.6mm}
-\setlength{\topmargin}{4.6mm}
-
-\usepackage{chngcntr}
-\usepackage{xspace}
-\usepackage{graphicx}
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage[ ]{hyperref}
-\graphicspath{{Images/}}
-\usepackage[symbol]{footmisc}
-
-% Astronomical abbreviations (thanks to Dan Huber)
-\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
-\newcommand{\dnu}{\mbox{$\Delta \nu$}\xspace}
-\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
-\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
-\newcommand{\logg}{\mbox{$\log(g)$}\xspace}
-\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
-\newcommand{\msun}{\mbox{$\mathrm{M}_{\odot}$}\xspace}
-\newcommand{\lsun}{\mbox{$\mathrm{L}_{\odot}$}\xspace}
-\newcommand{\mearth}{\mbox{$\mathrm{M}_{\oplus}$}\xspace}
-\newcommand{\rsun}{\mbox{$\mathrm{R}_{\odot}$}\xspace}
-\newcommand{\kepler}{\emph{Kepler}\xspace}
-\newcommand{\tess}{\emph{TESS}\xspace}
-\newcommand{\ktwo}{K2\xspace}
-\newcommand{\gaia}{\emph{Gaia}\xspace}
-
-\begin{document}
-\noindent\textbf{\LARGE{New asteroseismic rotation rates of \emph{Kepler} dwarfs show strong agreement with weakened magnetic braking on the late-age main sequence}}\\
-
-\noindent Oliver J. Hall$^{1,2,3,}$\footnote[1]{Email: \texttt{oliver.hall@esa.int} | Twitter: \texttt{@asteronomer} | GitHub: \texttt{@ojhall94}}
-	Guy R. Davies$^{2,3}$, 
-	Jennifer van Saders$^{4,5,6}$,
-	Martin B. Nielsen$^{2,3}$
-	Mikkel N. Lund$^{3}$, 
-	William J. Chaplin$^{2,3}$, 
-	Rafael A. Garc\'ia$^{7, 8}$, 
-	Louis Amard$^{9}$,
-	Angela A. Breimann$^{9}$, 
-	Saniya Khan$^{2,3}$, 
-	Victor See$^{9}$, 
-	Jamie Tayar$^{4, 10}$
-	\\
-
-	% List of institutions
-	\noindent $^{1}$ European Space Agency (ESA), European Space Research and Technology Centre (ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, The Netherlands
-
-	\noindent 	$^{2}$ School of Physics and Astronomy, University of Birmingham, Edgbaston, Birmingham, B15 2TT, UK
-
-	\noindent 	$^{3}$ Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, 8000 Aarhus C, Denmark
-
-	\noindent 	$^{4}$ Institute for Astronomy, University of Hawai'i, Honolulu, HI 96822
-
-	\noindent 	$^{5}$ Observatories of the Carnegie Institution for Science, Pasadena, CA 91101
-
-	\noindent 	$^{6}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544
-
-	\noindent 	$^{7}$ IRFU, CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France
-
-	\noindent 	$^{8}$ AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, F-91191 Gif-sur-Yvette, France
-
-	\noindent 	$^{9}$ University of Exeter Department of Physics and Astronomy, Stocker Road, Devon, Exeter, EX4 4QL, UK
-
-	\noindent $^{10}$ Hubble Fellow
-
-\vspace{10mm}
-
-\textbf{Studies using asteroseismic ages and rotation rates from star spot rotation have shown that standard age-rotation relations break down roughly half-way through the main sequence lifetime, a phenomenon referred to as weakened magnetic braking.
-While rotation rates from spots can be difficult to determine for older, less active stars, rotational splitting of asteroseismic oscillation frequencies can provide rotation rates for both active and quiescent stars, and so can confirm whether this effect really takes place in older stars.\\
-We obtained asteroseismic rotation rates of 91 main sequence stars showing high signal-to-noise modes of oscillation.
-Using these new rotation rates, along with effective temperatures, metallicities and seismic masses and ages, we built a hierarchical Bayesian mixture model to determine whether the ensemble more closely agreed with a standard rotational evolution scenario \cite{vansaders+pinsonneault2013}, or one where weakened magnetic braking takes place \cite{vansaders+2016}.
-The weakened magnetic braking scenario was found to be $98.4\%$ more likely for our stellar ensemble, adding to the growing body of evidence for this stage of stellar rotational evolution.
-This work represents the largest catalogue of seismic rotation on the main sequence to date, opening up possibilities for more detailed ensemble analysis of rotational evolution with \textit{Kepler}.}
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
- %500 words
-Gyrochronology is the study of the relationship between a star's rotation period and its age.
-As a star grows older along the main sequence, magnetic winds will cause it to lose angular momentum, slowing it down.
-Because the loss rate is related to temperature, the rotation period of a young star will rapidly settle on to a plane in age-colour-rotation space \cite{barnes2007}.
-As a result, knowing the rotation and colour of a star provides an avenue to measure it's age, which can otherwise be difficult to come by, enabling more in-depth studies of stellar populations and individual stars \cite{leiner+2019,claytor+2019}.
-
-Gyrochronology was previously calibrated on stellar clusters, which have well constrained ages, but only up to roughly $2.5\, \rm{Gyr}$ so far \cite{meibom+2015}.
-With the launch of the \textit{Kepler} mission \cite{borucki+2010}, ages of main sequence field stars (i.e.
-not in clusters) became more widely available through asteroseismology, the study of stellar variability \cite{silvaaguirre+2015}.
-When looking at these stars ,disagreements were found with gyrochronology beyond the middle of their main sequence lifetime, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}.
-It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops, causing stars to keep fast rotation rates at old ages, which we would not expected from existing gyrochronology relations.
-
-The mechanism by which weakened magnetic braking occurs is  still subject to debate, and may be connected to changes in the magnetic field morphology \cite{reville+2015,garraffo+2016, metcalfe+2019, see+2019}.
-It may also be explained from an observational point of view.
-A large scale survey of stellar rotation rates measured using star spots pointed out a lack of slowly rotating stars older then Sun \cite{mcquillan+2014}.
-As activity reduces with age, older stars with fewer star spots are less likely to have their rotation measured \cite{matt+2015}.
-The point at which the detection probability drops appears to lie at a similar level of activity to that at which the proposed weakened magnetic braking takes place, pitting these two possibilities against one another \cite{vansaders+2019}.
-
-Determining whether weakened magnetic braking is a true phenomenon or a bias in star spot observations requires new data, which can be provided by asteroseismology.
-A star's rotation causes modes of oscillation to split into multiplets, making it possible to measure the rate of rotation by measuring the splitting between oscillation frequencies \cite{ledoux1951}.
-Asteroseismic rotation is more difficult to obtain than rotation from star spots, but does not require  spots to be visible, meaning that we can measure rotation for quiescent stars that would not have been present in existing catalogues of star-spot rotation.
-Previous studies have shown that asteroseismic rotation rates probe the near-surface of the star, making them comparable to spot rotation rates, and the perfect avenue to explore whether weakened magnetic braking truly takes place \cite{lund+2014, benomar+2015}.
-Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of colours and ages, and evaluate this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one where weakened magnetic braking takes place.\\
-
-\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) oscillations for each star, of which the latter have significantly lower signal-to noise.
-Radial oscillations ($\ell = 0$), which are also visible, do not split.
-In this work, we studied a sample of 95 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}.
-A table of parameters taken from these studies, as well as details on how these were obtained, can be found in \textbf{\textit{Methods}}.
-
-We separated our sample into three categories \cite{garcia+2014}: 64 main sequence stars (MS, $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$); 4 potential sub-giant stars (SG, $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$, which may have begun to evolve off the main sequence, complicating their rotational history\footnote{It should be noted that none of these stars have identified mixed dipole modes, which indicate an evolved structure (see \cite{bedding+2010}).}; and 24 `hot' stars (H, $T_{\rm eff} > 6250\, \rm K$), which lie above the Kraft break, the point at which convective envelopes are tenuous, and angular momentum loss through magnetic winds becomes inefficient \cite{kraft1967}.
-Our conclusions are largely insensitive to these categorical assignments, and they are intended solely to help explore results category-by-category.
-The sample, which can be seen in Figure \ref{fig:sample}, spans surface gravities of $3.8\, \rm{dex} < \rm{log(g)} < 4.6\, \rm{dex}$, temperatures of $5000\, \textrm{K} < T_{\rm eff} <  6700\, \rm{K}$, and ages from $1$ to $\sim 13\, \rm{Gyr}$.\\
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.6\textwidth]{data.pdf}
-	\caption{Our sample of 95 stars from the Kages and LEGACY catalogues coloured by asteroseismic age  \cite{silvaaguirre+2015, silvaaguirre+2017}.
-The dashed lines indicate our classification boundaries: main sequence (circles, $\teff < 6250\, K$, $\logg < 4\, \rm{dex}$), potential sub-giants (squares, $\teff < 6250\, K$, $\logg > 4\, \rm{dex}$), and `hot' stars (triangles, $\teff > 6250\, K$).
-The Sun is shown with the `$\odot$' symbol, and has an age of $4.6\, \rm{Gyr}$ \cite{bonanno+frohlich2015}.
-The solid lines are evolutionary tracks generated using MESA \cite{paxton+2017}, for a metallicity of $Z = 0.01493$ and helium content of $Y = 0.26588$.
-Left to right, they represent masses of $1.5$, $1.25$, $1$ and $0.75\, M_\odot$.
-Vertical errorbars are too small to be visible.}
-	\label{fig:sample}
-\end{figure}
-
-\textbf{Results of asteroseismic fitting:} The `Kages' and LEGACY catalogues that form our stellar sample both performed detailed asteroseismic frequency fitting, but did not report asteroseismic rotation.
-Here, we repeated the mode frequency fitting with an improved Bayesian model that accounted for rotation in more detail (see \textbf{\textit{Methods}}).
-We fit our model to \kepler power-spectra of 95 stars, which was successful in 94 cases.
-We compared our results with both published and unpublished asteroseismic rotation rates, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with previous work.
-To some degree this was expected, as  for stars viewed near pole-on the power of the split modes of oscillation are extremely small.
-We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we judge our asteroseismic rotation measurements to be robust (for a full justification, see \textit{\textbf{Methods}}).\\
-
-\textbf{Seismic versus surface rotation rates:}\\
-
-\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two models of rotational evolution: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model').
-The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$ (for details, see \textbf{\textit{Methods}}).
-
-We evaluated our ensemble against both population models simultaneously using a Bayesian mixture model, which treated the data as being drawn from a mixture made from Kernel Density Estimates of both populations, modulated by a mixing parameter $P_{\rm s}$.
-In the limit that $P_{\rm s} \rightarrow 1$, the data are mostly likely drawn from the standard model.
-In the limit $P_{\rm s} \rightarrow 0$, the WMB model is more likely.
-This mixture model was evaluated in a five-dimensional parameter space, accounting for the population distributions in effective temperature ($T_{\rm eff}$), metallicity (\feh), asteroseismic mass ($M$) and age ($t$) and our new rotation periods ($P$).
-
-We fit our mixture model to the 73 stars in our sample with the best convergence metrics on the asteroseismic mode frequency fitting (see \textbf{\textit{Table 1}}).
-This sample included 22 `hot` stars, 4 potential sub-giants, and 47 main sequence stars.
-We calculated a joint posterior for this sample by multiplying the posterior probabilities obtained for $P_{\rm s}$ for each stars.
-This joint probability can be seen in Figure \ref{fig:gyroresults} in the left-hand plot, and the cumulative probability can be seen in the right-hand plot.
-In both of these plots, their left-hand sides hold 98.4\% of the probability, indicating that the weakened magnetic braking model is preferred.
-When only considering the main sequence stars, which are expected to be driving this distinction, this rises to 99.2\%.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{modelresults.pdf}
-	\caption{Posterior estimates of the mixture model parameter $P_{\rm s}$, broken down by stellar classification.
-A value of $P_{\rm s}$ close to zero indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 1 indicates that the data are more consistent with a standard rotational evolution scenario.
-\textit{Left:} the product of histograms of the posterior estimates for 73 stars, or subsets thereof for different stellar classifications.
-\textit{Right:} the cumulative posterior probability for 73 stars, or subsets thereof for different stellar types.}
-	\label{fig:gyroresults}
-\end{figure}
-
-\textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we made sure to test the same results were obtained using different subsets of the ensemble.
-Figure 3 shows ....
-[metallicity, full sample, biases, asteroseismology, van saders].\\
-
-We leave the reader with the following conclusions:
-\begin{enumerate}
-	\item We found that our ensemble was $98.4\%$ more likely to be drawn from the WMB model than the standard model, for stars evolved under a standard braking law \cite{vansaders+pinsonneault2013}.
-In other words, our asteroseismic observations strongly favour a model of weakened magnetic braking \cite{vansaders+2016}, at a critical Rossby number of $Ro_{\rm{crit}} = 1.97$.
-This work expands upon previous analysis (\cite{vansaders+2019}) by including quiescent stars older than the Sun.
-This conclusion was found to be robust against choice of ensemble members and potentially underestimated asteroseismic systematic uncertainties.
-A comparison to other braking laws \cite{matt+2015} using our asteroseismic ensemble will take place in future work.
-
-	\item We compared our new asteroseismic rotation rates with surface rotation measures from spot modulation.
-Our findings replicate those in similar studies (\cite{nielsen+2015,benomar+2015}), in the sense that we find no statistically significant difference between seismic and spot modulation measures of stellar rotation in our ensemble.
-
-	\item We present new techniques for asteroseismic `peak-bagging' frequency analyses, specifically: expressing well known empirical asteroseismic relations in a hierarchical modeling structure to account for small-scale effects not included in our model (such as acoustic glitches), and replacing uninformative empirical relations with Gaussian Process priors.
-
-	\item The new asteroseismic rotation catalogue presented in this work will act as an entry point for more detailed studies, including comparisons between different braking laws and individually modeled values of stellar rotation at different critical Rossby numbers.
-\end{enumerate}
-
-Finally, in the near future our asteroseismic rotation catalogue will be further complemented; with high-precision surface rotation measurements and atmospheric parameters from spectroscopic surveys such as LAMOST \cite{deng+2012}, 4MOST \cite{dejong+2014} and WEAVE \cite{dalton+2014}; and new asteroseismic measurements of age from the \ktwo and \tess missions.
-With these surveys, large scale ensemble asteroseismology will continue to increase the possibilities for understanding gyrochronology.\\
-
-All analysis performed as part of this work is stored in an online public repository\footnote{\url{https://github.com/ojhall94/malatium}}.\\
-
-\textbf{Software}: \texttt{astropy} \cite{astropycollaboration+2013, astropycollaboration+2018}, \texttt{astroquery} \cite{ginsburg+2019}, \texttt{Lightkurve} \cite{lightkurvecollaboration+2018}, \texttt{corner} \cite{foreman-mackey2016}, \texttt{emcee} \cite{foreman-mackey+2013}, \href{https://docs.daft-pgm.org/}{\texttt{daft}}, \texttt{Stan} \cite{carpenter+2017}, \texttt{PyStan} \cite{vanhoey+2013}, \texttt{iPython} \cite{perez+granger2007}, \texttt{Jupyter Notebooks} \cite{kluyver+2016}, \texttt{numpy}  \cite{vanderwalt+2011}, \texttt{pandas} and \texttt{scipy} \cite{mckinney2010}, \texttt{matplotlib} \cite{hunter2007}, \texttt{seaborn} \cite{waskom+2018}, \texttt{statsmodels} \cite{seabold+perktold2010}, \texttt{PyMC3} \cite{salvatier+2016}, \texttt{theano} \cite{thetheanodevelopmentteam+2016}.\\
-
-\textbf{Acknowledgments}:The authors would like to thank Sean Matt, Ellis Avallone, Alex Dixon, Warrick Ball and Brett Morris for helpful discussions. 
-OJH, GRD and WJC acknowledge the support of the UK Science and Technology Facilities Council (STFC). 
-JvS acknowledges support from the TESS Guest Investigator Program (80NSSC18K18584).
-MBN acknowledges support from the UK Space Agency
-This work has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (CartographY GA. 804752)
-Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement no.: DNRF106). 
-LA, AB and VS acknowledge funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation program (grant agreement No.
-682393 AWESoMeStars).
-AB also acknowledges the support of the College of Engineering, Mathematics and Physical Sciences at the University of Exeter.
-RAG acknowledges the support from the PLATO and GOLF CNES grants.
-JT acknowledges that support for this work was provided by NASA through the NASA Hubble Fellowship grant $\#51424$ awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
-The computations described in this paper were performed using the University of Birmingham's BlueBEAR HPC service.
-This paper includes data collected by the Kepler mission and obtained from the MAST data archive at the Space Telescope Science Institute (STScI).
-Funding for the Kepler mission is provided by the NASA Science Mission Directorate.
-STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5–26555.\\
-
-% The best way to enter references is to use BibTeX:
-\bibliographystyle{naturemag}
-\bibliography{library.bib} %
-
-\textbf{Author Contributions:} O.J.H.
-led the project, with help from G.R.D., J.V.S., M.B.N and W.J.C..
-J.V.S.
-also led the development of the stellar population models.
-M.N.L., R.A.G.
-and S.K.
-both provided data or stellar models and along with J.T.
-assessed the validity of our asteroseismic results.
-L.A., A.B.
-and V.S.
-provided the assessment of the theoretical implications of the gyrochronology results.
-All authors have contributed to the interpretation of the data and the results, and all discussed and provided comments for all drafts of the paper.
-
-\textbf{Competing Interests:} The authors declare that they have no competing financial interests.
-
-\textbf{Correspondence:} Correspondence and requests for materials should be addressed to O.J.H.. (email: oliver.hall@esa.int).
-
-\clearpage
-
-\section*{Supplementary materials}
+\section*{Methods}
 \setcounter{tocdepth}{2}
@@
 \end{figure*}
-
-\subsection{Asteroseismic Model}\label{s:seismo}
-In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background ($B(\nu)$), the oscillations ($O(\nu)$), and the white noise ($W$) in the style of e.g.
-\cite{davies+2015}.
-Our data, observed with \kepler, are also subject to the apodization (attenuation) of signals in the frequency-domain, where we fit our model \cite{chaplin+2011}.
-The apodization in power is given by
-
-\begin{equation}\label{eq:apodization}
-	\eta^2(\nu) = \rm{sinc}^2\left(\frac{\pi}{2}\frac{\nu}{\nu_{\rm nyq}}\right)\, ,
-\end{equation}
-where $\nu_{\rm nyq}$ is the Nyquist frequency for the \kepler short cadence, which was treated as a free parameter in our model to account for gaps in the data.
-Apodization only affects signals with characteristic timescales, meaning that it does not affect the white noise level, only the oscillations and convective background components.
-Given the above, our comprehensive model for the power spectrum is
-
-\begin{equation}\label{eq:model}
-	M(\nu) = W + \eta^2(\nu)[O(\nu) + B(\nu)]\, .
-\end{equation}
-
-\subsubsection{Convective Background}
-To model the convective background we used three Harvey components \cite{harvey1985}, which express the background in power as Lorentzian-like functions centered on zero frequency.
-The Harvey components take the form
-
-\begin{equation}
-	H(\nu, a, b, x) = \frac{4a^2/b}{1 + (2\pi b\nu)^x}\, ,
-\end{equation}
-
-\noindent where $a$ and $b$ are the free parameters in our model, and $x$ is fixed. The three Harvey components together form our background function as
-
-\begin{equation}\label{eq:background}
-	B(\nu) = H(\nu, a, b, x=4) + H(\nu, c, d, x=4) + H(\nu, j, k, x=2)\, ,
-\end{equation}
-
-\noindent where we have labeled parameters for the separate components.
-The $x = 2$ term here contributes to the background at high frequencies, whereas the $x=4$ terms contribute the background at low frequencies.
-
-\subsubsection{Modes of Oscillation}
-Modes of oscillation appear in the power spectrum as Lorentzian peaks \cite{chaplin+basu2017}.
-Due to stellar rotation, each mode with an angular degree of $\ell > 0$ is split into its $(2\ell +1)$ Lorentzian components, labeled by $m$, the azimuthal order.
-For all $\ell=(0,1,2)$ modes identified in \cite{davies+2016,lund+2017} we add a (set of) Lorentzian(s) to our model, building a composite model representing all visible modes.
-The construction of our oscillation model takes the form
-
-\begin{equation}
-	O(\nu) = \sum_n \sum_\ell \sum_{m=-\ell}^\ell \frac{H_{n,\ell,m}}{1 + \frac{4}{\Gamma^2_{n,\ell}}(\nu - \nu_{n,\ell,m})^2}\, ,
-\end{equation}
-
-\noindent where $n$ is the radial order of a mode (i.e.
-the overtone number of the oscillation), $H_{n,\ell,m}$ is the height of the mode, $\Gamma_{n,\ell}$ is the linewidth of the mode (approximated to be equal for all split components at a single $n$ and $\ell$) and $\nu_{n, \ell, m}$ is the frequency of the mode.
-The range of $n$ differs per star depending on how many radial orders were reported in LEGACY or Kages, and the range of $\ell$ depends on how many angular degrees were reported for the corresponding radial order.
-
-\subsubsection{Mode Frequencies and Rotational Splitting}\label{ssec:frequencies}
-The mode frequencies of main sequence stars are described by the asymptotic expression \cite{tassoul1980, vrard+2016}.
-The asymptotic expression defines the locations of the modes as regularly spaced, with structured deviation around \numax, the frequency of maximum oscillation amplitude.
-The expression takes the form
-
-\begin{equation}\label{eq:asymptotic}
-	\nu_{n,\ell,m} = \dnu\left(n + \epsilon + \delta\nu_{0,\ell} + \frac{\alpha}{2}(n - \frac{\numax}{\dnu} + \epsilon)^2\right) + m\nu_{s}\, ,
-\end{equation}
-
-\noindent where \dnu is the large frequency separation between two consecutive radial orders, $\epsilon$ is a a phase offset, $\delta\nu_{0,\ell}$ is the small frequency separation between two oscillation modes of different $\ell$ at the same radial order, $\alpha$ describes the curvature of the spacing around \numax, and $\nu_s$ is the rotational splitting.
-Note that here we have expressed the small separation $\delta\nu_{0,\ell}$ as a fraction of $\dnu$.
-In order to improve the computational efficiency of this analysis, we fixed \dnu to the values reported in LEGACY and Kages.
-
-Instead of calculating mode frequencies directly from Equation \ref{eq:asymptotic} for the model, we treated the individual mode frequencies as parameters as well, drawn from Equation \ref{eq:asymptotic}.
-This is called a `latent parameter' implementation \cite{hogg2012, hall+2019}, as it forms a step between the parameters we want to draw inference on (also called hyperparameters) and our data.
-The parameters $\nu_{n,\ell,m}$ were allowed to vary within an uncertainty $\sigma_{\ell}$, which has a single value for each angular degree and also varied as a free parameter.
-This allowed us to account for small shifts in frequency due to sudden changes in the stellar structure \cite[called acoustic glitches]{mazumdar+2014}.
-The mode frequency latent parameters were drawn from a normal distribution using Equation \ref{eq:asymptotic} as its mean function, as
-
-\begin{equation}
-	\nu_{n, \ell, m} \sim \mathcal{N}(\nu_{n, \ell, m}, \sigma_{\ell})\, ,
-\end{equation}
-
-\noindent where the expression $\nu_{n, \ell, m}$ on the right hand side represents the contents of Equation \ref{eq:asymptotic}, and $\mathcal{N}$ represents a normal distribution with a mean equal to $\nu_{n, \ell, m}$ and a standard deviation equal to $\sigma_{\ell}$.
-The symbol `$\sim$' indicates that the parameters on the left hand side of the equation are drawn from the probability distribution on the right hand side.
-This notation will be used throughout this paper.
-
-\subsubsection{Mode Linewidth}
-The linewidths of asteroseismic p modes vary roughly as a function of mode frequency, and do so slowly relative to \dnu.
-This can be expressed as an empirical relation \cite{davies+2014, appourchaux+2016, lund+2017}.
-However, this relation has six free parameters, none of which are directly relevant to this work.
-Instead of fitting this relation, we chose to employ a more flexible Gaussian Process \cite[GP]{rasmussen+williams2006} to act as a prior on the linewidths.
-This can be considered as us modelling the linewidths as correlated measurements.
-As our GP covariance kernel we used a Squared Exponential Kernel to capture the slight periodicity of linewidth with frequency, as
-
-\begin{equation}\label{eq:gpkernel}
-	K_{i,j} = \rho^2 \exp \left[ -\frac{(n_{\textrm{f}, i} - n_{\textrm{f}, j})^2}{2L^2} \right]\, ,
-\end{equation}
-
-\noindent where $n_{\rm f}$ is the fractional radial order of a given mode.
-For each star, the overtone numbers $n$ were rescaled to be between 0 (for the lowest $n$) and 1 (for the highest $n$)\footnote{Overtones of $\ell = 2$ modes were increased by $1$ to ensure this approximation applied to all modes.}.
-This approximation was used to describe the change in linewidth as a function of frequency without depending on the exact frequencies of the modes.
-$K_{i,j}$ represents an element of the covariance matrix $\underline{K}$, describing the covariance between two values of linewidth at different fractional radial orders.
-The GP kernel has two hyperparameters: $\rho$, which determines the spread of the kernel, and $L$, which determines the length scale in terms of $n_{\rm f}$.
-The length scale was significantly larger than the large frequency separation (\dnu) in all cases, and so we considered the use of fractional radial orders a valid approximation in this model.
-
-A linear function was used for the mean of the GP, as
-
-\begin{equation}\label{eq:gpmean}
-	\mu = m \times n_{\textrm{f}} + c\, ,
-\end{equation}
-where $m$ and $c$ are the slope and intercept of the line. The linewidth latent parameters were then drawn from the multivariate probability distribution
-
-\begin{equation}\label{eq:gammagp}
-	\Gamma \sim \mathcal{N}(\mu, \underline{K})\, ,
-\end{equation}
-
-\noindent where $\Gamma$ represents the linewidths of all the modes in the model. The parameters $m$, $c$ and $\rho$ were marginalised over, whereas $L$ was fixed to a pre-determined value.
-
-\subsubsection{Mode Heights and Angle of Inclination}
-The height in power of each mode, $H_{n, \ell, m}$, varies not only as a function of distance in frequency from \numax, but also due to observation conditions, such as inclination angle and passband.
-In our model, we treated $H_{n, \ell, m}$ as a deterministic parameter, as
-
-\begin{equation}\label{eq:height}
-	H_{n, \ell, m} =  \varepsilon_{\ell, m}(i) \frac{2 (A_{n, \ell})^2}{\pi \Gamma_{n, \ell}}\, ,
-\end{equation}
-
-\noindent where $\varepsilon_{\ell, m}(i)$ modulates the height as a function of inclination angle ($i$) (see below), and $A_{n, \ell}$ and $\Gamma_{n, \ell}$ are the mode amplitude and linewidth respectively for a given radial order and angular degree.
-Instead of modeling and modulating height directly, we instead sampled in amplitude and linewidth.
-This approach mitigates the correlations between height and linewidth in the sampling process \cite{toutain+appourchaux1994}.
-
-As done above for the mode frequencies and linewidths, the mode amplitudes $A_{n,\ell}$ were also treated as latent parameters drawn from a probability distribution governed by hyperparameters.
-We used a Gaussian function $G(\nu)$, centered on $\numax$, so that
-
-\begin{equation}\label{eq:amplitude}
-	G(\nu) = A \times \exp\left[-\frac{(\nu - \numax)^2}{2w^2}\right]\, ,
-\end{equation}
-
-\noindent where $A$ is the amplitude at \numax, and $w$ is the width of the Gaussian, both free parameters in our model. 
-The mode amplitude latent parameters were then drawn from the probability distribution
-
-\begin{equation}
-	A_{n, \ell} \sim \mathcal{N}(G(\nu_{n,\ell}) \times V_\ell, \sigma_{A})\, ,
-\end{equation}
-
-\noindent where $V_\ell$ is a free parameter for the mode visibility of different angular degrees, which should be consistent for all \kepler observations.
-The mode visibility for $V_0$ is fixed at 1, and $V_{1,2}$ are treated as free parameters.
-The parameter $\sigma_{A}$, the uncertainty on the distribution, is also a free parameter, and takes the same value for all amplitudes regardless of angular degree.\\
-
-The angle of inclination of a star with respect to Earth changes the net perturbation by a given mode when integrated across the stellar disc, changing the amplitudes of modes of different azimuthal orders.
-This is a geometric problem, and is expressed by $\varepsilon_{\ell, m}(i)$, which takes the form \cite{gizon+solanki2003}
-
-\begin{equation}\label{eq:legendre}
-	\varepsilon_{\ell, m}(i) = \frac{(\ell - |m|)!}{(\ell + |m|)!}\left[P_\ell^{|m|}(\cos(i))\right]^2\, ,
-\end{equation}
-
-\noindent where $P_\ell^{|m|}$ are associated Legendre functions. For the first three angular degrees, Equation \ref{eq:legendre} takes the form \cite{handberg+campante2011}
-
-\begin{equation}
-	\begin{split}
-		\varepsilon_{0,0}(i) &= 1\, ,\\
-		\varepsilon_{1,0}(i) &= \cos^2(i)\, ,    \\
-		\varepsilon_{1,\pm1}(i) &= \frac{1}{2}\sin^2(i)\, ,\\
-		\varepsilon_{2,0}(i) &= \frac{1}{4}(3\cos^2(i) - 1)^2\, ,\\
-		\varepsilon_{2,\pm1}(i) &= \frac{3}{8}\sin^2(2i)\, ,\\
-		\varepsilon_{2,\pm2}(i) &= \frac{3}{8}\sin^4(i)\, ,
-	\end{split}
-\end{equation}
-
-\noindent where the sum of available components for a single $\ell$ are normalized to one.
-
-\subsubsection{Likelihood Function}\label{sec:like}
-If data have Gaussian noise in the time domain, they will appear in the frequency domain with noise following a $\chi^2$ distribution with two degrees of freedom \cite[$\chi^2_2$ hereafter][]{woodard1984}.
-The noise properties of $\chi^2_2$ distributed data are multiplicative, and require a specific treatment when fitting a model.
-As our frequency bins can be approximated to be independent, we used the likelihood function \cite{anderson+1990},
-
-\begin{equation}
-	\ln p(\mathcal{P} | M) = \sum_{j=0}^{N-1} \left[\ln[M_j(\nu)] + \frac{\mathcal{P}_j}{M_j(\nu)}\right]\, , 
-\end{equation}
-
-\noindent where $\mathcal{P}$ is the power spectral density (and thus our data), and $M(\nu)$ represents our model.
-The subscript $j$ denotes an individual datum, for a total of $N$ data.
-We have omitted the dependence of the model $M(\nu)$ on its parameters, for clarity.
-This equation is functionally equivalent to the evaluation of a gamma distribution of the form $\gamma(\mathcal{P} | 1, \beta)$, where $\beta = 1/M(\nu)$, which is the implementation we used in the sampling process.
-
-\subsubsection{Fitting the convective background}\label{sec:background}
-Fitting the convective background, apodization and white noise component must be done for the full range of the power spectrum in order to be accurately constrained.
-However, fitting a single model to the full range of frequencies is computationally inefficient when we are interested in the modes of oscillation, as these occupy a relatively small range of frequencies.
-
-In order to speed up this process, the background was first fit independently to a subset of our data for each star.
-This subset was created by removing all frequencies within a range $0.1 \times \dnu$ below and above the minimum and maximum mode frequencies reported in LEGACY and Kages.
-For KIC 3427720 we also removed frequencies in the range $90\, \mu\rm{Hz} < \nu < 400\, \mu{\rm{Hz}}$, where there were large peaks not of asteroseismic origin, skewing the background fit.
-
-For each star the model function (see Eq. \ref{eq:model}) was fit, as
-
-\begin{equation}
-	M_{B}(\nu) = W + \eta^2(\nu)B(\nu)\, ,
-\end{equation}
-
-\noindent where $B(\nu)$ is the background model described in Equation \ref{eq:background}.
-The parameter components of our background fit are then $\phi_B = \{\log(a), \log(b), \log(c), \log(d), \log(j), \log(k), W, \nu_{\rm nyq}\}$, where the parameters of the Harvey components were sampled in log space.
-The model was fit to the background data using \texttt{PyStan} \cite{vanhoey+2013}, run for 10,000 iterations on each star\footnote{These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work.}.
-
-\subsubsection{Obtaining First Guesses and Prior Values}
-In order to utilise some of the prior measurements of our targets without using them as hard constraints on our parameters, some of our model equations were fit to LEGACY and Kages data to obtain first guesses and mean values on hyperparameter priors.
-
-For first guesses for parameters in the asymptotic expression, we fit Equation \ref{eq:asymptotic}, \textit{not} including the rotational component $m\nu_s$, to the $\ell = (0, 1, 2)$ mode frequencies reported in LEGACY and Kages for each star, using their reported uncertainties.
-This yielded estimates of $\hat{\epsilon}$, $\widehat{\delta\nu}_{01}$, $\widehat{\delta\nu}_{02}$ and $\hat{\alpha}$, where the hat symbol `\, $\widehat{}$\, ' indicates a prior value (e.g.
-$\hat{\nu}_{\rm max}$ is taken from LEGACY or Kages).
-While not precise, as we did not mitigate any perturbations due to acoustic glitches (sudden changes in interior sound speed, which the latent parameter treatment takes care of in the full model), these rough results act as functional first guesses and prior mean values.
-The relation was fit to each star using PyMC3 \cite{salvatier+2016} using 5000 iterations on 4 chains.
-
-To obtain first guesses for the parameters used to set the GP prior on linewidth, we fit a GP constructed as in Equation \ref{eq:gammagp} to the linewidths of the $\ell = 0$ modes reported in LEGACY.
-Linewidths were not reported for the other angular degrees in LEGACY, but the estimates may be generalised to other $\ell$, as linewidth is a strong function of frequency.
-The relation was fit to each star using PyMC3 using 2500 iterations on 4 chains.
-
-Fitting the LEGACY linewidths yielded rough estimates of $\hat{m}$, $\hat{c}$, $\hat{\rho}$ and $L$ for each star.
-As is noted in Equation \ref{eq:gammagp}, $L$ was fixed to this fit value when fitting our full model to our data.
-For stars in Kages, for which no linewidths were reported, we instead fixed these prior values to $\hat{m} = 1$, $\hat{c} = 0.5$, $\hat{\rho} = 0.1$, and the length scale to $L = 0.3$.
-These values were chosen to reflect those found for the LEGACY stars.
-
-Finally, we obtained prior values for the Gaussian function describing the distribution of mode amplitudes around \numax.
-The mode amplitude of the highest peak in the spectrum was used for the amplitude, which was typically at or near \numax.
-For the width of the Gaussian we used the empirical function \cite{lund+2017}
-
-\begin{equation}
-	\hat{w} = 0.25 \times \numax\, .
-\end{equation}
-
-\noindent For the mode visibilities, we used $\hat{V}_1 = 1.2$ and $\hat{V}_2 = 0.7$, which reflect the results for these parameters reported in the LEGACY catalogue.
-
-\subsubsection{Priors on our Hyperparameters}
-Given our first guesses and measured prior values, we can define the prior probabilities of the hyperparameters on which our model depends. For the mode frequency hyperparameters, these are
-
-\begin{equation}
-	\begin{split}
-		\numax &\sim \mathcal{N}(\hat{\nu}_{\rm max}, 10)\, ,\\
-		\epsilon &\sim \mathcal{N}(\hat{\epsilon}, 1)\, ,\\
-		\alpha &\sim \ln\mathcal{N}(\ln(\hat{\alpha}), 0.01)\, ,\\
-		\delta\nu_{01} &\sim \ln\mathcal{N}(\ln(\widehat{\delta\nu}_{01}), 0.1)\, ,\\
-		\delta\nu_{02} &\sim \ln\mathcal{N}(\ln(\widehat{\delta\nu}_{02}), 0.1)\, ,\\
-		\sigma_{0,1,2} &\sim \mathcal{C}_{1/2}(\beta = 2)\, ,
-	\end{split}
-\end{equation}
-
-\noindent where $\ln\mathcal{N}$ represents a log-Normal distribution and $\mathcal{C}_{1/2}$ represents a half-Cauchy distribution, and other symbols are as described above.
-All three hyperparameters $\sigma_{0,1,2}$ describing the uncertainty on the latent parameters of different angular degree were subject to the same prior.
-
-For the mode linewidths, our hyperparameter priors took the form
-
-\begin{equation}
-	\begin{split}
-		m &\sim \mathcal{N}(\hat{m}, 1)\, ,\\
-		c &\sim \mathcal{N}(\hat{c}, 1)\, ,\\
-		\rho &\sim \ln\mathcal{N}(\ln(\hat{\rho}), 0.1)\, ,\\
-	\end{split}
-\end{equation}
-
-\noindent where the conventions are the same as above. For our mode amplitudes, they took the form
-
-\begin{equation}
-	\begin{split}
-		w &\sim \ln\mathcal{N}(\ln(\hat{w}), 10)\, ,\\
-		A &\sim \ln\mathcal{N}(\ln(\hat{A}), 1)\, ,\\
-		V_1 &\sim \ln\mathcal{N}(\ln(\hat{V}_1), 0.1)\, ,\\
-		V_2 &\sim \ln\mathcal{N}(\ln(\hat{V}_2), 0.1)\, ,\\
-		\sigma_A &\sim \mathcal{C}_{1/2}(\beta = 1)\, .
-	\end{split}
-\end{equation}
-
-As the convective background had already been fit to our data excluding the region where the modes are present, the results from that fit could be used as extremely informative priors on our fit to the region containing the modes, where there is little information present to constrain the background.
-To do so, we modeled the background parameters $\phi_B$ in our full model as being drawn from a multivariate normal distribution as
-
-\begin{equation}
-	\phi_{B}\sim\mathcal{N}(\hat{\phi}_{B},\underline{\Sigma}_{\hat{\phi}_{B}})\, ,
-\end{equation}
-
-\noindent where $\hat{\phi}_B$ are the median values of our posterior distributions from our prior background fit, and $\underline{\Sigma}_{\hat{\phi}_{B}}$ is the full covariance matrix of all the posterior distributions from our prior background fit, taking into account the correlations between the different Harvey components.
-
-Finally, we defined the priors on the rotational parameters: the mode splitting ($\nu_s$), and the inclination angle ($i$).
-In order to give these an appropriate treatment, we made two reparameterizations.
-First, we sampled the projected rotational splitting, $\nu_{\rm{s}}\sin(i)$, which is more efficiently sampled due to the strong correlations between $i$ and $\nu_{\rm s}$ \cite{ballot+2006,ballot+2008a}.
-A prior was applied over this as
-
-\begin{equation}
-	\nu_s\sin(i) \sim \ln\mathcal{N}(\ln(0.75), 0.75)\, ,
-\end{equation}
-
-\noindent where conventions are as above.
-This subjective prior was chosen to reflect that most stars will have a solar-like rotation, with a long tail to allow for the fastest rotators.
-Second, we sampled in $\cos(i)$, and gave this a prior of
-
-\begin{equation}
-	\begin{split}
-		\cos(i) &\sim \mathcal{U}(0, 1)\, ,
-	\end{split}
-\end{equation}
-which is equivalent to stating that probability to observe an inclination angle $i$ is equal to $\sin(i)$.
-Here, the $\mathcal{U}(0,1)$ indicates a uniform prior between 0 and 1.
-Using a uniform prior on $\cos(i)$ allowed us to account for the geometric effect that stars with a large inclination angle with respect to us are more common \cite{chaplin+basu2017}.
-
-\subsubsection{Fitting procedure}
-Using our prior information and model described above, we fit Equation \ref{eq:model} to our data $\mathcal{P}$, using the likelihood function described in Section \ref{sec:like}.
-
-In order to speed up the fitting process, we only applied our model to the region of the power spectrum that contains visible modes of oscillation.
-We created this subset by removing all frequencies outside a range $0.25 \times \Delta\nu$ below and above the minimum and maximum mode frequencies reported in LEGACY and Kages.
-This region overlaps minimally with the data used to fit for our prior information of the convective background (see Section \ref{sec:background}), so that both model fits are independent.
-
-To improve computational efficiency, we reduced the number of oscillation modes being fit in five targets.
-For 16 Cyg A \& B, KIC 7970740 and KIC 8478994, we excluded any modes with a Bayes Factor ($\ln(K)$) of less than 6, as reported in LEGACY \cite{kass+raftery1995,davies+2016,lund+2017}.
-For KIC 8478994, which is reported without a value for $\ln(K)$ in Kages, we only included modes of an overtone number that contained a detection for all of $\ell = (0, 1, 2)$, retaining 5 sets of higher signal-to-noise overtones.
-We do not expect this reduced scope to bias our results, although they may reduce the precision on our measured rotation rates.
-
-We fit our model to our power spectrum data with \texttt{PyMC3}, using 2500 iterations each on 4 chains.
-An example of our model fit to an asteroseismic power spectrum of 16 Cyg A is shown in Figure \ref{fig:modelfit}.
 
@@
 The array of 100 bins for all stars were multiplied, resulting in an approximation of the joint posterior probability function for $P_{\rm s}$ given all stars in the ensemble.
+
+\section{Results}
+bla bla short shpiel about which values were included and which weren't
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.49\textwidth]{Images/surf-seis-comparison.pdf}
-	\caption{Comparisons between asteroseismic and photometric measures of stellar rotation, for 48 stars.
-Literature values were taken, in order of priority, from: \cite{garcia+2014} and \cite{nielsen+2013} (i.e.
-if a value was reported in \cite{nielsen+2013} and also in \cite{garcia+2014}, the latter was used).
-Stars used in \cite{vansaders+2016} are highlighted.
-The four triangles represent stars included in the original \cite{nielsen+2015} work.
-The solid line indicates 1:1 line, while the dash-dotted lines represent 2:1 and 1:2 lines.
-The shaded region around the 1:1 line is the $1\sigma$ credible interval of the fit to the data, the result of which is shown as the title of the figure.
-Stars that were not included in the fitting process are transparent.}
-	\label{fig:protlit}
-\end{figure}
+\subsection{Asteroseismic detection biases}
 
@@
 While a comparison to models of different Rossby numbers is outside the scope of this study, the LEGACY and Kages rotation sample may facilitate such studies in the future.
-
-% The best way to enter references is to use BibTeX:
-%\bibliographystyle{naturemag}
-%\bibliography{library.bib} %
-
-\end{document}

### 2020-09-29 paper/natastron/paper.tex
Chpping away

--- 2020-09-25 paper/natastron/paper.tex
@@
 
-\textbf{Studies using asteroseismic ages and rotation rates from star spot rotation have shown that standard age-rotation relations break down roughly half-way through the main sequence lifetime, a phenomenon referred to as weakened magnetic braking.
+\textbf{Studies using asteroseismic ages and rotation rates from star-spot rotation have indicated that standard age-rotation relations may break down roughly half-way through the main sequence lifetime, a phenomenon referred to as weakened magnetic braking.
 While rotation rates from spots can be difficult to determine for older, less active stars, rotational splitting of asteroseismic oscillation frequencies can provide rotation rates for both active and quiescent stars, and so can confirm whether this effect really takes place in older stars.\\
@@
 Because the loss rate is related to temperature, the rotation period of a young star will rapidly settle on to a plane in age-colour-rotation space \cite{barnes2007}.
-As a result, knowing the rotation and colour of a star provides an avenue to measure it's age, which can otherwise be difficult to come by, enabling more in-depth studies of stellar populations and individual stars \cite{leiner+2019,claytor+2019}.
+As a result, knowing the rotation and colour of a star provides an avenue to measure it's age, to a precision of $\sim 10\%$ for stars most similar to the Sun \cite{meibom+2015}.
+Age can otherwise be difficult to come by, and so gyrochronology enables more in-depth studies of stellar populations and individual stars \cite{leiner+2019,claytor+2019}.
 
@@
 not in clusters) became more widely available through asteroseismology, the study of stellar variability \cite{silvaaguirre+2015}.
-When looking at these stars ,disagreements were found with gyrochronology beyond the middle of their main sequence lifetime, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}.
-It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops, causing stars to keep fast rotation rates at old ages, which we would not expected from existing gyrochronology relations.
+When looking at these stars, disagreements were found between the observations and gyrochronology beyond the middle of stars' main sequence lifetimes, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}.
+It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops.
+This would cause stars to keep fast rotation rates at old ages, which we would not expected from existing gyrochronology relations.
 
-The mechanism by which weakened magnetic braking occurs is  still subject to debate, and may be connected to changes in the magnetic field morphology \cite{reville+2015,garraffo+2016, metcalfe+2019, see+2019}.
+The mechanism by which weakened magnetic braking occurs has since been the subject of ongoing debate, and may be connected to changes in the magnetic field morphology \cite{reville+2015,garraffo+2016, metcalfe+2019, see+2019}.
 It may also be explained from an observational point of view.
-A large scale survey of stellar rotation rates measured using star spots pointed out a lack of slowly rotating stars older then Sun \cite{mcquillan+2014}.
-As activity reduces with age, older stars with fewer star spots are less likely to have their rotation measured \cite{matt+2015}.
-The point at which the detection probability drops appears to lie at a similar level of activity to that at which the proposed weakened magnetic braking takes place, pitting these two possibilities against one another \cite{vansaders+2019}.
+A large scale survey of stellar rotation rates measured using star-spots pointed out a lack of slowly rotating stars older then Sun \cite{mcquillan+2014}.
+As activity reduces with age, older stars with fewer star-spots are less likely to have their rotation measured \cite{matt+2015}.
+The point at which the detection probability drops appears to lie at a similar level of activity as when the proposed weakened magnetic braking takes place, pitting these two possibilities against one another \cite{vansaders+2019}.
 
-Determining whether weakened magnetic braking is a true phenomenon or a bias in star spot observations requires new data, which can be provided by asteroseismology.
-A star's rotation causes modes of oscillation to split into multiplets, making it possible to measure the rate of rotation by measuring the splitting between oscillation frequencies \cite{ledoux1951}.
-Asteroseismic rotation is more difficult to obtain than rotation from star spots, but does not require  spots to be visible, meaning that we can measure rotation for quiescent stars that would not have been present in existing catalogues of star-spot rotation.
-Previous studies have shown that asteroseismic rotation rates probe the near-surface of the star, making them comparable to spot rotation rates, and the perfect avenue to explore whether weakened magnetic braking truly takes place \cite{lund+2014, benomar+2015}.
-Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of colours and ages, and evaluate this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one where weakened magnetic braking takes place.\\
+Determining whether weakened magnetic braking is a true phenomenon or a bias in star-spot observations requires new data, which can be provided by asteroseismology.
+A star's rotation causes modes of oscillation to split into multiplets, making it possible to obtain an independent rate of rotation by measuring the splitting between oscillation frequencies \cite{ledoux1951}.
+Asteroseismic rotation is more difficult to obtain than spot rotation, but does not require spots to be visible, meaning that we can measure rotation for older, quiescent stars that would not have been present in existing rotation catalogues.
+This makes asteroseismic rotation rates the perfect avenue to explore whether weakened magnetic braking truly takes place on the main sequence.
+Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of  ages, and evaluated this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one where weakened magnetic braking takes place.\\
 
@@
 In this work, we studied a sample of 95 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}.
-A table of parameters taken from these studies, as well as details on how these were obtained, can be found in \textbf{\textit{Methods}}.
+Further details on how these data can be found in \textbf{\textit{Methods}}.
 
-We separated our sample into three categories \cite{garcia+2014}: 64 main sequence stars (MS, $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$); 4 potential sub-giant stars (SG, $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$, which may have begun to evolve off the main sequence, complicating their rotational history\footnote{It should be noted that none of these stars have identified mixed dipole modes, which indicate an evolved structure (see \cite{bedding+2010}).}; and 24 `hot' stars (H, $T_{\rm eff} > 6250\, \rm K$), which lie above the Kraft break, the point at which convective envelopes are tenuous, and angular momentum loss through magnetic winds becomes inefficient \cite{kraft1967}.
+We separated our sample into three categories \cite{garcia+2014}: 64 main sequence stars (MS, $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$); 4 potential sub-giant stars (SG, $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$), which may have begun to evolve off the main sequence, complicating their rotational history\footnote{It should be noted that none of these stars have identified mixed dipole modes, which indicate an evolved structure (see \cite{bedding+2010}).}; and 24 `hot' stars (H, $T_{\rm eff} > 6250\, \rm K$), which lie above the Kraft break, the point at which convective envelopes are tenuous, and angular momentum loss through magnetic winds becomes inefficient \cite{kraft1967}.
+Our conclusions are largely insensitive to these categorical assignments, and they are intended solely to help explore results category-by-category.
 The sample, which can be seen in Figure \ref{fig:sample}, spans surface gravities of $3.8\, \rm{dex} < \rm{log(g)} < 4.6\, \rm{dex}$, temperatures of $5000\, \textrm{K} < T_{\rm eff} <  6700\, \rm{K}$, and ages from $1$ to $\sim 13\, \rm{Gyr}$.\\
@@
 
-\textbf{Results of asteroseismic fitting:} The `Kages' and LEGACY catalogues that form our stellar sample both performed detailed asteroseismic frequency fitting, but did not report asteroseismic rotation.
-Here, we repeated the mode frequency fitting with an improved Bayesian model that accounted for rotation in more detail (see \textbf{\textit{Methods}}).
-We fit our model to \kepler power-spectra of 95 stars, which was successful in 94 cases.
-We compared our results with both published and unpublished asteroseismic rotation rates, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with previous work.
-To some degree this was expected, as  for stars viewed near pole-on the power of the split modes of oscillation are extremely small.
-We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we judge our asteroseismic rotation measurements to be robust (for a full justification, see \textit{\textbf{Methods}}).\\
+\textbf{Results of asteroseismic fitting:} The stars in `Kages' and LEGACY form our stellar sample have been subject to detailed asteroseismic frequency fitting in the catalogue papers, but did not report asteroseismic rotation.
+Here, we repeated the mode frequency fitting with a Bayesian model that accounted for rotation in more detail, and improved the treatment of existing asteroseismic relations in frequency fitting techniques (see \textbf{\textit{Methods}} and \textit{\textbf{Supplementary Information}}).
+We fit our new model to \kepler power-spectra of 95 stars, which was successful in 94 cases.
+We compared our results with both published and unpublished asteroseismic rotation rates, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with multiple other studies.
+To some degree this was expected, as  for stars viewed near pole-on the split modes of oscillation have extremely low power, making them hard to detect reliably.
+We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we considered our asteroseismic rotation measurements to be robust (for a full justification, see \textit{\textbf{Methods}}).\\
 
-\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two models of rotational evolution: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model').
-The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$ (for details, see \textbf{\textit{Methods}}).
+\textbf{Seismic versus surface rotation rates:} Different methods of rotation measurement probe different depths of stars.
+Asteroseismology of main sequence stars probes internal rotation in the near surface layers, where the observed modes of oscillation are most sensitive \cite{lund+2014}.
+Measurements of star-spot modulation instead probe the rotation rates of star-spots on the surface.
+Previous studies have shown that seismic rotation rates show no statistically significant deviation from spot rotation rates \cite{nielsen+2015, benomar+2015}.
+We confirm that this holds true for our larger sample, in order to ensure that our seismic rotation periods can be reliably used to draw conclusions on the evolution of surface rotation.
 
-We evaluated our ensemble against both population models simultaneously using a Bayesian mixture model, which treated the data as being drawn from a mixture made from Kernel Density Estimates of both populations, modulated by a mixing parameter $P_{\rm s}$.
+Figure \ref{fig:protlit} shows a comparison between 48 stars from our sample for which spot  rotation rates had previously been measured.
+Rotation rates from spot modulation are subject to measuring multiples of the true rotation rate, and also sometimes over-correct for this effect.
+This is not the case for asteroseismic rotation, and so some stars may appear at the 2:1 and 1:2 lines in the Figure.
+We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid outliers (transparent in the Figure).
+Our fit found a value of $m = 0.96 \pm 0.03$, showing a close agreement ($<2\sigma$) between asteroseismic and surface rotation rates on a population level.
+%Of the stars used in this comparison, 21 had a median value of $P_{\rm s}$ in the gyrochronology analysis. We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.  
+This overall agreement between spot and seismic rotation rates is in line with previous studies of Sun-like stars \cite{gizon+2013, chaplin+2013, nielsen+2015, benomar+2015}, and so we can conclude that our asteroseismic ensemble can be reliably used to draw inferences about gyrochronology.\\
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.6\textwidth]{Images/surf-seis-comparison.pdf}
+	\caption{Comparisons between asteroseismic and photometric measures of stellar rotation, for 48 stars.
+Literature values were taken, in order of priority, from: \cite{garcia+2014} and \cite{nielsen+2013} (i.e.
+if a value was reported in \cite{nielsen+2013} and also in \cite{garcia+2014}, the latter was used).
+Stars used in \cite{vansaders+2016} are highlighted.
+The four triangles represent stars included in the original \cite{nielsen+2015} work.
+The solid line indicates 1:1 line, while the dash-dotted lines represent 2:1 and 1:2 lines.
+The shaded region around the 1:1 line is the $1\sigma$ credible interval of the fit to the data, the result of which is shown as the title of the figure.
+Stars that were not included in the fitting process are transparent.}
+	\label{fig:protlit}
+\end{figure}
+
+\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two population models of rotational evolution: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model').
+The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$.
+Instead of comparing our rotation rates directly to models of individual stars, we instead compared them to synthetic populations based on what the \textit{Kepler} field would look like under these two different braking laws \cite{girardi+2012,vansaders+2019}.
+For the full details on how these models were constructed, see \textbf{\textit{Methods}}.
+
+In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting\footnote{Excluding those with a number of effective samples $n_{\rm eff} < 25\%$ and a Gelman-Rubin metric of $\hat{R}>1.1$ \cite{gelman+rubin1992,salvatier+2016}} (see \textbf{\textit{Extended Data Table 1}}).
+The remaining sample of 73 stars contained 4 potential sub-giants, 22 `hot' stars and 47 main sequence stars.
+Figure \ref{fig:fullsample} shows these stars plotted over the top of both the standard and WMB population models in rotation-temperature space, alongside the stars not used in the gyrochronology analysis (shown without uncertainties).
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{fullsample.png}
+	\caption{Stars for which rotation was measured in this work, plotted over stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution.
+The 21 Stars that were excluded from the gyrochronology analysis are marked with crosses and without uncertainties (see text).
+Circles, squares and triangles denote main sequence, sub-giant, and `hot' stars respectively.
+Stars with a metallicity of $\bigl\lvert \feh \bigl\rvert > 0.4$ are coloured differently (darker), to indicate that they fall outside the functional range of the \cite{vansaders+2019} stellar models.
+Note that only period-temperature space is shown here, but when evaluating between the two model prescriptions we also considered mass, age and metallicity.}
+	\label{fig:fullsample}
+\end{figure*}
+
+We evaluated our ensemble against both population models simultaneously using a Bayesian mixture model, which treated the data as being drawn from a mixture made from Kernel Density Estimates (KDEs) of both populations, modulated by a mixing parameter $P_{\rm s}$.
 In the limit that $P_{\rm s} \rightarrow 1$, the data are mostly likely drawn from the standard model.
 In the limit $P_{\rm s} \rightarrow 0$, the WMB model is more likely.
-We then this mixture model to our ensemble, accounting for the population distributions in effective temperature ($T_{\rm eff}$), metallicity (\feh), asteroseismic mass ($M$) and age ($t$) and our new rotation periods ($P$).
+This mixture model was evaluated in a five-dimensional parameter space, accounting for the population distributions in effective temperature ($T_{\rm eff}$), metallicity (\feh), asteroseismic mass ($M$) and age ($t$) and our new rotation periods ($P$).
 
-\section{Discussion}
+We fit our mixture model to each star individually, which yielded a posterior probability density for the value of $P_{\rm s}$ for that star.
+In order to assess the posterior probability for the full sample, we multiplied the individual posterior probabilities for $P_{\rm s}$.
+This was done for the full ensemble of 73 stars, as well as for the three different stellar types.
+These joint probabilities can be seen in Figure \ref{fig:gyroresults} in the left-hand plot.
+The cumulative probability can be seen in the right-hand plot.
+In both of these plots, the left-hand side holds 98.4\% of the probability\footnote{When performing this analysis on all 91 stars for which seismic rotation was measured, this value is 96.6\%.}, indicating that the weakened magnetic braking model is preferred.
+When only considering the 47 main sequence stars, for which we expect the effects of weakened magnetic braking to be strongest, this rises to 99.2\%.
+\\
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{modelresults.pdf}
+	\caption{Posterior estimates of the mixture model parameter $P_{\rm s}$, broken down by stellar classification.
+A value of $P_{\rm s}$ close to zero indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 1 indicates that the data are more consistent with a standard rotational evolution scenario.
+\textit{Left:} the product of histograms of the posterior estimates for 73 stars, or subsets thereof for different stellar classifications.
+\textit{Right:} the cumulative posterior probability for 73 stars, or subsets thereof for different stellar types.}
+	\label{fig:gyroresults}
+\end{figure}
+
+\textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we ensured that the same results were obtained when using different subsets of the ensemble, and when exploring potential biases.
+We found that the joint posterior distribution did not change significantly when excluding stars with a metallicity outside the model range (purple in Figure \ref{fig:fullsample}), or those with extremely small uncertainties on asteroseismic mass.Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $P_{\rm s}$.
+
+The same was true when repeating the analysis with increased uncertainties on asteroseismic mass and age, or when shifting asteroseismic ages younger by their systematic uncertainties \cite{silvaaguirre+2015, silvaaguirre+2017}.
+For a full discussion of these tests and other biases, see \textbf{\textit{Methods}}.\\
+
+Section 5.2.5.
+
+We leave the reader with the following conclusions:
+\begin{enumerate}
+	\item We found that our ensemble was $98.4\%$ more likely to be drawn from a weakened magnetic braking model than a standard model of rotational evolution \cite{vansaders+pinsonneault2013}, at a critical Rossby number of $Ro_{\rm{crit}} = 1.97$.
+This work expands upon previous analysis (\cite{vansaders+2019}) by including quiescent stars older than the Sun.
+This conclusion was found to be robust against choice of ensemble members and potentially underestimated asteroseismic systematic uncertainties.
+A comparison to other braking laws \cite{matt+2015} and other gyrochronology relations using our asteroseismic ensemble will take place in future work.
+
+	\item We compared our new asteroseismic rotation rates with surface rotation measures from spot modulation.
+Our findings replicate those in similar studies \cite{nielsen+2015,benomar+2015}, in the sense that we find no statistically significant difference between seismic and spot modulation measures of stellar rotation in our ensemble.
+
+	\item We present new techniques for asteroseismic `peak-bagging' frequency analyses, specifically: expressing well known empirical asteroseismic relations in a hierarchical modeling structure to account for small-scale effects not included in our model (such as acoustic glitches), and replacing uninformative empirical relations with Gaussian Process priors.
+
+	\item The new asteroseismic rotation catalogue presented in this work will act as an entry point for more detailed studies, including comparisons between different braking laws and individually modeled values of stellar rotation at different critical Rossby numbers.
+\end{enumerate}
+
+Finally, in the near future our asteroseismic rotation catalogue will be further complemented; with high-precision surface rotation measurements and atmospheric parameters from spectroscopic surveys such as LAMOST \cite{deng+2012}, 4MOST \cite{dejong+2014} and WEAVE \cite{dalton+2014}; and new asteroseismic measurements of age from the \ktwo and \tess missions.
+With these surveys, large scale ensemble asteroseismology will continue to increase the possibilities for understanding gyrochronology.\\
+
+All analysis performed as part of this work is stored in an online public repository\footnote{\url{https://github.com/ojhall94/malatium}}.\\
+
+\textbf{Software}: \texttt{astropy} \cite{astropycollaboration+2013, astropycollaboration+2018}, \texttt{astroquery} \cite{ginsburg+2019}, \texttt{Lightkurve} \cite{lightkurvecollaboration+2018}, \texttt{corner} \cite{foreman-mackey2016}, \texttt{emcee} \cite{foreman-mackey+2013}, \href{https://docs.daft-pgm.org/}{\texttt{daft}}, \texttt{Stan} \cite{carpenter+2017}, \texttt{PyStan} \cite{vanhoey+2013}, \texttt{iPython} \cite{perez+granger2007}, \texttt{Jupyter Notebooks} \cite{kluyver+2016}, \texttt{numpy}  \cite{vanderwalt+2011}, \texttt{pandas} and \texttt{scipy} \cite{mckinney2010}, \texttt{matplotlib} \cite{hunter2007}, \texttt{seaborn} \cite{waskom+2018}, \texttt{statsmodels} \cite{seabold+perktold2010}, \texttt{PyMC3} \cite{salvatier+2016}, \texttt{theano} \cite{thetheanodevelopmentteam+2016}.\\
+
+\textbf{Acknowledgments}:The authors would like to thank Sean Matt, Ellis Avallone, Alex Dixon, Warrick Ball and Brett Morris for helpful discussions. 
+OJH, GRD and WJC acknowledge the support of the UK Science and Technology Facilities Council (STFC). 
+JvS acknowledges support from the TESS Guest Investigator Program (80NSSC18K18584).
+MBN acknowledges support from the UK Space Agency
+This work has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (CartographY GA. 804752)
+Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement no.: DNRF106). 
+LA, AB and VS acknowledge funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation program (grant agreement No.
+682393 AWESoMeStars).
+AB also acknowledges the support of the College of Engineering, Mathematics and Physical Sciences at the University of Exeter.
+RAG acknowledges the support from the PLATO and GOLF CNES grants.
+JT acknowledges that support for this work was provided by NASA through the NASA Hubble Fellowship grant $\#51424$ awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
+The computations described in this paper were performed using the University of Birmingham's BlueBEAR HPC service.
+This paper includes data collected by the Kepler mission and obtained from the MAST data archive at the Space Telescope Science Institute (STScI).
+Funding for the Kepler mission is provided by the NASA Science Mission Directorate.
+STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5–26555.\\
 
 % The best way to enter references is to use BibTeX:
+%\bibliographystyle{naturemag}
+%\bibliography{library.bib} %
+
+\textbf{Author Contributions:} O.J.H.
+led the project, with help from G.R.D., J.V.S., M.B.N and W.J.C..
+J.V.S.
+also led the development of the stellar population models.
+M.N.L., R.A.G.
+and S.K.
+both provided data or stellar models and along with J.T.
+assessed the validity of our asteroseismic results.
+L.A., A.B.
+and V.S.
+provided the assessment of the theoretical implications of the gyrochronology results.
+All authors have contributed to the interpretation of the data and the results, and all discussed and provided comments for all drafts of the paper.
+
+\textbf{Competing Interests:} The authors declare that they have no competing financial interests.
+
+\textbf{Correspondence:} Correspondence and requests for materials should be addressed to O.J.H.. (email: oliver.hall@esa.int).
+
+\clearpage
+
+\input{methods.tex}
+
+\input{si.tex}
+
 \bibliographystyle{naturemag}
@@
 
-\section*{Acknowledgements}
-
-\section*{Methods}
-
-\section*{Author Contributions}
-
 \end{document}

### 2020-09-29 paper/natastron/si.tex
Chpping away

\section{Supplementary Information}
\subsection{Asteroseismic Model}\label{s:seismo}
In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background ($B(\nu)$), the oscillations ($O(\nu)$), and the white noise ($W$) in the style of e.g. \cite{davies+2015}. Our data, observed with \kepler, are also subject to the apodization (attenuation) of signals in the frequency-domain, where we fit our model \cite{chaplin+2011}. The apodization in power is given by

\begin{equation}\label{eq:apodization}
	\eta^2(\nu) = \rm{sinc}^2\left(\frac{\pi}{2}\frac{\nu}{\nu_{\rm nyq}}\right)\, ,
\end{equation}
where $\nu_{\rm nyq}$ is the Nyquist frequency for the \kepler short cadence, which was treated as a free parameter in our model to account for gaps in the data. Apodization only affects signals with characteristic timescales, meaning that it does not affect the white noise level, only the oscillations and convective background components. Given the above, our comprehensive model for the power spectrum is

\begin{equation}\label{eq:model}
	M(\nu) = W + \eta^2(\nu)[O(\nu) + B(\nu)]\, .
\end{equation}

\subsubsection{Convective Background}
To model the convective background we used three Harvey components \cite{harvey1985}, which express the background in power as Lorentzian-like functions centered on zero frequency. The Harvey components take the form

\begin{equation}
	H(\nu, a, b, x) = \frac{4a^2/b}{1 + (2\pi b\nu)^x}\, ,
\end{equation}

\noindent where $a$ and $b$ are the free parameters in our model, and $x$ is fixed. The three Harvey components together form our background function as

\begin{equation}\label{eq:background}
	B(\nu) = H(\nu, a, b, x=4) + H(\nu, c, d, x=4) + H(\nu, j, k, x=2)\, ,
\end{equation}

\noindent where we have labeled parameters for the separate components. The $x = 2$ term here contributes to the background at high frequencies, whereas the $x=4$ terms contribute the background at low frequencies.

\subsubsection{Modes of Oscillation}
Modes of oscillation appear in the power spectrum as Lorentzian peaks \cite{chaplin+basu2017}. Due to stellar rotation, each mode with an angular degree of $\ell > 0$ is split into its $(2\ell +1)$ Lorentzian components, labeled by $m$, the azimuthal order. For all $\ell=(0,1,2)$ modes identified in \cite{davies+2016,lund+2017} we add a (set of) Lorentzian(s) to our model, building a composite model representing all visible modes. The construction of our oscillation model takes the form

\begin{equation}
	O(\nu) = \sum_n \sum_\ell \sum_{m=-\ell}^\ell \frac{H_{n,\ell,m}}{1 + \frac{4}{\Gamma^2_{n,\ell}}(\nu - \nu_{n,\ell,m})^2}\, ,
\end{equation}

\noindent where $n$ is the radial order of a mode (i.e. the overtone number of the oscillation), $H_{n,\ell,m}$ is the height of the mode, $\Gamma_{n,\ell}$ is the linewidth of the mode (approximated to be equal for all split components at a single $n$ and $\ell$) and $\nu_{n, \ell, m}$ is the frequency of the mode. The range of $n$ differs per star depending on how many radial orders were reported in LEGACY or Kages, and the range of $\ell$ depends on how many angular degrees were reported for the corresponding radial order.

\subsubsection{Mode Frequencies and Rotational Splitting}\label{ssec:frequencies}
The mode frequencies of main sequence stars are described by the asymptotic expression \cite{tassoul1980, vrard+2016}. The asymptotic expression defines the locations of the modes as regularly spaced, with structured deviation around \numax, the frequency of maximum oscillation amplitude. The expression takes the form

\begin{equation}\label{eq:asymptotic}
	\nu_{n,\ell,m} = \dnu\left(n + \epsilon + \delta\nu_{0,\ell} + \frac{\alpha}{2}(n - \frac{\numax}{\dnu} + \epsilon)^2\right) + m\nu_{s}\, ,
\end{equation}

\noindent where \dnu is the large frequency separation between two consecutive radial orders, $\epsilon$ is a a phase offset, $\delta\nu_{0,\ell}$ is the small frequency separation between two oscillation modes of different $\ell$ at the same radial order, $\alpha$ describes the curvature of the spacing around \numax, and $\nu_s$ is the rotational splitting. Note that here we have expressed the small separation $\delta\nu_{0,\ell}$ as a fraction of $\dnu$. In order to improve the computational efficiency of this analysis, we fixed \dnu to the values reported in LEGACY and Kages.

Instead of calculating mode frequencies directly from Equation \ref{eq:asymptotic} for the model, we treated the individual mode frequencies as parameters as well, drawn from Equation \ref{eq:asymptotic}. This is called a `latent parameter' implementation \cite{hogg2012, hall+2019}, as it forms a step between the parameters we want to draw inference on (also called hyperparameters) and our data. 
The parameters $\nu_{n,\ell,m}$ were allowed to vary within an uncertainty $\sigma_{\ell}$, which has a single value for each angular degree and also varied as a free parameter.
This allowed us to account for small shifts in frequency due to sudden changes in the stellar structure \cite[called acoustic glitches]{mazumdar+2014}. The mode frequency latent parameters were drawn from a normal distribution using Equation \ref{eq:asymptotic} as its mean function, as

\begin{equation}
	\nu_{n, \ell, m} \sim \mathcal{N}(\nu_{n, \ell, m}, \sigma_{\ell})\, ,
\end{equation}

\noindent where the expression $\nu_{n, \ell, m}$ on the right hand side represents the contents of Equation \ref{eq:asymptotic}, and $\mathcal{N}$ represents a normal distribution with a mean equal to $\nu_{n, \ell, m}$ and a standard deviation equal to $\sigma_{\ell}$. The symbol `$\sim$' indicates that the parameters on the left hand side of the equation are drawn from the probability distribution on the right hand side. This notation will be used throughout this paper.

\subsubsection{Mode Linewidth}
The linewidths of asteroseismic p modes vary roughly as a function of mode frequency, and do so slowly relative to \dnu. This can be expressed as an empirical relation \cite{davies+2014, appourchaux+2016, lund+2017}. However, this relation has six free parameters, none of which are directly relevant to this work. Instead of fitting this relation, we chose to employ a more flexible Gaussian Process \cite[GP]{rasmussen+williams2006} to act as a prior on the linewidths. This can be considered as us modelling the linewidths as correlated measurements. As our GP covariance kernel we used a Squared Exponential Kernel to capture the slight periodicity of linewidth with frequency, as

\begin{equation}\label{eq:gpkernel}
	K_{i,j} = \rho^2 \exp \left[ -\frac{(n_{\textrm{f}, i} - n_{\textrm{f}, j})^2}{2L^2} \right]\, ,
\end{equation}

\noindent where $n_{\rm f}$ is the fractional radial order of a given mode. For each star, the overtone numbers $n$ were rescaled to be between 0 (for the lowest $n$) and 1 (for the highest $n$)\footnote{Overtones of $\ell = 2$ modes were increased by $1$ to ensure this approximation applied to all modes.}. This approximation was used to describe the change in linewidth as a function of frequency without depending on the exact frequencies of the modes. $K_{i,j}$ represents an element of the covariance matrix $\underline{K}$, describing the covariance between two values of linewidth at different fractional radial orders. The GP kernel has two hyperparameters: $\rho$, which determines the spread of the kernel, and $L$, which determines the length scale in terms of $n_{\rm f}$. The length scale was significantly larger than the large frequency separation (\dnu) in all cases, and so we considered the use of fractional radial orders a valid approximation in this model.

A linear function was used for the mean of the GP, as

\begin{equation}\label{eq:gpmean}
	\mu = m \times n_{\textrm{f}} + c\, ,
\end{equation}
where $m$ and $c$ are the slope and intercept of the line. The linewidth latent parameters were then drawn from the multivariate probability distribution

\begin{equation}\label{eq:gammagp}
	\Gamma \sim \mathcal{N}(\mu, \underline{K})\, ,
\end{equation}

\noindent where $\Gamma$ represents the linewidths of all the modes in the model. The parameters $m$, $c$ and $\rho$ were marginalised over, whereas $L$ was fixed to a pre-determined value.

\subsubsection{Mode Heights and Angle of Inclination}
The height in power of each mode, $H_{n, \ell, m}$, varies not only as a function of distance in frequency from \numax, but also due to observation conditions, such as inclination angle and passband. In our model, we treated $H_{n, \ell, m}$ as a deterministic parameter, as

\begin{equation}\label{eq:height}
	H_{n, \ell, m} =  \varepsilon_{\ell, m}(i) \frac{2 (A_{n, \ell})^2}{\pi \Gamma_{n, \ell}}\, ,
\end{equation}

\noindent where $\varepsilon_{\ell, m}(i)$ modulates the height as a function of inclination angle ($i$) (see below), and $A_{n, \ell}$ and $\Gamma_{n, \ell}$ are the mode amplitude and linewidth respectively for a given radial order and angular degree. Instead of modeling and modulating height directly, we instead sampled in amplitude and linewidth. This approach mitigates the correlations between height and linewidth in the sampling process \cite{toutain+appourchaux1994}.

As done above for the mode frequencies and linewidths, the mode amplitudes $A_{n,\ell}$ were also treated as latent parameters drawn from a probability distribution governed by hyperparameters. We used a Gaussian function $G(\nu)$, centered on $\numax$, so that

\begin{equation}\label{eq:amplitude}
	G(\nu) = A \times \exp\left[-\frac{(\nu - \numax)^2}{2w^2}\right]\, ,
\end{equation}

\noindent where $A$ is the amplitude at \numax, and $w$ is the width of the Gaussian, both free parameters in our model. 
The mode amplitude latent parameters were then drawn from the probability distribution

\begin{equation}
	A_{n, \ell} \sim \mathcal{N}(G(\nu_{n,\ell}) \times V_\ell, \sigma_{A})\, ,
\end{equation}

\noindent where $V_\ell$ is a free parameter for the mode visibility of different angular degrees, which should be consistent for all \kepler observations. The mode visibility for $V_0$ is fixed at 1, and $V_{1,2}$ are treated as free parameters. The parameter $\sigma_{A}$, the uncertainty on the distribution, is also a free parameter, and takes the same value for all amplitudes regardless of angular degree.\\

The angle of inclination of a star with respect to Earth changes the net perturbation by a given mode when integrated across the stellar disc, changing the amplitudes of modes of different azimuthal orders. This is a geometric problem, and is expressed by $\varepsilon_{\ell, m}(i)$, which takes the form \cite{gizon+solanki2003}

\begin{equation}\label{eq:legendre}
	\varepsilon_{\ell, m}(i) = \frac{(\ell - |m|)!}{(\ell + |m|)!}\left[P_\ell^{|m|}(\cos(i))\right]^2\, ,
\end{equation}

\noindent where $P_\ell^{|m|}$ are associated Legendre functions. For the first three angular degrees, Equation \ref{eq:legendre} takes the form \cite{handberg+campante2011}

\begin{equation}
	\begin{split}
		\varepsilon_{0,0}(i) &= 1\, ,\\
		\varepsilon_{1,0}(i) &= \cos^2(i)\, ,    \\
		\varepsilon_{1,\pm1}(i) &= \frac{1}{2}\sin^2(i)\, ,\\
		\varepsilon_{2,0}(i) &= \frac{1}{4}(3\cos^2(i) - 1)^2\, ,\\
		\varepsilon_{2,\pm1}(i) &= \frac{3}{8}\sin^2(2i)\, ,\\
		\varepsilon_{2,\pm2}(i) &= \frac{3}{8}\sin^4(i)\, ,
	\end{split}
\end{equation}

\noindent where the sum of available components for a single $\ell$ are normalized to one.

\subsubsection{Likelihood Function}\label{sec:like}
If data have Gaussian noise in the time domain, they will appear in the frequency domain with noise following a $\chi^2$ distribution with two degrees of freedom \cite[$\chi^2_2$ hereafter][]{woodard1984}. The noise properties of $\chi^2_2$ distributed data are multiplicative, and require a specific treatment when fitting a model. As our frequency bins can be approximated to be independent, we used the likelihood function \cite{anderson+1990},

\begin{equation}
	\ln p(\mathcal{P} | M) = \sum_{j=0}^{N-1} \left[\ln[M_j(\nu)] + \frac{\mathcal{P}_j}{M_j(\nu)}\right]\, , 
\end{equation}

\noindent where $\mathcal{P}$ is the power spectral density (and thus our data), and $M(\nu)$ represents our model. The subscript $j$ denotes an individual datum, for a total of $N$ data. We have omitted the dependence of the model $M(\nu)$ on its parameters, for clarity. This equation is functionally equivalent to the evaluation of a gamma distribution of the form $\gamma(\mathcal{P} | 1, \beta)$, where $\beta = 1/M(\nu)$, which is the implementation we used in the sampling process.

\subsubsection{Fitting the convective background}\label{sec:background}
Fitting the convective background, apodization and white noise component must be done for the full range of the power spectrum in order to be accurately constrained. However, fitting a single model to the full range of frequencies is computationally inefficient when we are interested in the modes of oscillation, as these occupy a relatively small range of frequencies.

In order to speed up this process, the background was first fit independently to a subset of our data for each star. This subset was created by removing all frequencies within a range $0.1 \times \dnu$ below and above the minimum and maximum mode frequencies reported in LEGACY and Kages. For KIC 3427720 we also removed frequencies in the range $90\, \mu\rm{Hz} < \nu < 400\, \mu{\rm{Hz}}$, where there were large peaks not of asteroseismic origin, skewing the background fit.

For each star the model function (see Eq. \ref{eq:model}) was fit, as

\begin{equation}
	M_{B}(\nu) = W + \eta^2(\nu)B(\nu)\, ,
\end{equation}

\noindent where $B(\nu)$ is the background model described in Equation \ref{eq:background}. The parameter components of our background fit are then $\phi_B = \{\log(a), \log(b), \log(c), \log(d), \log(j), \log(k), W, \nu_{\rm nyq}\}$, where the parameters of the Harvey components were sampled in log space. The model was fit to the background data using \texttt{PyStan} \cite{vanhoey+2013}, run for 10,000 iterations on each star\footnote{These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work.}.

\subsubsection{Obtaining First Guesses and Prior Values}
In order to utilise some of the prior measurements of our targets without using them as hard constraints on our parameters, some of our model equations were fit to LEGACY and Kages data to obtain first guesses and mean values on hyperparameter priors.

For first guesses for parameters in the asymptotic expression, we fit Equation \ref{eq:asymptotic}, \textit{not} including the rotational component $m\nu_s$, to the $\ell = (0, 1, 2)$ mode frequencies reported in LEGACY and Kages for each star, using their reported uncertainties. This yielded estimates of $\hat{\epsilon}$, $\widehat{\delta\nu}_{01}$, $\widehat{\delta\nu}_{02}$ and $\hat{\alpha}$, where the hat symbol `\, $\widehat{}$\, ' indicates a prior value (e.g. $\hat{\nu}_{\rm max}$ is taken from LEGACY or Kages). While not precise, as we did not mitigate any perturbations due to acoustic glitches (sudden changes in interior sound speed, which the latent parameter treatment takes care of in the full model), these rough results act as functional first guesses and prior mean values. The relation was fit to each star using PyMC3 \cite{salvatier+2016} using 5000 iterations on 4 chains.

To obtain first guesses for the parameters used to set the GP prior on linewidth, we fit a GP constructed as in Equation \ref{eq:gammagp} to the linewidths of the $\ell = 0$ modes reported in LEGACY. Linewidths were not reported for the other angular degrees in LEGACY, but the estimates may be generalised to other $\ell$, as linewidth is a strong function of frequency.  The relation was fit to each star using PyMC3 using 2500 iterations on 4 chains.

Fitting the LEGACY linewidths yielded rough estimates of $\hat{m}$, $\hat{c}$, $\hat{\rho}$ and $L$ for each star. As is noted in Equation \ref{eq:gammagp}, $L$ was fixed to this fit value when fitting our full model to our data. For stars in Kages, for which no linewidths were reported, we instead fixed these prior values to $\hat{m} = 1$, $\hat{c} = 0.5$, $\hat{\rho} = 0.1$, and the length scale to $L = 0.3$. These values were chosen to reflect those found for the LEGACY stars.

Finally, we obtained prior values for the Gaussian function describing the distribution of mode amplitudes around \numax. The mode amplitude of the highest peak in the spectrum was used for the amplitude, which was typically at or near \numax. For the width of the Gaussian we used the empirical function \cite{lund+2017}

\begin{equation}
	\hat{w} = 0.25 \times \numax\, .
\end{equation}

\noindent For the mode visibilities, we used $\hat{V}_1 = 1.2$ and $\hat{V}_2 = 0.7$, which reflect the results for these parameters reported in the LEGACY catalogue.

\subsubsection{Priors on our Hyperparameters}
Given our first guesses and measured prior values, we can define the prior probabilities of the hyperparameters on which our model depends. For the mode frequency hyperparameters, these are

\begin{equation}
	\begin{split}
		\numax &\sim \mathcal{N}(\hat{\nu}_{\rm max}, 10)\, ,\\
		\epsilon &\sim \mathcal{N}(\hat{\epsilon}, 1)\, ,\\
		\alpha &\sim \ln\mathcal{N}(\ln(\hat{\alpha}), 0.01)\, ,\\
		\delta\nu_{01} &\sim \ln\mathcal{N}(\ln(\widehat{\delta\nu}_{01}), 0.1)\, ,\\
		\delta\nu_{02} &\sim \ln\mathcal{N}(\ln(\widehat{\delta\nu}_{02}), 0.1)\, ,\\
		\sigma_{0,1,2} &\sim \mathcal{C}_{1/2}(\beta = 2)\, ,
	\end{split}
\end{equation}

\noindent where $\ln\mathcal{N}$ represents a log-Normal distribution and $\mathcal{C}_{1/2}$ represents a half-Cauchy distribution, and other symbols are as described above. All three hyperparameters $\sigma_{0,1,2}$ describing the uncertainty on the latent parameters of different angular degree were subject to the same prior.

For the mode linewidths, our hyperparameter priors took the form

\begin{equation}
	\begin{split}
		m &\sim \mathcal{N}(\hat{m}, 1)\, ,\\
		c &\sim \mathcal{N}(\hat{c}, 1)\, ,\\
		\rho &\sim \ln\mathcal{N}(\ln(\hat{\rho}), 0.1)\, ,\\
	\end{split}
\end{equation}

\noindent where the conventions are the same as above. For our mode amplitudes, they took the form

\begin{equation}
	\begin{split}
		w &\sim \ln\mathcal{N}(\ln(\hat{w}), 10)\, ,\\
		A &\sim \ln\mathcal{N}(\ln(\hat{A}), 1)\, ,\\
		V_1 &\sim \ln\mathcal{N}(\ln(\hat{V}_1), 0.1)\, ,\\
		V_2 &\sim \ln\mathcal{N}(\ln(\hat{V}_2), 0.1)\, ,\\
		\sigma_A &\sim \mathcal{C}_{1/2}(\beta = 1)\, .
	\end{split}
\end{equation}

As the convective background had already been fit to our data excluding the region where the modes are present, the results from that fit could be used as extremely informative priors on our fit to the region containing the modes, where there is little information present to constrain the background. To do so, we modeled the background parameters $\phi_B$ in our full model as being drawn from a multivariate normal distribution as

\begin{equation}
	\phi_{B}\sim\mathcal{N}(\hat{\phi}_{B},\underline{\Sigma}_{\hat{\phi}_{B}})\, ,
\end{equation}

\noindent where $\hat{\phi}_B$ are the median values of our posterior distributions from our prior background fit, and $\underline{\Sigma}_{\hat{\phi}_{B}}$ is the full covariance matrix of all the posterior distributions from our prior background fit, taking into account the correlations between the different Harvey components.

Finally, we defined the priors on the rotational parameters: the mode splitting ($\nu_s$), and the inclination angle ($i$). In order to give these an appropriate treatment, we made two reparameterizations. First, we sampled the projected rotational splitting, $\nu_{\rm{s}}\sin(i)$, which is more efficiently sampled due to the strong correlations between $i$ and $\nu_{\rm s}$ \cite{ballot+2006,ballot+2008a}. A prior was applied over this as

\begin{equation}
	\nu_s\sin(i) \sim \ln\mathcal{N}(\ln(0.75), 0.75)\, ,
\end{equation}

\noindent where conventions are as above. This subjective prior was chosen to reflect that most stars will have a solar-like rotation, with a long tail to allow for the fastest rotators. Second, we sampled in $\cos(i)$, and gave this a prior of

\begin{equation}
	\begin{split}
		\cos(i) &\sim \mathcal{U}(0, 1)\, ,
	\end{split}
\end{equation}
which is equivalent to stating that probability to observe an inclination angle $i$ is equal to $\sin(i)$. Here, the $\mathcal{U}(0,1)$ indicates a uniform prior between 0 and 1. Using a uniform prior on $\cos(i)$ allowed us to account for the geometric effect that stars with a large inclination angle with respect to us are more common \cite{chaplin+basu2017}.

\subsubsection{Fitting procedure}
Using our prior information and model described above, we fit Equation \ref{eq:model} to our data $\mathcal{P}$, using the likelihood function described in Section \ref{sec:like}.

In order to speed up the fitting process, we only applied our model to the region of the power spectrum that contains visible modes of oscillation. We created this subset by removing all frequencies outside a range $0.25 \times \Delta\nu$ below and above the minimum and maximum mode frequencies reported in LEGACY and Kages. This region overlaps minimally with the data used to fit for our prior information of the convective background (see Section \ref{sec:background}), so that both model fits are independent.

To improve computational efficiency, we reduced the number of oscillation modes being fit in five targets. For 16 Cyg A \& B, KIC 7970740 and KIC 8478994, we excluded any modes with a Bayes Factor ($\ln(K)$) of less than 6, as reported in LEGACY \cite{kass+raftery1995,davies+2016,lund+2017}. For KIC 8478994, which is reported without a value for $\ln(K)$ in Kages, we only included modes of an overtone number that contained a detection for all of $\ell = (0, 1, 2)$, retaining 5 sets of higher signal-to-noise overtones. We do not expect this reduced scope to bias our results, although they may reduce the precision on our measured rotation rates.

We fit our model to our power spectrum data with \texttt{PyMC3}, using 2500 iterations each on 4 chains. An example of our model fit to an asteroseismic power spectrum of 16 Cyg A is shown in Figure \ref{fig:modelfit}.

### 2020-09-29 paper/natastron/comments.tex
Finished main body

I had a look at your most recent version, and here are some structural comments based on that. Bear in mind that Nature Astronomy is a short-format journal, so there’s typically no available room for extensive setting of context or exhaustive literature studies… this means you really have to crystallise what it is you want to say, and just include the absolutely necessary information to support your scientific case.

There is too much in the way of introduction in your most recent manuscript… we don’t need a history of gyrochronology or of asteroseismology, but just the key aspects that you will build on later. For instance, you want to support the van Saders+16/19 results… that means we need to know the context of the van Saders+16 paper, the response in the literature around that time period, the impact of the van Saders+19 paper on the landscape, and then how your work will build on what has gone on previously to strengthen the evidence for weakened magnetic braking. We typically suggest that the entire introduction (so, your Section 1) should be about 500 words, and currently yours is over 1,000, so plenty of cutting can be done there. We do not usually lay out the structure of a paper (the final paragraph of S1)… Articles are so short that the structure is usually evident from the section headings.

DONE

Section 2 can largely be moved to the Methods section (by Methods section I mean the section that follows on from the main references in a NAstro paper, not your Section 3…), and an overall summary can be included in say, a single paragraph in the main text. Your Section 3 is very extensive, and probably should be kept together, meaning that it is probably best put into the Supplementary Information PDF.

DONE

Your Section 4 can probably be kept in the main text of the paper, but you might want to reduce the level of detail… for instance, all the checks you carried out can probably be mentioned more succinctly, or given a section in the Methods.

DONE

Discussion of your results should make up about half of the main text. Looking at your Section 5, you may want to reduce the level of detail to focus on what new information your work brings about. For instance, S5.1.2, comparison to previous studies… this looks like another checking section, so should be moved to the Methods or the SI. S5.1.3 has a lot of confirmations and comparisons… unless you are saying something new, this should be moved elsewhere. S5.2 in general, more verification… not for the main text. S5.2.5 is the key point of your paper, the main result, and this should be the highlight… this is what you set out to prove. At present it is a bit lost in the surrounding huge amounts of detail.

DONE

Your Conclusion section is good… in fact, it is exactly the right amount of detail for the Discussion section. So, I would say the Discussion section of your NAstro paper should be made up of your Sections 5.2.5 and 6. The actual conclusion paragraph of your NAstro paper should just be a reiteration of your main point(s), in perhaps a sentence each.

 DONE

Note that if you want software to be cited (as is good and right), you should incorporate the citations into the text somewhere (the Methods section or figure/table captions are ideal for this)… we don’t have a software section in its own right.

Apologies if this comes across as a bit brutal… you have clearly put a lot of work into this project and of course you want to display it in a paper. However, papers in NAstro or Nature or Science require a very different approach to paper-writing… they are quite a challenge to write, because you need a logical flow, a certain level of detail, great focus, and of course everything you would need to make your work reproducible… but all in a very small space.

So, as a reminder, your main text (intro, brief outline of procedure, results, discussion, conclusion/outlook) should be about 3,000-3,500 words (not including Abstract), your Methods section should be a similar length, and everything else can go into the Supplementary Information. In terms of figures/tables: six in the main text, zero in the Methods (okay, one small table if you need it), up to 10 in an Extended Data section (caveat: all of these figures/tables should be cited from the main text/Methods) and everything else in the Supplementary Information.

I hope that helps, and if you have any further questions, feel free to get in touch.

### 2020-09-29 paper/natastron/paper.tex
Finished main body

@@
 \textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we ensured that the same results were obtained when using different subsets of the ensemble, and when exploring potential biases.
-We found that the joint posterior distribution did not change significantly when excluding stars with a metallicity outside the model range (purple in Figure \ref{fig:fullsample}), or those with extremely small uncertainties on asteroseismic mass.Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $P_{\rm s}$.
+We found that the joint posterior distribution did not change significantly when excluding stars with a metallicity outside the model range (purple in Figure \ref{fig:fullsample}), or those with extremely small uncertainties on asteroseismic mass.
+Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $P_{\rm s}$.
 
-The same was true when repeating the analysis with increased uncertainties on asteroseismic mass and age, or when shifting asteroseismic ages younger by their systematic uncertainties \cite{silvaaguirre+2015, silvaaguirre+2017}.
+We checked that our results remained the same if the `Kages' and LEGACY catalogues had underestimated the uncertainties on the asteroseismic mass and age, which form part of our mixture model analysis.
+We reran our analysis after inflating the uncertainties on these properties to align with the expected systematic uncertainty from stellar models \cite{silvaaguirre+2015,silvaaguirre+2017}.
+The results from this echoed what we found for the unaltered ensemble.
+We also accounted for the possibility that asteroseismic methods systematically overestimated stellar age, and reran our analysis after shifting the seismic ages younger by their systematic uncertainty.
+This resulted in $95.8\%$ of the posterior probability to lie below $P_{\rm s} = 0.5$, compared to $98.4\%$ for the unaltered ensemble.
+From this, we can infer that our conclusions are robust against (relatively severe) potential issues in seismic analyses.
 For a full discussion of these tests and other biases, see \textbf{\textit{Methods}}.\\
 
-Section 5.2.5.
+Weakened magnetic braking was first proposed by van Saders et al.
+(2016) \cite[hereafter the `van Saders' study]{vansaders+2016} in response to stars with spot rotation rates faster than expected from gyrochronology at their asteroseismic ages \cite{vansaders+2016}.
+This discrepancy was also indicated at around the same time in other studies of asteroseismic ages of main sequence stars \cite{nielsen+2015, angus+2015, davies+2015}.
+The theory of weakened magnetic braking has been both reinforced by recent studies \cite{metcalfe+egeland2019}, as well as disputed \cite{lorenzo-oliveira+2019}, at least at the critical Rossby number originally proposed.
+
+A recent study using spectroscopic rotation measurements of 14 solar twins, compared to grids of stellar models, found marginal evidence favouring a standard rotational evolution \cite{lorenzo-oliveira+2019}.
+If weakened magnetic braking were to take place, this work proposed that it would most likely be outside the range of their sample, at $Ro_{\rm {crit}} \geq 2.29$, compared to the value of $1.97$ used in this work.
+Our sample does not overlap with theirs, so we can not directly compare to their results.
+However, our work does find statistical agreement between our asteroseismic rotation rates and ages, and a model of weakened magnetic braking at a critical Rossby number of $1.97$.
+A comparison to models of different Rossby numbers will be explored in future papers, using the LEGACY and Kages rotation sample presented in this work.
+
+As a sanity check that the evidence in favour of weakened magnetic braking presented in this work is independently robust, we recreated the joint posterior probability for $P_{\rm s}$, this time looking only at MS stars, and excluding any of the 22 stars that were included in the original van Saders study used to detect weakened magnetic braking.
+Of the 47 MS stars used to distinguish between stellar models, 16 were included in the van Saders sample.
+Both the 16 stars in the original van Saders study as well as the remaining MS stars favoured the WMB model, although the van Saders stars did so more strongly, not including any stars that favoured the standard model.
+Specifically, when considering only the van Saders stars, $96.3\%$ of the total joint probability lay below $P_{\rm s} = 0.5$, compared to $91.7\%$ when considering only those stars \emph{not} included in the van Saders study.
+The stars initially used to propose the WMB model are still those most strongly in favour of it even when using asteroseismic rotation rates only, a result which is now further reinforced by an expanded sample that includes quiescent stars.\\
+
+\textbf{Conclusions:} In this work, we obtained asteroseismic rotation rates for 91 stars using a hierarchical Bayesian model to fit for oscillation frequencies, convective background, and rotational splitting simultaneously.
+We validated these results against previously published and unpublished asteroseismic rotation measurements, making our new rotation catalogue the largest self-consistent sample of asteroseismic rotation in main sequence stars to date.
+We evaluated the stars in our sample against synthetic population models of the \textit{Kepler} field evolved under either a `standard' model of rotational evolution, or one where weakened magnetic braking takes place.
+This evaluation was done using a Bayesian mixture model to determine whether the ensemble preferred one model over another, and was done in simultaneously in asteroseismic rotation, mass, age, and spectroscopic temperature and metallicity.\\
 
@@
 
-	\item We present new techniques for asteroseismic `peak-bagging' frequency analyses, specifically: expressing well known empirical asteroseismic relations in a hierarchical modeling structure to account for small-scale effects not included in our model (such as acoustic glitches), and replacing uninformative empirical relations with Gaussian Process priors.
+	\item We present new techniques for asteroseismic `peak-bagging' frequency analyses, specifically: expressing well known empirical asteroseismic relations in a hierarchical modeling structure to account for small-scale effects not included in our model (such as acoustic glitches), and replacing uninformative empirical relations with Gaussian Process priors, detailed in the \textit{\textbf{Supplementary Information}}.
 
-	\item The new asteroseismic rotation catalogue presented in this work will act as an entry point for more detailed studies, including comparisons between different braking laws and individually modeled values of stellar rotation at different critical Rossby numbers.
 \end{enumerate}
 
-Finally, in the near future our asteroseismic rotation catalogue will be further complemented; with high-precision surface rotation measurements and atmospheric parameters from spectroscopic surveys such as LAMOST \cite{deng+2012}, 4MOST \cite{dejong+2014} and WEAVE \cite{dalton+2014}; and new asteroseismic measurements of age from the \ktwo and \tess missions.
+In the near future this asteroseismic rotation catalogue will be further complemented with high-precision surface rotation measurements and atmospheric parameters from spectroscopic surveys such as LAMOST \cite{deng+2012}, 4MOST \cite{dejong+2014} and WEAVE \cite{dalton+2014}, and new asteroseismic measurements of age from the \ktwo and \tess missions.
 With these surveys, large scale ensemble asteroseismology will continue to increase the possibilities for understanding gyrochronology.\\
@@
 
-\textbf{Software}: \texttt{astropy} \cite{astropycollaboration+2013, astropycollaboration+2018}, \texttt{astroquery} \cite{ginsburg+2019}, \texttt{Lightkurve} \cite{lightkurvecollaboration+2018}, \texttt{corner} \cite{foreman-mackey2016}, \texttt{emcee} \cite{foreman-mackey+2013}, \href{https://docs.daft-pgm.org/}{\texttt{daft}}, \texttt{Stan} \cite{carpenter+2017}, \texttt{PyStan} \cite{vanhoey+2013}, \texttt{iPython} \cite{perez+granger2007}, \texttt{Jupyter Notebooks} \cite{kluyver+2016}, \texttt{numpy}  \cite{vanderwalt+2011}, \texttt{pandas} and \texttt{scipy} \cite{mckinney2010}, \texttt{matplotlib} \cite{hunter2007}, \texttt{seaborn} \cite{waskom+2018}, \texttt{statsmodels} \cite{seabold+perktold2010}, \texttt{PyMC3} \cite{salvatier+2016}, \texttt{theano} \cite{thetheanodevelopmentteam+2016}.\\
+%\textbf{Software}: \texttt{astropy} \cite{astropycollaboration+2013, astropycollaboration+2018}, \texttt{astroquery} \cite{ginsburg+2019}, \texttt{Lightkurve} \cite{lightkurvecollaboration+2018}, \texttt{corner} \cite{foreman-mackey2016}, \texttt{emcee} \cite{foreman-mackey+2013}, \href{https://docs.daft-pgm.org/}{\texttt{daft}}, \texttt{Stan} \cite{carpenter+2017}, \texttt{PyStan} \cite{vanhoey+2013}, \texttt{iPython} \cite{perez+granger2007}, \texttt{Jupyter Notebooks} \cite{kluyver+2016}, \texttt{numpy}  \cite{vanderwalt+2011}, \texttt{pandas} and \texttt{scipy} \cite{mckinney2010}, \texttt{matplotlib} \cite{hunter2007}, \texttt{seaborn} \cite{waskom+2018}, \texttt{statsmodels} \cite{seabold+perktold2010}, \texttt{PyMC3} \cite{salvatier+2016}, \texttt{theano} \cite{thetheanodevelopmentteam+2016}.\\
 
@@
 and S.K.
-both provided data or stellar models and along with J.T.
+provided data or stellar models and along with J.T.
 assessed the validity of our asteroseismic results.

### 2020-09-29 paper/natastron/ed.tex
Done with the main body pretty much

--- 2020-09-29 paper/natastron/methods.tex
@@
-\section*{Methods}
-\setcounter{tocdepth}{2}
-\tableofcontents
-\section{Asteroseismic Methods}
-\subsection{Asteroseismic Data}
-For our asteroseismic power spectrum data we used the unweighted power spectra from the KASOC pipeline \cite{handberg+lund2014}\footnote{Obtainable from the \href{http://kasoc.phys.au.dk/}{KASOC} webpage.}.
-We did not apply any additional treatment to these data.
-For 16 Cyg A \& B (KIC 12069424 and KIC 12069449) we used the KEPSEISMIC lightcurves \cite{garcia+2011}\footnote{Obtainable from \href{https://archive.
-		stsci.edu/prepds/kepseismic/}{MAST}.}, which have significantly better signal-to-noise for these two stars.
-
-For our sample, we used the asteroseismic ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{silvaaguirre+2015} in the Kages and LEGACY catalogues.
-These ages have been obtained by comparisons of measured oscillation properties to stellar models, accounting for an expanded range of metallicities.
-\texttt{BASTA} is thoroughly compared to four other seismic modelling techniques in \cite{silvaaguirre+2017}.
-While uncertainties found through \texttt{BASTA} are typically higher than for other techniques, only \texttt{BASTA} and \texttt{ASTFIT} \cite[Aarhus STellar Evolution Code]{christensen-dalsgaard2008} recover the radius, mass and age of the Sun, when applied to solar data.
-Although the uncertainties on \texttt{ASTFIT} ages are overall lower, they are not reported in \cite{silvaaguirre+2015} for the Kages sample.
-In order to maintain an internally consistent stellar age sample, we used age results from \texttt{BASTA} for both the Kages and LEGACY samples.
-
-For our stellar masses we used asteroseismic model masses obtained by \texttt{BASTA} reported in Kages and LEGACY, in order to maintain internal consistency with the age measurements.
-We note that age and mass posteriors from \texttt{BASTA} are correlated, but chose not to account for the unpublished correlations in this work.
-As described in the catalogue papers, for Kages stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy reported in \cite{huber+2013a}.
-For LEGACY stars, atmospheric properties were similarly taken from \cite{buchhave+latham2015} for most stars in the catalogue, and complemented by other values from the literature for the remaining stars \cite[see Table 3]{silvaaguirre+2017}.
-
+\clearpage 
  \begin{figure*}
@@
 
-\section{Gyrochronology Methods}\label{s:gyro}
-\subsection{Stellar Models}\label{ssec:models}
-The braking models used in this work have several parameters that inform the rotational evolution.
-These are: a normalization factor to reproduce the solar rotation ($f_k$); a disk locking timescale ($T_{\rm disk}$) and period ($P_{\rm disk}$) which together regulate the stellar angular velocity during the pre-main sequence; the critical angular velocity that marks the transition from saturated (rapidly rotating) to unsaturated (slowly rotating) regimes ($\omega_{\rm crit}$), and the critical Rossby number, above which stars conserve angular momentum ($Ro_{\rm crit}$), mentioned above.
-$T_{\rm disk}$, $P_{\rm disk}$ and $\omega_{\rm crit}$ are calibrated to match the behavior in young open clusters, but have little impact on the rotational evolution beyond $\approx 1\, \rm{Gyr}$ in solar-mass stars.
-Both $f_k$ and $Ro_{\rm crit}$ affect the late-time evolution.
-Both models adopt $\omega_{\rm crit} = 3.4  \times 10^{-5}\, \rm{s}^{-1}$, $P_{\rm disk} = 8.1$, $T_{\rm disk} = 0.28$ and $f_k = 6.6$.
-In the weakened magnetic braking model, $Ro_{\rm crit} = 1.97$.
-For further details, see \cite{vansaders+pinsonneault2013} and \cite{vansaders+2016, vansaders+2019}.
-
-Instead of comparing asteroseismic measurements of age and rotation directly to rotational models of individual stars, we instead compared them to synthetic populations based on rotational models, similar to those presented in \cite{vansaders+2019}, with some adaptations.
-To construct a synthetic population of rotating stars, \cite{vansaders+2019} applied the rotational braking laws described above to a galactic population model.
-Their approach used a TRILEGAL \cite{girardi+2012} Milky-Way simulation of the \kepler field, using the standard population values intended for this purpose from \cite{girardi+2015}.
-Stars from the TRILEGAL simulations were then drawn randomly in bins until they matched observations of stellar parameters of the \kepler field \cite{mathur+2017}.
-This aimed to replicate the \kepler selection effect, by ensuring the TRILEGAL population properties matched those observed in the \kepler field.
-
-We used the same approach here, with two changes.
-First, we updated the distribution of stellar parameters matched to the TRILEGAL populations.
-Instead of \cite{mathur+2017}, we used the \cite{berger+2020} temperatures and luminosities, and 2MASS $K$-band magnitudes as our stellar parameter distributions for the \kepler field, which are more accurate following the use of \gaia DR2 parallaxes \cite{gaiacollaboration+2018}.
-The TRILEGAL simulation was matched to the \cite{berger+2020} sample using a nearest-neighbours approach (as opposed to binning), based on the density of stars on the HR diagram.
-
-Second, we made further changes to account for possible binarity in the the \cite{berger+2020} sample.
-If the first step is performed blindly, blended binaries in the sample cause an overestimation of the number of old stars.
-In order to overcome this, we:
-
-\begin{enumerate}
-	\item blended the TRILEGAL stars with binary companions drawn from a flat mass-ratio distribution, using the binary fraction of \cite{raghavan+2010},
-	\item recalculated the `observed' luminosities and magnitudes assuming that each binary pair was blended, and
-	\item shifted these stars' temperatures following the $g$-$K$ relation presented in \cite{berger+2020}.
-\end{enumerate}
-
-This new distribution was used for the nearest-neighbour matching.
-Once drawn we dropped the binary companion and used the true TRILEGAL properties of those stars.
-For stars where the mass of the companion was $M < 0.4\, M_\odot$, binary contributions were ignored.
-Every binary was assumed to result in a blend, regardless of separation.
-This results in slightly more young stars than reality, because young, blended binary systems contaminate regions of the HR diagram where one expects to find old stars, and the number of blends is overestimated by assuming every binary system is a blend.
-
-Our asteroseismic sample of stars with short cadence observations are subject to additional selection functions not included in the creation of the model populations above.
-We did \textit{not} explicitly account for these asteroseismic selection functions in our model, by design.
-Both the standard and WMB models contain stars with the same fundamental parameters (mass, radius, effective temperature, metallicity) but a different period based on the choice of rotational evolution prescription.
-Applying an asteroseismic selection function that depends on these fundamental parameters \cite{chaplin+2011} would apply an identical prior to both models, therefore providing no net effect on our posterior distribution.
-Additionally, we expected any seismic selection function to be relatively flat (and therefore uninformative) on a star-by-star scale, on which we run our model analysis (as opposed to a population scale, see below).
-
-\subsection{Bayesian Mixture Models}
-In order to determine whether weakened magnetic braking occurs on the main sequence, we compared our sample of seismic age and rotation, along with temperature, metallicity and mass, to the two stellar population models of the \kepler field adapted from \cite{vansaders+2019}, discussed above.
-Both stellar models were evaluated in a Bayesian framework, with the rationale of determining which of the two models (standard or WMB) is most likely to reproduce our observed data.
-Each model sample contained temperature (\teff), mass ($M$), age ($t$), metallicity ($\rm{[Fe/H]}$) and rotation ($P$) information.
-
-In order to draw probabilistic inference about the models, we built a five-dimensional Kernel Density Estimate (KDE) of both model populations using the \texttt{statsmodels} package \cite{seabold+perktold2010}.
-We used a band-width (setting the resolution of the KDE) of $0.02\, M_\odot$ in mass, $10\, \rm K$ in \teff, $0.01\, \rm{dex}$ in $\ln(t)$, $0.01\, \rm{dex}$ in $\rm{[Fe/H]}$ and $0.01\, \rm{dex}$ in $\ln(P)$.
-Note that age and rotation were treated in log space, where the posterior estimates from asteroseismology more closely resemble normal distributions.
-This approach translates the population models to a probability distribution we can use in a Bayesian framework.
-
 \begin{figure}
@@
 \end{figure}
-
-We evaluated our data against both models simultaneously by treating the data as being drawn from a mixture of both model KDEs.
-In this mixture model structure, the two KDEs were modulated by a weighting factor, $P_{\rm s}$.
-In the limit $P_{\rm s} \rightarrow 1$, the data are most likely drawn from the standard model.
-In the limit $P_{\rm s} \rightarrow 0$, the data are most likely drawn from the WMB model.
-
-The posterior probability of obtaining $P_{\rm s}$ and additional parameters $\theta$ given our data $\mathcal{D}$ is $p(P_{\rm{s}}, \theta | \mathcal{D})$.
-Using Bayes equation, we can express this as:
-
-\begin{equation}\label{eq:modelll}
-	p(P_{\rm{s}}, \theta | \mathcal{D}) \propto p(\mathcal{D} | \theta)\ p(\theta | P_{\rm{s}}, \kappa_{\rm{s}}, \kappa_{\rm{WMB}})\ p(P_{\rm{s}})\, ,
-\end{equation}
-
-\noindent where $\kappa_{\rm{s}}$ and $\kappa_{\rm{WMB}}$ are the KDE functions for the standard and WMB models respectively, and $\theta$ here are parameters, $\theta = \{M, \teff, \ln(t), \feh, \ln(P)\}$.
-As done above for the asteroseismic model, the parameters $\theta$ may be referred to as latent parameters, as they form a step between the parameter we want to infer ($P_{\rm{s}}$) and our data.
-Using this approach allowed our model to properly take into account the observational uncertainties on the data.
-
-The second component on the right hand side of Equation \ref{eq:modelll} describes the probability of obtaining our latent parameters $\theta$ given our KDEs and the mixture model weighting parameter $P_{\rm s}$, and is described by the mixture model
-
-\begin{equation}\label{eq:mixturell}
-	p(\theta | P_{\rm{s}}, \kappa_{\rm{s}}, \kappa_{\rm{WMB}}) = P_{\rm s} \times \kappa_{\rm s}(\theta) + (1 - P_{\rm s}) \times \kappa_{\rm WMB}(\theta)\, ,
-\end{equation}
-
-\noindent where all parameters are as described above.
-This probability function describes a distribution that is a mixture of both KDEs.
-While the KDEs are constant, $P_{\rm s}$ is a free parameter, and so the shape of this distribution can vary.
-The latent parameters $\theta$ are drawn from this distribution, and therefore from some combination of the two stellar models.
-
-The first component in Equation \ref{eq:modelll} describes the likelihood of obtaining the parameters $\theta$ given our data and their observational uncertainty. It takes the form
-
-\begin{equation}
-	p(\mathcal{D} | \theta) = \mathcal{N}(\mathcal{D} | \theta, \sigma_{\mathcal{D}})\, ,
-\end{equation}
-
-\noindent a normal distribution evaluating the latent parameters $\theta$ against the observations, with observational uncertainty $\sigma_{\mathcal{D}}$.
-This approach means that in each parameter space (such as age), the age drawn from the stellar model mixture is entered into the likelihood equation with our static observations.
-The value of this equation (and thus the likelihood) will increase if $\theta$ is closer to the observations, and the mixture model will be modulated in a manner that maximises this probability, inferring whether one stellar model is more likely to produce our data than the other.
-
-The final term, $p(P_{\rm s})$, represents the prior on the mixture model weight, which is uniform between 0 and 1. A visual representation of our model is shown in Figure \ref{fig:pgm}.
-
-Typically, this model would evaluate all stars in our sample against the stellar models simultaneously for a single posterior estimate of $P_{\rm s}$.
-At 95 stars, in 5 parameter spaces, this totals 476 free parameters to marginalise over.
-This is not an issue for Hamiltonian Monte Carlo \cite[HMC]{betancourt+girolami2013}, however the use of KDE functions, over which a probabilistic gradient can not be measured, reduces HMCs effectiveness.
-Alternative Markov Chain Monte Carlo techniques \cite[MCMC]{foreman-mackey+2013} can more efficiently sample the KDE functions, but can not treat the large number of hierarchical parameters.
-To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $P_{\rm s}$, and multiplied these post hoc to obtain a combined posterior.
-This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications (see Section \ref{s:class}), at the expense of the ability to marginalise for a single value of $P_{\rm s}$ directly.
-
-\subsubsection{Fitting procedure}
-The parameter space of the stellar models was reduced before calculating the KDEs.
-These cuts were made in $M$, $\teff$, $\ln(t)$ and \feh, removing any stars in the models that fell more than $3 \times \sigma_{\mathcal{D}}$ outside the observations.
-Our observables $M$, $t$ and $P$ have asymmetric uncertainties from the Bayesian asteroseismic analysis.
-We used the larger of the reported uncertainties on each parameter as $\sigma_{\mathcal{D}}$ in each parameter space.
-
-KIC 6278762 was excluded from this stellar model analysis, because its age fell more than $3\sigma$ outside of the highest age in the stellar models\footnote{This is a metallicity issue, as the oldest stars have metallicities outside the range of the rotational model grids.}, and KICs 7106245 and 8760414 were excluded for the same reason due to low metallicities outside the functional range of the stellar models (-0.99 and -0.92 respectively).
-
-We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{foreman-mackey+2013}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.
-
-After fitting, we took a normalised histogram of the posterior estimate of $P_{\rm s}$ for each star, using 100 bins.
-In this histogram, each bin approximated the value of the posterior function for $P_{\rm s}$.
-The array of 100 bins for all stars were multiplied, resulting in an approximation of the joint posterior probability function for $P_{\rm s}$ given all stars in the ensemble.
-
-\section{Results}
-bla bla short shpiel about which values were included and which weren't
-
-\section{Verifying asteroseismic results}
-\subsection{Priors on rotational parameters}
-In our Bayesian analysis, we have placed weakly informative priors on our sampled rotational parameters, $\nu_{\rm s}\sin(i)$ and $\cos(i)$ (see Section \ref{s:seismo}).
-The prior is especially important for the angle of inclination, which is hardest to infer from the data.
-We are able to validate the robustness of our asteroseismic results by confirming that their posterior distributions are data-dominated, and not prior-dominated.
-We can do so by comparing the $68\%$ credible regions of the posterior estimates of $\nu_{\rm s}\sin(i)$ and $i$ against the $68\%$ credible regions of their priors.
-
-A comparison between prior and posterior is shown for 94 stars in $\nu_{\rm s}\sin(i)$, $i$ and $P_{\rm rot}$ in Figure \ref{fig:priors}, arranged by age.
-In the Figure, results with means and error bars that closely resemble the prior distribution can be interpreted as prior-dominated (i.e.
-poorly informed by the data).
-The projected splitting, $\nu_{\rm s}\sin(i)$, is overall well constrained, with only one star appearing prior dominated.
-This is expected, as the projected splitting is what we observe on the star before decoupling inclination and rotation.
-The angle of inclination $i$, sampled as $\cos(i)$, more closely follows the prior distribution in most cases.
-Combining the two, the rotation period $P_{\rm rot}$ has no stars directly corresponding to the effective prior on period, and globally follows a trend with increasing age.
-The three outliers with fast rotation at late ages (KICs 6603624, 8760414 and 8938364) are discussed in more detail in Section \ref{ssec:litcomp}.
-
-The rotation rates as presented in this work are a product of our Bayesian sampling of both projected splitting and angle of inclination.
-As seen in Figure \ref{fig:priors} there are instances where $i$ or $\nu_{\rm s}\sin(i)$ closely resemble the prior (and are therefore prior-dominated).
-There are no cases of this when looking at the resulting period measurements, as they will have been informed by at least one strongly data-driven parameter (judging from Figure \ref{fig:priors}, commonly $\nu_{\rm s}\sin(i)$).
-From this, we conclude that our ensemble of asteroseismic rotation is not strongly dominated by the priors imposed on projected splitting and inclination in our Bayesian analysis.
-
-\subsection{Comparisons to previous studies}\label{ssec:litcomp}
-In order to validate our results, we compared our rotational parameters to those obtained in the literature, as well as those resulting from the work presented in LEGACY and Kages, which were unreported and received through private communication by the authors of the catalogue papers.
-
-Comparisons with LEGACY and Kages are shown in Figure \ref{fig:legacykages} for projected splitting, inclination angle, and rotation period.
-In all three cases we show the fractional difference between the values obtained in this work and those from LEGACY and Kages.
-On the right of Figure \ref{fig:legacykages}, we show the distribution of the fractional differences for the three parameters.
-The projected splitting is in good agreement with both studies, however LEGACY finds slightly lower $\nu_{\rm s}\sin(i)$ for the faster rotators, deviating from our work by over $1\sigma$.
-Neither LEGACY nor Kages used a spatially isotropic prior for the inclination angle in their analyses, instead opting for a uniform prior.
-As posterior estimates of inclination angle are only loosely data-driven, the introduction of an isotropic prior should result in our analysis reporting globally higher inclination angles.
-This effect is seen in the comparisons of both inclination angles and rotation rates for the LEGACY stars, where we find overall lower rotation rates compared to LEGACY for stars at very similar $\nu_{\rm s}\sin(i)$.
-
-A number of stars are excluded from Figure \ref{fig:legacykages} and compared individually as extreme outliers: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have fast rotation rates ($<5\, \rm days$) in Kages, but are found to have a broader spread of rotation rates in this work.
-At similar values for $\nu_{\rm s}\sin(i)$, Kages found much lower inclination angles with highly asymmetrical uncertainties.
-Based on a comparison between the summary statistics of these stars, we conclude that the results found in this work have better marginalised over inclination angle, improving our measure of rotation.
-
-Conversely, KICs 6603624, 8760414 and 8938364 have extremely slow rotation periods in LEGACY, but extremely \textit{fast} ($<3\, \rm {days}$) in this work.
-KICs 8760414 and 8938364 are excluded from the gyrochronology analysis below based on checks for $\hat{R}$ and the number of effective samples.
-Both stars have ages greater than $10\, \rm Gyr$, making their fast rotation rates highly unlikely under any model of rotational evolution.
-The posterior estimate of $P$ for KIC 6603624 is well-defined in our analysis, but with an age of $7.8\, \rm Gyr$, its measured rotation of $1.2\, \rm days$ is also highly unlikely under any model of rotational evolution.
-The LEGACY estimate of rotation is similarly extreme at $378\, \rm days$.
-These three stars have the lowest inclination angles in our sample ($< 10^\circ$), at which point the power in the split components of the seismic modes is so low that it becomes difficult to probe the measure of splitting\footnote{The split components for these stars will have a height roughly 3\% of the central mode.
-For comparison, for the next lowest inclined star at $17^\circ$, this rises to $10\%$.}.
-In cases such as these with lower signal-to-noise, spurious peaks may be interpreted as split components.\\
 
@@
 
-We also compared our asteroseismic estimates of stellar rotation with similar studies in the literature, shown in Figure \ref{fig:literaturecomp}.
-These included: \cite{davies+2015}, a study of the binary solar analogues 16 Cyg A \& B; \cite{nielsen+2015}, which our catalogue shares 5 stars with; and \cite{benomar+2018}, an asteroseismic study of differential rotation with which our catalogue shares 40 targets.
-For the latter, we used their reported splitting value $a_1$, which is equivalent to $\nu_{\rm s}$.
-
-Overall, Figure \ref{fig:literaturecomp} shows no strong disagreements between our asteroseismic measurements for stellar rotation and those from the literature.
-The scatter of the fractional differences lies cleanly around the zero line, with a mean and spread of $0.0_{-15.6}^{+16.4}\, \%$.
-The increase in uncertainty with period is due to more slowly rotating stars being more difficult to constrain using asteroseismology.
-% The agreement within $1\sigma$ here is encouraging, indicating that these independent Bayesian analyses are finding appropriate uncertainties on these rotation measurements.
-
-It is of note that 16 Cyg A, as reported by \cite{davies+2015} was found to be rotating slightly faster in our analysis (deviating within $2\sigma$), despite the fit being performed on the same data.
-We found an inclination angle that is slightly lower than \cite{davies+2015} for 16 Cyg A but a similar projected splitting, which would explain finding a lower value of rotation.
-
-There are three outliers at low period in Figure \ref{fig:literaturecomp}: KICs 6603624, 8760414 and 8938364.
-These are the same targets found to be outliers in a comparison to the LEGACY and Kages measurements (see above), with anomalously fast rotation rates and low inclination angles.
-As these stars represent the lowest inclination angles in our sample, and were found to disagree with two independent studies, we opted to exclude them from the gyrochronology analysis, and to flag the rotation measurements for these three stars presented in this work.
-
 \begin{figure}
@@
 \end{figure}
-
-\subsection{Internal vs external rotation}
-Different methods of rotation measurement probe different regions of stars.
-Asteroseismology of main sequence stars probes internal rotation in the near surface layers, where the observed p modes are most sensitive \cite{lund+2014}.
-Measurements of star-spot modulation instead probe the rotation rates of star spots on the surface.
-A distinct difference between rotation rates obtained through these different techniques would hold information about differential rotation (both latitudinal and radial) of near-surface layers, such as those we observe in the Sun \cite{beck2000}.
-
-\cite{nielsen+2015} performed a comparative analysis of 5 Sun-like stars observed with \kepler for which both star-spot modulation and asteroseismic rotation could be measured.
-They found no statistically significant difference between the two techniques.
-
-Similarly, \cite{benomar+2015} performed an analysis on a larger sample of 22 stars.
-In this work they not only considered rotation rates from spots, but also spectroscopic measures of the projected surface rotation $\textrm{v}\sin(i)$, which they found to be more reliable.
-Comparisons with asteroseismic observations again showed no significant radial differential rotation.
-
-With our expanded sample of asteroseismic rotation we can perform a similar analysis, to both validate our sample and probe radial differential rotation.
-Figure \ref{fig:vsinilit} shows a comparison between spectroscopic $\textrm{v}\sin(i)$ measurements as listed in LEGACY and Kages (left) and \cite{benomar+2015} (right).
-In these cases the asteroseismic $\textrm{v}\sin(i)$ has been calculated using our measure of asteroseismic $\nu_s\sin(i)$ and the known asteroseismic radii.
-Three stars (KICs 6603624, 8760414 and 8938364) have been excluded from this figure due to strong disagreements of measured rotation rates with the literature (see Section \ref{ssec:litcomp} above).
-
-For the LEGACY and Kages sample, we find no strong deviation from the 1:1 line except at very low velocities, which is likely due to biases inherent to spectroscopic line broadening measurements \cite{doyle+2014, tayar+2015}.
-For the \cite{benomar+2015} sample stars lie a lot closer to the 1:1 line.
-% , apart from one clear outlier.
-While we find no statistically significant difference between these observations, more in-depth studies of stars furthest away from the bisector in this sample may prove valuable in future work.
-
-Overall, there appears to be a global offset where spectroscopic measurements of projected rotation appear faster than asteroseismic measures.
-Based on the LEGACY and Kages $v\sin(i)$ values, this offset is roughly $18\%$ (i.e.
-spectroscopic projected rotation rates are higher than asteroseismic rates).
-This offset is much smaller ($\sim5\%$) for the \cite{benomar+2015} sample, albeit for far fewer stars.
-These offsets are within the typical disagreement between spectroscopic methods, based on comparisons of projected rotation measurements for red giant stars \cite[see Figure 2]{tayar+2015}, especially at $< 5\, \rm{km\,s^{-1}}$.\\
 
@@
 
-We also repeated the \cite{nielsen+2015} comparison of asteroseismic rotation rates to surface rotation rates, using surface rotation measurements from \cite{nielsen+2013} and \cite{garcia+2014}.
-Figure \ref{fig:protlit} shows comparisons for 48 stars with rotation rates from both techniques, including 4 from the original \cite{nielsen+2015} sample.
-Rotation from spot-modulation are subject to measuring multiples of the true rotation rate, unlike an asteroseismic analysis \cite{mcquillan+2014}, and therefore some stars may appear at the 2:1 and 1:2 lines on the Figure.
-
-We repeated the analysis in \cite{nielsen+2015} by fitting a line of the form $P_{\rm surf} = m \times P_{\rm seis}$.
-For the purposes of this fit we used the larger of the asymmetrical uncertainties on the seismic rotation from this work.
-In order to avoid biasing the fit due to outliers, we only included stars below the 1.8:1 line.
-
-Our fit found a value of $m = 0.96\pm0.03$, showing a close agreement ($< 2\sigma$) between asteroseismic and surface rotation rates on a population level.
-Of the 40 stars that were part of this analysis, 21 had a median value of $P_{\rm s} < 0.5$ in the gyrochronology analysis.
-We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.
-As we find no statistically significant deviation, we conclude that our asteroseismic ensemble is in agreement with surface rotation measurements of these stars, and can therefore be used to draw inferences about gyrochronology.
-
-The overall agreement within the ensemble between the photometric measures of surface rotation and the asteroseismic rotation rates is in line with previous studies of Sun-like stars \cite{gizon+2013, chaplin+2013, nielsen+2015, benomar+2015}, where different measures of rotation appear indistinguishable.
-Individual deviations from this agreement, as appears to be the case for a number of stars that lie distinctly off the bisector, may warrant a more in-depth analysis, which we leave to future work.
-
-\subsection{Asteroseismic detection biases}
-
-\section{Verifying consequences for gyrochronology}
-\subsection{Rotational models for different stellar types}
-Of the 73 stars for which posterior probability distributions of $P_{\rm s}$ were obtained, 4 were potential sub-giants, 22 were `hot' stars, and 47 were main sequence stars.
-Different stellar types should hold different amounts of diagnostic information about the standard or WMB models.
-Our `hot' stars should hold little to no information, as they lie above the Kraft break, where traditional gyrochronology relations used to build the stellar models break down (specifically, they do not lose angular momentum with time).
-Similarly, the rotational evolution of sub-giant stars is dominated by envelope expansion, complicating the interpretation of rotation.
-
-Figure \ref{fig:modelresults} shows joint posterior distributions for $P_{\rm s}$ for the three different stellar types, as well as their cumulative distributions.
-Both the  4 sub-giant stars and the 22 `hot' stars marginally prefer the standard model.
-The 47 MS stars on the other hand were most strongly in favour of weakened magnetic braking and dominate the full joint posterior.
-When only considering these stars, $99.2\%$ of the joint probability fell below $P_{\rm{s}} = 0.5$, compared to $98.4\%$ for all 73 stars.
-
-\subsection{Limits of our stellar models}\label{ssec:limits}
-The models presented in \cite{vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$.
-Our sample of 91 stars contained 4 stars with metallicities below $-0.4\, \rm{dex}$, which are shown as shaded symbols in Figure \ref{fig:fullmodels}.
-Of these 4, 3 were included in our final sample of 73 stars used to evaluate our stellar models: KICs 7970740, 8684723 and KIC 9965715.
-All three are classed as MS stars, with metallicities of $-0.54 \pm 0.10$, $-0.42 \pm 0.10$ and $-0.44 \pm 0.18\, \rm {dex}$ respectively, placing them within $3\sigma$ of the metallicity limits of our stellar models.
-KICs 8684723 and 9965715 strongly agree with the WMB model, whereas KIC 7970740 weakly prefers the standard model.
-Excluding these stars was not found to significantly alter the joint posterior distribution shown in Figure \ref{fig:modelresults}.
-
-Recently, \cite{amard+matt2020} compared different rotational evolution models \cite[][of which we use the former in this work]{vansaders+pinsonneault2013,matt+2015} while studying the effect metallicity has on rotation.
-They found that metal-rich stars spin down significantly more effectively than metal poor stars.
-The population of 73 stars used in our stellar model comparisons is roughly centered on a $\rm{[Fe/H]}$ of 0 $\rm dex$, with a spread of $~0.16\, \rm dex$, with no stars significantly above or below $\pm 0.4\, \rm dex$ (as discussed above).
-While differences in stellar rotational evolution as a function of metallicity in this region are still somewhat pronounced, they are much less so than for more metal-rich or poor stars \cite[see Figure 2][]{amard+matt2020}.
-However, for stars with $\feh < 0$, the \cite{matt+2015} model prescription sees stars spin down more slowly than the models used in this work (i.e.
-they will rotate faster at later ages).
-This work only explores the presence of weakened magnetic braking for a single braking law, and a comparison to the \cite{matt+2015} braking model will be explored in a future paper.
-
-When constructing KDEs from our stellar model samples (see Section \ref{s:gyro}), we selected fixed resolutions (or band-widths) for the KDEs.
-In mass, the band-width of $0.02\, M_\odot$, was larger than the uncertainties of 24 of 73 stars used to construct our joint posterior.
-For the stars with the smallest uncertainties, this significantly limits the size of the KDE being evaluated (as subsections of the full stellar models are used to evaluate individual stars, for computational efficiency).
-In order to confirm that these stars do not significantly affect the ensemble's preference towards the WMB model, we recalculated the joint posterior distribution for $P_{\rm s}$, excluding stars with an uncertainty on mass smaller than the KDE band-width.
-While the 24 stars with small uncertainties do favour the WMB model, they do so very weakly, whereas the remaining 49 stars with larger uncertainties strongly favour the WMB model.
-Their removal from the total joint posterior probability does not significantly alter it from the distribution shown in Figure \ref{fig:modelresults}.
-
-\subsection{Systematic uncertainties from asteroseismology}
-In our model analysis, we used asteroseismic mass and age obtained using \texttt{BASTA}, as reported in LEGACY and Kages.
-Asteroseismic properties obtained through stellar models can be subject to systematic errors arising from differences in input physics and choice of stellar models not included in the reported statistical uncertainties.
-A quantification of these different systematic effects can be found in Section 4 of \cite{silvaaguirre+2015}, based on the Kages catalogue.
-Combining their reported median systematic uncertainties due to input physics results in median uncertainties of $20\%$ (up from $14\%)$ on age and $5\%$ (up from $3\%$) on mass for the Kages sample.
-For LEGACY, the median uncertainties are $18\%$ (up from $10\%)$ and $5.6\%$ (up from $4\%$) for age and mass respectively.
-
-In order to check the effect of systematic seismic uncertainties on our results for gyrochronology, we re-ran our model analysis described in Section \ref{s:gyro} after inflating uncertainties on mass and age.
-We increased uncertainties by the fractional difference between the \texttt{BASTA} statistical uncertainties and the median full statistical and systematic uncertainties described above.
-For example, a LEGACY star with a mass of $2.0 \pm 0.5\, M_\odot$ would have its uncertainty inflated by $1.6\%$ of its mass, to $0.53\, M_\odot$.
-
-The results we found by repeating our model analysis with inflated uncertainties on asteroseismic mass and age closely replicated those found in our initial analysis.
-Specifically: subgiants preferred the standard model, and MS stars strongly favoured the WMB model.
-The `hot' stars in this case slightly preferred the WMB model compared to the unaltered ensemble.
-The full joint posterior distribution for 73 stars still strongly favours of the WMB model even with the inflated uncertainties, including when considering only stars on the main sequence, when excluding stars outside the models' metallicity range, and when excluding stars with low uncertainties on mass (see Section \ref{ssec:limits}).
-
-To further test the limits of this analysis, we reran our mixture model fit, this time only shifting the asteroseismic ages younger by the systematic uncertainty, and retaining the statistical uncertainty (i.e.
-the ages of LEGACY and Kages stars were reduced by $8\%$ and $6\%$ respectively).
-In this scenario where all asteroseismic ages are overestimated, `true' fast rotators at young ages would have been mistaken for fast rotators at old ages, suggesting the presence of weakened magnetic braking where none existed.
-Despite the shift in age, the results from this mixture model fit closely matched those found for the unaltered ensemble, finding $95.8\%$ of the total posterior probability to lie below $P_{\rm s} = 0.5$ (as opposed to $98.4\%$ for the unaltered ensemble).
-While the preference for the WMB model is slightly reduced, we conclude that the use of asteroseismic age is valid for the gyrochronology analyses presented in this work.
-
-\subsection{Binaries and Planet Hosts}
-For stars to be good probes of existing gyrochronology relations, their rotational evolution must occur in isolation.
-If a star interacts with a close binary companion (through tides, or a merger) the natural angular momentum loss can be disturbed, causing gyrochronology to mispredict ages \cite{leiner+2019, fleming+2019}.
-Between LEGACY and Kages, we have 8 known binaries.
-
-First, KIC 8379927, KIC 7510397, KIC 10454113 and KIC 9025370 are spectroscopic binaries.
-This does not affect the asteroseismic analysis, but may affect their rotational evolution.
-Of these, KICs 8379927, 7510397 and 9025370 were included in the gyrochronology analysis.
-None of them preferred one model strongly over the other, with all three finding flat posteriors for $P_{\rm s}$.
-% This implies that they are not yet at the Rossby number where weakened magnetic braking is proposed to take place in the models used in this work.
-
-Second, the binary pairs of KIC 9139151 \& 9139163 and 16 Cyg A \& B are individually observed binary components with wide orbital separations, so we do not expect their binarity to have affected their rotational evolution.
-
-While we chose not to account for star-planet tidal interactions in this work, we note that this may also disturb the natural stellar rotational evolution when tidal forces are at play \cite{maxted+2015,gallet+delorme2019, benbakoura+2019}, although this has been disputed by observations of asteroseismic planet hosts \cite{ceillier+2016}.\\
-
-\subsection{Evidence for Weakened Magnetic Braking in the literature}
-Weakened magnetic braking was first proposed by \cite{vansaders+2016}, in response to stars with spot rotation rates faster than expected from gyrochronology at their asteroseismic ages.
-This discrepancy was also indicated at around the same time in other studies of asteroseismic ages of main sequence stars \cite{nielsen+2015, angus+2015, davies+2015}.
-The theory of weakened magnetic braking has been both reinforced by recent studies \cite{metcalfe+egeland2019}, as well as disputed \cite{lorenzo-oliveira+2019}, at least at the critical Rossby number originally proposed.
-
-As a sanity check that the evidence in favour of weakened magnetic braking presented in this work is independently robust, we recreated the joint posterior probability for $P_{\rm s}$, this time looking only at MS stars, and excluding any of the 22 stars that were included in the original \cite{vansaders+2016} sample.
-Of the 47 MS stars used to distinguish between stellar models, 16 were included in the \cite{vansaders+2016} sample.
-Both the 16 \cite{vansaders+2016} stars as well as the remaining MS stars favoured the WMB model, although the \cite{vansaders+2016} stars did so more strongly, not including any stars that favoured the standard model.
-Specifically, when considering only the \cite{vansaders+2016} stars, $96.3\%$ of the total joint probability lay below $P_{\rm s} = 0.5$, compared to $91.7\%$ when considering only those stars \emph{not} included in the \cite{vansaders+2016} study.
-The stars initially used to propose the WMB model are still those most strongly in favour of it even when using asteroseismic rotation rates only.
-% It is encouraging that the inclusion of older, more quiescent stars and the use of asteroseismic rotation rates finds the same conclusion.}
-
-Finally, we comment on the results found by \cite{lorenzo-oliveira+2019}.
-Using spectroscopic rotation measurements of 14 solar twins, compared to grids of stellar models, they found marginal evidence favouring a standard rotational evolution.
-If weakened magnetic braking were to take place, it would most likely be outside the range of their sample, at $Ro_{\rm {crit}} \geq 2.29$, compared to the value of $1.97$ used in this work.
-Our sample does not overlap with theirs, so we can not directly compare to their results.
-However, our work does find statistical agreement between our asteroseismic rotation rates and ages, and a model of weakened magnetic braking at a critical Rossby number of $1.97$.
-While a comparison to models of different Rossby numbers is outside the scope of this study, the LEGACY and Kages rotation sample may facilitate such studies in the future.
+%\input{tabulate.tex}

### 2020-09-29 paper/natastron/methods.tex
Done with the main body pretty much

@@
 
-For our sample, we used the asteroseismic ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{silvaaguirre+2015} in the Kages and LEGACY catalogues.
+For our asteroseismic ages, we used the ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{silvaaguirre+2015} in the Kages and LEGACY catalogues.
 These ages have been obtained by comparisons of measured oscillation properties to stellar models, accounting for an expanded range of metallicities.
@@
 While uncertainties found through \texttt{BASTA} are typically higher than for other techniques, only \texttt{BASTA} and \texttt{ASTFIT} \cite[Aarhus STellar Evolution Code]{christensen-dalsgaard2008} recover the radius, mass and age of the Sun, when applied to solar data.
-Although the uncertainties on \texttt{ASTFIT} ages are overall lower, they are not reported in \cite{silvaaguirre+2015} for the Kages sample.
+Although the uncertainties on \texttt{ASTFIT} ages are overall lower, they are not published for the Kages sample.
 In order to maintain an internally consistent stellar age sample, we used age results from \texttt{BASTA} for both the Kages and LEGACY samples.
@@
 We note that age and mass posteriors from \texttt{BASTA} are correlated, but chose not to account for the unpublished correlations in this work.
+
 As described in the catalogue papers, for Kages stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy reported in \cite{huber+2013a}.
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=.99\textwidth]{Images/modelfit.pdf}
-	\caption{A power spectrum constructed from four years of \kepler observations of 16 Cyg A (KIC 12069424).
-Plotted over the top is the model resulting from the fit to the data described in this work.
-The model implements both the mode frequencies, seen on the right hand side of the plot, and the convective background, the effects of which are seen on the left.
-Low frequencies have been cropped out for clarity.
-\textit{Inset}: A zoom in on a radial (right) and quadrupole (left) ($\ell = 0, 2$) pair of modes.
-The quadrupole mode is split into five components by the star's rotation.
-Due to the star's inclination angle with respect to us, two out of five peaks are more distinct.
-The height and spacing of the mode components is a function of the star's rotational splitting ($0.56\, \mu\rm{Hz}$, equivalent to $P_{\rm rot} = 20.5\, \rm{days}$) and angle of inclination ($45^\circ$).}
-	\label{fig:modelfit}
-\end{figure*}
+Other asteroseismic properties used in this study, such as those used as first guesses on the free parameters in our asteroseismic model, are taken from the Kages and LEGACY catalogues \cite{astropycollaboration+2013, astropycollaboration+2018, ginsburg+2019}.
+In cases where both catalogues contained the same target, we used the stellar parameters reported in LEGACY.
+This is also the case for the masses and ages described above.
+
+\subsection{Mode Frequency Fitting}
+
+Todo: water down the contents of the methods here.
 
@@
 In the weakened magnetic braking model, $Ro_{\rm crit} = 1.97$.
-For further details, see \cite{vansaders+pinsonneault2013} and \cite{vansaders+2016, vansaders+2019}.
+For further details, see \cite{vansaders+pinsonneault2013} and \cite{vansaders+2016, vansaders+2019} for the standard and weakened magnetic braking cases respectively.
 
-Instead of comparing asteroseismic measurements of age and rotation directly to rotational models of individual stars, we instead compared them to synthetic populations based on rotational models, similar to those presented in \cite{vansaders+2019}, with some adaptations.
 To construct a synthetic population of rotating stars, \cite{vansaders+2019} applied the rotational braking laws described above to a galactic population model.
@@
 
-We used the same approach here, with two changes.
-First, we updated the distribution of stellar parameters matched to the TRILEGAL populations.
-Instead of \cite{mathur+2017}, we used the \cite{berger+2020} temperatures and luminosities, and 2MASS $K$-band magnitudes as our stellar parameter distributions for the \kepler field, which are more accurate following the use of \gaia DR2 parallaxes \cite{gaiacollaboration+2018}.
-The TRILEGAL simulation was matched to the \cite{berger+2020} sample using a nearest-neighbours approach (as opposed to binning), based on the density of stars on the HR diagram.
+To construct a synthetic population of rotating stars, we expanded upon previous forward-models of the \textit{Kepler} field with the purpose of studying weakened magnetic braking \cite{vansaders+2019}, with some important improvements.
+We started with a TRILEGAL \cite{girardi+2012} Milky-Way simulation of the \kepler field, using the simulation's standard population values intended for this purpose.
+In order to replicate the \kepler selection effect, the TRILEGAL simulation was matched to the largest current catalogue of temperatures, luminosities and 2MASS $K$-band magnitudes of stars in the \kepler field \cite{berger+2020}.
+This was done using a nearest-neighbours approach, based on the density of stars on the HR diagram.
+This ensured that the TRILEGAL population matched the density of stars actually observed by \kepler, replicating its selection effects.
 
-Second, we made further changes to account for possible binarity in the the \cite{berger+2020} sample.
+We made further changes to account for possible binarity in the the matching sample \cite{berger+2020}.
 If the first step is performed blindly, blended binaries in the sample cause an overestimation of the number of old stars.
@@
 \begin{enumerate}
-	\item blended the TRILEGAL stars with binary companions drawn from a flat mass-ratio distribution, using the binary fraction of \cite{raghavan+2010},
+	\item blended the TRILEGAL stars with binary companions drawn from a flat mass-ratio distribution, using a known binary fraction \cite{raghavan+2010},
 	\item recalculated the `observed' luminosities and magnitudes assuming that each binary pair was blended, and
@@
 Both the standard and WMB models contain stars with the same fundamental parameters (mass, radius, effective temperature, metallicity) but a different period based on the choice of rotational evolution prescription.
-Applying an asteroseismic selection function that depends on these fundamental parameters \cite{chaplin+2011} would apply an identical prior to both models, therefore providing no net effect on our posterior distribution.
-Additionally, we expected any seismic selection function to be relatively flat (and therefore uninformative) on a star-by-star scale, on which we run our model analysis (as opposed to a population scale, see below).
+Applying an asteroseismic selection function that depends on these fundamental parameters would apply an identical prior to both models, therefore providing no net effect on our posterior distribution \cite{chaplin+2011}.
+Additionally, we expected any seismic selection function to be relatively flat (and therefore uninformative) on a star-by-star scale, on which we run our model analysis.
 
@@
 This approach translates the population models to a probability distribution we can use in a Bayesian framework.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.45\textwidth]{pgm_models.pdf}
-	\caption{A probabilistic graphical model (PGM) represented algebraically in Equation \ref{eq:modelll}.
-The shaded circle indicates observed data, and solid black points represent other fixed information, such as the KDEs and observational uncertainties.
-The remaining circles represent parameters.
-The underline indicates that the symbol represents a set of parameters or data.
-Here, $\kappa_{\rm{s}}$ and $\kappa_{\rm WMB}$ represent the KDEs of standard and WMB model populations respectively.
-$P_{\rm{s}}$ is the mixture model weighting factor.
-The latent parameters $\underline{\theta}$, our observations $\underline{\mathcal{D}}$ and their uncertainties $\underline{\sigma_{\mathcal{D}}}$ include temperature (\teff), mass ($M$), log-age ($\ln(t)$), metallicity (\feh) and log-rotation ($\ln(P)$).
-This model is \textit{hierarchical}, as all the latent parameters are drawn from the common probability distribution set by $P_{\rm{s}}$ and described in Equation \ref{eq:mixturell}.}
-	\label{fig:pgm}
-\end{figure}
 
@@
 To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $P_{\rm s}$, and multiplied these post hoc to obtain a combined posterior.
-This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications (see Section \ref{s:class}), at the expense of the ability to marginalise for a single value of $P_{\rm s}$ directly.
+This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications, at the expense of the ability to marginalise for a single value of $P_{\rm s}$ directly.
 
 \subsubsection{Fitting procedure}
-The parameter space of the stellar models was reduced before calculating the KDEs.
+The parameter space of the stellar models populations were reduced before calculating the KDEs.
 These cuts were made in $M$, $\teff$, $\ln(t)$ and \feh, removing any stars in the models that fell more than $3 \times \sigma_{\mathcal{D}}$ outside the observations.
@@
 
-We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{foreman-mackey+2013}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.
+We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{foreman-mackey+2013, foreman-mackey2016}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.
 
@@
 \subsection{Priors on rotational parameters}
-In our Bayesian analysis, we have placed weakly informative priors on our sampled rotational parameters, $\nu_{\rm s}\sin(i)$ and $\cos(i)$ (see Section \ref{s:seismo}).
+In our Bayesian analysis, we have placed weakly informative priors on our sampled rotational parameters, $\nu_{\rm s}\sin(i)$ and $\cos(i)$.
 The prior is especially important for the angle of inclination, which is hardest to infer from the data.
@@
 Combining the two, the rotation period $P_{\rm rot}$ has no stars directly corresponding to the effective prior on period, and globally follows a trend with increasing age.
-The three outliers with fast rotation at late ages (KICs 6603624, 8760414 and 8938364) are discussed in more detail in Section \ref{ssec:litcomp}.
-
+The three outliers with fast rotation at late ages (KICs 6603624, 8760414 and 8938364) are discussed in more detail in below.
+ blow
 The rotation rates as presented in this work are a product of our Bayesian sampling of both projected splitting and angle of inclination.
@@
 The LEGACY estimate of rotation is similarly extreme at $378\, \rm days$.
-These three stars have the lowest inclination angles in our sample ($< 10^\circ$), at which point the power in the split components of the seismic modes is so low that it becomes difficult to probe the measure of splitting\footnote{The split components for these stars will have a height roughly 3\% of the central mode.
-For comparison, for the next lowest inclined star at $17^\circ$, this rises to $10\%$.}.
+These three stars have the lowest inclination angles in our sample ($< 10^\circ$), at which point the power in the split components of the seismic modes is so low that it becomes difficult to probe the measure of splitting.
+The split components for these stars will have a height roughly 3\% of the central mode.
+For comparison, for the next lowest inclined star at $17^\circ$, this rises to $10\%$.
 In cases such as these with lower signal-to-noise, spurious peaks may be interpreted as split components.\\
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{Images/litcomp_alt2.pdf}
-	\caption{Comparisons between posterior estimates of rotational parameters from this work, LEGACY and Kages \cite[private communication]{davies+2016, lund+2017}.
-Fractional differences are plotted against stellar rotation obtained in this work.
-The $\Delta$ indicates the fractional difference betwen thsi work and the literature (i.e.
-stars above the zero-line have higher values in this work).
-The right hand panels the distribution of the fractional differences around the zero line.
-The colour legend is consistent throughout all panels.
-The x-axis units on the right hand panels are equivalent to the y-axis of the left hand panels.
-10 stars have been omitted from this plot and are discussed in more detail in the text: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have extremely low rotation periods in Kages, with high uncertainties.
-Conversely, KICs 6603624, 8760414 and 8938364 have extremely high rotation periods in LEGACY with low uncertainties.
-In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
-	\label{fig:legacykages}
-\end{figure*}
-
 We also compared our asteroseismic estimates of stellar rotation with similar studies in the literature, shown in Figure \ref{fig:literaturecomp}.
-These included: \cite{davies+2015}, a study of the binary solar analogues 16 Cyg A \& B; \cite{nielsen+2015}, which our catalogue shares 5 stars with; and \cite{benomar+2018}, an asteroseismic study of differential rotation with which our catalogue shares 40 targets.
+These included: a study of the binary solar analogues 16 Cyg A \& B \cite{davies+2015}, ; a study of surface and seismic rotation which our catalogue shares 5 stars with \cite{nielsen+2015}, ; and an asteroseismic study of differential rotation with which our catalogue shares 40 targets \cite{benomar+2018}.
 For the latter, we used their reported splitting value $a_1$, which is equivalent to $\nu_{\rm s}$.
@@
 
-It is of note that 16 Cyg A, as reported by \cite{davies+2015} was found to be rotating slightly faster in our analysis (deviating within $2\sigma$), despite the fit being performed on the same data.
-We found an inclination angle that is slightly lower than \cite{davies+2015} for 16 Cyg A but a similar projected splitting, which would explain finding a lower value of rotation.
+It is of note that 16 Cyg A was found to be rotating slightly faster in our analysis compared to the literature \cite{davies+2015} (deviating within $2\sigma$), despite the fit being performed on the same data.
+We found an inclination angle that is slightly lower for 16 Cyg A but at a similar projected splitting, which would explain finding a lower value of rotation.
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.49\textwidth]{Images/seis_comparison_rot_alt2.pdf}
-	\caption{Fractional differences between posterior estimates of asteroseismic rotation period from this work.
-Literature sources are: \cite{davies+2015} (16 Cyg A \& B), \cite{nielsen+2015} (5 stars) and \cite{benomar+2018} (40 stars).
-We used the reported parameter $a_{1}$ from \cite{benomar+2018}, which represents the rotational splitting in the case of uniform latitudinal rotation in their model.
-The dashed line represents the median of the sample shown, with the dotted lines representing the $15.9^{\rm{th}}$ and $84.1^{\rm{st}}$ percentiles.
-In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
-	\label{fig:literaturecomp}
-\end{figure}
-
-\subsection{Internal vs external rotation}
+\subsection{Seismic vs spectroscopic rotation}
 Different methods of rotation measurement probe different regions of stars.
@@
 
-\cite{nielsen+2015} performed a comparative analysis of 5 Sun-like stars observed with \kepler for which both star-spot modulation and asteroseismic rotation could be measured.
-They found no statistically significant difference between the two techniques.
-
-Similarly, \cite{benomar+2015} performed an analysis on a larger sample of 22 stars.
+A previous comparison of spectroscopic and seismic rotation rates, performed on a sample of 22 stars, found no significant radial differential rotation.
 In this work they not only considered rotation rates from spots, but also spectroscopic measures of the projected surface rotation $\textrm{v}\sin(i)$, which they found to be more reliable.
-Comparisons with asteroseismic observations again showed no significant radial differential rotation.
 
@@
 In these cases the asteroseismic $\textrm{v}\sin(i)$ has been calculated using our measure of asteroseismic $\nu_s\sin(i)$ and the known asteroseismic radii.
-Three stars (KICs 6603624, 8760414 and 8938364) have been excluded from this figure due to strong disagreements of measured rotation rates with the literature (see Section \ref{ssec:litcomp} above).
+Three stars (KICs 6603624, 8760414 and 8938364) have been excluded from this figure due to strong disagreements of measured rotation rates with the literature (see above).
 
@@
 For the \cite{benomar+2015} sample stars lie a lot closer to the 1:1 line.
-% , apart from one clear outlier.
-While we find no statistically significant difference between these observations, more in-depth studies of stars furthest away from the bisector in this sample may prove valuable in future work.
 
@@
 This offset is much smaller ($\sim5\%$) for the \cite{benomar+2015} sample, albeit for far fewer stars.
-These offsets are within the typical disagreement between spectroscopic methods, based on comparisons of projected rotation measurements for red giant stars \cite[see Figure 2]{tayar+2015}, especially at $< 5\, \rm{km\,s^{-1}}$.\\
+These offsets are within the typical disagreement between spectroscopic methods, based on comparisons of projected rotation measurements for red giant stars \cite[see Figure 2]{tayar+2015}, especially at $< 5\, \rm{km\,s^{-1}}$.
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{Images/vsini-comparison.pdf}
-	\caption{Comparisons between asteroseismic and spectroscopic measures of projected surface rotation, $\textrm{v}\sin(i)$.
-All asteroseismic (x-axis) values are from this work, all spectroscopic (y-axis) values are from the literature.
-\textit{Left}: comparisons to 81 stars values reported in LEGACY and Kages.
-\textit{Right}: comparisons to 16 stars observed by \cite{benomar+2015}.
-Asteroseismic values are transformed from projected splitting ($\nu_s\sin(i)$) using the asteroseismic radius measurements presented in LEGACY and Kages.
-The solid lines indicate the 1:1 line, while the dash-dotted lines represent the 2:1 and 1:2 lines.}
-	\label{fig:vsinilit}
-\end{figure*}
-
-We also repeated the \cite{nielsen+2015} comparison of asteroseismic rotation rates to surface rotation rates, using surface rotation measurements from \cite{nielsen+2013} and \cite{garcia+2014}.
-Figure \ref{fig:protlit} shows comparisons for 48 stars with rotation rates from both techniques, including 4 from the original \cite{nielsen+2015} sample.
-Rotation from spot-modulation are subject to measuring multiples of the true rotation rate, unlike an asteroseismic analysis \cite{mcquillan+2014}, and therefore some stars may appear at the 2:1 and 1:2 lines on the Figure.
-
-We repeated the analysis in \cite{nielsen+2015} by fitting a line of the form $P_{\rm surf} = m \times P_{\rm seis}$.
-For the purposes of this fit we used the larger of the asymmetrical uncertainties on the seismic rotation from this work.
-In order to avoid biasing the fit due to outliers, we only included stars below the 1.8:1 line.
-
-Our fit found a value of $m = 0.96\pm0.03$, showing a close agreement ($< 2\sigma$) between asteroseismic and surface rotation rates on a population level.
-Of the 40 stars that were part of this analysis, 21 had a median value of $P_{\rm s} < 0.5$ in the gyrochronology analysis.
-We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.
-As we find no statistically significant deviation, we conclude that our asteroseismic ensemble is in agreement with surface rotation measurements of these stars, and can therefore be used to draw inferences about gyrochronology.
-
-The overall agreement within the ensemble between the photometric measures of surface rotation and the asteroseismic rotation rates is in line with previous studies of Sun-like stars \cite{gizon+2013, chaplin+2013, nielsen+2015, benomar+2015}, where different measures of rotation appear indistinguishable.
-Individual deviations from this agreement, as appears to be the case for a number of stars that lie distinctly off the bisector, may warrant a more in-depth analysis, which we leave to future work.
+It is worth addressing the impact this comparison would have on our conclusions for gyrochronology, were we to take the spectroscopic rotation rates as if they were the truth, even at velocities of $< 5\, \rm{km\,s^{-1}}$.
+For the majority of cases, the seismic velocities are slower than the spectroscopic velocities, which would bias our ensemble towards favouring a standard evolution over a weakened magnetic braking scenario (as stars would overall appear to be rotating slower at late ages).
+Based on the comparison to spot rotation presented in the main body of this paper, and given known issues comparing seismic and spectroscopic rotation at low velocities, we conclude that the divergence seen in Figure \ref{fig:vsinilit} does not undermine our results.
 
@@
 
+Do this
+
 \section{Verifying consequences for gyrochronology}
-\subsection{Rotational models for different stellar types}
-Of the 73 stars for which posterior probability distributions of $P_{\rm s}$ were obtained, 4 were potential sub-giants, 22 were `hot' stars, and 47 were main sequence stars.
-Different stellar types should hold different amounts of diagnostic information about the standard or WMB models.
-Our `hot' stars should hold little to no information, as they lie above the Kraft break, where traditional gyrochronology relations used to build the stellar models break down (specifically, they do not lose angular momentum with time).
-Similarly, the rotational evolution of sub-giant stars is dominated by envelope expansion, complicating the interpretation of rotation.
-
-Figure \ref{fig:modelresults} shows joint posterior distributions for $P_{\rm s}$ for the three different stellar types, as well as their cumulative distributions.
-Both the  4 sub-giant stars and the 22 `hot' stars marginally prefer the standard model.
-The 47 MS stars on the other hand were most strongly in favour of weakened magnetic braking and dominate the full joint posterior.
-When only considering these stars, $99.2\%$ of the joint probability fell below $P_{\rm{s}} = 0.5$, compared to $98.4\%$ for all 73 stars.
-
 \subsection{Limits of our stellar models}\label{ssec:limits}
@@
 For example, a LEGACY star with a mass of $2.0 \pm 0.5\, M_\odot$ would have its uncertainty inflated by $1.6\%$ of its mass, to $0.53\, M_\odot$.
-
-The results we found by repeating our model analysis with inflated uncertainties on asteroseismic mass and age closely replicated those found in our initial analysis.
-Specifically: subgiants preferred the standard model, and MS stars strongly favoured the WMB model.
-The `hot' stars in this case slightly preferred the WMB model compared to the unaltered ensemble.
-The full joint posterior distribution for 73 stars still strongly favours of the WMB model even with the inflated uncertainties, including when considering only stars on the main sequence, when excluding stars outside the models' metallicity range, and when excluding stars with low uncertainties on mass (see Section \ref{ssec:limits}).
+The resulting joint posterior distribution for 73 stars still strongly favoured of the WMB model even with the inflated uncertainties, including when considering only stars on the main sequence, when excluding stars outside the models' metallicity range, and when excluding stars with low uncertainties on mass.
 
@@
 Despite the shift in age, the results from this mixture model fit closely matched those found for the unaltered ensemble, finding $95.8\%$ of the total posterior probability to lie below $P_{\rm s} = 0.5$ (as opposed to $98.4\%$ for the unaltered ensemble).
-While the preference for the WMB model is slightly reduced, we conclude that the use of asteroseismic age is valid for the gyrochronology analyses presented in this work.
 
@@
 None of them preferred one model strongly over the other, with all three finding flat posteriors for $P_{\rm s}$.
-% This implies that they are not yet at the Rossby number where weakened magnetic braking is proposed to take place in the models used in this work.
 
@@
 While we chose not to account for star-planet tidal interactions in this work, we note that this may also disturb the natural stellar rotational evolution when tidal forces are at play \cite{maxted+2015,gallet+delorme2019, benbakoura+2019}, although this has been disputed by observations of asteroseismic planet hosts \cite{ceillier+2016}.\\
-
-\subsection{Evidence for Weakened Magnetic Braking in the literature}
-Weakened magnetic braking was first proposed by \cite{vansaders+2016}, in response to stars with spot rotation rates faster than expected from gyrochronology at their asteroseismic ages.
-This discrepancy was also indicated at around the same time in other studies of asteroseismic ages of main sequence stars \cite{nielsen+2015, angus+2015, davies+2015}.
-The theory of weakened magnetic braking has been both reinforced by recent studies \cite{metcalfe+egeland2019}, as well as disputed \cite{lorenzo-oliveira+2019}, at least at the critical Rossby number originally proposed.
-
-As a sanity check that the evidence in favour of weakened magnetic braking presented in this work is independently robust, we recreated the joint posterior probability for $P_{\rm s}$, this time looking only at MS stars, and excluding any of the 22 stars that were included in the original \cite{vansaders+2016} sample.
-Of the 47 MS stars used to distinguish between stellar models, 16 were included in the \cite{vansaders+2016} sample.
-Both the 16 \cite{vansaders+2016} stars as well as the remaining MS stars favoured the WMB model, although the \cite{vansaders+2016} stars did so more strongly, not including any stars that favoured the standard model.
-Specifically, when considering only the \cite{vansaders+2016} stars, $96.3\%$ of the total joint probability lay below $P_{\rm s} = 0.5$, compared to $91.7\%$ when considering only those stars \emph{not} included in the \cite{vansaders+2016} study.
-The stars initially used to propose the WMB model are still those most strongly in favour of it even when using asteroseismic rotation rates only.
-% It is encouraging that the inclusion of older, more quiescent stars and the use of asteroseismic rotation rates finds the same conclusion.}
-
-Finally, we comment on the results found by \cite{lorenzo-oliveira+2019}.
-Using spectroscopic rotation measurements of 14 solar twins, compared to grids of stellar models, they found marginal evidence favouring a standard rotational evolution.
-If weakened magnetic braking were to take place, it would most likely be outside the range of their sample, at $Ro_{\rm {crit}} \geq 2.29$, compared to the value of $1.97$ used in this work.
-Our sample does not overlap with theirs, so we can not directly compare to their results.
-However, our work does find statistical agreement between our asteroseismic rotation rates and ages, and a model of weakened magnetic braking at a critical Rossby number of $1.97$.
-While a comparison to models of different Rossby numbers is outside the scope of this study, the LEGACY and Kages rotation sample may facilitate such studies in the future.

### 2020-09-30 paper/natastron/methods.tex
Almost done with methods

@@
 
-For our asteroseismic ages, we used the ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{silvaaguirre+2015} in the Kages and LEGACY catalogues.
+For our asteroseismic ages, we used the ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{silvaaguirre+2015} in the `Kages' and LEGACY catalogues.
 These ages have been obtained by comparisons of measured oscillation properties to stellar models, accounting for an expanded range of metallicities.
@@
 While uncertainties found through \texttt{BASTA} are typically higher than for other techniques, only \texttt{BASTA} and \texttt{ASTFIT} \cite[Aarhus STellar Evolution Code]{christensen-dalsgaard2008} recover the radius, mass and age of the Sun, when applied to solar data.
-Although the uncertainties on \texttt{ASTFIT} ages are overall lower, they are not published for the Kages sample.
-In order to maintain an internally consistent stellar age sample, we used age results from \texttt{BASTA} for both the Kages and LEGACY samples.
+Although the uncertainties on \texttt{ASTFIT} ages are overall lower, they are not published for the `Kages' sample.
+In order to maintain an internally consistent stellar age sample, we used age results from \texttt{BASTA} for both the `Kages' and LEGACY samples.
 
-For our stellar masses we used asteroseismic model masses obtained by \texttt{BASTA} reported in Kages and LEGACY, in order to maintain internal consistency with the age measurements.
+For our stellar masses we used asteroseismic model masses obtained by \texttt{BASTA} reported in `Kages' and LEGACY, in order to maintain internal consistency with the age measurements.
 We note that age and mass posteriors from \texttt{BASTA} are correlated, but chose not to account for the unpublished correlations in this work.
 
-As described in the catalogue papers, for Kages stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy reported in \cite{huber+2013a}.
+As described in the catalogue papers, for `Kages' stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy reported in \cite{huber+2013a}.
 For LEGACY stars, atmospheric properties were similarly taken from \cite{buchhave+latham2015} for most stars in the catalogue, and complemented by other values from the literature for the remaining stars \cite[see Table 3]{silvaaguirre+2017}.
 
-Other asteroseismic properties used in this study, such as those used as first guesses on the free parameters in our asteroseismic model, are taken from the Kages and LEGACY catalogues \cite{astropycollaboration+2013, astropycollaboration+2018, ginsburg+2019}.
-In cases where both catalogues contained the same target, we used the stellar parameters reported in LEGACY.
+Other asteroseismic properties used in this study, such as those used as first guesses on the free parameters in our asteroseismic model, were taken from the `Kages' and LEGACY catalogues \cite{astropycollaboration+2013, astropycollaboration+2018, ginsburg+2019}.
+In cases where both catalogues contained the same target, we used the stellar parameters reported in LEGACY \cite{mckinney2010}.
 This is also the case for the masses and ages described above.
@@
 Todo: water down the contents of the methods here.
+
+From our asteroseismic analysis, we report inclination angle, rotational splitting, and rotation period in \textbf{Extended Data} Table 1.
+The summary statistics on these parameters were taken as the median of the posterior distribution, with uncertainties being the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles.
+For inclination angle ($i = \arccos(\cos(i))$) and rotation ($P = 1/\nu_{\rm s}$, the full posterior samples were transformed before taking the summary statistics, as our model sampled in $\cos(i)$ and $\nu_{\rm s}$.
+
+We flagged any sub-optimal conditions of the final fit.
+Of 94 stars, we flagged 5 for which the Gelman-Rubin convergence metric, $\hat{R}$, was greater than 1.01 and 2 stars for which it was greater than 1.1 on inclination angle or rotation, where a $\hat{R} = 1$ indicates a converged result \cite{gelman+rubin1992}.
+We also performed visual checks of the sampled chains on all hyperparameters and of the best-fit model compared to both the raw and smoothed asteroseismic data.
+We found no issues in the visual investigation of the 94 stars.
+KIC 8478994 was excluded due to both a poor fit as well as high $\hat{R}$ on rotational parameters.
+KICs 6603624, 8760414 and 8938364 are reported in \textbf{Extended Data} Table 1, but were excluded from the gyrochronology analysis due to strong disagreement with multiple studies in the literature (see main body of paper).
+Finally, we flagged any stars with fewer than 1000 effective samples ($n_{\rm eff}$) of $\nu_s$.
 
@@
 
-To construct a synthetic population of rotating stars, \cite{vansaders+2019} applied the rotational braking laws described above to a galactic population model.
-Their approach used a TRILEGAL \cite{girardi+2012} Milky-Way simulation of the \kepler field, using the standard population values intended for this purpose from \cite{girardi+2015}.
-Stars from the TRILEGAL simulations were then drawn randomly in bins until they matched observations of stellar parameters of the \kepler field \cite{mathur+2017}.
-This aimed to replicate the \kepler selection effect, by ensuring the TRILEGAL population properties matched those observed in the \kepler field.
-
 To construct a synthetic population of rotating stars, we expanded upon previous forward-models of the \textit{Kepler} field with the purpose of studying weakened magnetic braking \cite{vansaders+2019}, with some important improvements.
@@
 This was done using a nearest-neighbours approach, based on the density of stars on the HR diagram.
-This ensured that the TRILEGAL population matched the density of stars actually observed by \kepler, replicating its selection effects.
+This ensured that the TRILEGAL population matched the density of stars actually observed by \kepler, replicating its selection effects, and improved upon previous efforts \cite{vansaders+2019} by incorporating contemporary \textit{Gaia} mission data \cite{gaiacollaboration+2018}.
 
@@
 	\item recalculated the `observed' luminosities and magnitudes assuming that each binary pair was blended, and
-	\item shifted these stars' temperatures following the $g$-$K$ relation presented in \cite{berger+2020}.
+	\item shifted these stars' temperatures following a $g$-$K$ magnitude relation \cite{berger+2020}.
 \end{enumerate}
@@
 
-\subsection{Bayesian Mixture Models}
+\subsection{Bayesian Mixture Model}
 In order to determine whether weakened magnetic braking occurs on the main sequence, we compared our sample of seismic age and rotation, along with temperature, metallicity and mass, to the two stellar population models of the \kepler field adapted from \cite{vansaders+2019}, discussed above.
@@
 KIC 6278762 was excluded from this stellar model analysis, because its age fell more than $3\sigma$ outside of the highest age in the stellar models\footnote{This is a metallicity issue, as the oldest stars have metallicities outside the range of the rotational model grids.}, and KICs 7106245 and 8760414 were excluded for the same reason due to low metallicities outside the functional range of the stellar models (-0.99 and -0.92 respectively).
+We also excluded any stars with $n_{\rm eff} < 1000$ for rotational splitting, and those with $\hat{R} > 1.1$.
+The remaining sample of 73 stars contained 4 sub-giants, 22 `hot' stars, and 47 main sequence stars.
 
@@
 The array of 100 bins for all stars were multiplied, resulting in an approximation of the joint posterior probability function for $P_{\rm s}$ given all stars in the ensemble.
-
-\section{Results}
-bla bla short shpiel about which values were included and which weren't
 
@@
 
-A comparison between prior and posterior is shown for 94 stars in $\nu_{\rm s}\sin(i)$, $i$ and $P_{\rm rot}$ in Figure \ref{fig:priors}, arranged by age.
+A comparison between prior and posterior is shown for 94 stars in $\nu_{\rm s}\sin(i)$, $i$ and $P_{\rm rot}$ in \textbf{Extended Data} Figure \ref{fig:priors}, arranged by age.
 In the Figure, results with means and error bars that closely resemble the prior distribution can be interpreted as prior-dominated (i.e.
@@
 The three outliers with fast rotation at late ages (KICs 6603624, 8760414 and 8938364) are discussed in more detail in below.
- blow
+
 The rotation rates as presented in this work are a product of our Bayesian sampling of both projected splitting and angle of inclination.
-As seen in Figure \ref{fig:priors} there are instances where $i$ or $\nu_{\rm s}\sin(i)$ closely resemble the prior (and are therefore prior-dominated).
-There are no cases of this when looking at the resulting period measurements, as they will have been informed by at least one strongly data-driven parameter (judging from Figure \ref{fig:priors}, commonly $\nu_{\rm s}\sin(i)$).
+As seen in the Figure there are instances where $i$ or $\nu_{\rm s}\sin(i)$ closely resemble the prior (and are therefore prior-dominated).
+There are no cases of this when looking at the resulting period measurements, as they will have been informed by at least one strongly data-driven parameter (judging from the Figure, commonly $\nu_{\rm s}\sin(i)$).
 From this, we conclude that our ensemble of asteroseismic rotation is not strongly dominated by the priors imposed on projected splitting and inclination in our Bayesian analysis.
@@
 
-Comparisons with LEGACY and Kages are shown in Figure \ref{fig:legacykages} for projected splitting, inclination angle, and rotation period.
+Comparisons with LEGACY and `Kages' are shown in \textbf{Extended Data} Figure \ref{fig:legacykages} for projected splitting, inclination angle, and rotation period.
 In all three cases we show the fractional difference between the values obtained in this work and those from LEGACY and Kages.
-On the right of Figure \ref{fig:legacykages}, we show the distribution of the fractional differences for the three parameters.
+On the right of the Figure, we show the distribution of the fractional differences for the three parameters.
 The projected splitting is in good agreement with both studies, however LEGACY finds slightly lower $\nu_{\rm s}\sin(i)$ for the faster rotators, deviating from our work by over $1\sigma$.
-Neither LEGACY nor Kages used a spatially isotropic prior for the inclination angle in their analyses, instead opting for a uniform prior.
+Neither LEGACY nor `Kages' used a spatially isotropic prior for the inclination angle in their analyses, instead opting for a uniform prior.
 As posterior estimates of inclination angle are only loosely data-driven, the introduction of an isotropic prior should result in our analysis reporting globally higher inclination angles.
@@
 
-A number of stars are excluded from Figure \ref{fig:legacykages} and compared individually as extreme outliers: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have fast rotation rates ($<5\, \rm days$) in Kages, but are found to have a broader spread of rotation rates in this work.
-At similar values for $\nu_{\rm s}\sin(i)$, Kages found much lower inclination angles with highly asymmetrical uncertainties.
+A number of stars are excluded from \textbf{Extended Data} Figure \ref{fig:legacykages} and compared individually as extreme outliers: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have fast rotation rates ($<5\, \rm days$) in Kages, but are found to have a broader spread of rotation rates in this work.
+At similar values for $\nu_{\rm s}\sin(i)$, `Kages' found much lower inclination angles with highly asymmetrical uncertainties.
 Based on a comparison between the summary statistics of these stars, we conclude that the results found in this work have better marginalised over inclination angle, improving our measure of rotation.
@@
 
-We also compared our asteroseismic estimates of stellar rotation with similar studies in the literature, shown in Figure \ref{fig:literaturecomp}.
+We also compared our asteroseismic estimates of stellar rotation with similar studies in the literature, shown in \textbf{Extended Data} Figure \ref{fig:literaturecomp}.
 These included: a study of the binary solar analogues 16 Cyg A \& B \cite{davies+2015}, ; a study of surface and seismic rotation which our catalogue shares 5 stars with \cite{nielsen+2015}, ; and an asteroseismic study of differential rotation with which our catalogue shares 40 targets \cite{benomar+2018}.
@@
 
-Overall, Figure \ref{fig:literaturecomp} shows no strong disagreements between our asteroseismic measurements for stellar rotation and those from the literature.
+Overall,  \textbf{Extended Data} Figure \ref{fig:literaturecomp} shows no strong disagreements between our asteroseismic measurements for stellar rotation and those from the literature.
 The scatter of the fractional differences lies cleanly around the zero line, with a mean and spread of $0.0_{-15.6}^{+16.4}\, \%$.
@@
 
-There are three outliers at low period in Figure \ref{fig:literaturecomp}: KICs 6603624, 8760414 and 8938364.
-These are the same targets found to be outliers in a comparison to the LEGACY and Kages measurements (see above), with anomalously fast rotation rates and low inclination angles.
+There are three outliers at low period in  \textbf{Extended Data} Figure \ref{fig:literaturecomp}: KICs 6603624, 8760414 and 8938364.
+These are the same targets found to be outliers in a comparison to the LEGACY and `Kages' measurements (see above), with anomalously fast rotation rates and low inclination angles.
 As these stars represent the lowest inclination angles in our sample, and were found to disagree with two independent studies, we opted to exclude them from the gyrochronology analysis, and to flag the rotation measurements for these three stars presented in this work.
@@
 \subsection{Seismic vs spectroscopic rotation}
-Different methods of rotation measurement probe different regions of stars.
-Asteroseismology of main sequence stars probes internal rotation in the near surface layers, where the observed p modes are most sensitive \cite{lund+2014}.
-Measurements of star-spot modulation instead probe the rotation rates of star spots on the surface.
-A distinct difference between rotation rates obtained through these different techniques would hold information about differential rotation (both latitudinal and radial) of near-surface layers, such as those we observe in the Sun \cite{beck2000}.
-
-A previous comparison of spectroscopic and seismic rotation rates, performed on a sample of 22 stars, found no significant radial differential rotation.
+A distinct difference between rotation rates obtained through different techniques may hold information about differential rotation (both latitudinal and radial) of near-surface layers, such as those we observe in the Sun \cite{beck2000}.
+A previous comparison of spectroscopic and seismic rotation rates, performed on a sample of 22 stars, found no significant radial differential rotation \cite{benomar+2018}.
 In this work they not only considered rotation rates from spots, but also spectroscopic measures of the projected surface rotation $\textrm{v}\sin(i)$, which they found to be more reliable.
@@
 With our expanded sample of asteroseismic rotation we can perform a similar analysis, to both validate our sample and probe radial differential rotation.
-Figure \ref{fig:vsinilit} shows a comparison between spectroscopic $\textrm{v}\sin(i)$ measurements as listed in LEGACY and Kages (left) and \cite{benomar+2015} (right).
+\textbf{Extended Data} Figure \ref{fig:vsinilit} shows a comparison between spectroscopic $\textrm{v}\sin(i)$ measurements as listed in LEGACY and `Kages' (left) and \cite{benomar+2015} (right).
 In these cases the asteroseismic $\textrm{v}\sin(i)$ has been calculated using our measure of asteroseismic $\nu_s\sin(i)$ and the known asteroseismic radii.
@@
 
-For the LEGACY and Kages sample, we find no strong deviation from the 1:1 line except at very low velocities, which is likely due to biases inherent to spectroscopic line broadening measurements \cite{doyle+2014, tayar+2015}.
+For the LEGACY and `Kages' sample, we find no strong deviation from the 1:1 line except at very low velocities, which is likely due to biases inherent to spectroscopic line broadening measurements \cite{doyle+2014, tayar+2015}.
 For the \cite{benomar+2015} sample stars lie a lot closer to the 1:1 line.
@@
 Overall, there appears to be a global offset where spectroscopic measurements of projected rotation appear faster than asteroseismic measures.
-Based on the LEGACY and Kages $v\sin(i)$ values, this offset is roughly $18\%$ (i.e.
-spectroscopic projected rotation rates are higher than asteroseismic rates).
+Based on the LEGACY and `Kages' $v\sin(i)$ values, this offset is roughly $18\%$ (i.e.
+spectroscopic projected rotation rates are faster than asteroseismic rates).
 This offset is much smaller ($\sim5\%$) for the \cite{benomar+2015} sample, albeit for far fewer stars.
@@
 For the majority of cases, the seismic velocities are slower than the spectroscopic velocities, which would bias our ensemble towards favouring a standard evolution over a weakened magnetic braking scenario (as stars would overall appear to be rotating slower at late ages).
-Based on the comparison to spot rotation presented in the main body of this paper, and given known issues comparing seismic and spectroscopic rotation at low velocities, we conclude that the divergence seen in Figure \ref{fig:vsinilit} does not undermine our results.
+Based on the comparison to spot rotation presented in the main body of this paper, and given known issues comparing seismic and spectroscopic rotation at low velocities, we conclude that the divergence seen in  \textbf{Extended Data} Figure \ref{fig:vsinilit} does not undermine our results.
 
@@
 
-Do this
+Stars that are rotating very slowly will show small rotational splittings, which may be indistinguishable from a non-rotating case, wheras stars that are spinning very fast may find that their splitting is so wide that they cross over with split modes at different radial orders ($n$).
+Asteroseismic selection techniques may also introduce additional biases on a population level.
+We consider the limitations this places on our asteroseismic method.
+
+\begin{itemize}
+	\item \textit{Fast rotating stars:} In prinicple, a star could rotate fast enough that the highest-frequency peak in a split dipole ($\ell = 2$) mode would overlap with the radial ($\ell = 0$) mode.
+This would occur if $2\nu_{\rm s}$ > $\delta\nu_{02}$, the small separation.
+For the star in our sample with the smallest $\delta\nu_{02}$ (so the highest risk of this happening), this would occur at a rotation of 8.8 days or faster.
+For the star with the largest $\delta\nu_{02}$, this limit was roughly 2 days.
+
+	In practice, the model would still properly fit a spectrum where this kind of mode-overlapping occurred, as the $\ell = 0$ modes don't split, meaning that there are no degenerate solutions in this regime.
+A more serious issue may be when the $\ell = 1$ mode at lower frequencies overlapped with the $\ell = 2$ mode as well, which would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.
+
+	\item \textit{Slow rotating stars:} Except for the most fast rotating cases, asteroseismic mode splitting is detected by a broadening of the mode frequencies as the split components begin to separate from the central mode.
+If there is to be hard limit at which this measurement is not possible, it should be in the case that $\nu_{\rm s} < 2/T$, where $T$ is the observation time, and $1/T$ is the frequency bin width.
+For the star in our sample with the shortest observing time, this limit would be $\sim 89$ days, which quickly rises for longer observing baselines.
+While this constitutes a hard limit, slower rotation rates will become harder and harder to constrain as the rate of splitting becomes smaller.
+A benefit of the Bayesian approach used in this paper is that it should accurately reflect the increased uncertainty associated with the small rotational splitting.
+\end{itemize}
+
+While these two limits cause concern when studying the most extreme rotators, the results presented in this work are driven by stars with rotation rates in the regime of 10 to 40 days, and so we do not expect these limits to bias our conclusions.
+
+Finally, we also consider bias in asteroseismic detections.
+The probability of an asteroseismic detection with \kepler scales with temperature and radius (i.e.
+scales inversely with \logg, and therefore main sequence age) \cite{chaplin+2011, schofield+2019}.
+More active, magnetic stars may also suppress their oscillation modes, making it more likely to detect seismic oscillations in older stars \cite{mathur+2019}.
+Through these two effects, asteroseismology is biased towards detecting older over younger stars.
+As it is older stars, undergoing magnetic braking, that are required to drive the distinction between stellar models, we do not expect this observing bias to effect our conclusions.
 
@@
 \subsection{Limits of our stellar models}\label{ssec:limits}
-The models presented in \cite{vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$.
-Our sample of 91 stars contained 4 stars with metallicities below $-0.4\, \rm{dex}$, which are shown as shaded symbols in Figure \ref{fig:fullmodels}.
-Of these 4, 3 were included in our final sample of 73 stars used to evaluate our stellar models: KICs 7970740, 8684723 and KIC 9965715.
+The rotational stellar models used in this work \cite{vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$.
+Our sample of 91 stars contained 4 stars with metallicities below $-0.4\, \rm{dex}$, which are shown as shaded symbols in Figure \ref{fig:fullsample}.
+Of these, 3 were included in our final sample of 73 stars used to evaluate our stellar models: KICs 7970740, 8684723 and KIC 9965715.
 All three are classed as MS stars, with metallicities of $-0.54 \pm 0.10$, $-0.42 \pm 0.10$ and $-0.44 \pm 0.18\, \rm {dex}$ respectively, placing them within $3\sigma$ of the metallicity limits of our stellar models.
 KICs 8684723 and 9965715 strongly agree with the WMB model, whereas KIC 7970740 weakly prefers the standard model.
-Excluding these stars was not found to significantly alter the joint posterior distribution shown in Figure \ref{fig:modelresults}.
+Excluding these stars was not found to significantly alter the joint posterior distribution shown in Figure \ref{fig:gyroresults}.
 
-Recently, \cite{amard+matt2020} compared different rotational evolution models \cite[][of which we use the former in this work]{vansaders+pinsonneault2013,matt+2015} while studying the effect metallicity has on rotation.
+A recent study \cite{amard+matt2020} compared different rotational evolution models \cite[of which we use the former in this work]{vansaders+pinsonneault2013,matt+2015} while studying the effect metallicity has on rotation.
 They found that metal-rich stars spin down significantly more effectively than metal poor stars.
 The population of 73 stars used in our stellar model comparisons is roughly centered on a $\rm{[Fe/H]}$ of 0 $\rm dex$, with a spread of $~0.16\, \rm dex$, with no stars significantly above or below $\pm 0.4\, \rm dex$ (as discussed above).
-While differences in stellar rotational evolution as a function of metallicity in this region are still somewhat pronounced, they are much less so than for more metal-rich or poor stars \cite[see Figure 2][]{amard+matt2020}.
-However, for stars with $\feh < 0$, the \cite{matt+2015} model prescription sees stars spin down more slowly than the models used in this work (i.e.
+While differences in stellar rotational evolution as a function of metallicity in this region are still somewhat pronounced, they are much less so than for more metal-rich or poor stars \cite[see Figure 2]{amard+matt2020}.
+However, for stars with $\feh < 0$, the alternative model prescription \cite{matt+2015} sees stars spin down more slowly than the models used in this work (i.e.
 they will rotate faster at later ages).
@@
 While the 24 stars with small uncertainties do favour the WMB model, they do so very weakly, whereas the remaining 49 stars with larger uncertainties strongly favour the WMB model.
-Their removal from the total joint posterior probability does not significantly alter it from the distribution shown in Figure \ref{fig:modelresults}.
+Their removal from the total joint posterior probability does not significantly alter it from the distribution shown in Figure \ref{fig:gyroresults}.
 
@@
 Asteroseismic properties obtained through stellar models can be subject to systematic errors arising from differences in input physics and choice of stellar models not included in the reported statistical uncertainties.
-A quantification of these different systematic effects can be found in Section 4 of \cite{silvaaguirre+2015}, based on the Kages catalogue.
-Combining their reported median systematic uncertainties due to input physics results in median uncertainties of $20\%$ (up from $14\%)$ on age and $5\%$ (up from $3\%$) on mass for the Kages sample.
+A quantification of these different systematic effects can be found in the `Kages' catalogue paper \cite{silvaaguirre+2015}.
+Combining their reported median systematic uncertainties due to input physics results in median uncertainties of $20\%$ (up from $14\%)$ on age and $5\%$ (up from $3\%$) on mass for the `Kages' sample.
 For LEGACY, the median uncertainties are $18\%$ (up from $10\%)$ and $5.6\%$ (up from $4\%$) for age and mass respectively.
 
-In order to check the effect of systematic seismic uncertainties on our results for gyrochronology, we re-ran our model analysis described in Section \ref{s:gyro} after inflating uncertainties on mass and age.
+We re-ran our model analysis after inflating uncertainties on mass and age.
 We increased uncertainties by the fractional difference between the \texttt{BASTA} statistical uncertainties and the median full statistical and systematic uncertainties described above.
 For example, a LEGACY star with a mass of $2.0 \pm 0.5\, M_\odot$ would have its uncertainty inflated by $1.6\%$ of its mass, to $0.53\, M_\odot$.
-The resulting joint posterior distribution for 73 stars still strongly favoured of the WMB model even with the inflated uncertainties, including when considering only stars on the main sequence, when excluding stars outside the models' metallicity range, and when excluding stars with low uncertainties on mass.
 
-To further test the limits of this analysis, we reran our mixture model fit, this time only shifting the asteroseismic ages younger by the systematic uncertainty, and retaining the statistical uncertainty (i.e.
-the ages of LEGACY and Kages stars were reduced by $8\%$ and $6\%$ respectively).
+To further test the limits of this analysis, we also reran our mixture model fit, this time only shifting the asteroseismic ages younger by the systematic uncertainty, and retaining the statistical uncertainty (i.e.
+the ages of LEGACY and `Kages' stars were reduced by $8\%$ and $6\%$ respectively).
 In this scenario where all asteroseismic ages are overestimated, `true' fast rotators at young ages would have been mistaken for fast rotators at old ages, suggesting the presence of weakened magnetic braking where none existed.
-Despite the shift in age, the results from this mixture model fit closely matched those found for the unaltered ensemble, finding $95.8\%$ of the total posterior probability to lie below $P_{\rm s} = 0.5$ (as opposed to $98.4\%$ for the unaltered ensemble).
+
+The results of these tests are discussed further in the main body of the paper.
 

### 2020-09-30 paper/natastron/paper.tex
Done with the main body pretty much
Almost done with methods

@@
 \textbf{Studies using asteroseismic ages and rotation rates from star-spot rotation have indicated that standard age-rotation relations may break down roughly half-way through the main sequence lifetime, a phenomenon referred to as weakened magnetic braking.
-While rotation rates from spots can be difficult to determine for older, less active stars, rotational splitting of asteroseismic oscillation frequencies can provide rotation rates for both active and quiescent stars, and so can confirm whether this effect really takes place in older stars.\\
+While rotation rates from spots can be difficult to determine for older, less active stars, rotational splitting of asteroseismic oscillation frequencies can provide rotation rates for both active and quiescent stars, and so can confirm whether this effect really takes place on the main sequence.\\
 We obtained asteroseismic rotation rates of 91 main sequence stars showing high signal-to-noise modes of oscillation.
@@
 It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops.
-This would cause stars to keep fast rotation rates at old ages, which we would not expected from existing gyrochronology relations.
+This would cause stars to keep fast rotation rates at old ages, which we would not expect from existing gyrochronology relations.
 
@@
 In this work, we studied a sample of 95 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}.
-Further details on how these data can be found in \textbf{\textit{Methods}}.
+Further details on these data can be found in \textbf{Methods}.
 
@@
 	\includegraphics[width=0.6\textwidth]{data.pdf}
-	\caption{Our sample of 95 stars from the Kages and LEGACY catalogues coloured by asteroseismic age  \cite{silvaaguirre+2015, silvaaguirre+2017}.
+	\caption{Our sample of 95 stars from the `Kages' and LEGACY catalogues coloured by asteroseismic age  \cite{silvaaguirre+2015, silvaaguirre+2017}.
 The dashed lines indicate our classification boundaries: main sequence (circles, $\teff < 6250\, K$, $\logg < 4\, \rm{dex}$), potential sub-giants (squares, $\teff < 6250\, K$, $\logg > 4\, \rm{dex}$), and `hot' stars (triangles, $\teff > 6250\, K$).
@@
 Left to right, they represent masses of $1.5$, $1.25$, $1$ and $0.75\, M_\odot$.
-Vertical errorbars are too small to be visible.}
+Vertical errorbars are too small to be visible \cite{hunter2007}.}
 	\label{fig:sample}
@@
 
-\textbf{Results of asteroseismic fitting:} The stars in `Kages' and LEGACY form our stellar sample have been subject to detailed asteroseismic frequency fitting in the catalogue papers, but did not report asteroseismic rotation.
-Here, we repeated the mode frequency fitting with a Bayesian model that accounted for rotation in more detail, and improved the treatment of existing asteroseismic relations in frequency fitting techniques (see \textbf{\textit{Methods}} and \textit{\textbf{Supplementary Information}}).
+\textbf{Results of asteroseismic fitting:} The stars in `Kages' and LEGACY which form our stellar sample have been subject to detailed asteroseismic frequency fitting in the catalogue papers, but did not have reported asteroseismic rotation.
+Here, we repeated the mode frequency fitting with a Bayesian model that accounted for rotation in more detail, and improved the treatment of existing asteroseismic relations in frequency fitting techniques (see \textbf{Methods} and \textbf{Supplementary Information}).
 We fit our new model to \kepler power-spectra of 95 stars, which was successful in 94 cases.
-We compared our results with both published and unpublished asteroseismic rotation rates, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with multiple other studies.
+The summary statistics used throughout the rest of this paper were taken as the median of the posterior distribution on the model parameters, with the uncertainties being the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles, meaning that some reported parameters (such as period) have asymmetric uncertainties.
+
+We compared our results with both published and unpublished asteroseismic rotation rates \cite{davies+2016, lund+2017,davies+2015, nielsen+2015, benomar+2018}, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with multiple other studies.
 To some degree this was expected, as  for stars viewed near pole-on the split modes of oscillation have extremely low power, making them hard to detect reliably.
-We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we considered our asteroseismic rotation measurements to be robust (for a full justification, see \textit{\textbf{Methods}}).\\
+We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we considered our asteroseismic rotation measurements to be robust (for a full justification, see \textbf{Methods}).\\
 
@@
 Rotation rates from spot modulation are subject to measuring multiples of the true rotation rate, and also sometimes over-correct for this effect.
-This is not the case for asteroseismic rotation, and so some stars may appear at the 2:1 and 1:2 lines in the Figure.
+This is not the case for asteroseismic rotation, and so some stars may appear at the 2:1 and 1:2 lines in the figure.
 We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid outliers (transparent in the Figure).
@@
 %Of the stars used in this comparison, 21 had a median value of $P_{\rm s}$ in the gyrochronology analysis. We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.  
-This overall agreement between spot and seismic rotation rates is in line with previous studies of Sun-like stars \cite{gizon+2013, chaplin+2013, nielsen+2015, benomar+2015}, and so we can conclude that our asteroseismic ensemble can be reliably used to draw inferences about gyrochronology.\\
+This overall agreement between spot and seismic rotation rates is in line with previous studies of Sun-like stars \cite{gizon+2013, chaplin+2013, nielsen+2015, benomar+2015}, and so we concluded that our asteroseismic ensemble can be reliably used to draw inferences about gyrochronology.\\
 
@@
 The shaded region around the 1:1 line is the $1\sigma$ credible interval of the fit to the data, the result of which is shown as the title of the figure.
-Stars that were not included in the fitting process are transparent.}
+Stars that were not included in the fitting process are transparent.
+The errorbars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions.}
 	\label{fig:protlit}
@@
 
-\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two population models of rotational evolution: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model').
-The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$.
-Instead of comparing our rotation rates directly to models of individual stars, we instead compared them to synthetic populations based on what the \textit{Kepler} field would look like under these two different braking laws \cite{girardi+2012,vansaders+2019}.
-For the full details on how these models were constructed, see \textbf{\textit{Methods}}.
+\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two population models of rotational evolution \cite{vansaders+2019}: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model') \cite{vansaders+2016}  The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$\footnote{The Rossby number may be defined as $Ro \equiv P/\tau_{\rm cz}$, where $\tau_{\rm cz}$ is the convective turnover timescale, and $P$ is the rotation.
+The Rossby number roughly scales inversely with stellar activity (and so increases as stars age).}
 
-In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting\footnote{Excluding those with a number of effective samples $n_{\rm eff} < 25\%$ and a Gelman-Rubin metric of $\hat{R}>1.1$ \cite{gelman+rubin1992,salvatier+2016}} (see \textbf{\textit{Extended Data Table 1}}).
+Instead of comparing our rotation rates directly to models of individual stars, we instead compared them to synthetic TRILEGAL populations based on what the \textit{Kepler} field would look like under these two different braking laws \cite{girardi+2012,vansaders+2019}.
+These synthetic populations were then altered to match the distribution of existing catalogues of stars in the \kepler field in order to replicate the \kepler selection effect \cite{berger+2020}, and evolved following a standard or WMB braking law.
+For the full details on how these models were constructed, see \textbf{Methods}.
+
+In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting, Excluding those with a number of effective samples $n_{\rm eff} < 25\%$ and a Gelman-Rubin metric of $\hat{R}>1.1$ \cite{gelman+rubin1992,salvatier+2016} (see \textbf{Extended Data Table 1}).
 The remaining sample of 73 stars contained 4 potential sub-giants, 22 `hot' stars and 47 main sequence stars.
@@
 	\includegraphics[width=\textwidth]{fullsample.png}
-	\caption{Stars for which rotation was measured in this work, plotted over stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution.
+	\caption{Stars for which rotation was measured in this work, plotted over TREILGAL \cite{girardi+2012} stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution.
 The 21 Stars that were excluded from the gyrochronology analysis are marked with crosses and without uncertainties (see text).
 Circles, squares and triangles denote main sequence, sub-giant, and `hot' stars respectively.
-Stars with a metallicity of $\bigl\lvert \feh \bigl\rvert > 0.4$ are coloured differently (darker), to indicate that they fall outside the functional range of the \cite{vansaders+2019} stellar models.
-Note that only period-temperature space is shown here, but when evaluating between the two model prescriptions we also considered mass, age and metallicity.}
+Stars with a metallicity of $\bigl\lvert \feh \bigl\rvert > 0.4$ are shown in purple, to indicate that they fall outside the functional range of the \cite{vansaders+2019} stellar models.
+Note that only period-temperature space is shown here, but when evaluating between the two model prescriptions we also considered mass, age and metallicity.
+The errorbars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions.}
 	\label{fig:fullsample}
@@
 We evaluated our ensemble against both population models simultaneously using a Bayesian mixture model, which treated the data as being drawn from a mixture made from Kernel Density Estimates (KDEs) of both populations, modulated by a mixing parameter $P_{\rm s}$.
-In the limit that $P_{\rm s} \rightarrow 1$, the data are mostly likely drawn from the standard model.
+In the limit that $P_{\rm s} \rightarrow 1$, the data are most likely drawn from the standard model.
 In the limit $P_{\rm s} \rightarrow 0$, the WMB model is more likely.
 This mixture model was evaluated in a five-dimensional parameter space, accounting for the population distributions in effective temperature ($T_{\rm eff}$), metallicity (\feh), asteroseismic mass ($M$) and age ($t$) and our new rotation periods ($P$).
+For further detail, see \textbf{Methods}.\\
 
-We fit our mixture model to each star individually, which yielded a posterior probability density for the value of $P_{\rm s}$ for that star.
-In order to assess the posterior probability for the full sample, we multiplied the individual posterior probabilities for $P_{\rm s}$.
+\textbf{Results of comparing models:} We fit our mixture model to each star individually, which yielded a posterior probability density for the value of $P_{\rm s}$ for that star.
+In order to assess the posterior probability for the full sample, we multiplied the individual posterior probabilities for $P_{\rm{s}}$.
 This was done for the full ensemble of 73 stars, as well as for the three different stellar types.
@@
 The cumulative probability can be seen in the right-hand plot.
-In both of these plots, the left-hand side holds 98.4\% of the probability\footnote{When performing this analysis on all 91 stars for which seismic rotation was measured, this value is 96.6\%.}, indicating that the weakened magnetic braking model is preferred.
+In both of these plots, the left-hand side holds 98.4\% of the probability, indicating that the weakened magnetic braking model is preferred.
 When only considering the 47 main sequence stars, for which we expect the effects of weakened magnetic braking to be strongest, this rises to 99.2\%.
+
+Both hot and sub-giant stars do not strongly prefer one model over the other (both crossing the $P_{\rm{s}} = 0.5$ line at roughly $45\%$), which is expected given that the rotation rates of both these stellar types are not expected to be strongly influenced by weakened magnetic braking.
+When performing this analysis on the full ensemble of 91 stars for which seismic rotation was measured, this the total probability below $P_{\rm{s}} = 0.5$ is 96.6\%.
 \\
@@
 This resulted in $95.8\%$ of the posterior probability to lie below $P_{\rm s} = 0.5$, compared to $98.4\%$ for the unaltered ensemble.
-From this, we can infer that our conclusions are robust against (relatively severe) potential issues in seismic analyses.
-For a full discussion of these tests and other biases, see \textbf{\textit{Methods}}.\\
+From this, we can infer that our conclusions are robust against potential issues in seismic analyses.
+For a full discussion of these tests and other biases, see \textbf{Methods}.\\
 
 Weakened magnetic braking was first proposed by van Saders et al.
-(2016) \cite[hereafter the `van Saders' study]{vansaders+2016} in response to stars with spot rotation rates faster than expected from gyrochronology at their asteroseismic ages \cite{vansaders+2016}.
+(2016) \cite[hereafter the `van Saders' study]{vansaders+2016} in response to stars with spot rotation rates faster than expected from gyrochronology at their asteroseismic ages.
 This discrepancy was also indicated at around the same time in other studies of asteroseismic ages of main sequence stars \cite{nielsen+2015, angus+2015, davies+2015}.
@@
 Our sample does not overlap with theirs, so we can not directly compare to their results.
-However, our work does find statistical agreement between our asteroseismic rotation rates and ages, and a model of weakened magnetic braking at a critical Rossby number of $1.97$.
-A comparison to models of different Rossby numbers will be explored in future papers, using the LEGACY and Kages rotation sample presented in this work.
+Our work does find statistical agreement with a model of weakened magnetic braking at a critical Rossby number of $1.97$ over one without any braking at all, indicating that traces of weakened magnetic braking do occur at Rossby numbers of around $2$.
+A comparison to models of different Rossby numbers will be explored in future papers, using the LEGACY and `Kages' rotation sample presented in this work.
 
@@
 We evaluated the stars in our sample against synthetic population models of the \textit{Kepler} field evolved under either a `standard' model of rotational evolution, or one where weakened magnetic braking takes place.
-This evaluation was done using a Bayesian mixture model to determine whether the ensemble preferred one model over another, and was done in simultaneously in asteroseismic rotation, mass, age, and spectroscopic temperature and metallicity.\\
+This evaluation was done using a Bayesian mixture model to determine whether the ensemble preferred one model over another, and was done simultaneously in asteroseismic rotation, mass, age, and spectroscopic temperature and metallicity.\\
 
@@
 	\item We found that our ensemble was $98.4\%$ more likely to be drawn from a weakened magnetic braking model than a standard model of rotational evolution \cite{vansaders+pinsonneault2013}, at a critical Rossby number of $Ro_{\rm{crit}} = 1.97$.
-This work expands upon previous analysis (\cite{vansaders+2019}) by including quiescent stars older than the Sun.
-This conclusion was found to be robust against choice of ensemble members and potentially underestimated asteroseismic systematic uncertainties.
-A comparison to other braking laws \cite{matt+2015} and other gyrochronology relations using our asteroseismic ensemble will take place in future work.
+This work expands upon previous analysis \cite{vansaders+2019} by including quiescent stars older than the Sun.
+This conclusion was found to be robust against change of ensemble members and potentially underestimated asteroseismic systematic uncertainties.
+A comparison to other braking laws \cite{matt+2015} and other gyrochronology relations \cite{barnes2010} using our asteroseismic ensemble will take place in future work.
 
@@
 
-	\item We present new techniques for asteroseismic `peak-bagging' frequency analyses, specifically: expressing well known empirical asteroseismic relations in a hierarchical modeling structure to account for small-scale effects not included in our model (such as acoustic glitches), and replacing uninformative empirical relations with Gaussian Process priors, detailed in the \textit{\textbf{Supplementary Information}}.
+	\item We present new techniques for asteroseismic `peak-bagging' frequency analyses, specifically: expressing well known empirical asteroseismic relations in a hierarchical modeling structure to account for small-scale effects not included in our model (such as acoustic glitches), and replacing uninformative empirical relations with Gaussian Process priors, detailed in the \textbf{Supplementary Information}.
 
@@
 
-In the near future this asteroseismic rotation catalogue will be further complemented with high-precision surface rotation measurements and atmospheric parameters from spectroscopic surveys such as LAMOST \cite{deng+2012}, 4MOST \cite{dejong+2014} and WEAVE \cite{dalton+2014}, and new asteroseismic measurements of age from the \ktwo and \tess missions.
+In the near future our new asteroseismic rotation catalogue will be further complemented with high-precision surface rotation measurements and atmospheric parameters from spectroscopic surveys such as LAMOST \cite{deng+2012}, 4MOST \cite{dejong+2014} and WEAVE \cite{dalton+2014}, and new asteroseismic measurements of age from the \ktwo and \tess missions.
 With these surveys, large scale ensemble asteroseismology will continue to increase the possibilities for understanding gyrochronology.\\
@@
 
+\input{ed.tex}
+
 \bibliographystyle{naturemag}

### 2020-09-30 paper/natastron/methods.tex
Finished Methods

@@
 
-Todo: water down the contents of the methods here.
+In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background, modes of oscillation, and white noise, while accounting for rotational splitting.
+The foundations of this approach follows best-practices in asteroseismology \cite{davies+2015}, fitting Harvey profiles for the background \cite{harvey1985}, and expressing the frequencies of the modes using an asymptotic expression \cite{tassoul1980, vrard+2016}.
 
-From our asteroseismic analysis, we report inclination angle, rotational splitting, and rotation period in \textbf{Extended Data} Table 1.
+The first core improvement in this work come in the form of the use of hierarchical models, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{mazumdar+2014}).
+By improving the inference of mode frequencies in this way, we also improve the ability to resolve the rotational splitting.
+The second improvement comes in the form of priors on our parameters, and in particular the rotational inclination, which more accurately reflects the true distribution of angles than previous techniques \cite{chaplin+basu2017}.
+A step-by-step breakdown of the model and all priors can be found in \textbf{Supplementary Materials}.\\
+
+We separated our model fitting into two parts.
+First, we fit a model for the convective background and white noise only, to the region of the power spectra that did not contain modes of oscillation.
+This was done using \texttt{PyStan} \cite{vanhoey+2013,carpenter+2017}, for 10,000 iterations on each star\footnote{These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work}.
+Second, we fit our full model (including the convective background) to the region containing the modes of oscillation.
+The results of the first fit to the convective background were used as extremely informative priors on the background parameters in this second fit.
+This was done using \texttt{PyMC3} \cite{vanderwalt+2011,salvatier+2016, thetheanodevelopmentteam+2016} for 2500 iterations each on 4 chains.
+
+From this asteroseismic analysis, we report inclination angle ($i$), rotational splitting ($\nu_{\rm s}$), and rotation period ($P$) in \textbf{Extended Data} Table 1.
 The summary statistics on these parameters were taken as the median of the posterior distribution, with uncertainties being the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles.
-For inclination angle ($i = \arccos(\cos(i))$) and rotation ($P = 1/\nu_{\rm s}$, the full posterior samples were transformed before taking the summary statistics, as our model sampled in $\cos(i)$ and $\nu_{\rm s}$.
+For inclination angle ($i = \arccos(\cos(i))$) and rotation ($P = 1/\nu_{\rm s}$), the full posterior samples were transformed before taking the summary statistics, as our model sampled in $\cos(i)$ and $\nu_{\rm s}$.
 
@@
 To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $P_{\rm s}$, and multiplied these post hoc to obtain a combined posterior.
-This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications, at the expense of the ability to marginalise for a single value of $P_{\rm s}$ directly.
+This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications, at the expense of the ability to marginalise for a single value of $P_{\rm s}$ directly.\\
 
-\subsubsection{Fitting procedure}
 The parameter space of the stellar models populations were reduced before calculating the KDEs.

### 2020-10-01 paper/natastron/ed.tex
Finished SI

@@
 \clearpage
- \begin{figure*}
- 	\centering
- 	\includegraphics[width=.99\textwidth]{Images/modelfit.pdf}
- 	\caption{A power spectrum constructed from four years of \kepler observations of 16 Cyg A (KIC 12069424).
-Plotted over the top is the model resulting from the fit to the data described in this work.
-The model implements both the mode frequencies, seen on the right hand side of the plot, and the convective background, the effects of which are seen on the left.
-Low frequencies have been cropped out for clarity.
-\textit{Inset}: A zoom in on a radial (right) and quadrupole (left) ($\ell = 0, 2$) pair of modes.
-The quadrupole mode is split into five components by the star's rotation.
-Due to the star's inclination angle with respect to us, two out of five peaks are more distinct.
-The height and spacing of the mode components is a function of the star's rotational splitting ($0.56\, \mu\rm{Hz}$, equivalent to $P_{\rm rot} = 20.5\, \rm{days}$) and angle of inclination ($45^\circ$).}
- 	\label{fig:modelfit}
- \end{figure*}
 

### 2020-10-01 paper/natastron/methods.tex
Finished SI

@@
 
-The first core improvement in this work come in the form of the use of hierarchical models, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{mazumdar+2014}).
+The first core improvement in this work come in the form of the use of hierarchical latent variable models \cite{hogg+2010, hall+2019}, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{mazumdar+2014}).
 By improving the inference of mode frequencies in this way, we also improve the ability to resolve the rotational splitting.
@@
 	\item \textit{Fast rotating stars:} In prinicple, a star could rotate fast enough that the highest-frequency peak in a split dipole ($\ell = 2$) mode would overlap with the radial ($\ell = 0$) mode.
-This would occur if $2\nu_{\rm s}$ > $\delta\nu_{02}$, the small separation.
+This would occur if $2\nu_{\rm s}$ > $\delta\nu_{0,2}$, the small separation.
 For the star in our sample with the smallest $\delta\nu_{02}$ (so the highest risk of this happening), this would occur at a rotation of 8.8 days or faster.

### 2020-10-01 paper/natastron/si.tex
Done with the main body pretty much
Finished Methods
Finished SI

@@
-\section{Supplementary Information}
-\subsection{Asteroseismic Model}\label{s:seismo}
-In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background ($B(\nu)$), the oscillations ($O(\nu)$), and the white noise ($W$) in the style of e.g.
-\cite{davies+2015}.
+\clearpage
+\section*{Supplementary Information}
+
+\section*{Asteroseismic Model}\label{s:seismo}
+In order to extract signatures of stellar rotation from the asteroseismic p mode frequencies, we built a model that simultaneously treats the convective background ($B(\nu)$), the oscillations ($O(\nu)$), and the white noise ($W$), where $\nu$ is frequency \cite{davies+2015}.
 Our data, observed with \kepler, are also subject to the apodization (attenuation) of signals in the frequency-domain, where we fit our model \cite{chaplin+2011}.
@@
 
-\subsubsection{Convective Background}
+\subsection*{Convective Background ($B(\nu)$)}
 To model the convective background we used three Harvey components \cite{harvey1985}, which express the background in power as Lorentzian-like functions centered on zero frequency.
@@
 
-\subsubsection{Modes of Oscillation}
+\subsection*{Modes of Oscillation ($O(\nu)$)}
 Modes of oscillation appear in the power spectrum as Lorentzian peaks \cite{chaplin+basu2017}.
-Due to stellar rotation, each mode with an angular degree of $\ell > 0$ is split into its $(2\ell +1)$ Lorentzian components, labeled by $m$, the azimuthal order.
-For all $\ell=(0,1,2)$ modes identified in \cite{davies+2016,lund+2017} we add a (set of) Lorentzian(s) to our model, building a composite model representing all visible modes.
+These peaks can be described by three values: the radial order ($n$, the overtone number of the oscillation), the angular degree ($\ell$) and the azimuthal order ($m$).
+Due to stellar rotation, each mode with an angular degree of $\ell > 0$ is split into its $(2\ell +1)$ Lorentzian components, labeled by $m$.
+For all $\ell=(0,1,2)$ modes identified for our targets in the  `Kages'  and LEGACY studies \cite{davies+2016,lund+2017} we add a (set of) Lorentzian(s) to our model, building a composite model representing all visible modes.
 The construction of our oscillation model takes the form
@@
 
-\noindent where $n$ is the radial order of a mode (i.e.
-the overtone number of the oscillation), $H_{n,\ell,m}$ is the height of the mode, $\Gamma_{n,\ell}$ is the linewidth of the mode (approximated to be equal for all split components at a single $n$ and $\ell$) and $\nu_{n, \ell, m}$ is the frequency of the mode.
+\noindent where $H_{n,\ell,m}$ is the height of the mode, $\Gamma_{n,\ell}$ is the linewidth of the mode (approximated to be equal for all split azimuthal orders at a single $n$ and $\ell$) and $\nu_{n, \ell, m}$ is the frequency of the mode.
 The range of $n$ differs per star depending on how many radial orders were reported in LEGACY or Kages, and the range of $\ell$ depends on how many angular degrees were reported for the corresponding radial order.
 
-\subsubsection{Mode Frequencies and Rotational Splitting}\label{ssec:frequencies}
+\subsubsection*{Mode Frequencies and Rotational Splitting ($\nu_{n,\ell,m}$)}\label{ssec:frequencies}
 The mode frequencies of main sequence stars are described by the asymptotic expression \cite{tassoul1980, vrard+2016}.
@@
 \begin{equation}\label{eq:asymptotic}
-	\nu_{n,\ell,m} = \dnu\left(n + \epsilon + \delta\nu_{0,\ell} + \frac{\alpha}{2}(n - \frac{\numax}{\dnu} + \epsilon)^2\right) + m\nu_{s}\, ,
+	\nu_{n,\ell,m} = \dnu\left(n + \epsilon + \delta\nu_{0\ell} + \frac{\alpha}{2}(n - \frac{\numax}{\dnu} + \epsilon)^2\right) + m\nu_{s}\, ,
 \end{equation}
 
-\noindent where \dnu is the large frequency separation between two consecutive radial orders, $\epsilon$ is a a phase offset, $\delta\nu_{0,\ell}$ is the small frequency separation between two oscillation modes of different $\ell$ at the same radial order, $\alpha$ describes the curvature of the spacing around \numax, and $\nu_s$ is the rotational splitting.
-Note that here we have expressed the small separation $\delta\nu_{0,\ell}$ as a fraction of $\dnu$.
+\noindent where \dnu is the large frequency separation between two consecutive radial orders $n$, $\epsilon$ is a a phase offset, $\delta\nu_{0\ell}$ is the small frequency separation between two oscillation modes of different $\ell$ at the same radial order, $\alpha$ describes the curvature of the spacing around \numax, and $\nu_s$ is the rotational splitting.
+Note that here we have expressed the small separation $\delta\nu_{0\ell}$ as a fraction of $\dnu$.
 In order to improve the computational efficiency of this analysis, we fixed \dnu to the values reported in LEGACY and Kages.
@@
 The parameters $\nu_{n,\ell,m}$ were allowed to vary within an uncertainty $\sigma_{\ell}$, which has a single value for each angular degree and also varied as a free parameter.
-This allowed us to account for small shifts in frequency due to sudden changes in the stellar structure \cite[called acoustic glitches]{mazumdar+2014}.
+This allowed us to account for small shifts in frequency due to sudden changes in the stellar structure \cite{mazumdar+2014}.
+
 The mode frequency latent parameters were drawn from a normal distribution using Equation \ref{eq:asymptotic} as its mean function, as
@@
 The symbol `$\sim$' indicates that the parameters on the left hand side of the equation are drawn from the probability distribution on the right hand side.
-This notation will be used throughout this paper.
+This notation will be used throughout this work.
 
-\subsubsection{Mode Linewidth}
+\subsubsection*{Mode Linewidth ($\Gamma_{n,\ell}$)}
 The linewidths of asteroseismic p modes vary roughly as a function of mode frequency, and do so slowly relative to \dnu.
@@
 Instead of fitting this relation, we chose to employ a more flexible Gaussian Process \cite[GP]{rasmussen+williams2006} to act as a prior on the linewidths.
-This can be considered as us modelling the linewidths as correlated measurements.
-As our GP covariance kernel we used a Squared Exponential Kernel to capture the slight periodicity of linewidth with frequency, as
+This can be considered as us modelling the linewidths as correlated measurements, effectively loosely constraining how linewidth varies with frequency.
+
+A GP is defined by a covariance kernel (describing the degree of correlation between linewidths) and a mean function (describing a global trend with frequency).
+As this approach describes the mode linewidths relative to one another in frequency, the radial orders of each target $n$ were rescaled to be between 0 (for the lowest $n$) and 1 (for the highest $n$)\footnote{The radial orders of $\ell = 2$ modes were increased by $1$ to ensure this approximation applied to all modes.}.
+This approximation was used to describe the change in linewidth as a function of frequency without depending on the exact frequencies of the modes, which themselves were free parameters (see above).
+Given this, we defined our GP covariance kernel as a Squared Exponential Kernel to capture the slight periodicity of linewidth with frequency, as
 
@@
 
-\noindent where $n_{\rm f}$ is the fractional radial order of a given mode.
-For each star, the overtone numbers $n$ were rescaled to be between 0 (for the lowest $n$) and 1 (for the highest $n$)\footnote{Overtones of $\ell = 2$ modes were increased by $1$ to ensure this approximation applied to all modes.}.
-This approximation was used to describe the change in linewidth as a function of frequency without depending on the exact frequencies of the modes.
-$K_{i,j}$ represents an element of the covariance matrix $\underline{K}$, describing the covariance between two values of linewidth at different fractional radial orders.
-The GP kernel has two hyperparameters: $\rho$, which determines the spread of the kernel, and $L$, which determines the length scale in terms of $n_{\rm f}$.
-The length scale was significantly larger than the large frequency separation (\dnu) in all cases, and so we considered the use of fractional radial orders a valid approximation in this model.
+\noindent where $n_{\rm f}$ is the fractional radial order of a given mode and  $K_{i,j}$ represents an element of the covariance matrix $\underline{K}$, describing the covariance between two values of linewidth at different fractional radial orders.
+The GP kernel has two hyperparameters: $\rho$, which determines the spread of the kernel in linewidth, and $L$, which determines the length scale in terms of $n_{\rm f}$.
+The length scale $L$ was significantly larger than the large frequency separation (\dnu) in all cases, and so we considered the use of fractional radial orders a valid approximation in this model.
 
@@
 
-\subsubsection{Mode Heights and Angle of Inclination}
+\subsubsection*{Mode Heights and Angle of Inclination ($H_{n,\ell,m}$)}
 The height in power of each mode, $H_{n, \ell, m}$, varies not only as a function of distance in frequency from \numax, but also due to observation conditions, such as inclination angle and passband.
@@
 
-\noindent where $\varepsilon_{\ell, m}(i)$ modulates the height as a function of inclination angle ($i$) (see below), and $A_{n, \ell}$ and $\Gamma_{n, \ell}$ are the mode amplitude and linewidth respectively for a given radial order and angular degree.
+\noindent where $\varepsilon_{\ell, m}(i)$ modulates the height as a function of inclination angle $i$ (see below), and $A_{n, \ell}$ and $\Gamma_{n, \ell}$ are the mode amplitude and linewidth respectively for a given radial order and angular degree.
 Instead of modeling and modulating height directly, we instead sampled in amplitude and linewidth.
@@
 As done above for the mode frequencies and linewidths, the mode amplitudes $A_{n,\ell}$ were also treated as latent parameters drawn from a probability distribution governed by hyperparameters.
-We used a Gaussian function $G(\nu)$, centered on $\numax$, so that
+For this, we used a Gaussian function $G(\nu)$, centered on $\numax$, as
 
@@
 
-\noindent where $A$ is the amplitude at \numax, and $w$ is the width of the Gaussian, both free parameters in our model. 
+\noindent where $A$ is the modes' amplitude at \numax, and $w$ is the width of the Gaussian, both free parameters in our model. 
 The mode amplitude latent parameters were then drawn from the probability distribution
 
-\begin{equation}
+\begin{equation}\label{eq:amplitwod}
 	A_{n, \ell} \sim \mathcal{N}(G(\nu_{n,\ell}) \times V_\ell, \sigma_{A})\, ,
@@
 \noindent where $V_\ell$ is a free parameter for the mode visibility of different angular degrees, which should be consistent for all \kepler observations.
+These parameters describe the difference in relative height between modes of different radial order.
 The mode visibility for $V_0$ is fixed at 1, and $V_{1,2}$ are treated as free parameters.
@@
 
-\subsubsection{Likelihood Function}\label{sec:like}
-If data have Gaussian noise in the time domain, they will appear in the frequency domain with noise following a $\chi^2$ distribution with two degrees of freedom \cite[$\chi^2_2$ hereafter][]{woodard1984}.
+\subsection*{Likelihood Function for $M(\nu)$}\label{sec:like}
+If data have Gaussian noise in the time domain, they will appear in the frequency domain with noise following a $\chi^2$ distribution with two degrees of freedom \cite[$\chi^2_2$ hereafter]{woodard1984}.
 The noise properties of $\chi^2_2$ distributed data are multiplicative, and require a specific treatment when fitting a model.
@@
 \begin{equation}
-	\ln p(\mathcal{P} | M) = \sum_{j=0}^{N-1} \left[\ln[M_j(\nu)] + \frac{\mathcal{P}_j}{M_j(\nu)}\right]\, , 
+	\ln p(\mathcal{P} | M(\nu)) = \sum_{j=0}^{N-1} \left[\ln[M_j(\nu)] + \frac{\mathcal{P}_j}{M_j(\nu)}\right]\, , 
 \end{equation}
@@
 
-\subsubsection{Fitting the convective background}\label{sec:background}
+\subsection*{Model preparation and hyperparameter priors}
+\subsubsection*{Fitting the convective background}\label{sec:background}
 Fitting the convective background, apodization and white noise component must be done for the full range of the power spectrum in order to be accurately constrained.
@@
 The parameter components of our background fit are then $\phi_B = \{\log(a), \log(b), \log(c), \log(d), \log(j), \log(k), W, \nu_{\rm nyq}\}$, where the parameters of the Harvey components were sampled in log space.
-The model was fit to the background data using \texttt{PyStan} \cite{vanhoey+2013}, run for 10,000 iterations on each star\footnote{These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work.}.
+The model was fit to the background data using \texttt{PyStan} \cite{vanhoey+2013}, run for 10,000 iterations on each star.
 
-\subsubsection{Obtaining First Guesses and Prior Values}
-In order to utilise some of the prior measurements of our targets without using them as hard constraints on our parameters, some of our model equations were fit to LEGACY and Kages data to obtain first guesses and mean values on hyperparameter priors.
+\subsubsection*{Obtaining First Guesses and Prior Values}
+In order to utilise some of the prior measurements of our targets without using them as hard constraints on our parameters, some of our model equations were fit to LEGACY and `Kages' data to obtain first guesses and mean values on hyperparameter priors.
 
-For first guesses for parameters in the asymptotic expression, we fit Equation \ref{eq:asymptotic}, \textit{not} including the rotational component $m\nu_s$, to the $\ell = (0, 1, 2)$ mode frequencies reported in LEGACY and Kages for each star, using their reported uncertainties.
+For first guesses for parameters in the asymptotic expression, we fit Equation \ref{eq:asymptotic}, \textit{not} including the rotational component $m\nu_s$, to the $\ell = (0, 1, 2)$ mode frequencies reported in LEGACY and `Kages' for each star, using their reported uncertainties.
 This yielded estimates of $\hat{\epsilon}$, $\widehat{\delta\nu}_{01}$, $\widehat{\delta\nu}_{02}$ and $\hat{\alpha}$, where the hat symbol `\, $\widehat{}$\, ' indicates a prior value (e.g.
-$\hat{\nu}_{\rm max}$ is taken from LEGACY or Kages).
-While not precise, as we did not mitigate any perturbations due to acoustic glitches (sudden changes in interior sound speed, which the latent parameter treatment takes care of in the full model), these rough results act as functional first guesses and prior mean values.
+$\hat{\nu}_{\rm max}$ is taken from LEGACY or `Kages').
+While not precise, as we did not mitigate any perturbations due to acoustic glitches, these rough results act as functional first guesses and prior mean values.
 The relation was fit to each star using PyMC3 \cite{salvatier+2016} using 5000 iterations on 4 chains.
@@
 As is noted in Equation \ref{eq:gammagp}, $L$ was fixed to this fit value when fitting our full model to our data.
-For stars in Kages, for which no linewidths were reported, we instead fixed these prior values to $\hat{m} = 1$, $\hat{c} = 0.5$, $\hat{\rho} = 0.1$, and the length scale to $L = 0.3$.
+For stars in `Kages', for which no linewidths were reported, we instead fixed these prior values to $\hat{m} = 1$, $\hat{c} = 0.5$, $\hat{\rho} = 0.1$, and the length scale to $L = 0.3$.
 These values were chosen to reflect those found for the LEGACY stars.
 
-Finally, we obtained prior values for the Gaussian function describing the distribution of mode amplitudes around \numax.
-The mode amplitude of the highest peak in the spectrum was used for the amplitude, which was typically at or near \numax.
+Finally, we obtained prior values for the Gaussian function describing the distribution of mode amplitudes around \numax (Eq.
+\ref{eq:amplitude}).
+The mode amplitude of the highest peak in the spectrum was used for $\hat{A}$, which was typically at or near \numax.
 For the width of the Gaussian we used the empirical function \cite{lund+2017}
@@
 \begin{equation}
-	\hat{w} = 0.25 \times \numax\, .
+	\hat{w} = 0.25 \times \hat{\nu}_{\rm max},\, .
 \end{equation}
@@
 
-\subsubsection{Priors on our Hyperparameters}
-Given our first guesses and measured prior values, we can define the prior probabilities of the hyperparameters on which our model depends. For the mode frequency hyperparameters, these are
+\subsubsection*{Priors on our Hyperparameters}
+Given our first guesses and measured prior values, we can define the prior probabilities of the hyperparameters on which our model depends.
+For the mode frequency hyperparameters (Eq.
+\ref{eq:asymptotic}), these are
 
@@
 
-\noindent where $\ln\mathcal{N}$ represents a log-Normal distribution and $\mathcal{C}_{1/2}$ represents a half-Cauchy distribution, and other symbols are as described above.
+\noindent where $\ln\mathcal{N}$ represents a log-Normal distribution and $\mathcal{C}_{1/2}$ represents a half-Cauchy distribution\footnote{The half-Cauchy distribution ensures the standard deviations do not inflate to large numbers, and is generally well-behaved close to zero in the case of stars with little deviation from Eq.
+\ref{eq:asymptotic} \cite{gelman2006}.}, and other symbols are as described above.
 All three hyperparameters $\sigma_{0,1,2}$ describing the uncertainty on the latent parameters of different angular degree were subject to the same prior.
 
-For the mode linewidths, our hyperparameter priors took the form
+For the mode linewidths (Eq. \ref{eq:gpkernel} and \ref{eq:gpmean}), our hyperparameter priors took the form
 
@@
 
-\noindent where the conventions are the same as above. For our mode amplitudes, they took the form
+\noindent where the conventions are the same as above. For our mode amplitudes (Eq. \ref{eq:amplitude} and \ref{eq:amplitwod}), they took the form
 
@@
 
-\subsubsection{Fitting procedure}
+\subsection*{Fitting procedure}
 Using our prior information and model described above, we fit Equation \ref{eq:model} to our data $\mathcal{P}$, using the likelihood function described in Section \ref{sec:like}.
@@
 An example of our model fit to an asteroseismic power spectrum of 16 Cyg A is shown in Figure \ref{fig:modelfit}.
+
+ \begin{figure*}
+	\centering
+	\includegraphics[width=.99\textwidth]{Images/modelfit.pdf}
+	\caption{A power spectrum constructed from four years of \kepler observations of 16 Cyg A (KIC 12069424).
+Plotted over the top is the model resulting from the fit to the data described in this work.
+The model implements both the mode frequencies, seen on the right hand side of the plot, and the convective background, the effects of which are seen on the left.
+Low frequencies have been cropped out for clarity.
+\textit{Inset}: A zoom in on a radial (right) and quadrupole (left) ($\ell = 0, 2$) pair of modes.
+The quadrupole mode is split into five components by the star's rotation.
+Due to the star's inclination angle with respect to us, two out of five peaks are more distinct.
+The height and spacing of the mode components is a function of the star's rotational splitting ($0.56\, \mu\rm{Hz}$, equivalent to $P = 20.5\, \rm{days}$) and angle of inclination ($45^\circ$).}
+	\label{fig:modelfit}
+\end{figure*}

### 2020-10-01 paper/natastron/paper.tex
Tidied up separate documents

@@
 \graphicspath{{Images/}}
-\usepackage[symbol]{footmisc}
+%\usepackage[symbol]{footmisc}
 
@@
 
-\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) oscillations for each star, of which the latter have significantly lower signal-to noise.
+\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) p mode\footnote{\textit{Pressure} modes, the visible type of oscillation in main sequence stars} oscillations for each star, of which the latter have significantly lower signal-to noise.
 Radial oscillations ($\ell = 0$), which are also visible, do not split.
@@
 
-\input{si.tex}
+\bibliographystyle{naturemag}
+\bibliography{library.bib} %
 
@@
 
-\bibliographystyle{naturemag}
-\bibliography{library.bib} %
-
 \end{document}

### 2020-10-01 paper/natastron/si.tex
Tidied up separate documents

@@
-\clearpage
-\section*{Supplementary Information}
+\documentclass[12pt]{article}
+\setlength{\textwidth}{167mm}
+\setlength{\headsep}{0mm}
+\setlength{\headheight}{0mm}
+\setlength{\textheight}{230mm}
+\setlength{\oddsidemargin}{1.6mm}
+\setlength{\evensidemargin}{1.6mm}
+\setlength{\topmargin}{4.6mm}
 
-\section*{Asteroseismic Model}\label{s:seismo}
+\usepackage{chngcntr}
+\usepackage{xspace}
+\usepackage{graphicx}
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+\usepackage[ ]{hyperref}
+\graphicspath{{Images/}}
+%\usepackage[symbol]{footmisc}
+
+% Astronomical abbreviations (thanks to Dan Huber)
+\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
+\newcommand{\dnu}{\mbox{$\Delta \nu$}\xspace}
+\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
+\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
+\newcommand{\logg}{\mbox{$\log(g)$}\xspace}
+\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
+\newcommand{\msun}{\mbox{$\mathrm{M}_{\odot}$}\xspace}
+\newcommand{\lsun}{\mbox{$\mathrm{L}_{\odot}$}\xspace}
+\newcommand{\mearth}{\mbox{$\mathrm{M}_{\oplus}$}\xspace}
+\newcommand{\rsun}{\mbox{$\mathrm{R}_{\odot}$}\xspace}
+\newcommand{\kepler}{\emph{Kepler}\xspace}
+\newcommand{\tess}{\emph{TESS}\xspace}
+\newcommand{\ktwo}{K2\xspace}
+\newcommand{\gaia}{\emph{Gaia}\xspace}
+
+\begin{document}
+
+\section*{\underline{Supplementary Information}}
+\tableofcontents
+
+\section{Asteroseismic Model}\label{s:seismo}
 In order to extract signatures of stellar rotation from the asteroseismic p mode frequencies, we built a model that simultaneously treats the convective background ($B(\nu)$), the oscillations ($O(\nu)$), and the white noise ($W$), where $\nu$ is frequency \cite{davies+2015}.
@@
 
-\subsection*{Convective Background ($B(\nu)$)}
+\subsection{Convective Background ($B(\nu)$)}
 To model the convective background we used three Harvey components \cite{harvey1985}, which express the background in power as Lorentzian-like functions centered on zero frequency.
@@
 
-\subsection*{Modes of Oscillation ($O(\nu)$)}
+\subsection{Modes of Oscillation ($O(\nu)$)}
 Modes of oscillation appear in the power spectrum as Lorentzian peaks \cite{chaplin+basu2017}.
@@
 
-\subsubsection*{Mode Frequencies and Rotational Splitting ($\nu_{n,\ell,m}$)}\label{ssec:frequencies}
+\subsubsection{Mode Frequencies and Rotational Splitting ($\nu_{n,\ell,m}$)}\label{ssec:frequencies}
 The mode frequencies of main sequence stars are described by the asymptotic expression \cite{tassoul1980, vrard+2016}.
@@
 
-\subsubsection*{Mode Linewidth ($\Gamma_{n,\ell}$)}
+\subsubsection{Mode Linewidth ($\Gamma_{n,\ell}$)}
 The linewidths of asteroseismic p modes vary roughly as a function of mode frequency, and do so slowly relative to \dnu.
@@
 
-\subsubsection*{Mode Heights and Angle of Inclination ($H_{n,\ell,m}$)}
+\subsubsection{Mode Heights and Angle of Inclination ($H_{n,\ell,m}$)}
 The height in power of each mode, $H_{n, \ell, m}$, varies not only as a function of distance in frequency from \numax, but also due to observation conditions, such as inclination angle and passband.
@@
 
-\subsection*{Likelihood Function for $M(\nu)$}\label{sec:like}
+\subsection{Likelihood Function for $M(\nu)$}\label{sec:like}
 If data have Gaussian noise in the time domain, they will appear in the frequency domain with noise following a $\chi^2$ distribution with two degrees of freedom \cite[$\chi^2_2$ hereafter]{woodard1984}.
@@
 
-\subsection*{Model preparation and hyperparameter priors}
-\subsubsection*{Fitting the convective background}\label{sec:background}
+\subsection{Model preparation and hyperparameter priors}
+\subsubsection{Fitting the convective background}\label{sec:background}
 Fitting the convective background, apodization and white noise component must be done for the full range of the power spectrum in order to be accurately constrained.
@@
 
-\subsubsection*{Obtaining First Guesses and Prior Values}
+\subsubsection{Obtaining First Guesses and Prior Values}
 In order to utilise some of the prior measurements of our targets without using them as hard constraints on our parameters, some of our model equations were fit to LEGACY and `Kages' data to obtain first guesses and mean values on hyperparameter priors.
@@
 
-\subsubsection*{Priors on our Hyperparameters}
+\subsubsection{Priors on our Hyperparameters}
 Given our first guesses and measured prior values, we can define the prior probabilities of the hyperparameters on which our model depends.
@@
 
-\subsection*{Fitting procedure}
+ \begin{figure*}
+	\centering
+	\includegraphics[width=.99\textwidth]{Images/modelfit.pdf}
+	\caption{A power spectrum constructed from four years of \kepler observations of 16 Cyg A (KIC 12069424).
+Plotted over the top is the model resulting from the fit to the data described in this work.
+The model implements both the mode frequencies, seen on the right hand side of the plot, and the convective background, the effects of which are seen on the left.
+Low frequencies have been cropped out for clarity.
+\textit{Inset}: A zoom in on a radial (right) and quadrupole (left) ($\ell = 0, 2$) pair of modes.
+The quadrupole mode is split into five components by the star's rotation.
+Due to the star's inclination angle with respect to us, two out of five peaks are more distinct.
+The height and spacing of the mode components is a function of the star's rotational splitting ($0.56\, \mu\rm{Hz}$, equivalent to $P = 20.5\, \rm{days}$) and angle of inclination ($45^\circ$).}
+	\label{fig:modelfit}
+\end{figure*}
+
+\subsection{Fitting procedure}
 Using our prior information and model described above, we fit Equation \ref{eq:model} to our data $\mathcal{P}$, using the likelihood function described in Section \ref{sec:like}.
@@
 
- \begin{figure*}
-	\centering
-	\includegraphics[width=.99\textwidth]{Images/modelfit.pdf}
-	\caption{A power spectrum constructed from four years of \kepler observations of 16 Cyg A (KIC 12069424).
-Plotted over the top is the model resulting from the fit to the data described in this work.
-The model implements both the mode frequencies, seen on the right hand side of the plot, and the convective background, the effects of which are seen on the left.
-Low frequencies have been cropped out for clarity.
-\textit{Inset}: A zoom in on a radial (right) and quadrupole (left) ($\ell = 0, 2$) pair of modes.
-The quadrupole mode is split into five components by the star's rotation.
-Due to the star's inclination angle with respect to us, two out of five peaks are more distinct.
-The height and spacing of the mode components is a function of the star's rotational splitting ($0.56\, \mu\rm{Hz}$, equivalent to $P = 20.5\, \rm{days}$) and angle of inclination ($45^\circ$).}
-	\label{fig:modelfit}
-\end{figure*}
+\bibliographystyle{naturemag}
+\bibliography{library.bib} %
+
+\end{document}

### 2020-10-07 paper/natastron/response/response.tex

\documentclass[11pt]{article}
\usepackage[left=1in, right=1in, bottom=0.5in, top=0.5in]{geometry}
\usepackage{graphicx}
\begin{document}

\section*{Response to the Referees}

To whom it may concern,

First we would like to thank the reviewer for their comments, which have helped us polish up our discussion of biases. The paper has now been re-written to fit the Nature format, and therefore some of the content has changed or moved. The main body of the paper is mostly new or adapted writing, and the Methods contains the more detailed information on data, methods, and discussion. At the end of this document we’ve listed any major changes made, which is duplicated in our cover letter to the editor.

Our responses are below. We’d like to address the bias comment first, as it is the most significant one, and shows up a couple of times in the reviewer’s report. \\

\noindent \textbf{With photometry, rotation is much easier to measure for the stars that are active and faster rotating. Is there a similar bias in the case of seismology? }

In short, yes, there are biases at play, but we don’t think these will affect our results. We’ve discussed them below, and have included a version of this discussion in the \textbf{Methods} section of the new draft.

\textit{Bias in rotation detection:} stars that are rotating very slowly will show very small splittings, which may be indistinguishable from a non-rotating case, whereas stars that are spinning very fast may find that their splitting is so wide that they cross over with split modes at different radial orders. We’ve done some calculations to show that this shouldn’t affect the region of rotation we’re interested in.
\begin{enumerate}
\item \textit{Fast rotating stars}: in principle, a star could rotate fast enough that the highest-frequency peak in a split dipole ($\ell=2$) mode would overlap with the radial ($\ell=0$) mode. This would occur if $2\nu_{\rm{s}} > \delta\nu_{02}$. For the star in our sample with the smallest $\delta\nu_{02}$ (so the highest risk of this happening), this limit is at 8.8 days. However for the star with the largest $\delta\nu_{02}$, this lies at ~2 days.

In practice, we think that the model would properly fit a spectrum where this kind of mode-overlapping was happening. The $\ell=0$ modes don’t split, and so if a $\ell=2$ mode were split so far that overlap was occurring, the $\ell=0$ mode would appear broadened or asymmetrical, which would have no other explanation. There would still be a constraint on the splitting from the lower-frequency peaks. We can envision this being a serious issue if an $\ell=2$ mode is overlapping with an $\ell=1$ mode at lower frequencies as well, however this would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.

In our sample, there are 9 stars for which we measured splittings faster than the limit of $2\nu_s > \delta\nu{02}$. All these stars showed good agreement with previous work, and were well converged, which implies that asteroseismic models such as ours can handle such mode overlap. But as far as our conclusions are concerned, all 9 are either Hot or Subgiant stars, which we show don’t impact our conclusions either way in the paper.

\item \textit{Slow rotating stars:} Below, the reviewer raises concerns that for a limit of $\nu_s < 2\Gamma$ (when the splitting is smaller than the double the linewidth), splitting may not be accurately constrained. We dont believe this is the fundamental limit on this measurement, as splitting instead more frequently causes a broadening of the modes. Detection of this broadening makes it possible to measure seismic rotation even when the split components are not fully separated. We discuss this more below. If there is to be a hard limit at which the broadening of a mode due to splitting can not be measured, we suggest that it is when it would be impossible to resolve it, so where $\nu_s < 2/T$, two times the frequency bin width. The bin width is set by observing time, so to make an conservative estimate, we can take our star with the shortest observing time  (0.49 years). For this star, the limit on measuring rotation would be ~89 days (and going up for longer observing baselines). Of course, as discussed below, as you get to slower rotation rates it becomes harder to constrain the small rate of mode broadening and so the uncertainty will increase. We believe this is dealt with appropriately in our model comparison through the use of hierarchical models.
\end{enumerate}

Hopefully with this discussion we’ve shown that both the slow (hard limit) and fast (soft limit) limits on measuring rotation with asteroseismology shouldn’t affect the analysis driving our conclusions, which is done by stars between 10 and 40 days. We’ve added a plot below which should help illustrate our arguments. The circles represent stars in our sample, coloured by their seismic rotation.\\

\includegraphics[width=\textwidth]{image1.png}

\textit{Bias in stellar populations:} The reviewer/reader might be concerned there is a second potential observational bias in that asteroseismology does not detect stars in the 6200-5800 Kelvin range in the latter half of their main sequence lifetime, and is therefore only detecting younger, faster rotators. This concern is more easily alleviated. The probability of an asteroseismic detection scales with temperature and radius (i.e. scales inversely with log g, and therefore age on the main sequence). More active, magnetic stars may also suppress their oscillation modes, meaning that it is actually more likely to detect seismic oscillations in older stars.  Because of both these effects asteroseismic detection probabilities are slightly biased towards older stars on the main sequence, not younger. See e.g. Chaplin et al. (2011), Schofield et al. (2019) for Kepler and TESS respectively, and Mathur et al. 2019 for the magnetic suppression.

Between these two statements -- that our method measures accurate rotation in the regions that matter, and that asteroseismology is biased towards older, not younger, stars -- we don’t believe that observing biases affect our conclusions. We’ve included a paraphrased version of the discussion as above in the paper \textbf{Methods} Section 3.4. \\

\noindent\textbf{The significance of the results, would be much stronger if:
\begin{itemize}
\item it could be shown that there is no observational bias
associated with the seismic data and 
\item if a range of rotation evolution models were considered, not just one model with and without weakened breaking.
\end{itemize}
}
With regards to the observational bias, we don’t believe this is an issue (see our response above), and have tried to make this clearer in the paper.

With regards to the rotation models: we agree, which is why we want to explore this option in a future paper, as mentioned in the conclusions. It is our opinion that performing this comparison in a separate work would be more appropriate. The two models we use to compare to our data in this work have already been used in the past to forward-model the Kepler field (see van Saders et al. (2019)), so their inclusion here is straightforward. It is also worth pointing out that most rotation models without weakened magnetic braking will have pretty similar predictions in this regime our sample occupies anyway, as they are all calibrated to reproduce the Sun (and at younger ages, clusters), and so the largest difference between models will come from the inclusion of a change in the braking law. It’s not that we think that such a comparison isn’t important -- on the contrary -- but we think it should be explored in a separate paper with more of a focus on the differences in theoretical models, and including a much broader range of models both with- and without changes to the braking.

We’ve tried to be careful throughout and reiterate that this is only a comparison of two models, so that there isn’t any confusion for the readers.\\

\noindent\textbf{One may fear that seismology works only for $\nu_s / \Gamma$ large (ratio of rotational splitting to mode line width, not provided). 
\begin{itemize}
\item How many stars have $\nu_s /  \Gamma < 2$ here (the problematic cases)?
\item How many of these are slow rotators? 
\end{itemize}
}

That seismic rotation can only be probed in cases where split components are fully separated from one another, as the reviewer is suggesting, is a common misconception. Asteroseismic splitting is rarely larger than double the linewidth (in our sample this is only the case for a handful of the fastest rotators). Instead, rotational splitting is visible as a broadening of the modes, which take a specific form depending on the angular degree of the mode and the inclination angle of the star. This is why marginalising over inclination angle is important, because only by constructing a model that accounts for inclination angle and rotation together can you accurately represent how rotation affects the modes.

It is also worth noting that our fitting method marginalises over inclination angle, rotational splitting and linewidth, and so the final rotational period measurements have uncertainties that accurately reflect the uncertainty associated with the slow rotation only having a small effect on the broadening of the modes of oscillation. To be clear, there is no boundary beyond which this methodology of measuring asteroseismic rotation no longer works, until you start pushing up against the frequency resolution of the power spectrum (as discussed above).

As discussed at the top of this response, the reviewer may be concerned that Figure 3 (Figure 5 in the old draft) shows  a number of slow rotators that were not included in the model comparison, because they had poor convergence metrics. It is indeed harder to measure rotation in slow rotators (as mentioned above), and so fewer of these stars were able to converge within the computational time we had available. When we repeated the model comparison analysis while still including these stars, our conclusions did not change, a statement which we have now included in the paper.\\

\noindent\textbf{Does the seismic catalog contain enough accurate measurements for the slow rotating stars?}

We believe that we do have enough accurate measurements for the slow rotating stars, in this case referring to those with periods of roughly 20 days and up. \textbf{Extended Data} Figures 3 and 4 (Figures 7 and 8 in the old draft) show that stars in this regime appear to be consistent with with previous measurements of rotation where those are available. Based on these comparisons to external data, we think the accuracy is sufficient.\\

\noindent\textbf{Is the apparent deficit of slow rotators in the catalog due to weakened magnetic braking or to observational biases? Figure 9 [\textbf{Extended Data} Figure 5 in the new draft] left is not reassuring.}

As discussed above, we believe there is sufficient ground to claim that our deficit of slow rotators is due to weakened magnetic braking and not observational biases in seismology. With regards to \textbf{Extended Data} Figure 5 (Figure 9 in the old draft), as discussed in the text, the disagreements below $5\,  \rm{kms}^{-1}$ are within the expected deviation between seismic and spectroscopic comparisons in this region (Tayar et al. 2015). We’ve added a line to indicate the border of this region. In addition, the majority of slowly rotating stars in the Figure lie above the 1:1 line, implying that if spectroscopic values were the truth, seismology would find rotation rates that are *slower* than the truth, which would bias our results towards a standard model, and not towards weakened magnetic braking.

The spectroscopy comparison is there for completeness, but in our opinion the more important test is the comparison to surface rotation rates (Figure 2 in the new draft), which shows good agreement. A paraphrased version of this answer is now included in the text in \textbf{Methods} Section 3.3.\\

\noindent \textbf{The stellar inclination angle i is clearly not measured, as shown in figure 6-middle [\textbf{Extended Data} Figure 2 in the new draft]. Therefore the stellar rotation rate itself is not determined for individual stars. Is this not a problem for the interpretation of the data in terms of rotation evolution models, esp. toward the slow-rotator end of the distribution?}

We strongly disagree, and so hopefully we can convince the reviewer. The purpose of \textbf{Extended Data} Figure 2 (Figure 6 in the old draft) is to check whether our inclination angle returns the prior, which it doesn’t in the majority of cases. Even in the cases where it does closely resemble the prior, our Bayesian approach will ensure that this is properly reflected in the results for rotation period. In our analysis, rotational splitting ($\nu_{s}\sin(i)$), inclination ($i$) and rotation ($P$) are all marginalised over, and so the uncertainties reflect the posterior probability distribution these values can take given the data. Because of this, the uncertainties on rotation visible in the Figure have already accurately incorporated the uncertainty in the inclination angle. We have added extra description to the figure caption that clarifies this. We would say that the stellar rotation rate is well determined for individual stars in spite of the difficulties with constraining inclination angle, because it has been fully marginalised over in our Bayesian analysis.

If I’m interpreting the reviewer’s report correctly, we understand that they are concerned that there are fewer slowly rotating stars, and that those that are slowly rotating appear to have large uncertainties. There are relatively few stars in this slowly rotating regime, and we address this in the comments about observational bias above. We don’t think the larger uncertainties should raise concern. The latent variable model we use to compare the two rotational evolution models allowed us to incorporate the uncertainties appropriately, and bear in mind that it’s not just rotation space where the models are compared, but mass, metallicity, temperature, and age as well.\\

\noindent\textbf{ Two rotation evolution models are tested against each other. One model is favoured (more likely than the other). However, it is not clear how good is this model, i.e. whether it fits the data. In particular, it is not clear whether the data really favour a transition model and not another spin-down model (e.g., Matt et al. 2015).}

Our model is based on the Matt formalism, although our choices of scalings for stellar loss and magnetism are different (see van Saders et al. 2019), and so our models are more similar to the Matt models than other models available in the literature (see Fig 1 in Matt et al. 2015)

The Matt et al. 2015 model and associated paper puzzled over the fact that the apparent edge of the period distribution in the McQuillan sample was at roughly the solar age in their model (see fig 3 in Matt 2015), and wondered whether it meant the age distribution in the Kepler field was very different (younger) than expected. Their 4 Gyr model is already at the McQuillan period distribution edge. Their model would have predicted the same long rotation periods as our standard model, with differences in detail because of the different braking law scalings. In other words: a 8-9 Gyr star in the Matt model would not be sitting on that McQuillan edge, it would be above it.

Of course, there are still other models of rotational evolution worth comparing to. Comparing our seismic rotation sample to different models (both with- and without magnetic braking present) is an important next step for this research, but not one we feel belongs in this paper. With this study, we’re really focused on repeating the research that first proposed weakened magnetic braking (van Saders et al. 2016) with the improved seismic sample that includes rotation.\\

\noindent\textbf{The authors may consider making a plot like Figure 2 from van Saders et al. 2016, i.e. ratio of $P_{\rm obs}/P_{\rm predicted}$ versus age. The advantage for plotting the ratio is that it is easier to see whether there is a transition in the data (less impact from the systematic biases in the models).}

We considered including such a plot in our paper, but omitted it for specific reasons, which we can hopefully convince the referee of.

Most importantly, we don’t believe that such a plot would provide any new information beyond what is already included in the paper. The core of this paper is the use of a probabilistic analysis of a full ensemble of stars to distinguish between two competing models. We believe that a plot that shows that \textit{individual} stars are in \textit{disagreement} with a standard evolution doesn’t add any new information, especially when the format requires conciseness (and the discrepancy already been demonstrated in previous work for many stars in this sample). We think it is more important to tread new ground with a Bayesian method that accounts for multiple parameter spaces (metallicity being the most important one), to drive our conclusions.

A $P_{\rm obs}/P_{\rm predicted}$  plot would also require us to either model the rotation of individual stars, or delve into empirical gyrochronology, both of which are outside the scope of this paper in its current form, and are better explored in separate work.\\

\noindent\textbf{ Does TRILEGAL correctly synthesize the stellar population? Any free parameters?}

To the best of our knowledge the TRILEGAL simulation is appropriate for this purpose, and any issues that may arise through the use of TRILEGAL are also mitigated by our treatment in the paper--- drawing from TRILEGAL simulated stars until they match the distributions seen by Berger et al. (2020) in the Kepler field. As for the parameters, our TRILEGAL simulation is the same as that used for van Saders et al. (2019), and is using the standard values from Girardi et al. (2005), as described in both those papers (this was wrongly cited as Girardi et al. 2015 in the first draft, and has since been corrected). \\

\noindent\textbf{ Should the paper be published, I would suggest to move most of the asteroseismology details to an appendix at the end of the paper (the asteroseismic analysis is mostly standard). Even though these details are important, the reader should not be diverted from the main topic of the paper, ie the discussion about the rotation evolution models.
Some sections, for example 3.1.4, contain a lot of jargon and are hard to follow even for a specialist. }

There’s been quite a bit of a reshuffle between drafts here to match the Nature Astronomy style. Section 3.1 (the asteroseismic methods) is now in \textbf{Supplementary Information}, which has improved the flow a lot. The Gyrochronology methods and the majority of the discussion are now in \textbf{Methods}, so the core body of the paper is a lot more streamlined.

When transferring the methods to the Supplementary Information, we have tried to improve the explanations of the more complicated terms (such as Gaussian Processes), and have hopefully improved this somewhat.

\clearpage
\section*{Changes to the manuscript}
\subsection*{Structural Changes}
There has been a major structural overhaul of the manuscript to help it comply with the Nature Astronomy guidelines.

\begin{itemize}
	\item The detailed sections of Section 2: Data have been moved to \textbf{Methods}.
	\item Section 3.1: Asteroseismic Model has been moved to \textbf{Supplementary Data}.
	\item Section 3.2: Distinguishing between Gyrochronology Models has been moved to \textbf{Methods}
	\item Portions of the \textit{Fitting Procedure} components of both Model sections are now included in the \textbf{Methods} section.
	\item The detailed sections of Section 4: Results have been moved to \textbf{Methods}.
	\item Table 1 is has been moved to \textbf{Extended Data}.
	\item Section 5.1.1., 5.1.2., and the spectroscopy half of 5.1.3. have all been moved to \textbf{Methods}. Their conclusions are mentioned in the main text.
	\item Section 5.2.2, 5.2.3. and 5.2.4. have all been moved to \textbf{Methods.} Their conclusions are mentioned in the main text.
	\item Figures 3, 6, 7, 8 and 9 have been moved to \textbf{Extended Data} and are referenced from \textbf{Methods}.
	\item Figure 2 has been moved to \textbf{Supplementary Information}.
\end{itemize}

\subsection*{Content Changes}
The main body of the text (pages 2 through 10) is either new or paraphrased from sections of the previous manuscript. We have tried to retain the same contents and citations as in the previous manuscript, to avoid the need for in-depth review of this section of the paper.

Other changes include:
\begin{itemize}
	\item Figure captions have been updated with extra descriptions to match the Nature Astronomy requirements.
	\item \textbf{Methods} Section 1.2 is a new section that briefly describes the mode frequency fitting process without much detail (which is available in the \textbf{Supplementary Information})
	\item Added a paragraph to \textbf{Methods} Section 3.3. (spectroscopic rotation comparison) going into a little more depth about what the discrepancy between these methods means for our conclusions.
	\item Added a line indicating the 5 km/s boundary to \textbf{Extended Data} Figure 5.
	\item Added \textbf{Methods} Section 3.4, which covers asteroseismic detection biases.
	\item Refactored the headings describing the asteroseismic method in \textbf{Supplementary Information} to make the flow clearer.
	\item Expanded the explanation of Gaussian Processes in \textbf{Supplementary Information} Section 1.2.2.
\end{itemize}

\end{document}

### 2020-10-07 paper/natastron/bblmethods.tex

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{m_handberg+lund2014}
\bibinfo{author}{Handberg, R.} \& \bibinfo{author}{Lund, M.~N.}
\newblock \bibinfo{title}{Automated preparation of {{Kepler}} time series of
  planet hosts for asteroseismic analysis}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{445}}, \bibinfo{pages}{2698--2709}
  (\bibinfo{year}{2014}).

\bibitem{m_garcia+2011}
\bibinfo{author}{Garc{\'i}a, R.~A.} \emph{et~al.}
\newblock \bibinfo{title}{Preparation of {{Kepler}} light curves for
  asteroseismic analyses}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{414}}, \bibinfo{pages}{L6--L10}
  (\bibinfo{year}{2011}).

\bibitem{m_silvaaguirre+2015}
\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
\newblock \bibinfo{title}{Ages and fundamental properties of {{Kepler}}
  exoplanet host stars from asteroseismology}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2127}
  (\bibinfo{year}{2015}).

\bibitem{m_silvaaguirre+2017}
\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
  {{Kepler Asteroseismic LEGACY Sample}}. {{II}}.{{Radii}}, {{Masses}}, and
  {{Ages}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{173} (\bibinfo{year}{2017}).

\bibitem{m_christensen-dalsgaard2008}
\bibinfo{author}{{Christensen-Dalsgaard}, J.}
\newblock \bibinfo{title}{{{ASTEC}}\textemdash the {{Aarhus STellar Evolution
  Code}}}.
\newblock \emph{\bibinfo{journal}{Astrophysics and Space Science}}
  \textbf{\bibinfo{volume}{316}}, \bibinfo{pages}{13} (\bibinfo{year}{2008}).

\bibitem{m_huber+2013a}
\bibinfo{author}{Huber, D.} \emph{et~al.}
\newblock \bibinfo{title}{Stellar {{Spin}}-{{Orbit Misalignment}} in a
  {{Multiplanet System}}}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{342}},
  \bibinfo{pages}{331} (\bibinfo{year}{2013}).

\bibitem{m_buchhave+latham2015}
\bibinfo{author}{Buchhave, L.~A.} \& \bibinfo{author}{Latham, D.~W.}
\newblock \bibinfo{title}{The {{Metallicities}} of {{Stars}} with and without
  {{Transiting Planets}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{808}}, \bibinfo{pages}{187} (\bibinfo{year}{2015}).

\bibitem{m_astropycollaboration+2013}
\bibinfo{author}{{Astropy Collaboration}} \emph{et~al.}
\newblock \bibinfo{title}{Astropy: {{A}} community {{Python}} package for
  astronomy}.
\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{558}}, \bibinfo{pages}{A33} (\bibinfo{year}{2013}).

\bibitem{m_astropycollaboration+2018}
\bibinfo{author}{{Astropy Collaboration}} \emph{et~al.}
\newblock \bibinfo{title}{The {{Astropy Project}}: {{Building}} an
  {{Open}}-science {{Project}} and {{Status}} of the v2.0 {{Core Package}}}.
\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
  \textbf{\bibinfo{volume}{156}}, \bibinfo{pages}{123} (\bibinfo{year}{2018}).

\bibitem{m_ginsburg+2019}
\bibinfo{author}{Ginsburg, A.} \emph{et~al.}
\newblock \bibinfo{title}{Astroquery: {{An Astronomical Web}}-querying
  {{Package}} in {{Python}}}.
\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
  \textbf{\bibinfo{volume}{157}}, \bibinfo{pages}{98} (\bibinfo{year}{2019}).

\bibitem{m_mckinney2010}
\bibinfo{author}{McKinney, W.}
\newblock \bibinfo{title}{Data {{Structures}} for {{Statistical Computing}} in
  {{Python}}}.
\newblock In \emph{\bibinfo{booktitle}{Proceedings of the 9th {{Python}} in
  {{Science Conference}}}}, \bibinfo{pages}{51--56} (\bibinfo{year}{2010}).

\bibitem{m_davies+2015}
\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
\newblock \bibinfo{title}{Asteroseismic inference on rotation, gyrochronology
  and planetary system dynamics of 16 {{Cygni}}}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959}
  (\bibinfo{year}{2015}).

\bibitem{m_harvey1985}
\bibinfo{author}{Harvey, J.}
\newblock \bibinfo{title}{High-{{Resolution Helioseismology}}}.
\newblock \emph{\bibinfo{journal}{Future Missions in Solar, Heliospheric \&
  Space Plasma Physics}} \textbf{\bibinfo{volume}{235}}, \bibinfo{pages}{199}
  (\bibinfo{year}{1985}).

\bibitem{m_tassoul1980}
\bibinfo{author}{Tassoul, M.}
\newblock \bibinfo{title}{Asymptotic approximations for stellar nonradial
  pulsations}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
  \textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{469} (\bibinfo{year}{1980}).

\bibitem{m_vrard+2016}
\bibinfo{author}{Vrard, M.}, \bibinfo{author}{Mosser, B.} \&
  \bibinfo{author}{Samadi, R.}
\newblock \bibinfo{title}{Period spacings in red giants. {{II}}. {{Automated}}
  measurement}.
\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{588}}, \bibinfo{pages}{A87} (\bibinfo{year}{2016}).

\bibitem{m_hogg+2010}
\bibinfo{author}{Hogg, D.~W.}, \bibinfo{author}{Bovy, J.} \&
  \bibinfo{author}{Lang, D.}
\newblock \bibinfo{title}{Data analysis recipes: {{Fitting}} a model to data}.
\newblock \emph{\bibinfo{journal}{ArXiv e-prints}}
  \bibinfo{pages}{arXiv:1008.4686} (\bibinfo{year}{2010}).

\bibitem{m_hall+2019}
\bibinfo{author}{Hall, O.~J.} \emph{et~al.}
\newblock \bibinfo{title}{Testing asteroseismology with {{Gaia DR2}}:
  {{Hierarchical}} models of the {{Red Clump}}}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{3569--3585}
  (\bibinfo{year}{2019}).
\newblock \eprint{1904.07919}.

\bibitem{m_mazumdar+2014}
\bibinfo{author}{Mazumdar, A.} \emph{et~al.}
\newblock \bibinfo{title}{Measurement of acoustic glitches in solar-type stars
  from oscillation frequencies observed by {{Kepler}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{782}}, \bibinfo{pages}{18} (\bibinfo{year}{2014}).
\newblock \eprint{1312.4907}.

\bibitem{m_chaplin+basu2017}
\bibinfo{author}{Chaplin, W.~J.} \& \bibinfo{author}{Basu}.
\newblock \emph{\bibinfo{title}{Asteroseismic {{Data Analysis}}:
  {{Foundations}} and {{Techniques}}}} (\bibinfo{publisher}{{Princeton
  University Press}}, \bibinfo{address}{{Princeton, New Jersey}},
  \bibinfo{year}{2017}), \bibinfo{edition}{1st} edn.

\bibitem{m_vanhoey+2013}
\bibinfo{author}{Van~Hoey, S.}, \bibinfo{author}{{van der Kwast}, J.},
  \bibinfo{author}{Nopens, I.} \& \bibinfo{author}{Seuntjens, P.}
\newblock \bibinfo{title}{Python package for model {{STructure ANalysis}}
  ({{pySTAN}})}.
\newblock \emph{\bibinfo{journal}{EGU General Assembly Conference Abstracts}}
  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{EGU2013--10059}
  (\bibinfo{year}{2013}).

\bibitem{m_carpenter+2017}
\bibinfo{author}{Carpenter, B.} \emph{et~al.}
\newblock \bibinfo{title}{Stan: {{A Probabilistic Programming Language}}}.
\newblock \emph{\bibinfo{journal}{Journal of Statistical Software}}
  \textbf{\bibinfo{volume}{76}}, \bibinfo{pages}{1--32} (\bibinfo{year}{2017}).

\bibitem{m_vanderwalt+2011}
\bibinfo{author}{{van der Walt}, S.}, \bibinfo{author}{Colbert, S.~C.} \&
  \bibinfo{author}{Varoquaux, G.}
\newblock \bibinfo{title}{The {{NumPy Array}}: {{A Structure}} for {{Efficient
  Numerical Computation}}}.
\newblock \emph{\bibinfo{journal}{Computing in Science and Engineering}}
  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{22--30}
  (\bibinfo{year}{2011}).

\bibitem{m_salvatier+2016}
\bibinfo{author}{Salvatier, J.}, \bibinfo{author}{Wiecki, T.~V.} \&
  \bibinfo{author}{Fonnesbeck, C.}
\newblock \bibinfo{title}{Probabilistic programming in {{Python}} using
  {{PyMC3}}}.
\newblock \emph{\bibinfo{journal}{PeerJ Computer Science}}
  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{e55} (\bibinfo{year}{2016}).

\bibitem{m_thetheanodevelopmentteam+2016}
\bibinfo{author}{{The Theano Development Team}} \emph{et~al.}
\newblock \bibinfo{title}{Theano: {{A Python}} framework for fast computation
  of mathematical expressions}.
\newblock \emph{\bibinfo{journal}{arXiv:1605.02688 [cs]}}
  (\bibinfo{year}{2016}).
\newblock \eprint{1605.02688}.

\bibitem{m_gelman+rubin1992}
\bibinfo{author}{Gelman, A.} \& \bibinfo{author}{Rubin, D.~B.}
\newblock \bibinfo{title}{Inference from {{Iterative Simulation Using Multiple
  Sequences}}}.
\newblock \emph{\bibinfo{journal}{Statistical Science}}
  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{457--472}
  (\bibinfo{year}{1992}).

\bibitem{m_vansaders+pinsonneault2013}
\bibinfo{author}{{van Saders}, J.~L.} \& \bibinfo{author}{Pinsonneault, M.~H.}
\newblock \bibinfo{title}{Fast {{Star}}, {{Slow Star}}; {{Old Star}}, {{Young
  Star}}: {{Subgiant Rotation}} as a {{Population}} and {{Stellar Physics
  Diagnostic}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{776}}, \bibinfo{pages}{67} (\bibinfo{year}{2013}).

\bibitem{m_vansaders+2016}
\bibinfo{author}{{van Saders}, J.~L.} \emph{et~al.}
\newblock \bibinfo{title}{Weakened magnetic braking as the origin of
  anomalously rapid rotation in old field stars}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{529}},
  \bibinfo{pages}{181} (\bibinfo{year}{2016}).

\bibitem{m_vansaders+2019}
\bibinfo{author}{{van Saders}, J.~L.}, \bibinfo{author}{Pinsonneault, M.~H.} \&
  \bibinfo{author}{Barbieri, M.}
\newblock \bibinfo{title}{Forward {{Modeling}} of the {{Kepler Stellar Rotation
  Period Distribution}}: {{Interpreting Periods}} from {{Mixed}} and {{Biased
  Stellar Populations}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{872}}, \bibinfo{pages}{128} (\bibinfo{year}{2019}).

\bibitem{m_girardi+2012}
\bibinfo{author}{Girardi, L.} \emph{et~al.}
\newblock \bibinfo{title}{{{TRILEGAL}}, a {{TRIdimensional modeL}} of {{thE
  GALaxy}}: {{Status}} and {{Future}}}.
\newblock \emph{\bibinfo{journal}{Astrophysics and Space Science Proceedings}}
  \textbf{\bibinfo{volume}{26}}, \bibinfo{pages}{165} (\bibinfo{year}{2012}).

\bibitem{m_berger+2020}
\bibinfo{author}{Berger, T.~A.} \emph{et~al.}
\newblock \bibinfo{title}{The \${{Gaia}}\$-\${{Kepler}}\$ {{Stellar Properties
  Catalog I}}: {{Homogeneous Fundamental Properties}} for 186,000
  \${{Kepler}}\$ {{Stars}}}.
\newblock \emph{\bibinfo{journal}{arXiv:2001.07737 [astro-ph]}}
  (\bibinfo{year}{2020}).
\newblock \eprint{2001.07737}.

\bibitem{m_gaiacollaboration+2018}
\bibinfo{author}{{Gaia Collaboration}} \emph{et~al.}
\newblock \bibinfo{title}{Gaia {{Data Release}} 2. {{Summary}} of the contents
  and survey properties}.
\newblock \emph{\bibinfo{journal}{ArXiv e-prints}}
  \bibinfo{pages}{arXiv:1804.09365} (\bibinfo{year}{2018}).

\bibitem{m_raghavan+2010}
\bibinfo{author}{Raghavan, D.} \emph{et~al.}
\newblock \bibinfo{title}{A {{Survey}} of {{Stellar Families}}:
  {{Multiplicity}} of {{Solar}}-type {{Stars}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
  \textbf{\bibinfo{volume}{190}}, \bibinfo{pages}{1--42}
  (\bibinfo{year}{2010}).

\bibitem{m_chaplin+2011}
\bibinfo{author}{Chaplin, W.~J.} \emph{et~al.}
\newblock \bibinfo{title}{Ensemble {{Asteroseismology}} of {{Solar}}-{{Type
  Stars}} with the {{NASA Kepler Mission}}}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{332}},
  \bibinfo{pages}{213} (\bibinfo{year}{2011}).

\bibitem{m_seabold+perktold2010}
\bibinfo{author}{Seabold, S.} \& \bibinfo{author}{Perktold, J.}
\newblock \bibinfo{title}{Statsmodels: {{Econometric}} and {{Statistical
  Modeling}} with {{Python}}} \bibinfo{pages}{5} (\bibinfo{year}{2010}).

\bibitem{m_betancourt+girolami2013}
\bibinfo{author}{Betancourt, M.~J.} \& \bibinfo{author}{Girolami, M.}
\newblock \bibinfo{title}{Hamiltonian {{Monte Carlo}} for {{Hierarchical
  Models}}}.
\newblock \emph{\bibinfo{journal}{arXiv:1312.0906 [stat]}}
  (\bibinfo{year}{2013}).
\newblock \eprint{1312.0906}.

\bibitem{m_foreman-mackey+2013}
\bibinfo{author}{{Foreman-Mackey}, D.}, \bibinfo{author}{Hogg, D.~W.},
  \bibinfo{author}{Lang, D.} \& \bibinfo{author}{Goodman, J.}
\newblock \bibinfo{title}{Emcee: {{The MCMC Hammer}}}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{125}}, \bibinfo{pages}{306--312}
  (\bibinfo{year}{2013}).
\newblock \eprint{1202.3665}.

\bibitem{m_foreman-mackey2016}
\bibinfo{author}{{Foreman-Mackey}, D.}
\newblock \bibinfo{title}{Corner.py: {{Scatterplot}} matrices in {{Python}}}.
\newblock \emph{\bibinfo{journal}{The Journal of Open Source Software}}
  \textbf{\bibinfo{volume}{1}} (\bibinfo{year}{2016}).

\bibitem{m_nielsen+2015}
\bibinfo{author}{Nielsen, M.~B.}, \bibinfo{author}{Schunker, H.},
  \bibinfo{author}{Gizon, L.} \& \bibinfo{author}{Ball, W.~H.}
\newblock \bibinfo{title}{Constraining differential rotation of {{Sun}}-like
  stars from asteroseismic and starspot rotation periods}.
\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{582}}, \bibinfo{pages}{A10} (\bibinfo{year}{2015}).

\bibitem{m_benomar+2018}
\bibinfo{author}{Benomar, O.} \emph{et~al.}
\newblock \bibinfo{title}{Asteroseismic detection of latitudinal differential
  rotation in 13 {{Sun}}-like stars}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{361}},
  \bibinfo{pages}{1231} (\bibinfo{year}{2018}).

\bibitem{m_beck2000}
\bibinfo{author}{Beck, J.~G.}
\newblock \bibinfo{title}{A comparison of differential rotation measurements -
  ({{Invited Review}})}.
\newblock \emph{\bibinfo{journal}{Solar Physics}}
  \textbf{\bibinfo{volume}{191}}, \bibinfo{pages}{47--70}
  (\bibinfo{year}{2000}).

\bibitem{m_benomar+2015}
\bibinfo{author}{Benomar, O.}, \bibinfo{author}{Takata, M.},
  \bibinfo{author}{Shibahashi, H.}, \bibinfo{author}{Ceillier, T.} \&
  \bibinfo{author}{Garc{\'i}a, R.~A.}
\newblock \bibinfo{title}{Nearly uniform internal rotation of solar-like
  main-sequence stars revealed by space-based asteroseismology and
  spectroscopic measurements}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2654--2674}
  (\bibinfo{year}{2015}).

\bibitem{m_doyle+2014}
\bibinfo{author}{Doyle, A.~P.}, \bibinfo{author}{Davies, G.~R.},
  \bibinfo{author}{Smalley, B.}, \bibinfo{author}{Chaplin, W.~J.} \&
  \bibinfo{author}{Elsworth, Y.}
\newblock \bibinfo{title}{Determining stellar macroturbulence using
  asteroseismic rotational velocities from {{Kepler}}}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{444}}, \bibinfo{pages}{3592--3602}
  (\bibinfo{year}{2014}).

\bibitem{m_tayar+2015}
\bibinfo{author}{Tayar, J.} \emph{et~al.}
\newblock \bibinfo{title}{Rapid {{Rotation}} of {{Low}}-mass {{Red Giants Using
  APOKASC}}: {{A Measure}} of {{Interaction Rates}} on the
  {{Post}}-main-sequence}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{807}}, \bibinfo{pages}{82} (\bibinfo{year}{2015}).

\bibitem{m_schofield+2019}
\bibinfo{author}{Schofield, M.} \emph{et~al.}
\newblock \bibinfo{title}{The {{Asteroseismic Target List}} for {{Solar}}-like
  {{Oscillators Observed}} in 2 minute {{Cadence}} with the {{Transiting
  Exoplanet Survey Satellite}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
  \textbf{\bibinfo{volume}{241}}, \bibinfo{pages}{12} (\bibinfo{year}{2019}).

\bibitem{m_mathur+2019}
\bibinfo{author}{{Mathur}, S.} \emph{et~al.}
\newblock \bibinfo{title}{{Revisiting the impact of stellar magnetic activity
  on the detection of solar-like oscillations by Kepler}}.
\newblock \emph{\bibinfo{journal}{Frontiers in Astronomy and Space Sciences}}
  \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{46} (\bibinfo{year}{2019}).
\newblock \eprint{1907.01415}.

\bibitem{m_amard+matt2020}
\bibinfo{author}{Amard, L.} \& \bibinfo{author}{Matt, S.~P.}
\newblock \bibinfo{title}{The {{Impact}} of {{Metallicity}} on the
  {{Evolution}} of {{Rotation}} and {{Magnetic Activity}} of {{Sun}}-{{Like
  Stars}}}.
\newblock \emph{\bibinfo{journal}{arXiv:2001.10404 [astro-ph]}}
  (\bibinfo{year}{2020}).
\newblock \eprint{2001.10404}.

\bibitem{m_matt+2015}
\bibinfo{author}{Matt, S.~P.}, \bibinfo{author}{Brun, A.~S.},
  \bibinfo{author}{Baraffe, I.}, \bibinfo{author}{Bouvier, J.} \&
  \bibinfo{author}{Chabrier, G.}
\newblock \bibinfo{title}{The {{Mass}}-dependence of {{Angular Momentum
  Evolution}} in {{Sun}}-like {{Stars}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{799}}, \bibinfo{pages}{L23} (\bibinfo{year}{2015}).

\bibitem{m_leiner+2019}
\bibinfo{author}{Leiner, E.}, \bibinfo{author}{Mathieu, R.~D.},
  \bibinfo{author}{Vanderburg, A.}, \bibinfo{author}{Gosnell, N.~M.} \&
  \bibinfo{author}{Smith, J.~C.}
\newblock \bibinfo{title}{Blue {{Lurkers}}: {{Hidden Blue Stragglers}} on the
  {{M67 Main Sequence Identified}} from {{Their Kepler}}/{{K2 Rotation
  Periods}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{881}}, \bibinfo{pages}{47} (\bibinfo{year}{2019}).

\bibitem{m_fleming+2019}
\bibinfo{author}{Fleming, D.~P.}, \bibinfo{author}{Barnes, R.},
  \bibinfo{author}{Davenport, J. R.~A.} \& \bibinfo{author}{Luger, R.}
\newblock \bibinfo{title}{Rotation {{Period Evolution}} in {{Low}}-mass
  {{Binary Stars}}: {{The Impact}} of {{Tidal Torques}} and {{Magnetic
  Braking}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{881}}, \bibinfo{pages}{88} (\bibinfo{year}{2019}).

\bibitem{m_maxted+2015}
\bibinfo{author}{Maxted, P. F.~L.}, \bibinfo{author}{Serenelli, A.~M.} \&
  \bibinfo{author}{Southworth, J.}
\newblock \bibinfo{title}{Comparison of gyrochronological and isochronal age
  estimates for transiting exoplanet host stars}.
\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{577}}, \bibinfo{pages}{A90} (\bibinfo{year}{2015}).

\bibitem{m_gallet+delorme2019}
\bibinfo{author}{Gallet, F.} \& \bibinfo{author}{Delorme, P.}
\newblock \bibinfo{title}{Star-planet tidal interaction and the limits of
  gyrochronology}.
\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
  \textbf{\bibinfo{volume}{1905}}, \bibinfo{pages}{arXiv:1905.06070}
  (\bibinfo{year}{2019}).

\bibitem{m_benbakoura+2019}
\bibinfo{author}{Benbakoura, M.}, \bibinfo{author}{R{\'e}ville, V.},
  \bibinfo{author}{Brun, A.~S.}, \bibinfo{author}{{Le Poncin-Lafitte}, C.} \&
  \bibinfo{author}{Mathis, S.}
\newblock \bibinfo{title}{Evolution of star-planet systems under magnetic
  braking and tidal interaction}.
\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{621}}, \bibinfo{pages}{A124} (\bibinfo{year}{2019}).

\bibitem{m_ceillier+2016}
\bibinfo{author}{Ceillier, T.} \emph{et~al.}
\newblock \bibinfo{title}{Rotation periods and seismic ages of {{KOIs}} -
  comparison with stars without detected planets from {{Kepler}} observations}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{119--125}
  (\bibinfo{year}{2016}).

\end{thebibliography}

### 2020-10-07 paper/natastron/bblpaper.tex

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{vansaders+pinsonneault2013}
\bibinfo{author}{{van Saders}, J.~L.} \& \bibinfo{author}{Pinsonneault, M.~H.}
\newblock \bibinfo{title}{Fast {{Star}}, {{Slow Star}}; {{Old Star}}, {{Young
  Star}}: {{Subgiant Rotation}} as a {{Population}} and {{Stellar Physics
  Diagnostic}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{776}}, \bibinfo{pages}{67} (\bibinfo{year}{2013}).

\bibitem{vansaders+2016}
\bibinfo{author}{{van Saders}, J.~L.} \emph{et~al.}
\newblock \bibinfo{title}{Weakened magnetic braking as the origin of
  anomalously rapid rotation in old field stars}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{529}},
  \bibinfo{pages}{181} (\bibinfo{year}{2016}).

\bibitem{barnes2007}
\bibinfo{author}{Barnes, S.~A.}
\newblock \bibinfo{title}{Ages for {{Illustrative Field Stars Using
  Gyrochronology}}: {{Viability}}, {{Limitations}}, and {{Errors}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{669}}, \bibinfo{pages}{1167} (\bibinfo{year}{2007}).

\bibitem{meibom+2015}
\bibinfo{author}{Meibom, S.} \emph{et~al.}
\newblock \bibinfo{title}{A spin-down clock for cool stars from observations of
  a 2.5-billion-year-old cluster}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{517}},
  \bibinfo{pages}{589} (\bibinfo{year}{2015}).

\bibitem{leiner+2019}
\bibinfo{author}{Leiner, E.}, \bibinfo{author}{Mathieu, R.~D.},
  \bibinfo{author}{Vanderburg, A.}, \bibinfo{author}{Gosnell, N.~M.} \&
  \bibinfo{author}{Smith, J.~C.}
\newblock \bibinfo{title}{Blue {{Lurkers}}: {{Hidden Blue Stragglers}} on the
  {{M67 Main Sequence Identified}} from {{Their Kepler}}/{{K2 Rotation
  Periods}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{881}}, \bibinfo{pages}{47} (\bibinfo{year}{2019}).

\bibitem{claytor+2019}
\bibinfo{author}{Claytor, Z.~R.} \emph{et~al.}
\newblock \bibinfo{title}{Chemical {{Evolution}} in the {{Milky Way}}:
  {{Rotation}}-based ages for {{APOGEE}}-{{Kepler}} cool dwarf stars}.
\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
  \bibinfo{pages}{arXiv:1911.04518} (\bibinfo{year}{2019}).

\bibitem{borucki+2010}
\bibinfo{author}{Borucki, W.~J.}, \bibinfo{author}{Koch, D.} \&
  \bibinfo{author}{Team, K.~S.}
\newblock \bibinfo{title}{Kepler {{Planet Detection Mission}}: {{Highlights}}
  of the {{First Results}}}.
\newblock \emph{\bibinfo{journal}{AAS/Division for Planetary Sciences Meeting
  Abstracts \#42}} \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{47.03}
  (\bibinfo{year}{2010}).

\bibitem{silvaaguirre+2015}
\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
\newblock \bibinfo{title}{Ages and fundamental properties of {{Kepler}}
  exoplanet host stars from asteroseismology}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2127}
  (\bibinfo{year}{2015}).

\bibitem{angus+2015}
\bibinfo{author}{Angus, R.}, \bibinfo{author}{Aigrain, S.},
  \bibinfo{author}{{Foreman-Mackey}, D.} \& \bibinfo{author}{McQuillan, A.}
\newblock \bibinfo{title}{Calibrating gyrochronology using {{Kepler}}
  asteroseismic targets}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{450}}, \bibinfo{pages}{1787}
  (\bibinfo{year}{2015}).

\bibitem{nielsen+2015}
\bibinfo{author}{Nielsen, M.~B.}, \bibinfo{author}{Schunker, H.},
  \bibinfo{author}{Gizon, L.} \& \bibinfo{author}{Ball, W.~H.}
\newblock \bibinfo{title}{Constraining differential rotation of {{Sun}}-like
  stars from asteroseismic and starspot rotation periods}.
\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{582}}, \bibinfo{pages}{A10} (\bibinfo{year}{2015}).

\bibitem{davies+2015}
\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
\newblock \bibinfo{title}{Asteroseismic inference on rotation, gyrochronology
  and planetary system dynamics of 16 {{Cygni}}}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959}
  (\bibinfo{year}{2015}).

\bibitem{reville+2015}
\bibinfo{author}{R{\'e}ville, V.}, \bibinfo{author}{Brun, A.~S.},
  \bibinfo{author}{Matt, S.}, \bibinfo{author}{Strugarek, A.} \&
  \bibinfo{author}{Pinto, R.}
\newblock \bibinfo{title}{The effect of magnetic topology on thermally-driven
  winds: Towards a general formulation of the braking law}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{798}}, \bibinfo{pages}{116} (\bibinfo{year}{2015}).
\newblock \eprint{1410.8746}.

\bibitem{garraffo+2016}
\bibinfo{author}{Garraffo, C.}, \bibinfo{author}{Drake, J.~J.} \&
  \bibinfo{author}{Cohen, O.}
\newblock \bibinfo{title}{The {{Missing Magnetic Morphology Term}} in {{Stellar
  Rotation Evolution}}}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{595}}, \bibinfo{pages}{A110} (\bibinfo{year}{2016}).
\newblock \eprint{1607.06096}.

\bibitem{metcalfe+2019}
\bibinfo{author}{Metcalfe, T.~S.} \emph{et~al.}
\newblock \bibinfo{title}{{{LBT}}/{{PEPSI Spectropolarimetry}} of a {{Magnetic
  Morphology Shift}} in {{Old Solar}}-type {{Stars}}}.
\newblock \emph{\bibinfo{journal}{arXiv:1912.01186 [astro-ph]}}
  (\bibinfo{year}{2019}).
\newblock \eprint{1912.01186}.

\bibitem{see+2019}
\bibinfo{author}{See, V.} \emph{et~al.}
\newblock \bibinfo{title}{Do {{Non}}-dipolar {{Magnetic Fields Contribute}} to
  {{Spin}}-down {{Torques}}?}
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{886}}, \bibinfo{pages}{120} (\bibinfo{year}{2019}).

\bibitem{mcquillan+2014}
\bibinfo{author}{McQuillan, A.}, \bibinfo{author}{Mazeh, T.} \&
  \bibinfo{author}{Aigrain, S.}
\newblock \bibinfo{title}{Rotation {{Periods}} of 34,030 {{Kepler
  Main}}-{{Sequence Stars}}: {{The Full Autocorrelation Sample}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
  \textbf{\bibinfo{volume}{211}}, \bibinfo{pages}{24} (\bibinfo{year}{2014}).
\newblock \eprint{1402.5694}.

\bibitem{matt+2015}
\bibinfo{author}{Matt, S.~P.}, \bibinfo{author}{Brun, A.~S.},
  \bibinfo{author}{Baraffe, I.}, \bibinfo{author}{Bouvier, J.} \&
  \bibinfo{author}{Chabrier, G.}
\newblock \bibinfo{title}{The {{Mass}}-dependence of {{Angular Momentum
  Evolution}} in {{Sun}}-like {{Stars}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{799}}, \bibinfo{pages}{L23} (\bibinfo{year}{2015}).

\bibitem{vansaders+2019}
\bibinfo{author}{{van Saders}, J.~L.}, \bibinfo{author}{Pinsonneault, M.~H.} \&
  \bibinfo{author}{Barbieri, M.}
\newblock \bibinfo{title}{Forward {{Modeling}} of the {{Kepler Stellar Rotation
  Period Distribution}}: {{Interpreting Periods}} from {{Mixed}} and {{Biased
  Stellar Populations}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{872}}, \bibinfo{pages}{128} (\bibinfo{year}{2019}).

\bibitem{ledoux1951}
\bibinfo{author}{Ledoux, P.}
\newblock \bibinfo{title}{The {{Nonradial Oscillations}} of {{Gaseous Stars}}
  and the {{Problem}} of {{Beta Canis Majoris}}.}
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{114}}, \bibinfo{pages}{373} (\bibinfo{year}{1951}).

\bibitem{davies+2016}
\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
\newblock \bibinfo{title}{Oscillation frequencies for 35 {{Kepler}} solar-type
  planet-hosting stars using {{Bayesian}} techniques and machine learning}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183}
  (\bibinfo{year}{2016}).

\bibitem{lund+2017}
\bibinfo{author}{Lund, M.~N.} \emph{et~al.}
\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
  {{Kepler Asteroseismic LEGACY Sample}}. {{I}}. {{Oscillation Mode
  Parameters}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{172} (\bibinfo{year}{2017}).

\bibitem{silvaaguirre+2017}
\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
  {{Kepler Asteroseismic LEGACY Sample}}. {{II}}.{{Radii}}, {{Masses}}, and
  {{Ages}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{173} (\bibinfo{year}{2017}).

\bibitem{garcia+2014}
\bibinfo{author}{Garc{\'i}a, R.~A.} \emph{et~al.}
\newblock \bibinfo{title}{Rotation and magnetism of {{Kepler}} pulsating
  solar-like stars. {{Towards}} asteroseismically calibrated age-rotation
  relations}.
\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{572}}, \bibinfo{pages}{A34} (\bibinfo{year}{2014}).

\bibitem{bedding+2010}
\bibinfo{author}{Bedding, T.~R.} \emph{et~al.}
\newblock \bibinfo{title}{Solar-like {{Oscillations}} in {{Low}}-luminosity
  {{Red Giants}}: {{First Results}} from {{Kepler}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Letters}}
  \textbf{\bibinfo{volume}{713}}, \bibinfo{pages}{L176--L181}
  (\bibinfo{year}{2010}).

\bibitem{kraft1967}
\bibinfo{author}{Kraft, R.~P.}
\newblock \bibinfo{title}{Studies of {{Stellar Rotation}}. {{V}}. {{The
  Dependence}} of {{Rotation}} on {{Age}} among {{Solar}}-{{Type Stars}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{150}}, \bibinfo{pages}{551} (\bibinfo{year}{1967}).

\bibitem{bonanno+frohlich2015}
\bibinfo{author}{Bonanno, A.} \& \bibinfo{author}{Fr{\"o}hlich, H.-E.}
\newblock \bibinfo{title}{A {{Bayesian}} estimation of the helioseismic solar
  age}.
\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{580}}, \bibinfo{pages}{A130} (\bibinfo{year}{2015}).

\bibitem{paxton+2017}
\bibinfo{author}{Paxton, B.} \emph{et~al.}
\newblock \bibinfo{title}{Modules for {{Experiments}} in {{Stellar
  Astrophysics}} ({{MESA}}): {{Convective Boundaries}}, {{Element Diffusion}},
  and {{Massive Star Explosions}}}.
\newblock \emph{\bibinfo{journal}{arXiv:1710.08424 [astro-ph]}}
  (\bibinfo{year}{2017}).
\newblock \eprint{1710.08424}.

\bibitem{hunter2007}
\bibinfo{author}{Hunter, J.~D.}
\newblock \bibinfo{title}{Matplotlib: {{A 2D Graphics Environment}}}.
\newblock \emph{\bibinfo{journal}{Computing in Science and Engineering}}
  \textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{90--95} (\bibinfo{year}{2007}).

\bibitem{benomar+2018}
\bibinfo{author}{Benomar, O.} \emph{et~al.}
\newblock \bibinfo{title}{Asteroseismic detection of latitudinal differential
  rotation in 13 {{Sun}}-like stars}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{361}},
  \bibinfo{pages}{1231} (\bibinfo{year}{2018}).

\bibitem{lund+2014}
\bibinfo{author}{Lund, M.~N.}, \bibinfo{author}{Miesch, M.~S.} \&
  \bibinfo{author}{{Christensen-Dalsgaard}, J.}
\newblock \bibinfo{title}{Differential rotation in main-sequence solar-like
  stars: {{Qualitative}} inference from asteroseismic data}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{790}}, \bibinfo{pages}{121} (\bibinfo{year}{2014}).
\newblock \eprint{1406.7873}.

\bibitem{benomar+2015}
\bibinfo{author}{Benomar, O.}, \bibinfo{author}{Takata, M.},
  \bibinfo{author}{Shibahashi, H.}, \bibinfo{author}{Ceillier, T.} \&
  \bibinfo{author}{Garc{\'i}a, R.~A.}
\newblock \bibinfo{title}{Nearly uniform internal rotation of solar-like
  main-sequence stars revealed by space-based asteroseismology and
  spectroscopic measurements}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2654--2674}
  (\bibinfo{year}{2015}).

\bibitem{gizon+2013}
\bibinfo{author}{Gizon, L.} \emph{et~al.}
\newblock \bibinfo{title}{Seismic constraints on rotation of {{Sun}}-like star
  and mass of exoplanet}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Science}} \textbf{\bibinfo{volume}{110}}, \bibinfo{pages}{13267}
  (\bibinfo{year}{2013}).

\bibitem{chaplin+2013}
\bibinfo{author}{Chaplin, W.~J.} \emph{et~al.}
\newblock \bibinfo{title}{Asteroseismic {{Determination}} of {{Obliquities}} of
  the {{Exoplanet Systems Kepler}}-50 and {{Kepler}}-65}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{766}}, \bibinfo{pages}{101} (\bibinfo{year}{2013}).

\bibitem{nielsen+2013}
\bibinfo{author}{Nielsen, M.~B.}, \bibinfo{author}{Gizon, L.},
  \bibinfo{author}{Schunker, H.} \& \bibinfo{author}{Karoff, C.}
\newblock \bibinfo{title}{Rotation periods of 12 000 main-sequence {{Kepler}}
  stars: {{Dependence}} on stellar spectral type and comparison with v sin i
  observations}.
\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{557}}, \bibinfo{pages}{L10} (\bibinfo{year}{2013}).

\bibitem{skumanich1972}
\bibinfo{author}{Skumanich, A.}
\newblock \bibinfo{title}{{{TIME SCALES FOR Ca}} n {{EMISSION DECAY}},
  {{ROTATIONAL BRAKING}}, {{AND LITHIUM DEPLETION}}}.
\newblock \emph{\bibinfo{journal}{ApJ. . .}} \bibinfo{pages}{4}
  (\bibinfo{year}{1972}).

\bibitem{kawaler1988}
\bibinfo{author}{Kawaler, S.~D.}
\newblock \bibinfo{title}{Angular momentum loss in low-mass stars}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{333}}, \bibinfo{pages}{236} (\bibinfo{year}{1988}).

\bibitem{girardi+2012}
\bibinfo{author}{Girardi, L.} \emph{et~al.}
\newblock \bibinfo{title}{{{TRILEGAL}}, a {{TRIdimensional modeL}} of {{thE
  GALaxy}}: {{Status}} and {{Future}}}.
\newblock \emph{\bibinfo{journal}{Astrophysics and Space Science Proceedings}}
  \textbf{\bibinfo{volume}{26}}, \bibinfo{pages}{165} (\bibinfo{year}{2012}).

\bibitem{berger+2020}
\bibinfo{author}{Berger, T.~A.} \emph{et~al.}
\newblock \bibinfo{title}{The \${{Gaia}}\$-\${{Kepler}}\$ {{Stellar Properties
  Catalog I}}: {{Homogeneous Fundamental Properties}} for 186,000
  \${{Kepler}}\$ {{Stars}}}.
\newblock \emph{\bibinfo{journal}{arXiv:2001.07737 [astro-ph]}}
  (\bibinfo{year}{2020}).
\newblock \eprint{2001.07737}.

\bibitem{gelman+rubin1992}
\bibinfo{author}{Gelman, A.} \& \bibinfo{author}{Rubin, D.~B.}
\newblock \bibinfo{title}{Inference from {{Iterative Simulation Using Multiple
  Sequences}}}.
\newblock \emph{\bibinfo{journal}{Statistical Science}}
  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{457--472}
  (\bibinfo{year}{1992}).

\bibitem{salvatier+2016}
\bibinfo{author}{Salvatier, J.}, \bibinfo{author}{Wiecki, T.~V.} \&
  \bibinfo{author}{Fonnesbeck, C.}
\newblock \bibinfo{title}{Probabilistic programming in {{Python}} using
  {{PyMC3}}}.
\newblock \emph{\bibinfo{journal}{PeerJ Computer Science}}
  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{e55} (\bibinfo{year}{2016}).

\bibitem{metcalfe+egeland2019}
\bibinfo{author}{Metcalfe, T.~S.} \& \bibinfo{author}{Egeland, R.}
\newblock \bibinfo{title}{Understanding the {{Limitations}} of
  {{Gyrochronology}} for {{Old Field Stars}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{871}}, \bibinfo{pages}{39} (\bibinfo{year}{2019}).
\newblock \eprint{1811.11905}.

\bibitem{lorenzo-oliveira+2019}
\bibinfo{author}{{Lorenzo-Oliveira}, D.} \emph{et~al.}
\newblock \bibinfo{title}{Constraining the evolution of stellar rotation using
  solar twins}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{485}}, \bibinfo{pages}{L68}
  (\bibinfo{year}{2019}).

\bibitem{barnes2010}
\bibinfo{author}{Barnes, S.~A.}
\newblock \bibinfo{title}{A {{Simple Nonlinear Model}} for the {{Rotation}} of
  {{Main}}-sequence {{Cool Stars}}. {{I}}. {{Introduction}}, {{Implications}}
  for {{Gyrochronology}}, and {{Color}}-{{Period Diagrams}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{722}}, \bibinfo{pages}{222} (\bibinfo{year}{2010}).

\bibitem{deng+2012}
\bibinfo{author}{Deng, L.-C.} \emph{et~al.}
\newblock \bibinfo{title}{{{LAMOST Experiment}} for {{Galactic Understanding}}
  and {{Exploration}} ({{LEGUE}}) \textemdash{} {{The}} survey's science plan}.
\newblock \emph{\bibinfo{journal}{Research in Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{735--754}
  (\bibinfo{year}{2012}).

\bibitem{dejong+2014}
\bibinfo{author}{{de Jong}, R.~S.} \emph{et~al.}
\newblock \bibinfo{title}{{{4MOST}}: 4-metre {{Multi}}-{{Object Spectroscopic
  Telescope}}} \textbf{\bibinfo{volume}{9147}}, \bibinfo{pages}{91470M}
  (\bibinfo{year}{2014}).

\bibitem{dalton+2014}
\bibinfo{author}{Dalton, G.} \emph{et~al.}
\newblock \bibinfo{title}{Project overview and update on {{WEAVE}}: The next
  generation wide-field spectroscopy facility for the {{William Herschel
  Telescope}}} \textbf{\bibinfo{volume}{9147}}, \bibinfo{pages}{91470L}
  (\bibinfo{year}{2014}).
\end{thebibliography}

### 2020-10-07 paper/natastron/ed.tex
Tidied up separate documents

@@
 \clearpage 
+\section*{\underline{Extended Data}}
 
-\begin{figure}
+%\renewcommand\thefigure{\thesection.\arabic{figure}}    
+\setcounter{figure}{0}
+
+\begin{figure}[h!]
 	\centering
-	\includegraphics[width=0.45\textwidth]{pgm_models.pdf}
+	\includegraphics[width=0.6 \textwidth]{pgm_models.pdf}
 	\caption{A probabilistic graphical model (PGM) represented algebraically in Equation \ref{eq:modelll}.
@@
 
-\begin{figure*}
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{Images/priors.png}
+	\caption{Comparisons between posterior estimates of rotational parameters (data points and error bars) and the priors on these parameters (shaded regions).
+Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$).
+Both the prior and values for $P$ are a transformation of the upper two parameters (see \textbf{Methods} and \textbf{Supplementary Information}) In all cases, the extent of the error bars and shaded regions indicate the 68\% credible ($1\sigma$) interval of the posterior and prior distributions respectively.
+The solid lines indicate the median of the prior distributions.
+In this figure, results with means and errorbars that closely resemble the prior distribution can be interpreted as prior-dominated (i.e.
+poorly informed by the data).
+All stars are sorted and coloured and sorted by age.
+In the case of inclination angle $i$ and rotation period $P$, the displayed priors are transformed from the priors imposed on the sampled parameters from which their posteriors were derived.}
+	\label{fig:priors}
+\end{figure}
+
+\begin{figure*}[h!]
 	\centering
 	\includegraphics[width=\textwidth]{Images/litcomp_alt2.pdf}
-	\caption{Comparisons between posterior estimates of rotational parameters from this work, LEGACY and Kages \cite[private communication]{davies+2016, lund+2017}.
+	\caption{Comparisons between posterior estimates of rotational parameters from this work, LEGACY and `Kages' \cite[private communication]{davies+2016, lund+2017}.
+Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$).
 Fractional differences are plotted against stellar rotation obtained in this work.
-The $\Delta$ indicates the fractional difference betwen thsi work and the literature (i.e.
+The $\Delta$ indicates the fractional difference between this work and the literature (i.e.
 stars above the zero-line have higher values in this work).
@@
 The x-axis units on the right hand panels are equivalent to the y-axis of the left hand panels.
-10 stars have been omitted from this plot and are discussed in more detail in the text: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have extremely low rotation periods in Kages, with high uncertainties.
+10 stars have been omitted from this plot and are discussed in more detail in \textbf{Methods}: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have extremely low rotation periods in Kages, with high uncertainties.
 Conversely, KICs 6603624, 8760414 and 8938364 have extremely high rotation periods in LEGACY with low uncertainties.
@@
 
-\begin{figure}
+\begin{figure}[h!]
  \centering
- \includegraphics[width=0.49\textwidth]{Images/seis_comparison_rot_alt2.pdf}
+ \includegraphics[width=0.8\textwidth]{Images/seis_comparison_rot_alt2.pdf}
  \caption{Fractional differences between posterior estimates of asteroseismic rotation period from this work.
-Literature sources are: \cite{davies+2015} (16 Cyg A \& B), \cite{nielsen+2015} (5 stars) and \cite{benomar+2018} (40 stars).
-We used the reported parameter $a_{1}$ from \cite{benomar+2018}, which represents the rotational splitting in the case of uniform latitudinal rotation in their model.
+Literature sources are: Davies et al.
+(2015) \cite{m_davies+2015} (16 Cyg A \& B), Nielsen et al.
+(2015) \cite{m_nielsen+2015} (5 stars) and Benomar et al.
+(2018) \cite{m_benomar+2018} (40 stars).
+We used the reported parameter $a_{1}$ from the latter, which represents the rotational splitting in the case of uniform latitudinal rotation in their model.
 The dashed line represents the median of the sample shown, with the dotted lines representing the $15.9^{\rm{th}}$ and $84.1^{\rm{st}}$ percentiles.
@@
 
- \begin{figure*}
+ \begin{figure*}[h!]
  	\centering
- 	\includegraphics[width=\textwidth]{Images/vsini-comparison.pdf}
+ 	\includegraphics[width=\textwidth]{Images/vsini_comparison_new.pdf}
  	\caption{Comparisons between asteroseismic and spectroscopic measures of projected surface rotation, $\textrm{v}\sin(i)$.
@@
 \textit{Left}: comparisons to 81 stars values reported in LEGACY and Kages.
-\textit{Right}: comparisons to 16 stars observed by \cite{benomar+2015}.
-Asteroseismic values are transformed from projected splitting ($\nu_s\sin(i)$) using the asteroseismic radius measurements presented in LEGACY and Kages.
-The solid lines indicate the 1:1 line, while the dash-dotted lines represent the 2:1 and 1:2 lines.}
+\textit{Right}: comparisons to 16 stars observed by Benomar et al.
+(2015) \cite{m_benomar+2015}.
+Asteroseismic values are transformed from projected splitting ($\nu_s\sin(i)$) using the asteroseismic radius measurements presented in LEGACY and `Kages'.
+The solid lines indicate the 1:1 line, while the dash-dotted lines represent the 2:1 and 1:2 lines.
+The dashed lines indicate the location of $v\sin(i) = 5\, \rm{kms^{-1}}$, the point at which surface and seismic measures of projected rotation begin to differ strongly \cite{m_tayar+2015}.}
  	\label{fig:vsinilit}
@@
 
-%\input{tabulate.tex}
+\input{tabulate.tex}

### 2020-10-07 paper/natastron/methods.tex
Tidied up separate documents

--- 2020-09-30 paper/natastron/methods.tex
@@
-\section*{Methods}
+%\documentclass[12pt]{article}
+%\setlength{\textwidth}{167mm}
+%\setlength{\headsep}{0mm}
+%\setlength{\headheight}{0mm}
+%\setlength{\textheight}{230mm}
+%\setlength{\oddsidemargin}{1.6mm}
+%\setlength{\evensidemargin}{1.6mm}
+%\setlength{\topmargin}{4.6mm}
+%
+%\usepackage{chngcntr}
+%\usepackage{xspace}
+%\usepackage{graphicx}
+%\usepackage{amsmath}	% Advanced maths commands
+%\usepackage{amssymb}	% Extra maths symbols
+%\usepackage[ ]{hyperref}
+%\graphicspath{{Images/}}
+%%\usepackage[symbol]{footmisc}
+%
+%
+%% Astronomical abbreviations (thanks to Dan Huber)
+%\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
+%\newcommand{\dnu}{\mbox{$\Delta \nu$}\xspace}
+%\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
+%\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
+%\newcommand{\logg}{\mbox{$\log(g)$}\xspace}
+%\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
+%\newcommand{\msun}{\mbox{$\mathrm{M}_{\odot}$}\xspace}
+%\newcommand{\lsun}{\mbox{$\mathrm{L}_{\odot}$}\xspace}
+%\newcommand{\mearth}{\mbox{$\mathrm{M}_{\oplus}$}\xspace}
+%\newcommand{\rsun}{\mbox{$\mathrm{R}_{\odot}$}\xspace}
+%\newcommand{\kepler}{\emph{Kepler}\xspace}
+%\newcommand{\tess}{\emph{TESS}\xspace}
+%\newcommand{\ktwo}{K2\xspace}
+%\newcommand{\gaia}{\emph{Gaia}\xspace}
+%
+%\begin{document}
+
+\section*{\underline{Methods}}
 \setcounter{tocdepth}{2}
@@
 \subsection{Asteroseismic Data}
-For our asteroseismic power spectrum data we used the unweighted power spectra from the KASOC pipeline \cite{handberg+lund2014}\footnote{Obtainable from the \href{http://kasoc.phys.au.dk/}{KASOC} webpage.}.
+For our asteroseismic power spectrum data we used the unweighted power spectra from the KASOC pipeline \cite{m_handberg+lund2014}\footnote{Obtainable from the \href{http://kasoc.phys.au.dk/}{KASOC} webpage.}.
 We did not apply any additional treatment to these data.
-For 16 Cyg A \& B (KIC 12069424 and KIC 12069449) we used the KEPSEISMIC lightcurves \cite{garcia+2011}\footnote{Obtainable from \href{https://archive.
+For 16 Cyg A \& B (KIC 12069424 and KIC 12069449) we used the KEPSEISMIC lightcurves \cite{m_garcia+2011}\footnote{Obtainable from \href{https://archive.
 		stsci.edu/prepds/kepseismic/}{MAST}.}, which have significantly better signal-to-noise for these two stars.
 
-For our asteroseismic ages, we used the ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{silvaaguirre+2015} in the `Kages' and LEGACY catalogues.
+For our asteroseismic ages, we used the ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{m_silvaaguirre+2015} in the `Kages' and LEGACY catalogues.
 These ages have been obtained by comparisons of measured oscillation properties to stellar models, accounting for an expanded range of metallicities.
-\texttt{BASTA} is thoroughly compared to four other seismic modelling techniques in \cite{silvaaguirre+2017}.
-While uncertainties found through \texttt{BASTA} are typically higher than for other techniques, only \texttt{BASTA} and \texttt{ASTFIT} \cite[Aarhus STellar Evolution Code]{christensen-dalsgaard2008} recover the radius, mass and age of the Sun, when applied to solar data.
+\texttt{BASTA} is thoroughly compared to four other seismic modelling techniques in \cite{m_silvaaguirre+2017}.
+While uncertainties found through \texttt{BASTA} are typically higher than for other techniques, only \texttt{BASTA} and \texttt{ASTFIT} \cite[Aarhus STellar Evolution Code]{m_christensen-dalsgaard2008} recover the radius, mass and age of the Sun, when applied to solar data.
 Although the uncertainties on \texttt{ASTFIT} ages are overall lower, they are not published for the `Kages' sample.
@@
 
-As described in the catalogue papers, for `Kages' stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy reported in \cite{huber+2013a}.
-For LEGACY stars, atmospheric properties were similarly taken from \cite{buchhave+latham2015} for most stars in the catalogue, and complemented by other values from the literature for the remaining stars \cite[see Table 3]{silvaaguirre+2017}.
+As described in the catalogue papers, for `Kages' stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy \cite{m_huber+2013a}.
+For LEGACY stars, atmospheric properties were similarly taken from one study \cite{m_buchhave+latham2015} for most stars in the catalogue, and complemented by other values from the literature for the remaining stars \cite[see Table 3]{m_silvaaguirre+2017}.
 
-Other asteroseismic properties used in this study, such as those used as first guesses on the free parameters in our asteroseismic model, were taken from the `Kages' and LEGACY catalogues \cite{astropycollaboration+2013, astropycollaboration+2018, ginsburg+2019}.
-In cases where both catalogues contained the same target, we used the stellar parameters reported in LEGACY \cite{mckinney2010}.
+Other asteroseismic properties used in this study, such as those used as first guesses on the free parameters in our asteroseismic model, were taken from the `Kages' and LEGACY catalogues \cite{m_astropycollaboration+2013, m_astropycollaboration+2018, m_ginsburg+2019}.
+In cases where both catalogues contained the same target, we used the stellar parameters reported in LEGACY \cite{m_mckinney2010}.
 This is also the case for the masses and ages described above.
@@
 In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background, modes of oscillation, and white noise, while accounting for rotational splitting.
-The foundations of this approach follows best-practices in asteroseismology \cite{davies+2015}, fitting Harvey profiles for the background \cite{harvey1985}, and expressing the frequencies of the modes using an asymptotic expression \cite{tassoul1980, vrard+2016}.
+The foundations of this approach follows best-practices in asteroseismology \cite{m_davies+2015}, fitting Harvey profiles for the background \cite{m_harvey1985}, and expressing the frequencies of the modes using an asymptotic expression \cite{m_tassoul1980, m_vrard+2016}.
 
-The first core improvement in this work come in the form of the use of hierarchical models, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{mazumdar+2014}).
+The first core improvement in this work come in the form of the use of hierarchical latent variable models \cite{m_hogg+2010, m_hall+2019}, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{m_mazumdar+2014}).
 By improving the inference of mode frequencies in this way, we also improve the ability to resolve the rotational splitting.
-The second improvement comes in the form of priors on our parameters, and in particular the rotational inclination, which more accurately reflects the true distribution of angles than previous techniques \cite{chaplin+basu2017}.
+The second improvement comes in the form of priors on our parameters, and in particular the rotational inclination, which more accurately reflects the true distribution of angles than previous techniques \cite{m_chaplin+basu2017}.
 A step-by-step breakdown of the model and all priors can be found in \textbf{Supplementary Materials}.\\
@@
 First, we fit a model for the convective background and white noise only, to the region of the power spectra that did not contain modes of oscillation.
-This was done using \texttt{PyStan} \cite{vanhoey+2013,carpenter+2017}, for 10,000 iterations on each star\footnote{These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work}.
+This was done using \texttt{PyStan} \cite{m_vanhoey+2013, m_carpenter+2017}, for 10,000 iterations on each star\footnote{These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work}.
 Second, we fit our full model (including the convective background) to the region containing the modes of oscillation.
 The results of the first fit to the convective background were used as extremely informative priors on the background parameters in this second fit.
-This was done using \texttt{PyMC3} \cite{vanderwalt+2011,salvatier+2016, thetheanodevelopmentteam+2016} for 2500 iterations each on 4 chains.
+This was done using \texttt{PyMC3} \cite{m_vanderwalt+2011,m_salvatier+2016, m_thetheanodevelopmentteam+2016} for 2500 iterations each on 4 chains.
 
-From this asteroseismic analysis, we report inclination angle ($i$), rotational splitting ($\nu_{\rm s}$), and rotation period ($P$) in \textbf{Extended Data} Table 1.
+From this asteroseismic analysis, we report inclination angle ($i$), rotational splitting ($\nu_{\rm s}$), and rotation period ($P$) in \textbf{Extended Data} Table \ref{tab:results}.
 The summary statistics on these parameters were taken as the median of the posterior distribution, with uncertainties being the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles.
@@
 We flagged any sub-optimal conditions of the final fit.
-Of 94 stars, we flagged 5 for which the Gelman-Rubin convergence metric, $\hat{R}$, was greater than 1.01 and 2 stars for which it was greater than 1.1 on inclination angle or rotation, where a $\hat{R} = 1$ indicates a converged result \cite{gelman+rubin1992}.
+Of 94 stars, we flagged 5 for which the Gelman-Rubin convergence metric, $\hat{R}$, was greater than 1.01 and 2 stars for which it was greater than 1.1 on inclination angle or rotation, where a $\hat{R} = 1$ indicates a converged result \cite{m_gelman+rubin1992}.
 We also performed visual checks of the sampled chains on all hyperparameters and of the best-fit model compared to both the raw and smoothed asteroseismic data.
@@
 KIC 8478994 was excluded due to both a poor fit as well as high $\hat{R}$ on rotational parameters.
-KICs 6603624, 8760414 and 8938364 are reported in \textbf{Extended Data} Table 1, but were excluded from the gyrochronology analysis due to strong disagreement with multiple studies in the literature (see main body of paper).
+KICs 6603624, 8760414 and 8938364 are reported in \textbf{Extended Data} Table \ref{tab:results}, but were excluded from the gyrochronology analysis due to strong disagreement with multiple studies in the literature (see main body of paper).
 Finally, we flagged any stars with fewer than 1000 effective samples ($n_{\rm eff}$) of $\nu_s$.
@@
 In the weakened magnetic braking model, $Ro_{\rm crit} = 1.97$.
-For further details, see \cite{vansaders+pinsonneault2013} and \cite{vansaders+2016, vansaders+2019} for the standard and weakened magnetic braking cases respectively.
+For further details, see \cite{m_vansaders+pinsonneault2013} and \cite{m_vansaders+2016, m_vansaders+2019} for the standard and weakened magnetic braking cases respectively.
 
-To construct a synthetic population of rotating stars, we expanded upon previous forward-models of the \textit{Kepler} field with the purpose of studying weakened magnetic braking \cite{vansaders+2019}, with some important improvements.
-We started with a TRILEGAL \cite{girardi+2012} Milky-Way simulation of the \kepler field, using the simulation's standard population values intended for this purpose.
-In order to replicate the \kepler selection effect, the TRILEGAL simulation was matched to the largest current catalogue of temperatures, luminosities and 2MASS $K$-band magnitudes of stars in the \kepler field \cite{berger+2020}.
+To construct a synthetic population of rotating stars, we expanded upon previous forward-models of the \textit{Kepler} field with the purpose of studying weakened magnetic braking \cite{m_vansaders+2019}, with some important improvements.
+We started with a TRILEGAL \cite{m_girardi+2012} Milky-Way simulation of the \kepler field, using the simulation's standard population values intended for this purpose.
+In order to replicate the \kepler selection effect, the TRILEGAL simulation was matched to the largest current catalogue of temperatures, luminosities and 2MASS $K$-band magnitudes of stars in the \kepler field \cite{m_berger+2020}.
 This was done using a nearest-neighbours approach, based on the density of stars on the HR diagram.
-This ensured that the TRILEGAL population matched the density of stars actually observed by \kepler, replicating its selection effects, and improved upon previous efforts \cite{vansaders+2019} by incorporating contemporary \textit{Gaia} mission data \cite{gaiacollaboration+2018}.
+This ensured that the TRILEGAL population matched the density of stars actually observed by \kepler, replicating its selection effects, and improved upon previous efforts \cite{m_vansaders+2019} by incorporating contemporary \textit{Gaia} mission data \cite{m_gaiacollaboration+2018}.
 
-We made further changes to account for possible binarity in the the matching sample \cite{berger+2020}.
+We made further changes to account for possible binarity in the the matching sample \cite{m_berger+2020}.
 If the first step is performed blindly, blended binaries in the sample cause an overestimation of the number of old stars.
@@
 \begin{enumerate}
-	\item blended the TRILEGAL stars with binary companions drawn from a flat mass-ratio distribution, using a known binary fraction \cite{raghavan+2010},
+	\item blended the TRILEGAL stars with binary companions drawn from a flat mass-ratio distribution, using a known binary fraction \cite{m_raghavan+2010},
 	\item recalculated the `observed' luminosities and magnitudes assuming that each binary pair was blended, and
-	\item shifted these stars' temperatures following a $g$-$K$ magnitude relation \cite{berger+2020}.
+	\item shifted these stars' temperatures following a $g$-$K$ magnitude relation \cite{m_berger+2020}.
 \end{enumerate}
@@
 Both the standard and WMB models contain stars with the same fundamental parameters (mass, radius, effective temperature, metallicity) but a different period based on the choice of rotational evolution prescription.
-Applying an asteroseismic selection function that depends on these fundamental parameters would apply an identical prior to both models, therefore providing no net effect on our posterior distribution \cite{chaplin+2011}.
+Applying an asteroseismic selection function that depends on these fundamental parameters would apply an identical prior to both models, therefore providing no net effect on our posterior distribution \cite{m_chaplin+2011}.
 Additionally, we expected any seismic selection function to be relatively flat (and therefore uninformative) on a star-by-star scale, on which we run our model analysis.
@@
 \subsection{Bayesian Mixture Model}
-In order to determine whether weakened magnetic braking occurs on the main sequence, we compared our sample of seismic age and rotation, along with temperature, metallicity and mass, to the two stellar population models of the \kepler field adapted from \cite{vansaders+2019}, discussed above.
+In order to determine whether weakened magnetic braking occurs on the main sequence, we compared our sample of seismic age and rotation, along with temperature, metallicity and mass, to the two stellar population models of the \kepler field \cite{m_vansaders+2019}, discussed above.
 Both stellar models were evaluated in a Bayesian framework, with the rationale of determining which of the two models (standard or WMB) is most likely to reproduce our observed data.
@@
 
-In order to draw probabilistic inference about the models, we built a five-dimensional Kernel Density Estimate (KDE) of both model populations using the \texttt{statsmodels} package \cite{seabold+perktold2010}.
+In order to draw probabilistic inference about the models, we built a five-dimensional Kernel Density Estimate (KDE) of both model populations using the \texttt{statsmodels} package \cite{m_seabold+perktold2010}.
 We used a band-width (setting the resolution of the KDE) of $0.02\, M_\odot$ in mass, $10\, \rm K$ in \teff, $0.01\, \rm{dex}$ in $\ln(t)$, $0.01\, \rm{dex}$ in $\rm{[Fe/H]}$ and $0.01\, \rm{dex}$ in $\ln(P)$.
@@
 
-The final term, $p(P_{\rm s})$, represents the prior on the mixture model weight, which is uniform between 0 and 1. A visual representation of our model is shown in Figure \ref{fig:pgm}.
+The final term, $p(P_{\rm s})$, represents the prior on the mixture model weight, which is uniform between 0 and 1.
+A visual representation of our model is shown in \textbf{Extended Data} Figure \ref{fig:pgm}.
 
@@
 At 95 stars, in 5 parameter spaces, this totals 476 free parameters to marginalise over.
-This is not an issue for Hamiltonian Monte Carlo \cite[HMC]{betancourt+girolami2013}, however the use of KDE functions, over which a probabilistic gradient can not be measured, reduces HMCs effectiveness.
-Alternative Markov Chain Monte Carlo techniques \cite[MCMC]{foreman-mackey+2013} can more efficiently sample the KDE functions, but can not treat the large number of hierarchical parameters.
+This is not an issue for Hamiltonian Monte Carlo \cite[HMC]{m_betancourt+girolami2013}, however the use of KDE functions, over which a probabilistic gradient can not be measured, reduces HMCs effectiveness.
+Alternative Markov Chain Monte Carlo techniques \cite[MCMC]{m_foreman-mackey+2013} can more efficiently sample the KDE functions, but can not treat the large number of hierarchical parameters.
 To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $P_{\rm s}$, and multiplied these post hoc to obtain a combined posterior.
@@
 
-We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{foreman-mackey+2013, foreman-mackey2016}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.
+We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{m_foreman-mackey+2013, m_foreman-mackey2016}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.
 
@@
 We also compared our asteroseismic estimates of stellar rotation with similar studies in the literature, shown in \textbf{Extended Data} Figure \ref{fig:literaturecomp}.
-These included: a study of the binary solar analogues 16 Cyg A \& B \cite{davies+2015}, ; a study of surface and seismic rotation which our catalogue shares 5 stars with \cite{nielsen+2015}, ; and an asteroseismic study of differential rotation with which our catalogue shares 40 targets \cite{benomar+2018}.
+These included: a study of the binary solar analogues 16 Cyg A \& B \cite{m_davies+2015}, ; a study of surface and seismic rotation which our catalogue shares 5 stars with \cite{m_nielsen+2015}, ; and an asteroseismic study of differential rotation with which our catalogue shares 40 targets \cite{m_benomar+2018}.
 For the latter, we used their reported splitting value $a_1$, which is equivalent to $\nu_{\rm s}$.
@@
 The increase in uncertainty with period is due to more slowly rotating stars being more difficult to constrain using asteroseismology.
-% The agreement within $1\sigma$ here is encouraging, indicating that these independent Bayesian analyses are finding appropriate uncertainties on these rotation measurements.
 
-It is of note that 16 Cyg A was found to be rotating slightly faster in our analysis compared to the literature \cite{davies+2015} (deviating within $2\sigma$), despite the fit being performed on the same data.
+It is of note that 16 Cyg A was found to be rotating slightly faster in our analysis compared to the literature \cite{m_davies+2015} (deviating within $2\sigma$), despite the fit being performed on the same data.
 We found an inclination angle that is slightly lower for 16 Cyg A but at a similar projected splitting, which would explain finding a lower value of rotation.
@@
 \subsection{Seismic vs spectroscopic rotation}
-A distinct difference between rotation rates obtained through different techniques may hold information about differential rotation (both latitudinal and radial) of near-surface layers, such as those we observe in the Sun \cite{beck2000}.
-A previous comparison of spectroscopic and seismic rotation rates, performed on a sample of 22 stars, found no significant radial differential rotation \cite{benomar+2018}.
+A distinct difference between rotation rates obtained through different techniques may hold information about differential rotation (both latitudinal and radial) of near-surface layers, such as those we observe in the Sun \cite{m_beck2000}.
+A previous comparison of spectroscopic and seismic rotation rates, performed on a sample of 22 stars, found no significant radial differential rotation \cite{m_benomar+2018}.
 In this work they not only considered rotation rates from spots, but also spectroscopic measures of the projected surface rotation $\textrm{v}\sin(i)$, which they found to be more reliable.
@@
 With our expanded sample of asteroseismic rotation we can perform a similar analysis, to both validate our sample and probe radial differential rotation.
-\textbf{Extended Data} Figure \ref{fig:vsinilit} shows a comparison between spectroscopic $\textrm{v}\sin(i)$ measurements as listed in LEGACY and `Kages' (left) and \cite{benomar+2015} (right).
+\textbf{Extended Data} Figure \ref{fig:vsinilit} shows a comparison between spectroscopic $\textrm{v}\sin(i)$ measurements as listed in LEGACY and `Kages' (left) and Benomar et al.
+(2015) \cite{m_benomar+2015} (right).
 In these cases the asteroseismic $\textrm{v}\sin(i)$ has been calculated using our measure of asteroseismic $\nu_s\sin(i)$ and the known asteroseismic radii.
@@
 
-For the LEGACY and `Kages' sample, we find no strong deviation from the 1:1 line except at very low velocities, which is likely due to biases inherent to spectroscopic line broadening measurements \cite{doyle+2014, tayar+2015}.
-For the \cite{benomar+2015} sample stars lie a lot closer to the 1:1 line.
+For the LEGACY and `Kages' sample, we find no strong deviation from the 1:1 line except at very low velocities, which is likely due to biases inherent to spectroscopic line broadening measurements \cite{m_doyle+2014, m_tayar+2015}.
+For the Benomar et al.
+(2015) sample stars lie a lot closer to the 1:1 line.
 
@@
 spectroscopic projected rotation rates are faster than asteroseismic rates).
-This offset is much smaller ($\sim5\%$) for the \cite{benomar+2015} sample, albeit for far fewer stars.
-These offsets are within the typical disagreement between spectroscopic methods, based on comparisons of projected rotation measurements for red giant stars \cite[see Figure 2]{tayar+2015}, especially at $< 5\, \rm{km\,s^{-1}}$.
+This offset is much smaller ($\sim5\%$) for the \cite{m_benomar+2015} sample, albeit for far fewer stars.
+These offsets are within the typical disagreement between spectroscopic methods, based on comparisons of projected rotation measurements for red giant stars \cite[see Figure 2]{m_tayar+2015}, especially at $< 5\, \rm{km\,s^{-1}}$.
 
@@
 	\item \textit{Fast rotating stars:} In prinicple, a star could rotate fast enough that the highest-frequency peak in a split dipole ($\ell = 2$) mode would overlap with the radial ($\ell = 0$) mode.
-This would occur if $2\nu_{\rm s}$ > $\delta\nu_{02}$, the small separation.
+This would occur if $2\nu_{\rm s} > \delta\nu_{02}$, the small separation.
 For the star in our sample with the smallest $\delta\nu_{02}$ (so the highest risk of this happening), this would occur at a rotation of 8.8 days or faster.
@@
 The probability of an asteroseismic detection with \kepler scales with temperature and radius (i.e.
-scales inversely with \logg, and therefore main sequence age) \cite{chaplin+2011, schofield+2019}.
-More active, magnetic stars may also suppress their oscillation modes, making it more likely to detect seismic oscillations in older stars \cite{mathur+2019}.
+scales inversely with \logg, and therefore main sequence age) \cite{m_chaplin+2011, m_schofield+2019}.
+More active, magnetic stars may also suppress their oscillation modes, making it more likely to detect seismic oscillations in older stars \cite{m_mathur+2019}.
 Through these two effects, asteroseismology is biased towards detecting older over younger stars.
@@
 \subsection{Limits of our stellar models}\label{ssec:limits}
-The rotational stellar models used in this work \cite{vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$.
+The rotational stellar models used in this work \cite{m_vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$.
 Our sample of 91 stars contained 4 stars with metallicities below $-0.4\, \rm{dex}$, which are shown as shaded symbols in Figure \ref{fig:fullsample}.
@@
 
-A recent study \cite{amard+matt2020} compared different rotational evolution models \cite[of which we use the former in this work]{vansaders+pinsonneault2013,matt+2015} while studying the effect metallicity has on rotation.
+A recent study \cite{m_amard+matt2020} compared different rotational evolution models \cite[of which we use the former in this work]{m_vansaders+pinsonneault2013,m_matt+2015} while studying the effect metallicity has on rotation.
 They found that metal-rich stars spin down significantly more effectively than metal poor stars.
 The population of 73 stars used in our stellar model comparisons is roughly centered on a $\rm{[Fe/H]}$ of 0 $\rm dex$, with a spread of $~0.16\, \rm dex$, with no stars significantly above or below $\pm 0.4\, \rm dex$ (as discussed above).
-While differences in stellar rotational evolution as a function of metallicity in this region are still somewhat pronounced, they are much less so than for more metal-rich or poor stars \cite[see Figure 2]{amard+matt2020}.
-However, for stars with $\feh < 0$, the alternative model prescription \cite{matt+2015} sees stars spin down more slowly than the models used in this work (i.e.
+While differences in stellar rotational evolution as a function of metallicity in this region are still somewhat pronounced, they are much less so than for more metal-rich or poor stars \cite[see Figure 2]{m_amard+matt2020}.
+However, for stars with $\feh < 0$, the alternative model prescription \cite{m_matt+2015} sees stars spin down more slowly than the models used in this work (i.e.
 they will rotate faster at later ages).
-This work only explores the presence of weakened magnetic braking for a single braking law, and a comparison to the \cite{matt+2015} braking model will be explored in a future paper.
+This work only explores the presence of weakened magnetic braking for a single braking law, and a comparison to alternative braking model will be explored in a future paper.
 
@@
 Asteroseismic properties obtained through stellar models can be subject to systematic errors arising from differences in input physics and choice of stellar models not included in the reported statistical uncertainties.
-A quantification of these different systematic effects can be found in the `Kages' catalogue paper \cite{silvaaguirre+2015}.
+A quantification of these different systematic effects can be found in the `Kages' catalogue paper \cite{m_silvaaguirre+2015}.
 Combining their reported median systematic uncertainties due to input physics results in median uncertainties of $20\%$ (up from $14\%)$ on age and $5\%$ (up from $3\%$) on mass for the `Kages' sample.
@@
 For stars to be good probes of existing gyrochronology relations, their rotational evolution must occur in isolation.
-If a star interacts with a close binary companion (through tides, or a merger) the natural angular momentum loss can be disturbed, causing gyrochronology to mispredict ages \cite{leiner+2019, fleming+2019}.
+If a star interacts with a close binary companion (through tides, or a merger) the natural angular momentum loss can be disturbed, causing gyrochronology to mispredict ages \cite{m_leiner+2019, m_fleming+2019}.
 Between LEGACY and Kages, we have 8 known binaries.
@@
 
-While we chose not to account for star-planet tidal interactions in this work, we note that this may also disturb the natural stellar rotational evolution when tidal forces are at play \cite{maxted+2015,gallet+delorme2019, benbakoura+2019}, although this has been disputed by observations of asteroseismic planet hosts \cite{ceillier+2016}.\\
+While we chose not to account for star-planet tidal interactions in this work, we note that this may also disturb the natural stellar rotational evolution when tidal forces are at play \cite{m_maxted+2015,m_gallet+delorme2019, m_benbakoura+2019}, although this has been disputed by observations of asteroseismic planet hosts \cite{m_ceillier+2016}.\\
+
+\input{bblmethods.tex}
+
+%\end{document}

### 2020-10-07 paper/natastron/paper.tex

--- 2020-09-30 paper/natastron/paper.tex
@@
 \usepackage{amssymb}	% Extra maths symbols
+\usepackage{lscape}
+\usepackage{longtable}
+\usepackage{threeparttable}
+\usepackage{multirow}
+\usepackage{booktabs}
 \usepackage[ ]{hyperref}
 \graphicspath{{Images/}}
-\usepackage[symbol]{footmisc}
+%\usepackage[symbol]{footmisc}
 
@@
 
+\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
+
 \begin{document}
@@
 
-\noindent Oliver J. Hall$^{1,2,3,}$\footnote[1]{Email: \texttt{oliver.hall@esa.int} | Twitter: \texttt{@asteronomer} | GitHub: \texttt{@ojhall94}}
+\noindent Oliver J. Hall$^{1,2,3,}$\footnote[1]{Email: \texttt{oliver.hall@esa.int} | Twitter: \texttt{@asteronomer} | GitHub: \texttt{@ojhall94}},
 	Guy R. Davies$^{2,3}$, 
 	Jennifer van Saders$^{4,5,6}$,
-	Martin B. Nielsen$^{2,3}$
+	Martin B. Nielsen$^{2,3}$,
 	Mikkel N. Lund$^{3}$, 
@@
 \vspace{10mm}
+
+\renewcommand*{\thefootnote}{\arabic{footnote}}
+\setcounter{footnote}{0}
 
@@
 
-\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) oscillations for each star, of which the latter have significantly lower signal-to noise.
+\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) p mode\footnote{\textit{Pressure} modes, the type of oscillation visible in main sequence stars.} oscillations for each star, of which the latter have significantly lower signal-to noise.
 Radial oscillations ($\ell = 0$), which are also visible, do not split.
@@
 
-\begin{figure}
+\begin{figure}[h!]
 	\centering
@@
 
-We compared our results with both published and unpublished asteroseismic rotation rates \cite{davies+2016, lund+2017,davies+2015, nielsen+2015, benomar+2018}, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with multiple other studies.
+We compared our results with both published and unpublished asteroseismic rotation rates \cite{nielsen+2015,davies+2015,davies+2016, lund+2017, benomar+2018}, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with multiple other studies.
 To some degree this was expected, as  for stars viewed near pole-on the split modes of oscillation have extremely low power, making them hard to detect reliably.
@@
 %Of the stars used in this comparison, 21 had a median value of $P_{\rm s}$ in the gyrochronology analysis. We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.  
-This overall agreement between spot and seismic rotation rates is in line with previous studies of Sun-like stars \cite{gizon+2013, chaplin+2013, nielsen+2015, benomar+2015}, and so we concluded that our asteroseismic ensemble can be reliably used to draw inferences about gyrochronology.\\
+This overall agreement between spot and seismic rotation rates is in line with previous studies of Sun-like stars \cite{nielsen+2015, benomar+2015, gizon+2013, chaplin+2013}, and so we concluded that our asteroseismic ensemble can be reliably used to draw inferences about gyrochronology.\\
 
-\begin{figure}
+\begin{figure}[h!]
 	\centering
-	\includegraphics[width=0.6\textwidth]{Images/surf-seis-comparison.pdf}
+	\includegraphics[width=0.6\textwidth]{Images/surf-seis-comparison_update.pdf}
 	\caption{Comparisons between asteroseismic and photometric measures of stellar rotation, for 48 stars.
-Literature values were taken, in order of priority, from: \cite{garcia+2014} and \cite{nielsen+2013} (i.e.
-if a value was reported in \cite{nielsen+2013} and also in \cite{garcia+2014}, the latter was used).
-Stars used in \cite{vansaders+2016} are highlighted.
-The four triangles represent stars included in the original \cite{nielsen+2015} work.
+Literature values were taken, in order of priority, from: Garcia et al.
+(2014) \cite{garcia+2014} and Nielsen et al.
+(2013) \cite{nielsen+2013} (i.e.
+if a value was reported in Nielsen et al.
+(2013) and also in Garcia et al.
+(2014), the latter was used).
+Stars used in the original van Saders et al.
+(2019) \cite{vansaders+2016} study that first proposed weakened magnetic braking are highlighted.
+The four triangles represent stars included in the Nielsen et al.
+(2015) study \cite{nielsen+2015} that previously measured this relationship.
 The solid line indicates 1:1 line, while the dash-dotted lines represent 2:1 and 1:2 lines.
@@
 \textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two population models of rotational evolution \cite{vansaders+2019}: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model') \cite{vansaders+2016}  The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$\footnote{The Rossby number may be defined as $Ro \equiv P/\tau_{\rm cz}$, where $\tau_{\rm cz}$ is the convective turnover timescale, and $P$ is the rotation.
-The Rossby number roughly scales inversely with stellar activity (and so increases as stars age).}
+The Rossby number roughly scales inversely with stellar activity (and so increases as stars age).}.
 
-Instead of comparing our rotation rates directly to models of individual stars, we instead compared them to synthetic TRILEGAL populations based on what the \textit{Kepler} field would look like under these two different braking laws \cite{girardi+2012,vansaders+2019}.
+Instead of comparing our rotation rates directly to models of individual stars, we instead compared them to synthetic TRILEGAL populations based on what the \textit{Kepler} field would look like under these two different braking laws \cite{vansaders+2019, girardi+2012}.
 These synthetic populations were then altered to match the distribution of existing catalogues of stars in the \kepler field in order to replicate the \kepler selection effect \cite{berger+2020}, and evolved following a standard or WMB braking law.
@@
 
-In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting, Excluding those with a number of effective samples $n_{\rm eff} < 25\%$ and a Gelman-Rubin metric of $\hat{R}>1.1$ \cite{gelman+rubin1992,salvatier+2016} (see \textbf{Extended Data Table 1}).
+In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting, excluding those with a number of effective samples $n_{\rm eff} < 1000$ and a Gelman-Rubin metric of $\hat{R}>1.1$ \cite{gelman+rubin1992,salvatier+2016} (see \textbf{Extended Data} Table \ref{tab:results}).
+Two stars with low metallicities ($< -0.8\, \rm {dex}$) that fell outside the boundaries of our stellar models were also excluded.
 The remaining sample of 73 stars contained 4 potential sub-giants, 22 `hot' stars and 47 main sequence stars.
@@
 	\includegraphics[width=\textwidth]{fullsample.png}
-	\caption{Stars for which rotation was measured in this work, plotted over TREILGAL \cite{girardi+2012} stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution.
+	\caption{Stars for which rotation was measured in this work, plotted over TRILEGAL \cite{girardi+2012} stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution.
 The 21 Stars that were excluded from the gyrochronology analysis are marked with crosses and without uncertainties (see text).
 Circles, squares and triangles denote main sequence, sub-giant, and `hot' stars respectively.
-Stars with a metallicity of $\bigl\lvert \feh \bigl\rvert > 0.4$ are shown in purple, to indicate that they fall outside the functional range of the \cite{vansaders+2019} stellar models.
+Stars with a metallicity of $\bigl\lvert \feh \bigl\rvert > 0.4$ are shown in purple, to indicate that they fall outside the functional range of the stellar models  \cite{vansaders+2019}.
 Note that only period-temperature space is shown here, but when evaluating between the two model prescriptions we also considered mass, age and metallicity.
@@
 In order to assess the posterior probability for the full sample, we multiplied the individual posterior probabilities for $P_{\rm{s}}$.
-This was done for the full ensemble of 73 stars, as well as for the three different stellar types.
+This was done for the full ensemble of 73 stars together, as well as for the three different stellar types separately.
 These joint probabilities can be seen in Figure \ref{fig:gyroresults} in the left-hand plot.
-The cumulative probability can be seen in the right-hand plot.
+The cumulative probabilities can be seen in the right-hand plot.
 In both of these plots, the left-hand side holds 98.4\% of the probability, indicating that the weakened magnetic braking model is preferred.
@@
 Both hot and sub-giant stars do not strongly prefer one model over the other (both crossing the $P_{\rm{s}} = 0.5$ line at roughly $45\%$), which is expected given that the rotation rates of both these stellar types are not expected to be strongly influenced by weakened magnetic braking.
-When performing this analysis on the full ensemble of 91 stars for which seismic rotation was measured, this the total probability below $P_{\rm{s}} = 0.5$ is 96.6\%.
+When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), this the total probability below $P_{\rm{s}} = 0.5$ is 96.6\%.
 \\
@@
 \textit{Left:} the product of histograms of the posterior estimates for 73 stars, or subsets thereof for different stellar classifications.
-\textit{Right:} the cumulative posterior probability for 73 stars, or subsets thereof for different stellar types.}
+\textit{Right:} the cumulative posterior probability for 73 stars, or subsets thereof for different stellar types.
+On the y-axis of the left hand plot, $p(P_{\rm s} | \mathcal{D})$ represents the posterior distribution on $P_{\rm s}$ given the data.
+The product symbol represents the sum of the posteriors for individual stars $i$, for a total of $N$ stars (which differs depending on the stellar type being shown).}
 	\label{fig:gyroresults}
@@
 \textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we ensured that the same results were obtained when using different subsets of the ensemble, and when exploring potential biases.
-We found that the joint posterior distribution did not change significantly when excluding stars with a metallicity outside the model range (purple in Figure \ref{fig:fullsample}), or those with extremely small uncertainties on asteroseismic mass.
+We found that the joint posterior distribution did not change significantly when excluding stars with a metallicities that fell only slightly outside the model range, or those with extremely small uncertainties on asteroseismic mass (see \textbf{Methods}).
 Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $P_{\rm s}$.
@@
 (2016) \cite[hereafter the `van Saders' study]{vansaders+2016} in response to stars with spot rotation rates faster than expected from gyrochronology at their asteroseismic ages.
-This discrepancy was also indicated at around the same time in other studies of asteroseismic ages of main sequence stars \cite{nielsen+2015, angus+2015, davies+2015}.
+This discrepancy was also indicated at around the same time in other studies of asteroseismic ages of main sequence stars \cite{angus+2015, nielsen+2015,  davies+2015}.
 The theory of weakened magnetic braking has been both reinforced by recent studies \cite{metcalfe+egeland2019}, as well as disputed \cite{lorenzo-oliveira+2019}, at least at the critical Rossby number originally proposed.
@@
 
-All analysis performed as part of this work is stored in an online public repository\footnote{\url{https://github.com/ojhall94/malatium}}.\\
+\input{bblpaper.tex}
 
-%\textbf{Software}: \texttt{astropy} \cite{astropycollaboration+2013, astropycollaboration+2018}, \texttt{astroquery} \cite{ginsburg+2019}, \texttt{Lightkurve} \cite{lightkurvecollaboration+2018}, \texttt{corner} \cite{foreman-mackey2016}, \texttt{emcee} \cite{foreman-mackey+2013}, \href{https://docs.daft-pgm.org/}{\texttt{daft}}, \texttt{Stan} \cite{carpenter+2017}, \texttt{PyStan} \cite{vanhoey+2013}, \texttt{iPython} \cite{perez+granger2007}, \texttt{Jupyter Notebooks} \cite{kluyver+2016}, \texttt{numpy}  \cite{vanderwalt+2011}, \texttt{pandas} and \texttt{scipy} \cite{mckinney2010}, \texttt{matplotlib} \cite{hunter2007}, \texttt{seaborn} \cite{waskom+2018}, \texttt{statsmodels} \cite{seabold+perktold2010}, \texttt{PyMC3} \cite{salvatier+2016}, \texttt{theano} \cite{thetheanodevelopmentteam+2016}.\\
-
+\newpage
 \textbf{Acknowledgments}:The authors would like to thank Sean Matt, Ellis Avallone, Alex Dixon, Warrick Ball and Brett Morris for helpful discussions. 
@@
 
-% The best way to enter references is to use BibTeX:
-%\bibliographystyle{naturemag}
-%\bibliography{library.bib} %
-
 \textbf{Author Contributions:} O.J.H.
@@
 
-\textbf{Correspondence:} Correspondence and requests for materials should be addressed to O.J.H.. (email: oliver.hall@esa.int).
+\textbf{Correspondence:} Correspondence and requests for materials should be addressed to O.J.H.. (email: oliver.hall@esa.int).\\
 
 \clearpage
-
 \input{methods.tex}
 
-\input{si.tex}
-
+\clearpage
 \input{ed.tex}
 
-\bibliographystyle{naturemag}
-\bibliography{library.bib} %
-
 \end{document}

### 2020-10-07 paper/natastron/si.tex

@@
 The linewidths of asteroseismic p modes vary roughly as a function of mode frequency, and do so slowly relative to \dnu.
-This can be expressed as an empirical relation \cite{davies+2014, appourchaux+2016, lund+2017}.
+This can be expressed as an empirical relation \cite{lund+2017, davies+2014, appourchaux+2016}.
 However, this relation has six free parameters, none of which are directly relevant to this work.
@@
 To improve computational efficiency, we reduced the number of oscillation modes being fit in five targets.
-For 16 Cyg A \& B, KIC 7970740 and KIC 8478994, we excluded any modes with a Bayes Factor ($\ln(K)$) of less than 6, as reported in LEGACY \cite{kass+raftery1995,davies+2016,lund+2017}.
+For 16 Cyg A \& B, KIC 7970740 and KIC 8478994, we excluded any modes with a Bayes Factor ($\ln(K)$) of less than 6, as reported in LEGACY \cite{davies+2016,lund+2017,kass+raftery1995}.
 For KIC 8478994, which is reported without a value for $\ln(K)$ in Kages, we only included modes of an overtone number that contained a detection for all of $\ell = (0, 1, 2)$, retaining 5 sets of higher signal-to-noise overtones.
@@
 
-\bibliographystyle{naturemag}
-\bibliography{library.bib} %
+\begin{thebibliography}{10}
+	\expandafter\ifx\csname url\endcsname\relax
+	\def\url#1{\texttt{#1}}\fi
+	\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+	\providecommand{\bibinfo}[2]{#2}
+	\providecommand{\eprint}[2][]{\url{#2}}
+
+	\bibitem{davies+2015}
+	\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
+	\newblock \bibinfo{title}{Asteroseismic inference on rotation, gyrochronology
+		and planetary system dynamics of 16 {{Cygni}}}.
+	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
+			Society}} \textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959}
+	(\bibinfo{year}{2015}).
+
+	\bibitem{chaplin+2011}
+	\bibinfo{author}{Chaplin, W.~J.} \emph{et~al.}
+	\newblock \bibinfo{title}{Ensemble {{Asteroseismology}} of {{Solar}}-{{Type
+				Stars}} with the {{NASA Kepler Mission}}}.
+	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{332}},
+	\bibinfo{pages}{213} (\bibinfo{year}{2011}).
+
+	\bibitem{harvey1985}
+	\bibinfo{author}{Harvey, J.}
+	\newblock \bibinfo{title}{High-{{Resolution Helioseismology}}}.
+	\newblock \emph{\bibinfo{journal}{Future Missions in Solar, Heliospheric \&
+			Space Plasma Physics}} \textbf{\bibinfo{volume}{235}}, \bibinfo{pages}{199}
+	(\bibinfo{year}{1985}).
+
+	\bibitem{chaplin+basu2017}
+	\bibinfo{author}{Chaplin, W.~J.} \& \bibinfo{author}{Basu}.
+	\newblock \emph{\bibinfo{title}{Asteroseismic {{Data Analysis}}:
+			{{Foundations}} and {{Techniques}}}} (\bibinfo{publisher}{{Princeton
+			University Press}}, \bibinfo{address}{{Princeton, New Jersey}},
+	\bibinfo{year}{2017}), \bibinfo{edition}{1st} edn.
+
+	\bibitem{davies+2016}
+	\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
+	\newblock \bibinfo{title}{Oscillation frequencies for 35 {{Kepler}} solar-type
+		planet-hosting stars using {{Bayesian}} techniques and machine learning}.
+	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
+			Society}} \textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183}
+	(\bibinfo{year}{2016}).
+
+	\bibitem{lund+2017}
+	\bibinfo{author}{Lund, M.~N.} \emph{et~al.}
+	\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
+		{{Kepler Asteroseismic LEGACY Sample}}. {{I}}. {{Oscillation Mode
+				Parameters}}}.
+	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{172} (\bibinfo{year}{2017}).
+
+	\bibitem{tassoul1980}
+	\bibinfo{author}{Tassoul, M.}
+	\newblock \bibinfo{title}{Asymptotic approximations for stellar nonradial
+		pulsations}.
+	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
+	\textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{469} (\bibinfo{year}{1980}).
+
+	\bibitem{vrard+2016}
+	\bibinfo{author}{Vrard, M.}, \bibinfo{author}{Mosser, B.} \&
+	\bibinfo{author}{Samadi, R.}
+	\newblock \bibinfo{title}{Period spacings in red giants. {{II}}. {{Automated}}
+		measurement}.
+	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
+	\textbf{\bibinfo{volume}{588}}, \bibinfo{pages}{A87} (\bibinfo{year}{2016}).
+
+	\bibitem{hogg2012}
+	\bibinfo{author}{Hogg, D.~W.}
+	\newblock \bibinfo{title}{Data analysis recipes: {{Probability}} calculus for
+		inference}.
+	\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
+	\bibinfo{pages}{arXiv:1205.4446} (\bibinfo{year}{2012}).
+
+	\bibitem{hall+2019}
+	\bibinfo{author}{Hall, O.~J.} \emph{et~al.}
+	\newblock \bibinfo{title}{Testing asteroseismology with {{Gaia DR2}}:
+		{{Hierarchical}} models of the {{Red Clump}}}.
+	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
+			Society}} \textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{3569--3585}
+	(\bibinfo{year}{2019}).
+	\newblock \eprint{1904.07919}.
+
+	\bibitem{mazumdar+2014}
+	\bibinfo{author}{Mazumdar, A.} \emph{et~al.}
+	\newblock \bibinfo{title}{Measurement of acoustic glitches in solar-type stars
+		from oscillation frequencies observed by {{Kepler}}}.
+	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\textbf{\bibinfo{volume}{782}}, \bibinfo{pages}{18} (\bibinfo{year}{2014}).
+	\newblock \eprint{1312.4907}.
+
+	\bibitem{davies+2014}
+	\bibinfo{author}{Davies, G.~R.}, \bibinfo{author}{Chaplin, W.~J.},
+	\bibinfo{author}{Elsworth, Y.} \& \bibinfo{author}{Hale, S.~J.}
+	\newblock \bibinfo{title}{{{BiSON}} data preparation: A correction for
+		differential extinction and the weighted averaging of contemporaneous data}.
+	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
+			Society}} \textbf{\bibinfo{volume}{441}}, \bibinfo{pages}{3009--3017}
+	(\bibinfo{year}{2014}).
+
+	\bibitem{appourchaux+2016}
+	\bibinfo{author}{Appourchaux, T.} \emph{et~al.}
+	\newblock \bibinfo{title}{Oscillation mode linewidths and heights of 23
+		main-sequence stars observed by {{{\emph{Kepler}}}}
+		{\emph{(}}{{{\emph{Corrigendum}}}}{\emph{)}}}.
+	\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
+	\textbf{\bibinfo{volume}{595}}, \bibinfo{pages}{C2} (\bibinfo{year}{2016}).
+
+	\bibitem{rasmussen+williams2006}
+	\bibinfo{author}{Rasmussen, C.~E.} \& \bibinfo{author}{Williams, C. K.~I.}
+	\newblock \emph{\bibinfo{title}{Gaussian Processes for Machine Learning}}.
+	\newblock Adaptive Computation and Machine Learning (\bibinfo{publisher}{{MIT
+			Press}}, \bibinfo{address}{{Cambridge, Mass}}, \bibinfo{year}{2006}).
+
+	\bibitem{toutain+appourchaux1994}
+	\bibinfo{author}{Toutain, T.} \& \bibinfo{author}{Appourchaux, T.}
+	\newblock \bibinfo{title}{Maximum likelihood estimators: {{An}} application to
+		the estimation of the precision of helioseismic measurements}.
+	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
+	\textbf{\bibinfo{volume}{289}}, \bibinfo{pages}{649--658}
+	(\bibinfo{year}{1994}).
+
+	\bibitem{gizon+solanki2003}
+	\bibinfo{author}{Gizon, L.} \& \bibinfo{author}{Solanki, S.~K.}
+	\newblock \bibinfo{title}{Determining the {{Inclination}} of the {{Rotation
+				Axis}} of a {{Sun}}-like {{Star}}}.
+	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\textbf{\bibinfo{volume}{589}}, \bibinfo{pages}{1009} (\bibinfo{year}{2003}).
+
+	\bibitem{handberg+campante2011}
+	\bibinfo{author}{Handberg, R.} \& \bibinfo{author}{Campante, T.~L.}
+	\newblock \bibinfo{title}{Bayesian peak-bagging of solar-like oscillators using
+		{{MCMC}}: A comprehensive guide}.
+	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
+	\textbf{\bibinfo{volume}{527}}, \bibinfo{pages}{A56} (\bibinfo{year}{2011}).
+
+	\bibitem{woodard1984}
+	\bibinfo{author}{Woodard, M.~F.}
+	\newblock \emph{\bibinfo{title}{Short-{{Period Oscillations}} in the {{Total
+					Solar Irradiance}}.}}
+	\newblock Ph.D. thesis (\bibinfo{year}{1984}).
+
+	\bibitem{anderson+1990}
+	\bibinfo{author}{Anderson, E.~R.}, \bibinfo{author}{Duvall, T.~L.} \&
+	\bibinfo{author}{Jefferies, S.~M.}
+	\newblock \bibinfo{title}{Modeling of {{Solar Oscillation Power Spectra}}}.
+	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\textbf{\bibinfo{volume}{364}}, \bibinfo{pages}{699} (\bibinfo{year}{1990}).
+
+	\bibitem{vanhoey+2013}
+	\bibinfo{author}{Van~Hoey, S.}, \bibinfo{author}{{van der Kwast}, J.},
+	\bibinfo{author}{Nopens, I.} \& \bibinfo{author}{Seuntjens, P.}
+	\newblock \bibinfo{title}{Python package for model {{STructure ANalysis}}
+		({{pySTAN}})}.
+	\newblock \emph{\bibinfo{journal}{EGU General Assembly Conference Abstracts}}
+	\textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{EGU2013--10059}
+	(\bibinfo{year}{2013}).
+
+	\bibitem{salvatier+2016}
+	\bibinfo{author}{Salvatier, J.}, \bibinfo{author}{Wiecki, T.~V.} \&
+	\bibinfo{author}{Fonnesbeck, C.}
+	\newblock \bibinfo{title}{Probabilistic programming in {{Python}} using
+		{{PyMC3}}}.
+	\newblock \emph{\bibinfo{journal}{PeerJ Computer Science}}
+	\textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{e55} (\bibinfo{year}{2016}).
+
+	\bibitem{gelman2006}
+	\bibinfo{author}{Gelman, A.}
+	\newblock \bibinfo{title}{Prior distributions for variance parameters in
+		hierarchical models (comment on article by {{Browne}} and {{Draper}})}.
+	\newblock \emph{\bibinfo{journal}{Bayesian Analysis}}
+	\textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{515--534}
+	(\bibinfo{year}{2006}).
+
+	\bibitem{ballot+2006}
+	\bibinfo{author}{Ballot, J.}, \bibinfo{author}{Garcia, R.~A.} \&
+	\bibinfo{author}{Lambert, P.}
+	\newblock \bibinfo{title}{Rotation speed and stellar axis inclination from p
+		modes: How {{CoRoT}} would see other suns}.
+	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
+			Society}} \textbf{\bibinfo{volume}{369}}, \bibinfo{pages}{1281--1286}
+	(\bibinfo{year}{2006}).
+
+	\bibitem{ballot+2008a}
+	\bibinfo{author}{Ballot, J.}, \bibinfo{author}{Appourchaux, T.},
+	\bibinfo{author}{Toutain, T.} \& \bibinfo{author}{Guittet, M.}
+	\newblock \bibinfo{title}{On deriving p-mode parameters for inclined solar-like
+		stars}.
+	\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
+	\textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{867--875}
+	(\bibinfo{year}{2008}).
+	\newblock \eprint{0803.0885}.
+
+	\bibitem{kass+raftery1995}
+	\bibinfo{author}{Kass, R.~E.} \& \bibinfo{author}{Raftery, A.~E.}
+	\newblock \bibinfo{title}{Bayes {{Factors}}}.
+	\newblock \emph{\bibinfo{journal}{Journal of the American Statistical
+			Association}} \textbf{\bibinfo{volume}{90}}, \bibinfo{pages}{773--795}
+	(\bibinfo{year}{1995}).
+
+\end{thebibliography}
 

### 2020-10-07 paper/natastron/methods.tex
Jen's comments

@@
 
-The first core improvement in this work come in the form of the use of hierarchical latent variable models \cite{m_hogg+2010, m_hall+2019}, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{m_mazumdar+2014}).
+The first core improvement in this work is the use of hierarchical latent variable models \cite{m_hogg+2010, m_hall+2019}, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{m_mazumdar+2014}).
 By improving the inference of mode frequencies in this way, we also improve the ability to resolve the rotational splitting.
@@
 
-	\item \textit{Slow rotating stars:} Except for the most fast rotating cases, asteroseismic mode splitting is detected by a broadening of the mode frequencies as the split components begin to separate from the central mode.
+	\item \textit{Slow rotating stars:} Except for the most rapidly rotating cases, asteroseismic mode splitting is detected by a broadening of the mode frequencies as the split components begin to separate from the central mode.
 If there is to be hard limit at which this measurement is not possible, it should be in the case that $\nu_{\rm s} < 2/T$, where $T$ is the observation time, and $1/T$ is the frequency bin width.
@@
 
-While these two limits cause concern when studying the most extreme rotators, the results presented in this work are driven by stars with rotation rates in the regime of 10 to 40 days, and so we do not expect these limits to bias our conclusions.
+While these two limits cause concern when studying the most extreme rotators, the results presented in this work are data-driven by stars with rotation rates in the regime of 10 to 40 days, and so we do not expect these limits to bias our conclusions.
 

### 2020-10-07 paper/natastron/paper.tex
Jen's comments

@@
 	Guy R. Davies$^{2,3}$, 
-	Jennifer van Saders$^{4,5,6}$,
+	Jennifer van Saders$^{4}$,
 	Martin B. Nielsen$^{2,3}$,
@@
 	William J. Chaplin$^{2,3}$, 
-	Rafael A. Garc\'ia$^{7, 8}$, 
-	Louis Amard$^{9}$,
-	Angela A. Breimann$^{9}$, 
+	Rafael A. Garc\'ia$^{5, 6}$, 
+	Louis Amard$^{7}$,
+	Angela A. Breimann$^{7}$, 
 	Saniya Khan$^{2,3}$, 
-	Victor See$^{9}$, 
-	Jamie Tayar$^{4, 10}$
+	Victor See$^{7}$, 
+	Jamie Tayar$^{4, 8}$
 	\\
@@
 
-	\noindent 	$^{5}$ Observatories of the Carnegie Institution for Science, Pasadena, CA 91101
+	\noindent 	$^{5}$ IRFU, CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France
 
-	\noindent 	$^{6}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544
+	\noindent 	$^{6}$ AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, F-91191 Gif-sur-Yvette, France
 
-	\noindent 	$^{7}$ IRFU, CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France
+	\noindent 	$^{7}$ University of Exeter Department of Physics and Astronomy, Stocker Road, Devon, Exeter, EX4 4QL, UK
 
-	\noindent 	$^{8}$ AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, F-91191 Gif-sur-Yvette, France
-
-	\noindent 	$^{9}$ University of Exeter Department of Physics and Astronomy, Stocker Road, Devon, Exeter, EX4 4QL, UK
-
-	\noindent $^{10}$ Hubble Fellow
+	\noindent $^{8}$ Hubble Fellow
 
@@
 Gyrochronology is the study of the relationship between a star's rotation period and its age.
-As a star grows older along the main sequence, magnetic winds will cause it to lose angular momentum, slowing it down.
+As a star grows older along the main sequence, magnetic winds will cause it to lose angular momentum, slowing its rotation.
 Because the loss rate is related to temperature, the rotation period of a young star will rapidly settle on to a plane in age-colour-rotation space \cite{barnes2007}.
-As a result, knowing the rotation and colour of a star provides an avenue to measure it's age, to a precision of $\sim 10\%$ for stars most similar to the Sun \cite{meibom+2015}.
-Age can otherwise be difficult to come by, and so gyrochronology enables more in-depth studies of stellar populations and individual stars \cite{leiner+2019,claytor+2019}.
+As a result, knowing the rotation and colour of a star provides an avenue to measure its age, to a precision of $\sim 10\%$ for stars most similar to the Sun \cite{meibom+2015}.
+Age can otherwise be difficult to infer, and so gyrochronology enables more in-depth studies of stellar populations and individual stars \cite{leiner+2019,claytor+2019}.
 
-Gyrochronology was previously calibrated on stellar clusters, which have well constrained ages, but only up to roughly $2.5\, \rm{Gyr}$ so far \cite{meibom+2015}.
+Gyrochronology was previously calibrated on stellar clusters, which have well constrained ages, but only up to roughly $4\, \rm{Gyr}$ \cite{meibom+2015, barnes+2016}.
 With the launch of the \textit{Kepler} mission \cite{borucki+2010}, ages of main sequence field stars (i.e.
@@
 It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops.
-This would cause stars to keep fast rotation rates at old ages, which we would not expect from existing gyrochronology relations.
+This would cause stars to maintain relatively fast rotation rates at old ages, which we would not expect from the extrapolation of existing gyrochronology relations.
 
-The mechanism by which weakened magnetic braking occurs has since been the subject of ongoing debate, and may be connected to changes in the magnetic field morphology \cite{reville+2015,garraffo+2016, metcalfe+2019, see+2019}.
+The mechanism by which weakened magnetic braking occurs has since been the subject of ongoing debate, and may be connected to changes in the magnetic field morphology \cite{vansaders+2016,reville+2015,garraffo+2016, metcalfe+2016, metcalfe+2019, see+2019}.
 It may also be explained from an observational point of view.
 A large scale survey of stellar rotation rates measured using star-spots pointed out a lack of slowly rotating stars older then Sun \cite{mcquillan+2014}.
-As activity reduces with age, older stars with fewer star-spots are less likely to have their rotation measured \cite{matt+2015}.
-The point at which the detection probability drops appears to lie at a similar level of activity as when the proposed weakened magnetic braking takes place, pitting these two possibilities against one another \cite{vansaders+2019}.
+As activity reduces with age, older stars with fewer star-spots are less likely to have their rotation measured \cite{matt+2015, reinhold+2020}.
+The point at which the detection probability drops appears to lie at a similar level of activity as the expected onset of weakened magnetic braking, pitting these two possibilities against one another \cite{vansaders+2019}.
 
-Determining whether weakened magnetic braking is a true phenomenon or a bias in star-spot observations requires new data, which can be provided by asteroseismology.
+Determining whether weakened magnetic braking is a true phenomenon or a bias in star-spot observations requires new measurements of rotation in quiescent stars, which can be provided by asteroseismology.
 A star's rotation causes modes of oscillation to split into multiplets, making it possible to obtain an independent rate of rotation by measuring the splitting between oscillation frequencies \cite{ledoux1951}.
-Asteroseismic rotation is more difficult to obtain than spot rotation, but does not require spots to be visible, meaning that we can measure rotation for older, quiescent stars that would not have been present in existing rotation catalogues.
-This makes asteroseismic rotation rates the perfect avenue to explore whether weakened magnetic braking truly takes place on the main sequence.
-Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of  ages, and evaluated this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one where weakened magnetic braking takes place.\\
+Asteroseismic rotation requires a faster observing cadence and higher signal-to-noise than than spot rotation, but does not require spots to be visible, meaning that we can measure rotation for older, quiescent stars that would not have been present in existing rotation catalogues.
+This makes asteroseismic rotation rates a perfect test of weakened magnetic braking on the main sequence.
+Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of  ages, and evaluated this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one in which weakened magnetic braking takes place.\\
 
 \textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) p mode\footnote{\textit{Pressure} modes, the type of oscillation visible in main sequence stars.} oscillations for each star, of which the latter have significantly lower signal-to noise.
-Radial oscillations ($\ell = 0$), which are also visible, do not split.
+Radial oscillations ($\ell = 0$) are also visible, but do not split.
 In this work, we studied a sample of 95 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}.
@@
 
-We separated our sample into three categories \cite{garcia+2014}: 64 main sequence stars (MS, $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$); 4 potential sub-giant stars (SG, $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$), which may have begun to evolve off the main sequence, complicating their rotational history\footnote{It should be noted that none of these stars have identified mixed dipole modes, which indicate an evolved structure (see \cite{bedding+2010}).}; and 24 `hot' stars (H, $T_{\rm eff} > 6250\, \rm K$), which lie above the Kraft break, the point at which convective envelopes are tenuous, and angular momentum loss through magnetic winds becomes inefficient \cite{kraft1967}.
+We separated our sample into three categories \cite{garcia+2014}: 64 main sequence stars (MS, $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$); 4 potential sub-giant stars (SG, $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$), which may have begun to evolve off the main sequence, complicating their rotational history\footnote{It should be noted that none of these stars have identified mixed dipole modes, which indicate an evolved structure (see \cite{bedding+2010}).}; and 24 `hot' stars (H, $T_{\rm eff} > 6250\, \rm K$), which lie above the Kraft break, the point at which convective envelopes are thin, and angular momentum loss through magnetic winds becomes inefficient \cite{kraft1967}.
 Our conclusions are largely insensitive to these categorical assignments, and they are intended solely to help explore results category-by-category.
@@
 We fit our new model to \kepler power-spectra of 95 stars, which was successful in 94 cases.
-The summary statistics used throughout the rest of this paper were taken as the median of the posterior distribution on the model parameters, with the uncertainties being the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles, meaning that some reported parameters (such as period) have asymmetric uncertainties.
+We report summary statistics used throughout the rest of this paper as the median of the posterior distribution on the model parameters, with the uncertainties being the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles, meaning that some reported parameters (such as period) have asymmetric uncertainties.
 
@@
 Asteroseismology of main sequence stars probes internal rotation in the near surface layers, where the observed modes of oscillation are most sensitive \cite{lund+2014}.
-Measurements of star-spot modulation instead probe the rotation rates of star-spots on the surface.
+Measurements of star-spot modulation instead probe the rotation rates of star-spots on the surface, at active latitudes.
 Previous studies have shown that seismic rotation rates show no statistically significant deviation from spot rotation rates \cite{nielsen+2015, benomar+2015}.
@@
 This is not the case for asteroseismic rotation, and so some stars may appear at the 2:1 and 1:2 lines in the figure.
-We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid outliers (transparent in the Figure).
+We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid likely multiples of the true rotation rate acting as outliers (transparent in the Figure).
 Our fit found a value of $m = 0.96 \pm 0.03$, showing a close agreement ($<2\sigma$) between asteroseismic and surface rotation rates on a population level.
@@
 
-\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two population models of rotational evolution \cite{vansaders+2019}: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model') \cite{vansaders+2016}  The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$\footnote{The Rossby number may be defined as $Ro \equiv P/\tau_{\rm cz}$, where $\tau_{\rm cz}$ is the convective turnover timescale, and $P$ is the rotation.
+\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two population models of rotational evolution \cite{vansaders+2019}: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{vansaders+2016,skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model') \cite{vansaders+2016}  The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$\footnote{The Rossby number may be defined as $Ro \equiv P/\tau_{\rm cz}$, where $\tau_{\rm cz}$ is the convective turnover timescale, and $P$ is the rotation.
 The Rossby number roughly scales inversely with stellar activity (and so increases as stars age).}.
@@
 Instead of comparing our rotation rates directly to models of individual stars, we instead compared them to synthetic TRILEGAL populations based on what the \textit{Kepler} field would look like under these two different braking laws \cite{vansaders+2019, girardi+2012}.
-These synthetic populations were then altered to match the distribution of existing catalogues of stars in the \kepler field in order to replicate the \kepler selection effect \cite{berger+2020}, and evolved following a standard or WMB braking law.
+These synthetic populations were then altered to match the distribution of existing catalogues of stars in the \kepler field in order to replicate the \kepler selection effects \cite{berger+2020}, and evolved following a standard or WMB braking law.
 For the full details on how these models were constructed, see \textbf{Methods}.
@@
 	\caption{Stars for which rotation was measured in this work, plotted over TRILEGAL \cite{girardi+2012} stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution.
-The 21 Stars that were excluded from the gyrochronology analysis are marked with crosses and without uncertainties (see text).
+The 21 stars that were excluded from the gyrochronology analysis are marked with crosses and without uncertainties (see text).
 Circles, squares and triangles denote main sequence, sub-giant, and `hot' stars respectively.
 Stars with a metallicity of $\bigl\lvert \feh \bigl\rvert > 0.4$ are shown in purple, to indicate that they fall outside the functional range of the stellar models  \cite{vansaders+2019}.
-Note that only period-temperature space is shown here, but when evaluating between the two model prescriptions we also considered mass, age and metallicity.
+Note that this figure shows the projection of a 5-dimensional space onto a 2-dimensional representation, as only period-temperature space is shown here.
+When evaluating between the two model prescriptions we also considered mass, age and metallicity.
 The errorbars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions.}
@@
 In both of these plots, the left-hand side holds 98.4\% of the probability, indicating that the weakened magnetic braking model is preferred.
-When only considering the 47 main sequence stars, for which we expect the effects of weakened magnetic braking to be strongest, this rises to 99.2\%.
+When only considering the 47 main sequence stars, for which braking models are best calibrated, this rises to 99.2\%.
 
-Both hot and sub-giant stars do not strongly prefer one model over the other (both crossing the $P_{\rm{s}} = 0.5$ line at roughly $45\%$), which is expected given that the rotation rates of both these stellar types are not expected to be strongly influenced by weakened magnetic braking.
+Both hot and sub-giant stars do not strongly prefer one model over the other (both crossing the $P_{\rm{s}} = 0.5$ line at roughly $45\%$), which is expected given that these stars in our sample all lie at hot temperatures near the Kraft break.
 When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), this the total probability below $P_{\rm{s}} = 0.5$ is 96.6\%.
@@
 \textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we ensured that the same results were obtained when using different subsets of the ensemble, and when exploring potential biases.
-We found that the joint posterior distribution did not change significantly when excluding stars with a metallicities that fell only slightly outside the model range, or those with extremely small uncertainties on asteroseismic mass (see \textbf{Methods}).
+We found that the joint posterior distribution did not change significantly when excluding stars with metallicities that fell only slightly outside the model range, or those with extremely small uncertainties on asteroseismic mass (see \textbf{Methods}).
 Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $P_{\rm s}$.
@@
 The results from this echoed what we found for the unaltered ensemble.
-We also accounted for the possibility that asteroseismic methods systematically overestimated stellar age, and reran our analysis after shifting the seismic ages younger by their systematic uncertainty.
+We also accounted for the possibility that asteroseismic methods systematically overestimated stellar age, and reran our analysis after shifting the seismic ages younger by their systematic uncertainty ($6-8\%$).
 This resulted in $95.8\%$ of the posterior probability to lie below $P_{\rm s} = 0.5$, compared to $98.4\%$ for the unaltered ensemble.
@@
 
-	\item We present new techniques for asteroseismic `peak-bagging' frequency analyses, specifically: expressing well known empirical asteroseismic relations in a hierarchical modeling structure to account for small-scale effects not included in our model (such as acoustic glitches), and replacing uninformative empirical relations with Gaussian Process priors, detailed in the \textbf{Supplementary Information}.
+	\item The new asteroseismic rotation catalogue presented in this work will act as an entry point for more detailed studies, including comparisons between different braking laws and individually modeled values of stellar rotation at different critical Rossby numbers.
+
+%	\item We present new techniques for asteroseismic `peak-bagging' frequency analyses, specifically: expressing well known empirical asteroseismic relations in a hierarchical modeling structure to account for small-scale effects not included in our model (such as acoustic glitches), and replacing uninformative empirical relations with Gaussian Process priors, detailed in the \textbf{Supplementary Information}.
 
@@
 
-In the near future our new asteroseismic rotation catalogue will be further complemented with high-precision surface rotation measurements and atmospheric parameters from spectroscopic surveys such as LAMOST \cite{deng+2012}, 4MOST \cite{dejong+2014} and WEAVE \cite{dalton+2014}, and new asteroseismic measurements of age from the \ktwo and \tess missions.
+In the near future our new asteroseismic rotation catalogue will be further complemented with high-precision surface rotation measurements, activity indicators and atmospheric parameters from spectroscopic surveys such as LAMOST \cite{deng+2012}, 4MOST \cite{dejong+2014}, WEAVE \cite{dalton+2014} and SDSS-V \cite{blanton+2019, kollmeier+2019}, and new asteroseismic measurements of age from the \ktwo and \tess missions.
 With these surveys, large scale ensemble asteroseismology will continue to increase the possibilities for understanding gyrochronology.\\

### 2020-10-08 paper/natastron/response/response.tex
bill comments done

@@
 In practice, we think that the model would properly fit a spectrum where this kind of mode-overlapping was happening.
-The $\ell=0$ modes don’t split, and so if a $\ell=2$ mode were split so far that overlap was occurring, the $\ell=0$ mode would appear broadened or asymmetrical, which would have no other explanation.
+The $\ell=0$ modes don’t split, and so if a $\ell=2$ mode were split so far that overlap was occurring, the $\ell=0$ mode would appear broadened or asymmetrical, which is not degenerate with any other model states.
 There would still be a constraint on the splitting from the lower-frequency peaks.
-We can envision this being a serious issue if an $\ell=2$ mode is overlapping with an $\ell=1$ mode at lower frequencies as well, however this would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.
+We can envision there being an issue if an $\ell=2$ mode is overlapping with an $\ell=1$ mode at lower frequencies as well, however this would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.
 
@@
 \item \textit{Slow rotating stars:} Below, the reviewer raises concerns that for a limit of $\nu_s < 2\Gamma$ (when the splitting is smaller than the double the linewidth), splitting may not be accurately constrained.
-We dont believe this is the fundamental limit on this measurement, as splitting instead more frequently causes a broadening of the modes.
-Detection of this broadening makes it possible to measure seismic rotation even when the split components are not fully separated.
+We dont believe this is the fundamental limit on this measurement, as splitting instead more frequently causes a change in the power distribution in frequency of the modes.
+Detection of this change makes it possible to measure seismic rotation even when the split components are not fully separated.
+It is also worth noting that the non-split radial ($\ell=0$) modes provide strong constraints on the variation of linewidth with frequency.
 We discuss this more below.
-If there is to be a hard limit at which the broadening of a mode due to splitting can not be measured, we suggest that it is when it would be impossible to resolve it, so where $\nu_s < 2/T$, two times the frequency bin width.
+If there is to be a hard limit at which the the effects of splitting can not be measured, we suggest that it is when it would be impossible to resolve it, so where $\nu_s < 2/T$, two times the frequency bin width.
 The bin width is set by observing time, so to make an conservative estimate, we can take our star with the shortest observing time  (0.49 years).
 For this star, the limit on measuring rotation would be ~89 days (and going up for longer observing baselines).
-Of course, as discussed below, as you get to slower rotation rates it becomes harder to constrain the small rate of mode broadening and so the uncertainty will increase.
+Of course, as discussed below, as you get to slower rotation rates it becomes harder to constrain the small rate of mode splitting and so the uncertainty will increase.
 We believe this is dealt with appropriately in our model comparison through the use of hierarchical models.
@@
 Asteroseismic splitting is rarely larger than double the linewidth (in our sample this is only the case for a handful of the fastest rotators).
-Instead, rotational splitting is visible as a broadening of the modes, which take a specific form depending on the angular degree of the mode and the inclination angle of the star.
+Instead, rotational splitting changes the distribution of a mode's power with frequency, in a way that can be disentangled.
+This takes a specific form depending on the angular degree of the mode and the inclination angle of the star.
 This is why marginalising over inclination angle is important, because only by constructing a model that accounts for inclination angle and rotation together can you accurately represent how rotation affects the modes.
 
-It is also worth noting that our fitting method marginalises over inclination angle, rotational splitting and linewidth, and so the final rotational period measurements have uncertainties that accurately reflect the uncertainty associated with the slow rotation only having a small effect on the broadening of the modes of oscillation.
+It is also worth noting that our fitting method marginalises over inclination angle, rotational splitting and linewidth, and so the final rotational period measurements have uncertainties that accurately reflect the uncertainty associated with the slow rotation only having a small effect on the power distribution of the modes of oscillation.
 To be clear, there is no boundary beyond which this methodology of measuring asteroseismic rotation no longer works, until you start pushing up against the frequency resolution of the power spectrum (as discussed above).

### 2020-10-08 paper/natastron/methods.tex
bill comments done

@@
 
-	\item \textit{Slow rotating stars:} Except for the most rapidly rotating cases, asteroseismic mode splitting is detected by a broadening of the mode frequencies as the split components begin to separate from the central mode.
+	\item \textit{Slow rotating stars:} Except for the most rapidly rotating cases, asteroseismic mode splitting is detected by a change in the distribution of the power of mode frequencies as the split components begin to separate from the central mode.
 If there is to be hard limit at which this measurement is not possible, it should be in the case that $\nu_{\rm s} < 2/T$, where $T$ is the observation time, and $1/T$ is the frequency bin width.

### 2020-10-08 paper/natastron/methods.tex
Guy & Bill comments

@@
 
-While these two limits cause concern when studying the most extreme rotators, the results presented in this work are data-driven by stars with rotation rates in the regime of 10 to 40 days, and so we do not expect these limits to bias our conclusions.
+While these two limits cause concern when studying the most extreme rotators, the results presented in this work are driven by stars with rotation rates in the regime of 10 to 40 days.
+Above, we demonstrated that results on period for these stars were data-driven (i.e.
+do not reflect the priors), indicating that the splitting is well resolved in this regime, and so we do not expect these limits to bias our conclusions.
 

### 2020-10-08 paper/natastron/paper.tex
Guy & Bill comments

@@
 As a star grows older along the main sequence, magnetic winds will cause it to lose angular momentum, slowing its rotation.
-Because the loss rate is related to temperature, the rotation period of a young star will rapidly settle on to a plane in age-colour-rotation space \cite{barnes2007}.
-As a result, knowing the rotation and colour of a star provides an avenue to measure its age, to a precision of $\sim 10\%$ for stars most similar to the Sun \cite{meibom+2015}.
+The loss rate is thought to depend on the depth of the convection zone, which is a strong function of mass and temperature, and so the rotation period of a young star will rapidly settle on to a plane in age-colour-rotation space \cite{barnes2007}.
+Knowing the rotation and colour of stars therefore provides an avenue to measure ages, to a precision of $\sim 10\%$ for stars most similar to the Sun \cite{meibom+2015}.
 Age can otherwise be difficult to infer, and so gyrochronology enables more in-depth studies of stellar populations and individual stars \cite{leiner+2019,claytor+2019}.
@@
 Gyrochronology was previously calibrated on stellar clusters, which have well constrained ages, but only up to roughly $4\, \rm{Gyr}$ \cite{meibom+2015, barnes+2016}.
-With the launch of the \textit{Kepler} mission \cite{borucki+2010}, ages of main sequence field stars (i.e.
-not in clusters) became more widely available through asteroseismology, the study of stellar variability \cite{silvaaguirre+2015}.
+Recently, ages of main sequence field stars (i.e.
+not in clusters) observed by \kepler \cite{borucki+2010} became more widely available through asteroseismology, the study of stellar variability \cite{silvaaguirre+2015}.
 When looking at these stars, disagreements were found between the observations and gyrochronology beyond the middle of stars' main sequence lifetimes, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}.
@@
 
-The mechanism by which weakened magnetic braking occurs has since been the subject of ongoing debate, and may be connected to changes in the magnetic field morphology \cite{vansaders+2016,reville+2015,garraffo+2016, metcalfe+2016, metcalfe+2019, see+2019}.
+The mechanism by which weakened magnetic braking occurs is subject of debate, and may be connected to changes in the magnetic field morphology \cite{vansaders+2016,reville+2015,garraffo+2016, metcalfe+2016, metcalfe+2019, see+2019}.
 It may also be explained from an observational point of view.
-A large scale survey of stellar rotation rates measured using star-spots pointed out a lack of slowly rotating stars older then Sun \cite{mcquillan+2014}.
+A large survey of stellar rotation rates measured using star-spots found a lack of slowly rotating stars older then Sun \cite{mcquillan+2014}.
 As activity reduces with age, older stars with fewer star-spots are less likely to have their rotation measured \cite{matt+2015, reinhold+2020}.
-The point at which the detection probability drops appears to lie at a similar level of activity as the expected onset of weakened magnetic braking, pitting these two possibilities against one another \cite{vansaders+2019}.
+The point at which the detection probability drops appears to lie at a similar level of activity as the expected onset of weakened magnetic braking, placing these two possibilities in opposition to one another \cite{vansaders+2019}.
 
 Determining whether weakened magnetic braking is a true phenomenon or a bias in star-spot observations requires new measurements of rotation in quiescent stars, which can be provided by asteroseismology.
-A star's rotation causes modes of oscillation to split into multiplets, making it possible to obtain an independent rate of rotation by measuring the splitting between oscillation frequencies \cite{ledoux1951}.
-Asteroseismic rotation requires a faster observing cadence and higher signal-to-noise than than spot rotation, but does not require spots to be visible, meaning that we can measure rotation for older, quiescent stars that would not have been present in existing rotation catalogues.
+A star's rotation causes modes of oscillation to split into multiplets, enabling measurement of independent rotation rates by measuring the rate of splitting \cite{ledoux1951}.
+Asteroseismic rotation requires a faster observing cadence and higher signal-to-noise than spot rotation, but does not require spots to be visible, meaning that we can measure rotation for older, quiescent stars that would not have been present in existing rotation catalogues.
 This makes asteroseismic rotation rates a perfect test of weakened magnetic braking on the main sequence.
-Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of  ages, and evaluated this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one in which weakened magnetic braking takes place.\\
+Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of  ages, and determined whether this new ensemble agrees more closely with a classical rotational evolution scenario, or one in which weakened magnetic braking takes place.\\
 

### 2020-10-09 paper/natastron/methods.tex
Added availibilty statements

@@
 
-While we chose not to account for star-planet tidal interactions in this work, we note that this may also disturb the natural stellar rotational evolution when tidal forces are at play \cite{m_maxted+2015,m_gallet+delorme2019, m_benbakoura+2019}, although this has been disputed by observations of asteroseismic planet hosts \cite{m_ceillier+2016}.\\
+While we chose not to account for star-planet tidal interactions in this work, we note that this may disturb the natural stellar rotational evolution when tidal forces are at play \cite{m_maxted+2015,m_gallet+delorme2019, m_benbakoura+2019}, although this has been disputed by observations of asteroseismic planet hosts \cite{m_ceillier+2016}.\\
+
+\textbf{Data availability statement:} The core input data and results are summarised in \textbf{Extended Data} Table \ref{tab:results}, which is published with this article, and is also available on Vizier.
+Larger data files, such as stellar model populations and individual posterior distribution chains from the asteroseismic and gyrochronology model fitting are fully available on request.
+
+This work made use of publicly available data described in the text, and reiterated here.
+\kepler power spectral density  were obtained from the \href{http://kasoc.phys.au.dk/}{KASOC} webpages for the majority of stars, and from the \href{https://archive.
+		stsci.edu/prepds/kepseismic/}{MAST} for 16 Cyg A and B.
+This work used asteroseismic data from Silva Aguirre et al.
+(2015, 2017), Davies et al.
+(2016) and Lund et al.
+(2017) \cite{silvaaguirre+2015, davies+2016, lund+2017, silvaaguirre+2017 }.
+Parameter distributions of the \kepler field used to alter our stellar population models were taken from Berger et al.
+(2020) \cite{berger+2020}.\\
+
+\textbf{Code availability statement:} The code required to replicate our results has been placed in a curated online repository found here: \url{www.github.com/ojhall94/halletal2020}.
+
+All code written in the duration of this project, along with a full commit history, can be found in an un-curated online repository here: \url{www.github.com/ojhall94/malatium}.
+
+The code used to construct the stellar population models used in this work is available upon request.
 

### 2020-10-09 paper/natastron/paper.tex
Added availibilty statements

@@
 \newpage
-\textbf{Acknowledgments}:The authors would like to thank Sean Matt, Ellis Avallone, Alex Dixon, Warrick Ball and Brett Morris for helpful discussions. 
+\textbf{Acknowledgments}: The authors would like to thank the anonymous reviewer for their help improving this manuscript.
+They would also like to thank Sean Matt, Ellis Avallone, Alex Dixon, Warrick Ball and Brett Morris for helpful discussions.
 OJH, GRD and WJC acknowledge the support of the UK Science and Technology Facilities Council (STFC). 
@@
 MBN acknowledges support from the UK Space Agency
-This work has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (CartographY GA. 804752)
+This work has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (CartographY GA. 804752).
 Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement no.: DNRF106). 

### 2020-10-09 paper/natastron/response/response.tex
Updated response with martin's comments

@@
 
-First we would like to thank the reviewer for their comments, which have helped us polish up our discussion of biases.
+First we would like to thank the reviewer for their comments, which have helped us improve this manuscript.
 The paper has now been re-written to fit the Nature format, and therefore some of the content has changed or moved.
-The main body of the paper is mostly new or adapted writing, and the Methods contains the more detailed information on data, methods, and discussion.
-At the end of this document we’ve listed any major changes made, which is duplicated in our cover letter to the editor.
+The main body of the paper is mostly new or adapted writing, and the \textbf{Methods} and \textbf{Supplementary Information} contains details on data, methods, and discussion.
+At the end of this document we’ve listed any major changes made.
 
@@
 
-In short, yes, there are biases at play, but we don’t think these will affect our results.
+In short, yes, there are biases at play, but these do not affect our results.
 We’ve discussed them below, and have included a version of this discussion in the \textbf{Methods} section of the new draft.
@@
 
-In practice, we think that the model would properly fit a spectrum where this kind of mode-overlapping was happening.
-The $\ell=0$ modes don’t split, and so if a $\ell=2$ mode were split so far that overlap was occurring, the $\ell=0$ mode would appear broadened or asymmetrical, which is not degenerate with any other model states.
-There would still be a constraint on the splitting from the lower-frequency peaks.
+In practice, the mode frequency model would properly fit a spectrum where this kind of mode-overlapping was happening.
+The $\ell=0$ modes don’t split, and so if a $\ell=2$ mode were split so far that overlap was occurring, the power distribution of the $\ell=0$ mode would change, which is not degenerate with any other model states.
+There would also still be a constraint on the splitting from the lower-frequency split components of the $\ell=2$ mode, as well as constraints on the exact mode frequencies and linewidths from fits to other modes in the spectrum.
 We can envision there being an issue if an $\ell=2$ mode is overlapping with an $\ell=1$ mode at lower frequencies as well, however this would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.
 
-In our sample, there are 9 stars for which we measured splittings faster than the limit of $2\nu_s > \delta\nu{02}$.
+In our sample, there are 9 stars for which we measured splittings greater than the limit of $2\nu_s > \delta\nu{02}$.
 All these stars showed good agreement with previous work, and were well converged, which implies that asteroseismic models such as ours can handle such mode overlap.
-But as far as our conclusions are concerned, all 9 are either Hot or Subgiant stars, which we show don’t impact our conclusions either way in the paper.
+As far as our conclusions are concerned, all 9 are either Hot or Subgiant stars, which we show don’t impact our conclusions either way in the paper.
 
 \item \textit{Slow rotating stars:} Below, the reviewer raises concerns that for a limit of $\nu_s < 2\Gamma$ (when the splitting is smaller than the double the linewidth), splitting may not be accurately constrained.
-We dont believe this is the fundamental limit on this measurement, as splitting instead more frequently causes a change in the power distribution in frequency of the modes.
+This is not the fundamental limit on this measurement, and is instead a soft limit (making detection more difficult in stars low-signal-to-noise).
+Asteroseismic splitting causes a change in the power distribution in frequency of the modes.
 Detection of this change makes it possible to measure seismic rotation even when the split components are not fully separated.
 It is also worth noting that the non-split radial ($\ell=0$) modes provide strong constraints on the variation of linewidth with frequency.
-We discuss this more below.
-If there is to be a hard limit at which the the effects of splitting can not be measured, we suggest that it is when it would be impossible to resolve it, so where $\nu_s < 2/T$, two times the frequency bin width.
+
+ If there is to be a hard limit at which the the effects of splitting can not be measured, we suggest that it is where $\nu_s < 2/T$, two times the frequency bin width.
 The bin width is set by observing time, so to make an conservative estimate, we can take our star with the shortest observing time  (0.49 years).
-For this star, the limit on measuring rotation would be ~89 days (and going up for longer observing baselines).
-Of course, as discussed below, as you get to slower rotation rates it becomes harder to constrain the small rate of mode splitting and so the uncertainty will increase.
-We believe this is dealt with appropriately in our model comparison through the use of hierarchical models.
+For this star, the limit on measuring rotation would be ~89 days (and increasing for longer observing baselines).
+As discussed below, as you get to slower rotation rates it becomes harder to constrain the small rate of mode splitting and so the uncertainty will increase.
+This is dealt with appropriately in our model comparison through the use of hierarchical models.
 \end{enumerate}
 
-Hopefully with this discussion we’ve shown that both the slow (hard limit) and fast (soft limit) limits on measuring rotation with asteroseismology shouldn’t affect the analysis driving our conclusions, which is done by stars between 10 and 40 days.
+Hopefully with this discussion we’ve shown that both the slow (hard limit) and fast (soft limit) limits on measuring rotation with asteroseismology do not affect the analysis driving our conclusions, which is done by stars between 10 and 40 days.
 We’ve added a plot below which should help illustrate our arguments.
@@
 
+\begin{figure}[h!]
 \includegraphics[width=\textwidth]{image1.png}
+\caption{Representation of the limits on fast and slow rotation rates.
+The blue line represents how this limit changes with the small separation (for the fast limit) and the observation baseline (slow limit).
+The circles represent where stars in our sample fall on these diagrams, and are coloured by their rotation rate.}
+\end{figure}
 
@@
 scales inversely with log g, and therefore age on the main sequence).
-More active, magnetic stars may also suppress their oscillation modes, meaning that it is actually more likely to detect seismic oscillations in older stars.
+More active, magnetic stars may also suppress their oscillation modes, meaning that it is more likely to detect seismic oscillations in older stars.
 Because of both these effects asteroseismic detection probabilities are slightly biased towards older stars on the main sequence, not younger.
@@
 }
-With regards to the observational bias, we don’t believe this is an issue (see our response above), and have tried to make this clearer in the paper.
+With regards to the observational bias, see above.
 
-With regards to the rotation models: we agree, which is why we want to explore this option in a future paper, as mentioned in the conclusions.
-It is our opinion that performing this comparison in a separate work would be more appropriate.
-The two models we use to compare to our data in this work have already been used in the past to forward-model the Kepler field (see van Saders et al.
-(2019)), so their inclusion here is straightforward.
-It is also worth pointing out that most rotation models without weakened magnetic braking will have pretty similar predictions in this regime our sample occupies anyway, as they are all calibrated to reproduce the Sun (and at younger ages, clusters), and so the largest difference between models will come from the inclusion of a change in the braking law.
-It’s not that we think that such a comparison isn’t important -- on the contrary -- but we think it should be explored in a separate paper with more of a focus on the differences in theoretical models, and including a much broader range of models both with- and without changes to the braking.
-
-We’ve tried to be careful throughout and reiterate that this is only a comparison of two models, so that there isn’t any confusion for the readers.\\
+With regards to the rotation models: It is our opinion that performing this comparison in a separate work would be more appropriate.
+Most rotation models without weakened magnetic braking will have similar predictions in this regime our sample occupies, as they are all calibrated to reproduce the Sun (and at younger ages, clusters), and so the largest difference between models will come from the inclusion of a change in the braking law.
+It’s not that we think that such a comparison isn’t important -- on the contrary -- but it should be explored in a separate paper with more of a focus on the differences in theoretical models, and including a much broader range of models both with- and without changes to the braking.\\
 
@@
 
-We believe that we do have enough accurate measurements for the slow rotating stars, in this case referring to those with periods of roughly 20 days and up.
-\textbf{Extended Data} Figures 3 and 4 (Figures 7 and 8 in the old draft) show that stars in this regime appear to be consistent with with previous measurements of rotation where those are available.
-Based on these comparisons to external data, we think the accuracy is sufficient.\\
+We are confident that the accuracy of the measurements for the slow rotating stars is sufficient, in this case referring to those with periods of roughly 20 days and up.
+\textbf{Extended Data} Figures 3 and 4 (Figures 7 and 8 in the old draft) show that stars in this regime are consistent with with previous measurements of asteroseismic rotation where those are available.\\
 
@@
 
-We strongly disagree, and so hopefully we can convince the reviewer.
-The purpose of \textbf{Extended Data} Figure 2 (Figure 6 in the old draft) is to check whether our inclination angle returns the prior, which it doesn’t in the majority of cases.
-Even in the cases where it does closely resemble the prior, our Bayesian approach will ensure that this is properly reflected in the results for rotation period.
+The purpose of \textbf{Extended Data} Figure 2 (Figure 6 in the old draft) is to check whether our inclination angle returns the prior.
+In the majority of cases the spread of the posterior distribution is smaller than the prior, indicating that our measurement of $i$ is driven by the data.
+Even in the cases where it does closely resemble the prior, our Bayesian approach will ensure that this is properly reflected in the results for the rotation period.
 In our analysis, rotational splitting ($\nu_{s}\sin(i)$), inclination ($i$) and rotation ($P$) are all marginalised over, and so the uncertainties reflect the posterior probability distribution these values can take given the data.
@@
 We have added extra description to the figure caption that clarifies this.
-We would say that the stellar rotation rate is well determined for individual stars in spite of the difficulties with constraining inclination angle, because it has been fully marginalised over in our Bayesian analysis.
+The stellar rotation rate is well determined for individual stars in spite of the difficulties with constraining inclination angle, because it has been fully marginalised over in our Bayesian analysis.
 
@@
 
-Our model is based on the Matt formalism, although our choices of scalings for stellar loss and magnetism are different (see van Saders et al.
+Our model is based on the Matt formalism, although our choices of scalings for stellar angular momentum loss and magnetism are different (see van Saders et al.
 2019), and so our models are more similar to the Matt models than other models available in the literature (see Fig 1 in Matt et al.
@@
 
-We considered including such a plot in our paper, but omitted it for specific reasons, which we can hopefully convince the referee of.
-
-Most importantly, we don’t believe that such a plot would provide any new information beyond what is already included in the paper.
+We considered including such a plot in our paper, but omitted it because such a plot would not provide any new information beyond what is already included in the paper.
 The core of this paper is the use of a probabilistic analysis of a full ensemble of stars to distinguish between two competing models.
-We believe that a plot that shows that \textit{individual} stars are in \textit{disagreement} with a standard evolution doesn’t add any new information, especially when the format requires conciseness (and the discrepancy already been demonstrated in previous work for many stars in this sample).
+A plot that shows that \textit{individual} stars are in \textit{disagreement} with a standard evolution doesn’t add any new information, especially when the format requires conciseness (and the discrepancy already been demonstrated in previous work for many stars in this sample).
 We think it is more important to tread new ground with a Bayesian method that accounts for multiple parameter spaces (metallicity being the most important one), to drive our conclusions.

### 2020-10-09 paper/natastron/response/coverletter.tex
Updated response with martin's comments

\documentclass[11pt, a4paper, sans, colorlinks, linkcolor=True]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{black}
\usepackage{ragged2e}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[left=1in, right=1in, bottom=0.5in, top=0.5in]{geometry}
%\addtolength{\topmargin}{-.875in}
\pagenumbering{gobble}
\usepackage{setspace}

%Personal Details
\name{Oliver James}{Hall}
\title{Coverletter}
\address{European Space Agency (ESA)\\ European Space Research and Technology Centre (ESTEC)\\ Keplerlaan 1}{2201 AZ Noordwijk}{The Netherlands}
\email{ojhall94@gmail.com}
\homepage{https://www.ojhall94.github.io}

\begin{document}
\definecolor{links}{HTML}{3f28bd}
\hypersetup{urlcolor=links}
\recipient{\ }{\ }
\date{\today}
\opening{Dear Dr. Woods,}
\makelettertitle
\justify
\vspace{-0.5cm}

We hope this letter finds you well. We have completed our response to the reviewer, which is attached below this cover letter (and uploaded separately with resubmission). Based on our discussion over email on the reformatting of the original draft, we have done our best to reshuffle the paper's contents. We think the updated draft best matches the Nature format while keeping it accessible to the reader. However the Methods is longer than conventional, so please let us know if you have any suggestions on what we should move to the Supplementary Information, if necessary.

We have also added data and code availability statements. At the moment, our main results table is in Extended Data, as we don't think it is necessary to include it in the main text. Ideally we would publish this table digitally along with the article (as well as host it on Vizier). If you have any input on whether this table should be (partially) included in the main text, we would be grateful also.

The word count breakdown is as follows:
\begin{itemize}
	\item Abstract: 196
	\item Introduction: 500
	\item Main body (incl. Introduction): 2721
	\item Methods: 5145
	\item Supplementary Information: 2544
	\item Extended Data: Figures and Table only.
\end{itemize}

\vspace{0.5cm}

Yours sincerely, \\
\vspace{0.5em}
\includegraphics[scale=0.2]{signature.png} \\ 
\vspace{0.5em}
\textbf{Oliver J. Hall}, on behalf of the authors. \\
\end{document}

### 2020-10-09 paper/natastron/response/response.tex
Finished respones

@@
 
-\section*{Response to the Referees}
+\section*{Response to the Referee}
 
-To whom it may concern,
-
-First we would like to thank the reviewer for their comments, which have helped us improve this manuscript.
+First we would like to thank the referee for their comments, which have helped us improve this manuscript.
 The paper has now been re-written to fit the Nature format, and therefore some of the content has changed or moved.
@@
 \textit{Bias in rotation detection:} stars that are rotating very slowly will show very small splittings, which may be indistinguishable from a non-rotating case, whereas stars that are spinning very fast may find that their splitting is so wide that they cross over with split modes at different radial orders.
-We’ve done some calculations to show that this shouldn’t affect the region of rotation we’re interested in.
+We’ve done some calculations to show that this doesn’t affect the region of rotation we’re interested in.
 \begin{enumerate}
@@
 For the star in our sample with the smallest $\delta\nu_{02}$ (so the highest risk of this happening), this limit is at 8.8 days.
-However for the star with the largest $\delta\nu_{02}$, this lies at ~2 days.
+However for the star with the largest $\delta\nu_{02}$, this lies at $\sim 2$ days.
 
-In practice, the mode frequency model would properly fit a spectrum where this kind of mode-overlapping was happening.
+In practice, the mode frequency model would still properly fit a spectrum where this kind of mode-overlapping was happening.
 The $\ell=0$ modes don’t split, and so if a $\ell=2$ mode were split so far that overlap was occurring, the power distribution of the $\ell=0$ mode would change, which is not degenerate with any other model states.
@@
 
-In our sample, there are 9 stars for which we measured splittings greater than the limit of $2\nu_s > \delta\nu{02}$.
+In our sample, there are 9 stars for which we measured splittings greater than the limit of $2\nu_s > \delta\nu_{02}$.
 All these stars showed good agreement with previous work, and were well converged, which implies that asteroseismic models such as ours can handle such mode overlap.
@@
 \item \textit{Slow rotating stars:} Below, the reviewer raises concerns that for a limit of $\nu_s < 2\Gamma$ (when the splitting is smaller than the double the linewidth), splitting may not be accurately constrained.
-This is not the fundamental limit on this measurement, and is instead a soft limit (making detection more difficult in stars low-signal-to-noise).
+This is not the fundamental limit on this measurement, and is instead a very soft limit (making detection more difficult in stars low-signal-to-noise).
 Asteroseismic splitting causes a change in the power distribution in frequency of the modes.
 Detection of this change makes it possible to measure seismic rotation even when the split components are not fully separated.
-It is also worth noting that the non-split radial ($\ell=0$) modes provide strong constraints on the variation of linewidth with frequency.
+It is also worth noting that the non-split radial ($\ell=0$) modes provide strong constraints on the variation of linewidth with frequency, further constraining the change due to splitting.
 
- If there is to be a hard limit at which the the effects of splitting can not be measured, we suggest that it is where $\nu_s < 2/T$, two times the frequency bin width.
+ If there is to be a hard limit at which the the effects of splitting can not be measured, it is where $\nu_s < 2/T$, two times the frequency bin width.
 The bin width is set by observing time, so to make an conservative estimate, we can take our star with the shortest observing time  (0.49 years).
@@
 (2019) for Kepler and TESS respectively, and Mathur et al.
-2019 for the magnetic suppression.
+(2019) for the magnetic suppression.
 
-Between these two statements -- that our method measures accurate rotation in the regions that matter, and that asteroseismology is biased towards older, not younger, stars -- we don’t believe that observing biases affect our conclusions.
+Between these two statements -- that our method measures accurate rotation in the regions that matter, and that asteroseismology is biased towards older, not younger, stars -- we are confident that observing biases do not affect our conclusions.
 We’ve included a paraphrased version of the discussion as above in the paper \textbf{Methods} Section 3.4.
@@
 It is indeed harder to measure rotation in slow rotators (as mentioned above), and so fewer of these stars were able to converge within the computational time we had available.
-When we repeated the model comparison analysis while still including these stars, our conclusions did not change, a statement which we have now included in the paper.\\
+When we repeated the rotational model comparison analysis while still including these stars, our conclusions did not change, a statement which we have now included in the paper.\\
 
@@
 We’ve added a line to indicate the border of this region.
-In addition, the majority of slowly rotating stars in the Figure lie above the 1:1 line, implying that if spectroscopic values were the truth, seismology would find rotation rates that are *slower* than the truth, which would bias our results towards a standard model, and not towards weakened magnetic braking.
+In addition, the majority of slowly rotating stars in the Figure lie above the 1:1 line, implying that if spectroscopic values were the truth, seismology would find rotation rates that are \textit{slower} than the truth, which would bias our results towards a standard model, and not towards weakened magnetic braking.
 
@@
 
-If I’m interpreting the reviewer’s report correctly, we understand that they are concerned that there are fewer slowly rotating stars, and that those that are slowly rotating appear to have large uncertainties.
-There are relatively few stars in this slowly rotating regime, and we address this in the comments about observational bias above.
-We don’t think the larger uncertainties should raise concern.
+If we are interpreting the reviewer’s report correctly, we understand that they are concerned that there are fewer slowly rotating stars, and that those that are slowly rotating appear to have large uncertainties.
+There are relatively few stars in this slowly rotating regime, either due to weakened magnetic braking or observational bias, and we address this in the comments about observational bias above.
 The latent variable model we use to compare the two rotational evolution models allowed us to incorporate the uncertainties appropriately, and bear in mind that it’s not just rotation space where the models are compared, but mass, metallicity, temperature, and age as well.\\
@@
 The Matt et al.
-2015 model and associated paper puzzled over the fact that the apparent edge of the period distribution in the McQuillan sample was at roughly the solar age in their model (see fig 3 in Matt 2015), and wondered whether it meant the age distribution in the Kepler field was very different (younger) than expected.
+(2015) model and associated paper puzzled over the fact that the apparent edge of the period distribution in the McQuillan sample was at roughly the solar age in their model (see Fig 3 in Matt 2015), and wondered whether it meant the age distribution in the \textit{Kepler} field was very different (younger) than expected.
 Their 4 Gyr model is already at the McQuillan period distribution edge.
 Their model would have predicted the same long rotation periods as our standard model, with differences in detail because of the different braking law scalings.
-In other words: a 8-9 Gyr star in the Matt model would not be sitting on that McQuillan edge, it would be above it.
+In other words: a 8-9 Gyr star in the Matt model would not be sitting on the edge of the McQuillan sample, it would be above it.
 
@@
 
-When transferring the methods to the Supplementary Information, we have tried to improve the explanations of the more complicated terms (such as Gaussian Processes), and have hopefully improved this somewhat.
+When transferring the methods to the Supplementary Information, we have tried to improve the explanations of the more complicated terms (such as Gaussian Processes).
 
@@
 	\item Table 1 is has been moved to \textbf{Extended Data}.
-	\item Section 5.1.1., 5.1.2., and the spectroscopy half of 5.1.3. have all been moved to \textbf{Methods}. Their conclusions are mentioned in the main text.
-	\item Section 5.2.2, 5.2.3. and 5.2.4. have all been moved to \textbf{Methods.} Their conclusions are mentioned in the main text.
+	\item Sections 5.1.1., 5.1.2., and the spectroscopy half of 5.1.3. have all been moved to \textbf{Methods}. Their conclusions are mentioned in the main text.
+	\item Sections 5.2.2, 5.2.3. and 5.2.4. have all been moved to \textbf{Methods.} Their conclusions are mentioned in the main text.
 	\item Figures 3, 6, 7, 8 and 9 have been moved to \textbf{Extended Data} and are referenced from \textbf{Methods}.

### 2020-10-09 paper/natastron/ed.tex
prep for submission

@@
 	\includegraphics[width=\textwidth]{Images/litcomp_alt2.pdf}
-	\caption{Comparisons between posterior estimates of rotational parameters from this work, LEGACY and `Kages' \cite[private communication]{davies+2016, lund+2017}.
+	\caption{Comparisons between posterior estimates of rotational parameters from this work, LEGACY and `Kages' \cite[private communication]{m_davies+2016, m_lund+2017}.
 Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$).

### 2020-10-09 paper/natastron/bblmethods.tex

@@
 
+\bibitem{m_halbwachs1986}
+\bibinfo{author}{{Halbwachs}, J.~L.}
+\newblock \bibinfo{title}{{Common proper motion stars in the AGK 3.}}
+\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics, Supplement Series}} \textbf{\bibinfo{volume}{66}},
+\bibinfo{pages}{131--148} (\bibinfo{year}{1986}).
+
+\bibitem{m_white+2013}
+\bibinfo{author}{White, T.~R.} \emph{et~al.}
+\newblock \bibinfo{title}{Interferometric radii of bright {{Kepler}} stars with
+	the {{CHARA Array}}: {{Cygni}} and 16 {{Cygni A}} and {{B}}}.
+\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
+		Society}} \textbf{\bibinfo{volume}{433}}, \bibinfo{pages}{1262}
+(\bibinfo{year}{2013}).
+
 \bibitem{m_maxted+2015}
@@
 
+\bibitem{m_davies+2016}
+\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
+\newblock \bibinfo{title}{Oscillation frequencies for 35 {{Kepler}} solar-type
+	planet-hosting stars using {{Bayesian}} techniques and machine learning}.
+\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
+		Society}} \textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183}
+(\bibinfo{year}{2016}).
+
+\bibitem{m_lund+2017}
+\bibinfo{author}{Lund, M.~N.} \emph{et~al.}
+\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
+	{{Kepler Asteroseismic LEGACY Sample}}. {{I}}. {{Oscillation Mode
+			Parameters}}}.
+\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+\textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{172} (\bibinfo{year}{2017}).
 \end{thebibliography}

### 2020-10-09 paper/natastron/bblpaper.tex

@@
 	\bibinfo{pages}{arXiv:1911.04518} (\bibinfo{year}{2019}).
+
+	\bibitem{barnes+2016}
+	\bibinfo{author}{Barnes, S.~A.}, \bibinfo{author}{Weingrill, J.},
+	\bibinfo{author}{Fritzewski, D.}, \bibinfo{author}{Strassmeier, K.~G.} \&
+	\bibinfo{author}{Platais, I.}
+	\newblock \bibinfo{title}{Rotation {{Periods}} for {{Cool Stars}} in the 4
+		{{Gyr}} old {{Open Cluster M67}}, {{The Solar}}-{{Stellar Connection}}, and
+		the {{Applicability}} of {{Gyrochronology}} to at least {{Solar Age}}}.
+	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\textbf{\bibinfo{volume}{823}}, \bibinfo{pages}{16} (\bibinfo{year}{2016}).
 
@@
 
+	\bibitem{metcalfe+2016}
+	\bibinfo{author}{Metcalfe, T.~S.}, \bibinfo{author}{Egeland, R.} \&
+	\bibinfo{author}{{van Saders}, J.}
+	\newblock \bibinfo{title}{Stellar {{Evidence That}} the {{Solar Dynamo May Be}}
+		in {{Transition}}}.
+	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Letters}}
+	\textbf{\bibinfo{volume}{826}}, \bibinfo{pages}{L2} (\bibinfo{year}{2016}).
+
 	\bibitem{metcalfe+2019}
@@
 	\textbf{\bibinfo{volume}{799}}, \bibinfo{pages}{L23} (\bibinfo{year}{2015}).
+
+	\bibitem{reinhold+2020}
+	\bibinfo{author}{{Reinhold}, T.} \emph{et~al.}
+	\newblock \bibinfo{title}{{The Sun is less active than other solar-like
+			stars}}.
+	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{368}},
+	\bibinfo{pages}{518--521} (\bibinfo{year}{2020}).
+	\newblock \eprint{2005.01401}.
 
@@
 	(\bibinfo{year}{2014}).
+
+	\bibitem{blanton+2019}
+	\bibinfo{author}{{Blanton}, M.} \emph{et~al.}
+	\newblock \bibinfo{title}{{The Sloan Digital Sky Survey as an Archetypal
+			Mid-Scale Program}}.
+	\newblock In \emph{\bibinfo{booktitle}{Bulletin of the American Astronomical
+			Society}}, vol.~\bibinfo{volume}{51}, \bibinfo{pages}{196}
+	(\bibinfo{year}{2019}).
+
+	\bibitem{kollmeier+2019}
+	\bibinfo{author}{{Kollmeier}, J.} \emph{et~al.}
+	\newblock \bibinfo{title}{{SDSS-V Pioneering Panoptic Spectroscopy}}.
+	\newblock In \emph{\bibinfo{booktitle}{Bulletin of the American Astronomical
+			Society}}, vol.~\bibinfo{volume}{51}, \bibinfo{pages}{274}
+	(\bibinfo{year}{2019}).
+
 \end{thebibliography}

### 2020-10-09 paper/natastron/methods.tex

@@
 In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background, modes of oscillation, and white noise, while accounting for rotational splitting.
-The foundations of this approach follows best-practices in asteroseismology \cite{m_davies+2015}, fitting Harvey profiles for the background \cite{m_harvey1985}, and expressing the frequencies of the modes using an asymptotic expression \cite{m_tassoul1980, m_vrard+2016}.
+The foundations of this approach follows best-practices in asteroseismology \cite{m_davies+2015}, fitting Harvey profiles for the background \cite{m_harvey1985} and expressing the frequencies of the modes using an asymptotic expression \cite{m_tassoul1980, m_vrard+2016}.
 
@@
 
-	In practice, the model would still properly fit a spectrum where this kind of mode-overlapping occurred, as the $\ell = 0$ modes don't split, meaning that there are no degenerate solutions in this regime.
+	In practice, the model still properly fits a spectrum where this kind of mode-overlapping occurred, as the $\ell = 0$ modes don't split, meaning that there are no degenerate solutions in this regime, and further constraints can be obtained from the other modes and split components in the spectrum.
 A more serious issue may be when the $\ell = 1$ mode at lower frequencies overlapped with the $\ell = 2$ mode as well, which would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.
@@
 
-Second, the binary pairs of KIC 9139151 \& 9139163 and 16 Cyg A \& B are individually observed binary components with wide orbital separations, so we do not expect their binarity to have affected their rotational evolution.
+Second, the binary pairs of KIC 9139151 \& 9139163 and 16 Cyg A \& B are individually observed binary components with wide orbital separations, so we do not expect their binarity to have affected their rotational evolution \cite{m_halbwachs1986, m_white+2013}.
 
@@
 (2016) and Lund et al.
-(2017) \cite{silvaaguirre+2015, davies+2016, lund+2017, silvaaguirre+2017 }.
+(2017) \cite{m_silvaaguirre+2015, m_silvaaguirre+2017,m_davies+2016, m_lund+2017}.
 Parameter distributions of the \kepler field used to alter our stellar population models were taken from Berger et al.
-(2020) \cite{berger+2020}.\\
+(2020) \cite{m_berger+2020}.\\
 

### 2021-01-05 paper/natastron/1st_draft/comments.tex
minor corrections...

--- 2020-09-29 paper/natastron/comments.tex
@@
 
-Apologies if this comes across as a bit brutal… you have clearly put a lot of work into this project and of course you want to display it in a paper.
-However, papers in NAstro or Nature or Science require a very different approach to paper-writing… they are quite a challenge to write, because you need a logical flow, a certain level of detail, great focus, and of course everything you would need to make your work reproducible… but all in a very small space.
-
 So, as a reminder, your main text (intro, brief outline of procedure, results, discussion, conclusion/outlook) should be about 3,000-3,500 words (not including Abstract), your Methods section should be a similar length, and everything else can go into the Supplementary Information.
@@
 
-I hope that helps, and if you have any further questions, feel free to get in touch.
+Yes… the distinction between Methods, SI and Extended Data is a bit murky, especially as our website instructions have not caught up with our addition of Extended Data yet.
+
+As for your questions, yes, you can move Figs. 6–8 to the Extended Data, where they’ll be renamed as ‘Extended Data Figure 1’, etc. and you can cite them from the Methods.
+
+As for the software citations… yes, this is an issue.
+Unfortunately citations aren’t allowed in the Acknowledgments and citations in the Supplementary Information don’t ‘count’ (they are not indexed by Web of Science or ADS, etc.).
+My suggestion would be to have some citation-loaded sentences about the software packages scattered throughout the Methods… but don’t make these sound like acknowledgments or the copy editors will move them, and strip the citations… Sorry about this, it is a bit of a workaround.

### 2021-01-05 paper/natastron/1st_draft/paper.tex
minor corrections...

--- 2020-10-09 paper/natastron/paper.tex
@@
 Stars that were not included in the fitting process are transparent.
-The errorbars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions.}
+The errorbars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions, and are smaller than the points in some cases.}
 	\label{fig:protlit}
@@
 
-\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two population models of rotational evolution \cite{vansaders+2019}: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{vansaders+2016,skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model') \cite{vansaders+2016}  The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$\footnote{The Rossby number may be defined as $Ro \equiv P/\tau_{\rm cz}$, where $\tau_{\rm cz}$ is the convective turnover timescale, and $P$ is the rotation.
+\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two population models of rotational evolution \cite{vansaders+2019}: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{vansaders+2016,skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model') \cite{vansaders+2016}.
+The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$\footnote{The Rossby number may be defined as $Ro \equiv P/\tau_{\rm cz}$, where $\tau_{\rm cz}$ is the convective turnover timescale, and $P$ is the rotation.
 The Rossby number roughly scales inversely with stellar activity (and so increases as stars age).}.
@@
 
-In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting, excluding those with a number of effective samples $n_{\rm eff} < 1000$ and a Gelman-Rubin metric of $\hat{R}>1.1$ \cite{gelman+rubin1992,salvatier+2016} (see \textbf{Extended Data} Table \ref{tab:results}).
+In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting, excluding those with a number of effective samples $n_{\rm eff} < 1000$ and a Gelman-Rubin metric of $\hat{R}<1.1$ \cite{gelman+rubin1992,salvatier+2016} (see \textbf{Extended Data} Table \ref{tab:results}).
 Two stars with low metallicities ($< -0.8\, \rm {dex}$) that fell outside the boundaries of our stellar models were also excluded.
@@
 
-Both hot and sub-giant stars do not strongly prefer one model over the other (both crossing the $P_{\rm{s}} = 0.5$ line at roughly $45\%$), which is expected given that these stars in our sample all lie at hot temperatures near the Kraft break.
-When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), this the total probability below $P_{\rm{s}} = 0.5$ is 96.6\%.
+Both hot and sub-giant stars do not strongly prefer one model over the other (with both cumulative probabilities crossing the $P_{\rm{s}} = 0.5$ line at roughly $45\%$), which is expected given that these stars in our sample all lie at hot temperatures near the Kraft break.
+When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability below $P_{\rm{s}} = 0.5$ is 96.6\%.
 \\
@@
 
-%	\item We present new techniques for asteroseismic `peak-bagging' frequency analyses, specifically: expressing well known empirical asteroseismic relations in a hierarchical modeling structure to account for small-scale effects not included in our model (such as acoustic glitches), and replacing uninformative empirical relations with Gaussian Process priors, detailed in the \textbf{Supplementary Information}.
-
 \end{enumerate}
@@
 \input{bblpaper.tex}
+%\bibliographystyle{naturemag}
+%\bibliography{library.bib} % if your bibtex file is called example.bib
 

### 2021-01-05 paper/natastron/1st_draft/response/coverletter.tex
minor corrections...

--- 2020-10-09 paper/natastron/response/coverletter.tex
@@
 Ideally we would publish this table digitally along with the article (as well as host it on Vizier).
-If you have any input on whether this table should be (partially) included in the main text, we would be grateful also.
+If you have any input on whether this table should be (partially) included in the main text, or other thoughts on how to best present it in the Nature Astronomy format, we would be grateful also.
 
@@
 	\item Supplementary Information: 2544
-	\item Extended Data: Figures and Table only.
 \end{itemize}
 
+And the number of figures, tables and references are as follows:
+\begin{itemize}
+	\item Main body: 4 figures (1.2 MB), 51 references
+	\item Methods: 0 figures, 57 references
+	\item Supplementary Information: 1 figure (298 KB), 25 references
+	\item Extended Data: 5 Figures (1.1 MB), 1 Table (4 pages, 29 KB), 10 references
+\end{itemize}
+
+The references in the \textbf{Extended Data} are numbered following the references listed under Methods.
 \vspace{0.5cm}

### 2021-01-05 paper/natastron/2nd_draft/methods.tex
minor corrections...

--- 2020-10-09 paper/natastron/methods.tex
@@
 
+\subsection{\rtwo{Seismic vs Surface rotation}}
+As described in the main body of the paper, we compared a subsample of our asteroesismic rotation rates to surface rotation rates from spot rotation, where available.
+Both the surface $P_{\rm surf}$ and seismic $P_{\rm seis}$ rotation rates have associated uncertainties.
+Instead of fitting the slope between these two values directly, we instead fit the distribution
+
+\begin{equation}
+	p(\frac{P_{\rm seis}}{P_{\rm surf}}\, |\, m) = \mathcal{N}(m, \sigma_\frac{P_{\rm seis}}{P_{\rm surf}})\, ,
+\end{equation}
+
+\noindent where $m$ is the slope, and $\sigma_\frac{P_{\rm seis}}{P_{\rm surf}}$ is the uncertainty corresponding to $\frac{P_{\rm seis}}{P_{\rm surf}}$, following the propagation of the errors on both values.
+We used the larger of the asymmetrical uncertainties on asteroseismic rotation from our analysis.
+The model was fit using \texttt{PyMC3} for 2000 iterations each on 4 chains.
+Five stars for which both surface and seismic rotation were available, but which had a surface rotation above the 1.8:1 line, were excluded from this analysis.
+This was to exclude likely multiples of the true rotation rate skewing the fit, as measurements of double the true rotation may occur in spot rotation measurements.
+
+Our fit found a value of $m = 0.96 \pm 0.03$ using 48 stars.
+We reran this analysis using the 21 stars in this sample which had a value of $P_{\rm s} < 0.5$ in our stellar model analysis, preferring the WMB model.
+A fit to these stars alone found a value of $m = 0.96 \pm 0.04$.
+
 \subsection{Seismic vs spectroscopic rotation}

### 2021-01-05 paper/natastron/2nd_draft/paper.tex
minor corrections...

--- 2021-01-05 paper/natastron/1st_draft/paper.tex
@@
 \usepackage{xspace}
+\usepackage{color}
 \usepackage{graphicx}
@@
 \newcommand{\gaia}{\emph{Gaia}\xspace}
+\newcommand{\rtwo}[1]{\textcolor{red}{{#1}}}
 
@@
 \begin{document}
-\noindent\textbf{\LARGE{New asteroseismic rotation rates of \emph{Kepler} dwarfs show strong agreement with weakened magnetic braking on the late-age main sequence}}\\
+\noindent\textbf{\LARGE{New asteroseismic rotation rates of \emph{Kepler} dwarfs show strong \rtwo{preference for} weakened magnetic braking on the late-age main sequence}}\\
 
@@
 A large survey of stellar rotation rates measured using star-spots found a lack of slowly rotating stars older then Sun \cite{mcquillan+2014}.
-As activity reduces with age, older stars with fewer star-spots are less likely to have their rotation measured \cite{matt+2015, reinhold+2020}.
+As activity reduces with age, older stars with fewer spots are less likely to have their rotation measured \cite{matt+2015, reinhold+2020}.
 The point at which the detection probability drops appears to lie at a similar level of activity as the expected onset of weakened magnetic braking, placing these two possibilities in opposition to one another \cite{vansaders+2019}.
@@
 Determining whether weakened magnetic braking is a true phenomenon or a bias in star-spot observations requires new measurements of rotation in quiescent stars, which can be provided by asteroseismology.
-A star's rotation causes modes of oscillation to split into multiplets, enabling measurement of independent rotation rates by measuring the rate of splitting \cite{ledoux1951}.
+\rtwo{Rotation causes certain modes of oscillation -- which lie at the same frequency in a non-rotating case -- to shift to higher or lower frequencies.
+The size of this `splitting' provides a means of independently measuring the rotation of the star \cite{ledoux1951}}.
+
 Asteroseismic rotation requires a faster observing cadence and higher signal-to-noise than spot rotation, but does not require spots to be visible, meaning that we can measure rotation for older, quiescent stars that would not have been present in existing rotation catalogues.
-This makes asteroseismic rotation rates a perfect test of weakened magnetic braking on the main sequence.
+%This makes asteroseismic rotation rates a perfect test of weakened magnetic braking on the main sequence. 
 Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of  ages, and determined whether this new ensemble agrees more closely with a classical rotational evolution scenario, or one in which weakened magnetic braking takes place.\\
@@
 This is not the case for asteroseismic rotation, and so some stars may appear at the 2:1 and 1:2 lines in the figure.
-We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid likely multiples of the true rotation rate acting as outliers (transparent in the Figure).
+We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid likely multiples of the true rotation rate acting as outliers (transparent in the Figure, see \textit{\textbf{Methods}} for details.).
 Our fit found a value of $m = 0.96 \pm 0.03$, showing a close agreement ($<2\sigma$) between asteroseismic and surface rotation rates on a population level.
+=
 %Of the stars used in this comparison, 21 had a median value of $P_{\rm s}$ in the gyrochronology analysis. We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.  

### 2021-01-05 paper/natastron/2nd_draft/ed.tex
minor corrections

--- 2020-10-09 paper/natastron/ed.tex
@@
 Here, $\kappa_{\rm{s}}$ and $\kappa_{\rm WMB}$ represent the KDEs of standard and WMB model populations respectively.
-$P_{\rm{s}}$ is the mixture model weighting factor.
+$Q_{\rm{s}}$ is the mixture model weighting factor.
 The latent parameters $\underline{\theta}$, our observations $\underline{\mathcal{D}}$ and their uncertainties $\underline{\sigma_{\mathcal{D}}}$ include temperature (\teff), mass ($M$), log-age ($\ln(t)$), metallicity (\feh) and log-rotation ($\ln(P)$).
-This model is \textit{hierarchical}, as all the latent parameters are drawn from the common probability distribution set by $P_{\rm{s}}$ and described in Equation \ref{eq:mixturell}.}
+This model is \textit{hierarchical}, as all the latent parameters are drawn from the common probability distribution set by $Q_{\rm{s}}$ and described in Equation \ref{eq:mixturell}.}
 	\label{fig:pgm}

### 2021-01-05 paper/natastron/2nd_draft/methods.tex
minor corrections

@@
 We evaluated our data against both models simultaneously by treating the data as being drawn from a mixture of both model KDEs.
-In this mixture model structure, the two KDEs were modulated by a weighting factor, $P_{\rm s}$.
-In the limit $P_{\rm s} \rightarrow 1$, the data are most likely drawn from the standard model.
-In the limit $P_{\rm s} \rightarrow 0$, the data are most likely drawn from the WMB model.
+In this mixture model structure, the two KDEs were modulated by a weighting factor, $Q_{\rm s}$.
+In the limit $Q_{\rm s} \rightarrow 1$, the data are most likely drawn from the standard model.
+In the limit $Q_{\rm s} \rightarrow 0$, the data are most likely drawn from the WMB model.
 
-The posterior probability of obtaining $P_{\rm s}$ and additional parameters $\theta$ given our data $\mathcal{D}$ is $p(P_{\rm{s}}, \theta | \mathcal{D})$.
+The posterior probability of obtaining $Q_{\rm s}$ and additional parameters $\theta$ given our data $\mathcal{D}$ is $p(Q_{\rm{s}}, \theta | \mathcal{D})$.
 Using Bayes equation, we can express this as:
@@
 \begin{equation}\label{eq:modelll}
-	p(P_{\rm{s}}, \theta | \mathcal{D}) \propto p(\mathcal{D} | \theta)\ p(\theta | P_{\rm{s}}, \kappa_{\rm{s}}, \kappa_{\rm{WMB}})\ p(P_{\rm{s}})\, ,
+	p(Q_{\rm{s}}, \theta | \mathcal{D}) \propto p(\mathcal{D} | \theta)\ p(\theta | Q_{\rm{s}}, \kappa_{\rm{s}}, \kappa_{\rm{WMB}})\ p(Q_{\rm{s}})\, ,
 \end{equation}
@@
 \noindent where $\kappa_{\rm{s}}$ and $\kappa_{\rm{WMB}}$ are the KDE functions for the standard and WMB models respectively, and $\theta$ here are parameters, $\theta = \{M, \teff, \ln(t), \feh, \ln(P)\}$.
-As done above for the asteroseismic model, the parameters $\theta$ may be referred to as latent parameters, as they form a step between the parameter we want to infer ($P_{\rm{s}}$) and our data.
+As done above for the asteroseismic model, the parameters $\theta$ may be referred to as latent parameters, as they form a step between the parameter we want to infer ($Q_{\rm{s}}$) and our data.
 Using this approach allowed our model to properly take into account the observational uncertainties on the data.
 
-The second component on the right hand side of Equation \ref{eq:modelll} describes the probability of obtaining our latent parameters $\theta$ given our KDEs and the mixture model weighting parameter $P_{\rm s}$, and is described by the mixture model
+The second component on the right hand side of Equation \ref{eq:modelll} describes the probability of obtaining our latent parameters $\theta$ given our KDEs and the mixture model weighting parameter $Q_{\rm s}$, and is described by the mixture model
 
 \begin{equation}\label{eq:mixturell}
-	p(\theta | P_{\rm{s}}, \kappa_{\rm{s}}, \kappa_{\rm{WMB}}) = P_{\rm s} \times \kappa_{\rm s}(\theta) + (1 - P_{\rm s}) \times \kappa_{\rm WMB}(\theta)\, ,
+	p(\theta | Q_{\rm{s}}, \kappa_{\rm{s}}, \kappa_{\rm{WMB}}) = Q_{\rm s} \times \kappa_{\rm s}(\theta) + (1 - Q_{\rm s}) \times \kappa_{\rm WMB}(\theta)\, ,
 \end{equation}
@@
 This probability function describes a distribution that is a mixture of both KDEs.
-While the KDEs are constant, $P_{\rm s}$ is a free parameter, and so the shape of this distribution can vary.
+While the KDEs are constant, $Q_{\rm s}$ is a free parameter, and so the shape of this distribution can vary.
 The latent parameters $\theta$ are drawn from this distribution, and therefore from some combination of the two stellar models.
@@
 
-The final term, $p(P_{\rm s})$, represents the prior on the mixture model weight, which is uniform between 0 and 1.
+The final term, $p(Q_{\rm s})$, represents the prior on the mixture model weight, which is uniform between 0 and 1.
 A visual representation of our model is shown in \textbf{Extended Data} Figure \ref{fig:pgm}.
 
-Typically, this model would evaluate all stars in our sample against the stellar models simultaneously for a single posterior estimate of $P_{\rm s}$.
+Typically, this model would evaluate all stars in our sample against the stellar models simultaneously for a single posterior estimate of $Q_{\rm s}$.
 At 95 stars, in 5 parameter spaces, this totals 476 free parameters to marginalise over.
@@
 Alternative Markov Chain Monte Carlo techniques \cite[MCMC]{m_foreman-mackey+2013} can more efficiently sample the KDE functions, but can not treat the large number of hierarchical parameters.
-To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $P_{\rm s}$, and multiplied these post hoc to obtain a combined posterior.
-This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications, at the expense of the ability to marginalise for a single value of $P_{\rm s}$ directly.\\
+To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $Q_{\rm s}$, and multiplied these post hoc to obtain a combined posterior.
+This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications, at the expense of the ability to marginalise for a single value of $Q_{\rm s}$ directly.\\
 
@@
 
-After fitting, we took a normalised histogram of the posterior estimate of $P_{\rm s}$ for each star, using 100 bins.
-In this histogram, each bin approximated the value of the posterior function for $P_{\rm s}$.
-The array of 100 bins for all stars were multiplied, resulting in an approximation of the joint posterior probability function for $P_{\rm s}$ given all stars in the ensemble.
+After fitting, we took a normalised histogram of the posterior estimate of $Q_{\rm s}$ for each star, using 100 bins.
+In this histogram, each bin approximated the value of the posterior function for $Q_{\rm s}$.
+The array of 100 bins for all stars were multiplied, resulting in an approximation of the joint posterior probability function for $Q_{\rm s}$ given all stars in the ensemble.
 
@@
 
-A comparison between prior and posterior is shown for 94 stars in $\nu_{\rm s}\sin(i)$, $i$ and $P_{\rm rot}$ in \textbf{Extended Data} Figure \ref{fig:priors}, arranged by age.
+A comparison between prior and posterior is shown for 94 stars in $\nu_{\rm s}\sin(i)$, $i$ and $P$ in \textbf{Extended Data} Figure \ref{fig:priors}, arranged by age.
 In the Figure, results with means and error bars that closely resemble the prior distribution can be interpreted as prior-dominated (i.e.
@@
 The angle of inclination $i$, sampled as $\cos(i)$, more closely follows the prior distribution in most cases.
-Combining the two, the rotation period $P_{\rm rot}$ has no stars directly corresponding to the effective prior on period, and globally follows a trend with increasing age.
+Combining the two, the rotation period $P$ has no stars directly corresponding to the effective prior on period, and globally follows a trend with increasing age.
 The three outliers with fast rotation at late ages (KICs 6603624, 8760414 and 8938364) are discussed in more detail in below.
@@
 Our fit found a value of $m = 0.96 \pm 0.03$ using 48 stars.
-We reran this analysis using the 21 stars in this sample which had a value of $P_{\rm s} < 0.5$ in our stellar model analysis, preferring the WMB model.
+We reran this analysis using the 21 stars in this sample which had a value of $Q_{\rm s} < 0.5$ in our stellar model analysis, preferring the WMB model.
 A fit to these stars alone found a value of $m = 0.96 \pm 0.04$.
@@
 For the stars with the smallest uncertainties, this significantly limits the size of the KDE being evaluated (as subsections of the full stellar models are used to evaluate individual stars, for computational efficiency).
-In order to confirm that these stars do not significantly affect the ensemble's preference towards the WMB model, we recalculated the joint posterior distribution for $P_{\rm s}$, excluding stars with an uncertainty on mass smaller than the KDE band-width.
+In order to confirm that these stars do not significantly affect the ensemble's preference towards the WMB model, we recalculated the joint posterior distribution for $Q_{\rm s}$, excluding stars with an uncertainty on mass smaller than the KDE band-width.
 While the 24 stars with small uncertainties do favour the WMB model, they do so very weakly, whereas the remaining 49 stars with larger uncertainties strongly favour the WMB model.
@@
 Of these, KICs 8379927, 7510397 and 9025370 were included in the gyrochronology analysis.
-None of them preferred one model strongly over the other, with all three finding flat posteriors for $P_{\rm s}$.
+None of them preferred one model strongly over the other, with all three finding flat posteriors for $Q_{\rm s}$.
 

### 2021-01-05 paper/natastron/2nd_draft/paper.tex
minor corrections

@@
 =
-%Of the stars used in this comparison, 21 had a median value of $P_{\rm s}$ in the gyrochronology analysis. We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.  
+%Of the stars used in this comparison, 21 had a median value of $Q_{\rm s}$ in the gyrochronology analysis. We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.  
 This overall agreement between spot and seismic rotation rates is in line with previous studies of Sun-like stars \cite{nielsen+2015, benomar+2015, gizon+2013, chaplin+2013}, and so we concluded that our asteroseismic ensemble can be reliably used to draw inferences about gyrochronology.\\
@@
 	\centering
-	\includegraphics[width=\textwidth]{fullsample.png}
+	\includegraphics[width=.9\textwidth]{fullsample.png}
 	\caption{Stars for which rotation was measured in this work, plotted over TRILEGAL \cite{girardi+2012} stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution.
-The 21 stars that were excluded from the gyrochronology analysis are marked with crosses and without uncertainties (see text).
+\rtwo{The z-axis colour scale indicates the density of stars in $P$-\teff space for the models.} The 21 stars that were excluded from the gyrochronology analysis are marked with crosses and without uncertainties (see text).
 Circles, squares and triangles denote main sequence, sub-giant, and `hot' stars respectively.
@@
 
-We evaluated our ensemble against both population models simultaneously using a Bayesian mixture model, which treated the data as being drawn from a mixture made from Kernel Density Estimates (KDEs) of both populations, modulated by a mixing parameter $P_{\rm s}$.
-In the limit that $P_{\rm s} \rightarrow 1$, the data are most likely drawn from the standard model.
-In the limit $P_{\rm s} \rightarrow 0$, the WMB model is more likely.
+We evaluated our ensemble against both population models simultaneously using a Bayesian mixture model, which treated the data as being drawn from a mixture made from Kernel Density Estimates (KDEs) of both populations, modulated by a mixing parameter $Q_{\rm s}$.
+In the limit that $Q_{\rm s} \rightarrow 1$, the data are most likely drawn from the standard model.
+In the limit $Q_{\rm s} \rightarrow 0$, the WMB model is more likely.
 This mixture model was evaluated in a five-dimensional parameter space, accounting for the population distributions in effective temperature ($T_{\rm eff}$), metallicity (\feh), asteroseismic mass ($M$) and age ($t$) and our new rotation periods ($P$).
@@
 
-\textbf{Results of comparing models:} We fit our mixture model to each star individually, which yielded a posterior probability density for the value of $P_{\rm s}$ for that star.
-In order to assess the posterior probability for the full sample, we multiplied the individual posterior probabilities for $P_{\rm{s}}$.
-This was done for the full ensemble of 73 stars together, as well as for the three different stellar types separately.
+\textbf{Results of comparing models:} We fit our mixture model to each star individually, which yielded a posterior probability density for the value of $Q_{\rm s}$ given the data for that star.
+In order to assess the posterior probability for the full sample, we multiplied the individual posterior probabilities for $Q_{\rm{s}}$.
+\rtwo{This joint posterior then describes the probability distribution of $Q_{\rm s}$ given multiple stars.} This was done for the full ensemble of 73 stars together, as well as for the three different stellar types separately.
 These joint probabilities can be seen in Figure \ref{fig:gyroresults} in the left-hand plot.
@@
 
-Both hot and sub-giant stars do not strongly prefer one model over the other (with both cumulative probabilities crossing the $P_{\rm{s}} = 0.5$ line at roughly $45\%$), which is expected given that these stars in our sample all lie at hot temperatures near the Kraft break.
-When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability below $P_{\rm{s}} = 0.5$ is 96.6\%.
+Both hot and sub-giant stars do not strongly prefer one model over the other (with both cumulative probabilities crossing the $Q_{\rm{s}} = 0.5$ line at roughly $45\%$), which is expected given that these stars in our sample all lie at hot temperatures near the Kraft break.
+When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability below $Q_{\rm{s}} = 0.5$ is 96.6\%.
 \\
@@
 	\includegraphics[width=\textwidth]{modelresults.pdf}
-	\caption{Posterior estimates of the mixture model parameter $P_{\rm s}$, broken down by stellar classification.
-A value of $P_{\rm s}$ close to zero indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 1 indicates that the data are more consistent with a standard rotational evolution scenario.
+	\caption{Posterior estimates of the mixture model parameter $Q_{\rm s}$, broken down by stellar classification.
+A value of $Q_{\rm s}$ close to zero indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 1 indicates that the data are more consistent with a standard rotational evolution scenario.
 \textit{Left:} the product of histograms of the posterior estimates for 73 stars, or subsets thereof for different stellar classifications.
 \textit{Right:} the cumulative posterior probability for 73 stars, or subsets thereof for different stellar types.
-On the y-axis of the left hand plot, $p(P_{\rm s} | \mathcal{D})$ represents the posterior distribution on $P_{\rm s}$ given the data.
+On the y-axis of the left hand plot, $p(Q_{\rm s} | \mathcal{D})$ represents the posterior distribution on $Q_{\rm s}$ given the data.
 The product symbol represents the sum of the posteriors for individual stars $i$, for a total of $N$ stars (which differs depending on the stellar type being shown).}
@@
 We found that the joint posterior distribution did not change significantly when excluding stars with metallicities that fell only slightly outside the model range, or those with extremely small uncertainties on asteroseismic mass (see \textbf{Methods}).
-Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $P_{\rm s}$.
+Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $Q_{\rm s}$.
 
@@
 We also accounted for the possibility that asteroseismic methods systematically overestimated stellar age, and reran our analysis after shifting the seismic ages younger by their systematic uncertainty ($6-8\%$).
-This resulted in $95.8\%$ of the posterior probability to lie below $P_{\rm s} = 0.5$, compared to $98.4\%$ for the unaltered ensemble.
+This resulted in $95.8\%$ of the posterior probability to lie below $Q_{\rm s} = 0.5$, compared to $98.4\%$ for the unaltered ensemble.
 From this, we can infer that our conclusions are robust against potential issues in seismic analyses.
@@
 
-As a sanity check that the evidence in favour of weakened magnetic braking presented in this work is independently robust, we recreated the joint posterior probability for $P_{\rm s}$, this time looking only at MS stars, and excluding any of the 22 stars that were included in the original van Saders study used to detect weakened magnetic braking.
+As a sanity check that the evidence in favour of weakened magnetic braking presented in this work is independently robust, we recreated the joint posterior probability for $Q_{\rm s}$, this time looking only at MS stars, and excluding any of the 22 stars that were included in the original van Saders study used to detect weakened magnetic braking.
 Of the 47 MS stars used to distinguish between stellar models, 16 were included in the van Saders sample.
 Both the 16 stars in the original van Saders study as well as the remaining MS stars favoured the WMB model, although the van Saders stars did so more strongly, not including any stars that favoured the standard model.
-Specifically, when considering only the van Saders stars, $96.3\%$ of the total joint probability lay below $P_{\rm s} = 0.5$, compared to $91.7\%$ when considering only those stars \emph{not} included in the van Saders study.
+Specifically, when considering only the van Saders stars, $96.3\%$ of the total joint probability lay below $Q_{\rm s} = 0.5$, compared to $91.7\%$ when considering only those stars \emph{not} included in the van Saders study.
 The stars initially used to propose the WMB model are still those most strongly in favour of it even when using asteroseismic rotation rates only, a result which is now further reinforced by an expanded sample that includes quiescent stars.\\

### 2021-01-06 paper/natastron/2nd_draft/ed.tex
Changed Ps to QWMB

@@
 Here, $\kappa_{\rm{s}}$ and $\kappa_{\rm WMB}$ represent the KDEs of standard and WMB model populations respectively.
-$Q_{\rm{s}}$ is the mixture model weighting factor.
+$Q_{\rm{WMB}}$ is the mixture model weighting factor.
 The latent parameters $\underline{\theta}$, our observations $\underline{\mathcal{D}}$ and their uncertainties $\underline{\sigma_{\mathcal{D}}}$ include temperature (\teff), mass ($M$), log-age ($\ln(t)$), metallicity (\feh) and log-rotation ($\ln(P)$).
-This model is \textit{hierarchical}, as all the latent parameters are drawn from the common probability distribution set by $Q_{\rm{s}}$ and described in Equation \ref{eq:mixturell}.}
+This model is \textit{hierarchical}, as all the latent parameters are drawn from the common probability distribution set by $Q_{\rm{WMB}}$ and described in Equation \ref{eq:mixturell}.}
 	\label{fig:pgm}

### 2021-01-06 paper/natastron/2nd_draft/methods.tex
Changed Ps to QWMB

@@
 We evaluated our data against both models simultaneously by treating the data as being drawn from a mixture of both model KDEs.
-In this mixture model structure, the two KDEs were modulated by a weighting factor, $Q_{\rm s}$.
-In the limit $Q_{\rm s} \rightarrow 1$, the data are most likely drawn from the standard model.
-In the limit $Q_{\rm s} \rightarrow 0$, the data are most likely drawn from the WMB model.
+In this mixture model structure, the two KDEs were modulated by a weighting factor, $Q_{\rm WMB}$.
+In the limit $Q_{\rm WMB} \rightarrow 1$, the data are most likely drawn from the WMB model.
+In the limit $Q_{\rm WMB} \rightarrow 0$, the data are most likely drawn from the standard model.
 
-The posterior probability of obtaining $Q_{\rm s}$ and additional parameters $\theta$ given our data $\mathcal{D}$ is $p(Q_{\rm{s}}, \theta | \mathcal{D})$.
+The posterior probability of obtaining $Q_{\rm WMB}$ and additional parameters $\theta$ given our data $\mathcal{D}$ is $p(Q_{\rm{WMB}}, \theta | \mathcal{D})$.
 Using Bayes equation, we can express this as:
@@
 \begin{equation}\label{eq:modelll}
-	p(Q_{\rm{s}}, \theta | \mathcal{D}) \propto p(\mathcal{D} | \theta)\ p(\theta | Q_{\rm{s}}, \kappa_{\rm{s}}, \kappa_{\rm{WMB}})\ p(Q_{\rm{s}})\, ,
+	p(Q_{\rm{WMB}}, \theta | \mathcal{D}) \propto p(\mathcal{D} | \theta)\ p(\theta | Q_{\rm{WMB}}, \kappa_{\rm{s}}, \kappa_{\rm{WMB}})\ p(Q_{\rm{WMB}})\, ,
 \end{equation}
@@
 \noindent where $\kappa_{\rm{s}}$ and $\kappa_{\rm{WMB}}$ are the KDE functions for the standard and WMB models respectively, and $\theta$ here are parameters, $\theta = \{M, \teff, \ln(t), \feh, \ln(P)\}$.
-As done above for the asteroseismic model, the parameters $\theta$ may be referred to as latent parameters, as they form a step between the parameter we want to infer ($Q_{\rm{s}}$) and our data.
+As done above for the asteroseismic model, the parameters $\theta$ may be referred to as latent parameters, as they form a step between the parameter we want to infer ($Q_{\rm{WMB}}$) and our data.
 Using this approach allowed our model to properly take into account the observational uncertainties on the data.
 
-The second component on the right hand side of Equation \ref{eq:modelll} describes the probability of obtaining our latent parameters $\theta$ given our KDEs and the mixture model weighting parameter $Q_{\rm s}$, and is described by the mixture model
+The second component on the right hand side of Equation \ref{eq:modelll} describes the probability of obtaining our latent parameters $\theta$ given our KDEs and the mixture model weighting parameter $Q_{\rm WMB}$, and is described by the mixture model
 
 \begin{equation}\label{eq:mixturell}
-	p(\theta | Q_{\rm{s}}, \kappa_{\rm{s}}, \kappa_{\rm{WMB}}) = Q_{\rm s} \times \kappa_{\rm s}(\theta) + (1 - Q_{\rm s}) \times \kappa_{\rm WMB}(\theta)\, ,
+	p(\theta | Q_{\rm{WMB}}, \kappa_{\rm{WMB}}, \kappa_{\rm{s}}) = Q_{\rm WMB} \times \kappa_{\rm WMB}(\theta) + (1 - Q_{\rm WMB}) \times \kappa_{\rm s}(\theta)\, ,
 \end{equation}
@@
 This probability function describes a distribution that is a mixture of both KDEs.
-While the KDEs are constant, $Q_{\rm s}$ is a free parameter, and so the shape of this distribution can vary.
+While the KDEs are constant, $Q_{\rm WMB}$ is a free parameter, and so the shape of this distribution can vary.
 The latent parameters $\theta$ are drawn from this distribution, and therefore from some combination of the two stellar models.
@@
 
-The final term, $p(Q_{\rm s})$, represents the prior on the mixture model weight, which is uniform between 0 and 1.
+The final term, $p(Q_{\rm WMB})$, represents the prior on the mixture model weight, which is uniform between 0 and 1.
 A visual representation of our model is shown in \textbf{Extended Data} Figure \ref{fig:pgm}.
 
-Typically, this model would evaluate all stars in our sample against the stellar models simultaneously for a single posterior estimate of $Q_{\rm s}$.
+Typically, this model would evaluate all stars in our sample against the stellar models simultaneously for a single posterior estimate of $Q_{\rm WMB}$.
 At 95 stars, in 5 parameter spaces, this totals 476 free parameters to marginalise over.
@@
 Alternative Markov Chain Monte Carlo techniques \cite[MCMC]{m_foreman-mackey+2013} can more efficiently sample the KDE functions, but can not treat the large number of hierarchical parameters.
-To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $Q_{\rm s}$, and multiplied these post hoc to obtain a combined posterior.
-This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications, at the expense of the ability to marginalise for a single value of $Q_{\rm s}$ directly.\\
+To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $Q_{\rm WMB}$, and multiplied these post hoc to obtain a combined posterior.
+This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications, at the expense of the ability to marginalise for a single value of $Q_{\rm WMB}$ directly.\\
 
@@
 
-After fitting, we took a normalised histogram of the posterior estimate of $Q_{\rm s}$ for each star, using 100 bins.
-In this histogram, each bin approximated the value of the posterior function for $Q_{\rm s}$.
-The array of 100 bins for all stars were multiplied, resulting in an approximation of the joint posterior probability function for $Q_{\rm s}$ given all stars in the ensemble.
+After fitting, we took a normalised histogram of the posterior estimate of $Q_{\rm WMB}$ for each star, using 100 bins.
+In this histogram, each bin approximated the value of the posterior function for $Q_{\rm WMB}$.
+The array of 100 bins for all stars were multiplied, resulting in an approximation of the joint posterior probability function for $Q_{\rm WMB}$ given all stars in the ensemble.
 
@@
 Our fit found a value of $m = 0.96 \pm 0.03$ using 48 stars.
-We reran this analysis using the 21 stars in this sample which had a value of $Q_{\rm s} < 0.5$ in our stellar model analysis, preferring the WMB model.
+We reran this analysis using the 21 stars in this sample for which the median of the posterior for $Q_{\rm WMB}$ was greater than $0.5$ in our stellar model analysis, preferring the WMB model.
 A fit to these stars alone found a value of $m = 0.96 \pm 0.04$.
@@
 For the stars with the smallest uncertainties, this significantly limits the size of the KDE being evaluated (as subsections of the full stellar models are used to evaluate individual stars, for computational efficiency).
-In order to confirm that these stars do not significantly affect the ensemble's preference towards the WMB model, we recalculated the joint posterior distribution for $Q_{\rm s}$, excluding stars with an uncertainty on mass smaller than the KDE band-width.
+In order to confirm that these stars do not significantly affect the ensemble's preference towards the WMB model, we recalculated the joint posterior distribution for $Q_{\rm WMB}$, excluding stars with an uncertainty on mass smaller than the KDE band-width.
 While the 24 stars with small uncertainties do favour the WMB model, they do so very weakly, whereas the remaining 49 stars with larger uncertainties strongly favour the WMB model.
@@
 Of these, KICs 8379927, 7510397 and 9025370 were included in the gyrochronology analysis.
-None of them preferred one model strongly over the other, with all three finding flat posteriors for $Q_{\rm s}$.
+None of them preferred one model strongly over the other, with all three finding flat posteriors for $Q_{\rm WMB}$.
 

### 2021-01-06 paper/natastron/2nd_draft/paper.tex
Changed Ps to QWMB

@@
 =
-%Of the stars used in this comparison, 21 had a median value of $Q_{\rm s}$ in the gyrochronology analysis. We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.  
+%Of the stars used in this comparison, 21 had a median value of $Q_{\rm WMB}$ in the gyrochronology analysis.
+We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.
 This overall agreement between spot and seismic rotation rates is in line with previous studies of Sun-like stars \cite{nielsen+2015, benomar+2015, gizon+2013, chaplin+2013}, and so we concluded that our asteroseismic ensemble can be reliably used to draw inferences about gyrochronology.\\
@@
 
-We evaluated our ensemble against both population models simultaneously using a Bayesian mixture model, which treated the data as being drawn from a mixture made from Kernel Density Estimates (KDEs) of both populations, modulated by a mixing parameter $Q_{\rm s}$.
-In the limit that $Q_{\rm s} \rightarrow 1$, the data are most likely drawn from the standard model.
-In the limit $Q_{\rm s} \rightarrow 0$, the WMB model is more likely.
+We evaluated our ensemble against both population models simultaneously using a Bayesian mixture model, which treated the data as being drawn from a mixture made from Kernel Density Estimates (KDEs) of both populations, modulated by a mixing parameter $Q_{\rm WMB}$.
+In the limit that $Q_{\rm WMB} \rightarrow 1$, the data are most likely drawn from the WMB model.
+In the limit $Q_{\rm WMB} \rightarrow 0$, the standard model is more likely.
 This mixture model was evaluated in a five-dimensional parameter space, accounting for the population distributions in effective temperature ($T_{\rm eff}$), metallicity (\feh), asteroseismic mass ($M$) and age ($t$) and our new rotation periods ($P$).
@@
 
-\textbf{Results of comparing models:} We fit our mixture model to each star individually, which yielded a posterior probability density for the value of $Q_{\rm s}$ given the data for that star.
-In order to assess the posterior probability for the full sample, we multiplied the individual posterior probabilities for $Q_{\rm{s}}$.
-\rtwo{This joint posterior then describes the probability distribution of $Q_{\rm s}$ given multiple stars.} This was done for the full ensemble of 73 stars together, as well as for the three different stellar types separately.
+\textbf{Results of comparing models:} We fit our mixture model to each star individually, which yielded a posterior probability density for the value of $Q_{\rm WMB}$ given the data for that star.
+In order to assess the posterior probability for the full sample, we multiplied the individual posterior probabilities for $Q_{\rm{WMB}}$.
+\rtwo{This joint posterior then describes the probability distribution of $Q_{\rm WMB}$ given multiple stars.} This was done for the full ensemble of 73 stars together, as well as for the three different stellar types separately.
 These joint probabilities can be seen in Figure \ref{fig:gyroresults} in the left-hand plot.
 The cumulative probabilities can be seen in the right-hand plot.
-In both of these plots, the left-hand side holds 98.4\% of the probability, indicating that the weakened magnetic braking model is preferred.
+In both of these plots, the right-hand side holds 98.4\% of the probability, indicating that the weakened magnetic braking model is preferred.
 When only considering the 47 main sequence stars, for which braking models are best calibrated, this rises to 99.2\%.
 
-Both hot and sub-giant stars do not strongly prefer one model over the other (with both cumulative probabilities crossing the $Q_{\rm{s}} = 0.5$ line at roughly $45\%$), which is expected given that these stars in our sample all lie at hot temperatures near the Kraft break.
-When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability below $Q_{\rm{s}} = 0.5$ is 96.6\%.
+Both hot and sub-giant stars do not strongly prefer one model over the other (with both cumulative probabilities crossing the $Q_{\rm{WMB}} = 0.5$ line at roughly $45\%$), which is expected given that these stars in our sample all lie at hot temperatures near the Kraft break.
+When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability above $Q_{\rm{WMB}} = 0.5$ is 96.6\%.
 \\
@@
 	\includegraphics[width=\textwidth]{modelresults.pdf}
-	\caption{Posterior estimates of the mixture model parameter $Q_{\rm s}$, broken down by stellar classification.
-A value of $Q_{\rm s}$ close to zero indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 1 indicates that the data are more consistent with a standard rotational evolution scenario.
+	\caption{Posterior estimates of the mixture model parameter $Q_{\rm WMB}$, broken down by stellar classification.
+A value of $Q_{\rm WMB}$ close to 1 indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 0 indicates that the data are more consistent with a standard rotational evolution scenario.
 \textit{Left:} the product of histograms of the posterior estimates for 73 stars, or subsets thereof for different stellar classifications.
 \textit{Right:} the cumulative posterior probability for 73 stars, or subsets thereof for different stellar types.
-On the y-axis of the left hand plot, $p(Q_{\rm s} | \mathcal{D})$ represents the posterior distribution on $Q_{\rm s}$ given the data.
+On the y-axis of the left hand plot, $p(Q_{\rm WMB} | \mathcal{D})$ represents the posterior distribution on $Q_{\rm WMB}$ given the data.
 The product symbol represents the sum of the posteriors for individual stars $i$, for a total of $N$ stars (which differs depending on the stellar type being shown).}
@@
 We found that the joint posterior distribution did not change significantly when excluding stars with metallicities that fell only slightly outside the model range, or those with extremely small uncertainties on asteroseismic mass (see \textbf{Methods}).
-Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $Q_{\rm s}$.
+Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $Q_{\rm WMB}$.
 
@@
 We also accounted for the possibility that asteroseismic methods systematically overestimated stellar age, and reran our analysis after shifting the seismic ages younger by their systematic uncertainty ($6-8\%$).
-This resulted in $95.8\%$ of the posterior probability to lie below $Q_{\rm s} = 0.5$, compared to $98.4\%$ for the unaltered ensemble.
+This resulted in $95.8\%$ of the posterior probability to lie above $Q_{\rm WMB} = 0.5$, compared to $98.4\%$ for the unaltered ensemble.
 From this, we can infer that our conclusions are robust against potential issues in seismic analyses.
@@
 
-As a sanity check that the evidence in favour of weakened magnetic braking presented in this work is independently robust, we recreated the joint posterior probability for $Q_{\rm s}$, this time looking only at MS stars, and excluding any of the 22 stars that were included in the original van Saders study used to detect weakened magnetic braking.
+As a sanity check that the evidence in favour of weakened magnetic braking presented in this work is independently robust, we recreated the joint posterior probability for $Q_{\rm WMB}$, this time looking only at MS stars, and excluding any of the 22 stars that were included in the original van Saders study used to detect weakened magnetic braking.
 Of the 47 MS stars used to distinguish between stellar models, 16 were included in the van Saders sample.
 Both the 16 stars in the original van Saders study as well as the remaining MS stars favoured the WMB model, although the van Saders stars did so more strongly, not including any stars that favoured the standard model.
-Specifically, when considering only the van Saders stars, $96.3\%$ of the total joint probability lay below $Q_{\rm s} = 0.5$, compared to $91.7\%$ when considering only those stars \emph{not} included in the van Saders study.
+Specifically, when considering only the van Saders stars, $96.3\%$ of the total joint probability lay above $Q_{\rm WMB} = 0.5$, compared to $91.7\%$ when considering only those stars \emph{not} included in the van Saders study.
 The stars initially used to propose the WMB model are still those most strongly in favour of it even when using asteroseismic rotation rates only, a result which is now further reinforced by an expanded sample that includes quiescent stars.\\

### 2021-01-06 paper/natastron/2nd_draft/paper.tex
updated to Qwmb fully now

@@
 
-Both hot and sub-giant stars do not strongly prefer one model over the other (with both cumulative probabilities crossing the $Q_{\rm{WMB}} = 0.5$ line at roughly $45\%$), which is expected given that these stars in our sample all lie at hot temperatures near the Kraft break.
+Both hot and sub-giant stars do not strongly prefer one model over the other (with both cumulative probabilities crossing the $Q_{\rm{WMB}} = 0.5$ line at roughly $60\%$), which is expected given that these stars in our sample all lie at hot temperatures near the Kraft break.
 When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability above $Q_{\rm{WMB}} = 0.5$ is 96.6\%.

### 2021-01-06 paper/natastron/2nd_draft/paper.tex
minor comment

@@
 When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability above $Q_{\rm{WMB}} = 0.5$ is 96.6\%.
-\\
+\rtwo{The total posterior probability for all stars above $0.6$ and $0.7$ is $93.3\%$ and $78.2\%$  respectively.
+This does not necessarily mean that a mixture of the two models is preferred, as stars that have not yet undergone weakened braking, or which are near the transition period, will have a flat posterior distribution with no strong preference for either model.}\\
 

### 2021-01-06 paper/natastron/2nd_draft/methods.tex
minor corrections

@@
 A comparison between prior and posterior is shown for 94 stars in $\nu_{\rm s}\sin(i)$, $i$ and $P$ in \textbf{Extended Data} Figure \ref{fig:priors}, arranged by age.
-In the Figure, results with means and error bars that closely resemble the prior distribution can be interpreted as prior-dominated (i.e.
+\rtwo{In the Figure, results with means (symbols) and $68\%$ credible regions (error bars) that are close to those same values for the prior distribution (where the horizontal line is the mean, and the shaded area is the credible region) can be interpreted as prior-dominated (i.e.
 poorly informed by the data).
-The projected splitting, $\nu_{\rm s}\sin(i)$, is overall well constrained, with only one star appearing prior dominated.
+Cases where the means differ or the credible regions are smaller than the prior distribution are data-dominated.} The projected splitting, $\nu_{\rm s}\sin(i)$, is overall well constrained, with only one star appearing prior dominated.
 This is expected, as the projected splitting is what we observe on the star before decoupling inclination and rotation.

### 2021-01-06 paper/natastron/2nd_draft/methods.tex
minor corrections

@@
 In the weakened magnetic braking model, $Ro_{\rm crit} = 1.97$.
-For further details, see \cite{m_vansaders+pinsonneault2013} and \cite{m_vansaders+2016, m_vansaders+2019} for the standard and weakened magnetic braking cases respectively.
+\rtwo{This Rossby number is based on model comparisons to catalogues of spot rotation rates \cite{m_vansaders+2019}.
+Its exact value is not critical in our analysis, as any similar value would create a model population significantly different from the standard case.
+In the model, the Rossby number is defined as the rotation period divided by the convective turnover timescale, which in turn is defined as $\tau_{\rm cz} = H_p / v_{\rm conv}$, where $H_p$ is the pressure scale height at the base of the convection zone, and $v_{\rm conv}$ is the convetive velocity evaluated one pressure scale height above the base in a mixing length theory of convection.
+Solid body rotation is assumed \cite{m_nielsen+2015}.} For further details, see \cite{m_vansaders+pinsonneault2013} and \cite{m_vansaders+2016, m_vansaders+2019} for the standard and weakened magnetic braking cases respectively.
 

### 2021-01-06 paper/natastron/2nd_draft/paper.tex
paper corrections

@@
 	\item We found that our ensemble was $98.4\%$ more likely to be drawn from a weakened magnetic braking model than a standard model of rotational evolution \cite{vansaders+pinsonneault2013}, at a critical Rossby number of $Ro_{\rm{crit}} = 1.97$.
-This work expands upon previous analysis \cite{vansaders+2019} by including quiescent stars older than the Sun.
+\rtwo{Stars in our ensemble overall show a weaker rate of braking than one would expect from solar-calibrated gyrochronology relations.} This work expands upon previous analysis \cite{vansaders+2019} by including quiescent stars older than the Sun.
 This conclusion was found to be robust against change of ensemble members and potentially underestimated asteroseismic systematic uncertainties.

### 2021-01-07 paper/natastron/2nd_draft/ed.tex
Ready to circulate

@@
 $Q_{\rm{WMB}}$ is the mixture model weighting factor.
-The latent parameters $\underline{\theta}$, our observations $\underline{\mathcal{D}}$ and their uncertainties $\underline{\sigma_{\mathcal{D}}}$ include temperature (\teff), mass ($M$), log-age ($\ln(t)$), metallicity (\feh) and log-rotation ($\ln(P)$).
+The latent parameters $\theta$, our observations $\mathcal{D}$ and their uncertainties $\sigma_{\mathcal{D}}$ include temperature (\teff), mass ($M$), log-age ($\ln(t)$), metallicity (\feh) and log-rotation ($\ln(P)$).
 This model is \textit{hierarchical}, as all the latent parameters are drawn from the common probability distribution set by $Q_{\rm{WMB}}$ and described in Equation \ref{eq:mixturell}.}
@@
 The solid lines indicate the 1:1 line, while the dash-dotted lines represent the 2:1 and 1:2 lines.
-The dashed lines indicate the location of $v\sin(i) = 5\, \rm{kms^{-1}}$, the point at which surface and seismic measures of projected rotation begin to differ strongly \cite{m_tayar+2015}.}
+The dashed lines indicate the location of $\textrm{v}\sin(i) = 5\, \rm{kms^{-1}}$, the point at which surface and seismic measures of projected rotation begin to differ strongly \cite{m_tayar+2015}.}
  	\label{fig:vsinilit}

### 2021-01-07 paper/natastron/2nd_draft/methods.tex
Ready to circulate

@@
 First, we fit a model for the convective background and white noise only, to the region of the power spectra that did not contain modes of oscillation.
-This was done using \texttt{PyStan} \cite{m_vanhoey+2013, m_carpenter+2017}, for 10,000 iterations on each star\footnote{These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work}.
+This was done using \texttt{PyStan} \cite{m_vanhoey+2013, m_carpenter+2017}, for 10,000 iterations on each star\footnote{These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work.}.
 Second, we fit our full model (including the convective background) to the region containing the modes of oscillation.
@@
 We flagged any sub-optimal conditions of the final fit.
-Of 94 stars, we flagged 5 for which the Gelman-Rubin convergence metric, $\hat{R}$, was greater than 1.01 and 2 stars for which it was greater than 1.1 on inclination angle or rotation, where a $\hat{R} = 1$ indicates a converged result \cite{m_gelman+rubin1992}.
+We flagged 5 for which the Gelman-Rubin convergence metric, $\hat{R}$, was greater than 1.01 and 2 stars for which it was greater than 1.1 on inclination angle or rotation, where a $\hat{R} = 1$ indicates a converged result \cite{m_gelman+rubin1992}.
 We also performed visual checks of the sampled chains on all hyperparameters and of the best-fit model compared to both the raw and smoothed asteroseismic data.
-We found no issues in the visual investigation of the 94 stars.
-KIC 8478994 was excluded due to both a poor fit as well as high $\hat{R}$ on rotational parameters.
+We found no issues in the visual investigation of 94 stars.
+KIC 8478994 is not reported due to both a poor unconverged fit as well as high $\hat{R}$ on rotational parameters.
 KICs 6603624, 8760414 and 8938364 are reported in \textbf{Extended Data} Table \ref{tab:results}, but were excluded from the gyrochronology analysis due to strong disagreement with multiple studies in the literature (see main body of paper).
@@
 Both the standard and WMB models contain stars with the same fundamental parameters (mass, radius, effective temperature, metallicity) but a different period based on the choice of rotational evolution prescription.
-Applying an asteroseismic selection function that depends on these fundamental parameters would apply an identical prior to both models, therefore providing no net effect on our posterior distribution \cite{m_chaplin+2011}.
+Applying an asteroseismic selection function that depends on these fundamental parameters would have an identical effect on both models, therefore providing no net effect on our posterior distribution \cite{m_chaplin+2011}.
 Additionally, we expected any seismic selection function to be relatively flat (and therefore uninformative) on a star-by-star scale, on which we run our model analysis.
@@
 \noindent where $\kappa_{\rm{s}}$ and $\kappa_{\rm{WMB}}$ are the KDE functions for the standard and WMB models respectively, and $\theta$ here are parameters, $\theta = \{M, \teff, \ln(t), \feh, \ln(P)\}$.
-As done above for the asteroseismic model, the parameters $\theta$ may be referred to as latent parameters, as they form a step between the parameter we want to infer ($Q_{\rm{WMB}}$) and our data.
-Using this approach allowed our model to properly take into account the observational uncertainties on the data.
+The parameters $\theta$ may be referred to as latent parameters, as they form a step between the parameter we want to infer ($Q_{\rm{WMB}}$) and our data.
+Using this approach allowed our model to properly take into account the observational uncertainties on the data \rtwo{in five dimensions.}
 
@@
 
-The parameter space of the stellar models populations were reduced before calculating the KDEs.
+The parameter space of the stellar model populations were reduced before calculating the KDEs.
 These cuts were made in $M$, $\teff$, $\ln(t)$ and \feh, removing any stars in the models that fell more than $3 \times \sigma_{\mathcal{D}}$ outside the observations.
@@
 poorly informed by the data).
-Cases where the means differ or the credible regions are smaller than the prior distribution are data-dominated.} The projected splitting, $\nu_{\rm s}\sin(i)$, is overall well constrained, with only one star appearing prior dominated.
+Cases where the means differ or the credible regions are smaller than the prior distribution are data-dominated.} The projected splitting, $\nu_{\rm s}\sin(i)$, is overall well constrained, with only one star \rtwo{being} prior dominated.
 This is expected, as the projected splitting is what we observe on the star before decoupling inclination and rotation.
@@
 As seen in the Figure there are instances where $i$ or $\nu_{\rm s}\sin(i)$ closely resemble the prior (and are therefore prior-dominated).
-There are no cases of this when looking at the resulting period measurements, as they will have been informed by at least one strongly data-driven parameter (judging from the Figure, commonly $\nu_{\rm s}\sin(i)$).
-From this, we conclude that our ensemble of asteroseismic rotation is not strongly dominated by the priors imposed on projected splitting and inclination in our Bayesian analysis.
+There are no cases of this when looking at the resulting period measurements, as they will have been informed by at least one strongly data-driven parameter (commonly $\nu_{\rm s}\sin(i)$).
+From this, we concluded that our ensemble of asteroseismic rotation is not strongly dominated by the priors imposed on projected splitting and inclination in our Bayesian analysis.
 
 \subsection{Comparisons to previous studies}\label{ssec:litcomp}
-In order to validate our results, we compared our rotational parameters to those obtained in the literature, as well as those resulting from the work presented in LEGACY and Kages, which were unreported and received through private communication by the authors of the catalogue papers.
+In order to validate our results, we compared our rotational parameters to those obtained in the literature, as well as those resulting from the work presented in LEGACY and `Kages', which were unreported and received through private communication by the authors of the catalogue papers.
 
 Comparisons with LEGACY and `Kages' are shown in \textbf{Extended Data} Figure \ref{fig:legacykages} for projected splitting, inclination angle, and rotation period.
-In all three cases we show the fractional difference between the values obtained in this work and those from LEGACY and Kages.
+In all three cases we show the fractional difference between the values obtained in this work and those from LEGACY and `Kages'.
 On the right of the Figure, we show the distribution of the fractional differences for the three parameters.
@@
 
-A number of stars are excluded from \textbf{Extended Data} Figure \ref{fig:legacykages} and compared individually as extreme outliers: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have fast rotation rates ($<5\, \rm days$) in Kages, but are found to have a broader spread of rotation rates in this work.
+A number of stars are excluded from \textbf{Extended Data} Figure \ref{fig:legacykages} and compared individually as extreme outliers: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have fast rotation rates ($<5\, \rm days$) in `Kages', but are found to have a broader spread of rotation rates in this work.
 At similar values for $\nu_{\rm s}\sin(i)$, `Kages' found much lower inclination angles with highly asymmetrical uncertainties.
-Based on a comparison between the summary statistics of these stars, we conclude that the results found in this work have better marginalised over inclination angle, improving our measure of rotation.
+Based on a comparison between the summary statistics of these stars, we concluded that the results found in this work have better marginalised over inclination angle, improving our measure of rotation.
 
@@
 Our fit found a value of $m = 0.96 \pm 0.03$ using 48 stars.
-We reran this analysis using the 21 stars in this sample for which the median of the posterior for $Q_{\rm WMB}$ was greater than $0.5$ in our stellar model analysis, preferring the WMB model.
+We reran this analysis using the 21 stars in this sample for which the median of their posterior probability for $Q_{\rm WMB}$ was greater than $0.5$ in our stellar model analysis, preferring the WMB model.
 A fit to these stars alone found a value of $m = 0.96 \pm 0.04$.
@@
 For the majority of cases, the seismic velocities are slower than the spectroscopic velocities, which would bias our ensemble towards favouring a standard evolution over a weakened magnetic braking scenario (as stars would overall appear to be rotating slower at late ages).
-Based on the comparison to spot rotation presented in the main body of this paper, and given known issues comparing seismic and spectroscopic rotation at low velocities, we conclude that the divergence seen in  \textbf{Extended Data} Figure \ref{fig:vsinilit} does not undermine our results.
+Based on the comparison to spot rotation presented in the main body of this paper, and given known issues comparing seismic and spectroscopic rotation at low velocities, we concluded that the divergence seen in  \textbf{Extended Data} Figure \ref{fig:vsinilit} does not undermine our results.
 
@@
 
-	In practice, the model still properly fits a spectrum where this kind of mode-overlapping occurred, as the $\ell = 0$ modes don't split, meaning that there are no degenerate solutions in this regime, and further constraints can be obtained from the other modes and split components in the spectrum.
-A more serious issue may be when the $\ell = 1$ mode at lower frequencies overlapped with the $\ell = 2$ mode as well, which would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.
+	In practice, the model still properly fits a spectrum where this kind of mode-overlapping occurs, as the $\ell = 0$ modes don't split, meaning that there are no degenerate solutions in this regime, and further constraints can be obtained from the other modes and split components in the spectrum.
+A more serious issue may be when the $\ell = 1$ mode at lower frequencies overlaps with the $\ell = 2$ mode as well, which would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.
 
@@
 
-While these two limits cause concern when studying the most extreme rotators, the results presented in this work are driven by stars with rotation rates in the regime of 10 to 40 days.
+While these two limits cause concern when studying the most extreme rotators, the results presented in this work are driven by stars with rotation rates in the regime of 5 to 30 days.
 Above, we demonstrated that results on period for these stars were data-driven (i.e.

### 2021-01-07 paper/natastron/2nd_draft/paper.tex
Ready to circulate

--- 2021-01-06 paper/natastron/2nd_draft/paper.tex
@@
 not in clusters) observed by \kepler \cite{borucki+2010} became more widely available through asteroseismology, the study of stellar variability \cite{silvaaguirre+2015}.
-When looking at these stars, disagreements were found between the observations and gyrochronology beyond the middle of stars' main sequence lifetimes, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}.
+When looking at these stars, disagreements were found between observations and gyrochronology beyond the middle of stars' main sequence lifetimes, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}.
 It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops.
@@
 %This makes asteroseismic rotation rates a perfect test of weakened magnetic braking on the main sequence. 
-Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of  ages, and determined whether this new ensemble agrees more closely with a classical rotational evolution scenario, or one in which weakened magnetic braking takes place.\\
+Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of  ages, and determined whether \rtwo{these new data agree} more closely with a classical rotational evolution scenario, or one in which weakened magnetic braking takes place.\\
 
@@
 We compared our results with both published and unpublished asteroseismic rotation rates \cite{nielsen+2015,davies+2015,davies+2016, lund+2017, benomar+2018}, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with multiple other studies.
-To some degree this was expected, as  for stars viewed near pole-on the split modes of oscillation have extremely low power, making them hard to detect reliably.
+For stars viewed near pole-on the split modes of oscillation have extremely low power, making them hard to detect reliably \cite{lund+2014}.
 We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we considered our asteroseismic rotation measurements to be robust (for a full justification, see \textbf{Methods}).\\
@@
 This is not the case for asteroseismic rotation, and so some stars may appear at the 2:1 and 1:2 lines in the figure.
-We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid likely multiples of the true rotation rate acting as outliers (transparent in the Figure, see \textit{\textbf{Methods}} for details.).
+We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid likely multiples of the true rotation rate acting as outliers (transparent in the Figure, see \textbf{Methods}å for details).
 Our fit found a value of $m = 0.96 \pm 0.03$, showing a close agreement ($<2\sigma$) between asteroseismic and surface rotation rates on a population level.
-=
-%Of the stars used in this comparison, 21 had a median value of $Q_{\rm WMB}$ in the gyrochronology analysis.
-We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.
 This overall agreement between spot and seismic rotation rates is in line with previous studies of Sun-like stars \cite{nielsen+2015, benomar+2015, gizon+2013, chaplin+2013}, and so we concluded that our asteroseismic ensemble can be reliably used to draw inferences about gyrochronology.\\
@@
 	\caption{Comparisons between asteroseismic and photometric measures of stellar rotation, for 48 stars.
-Literature values were taken, in order of priority, from: Garcia et al.
+Literature values were taken Garcia et al.
 (2014) \cite{garcia+2014} and Nielsen et al.
-(2013) \cite{nielsen+2013} (i.e.
-if a value was reported in Nielsen et al.
-(2013) and also in Garcia et al.
-(2014), the latter was used).
+(2013) \cite{nielsen+2013} (if a value was reported in both, the Garcia et al.
+2014 value was used).
 Stars used in the original van Saders et al.
@@
 
-\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two population models of rotational evolution \cite{vansaders+2019}: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{vansaders+2016,skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model') \cite{vansaders+2016}.
+\textbf{Comparing gyrochronology models:} To evaluate the implications of our \rtwo{new seismic rotation rates} for gyrochronology, we compared \rtwo{the stars in our ensemble} to two population models of rotational evolution \cite{vansaders+2019}: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{vansaders+2016,skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model') \cite{vansaders+2016}.
 The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$\footnote{The Rossby number may be defined as $Ro \equiv P/\tau_{\rm cz}$, where $\tau_{\rm cz}$ is the convective turnover timescale, and $P$ is the rotation.
 The Rossby number roughly scales inversely with stellar activity (and so increases as stars age).}.
+\rtwo{Because of this, the distribution of stars with a Rossby number below this threshold will be identical in both models}.
 
-Instead of comparing our rotation rates directly to models of individual stars, we instead compared them to synthetic TRILEGAL populations based on what the \textit{Kepler} field would look like under these two different braking laws \cite{vansaders+2019, girardi+2012}.
+Instead of comparing our rotation rates directly to models of individual stars, we instead compared them to \rtwo{the distribution of} synthetic TRILEGAL populations based on what the \textit{Kepler} field would look like under these two different braking laws \cite{vansaders+2019, girardi+2012}.
 These synthetic populations were then altered to match the distribution of existing catalogues of stars in the \kepler field in order to replicate the \kepler selection effects \cite{berger+2020}, and evolved following a standard or WMB braking law.
-For the full details on how these models were constructed, see \textbf{Methods}.
+For details on how these models were constructed, see \textbf{Methods}.
 
@@
 This mixture model was evaluated in a five-dimensional parameter space, accounting for the population distributions in effective temperature ($T_{\rm eff}$), metallicity (\feh), asteroseismic mass ($M$) and age ($t$) and our new rotation periods ($P$).
-For further detail, see \textbf{Methods}.\\
+For further details, see \textbf{Methods}.\\
 
@@
 
-Both hot and sub-giant stars do not strongly prefer one model over the other (with both cumulative probabilities crossing the $Q_{\rm{WMB}} = 0.5$ line at roughly $60\%$), which is expected given that these stars in our sample all lie at hot temperatures near the Kraft break.
-When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability above $Q_{\rm{WMB}} = 0.5$ is 96.6\%.
-\rtwo{The total posterior probability for all stars above $0.6$ and $0.7$ is $93.3\%$ and $78.2\%$  respectively.
+Both hot and sub-giant stars do not strongly prefer one model over the other (with both cumulative probabilities crossing the $Q_{\rm{WMB}} = 0.5$ line at roughly $60\%$).
+\rtwo{This indicates that these stars lie below our model's critical Rossby number (and therefore in the parameter space where our two models are identical), or that they are only weakly affected by angular momentum loss (as is the case for hot stars near the Kraft break).} When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability above $Q_{\rm{WMB}} = 0.5$ is 96.6\%.
+\rtwo{The total posterior probability for all stars above $Q_{\rm{WMB}} = 0.6$ and $0.7$ is $93.3\%$ and $78.2\%$  respectively.
 This does not necessarily mean that a mixture of the two models is preferred, as stars that have not yet undergone weakened braking, or which are near the transition period, will have a flat posterior distribution with no strong preference for either model.}\\
@@
 A value of $Q_{\rm WMB}$ close to 1 indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 0 indicates that the data are more consistent with a standard rotational evolution scenario.
-\textit{Left:} the product of histograms of the posterior estimates for 73 stars, or subsets thereof for different stellar classifications.
+\textit{Left:} \rtwo{the joint posterior probabilities} for 73 stars, or subsets thereof for different stellar classifications.
 \textit{Right:} the cumulative posterior probability for 73 stars, or subsets thereof for different stellar types.
-On the y-axis of the left hand plot, $p(Q_{\rm WMB} | \mathcal{D})$ represents the posterior distribution on $Q_{\rm WMB}$ given the data.
-The product symbol represents the sum of the posteriors for individual stars $i$, for a total of $N$ stars (which differs depending on the stellar type being shown).}
+On the y-axis of the left hand plot, $p(Q_{\rm WMB} | \mathcal{D})$ represents the posterior distribution of $Q_{\rm WMB}$ given the data.
+The product symbol represents the combination of the posteriors for individual stars $i$, for a total of $N$ stars (which differs depending on the stellar type being shown).}
 	\label{fig:gyroresults}
@@
 
-\textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we ensured that the same results were obtained when using different subsets of the ensemble, and when exploring potential biases.
+\textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful \rtwo{conclusion about} weakened magnetic braking, we ensured that the same results were obtained when using different subsets of the ensemble, and when exploring potential biases.
 We found that the joint posterior distribution did not change significantly when excluding stars with metallicities that fell only slightly outside the model range, or those with extremely small uncertainties on asteroseismic mass (see \textbf{Methods}).
@@
 Our sample does not overlap with theirs, so we can not directly compare to their results.
-Our work does find statistical agreement with a model of weakened magnetic braking at a critical Rossby number of $1.97$ over one without any braking at all, indicating that traces of weakened magnetic braking do occur at Rossby numbers of around $2$.
-A comparison to models of different Rossby numbers will be explored in future papers, using the LEGACY and `Kages' rotation sample presented in this work.
+The statistical agreement between our seismic stars and a model of weakened magnetic braking at a critical Rossby number of $1.97$ over the standard scenario indicates that traces of weakened magnetic braking do occur at Rossby numbers of around $2$.
+\rtwo{However, we only intend to show that asteroseismic rotation rates indicate a preference for the presence of weakened magnetic braking, instead of claiming a particular critical Rossby number is correct.
+A measurement of the exact critical Rossby number at which these occurs, using individual models of our seismic targets, is the subject of a paper in preparation.}
 
-As a sanity check that the evidence in favour of weakened magnetic braking presented in this work is independently robust, we recreated the joint posterior probability for $Q_{\rm WMB}$, this time looking only at MS stars, and excluding any of the 22 stars that were included in the original van Saders study used to detect weakened magnetic braking.
+As a sanity check that the evidence in favour of weakened magnetic braking presented in this work is independently robust, we recreated the joint posterior probability for $Q_{\rm WMB}$, this time looking only at MS stars, and excluding any of the 22 stars that were part of the original van Saders study used to propose weakened magnetic braking.
 Of the 47 MS stars used to distinguish between stellar models, 16 were included in the van Saders sample.
@@
 We validated these results against previously published and unpublished asteroseismic rotation measurements, making our new rotation catalogue the largest self-consistent sample of asteroseismic rotation in main sequence stars to date.
-We evaluated the stars in our sample against synthetic population models of the \textit{Kepler} field evolved under either a `standard' model of rotational evolution, or one where weakened magnetic braking takes place.
+We evaluated the stars in our sample against synthetic population \rtwo{distribution} models of the \textit{Kepler} field evolved under either a `standard' model of rotational evolution, or one where weakened magnetic braking takes place.
 This evaluation was done using a Bayesian mixture model to determine whether the ensemble preferred one model over another, and was done simultaneously in asteroseismic rotation, mass, age, and spectroscopic temperature and metallicity.\\
@@
 	\item We found that our ensemble was $98.4\%$ more likely to be drawn from a weakened magnetic braking model than a standard model of rotational evolution \cite{vansaders+pinsonneault2013}, at a critical Rossby number of $Ro_{\rm{crit}} = 1.97$.
-This work expands upon previous analysis \cite{vansaders+2019} by including quiescent stars older than the Sun.
+\rtwo{Stars in our ensemble overall show a weaker rate of braking than one would expect from solar-calibrated rotational evolution models.} This work expands upon previous analysis \cite{vansaders+2019} by including quiescent stars older than the Sun.
 This conclusion was found to be robust against change of ensemble members and potentially underestimated asteroseismic systematic uncertainties.

### 2021-01-13 paper/natastron/2nd_draft/methods.tex
minor fixes

@@
 The probability of an asteroseismic detection with \kepler scales with temperature and radius (i.e.
-scales inversely with \logg, and therefore main sequence age) \cite{m_chaplin+2011, m_schofield+2019}.
-More active, magnetic stars may also suppress their oscillation modes, making it more likely to detect seismic oscillations in older stars \cite{m_mathur+2019}.
-Through these two effects, asteroseismology is biased towards detecting older over younger stars.
-As it is older stars, undergoing magnetic braking, that are required to drive the distinction between stellar models, we do not expect this observing bias to effect our conclusions.
+scales inversely with \logg, and therefore main sequence age), \rtwo{and detections are unlikely below roughly $5200\, K$} \cite{m_chaplin+2011, m_schofield+2019}.
+\rtwo{Very young ($\lesssim 2\, \rm{Gyr}$), very magnetically active stars may also suppress their oscillation modes.
+\cite{m_mathur+2019}.
+Though these two effects impose a bias on asteroseismic populations, they do so outside the parameter range on which our comparison takes place.
+As it is older stars, undergoing magnetic braking, that are required to drive the distinction between stellar models, we conclude that our seismic sample can be assumed to be complete for the purposes of this work.}
 

### 2021-01-20 paper/natastron/2nd_draft/response/response.tex
ready to submit

\documentclass[11pt]{article}
\usepackage[left=1in, right=1in, bottom=0.5in, top=0.5in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\begin{document}

\section*{Response to the Referee}

First we would like to thank the referee for their comments (and their quick turnaround in these busy times). They have helped us improve this manuscript, and made us really think about potential pitfalls. Major changes to the paper are shown in red. no changes have been made to the Supplementary Information.

First and foremost, we should highlight a major change to the presentation of our results. Following the referee’s comments, we now use $Q_{\rm WMB}$ to describe the mixture model weighting factor, where $Q_{\rm WMB} = 1 - P_{\rm s}$. This places the preference for weakened magnetic braking as the subject of our model analyses, making Figure 4 more readable, and hopefully our results more accessible. We have made sure to reverse any mentions of this parameter (e.g. ‘below $P_{\rm s} = 0.5$’ is now ‘above $Q_{\rm WMB} = 0.5$’).

\section*{Major comments:}

\noindent\noindent\textbf{ 1 - My main concern is that from the authors’ study one could only robustly conclude that Gyrochronology needs to be revisited or recalibrated, which we knew already. One could also conclude that WMB (or a mixture between the ‘standard’ and WMB models) offers a better description of the data than the ‘standard’ Gyrochronology model alone. However, comparing a single model to one that we know doesn’t work very well, is not enough to claim strong agreement of the data with WMB. From Fig 4, for example, it is clear that the cumulative probability Ps remains doesn’t change after Ps =0.5 for MS st	ars, which means that a mixture of ‘standard’ and WMB in equal proportions describes the data as well as the WMB alone. Surprisingly to me, the SG and Hot do show a steady increment all the way to Ps=1, which doesn’t seem to support the idea that WMB describes better MS stars.}\\

The novelty of this work is the use of new asteroseismic rotation rates, which probe a parameter space for which the concept of weakened magnetic braking had not yet been tested. This conclusively shows that (some form of) weakened braking is a true physical phenomenon, not something that is just suggested by biases in previous measurement techniques. We have gone through the paper again to try and make the language used reflect this, and have changed our title from “strong agreement with” to “strong preference for”.

To address the referee’s other concerns in this paragraph: stars which have not undergone weakened magnetic braking yet will by design have equal preference for both models, as the models are identical until Ro = 1.97. This also explains why the Hot and SG stars show a steady increment in cumulative probability-- they hold no diagnostic information in preference of one model over the other. We compare the stars to the models on an individual basis before multiplying the posteriors, and so stars that have not undergone braking just won’t have anything interesting to say. Conversely, any single star alone past the critical Rossby number will be able to differentiate between the standard or WMB models.

We would also like to clarify that in the mixture model, it will only be the cases with the most precise constraints on mass, age, rotation, temperature and metallicity that see an extremely strong result for $Q_{WMB}$. We are comparing two population distributions after all, which cover much of the same parameter space (with different densities). A star that prefers the WMB model will still be consistent with the standard model but with a much smaller probability. The mixture model is really showing which population the star is more likely to come from, not advocating for some model description that incorporates the physics of both.\\

\noindent\textbf{About the calibration of the rotation evolution model: the standard and WMB models are both calibrated on young clusters and to match the solar rotation at 4.6Gyr. The comparison of models is then one of "extrapolated solar braking" and "weaker than extrapolated solar braking", and is not really as definitive as WMB vs standard. If there is some stochasticity in rotation evolution toward older, slower rotators, the Sun might present a biased calibration point. I would suggest the authors note that their study is strictly only supporting this conclusion that some stars have weaker than solar and extrapolated solar rotation braking (and only then if selection bias missing more active stars is not significant).}\\

We have added the following to the first point in our conclusions: “Stars in our ensemble overall show a weaker rate of braking than one would expect from solar (and extrapolated solar) braking rates.”

We have no reason to suspect that seismic detection biases cause us to not measure active stars to the degree where it affects our results. Spot detection becomes extremely difficult for inactive stars, but asteroseismic detection biases are not the inverse of this. It is worth noting that over half our sample is active enough to have existing spot rotation measurements.

To respond to the risk of stochasticity in rotational evolution affecting our results: we don’t believe that there is enough support for this at late ages, especially in the space $> 6$ Gyr where most of our sample resides. The rotation rates at 2.5 Gyr in Meibom et al. (2015) have an exceptionally low scatter, and there is no mechanism in the standard spin-down model to introduce scatter after that point.\\

\noindent\noindent\textbf{ 2 - Another big concern is that the critical Rossby number is fixed from previous studies in which the rotation periods came from star-spots observations. The authors admit those are biased and one of the motivations of this study is to test if that bias explains the observed deviation of post-MS stellar rotation periods from those predicted by Gyrochronology.}\\

The use of Rocrit = 1.97, based on the van Saders et al. (2019) fit to the star-spot observations is chosen as the current best estimate of the critical Rossby number. We are not attempting to make any statements about the value of Rocrit in this work. However with our method, if the true Rocrit were to be much higher or lower than 1.97, this would water down our posterior probability for $Q_{WMB}$ (either towards the standard model if higher, or towards no preference for either if lower). The fact that this Rocrit is based on spot rotation rates, which are biased against inactive stars, is essentially unimportant for this comparison, as the stellar model populations we compare against are complete. However, that the WMB model is favoured when using independent asteroseismic rotation is important, of course.\\

\noindent\noindent\textbf{ 3 - I am also concerned about the selection bias:}

\noindent\textbf{Methods, top p25}

\textit{"More active, magnetic stars may also suppress their oscillation modes, making it more likely to detect seismic oscillations in older stars [45]. Through these two effects, asteroseismology is biased towards detecting older over younger stars. As it is older stars, undergoing magnetic braking, that are required to drive the distinction between stellar models, we do not expect this observing bias to effect our conclusions."}

\noindent\textbf{This does not address the selection bias problem inherent in the study.  Yes, the slower rotators are needed to find any WMB effects, but the synthetic populations do not include this selection bias and at face value will be lacking the more active stars that will favor the standard model, not WMB. The comparison is then inherently biased toward WMB.}\\

We think the referee is misinterpreting the asteroseismic selection effects. Spot rotation rates have a dearth of measurements for old, inactive stars. The seismic selection effect is not the opposite of this. Our sample includes both active and inactive stars (in fact, over half our sample has existing surface rotation measurements). The asteroseismic selection effect only excludes very young and very active stars ($\lesssim 2$ Gyr, Salabert+16 and Mathur+19), which would not inform $Q_{WMB}$ strongly. For the purposes of this comparison, the asteroseismic selection is essentially complete. Page 25 is intended to inform the reader of asteroseismic selection biases for completeness, and we have now changed it to make sure it clarifies that this is not an issue for this study. The paragraph now reads as follows:

“Finally, we also consider bias in asteroseismic detections. The probability of an asteroseismic detection with \textit{Kepler} scales with temperature and radius (i.e. scales inversely with $\log$g, and therefore main sequence age), and detections are unlikely below roughly $5200\, K$. Very young ($\lesssim 2$ Gyr), very magnetically active stars may also suppress their oscillation modes. Though these two effects impose a bias on asteroseismic populations, they do so outside the parameter range on which our comparison takes place. As it is older stars, undergoing magnetic braking, that are required to drive the distinction between stellar models, we conclude that our seismic sample can be assumed to be complete for the purposes of this work.”

The referee also mentions that the synthetic populations are lacking more active stars, so we would like to reiterate that we have no reason to believe the stellar models are not complete. The standard and WMB model populations are built using the same synthetic stellar sample evolved under angular momentum evolution prescriptions which are identical until the critical Rossby number.\\

\noindent\textbf{The only proper way to compare the TRILEGAL synthetic populations is with stellar samples that are not detection biased in a different way.  In this regard, it would also seem that a more complete sample could be constructed by including stars with spot-derived rotation period measurements to combine with the oscillations sample.}\\

The TRILEGAL sample is not detection biased, just calibrated to a particular critical Rossby number, which naturally includes the spot-derived rotation periods. The models describe what the Kepler field looks like in the cases with and without weakened braking at Rocrit = 1.97. Our analysis simply tells us which of these two cases our stars are in better agreement with. There is no reason to believe these model populations are incomplete.

We should also note that any individual star will be able to tell the difference between the standard and WMB models (provided it is evolved past the point where the two models diverge). These individual star-by-star posteriors are combined to give us a single combined posterior that describes whether the ensemble as a whole prefers the WMB model, which drives our conclusions. We have tried to emphasise the fact that the model comparison is done star-by-star more in the text.

The unique selection biases that asteroseismology is subject to do not need to be reflected in the stellar models for the purposes of our analysis, for two reasons:
\begin{itemize}
\item On a star-by-star basis, the effects of a seismic selection effect are slowly changing (there are no sharp cut-offs except at the extremes of the parameter space, which are not relevant to our sample), so we would not expect a selection effect to alter our posterior probability.
\item The selection effects would be applied to both models identically. Because we are comparing the two models in a mixture model, applying the selection effect would yield a net zero effect on the posterior probability, so there is no need to include it.\\
\end{itemize}

\noindent\textbf{This also raises the question of why not simply compute individual rotation models for all the parameters of the stars in the sample and compare directly synthetic to observed stars? At least as an additional test, it would seem the most obvious approach that should be much more amenable to simple statistical comparison.}\\

This is functionally what we have already done in our work. We have modeled rotation rates generated for each star in a simulation of the Kepler field. We then compare our observation to the distribution of these models in five parameter spaces simultaneously, and obtain a posterior distribution describing which angular momentum evolution prescription the observation more closely agrees with.\\

\section*{Minor comments:}
\noindent\textbf{TRILEGAL rotation model simulations:
I would like to see a little bit more detail here on how the rotation models are computed.  Eg. solid body rotation assumed? Definition of Rossby number in the code and how/where convective turnover time is computed? etc.  While these might be described in detail in the primary references, the model ingredients are crucial for the study and it helps the reader to have a more complete summary so as not to have to hunt for this in another paper.}\\

We’ve added an explanation of how the Rossby number and the convective turnover timescale are defined in the model, and mentioned our solid body rotation assumption.\\

\noindent\textbf{Page 2 - Asteroseismic main sequence targets: I find this sentence not too clear: “A star’s rotation causes modes of oscillation to split into multiplets, enabling measurement of independent rotation rates by measuring the rate of splitting [22]”
This will not be very helpful for anyone with no prior knowledge of asteroseismology, and will be obvious for anyone in that field.}\\

We’ve changed this to: “Rotation causes certain modes of oscillation -- which lie at the same frequency in a non-rotating case -- to shift to higher or lower frequencies. The size of this `splitting' provides a means of independently measuring the rotation of the star”.
To accommodate the extra words in the introduction, we removed “This makes asteroseismic rotation rates a perfect test of weakened magnetic braking on the main sequence” from the following paragraph.\\

\noindent\textbf{Page 4 - Seismic versus surface rotation rates: “How do the authors use the uncertainties to fit the line?
“We fit a line of the form Psurf = m x Pseis, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid likely multiples of the true rotation rate acting as outliers (transparent in the Figure).”}\\

This was an oversight, and we’ve now included a more detailed explanation in Methods, in its own section, including an extra test of the Psurf = m x Pseis fit using only stars that preferred the WMB model.\\

\noindent\textbf{Fig 3 would benefit from a more explicit explanation of the color code, which seems to be the number of stars predicted by each of the models. Also, the Caption overlaps with page number}\\

Added the sentence “The z-axis colour scale indicates the density of stars in $P$-$T_{\rm eff}$ space for the models.”, and reduced the image size.\\

\noindent\textbf{$P_s$ is a mixing parameter and not a rotation period. I find the choice of name confusing in this context.}\\

Good call. We’ve changed $P_s$ to $Q_{WMB}$ everywhere, which is more in line with other papers that use mixture models. $Q_{WMB}$ = 1 - $P_s$, and we think this helps communicate the main conclusion more clearly (and improves the readability of Figure 4).  While we’re at it, we made sure to use $P$ instead of $P_{rot}$ consistently for rotation.\\

\noindent\textbf{Page 6 - Results of Comparing Models:
- “In order to assess the posterior probability for the full sample, we multiplied the individual posterior probabilities for Ps.” Do the authors mean “multiplied the individual posterior probabilities by Ps”?}\\

We think the referee may misunderstand what is being described here. We have probability distributions for $Q_{\rm WMB}$ (=1-Ps) based on each individual star. By multiplying those distributions, we obtain a probability distribution that describes $Q_{\rm WMB}$ based on an ensemble of stars. We’ve added a sentence that clarifies this a little more here: “This joint posterior then describes the probability distribution of $Q_{\rm WMB}$ given multiple stars.” \\

\noindent\textbf{- ”Both hot and sub-giant stars do not strongly prefer one model over the other (with both
cumulative probabilities crossing the Ps = 0.5 line at roughly 45\%) […] When performing
this analysis on all 89 stars for which seismic rotation was measured (excluding the
two stars with low metallicity), the total probability below Ps = 0.5 is 96.6%.”
I think it is not fair to mix populations with such different probabilities and then compute an overall probability and assume it represents anything.}\\

All stars provide meaningful information, and the multiplication of individual posterior probability distributions to create a joint posterior probability distribution is a valid way of studying the ensemble as a whole. We feel that, for completeness sake, it’s important to report the results given our full ensemble, even though subgiant and ‘hot’ stars in our sample don’t appear to have undergone weakened braking yet.\\

\noindent\textbf{Did the authors try a smaller Rossby number to see if the method works? If it also resulted in statistical agreement with a model of weakened magnetic braking at critical Ro 1 for example, one could argue there is an issue.}\\

We already know how different critical Rossby numbers affect the distribution of stars undergoing weakened magnetic braking (see van Saders et al. 2016). The further our models critical Rossby number deviates from the truth, the more watered down our distribution of $Q_{WMB}$ will become, as stars will divert to favouring the standard model (in the case of a high Rocrit) or the standard and WMB models will become essentially the same (low Rocrit).

In this manuscript we are not making claims about statistical agreement between models and data, but relative statements about which models are preferred--- we’re not trying to report on any value of Ro in particular.\\

\noindent\textbf{How do authors rule out that the issue is just a Gyrochronology calibration issue? Or two branches of rotators that, on average, favor a WMB model? That could be explored by separating the samples in faster vs slower rotators.}\\

We’re assuming that the referee is referring to the Barnes et al. model of gyrochronology that has a fast and slow rotating branch. Even if that model is assumed to be correct, it is applicable at young ages, and based on observations at 2.5 Gyr (Meibom et al. 2015) we do not expect this potential dispersion to hold any weight at the late ages (> 6 Gyr) where most of our main sequence stars reside (i.e., any dispersion present would be far smaller than the uncertainties on rotation). Following the same line of thought, a fast and slow rotation branch at low ages would not average to form a distribution resembling the WMB model, as the WMB model has zero angular momentum loss past the critical Rossby number. Truncated braking may be a better name for the model, in retrospect.

We don’t think separating our sample by rotation rate is worthwhile, as we expect faster rotating stars to drive the distinction between the standard and WMB scenarios (rotating fast at late ages). For our distribution of $Q_{WMB}$ to be due to two separate streams of rotational evolution the dispersion between these two streams would have to be very dramatic, which isn’t supported by what we see in Meibom et al. (2015).\\

\subsection*{Methods:}
\noindent\textbf{Authors claim they use new measurements of rotation periods that do not suffer from the star-spots observational biased by which slower rotators will not be detected. However, they use a fixed critical Rossby number (Ro = 1.97) that comes from van Saders et al. 1013, 1016, and 1019, and was derived from rotation periods measured from starspots, which do include that bias that is consistent with that Rossby number.}\\

This is a good observation, however we don’t think these two things are mutually exclusive. The seismic observations are independent to surface rotation measurements, and are subject to entirely separate biases, as discussed in the text. The WMB model we compare to uses Ro = 1.97 based on the van Saders et al. (2019) paper, as the reviewer mentions. The population generated from this model looks similar to the distribution of rotation rates seen in McQuillan et al. (2014), prompting the question whether it is a spot rotation bias causing this trend (as mentioned in the text and by the reviewer). By showing that our seismic rotation rates, which are not subject to the same biases as spot rotation, agree with the WMB model, we can conclude that this signature of weakened magnetic braking is not just a population bias effect.

Bear in mind also that we are comparing to a model, and not population measurements. The exact value of the Rossby number itself matters little, as a population drawn from any WMB model will look sufficiently different to the standard scenario past the critical Rossby number. We would also like to reiterate that we believe that both the model and observed populations are, for the purposes of this comparison, complete.\\

\noindent\textbf{What is the probability of Ps $<$0.4, and Ps$<$0.3? This tells you more about WMB really being favored, rather than something in between.}\\

We’ve added the following: “The total posterior probability for all stars above $0.6$ and $0.7$ is $93.3\%$ and $78.2\%$  respectively. This does not necessarily mean that a mixture of the two models is preferred, as stars that have not yet undergone weakened braking, or which are near the transition period, will have a flat posterior distribution with no strong preference for either model.”\\

\noindent\textbf{I am not sure how the authors reach the conclusion that their posterior estimates on rotational parameters are data and not prior-dominated. Just by looking at Fig 2 by eye?}\\

The analysis by-eye just reflects a comparison of the summary statistics of the posterior distribution vs the prior. We’ve changed the language so this is better reflected in the text:

“In the Figure, results with means (symbols) and 68\% credible regions (error bars) that are close to those same values for the prior distribution (where the horizontal line is the mean, and the shaded area is the credible region) can be interpreted as prior-dominated (i.e. poorly informed by the data). Cases where the means differ or the credible regions are smaller than the prior distribution are data-dominated.”

\end{document}

### 2021-01-20 paper/natastron/2nd_draft/methods.tex
ready to submit

@@
 As described in the main body of the paper, we compared a subsample of our asteroesismic rotation rates to surface rotation rates from spot rotation, where available.
-Both the surface $P_{\rm surf}$ and seismic $P_{\rm seis}$ rotation rates have associated uncertainties.
+Both the surface ($P_{\rm surf}$) and seismic ($P_{\rm seis}$) rotation rates have associated uncertainties.
 Instead of fitting the slope between these two values directly, we instead fit the distribution
@@
 
-\textbf{Code availability statement:} The code required to replicate our results has been placed in a curated online repository found here: \url{www.github.com/ojhall94/halletal2020}.
+\textbf{Code availability statement:} The code required to replicate our results has been placed in a curated online repository found here: \url{www.github.com/ojhall94/halletal2021a}.
 

### 2021-01-20 paper/natastron/2nd_draft/paper.tex
ready to submit

@@
 Both hot and sub-giant stars do not strongly prefer one model over the other (with both cumulative probabilities crossing the $Q_{\rm{WMB}} = 0.5$ line at roughly $60\%$).
-\rtwo{This indicates that these stars lie below our model's critical Rossby number (and therefore in the parameter space where our two models are identical), or that they are only weakly affected by angular momentum loss (as is the case for hot stars near the Kraft break).} When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability above $Q_{\rm{WMB}} = 0.5$ is 96.6\%.
-\rtwo{The total posterior probability for all stars above $Q_{\rm{WMB}} = 0.6$ and $0.7$ is $93.3\%$ and $78.2\%$  respectively.
+\rtwo{This indicates that these stars lie below our model's critical Rossby number (and therefore in the parameter space where our two models are identical), or that they are only weakly affected by angular momentum loss (as is the case for hot stars near the Kraft break).} When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability above $Q_{\rm{WMB}} = 0.5$ was 96.6\%.
+\rtwo{The total posterior probability for all stars above $Q_{\rm{WMB}} = 0.6$ and $0.7$ was $93.3\%$ and $78.2\%$  respectively.
 This does not necessarily mean that a mixture of the two models is preferred, as stars that have not yet undergone weakened braking, or which are near the transition period, will have a flat posterior distribution with no strong preference for either model.}\\
@@
 \rtwo{However, we only intend to show that asteroseismic rotation rates indicate a preference for the presence of weakened magnetic braking, instead of claiming a particular critical Rossby number is correct.
-A measurement of the exact critical Rossby number at which these occurs, using individual models of our seismic targets, is the subject of a paper in preparation.}
+A measurement of the exact critical Rossby number at which these occurs is the subject of a paper in preparation.}
 
@@
 	\item We found that our ensemble was $98.4\%$ more likely to be drawn from a weakened magnetic braking model than a standard model of rotational evolution \cite{vansaders+pinsonneault2013}, at a critical Rossby number of $Ro_{\rm{crit}} = 1.97$.
-\rtwo{Stars in our ensemble overall show a weaker rate of braking than one would expect from solar-calibrated rotational evolution models.} This work expands upon previous analysis \cite{vansaders+2019} by including quiescent stars older than the Sun.
+\rtwo{Stars in our ensemble overall showed a weaker rate of braking than one would expect from solar (and extrapolated solar) braking rates.} This work expands upon previous analysis \cite{vansaders+2019} by including quiescent stars older than the Sun.
 This conclusion was found to be robust against change of ensemble members and potentially underestimated asteroseismic systematic uncertainties.
@@
 \newpage
-\textbf{Acknowledgments}: The authors would like to thank the anonymous reviewer for their help improving this manuscript.
+\textbf{Acknowledgments}: The authors would like to thank the anonymous reviewers for their help improving this manuscript.
 They would also like to thank Sean Matt, Ellis Avallone, Alex Dixon, Warrick Ball and Brett Morris for helpful discussions.
@@
 
-\textbf{Correspondence:} Correspondence and requests for materials should be addressed to O.J.H.. (email: oliver.hall@esa.int).\\
+\textbf{Correspondence:} Correspondence and requests for materials should be addressed to O.J.H. (email: oliver.hall@esa.int).\\
 

### 2021-01-20 paper/natastron/2nd_draft/response/coverletter.tex
ready to submit

--- 2021-01-05 paper/natastron/1st_draft/response/coverletter.tex
@@
 We have completed our response to the reviewer, which is attached below this cover letter (and uploaded separately with resubmission).
-Based on our discussion over email on the reformatting of the original draft, we have done our best to reshuffle the paper's contents.
-We think the updated draft best matches the Nature format while keeping it accessible to the reader.
-However the Methods is longer than conventional, so please let us know if you have any suggestions on what we should move to the Supplementary Information, if necessary.
+Major changes to the text are coloured red.
+Please note that this includes a change to the title.
+No changes have been made to the Supplementary Information.
 
-We have also added data and code availability statements.
-At the moment, our main results table is in Extended Data, as we don't think it is necessary to include it in the main text.
+At the moment, our main results table is still in Extended Data, as we don't think it is necessary to include it in the main text.
 Ideally we would publish this table digitally along with the article (as well as host it on Vizier).
-If you have any input on whether this table should be (partially) included in the main text, or other thoughts on how to best present it in the Nature Astronomy format, we would be grateful also.
+If you have any input on whether this table should be (partially) included in the main text, or other thoughts on how to best present it in the Nature Astronomy format, we would be grateful.
 
@@
 	\item Abstract: 196
-	\item Introduction: 500
-	\item Main body (incl. Introduction): 2721
-	\item Methods: 5145
+	\item Introduction: 499
+	\item Main body (incl. Introduction): 2886
+	\item Methods: 5507
 	\item Supplementary Information: 2544

### 2021-02-12 paper/natastron/Publication/methods.tex
making changes for the publication

--- 2021-01-20 paper/natastron/2nd_draft/methods.tex
@@
 \subsection{Asteroseismic Data}
-For our asteroseismic power spectrum data we used the unweighted power spectra from the KASOC pipeline \cite{m_handberg+lund2014}\footnote{Obtainable from the \href{http://kasoc.phys.au.dk/}{KASOC} webpage.}.
+For our asteroseismic power spectrum data we used the unweighted power spectra from the KASOC pipeline \cite{m_handberg+lund2014}.
 We did not apply any additional treatment to these data.
-For 16 Cyg A \& B (KIC 12069424 and KIC 12069449) we used the KEPSEISMIC lightcurves \cite{m_garcia+2011}\footnote{Obtainable from \href{https://archive.
-		stsci.edu/prepds/kepseismic/}{MAST}.}, which have significantly better signal-to-noise for these two stars.
+For 16 Cyg A \& B (KIC 12069424 and KIC 12069449) we used the KEPSEISMIC lightcurves \cite{m_garcia+2011}, which have significantly better signal-to-noise for these two stars.
 
@@
 The second improvement comes in the form of priors on our parameters, and in particular the rotational inclination, which more accurately reflects the true distribution of angles than previous techniques \cite{m_chaplin+basu2017}.
-A step-by-step breakdown of the model and all priors can be found in \textbf{Supplementary Materials}.\\
+A step-by-step breakdown of the model and all priors can be found in \textbf{Supplementary Information}.\\
 
@@
 First, we fit a model for the convective background and white noise only, to the region of the power spectra that did not contain modes of oscillation.
-This was done using \texttt{PyStan} \cite{m_vanhoey+2013, m_carpenter+2017}, for 10,000 iterations on each star\footnote{These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work.}.
+This was done using \texttt{PyStan} \cite{m_vanhoey+2013, m_carpenter+2017}, for 10,000 iterations on each star.
+These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work.
 Second, we fit our full model (including the convective background) to the region containing the modes of oscillation.
@@
 
-From this asteroseismic analysis, we report inclination angle ($i$), rotational splitting ($\nu_{\rm s}$), and rotation period ($P$) in \textbf{Extended Data} Table \ref{tab:results}.
+From this asteroseismic analysis, we report inclination angle ($i$), rotational splitting ($\nu_{\rm s}$), and rotation period ($P$) in \textbf{Supplementary Information} Table 1.
 The summary statistics on these parameters were taken as the median of the posterior distribution, with uncertainties being the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles.
@@
 KIC 8478994 is not reported due to both a poor unconverged fit as well as high $\hat{R}$ on rotational parameters.
-KICs 6603624, 8760414 and 8938364 are reported in \textbf{Extended Data} Table \ref{tab:results}, but were excluded from the gyrochronology analysis due to strong disagreement with multiple studies in the literature (see main body of paper).
+KICs 6603624, 8760414 and 8938364 are reported in  \textbf{Supplementary Information} Table 1, but were excluded from the gyrochronology analysis due to strong disagreement with multiple studies in the literature (see main body of paper).
 Finally, we flagged any stars with fewer than 1000 effective samples ($n_{\rm eff}$) of $\nu_s$.
@@
 
-KIC 6278762 was excluded from this stellar model analysis, because its age fell more than $3\sigma$ outside of the highest age in the stellar models\footnote{This is a metallicity issue, as the oldest stars have metallicities outside the range of the rotational model grids.}, and KICs 7106245 and 8760414 were excluded for the same reason due to low metallicities outside the functional range of the stellar models (-0.99 and -0.92 respectively).
+KIC 6278762 was excluded from this stellar model analysis, because its age fell more than $3\sigma$ outside of the highest age in the stellar models (this is a metallicity issue, as the oldest stars have metallicities outside the range of the rotational model grids), and KICs 7106245 and 8760414 were excluded for the same reason due to low metallicities outside the functional range of the stellar models (-0.99 and -0.92 respectively).
 We also excluded any stars with $n_{\rm eff} < 1000$ for rotational splitting, and those with $\hat{R} > 1.1$.
@@
 
-\textbf{Data availability statement:} The core input data and results are summarised in \textbf{Extended Data} Table \ref{tab:results}, which is published with this article, and is also available on Vizier.
+\textbf{Data availability statement:} The core input data and results are summarised in  \textbf{Supplementary Information} Table 1, which is published with this article, and is also available on Vizier.
 Larger data files, such as stellar model populations and individual posterior distribution chains from the asteroseismic and gyrochronology model fitting are fully available on request.
@@
 
-\textbf{Code availability statement:} The code required to replicate our results has been placed in a curated online repository found here: \url{www.github.com/ojhall94/halletal2021a}.
+\textbf{Code availability statement:} The code required to replicate our results has been placed in a curated online repository found here: \url{www.github.com/ojhall94/halletal2021}.
 

### 2021-02-12 paper/natastron/Publication/paper.tex
making changes for the publication

--- 2021-01-20 paper/natastron/2nd_draft/paper.tex
@@
 \newcommand{\gaia}{\emph{Gaia}\xspace}
-\newcommand{\rtwo}[1]{\textcolor{red}{{#1}}}
+\newcommand{\rtwo}[1]{{#1}}
 
@@
 We obtained asteroseismic rotation rates of 91 main sequence stars showing high signal-to-noise modes of oscillation.
-Using these new rotation rates, along with effective temperatures, metallicities and seismic masses and ages, we built a hierarchical Bayesian mixture model to determine whether the ensemble more closely agreed with a standard rotational evolution scenario \cite{vansaders+pinsonneault2013}, or one where weakened magnetic braking takes place \cite{vansaders+2016}.
+Using these new rotation rates, along with effective temperatures, metallicities and seismic masses and ages, we built a hierarchical Bayesian mixture model to determine whether the ensemble more closely agreed with a standard rotational evolution scenario, or one where weakened magnetic braking takes place.
 The weakened magnetic braking scenario was found to be $98.4\%$ more likely for our stellar ensemble, adding to the growing body of evidence for this stage of stellar rotational evolution.
@@
 
-\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) p mode\footnote{\textit{Pressure} modes, the type of oscillation visible in main sequence stars.} oscillations for each star, of which the latter have significantly lower signal-to noise.
+\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) p mode (\textit{Pressure} modes, the type of oscillation visible in main sequence stars) oscillations for each star, of which the latter have significantly lower signal-to noise.
 Radial oscillations ($\ell = 0$) are also visible, but do not split.
-In this work, we studied a sample of 95 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}.
+In this work, we studied a sample of 95 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues.
+For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.
 Further details on these data can be found in \textbf{Methods}.
 
-We separated our sample into three categories \cite{garcia+2014}: 64 main sequence stars (MS, $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$); 4 potential sub-giant stars (SG, $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$), which may have begun to evolve off the main sequence, complicating their rotational history\footnote{It should be noted that none of these stars have identified mixed dipole modes, which indicate an evolved structure (see \cite{bedding+2010}).}; and 24 `hot' stars (H, $T_{\rm eff} > 6250\, \rm K$), which lie above the Kraft break, the point at which convective envelopes are thin, and angular momentum loss through magnetic winds becomes inefficient \cite{kraft1967}.
+We separated our sample into three categories \cite{garcia+2014}: 64 main sequence stars (MS, $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$); 4 potential sub-giant stars (SG, $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$), which may have begun to evolve off the main sequence, complicating their rotational history.
+; and 24 `hot' stars (H, $T_{\rm eff} > 6250\, \rm K$), which lie above the Kraft break, the point at which convective envelopes are thin, and angular momentum loss through magnetic winds becomes inefficient \cite{kraft1967}.
+It should be noted that none of these stars have identified mixed dipole modes, which indicate an evolved structure (see \cite{bedding+2010}).
 Our conclusions are largely insensitive to these categorical assignments, and they are intended solely to help explore results category-by-category.
@@
 Left to right, they represent masses of $1.5$, $1.25$, $1$ and $0.75\, M_\odot$.
-Vertical errorbars are too small to be visible \cite{hunter2007}.}
+Data points represent median values.
+Horizontal error bars represent the standard deviation on \teff.
+Vertical error bars represent the 68\% confidence interval on \logg, and are too small to be visible \cite{hunter2007}.}
 	\label{fig:sample}
@@
 The solid line indicates 1:1 line, while the dash-dotted lines represent 2:1 and 1:2 lines.
-The shaded region around the 1:1 line is the $1\sigma$ credible interval of the fit to the data, the result of which is shown as the title of the figure.
+The slim shaded region around the 1:1 line is the $1\sigma$ credible interval of the fit to the data, the result of which is shown as the title of the figure.
 Stars that were not included in the fitting process are transparent.
-The errorbars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions, and are smaller than the points in some cases.}
+Data points represent median values.
+The error bars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions, and are smaller than the points in some cases.}
 	\label{fig:protlit}
@@
 \textbf{Comparing gyrochronology models:} To evaluate the implications of our \rtwo{new seismic rotation rates} for gyrochronology, we compared \rtwo{the stars in our ensemble} to two population models of rotational evolution \cite{vansaders+2019}: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{vansaders+2016,skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model') \cite{vansaders+2016}.
-The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$\footnote{The Rossby number may be defined as $Ro \equiv P/\tau_{\rm cz}$, where $\tau_{\rm cz}$ is the convective turnover timescale, and $P$ is the rotation.
-The Rossby number roughly scales inversely with stellar activity (and so increases as stars age).}.
+The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$.
+The Rossby number may be defined as $Ro \equiv P/\tau_{\rm cz}$, where $\tau_{\rm cz}$ is the convective turnover timescale, and $P$ is the rotation.
+The Rossby number roughly scales inversely with stellar activity (and so increases as stars age).
 \rtwo{Because of this, the distribution of stars with a Rossby number below this threshold will be identical in both models}.
@@
 
-In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting, excluding those with a number of effective samples $n_{\rm eff} < 1000$ and a Gelman-Rubin metric of $\hat{R}<1.1$ \cite{gelman+rubin1992,salvatier+2016} (see \textbf{Extended Data} Table \ref{tab:results}).
+In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting, excluding those with a number of effective samples $n_{\rm eff} < 1000$ and a Gelman-Rubin metric of $\hat{R}<1.1$ \cite{gelman+rubin1992,salvatier+2016} (see  \textbf{Supplementary Information} Table 1).
 Two stars with low metallicities ($< -0.8\, \rm {dex}$) that fell outside the boundaries of our stellar models were also excluded.
@@
 	\centering
-	\includegraphics[width=.9\textwidth]{fullsample.png}
+	\includegraphics[width=.9\textwidth]{fullsample.pdf}
 	\caption{Stars for which rotation was measured in this work, plotted over TRILEGAL \cite{girardi+2012} stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution.
@@
 When evaluating between the two model prescriptions we also considered mass, age and metallicity.
-The errorbars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions.}
+Data points represent median values.
+The error bars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions.}
 	\label{fig:fullsample}

### 2021-02-12 paper/natastron/Publication/si.tex
making changes for the publication

--- 2020-10-07 paper/natastron/si.tex
@@
 \usepackage{amssymb}	% Extra maths symbols
+\usepackage{lscape}
+\usepackage{longtable}
+\usepackage{threeparttable}
+\usepackage{multirow}
+\usepackage[figurename={Supplementary Figure}]{caption}
+\usepackage{booktabs}
 \usepackage[ ]{hyperref}
@@
 A GP is defined by a covariance kernel (describing the degree of correlation between linewidths) and a mean function (describing a global trend with frequency).
-As this approach describes the mode linewidths relative to one another in frequency, the radial orders of each target $n$ were rescaled to be between 0 (for the lowest $n$) and 1 (for the highest $n$)\footnote{The radial orders of $\ell = 2$ modes were increased by $1$ to ensure this approximation applied to all modes.}.
+As this approach describes the mode linewidths relative to one another in frequency, the radial orders of each target $n$ were rescaled to be between 0 (for the lowest $n$) and 1 (for the highest $n$).
+The radial orders of $\ell = 2$ modes were increased by $1$ to ensure this approximation applied to all modes.
 This approximation was used to describe the change in linewidth as a function of frequency without depending on the exact frequencies of the modes, which themselves were free parameters (see above).
@@
 
-\noindent where $\ln\mathcal{N}$ represents a log-Normal distribution and $\mathcal{C}_{1/2}$ represents a half-Cauchy distribution\footnote{The half-Cauchy distribution ensures the standard deviations do not inflate to large numbers, and is generally well-behaved close to zero in the case of stars with little deviation from Eq.
-\ref{eq:asymptotic} \cite{gelman2006}.}, and other symbols are as described above.
+\noindent where $\ln\mathcal{N}$ represents a log-Normal distribution and $\mathcal{C}_{1/2}$ represents a half-Cauchy distribution.
+The half-Cauchy distribution ensures the standard deviations do not inflate to large numbers, and is generally well-behaved close to zero in the case of stars with little deviation from Eq.
+\ref{eq:asymptotic} \cite{gelman2006}.
+Other symbols are as described above.
 All three hyperparameters $\sigma_{0,1,2}$ describing the uncertainty on the latent parameters of different angular degree were subject to the same prior.
@@
 We fit our model to our power spectrum data with \texttt{PyMC3}, using 2500 iterations each on 4 chains.
-An example of our model fit to an asteroseismic power spectrum of 16 Cyg A is shown in Figure \ref{fig:modelfit}.
+An example of our model fit to an asteroseismic power spectrum of 16 Cyg A is shown in Supplementary Figure \ref{fig:modelfit}.
+
+\section{Supplementary Table}
+\input{tabulate.tex}
 
@@
 
+	\bibitem{silvaaguirre+2017}
+	\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
+	\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
+		{{Kepler Asteroseismic LEGACY Sample}}. {{II}}.{{Radii}}, {{Masses}}, and
+		{{Ages}}}.
+	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{173} (\bibinfo{year}{2017}).
+
+		\bibitem{silvaaguirre+2015}
+	\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
+	\newblock \bibinfo{title}{Ages and fundamental properties of {{Kepler}}
+		exoplanet host stars from asteroseismology}.
+	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
+			Society}} \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2127}
+	(\bibinfo{year}{2015}).
+
 \end{thebibliography}

### 2021-02-15 paper/natastron/Publication/bblmethods.tex
tidying up for publication

--- 2020-10-07 paper/natastron/bblmethods.tex
@@
 
-\bibitem{m_handberg+lund2014}
+\bibitem{handberg+lund2014}
 \bibinfo{author}{Handberg, R.} \& \bibinfo{author}{Lund, M.~N.}
@@
 
-\bibitem{m_garcia+2011}
+\bibitem{garcia+2011}
 \bibinfo{author}{Garc{\'i}a, R.~A.} \emph{et~al.}
@@
 
-\bibitem{m_silvaaguirre+2015}
-\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
-\newblock \bibinfo{title}{Ages and fundamental properties of {{Kepler}}
-  exoplanet host stars from asteroseismology}.
-\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-  Society}} \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2127}
-  (\bibinfo{year}{2015}).
-
-\bibitem{m_silvaaguirre+2017}
-\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
-\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
-  {{Kepler Asteroseismic LEGACY Sample}}. {{II}}.{{Radii}}, {{Masses}}, and
-  {{Ages}}}.
-\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-  \textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{173} (\bibinfo{year}{2017}).
-
-\bibitem{m_christensen-dalsgaard2008}
-\bibinfo{author}{{Christensen-Dalsgaard}, J.}
-\newblock \bibinfo{title}{{{ASTEC}}\textemdash the {{Aarhus STellar Evolution
-  Code}}}.
-\newblock \emph{\bibinfo{journal}{Astrophysics and Space Science}}
-  \textbf{\bibinfo{volume}{316}}, \bibinfo{pages}{13} (\bibinfo{year}{2008}).
-
-\bibitem{m_huber+2013a}
+\bibitem{huber+2013a}
 \bibinfo{author}{Huber, D.} \emph{et~al.}
@@
 
-\bibitem{m_buchhave+latham2015}
+\bibitem{buchhave+latham2015}
 \bibinfo{author}{Buchhave, L.~A.} \& \bibinfo{author}{Latham, D.~W.}
@@
 
-\bibitem{m_astropycollaboration+2013}
+\bibitem{astropycollaboration+2013}
 \bibinfo{author}{{Astropy Collaboration}} \emph{et~al.}
@@
 
-\bibitem{m_astropycollaboration+2018}
-\bibinfo{author}{{Astropy Collaboration}} \emph{et~al.}
-\newblock \bibinfo{title}{The {{Astropy Project}}: {{Building}} an
-  {{Open}}-science {{Project}} and {{Status}} of the v2.0 {{Core Package}}}.
-\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
-  \textbf{\bibinfo{volume}{156}}, \bibinfo{pages}{123} (\bibinfo{year}{2018}).
-
-\bibitem{m_ginsburg+2019}
-\bibinfo{author}{Ginsburg, A.} \emph{et~al.}
-\newblock \bibinfo{title}{Astroquery: {{An Astronomical Web}}-querying
-  {{Package}} in {{Python}}}.
-\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
-  \textbf{\bibinfo{volume}{157}}, \bibinfo{pages}{98} (\bibinfo{year}{2019}).
-
-\bibitem{m_mckinney2010}
+\bibitem{mckinney2010}
 \bibinfo{author}{McKinney, W.}
@@
 
-\bibitem{m_davies+2015}
-\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
-\newblock \bibinfo{title}{Asteroseismic inference on rotation, gyrochronology
-  and planetary system dynamics of 16 {{Cygni}}}.
-\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-  Society}} \textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959}
-  (\bibinfo{year}{2015}).
-
-\bibitem{m_harvey1985}
+\bibitem{harvey1985}
 \bibinfo{author}{Harvey, J.}
@@
 
-\bibitem{m_tassoul1980}
+\bibitem{tassoul1980}
 \bibinfo{author}{Tassoul, M.}
@@
 
-\bibitem{m_vrard+2016}
-\bibinfo{author}{Vrard, M.}, \bibinfo{author}{Mosser, B.} \&
-  \bibinfo{author}{Samadi, R.}
-\newblock \bibinfo{title}{Period spacings in red giants. {{II}}. {{Automated}}
-  measurement}.
-\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
-  \textbf{\bibinfo{volume}{588}}, \bibinfo{pages}{A87} (\bibinfo{year}{2016}).
-
-\bibitem{m_hogg+2010}
+\bibitem{hogg+2010}
 \bibinfo{author}{Hogg, D.~W.}, \bibinfo{author}{Bovy, J.} \&
@@
 
-\bibitem{m_hall+2019}
-\bibinfo{author}{Hall, O.~J.} \emph{et~al.}
-\newblock \bibinfo{title}{Testing asteroseismology with {{Gaia DR2}}:
-  {{Hierarchical}} models of the {{Red Clump}}}.
-\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-  Society}} \textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{3569--3585}
-  (\bibinfo{year}{2019}).
-\newblock \eprint{1904.07919}.
-
-\bibitem{m_mazumdar+2014}
+\bibitem{mazumdar+2014}
 \bibinfo{author}{Mazumdar, A.} \emph{et~al.}
@@
 
-\bibitem{m_chaplin+basu2017}
+\bibitem{chaplin+basu2017}
 \bibinfo{author}{Chaplin, W.~J.} \& \bibinfo{author}{Basu}.
@@
 
-\bibitem{m_vanhoey+2013}
+\bibitem{vanhoey+2013}
 \bibinfo{author}{Van~Hoey, S.}, \bibinfo{author}{{van der Kwast}, J.},
@@
 
-\bibitem{m_carpenter+2017}
-\bibinfo{author}{Carpenter, B.} \emph{et~al.}
-\newblock \bibinfo{title}{Stan: {{A Probabilistic Programming Language}}}.
-\newblock \emph{\bibinfo{journal}{Journal of Statistical Software}}
-  \textbf{\bibinfo{volume}{76}}, \bibinfo{pages}{1--32} (\bibinfo{year}{2017}).
-
-\bibitem{m_vanderwalt+2011}
+\bibitem{vanderwalt+2011}
 \bibinfo{author}{{van der Walt}, S.}, \bibinfo{author}{Colbert, S.~C.} \&
@@
 
-\bibitem{m_salvatier+2016}
-\bibinfo{author}{Salvatier, J.}, \bibinfo{author}{Wiecki, T.~V.} \&
-  \bibinfo{author}{Fonnesbeck, C.}
-\newblock \bibinfo{title}{Probabilistic programming in {{Python}} using
-  {{PyMC3}}}.
-\newblock \emph{\bibinfo{journal}{PeerJ Computer Science}}
-  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{e55} (\bibinfo{year}{2016}).
-
-\bibitem{m_thetheanodevelopmentteam+2016}
-\bibinfo{author}{{The Theano Development Team}} \emph{et~al.}
-\newblock \bibinfo{title}{Theano: {{A Python}} framework for fast computation
-  of mathematical expressions}.
-\newblock \emph{\bibinfo{journal}{arXiv:1605.02688 [cs]}}
-  (\bibinfo{year}{2016}).
-\newblock \eprint{1605.02688}.
-
-\bibitem{m_gelman+rubin1992}
-\bibinfo{author}{Gelman, A.} \& \bibinfo{author}{Rubin, D.~B.}
-\newblock \bibinfo{title}{Inference from {{Iterative Simulation Using Multiple
-  Sequences}}}.
-\newblock \emph{\bibinfo{journal}{Statistical Science}}
-  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{457--472}
-  (\bibinfo{year}{1992}).
-
-\bibitem{m_vansaders+pinsonneault2013}
-\bibinfo{author}{{van Saders}, J.~L.} \& \bibinfo{author}{Pinsonneault, M.~H.}
-\newblock \bibinfo{title}{Fast {{Star}}, {{Slow Star}}; {{Old Star}}, {{Young
-  Star}}: {{Subgiant Rotation}} as a {{Population}} and {{Stellar Physics
-  Diagnostic}}}.
-\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-  \textbf{\bibinfo{volume}{776}}, \bibinfo{pages}{67} (\bibinfo{year}{2013}).
-
-\bibitem{m_vansaders+2016}
-\bibinfo{author}{{van Saders}, J.~L.} \emph{et~al.}
-\newblock \bibinfo{title}{Weakened magnetic braking as the origin of
-  anomalously rapid rotation in old field stars}.
-\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{529}},
-  \bibinfo{pages}{181} (\bibinfo{year}{2016}).
-
-\bibitem{m_vansaders+2019}
-\bibinfo{author}{{van Saders}, J.~L.}, \bibinfo{author}{Pinsonneault, M.~H.} \&
-  \bibinfo{author}{Barbieri, M.}
-\newblock \bibinfo{title}{Forward {{Modeling}} of the {{Kepler Stellar Rotation
-  Period Distribution}}: {{Interpreting Periods}} from {{Mixed}} and {{Biased
-  Stellar Populations}}}.
-\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-  \textbf{\bibinfo{volume}{872}}, \bibinfo{pages}{128} (\bibinfo{year}{2019}).
-
-\bibitem{m_girardi+2012}
-\bibinfo{author}{Girardi, L.} \emph{et~al.}
-\newblock \bibinfo{title}{{{TRILEGAL}}, a {{TRIdimensional modeL}} of {{thE
-  GALaxy}}: {{Status}} and {{Future}}}.
-\newblock \emph{\bibinfo{journal}{Astrophysics and Space Science Proceedings}}
-  \textbf{\bibinfo{volume}{26}}, \bibinfo{pages}{165} (\bibinfo{year}{2012}).
-
-\bibitem{m_berger+2020}
-\bibinfo{author}{Berger, T.~A.} \emph{et~al.}
-\newblock \bibinfo{title}{The \${{Gaia}}\$-\${{Kepler}}\$ {{Stellar Properties
-  Catalog I}}: {{Homogeneous Fundamental Properties}} for 186,000
-  \${{Kepler}}\$ {{Stars}}}.
-\newblock \emph{\bibinfo{journal}{arXiv:2001.07737 [astro-ph]}}
-  (\bibinfo{year}{2020}).
-\newblock \eprint{2001.07737}.
-
-\bibitem{m_gaiacollaboration+2018}
+\bibitem{gaiacollaboration+2018}
 \bibinfo{author}{{Gaia Collaboration}} \emph{et~al.}
@@
 
-\bibitem{m_raghavan+2010}
+\bibitem{raghavan+2010}
 \bibinfo{author}{Raghavan, D.} \emph{et~al.}
@@
 
-\bibitem{m_chaplin+2011}
+\bibitem{chaplin+2011}
 \bibinfo{author}{Chaplin, W.~J.} \emph{et~al.}
@@
 
-\bibitem{m_seabold+perktold2010}
+\bibitem{seabold+perktold2010}
 \bibinfo{author}{Seabold, S.} \& \bibinfo{author}{Perktold, J.}
@@
 
-\bibitem{m_betancourt+girolami2013}
-\bibinfo{author}{Betancourt, M.~J.} \& \bibinfo{author}{Girolami, M.}
-\newblock \bibinfo{title}{Hamiltonian {{Monte Carlo}} for {{Hierarchical
-  Models}}}.
-\newblock \emph{\bibinfo{journal}{arXiv:1312.0906 [stat]}}
-  (\bibinfo{year}{2013}).
-\newblock \eprint{1312.0906}.
-
-\bibitem{m_foreman-mackey+2013}
+\bibitem{foreman-mackey+2013}
 \bibinfo{author}{{Foreman-Mackey}, D.}, \bibinfo{author}{Hogg, D.~W.},
@@
 
-\bibitem{m_foreman-mackey2016}
-\bibinfo{author}{{Foreman-Mackey}, D.}
-\newblock \bibinfo{title}{Corner.py: {{Scatterplot}} matrices in {{Python}}}.
-\newblock \emph{\bibinfo{journal}{The Journal of Open Source Software}}
-  \textbf{\bibinfo{volume}{1}} (\bibinfo{year}{2016}).
-
-\bibitem{m_nielsen+2015}
-\bibinfo{author}{Nielsen, M.~B.}, \bibinfo{author}{Schunker, H.},
-  \bibinfo{author}{Gizon, L.} \& \bibinfo{author}{Ball, W.~H.}
-\newblock \bibinfo{title}{Constraining differential rotation of {{Sun}}-like
-  stars from asteroseismic and starspot rotation periods}.
-\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
-  \textbf{\bibinfo{volume}{582}}, \bibinfo{pages}{A10} (\bibinfo{year}{2015}).
-
-\bibitem{m_benomar+2018}
-\bibinfo{author}{Benomar, O.} \emph{et~al.}
-\newblock \bibinfo{title}{Asteroseismic detection of latitudinal differential
-  rotation in 13 {{Sun}}-like stars}.
-\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{361}},
-  \bibinfo{pages}{1231} (\bibinfo{year}{2018}).
-
-\bibitem{m_beck2000}
-\bibinfo{author}{Beck, J.~G.}
-\newblock \bibinfo{title}{A comparison of differential rotation measurements -
-  ({{Invited Review}})}.
-\newblock \emph{\bibinfo{journal}{Solar Physics}}
-  \textbf{\bibinfo{volume}{191}}, \bibinfo{pages}{47--70}
-  (\bibinfo{year}{2000}).
-
-\bibitem{m_benomar+2015}
-\bibinfo{author}{Benomar, O.}, \bibinfo{author}{Takata, M.},
-  \bibinfo{author}{Shibahashi, H.}, \bibinfo{author}{Ceillier, T.} \&
-  \bibinfo{author}{Garc{\'i}a, R.~A.}
-\newblock \bibinfo{title}{Nearly uniform internal rotation of solar-like
-  main-sequence stars revealed by space-based asteroseismology and
-  spectroscopic measurements}.
-\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-  Society}} \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2654--2674}
-  (\bibinfo{year}{2015}).
-
-\bibitem{m_doyle+2014}
-\bibinfo{author}{Doyle, A.~P.}, \bibinfo{author}{Davies, G.~R.},
-  \bibinfo{author}{Smalley, B.}, \bibinfo{author}{Chaplin, W.~J.} \&
-  \bibinfo{author}{Elsworth, Y.}
-\newblock \bibinfo{title}{Determining stellar macroturbulence using
-  asteroseismic rotational velocities from {{Kepler}}}.
-\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-  Society}} \textbf{\bibinfo{volume}{444}}, \bibinfo{pages}{3592--3602}
-  (\bibinfo{year}{2014}).
-
-\bibitem{m_tayar+2015}
-\bibinfo{author}{Tayar, J.} \emph{et~al.}
-\newblock \bibinfo{title}{Rapid {{Rotation}} of {{Low}}-mass {{Red Giants Using
-  APOKASC}}: {{A Measure}} of {{Interaction Rates}} on the
-  {{Post}}-main-sequence}.
-\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-  \textbf{\bibinfo{volume}{807}}, \bibinfo{pages}{82} (\bibinfo{year}{2015}).
-
-\bibitem{m_schofield+2019}
-\bibinfo{author}{Schofield, M.} \emph{et~al.}
-\newblock \bibinfo{title}{The {{Asteroseismic Target List}} for {{Solar}}-like
-  {{Oscillators Observed}} in 2 minute {{Cadence}} with the {{Transiting
-  Exoplanet Survey Satellite}}}.
-\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
-  \textbf{\bibinfo{volume}{241}}, \bibinfo{pages}{12} (\bibinfo{year}{2019}).
-
-\bibitem{m_mathur+2019}
-\bibinfo{author}{{Mathur}, S.} \emph{et~al.}
-\newblock \bibinfo{title}{{Revisiting the impact of stellar magnetic activity
-  on the detection of solar-like oscillations by Kepler}}.
-\newblock \emph{\bibinfo{journal}{Frontiers in Astronomy and Space Sciences}}
-  \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{46} (\bibinfo{year}{2019}).
-\newblock \eprint{1907.01415}.
-
-\bibitem{m_amard+matt2020}
-\bibinfo{author}{Amard, L.} \& \bibinfo{author}{Matt, S.~P.}
-\newblock \bibinfo{title}{The {{Impact}} of {{Metallicity}} on the
-  {{Evolution}} of {{Rotation}} and {{Magnetic Activity}} of {{Sun}}-{{Like
-  Stars}}}.
-\newblock \emph{\bibinfo{journal}{arXiv:2001.10404 [astro-ph]}}
-  (\bibinfo{year}{2020}).
-\newblock \eprint{2001.10404}.
-
-\bibitem{m_matt+2015}
-\bibinfo{author}{Matt, S.~P.}, \bibinfo{author}{Brun, A.~S.},
-  \bibinfo{author}{Baraffe, I.}, \bibinfo{author}{Bouvier, J.} \&
-  \bibinfo{author}{Chabrier, G.}
-\newblock \bibinfo{title}{The {{Mass}}-dependence of {{Angular Momentum
-  Evolution}} in {{Sun}}-like {{Stars}}}.
-\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-  \textbf{\bibinfo{volume}{799}}, \bibinfo{pages}{L23} (\bibinfo{year}{2015}).
-
-\bibitem{m_leiner+2019}
-\bibinfo{author}{Leiner, E.}, \bibinfo{author}{Mathieu, R.~D.},
-  \bibinfo{author}{Vanderburg, A.}, \bibinfo{author}{Gosnell, N.~M.} \&
-  \bibinfo{author}{Smith, J.~C.}
-\newblock \bibinfo{title}{Blue {{Lurkers}}: {{Hidden Blue Stragglers}} on the
-  {{M67 Main Sequence Identified}} from {{Their Kepler}}/{{K2 Rotation
-  Periods}}}.
-\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-  \textbf{\bibinfo{volume}{881}}, \bibinfo{pages}{47} (\bibinfo{year}{2019}).
-
-\bibitem{m_fleming+2019}
-\bibinfo{author}{Fleming, D.~P.}, \bibinfo{author}{Barnes, R.},
-  \bibinfo{author}{Davenport, J. R.~A.} \& \bibinfo{author}{Luger, R.}
-\newblock \bibinfo{title}{Rotation {{Period Evolution}} in {{Low}}-mass
-  {{Binary Stars}}: {{The Impact}} of {{Tidal Torques}} and {{Magnetic
-  Braking}}}.
-\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-  \textbf{\bibinfo{volume}{881}}, \bibinfo{pages}{88} (\bibinfo{year}{2019}).
-
-\bibitem{m_maxted+2015}
-\bibinfo{author}{Maxted, P. F.~L.}, \bibinfo{author}{Serenelli, A.~M.} \&
-  \bibinfo{author}{Southworth, J.}
-\newblock \bibinfo{title}{Comparison of gyrochronological and isochronal age
-  estimates for transiting exoplanet host stars}.
-\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
-  \textbf{\bibinfo{volume}{577}}, \bibinfo{pages}{A90} (\bibinfo{year}{2015}).
-
-\bibitem{m_gallet+delorme2019}
-\bibinfo{author}{Gallet, F.} \& \bibinfo{author}{Delorme, P.}
-\newblock \bibinfo{title}{Star-planet tidal interaction and the limits of
-  gyrochronology}.
-\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
-  \textbf{\bibinfo{volume}{1905}}, \bibinfo{pages}{arXiv:1905.06070}
-  (\bibinfo{year}{2019}).
-
-\bibitem{m_benbakoura+2019}
-\bibinfo{author}{Benbakoura, M.}, \bibinfo{author}{R{\'e}ville, V.},
-  \bibinfo{author}{Brun, A.~S.}, \bibinfo{author}{{Le Poncin-Lafitte}, C.} \&
-  \bibinfo{author}{Mathis, S.}
-\newblock \bibinfo{title}{Evolution of star-planet systems under magnetic
-  braking and tidal interaction}.
-\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
-  \textbf{\bibinfo{volume}{621}}, \bibinfo{pages}{A124} (\bibinfo{year}{2019}).
-
-\bibitem{m_ceillier+2016}
-\bibinfo{author}{Ceillier, T.} \emph{et~al.}
-\newblock \bibinfo{title}{Rotation periods and seismic ages of {{KOIs}} -
-  comparison with stars without detected planets from {{Kepler}} observations}.
-\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-  Society}} \textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{119--125}
-  (\bibinfo{year}{2016}).
-
 \end{thebibliography}

### 2021-02-15 paper/natastron/Publication/ed.tex
making changes for the publication
tidying up for publication

--- 2021-01-07 paper/natastron/2nd_draft/ed.tex
@@
 	\centering
-	\includegraphics[width=0.6 \textwidth]{pgm_models.pdf}
-	\caption{A probabilistic graphical model (PGM) represented algebraically in Equation \ref{eq:modelll}.
-The shaded circle indicates observed data, and solid black points represent other fixed information, such as the KDEs and observational uncertainties.
+	\includegraphics[width=0.6 \textwidth]{pgm_models.jpg}
+	\caption{\textbf{A probabilistic graphical model (PGM) represented algebraically in Equation \ref{eq:modelll}.} The shaded circle indicates observed data, and solid black points represent other fixed information, such as the KDEs and observational uncertainties.
 The remaining circles represent parameters.
@@
 \end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{Images/priors.png}
-	\caption{Comparisons between posterior estimates of rotational parameters (data points and error bars) and the priors on these parameters (shaded regions).
-Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$).
-Both the prior and values for $P$ are a transformation of the upper two parameters (see \textbf{Methods} and \textbf{Supplementary Information}) In all cases, the extent of the error bars and shaded regions indicate the 68\% credible ($1\sigma$) interval of the posterior and prior distributions respectively.
-The solid lines indicate the median of the prior distributions.
-In this figure, results with means and errorbars that closely resemble the prior distribution can be interpreted as prior-dominated (i.e.
-poorly informed by the data).
-All stars are sorted and coloured and sorted by age.
-In the case of inclination angle $i$ and rotation period $P$, the displayed priors are transformed from the priors imposed on the sampled parameters from which their posteriors were derived.}
-	\label{fig:priors}
-\end{figure}
-
-\begin{figure*}[h!]
-	\centering
-	\includegraphics[width=\textwidth]{Images/litcomp_alt2.pdf}
-	\caption{Comparisons between posterior estimates of rotational parameters from this work, LEGACY and `Kages' \cite[private communication]{m_davies+2016, m_lund+2017}.
-Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$).
-Fractional differences are plotted against stellar rotation obtained in this work.
-The $\Delta$ indicates the fractional difference between this work and the literature (i.e.
-stars above the zero-line have higher values in this work).
-The right hand panels the distribution of the fractional differences around the zero line.
-The colour legend is consistent throughout all panels.
-The x-axis units on the right hand panels are equivalent to the y-axis of the left hand panels.
-10 stars have been omitted from this plot and are discussed in more detail in \textbf{Methods}: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have extremely low rotation periods in Kages, with high uncertainties.
-Conversely, KICs 6603624, 8760414 and 8938364 have extremely high rotation periods in LEGACY with low uncertainties.
-In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
-	\label{fig:legacykages}
-\end{figure*}
-
-\begin{figure}[h!]
- \centering
- \includegraphics[width=0.8\textwidth]{Images/seis_comparison_rot_alt2.pdf}
- \caption{Fractional differences between posterior estimates of asteroseismic rotation period from this work.
-Literature sources are: Davies et al.
-(2015) \cite{m_davies+2015} (16 Cyg A \& B), Nielsen et al.
-(2015) \cite{m_nielsen+2015} (5 stars) and Benomar et al.
-(2018) \cite{m_benomar+2018} (40 stars).
-We used the reported parameter $a_{1}$ from the latter, which represents the rotational splitting in the case of uniform latitudinal rotation in their model.
-The dashed line represents the median of the sample shown, with the dotted lines representing the $15.9^{\rm{th}}$ and $84.1^{\rm{st}}$ percentiles.
-In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
- \label{fig:literaturecomp}
-\end{figure}
-
- \begin{figure*}[h!]
- 	\centering
- 	\includegraphics[width=\textwidth]{Images/vsini_comparison_new.pdf}
- 	\caption{Comparisons between asteroseismic and spectroscopic measures of projected surface rotation, $\textrm{v}\sin(i)$.
-All asteroseismic (x-axis) values are from this work, all spectroscopic (y-axis) values are from the literature.
-\textit{Left}: comparisons to 81 stars values reported in LEGACY and Kages.
-\textit{Right}: comparisons to 16 stars observed by Benomar et al.
-(2015) \cite{m_benomar+2015}.
-Asteroseismic values are transformed from projected splitting ($\nu_s\sin(i)$) using the asteroseismic radius measurements presented in LEGACY and `Kages'.
-The solid lines indicate the 1:1 line, while the dash-dotted lines represent the 2:1 and 1:2 lines.
-The dashed lines indicate the location of $\textrm{v}\sin(i) = 5\, \rm{kms^{-1}}$, the point at which surface and seismic measures of projected rotation begin to differ strongly \cite{m_tayar+2015}.}
- 	\label{fig:vsinilit}
- \end{figure*}
-
-\input{tabulate.tex}

### 2021-02-15 paper/natastron/Publication/methods.tex
tidying up for publication

@@
 \section*{\underline{Methods}}
-\setcounter{tocdepth}{2}
-\tableofcontents
+%\setcounter{tocdepth}{2}
+%\tableofcontents
 \section{Asteroseismic Methods}
 \subsection{Asteroseismic Data}
-For our asteroseismic power spectrum data we used the unweighted power spectra from the KASOC pipeline \cite{m_handberg+lund2014}.
+For our asteroseismic power spectrum data we used the unweighted power spectra from the KASOC pipeline \cite{handberg+lund2014}.
 We did not apply any additional treatment to these data.
-For 16 Cyg A \& B (KIC 12069424 and KIC 12069449) we used the KEPSEISMIC lightcurves \cite{m_garcia+2011}, which have significantly better signal-to-noise for these two stars.
+For 16 Cyg A \& B (KIC 12069424 and KIC 12069449) we used the KEPSEISMIC lightcurves \cite{garcia+2011}, which have significantly better signal-to-noise for these two stars.
 
@@
 These ages have been obtained by comparisons of measured oscillation properties to stellar models, accounting for an expanded range of metallicities.
-\texttt{BASTA} is thoroughly compared to four other seismic modelling techniques in \cite{m_silvaaguirre+2017}.
+\texttt{BASTA} is thoroughly compared to four other seismic modelling techniques in \cite{silvaaguirre+2017}.
 While uncertainties found through \texttt{BASTA} are typically higher than for other techniques, only \texttt{BASTA} and \texttt{ASTFIT} \cite[Aarhus STellar Evolution Code]{m_christensen-dalsgaard2008} recover the radius, mass and age of the Sun, when applied to solar data.
@@
 
-As described in the catalogue papers, for `Kages' stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy \cite{m_huber+2013a}.
-For LEGACY stars, atmospheric properties were similarly taken from one study \cite{m_buchhave+latham2015} for most stars in the catalogue, and complemented by other values from the literature for the remaining stars \cite[see Table 3]{m_silvaaguirre+2017}.
+As described in the catalogue papers, for `Kages' stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy \cite{huber+2013a}.
+For LEGACY stars, atmospheric properties were similarly taken from one study \cite{buchhave+latham2015} for most stars in the catalogue, and complemented by other values from the literature for the remaining stars \cite[see Table 3]{m_silvaaguirre+2017}.
 
-Other asteroseismic properties used in this study, such as those used as first guesses on the free parameters in our asteroseismic model, were taken from the `Kages' and LEGACY catalogues \cite{m_astropycollaboration+2013, m_astropycollaboration+2018, m_ginsburg+2019}.
-In cases where both catalogues contained the same target, we used the stellar parameters reported in LEGACY \cite{m_mckinney2010}.
+Other asteroseismic properties used in this study, such as those used as first guesses on the free parameters in our asteroseismic model, were taken from the `Kages' and LEGACY catalogues \cite{astropycollaboration+2013, m_astropycollaboration+2018, m_ginsburg+2019}.
+In cases where both catalogues contained the same target, we used the stellar parameters reported in LEGACY \cite{mckinney2010}.
 This is also the case for the masses and ages described above.
@@
 In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background, modes of oscillation, and white noise, while accounting for rotational splitting.
-The foundations of this approach follows best-practices in asteroseismology \cite{m_davies+2015}, fitting Harvey profiles for the background \cite{m_harvey1985} and expressing the frequencies of the modes using an asymptotic expression \cite{m_tassoul1980, m_vrard+2016}.
+The foundations of this approach follows best-practices in asteroseismology \cite{davies+2015}, fitting Harvey profiles for the background \cite{harvey1985} and expressing the frequencies of the modes using an asymptotic expression \cite{tassoul1980, m_vrard+2016}.
 
-The first core improvement in this work is the use of hierarchical latent variable models \cite{m_hogg+2010, m_hall+2019}, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{m_mazumdar+2014}).
+The first core improvement in this work is the use of hierarchical latent variable models \cite{hogg+2010, m_hall+2019}, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{mazumdar+2014}).
 By improving the inference of mode frequencies in this way, we also improve the ability to resolve the rotational splitting.
-The second improvement comes in the form of priors on our parameters, and in particular the rotational inclination, which more accurately reflects the true distribution of angles than previous techniques \cite{m_chaplin+basu2017}.
+The second improvement comes in the form of priors on our parameters, and in particular the rotational inclination, which more accurately reflects the true distribution of angles than previous techniques \cite{chaplin+basu2017}.
 A step-by-step breakdown of the model and all priors can be found in \textbf{Supplementary Information}.\\
@@
 First, we fit a model for the convective background and white noise only, to the region of the power spectra that did not contain modes of oscillation.
-This was done using \texttt{PyStan} \cite{m_vanhoey+2013, m_carpenter+2017}, for 10,000 iterations on each star.
+This was done using \texttt{PyStan} \cite{vanhoey+2013, m_carpenter+2017}, for 10,000 iterations on each star.
 These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work.
@@
 The results of the first fit to the convective background were used as extremely informative priors on the background parameters in this second fit.
-This was done using \texttt{PyMC3} \cite{m_vanderwalt+2011,m_salvatier+2016, m_thetheanodevelopmentteam+2016} for 2500 iterations each on 4 chains.
+This was done using \texttt{PyMC3} \cite{vanderwalt+2011,m_salvatier+2016, m_thetheanodevelopmentteam+2016} for 2500 iterations each on 4 chains.
 
@@
 We flagged any sub-optimal conditions of the final fit.
-We flagged 5 for which the Gelman-Rubin convergence metric, $\hat{R}$, was greater than 1.01 and 2 stars for which it was greater than 1.1 on inclination angle or rotation, where a $\hat{R} = 1$ indicates a converged result \cite{m_gelman+rubin1992}.
+We flagged 5 for which the Gelman-Rubin convergence metric, $\hat{R}$, was greater than 1.01 and 2 stars for which it was greater than 1.1 on inclination angle or rotation, where a $\hat{R} = 1$ indicates a converged result \cite{gelman+rubin1992}.
 We also performed visual checks of the sampled chains on all hyperparameters and of the best-fit model compared to both the raw and smoothed asteroseismic data.
@@
 Finally, we flagged any stars with fewer than 1000 effective samples ($n_{\rm eff}$) of $\nu_s$.
+
+\subsection{Seismic vs Surface rotation}
+As described in the main body of the paper, we compared a subsample of our asteroesismic rotation rates to surface rotation rates from spot rotation, where available.
+Both the surface ($P_{\rm surf}$) and seismic ($P_{\rm seis}$) rotation rates have associated uncertainties.
+Instead of fitting the slope between these two values directly, we instead fit the distribution
+
+\begin{equation}
+	p(\frac{P_{\rm seis}}{P_{\rm surf}}\, |\, m) = \mathcal{N}(m, \sigma_\frac{P_{\rm seis}}{P_{\rm surf}})\, ,
+\end{equation}
+
+\noindent where $m$ is the slope, and $\sigma_\frac{P_{\rm seis}}{P_{\rm surf}}$ is the uncertainty corresponding to $\frac{P_{\rm seis}}{P_{\rm surf}}$, following the propagation of the errors on both values.
+We used the larger of the asymmetrical uncertainties on asteroseismic rotation from our analysis.
+The model was fit using \texttt{PyMC3} for 2000 iterations each on 4 chains.
+Five stars for which both surface and seismic rotation were available, but which had a surface rotation above the 1.8:1 line, were excluded from this analysis.
+This was to exclude likely multiples of the true rotation rate skewing the fit, as measurements of double the true rotation may occur in spot rotation measurements.
+
+Our fit found a value of $m = 0.96 \pm 0.03$ using 48 stars.
+We reran this analysis using the 21 stars in this sample for which the median of their posterior probability for $Q_{\rm WMB}$ was greater than $0.5$ in our stellar model analysis, preferring the WMB model.
+A fit to these stars alone found a value of $m = 0.96 \pm 0.04$.
 
@@
 In the weakened magnetic braking model, $Ro_{\rm crit} = 1.97$.
-\rtwo{This Rossby number is based on model comparisons to catalogues of spot rotation rates \cite{m_vansaders+2019}.
+\rtwo{This Rossby number is based on model comparisons to catalogues of spot rotation rates \cite{vansaders+2019}.
 Its exact value is not critical in our analysis, as any similar value would create a model population significantly different from the standard case.
 In the model, the Rossby number is defined as the rotation period divided by the convective turnover timescale, which in turn is defined as $\tau_{\rm cz} = H_p / v_{\rm conv}$, where $H_p$ is the pressure scale height at the base of the convection zone, and $v_{\rm conv}$ is the convetive velocity evaluated one pressure scale height above the base in a mixing length theory of convection.
-Solid body rotation is assumed \cite{m_nielsen+2015}.} For further details, see \cite{m_vansaders+pinsonneault2013} and \cite{m_vansaders+2016, m_vansaders+2019} for the standard and weakened magnetic braking cases respectively.
+Solid body rotation is assumed \cite{nielsen+2015}.} For further details, see \cite{vansaders+pinsonneault2013} and \cite{vansaders+2016, m_vansaders+2019} for the standard and weakened magnetic braking cases respectively.
 
-To construct a synthetic population of rotating stars, we expanded upon previous forward-models of the \textit{Kepler} field with the purpose of studying weakened magnetic braking \cite{m_vansaders+2019}, with some important improvements.
-We started with a TRILEGAL \cite{m_girardi+2012} Milky-Way simulation of the \kepler field, using the simulation's standard population values intended for this purpose.
-In order to replicate the \kepler selection effect, the TRILEGAL simulation was matched to the largest current catalogue of temperatures, luminosities and 2MASS $K$-band magnitudes of stars in the \kepler field \cite{m_berger+2020}.
+To construct a synthetic population of rotating stars, we expanded upon previous forward-models of the \textit{Kepler} field with the purpose of studying weakened magnetic braking \cite{vansaders+2019}, with some important improvements.
+We started with a TRILEGAL \cite{girardi+2012} Milky-Way simulation of the \kepler field, using the simulation's standard population values intended for this purpose.
+In order to replicate the \kepler selection effect, the TRILEGAL simulation was matched to the largest current catalogue of temperatures, luminosities and 2MASS $K$-band magnitudes of stars in the \kepler field \cite{berger+2020}.
 This was done using a nearest-neighbours approach, based on the density of stars on the HR diagram.
-This ensured that the TRILEGAL population matched the density of stars actually observed by \kepler, replicating its selection effects, and improved upon previous efforts \cite{m_vansaders+2019} by incorporating contemporary \textit{Gaia} mission data \cite{m_gaiacollaboration+2018}.
+This ensured that the TRILEGAL population matched the density of stars actually observed by \kepler, replicating its selection effects, and improved upon previous efforts \cite{vansaders+2019} by incorporating contemporary \textit{Gaia} mission data \cite{gaiacollaboration+2018}.
 
-We made further changes to account for possible binarity in the the matching sample \cite{m_berger+2020}.
+We made further changes to account for possible binarity in the the matching sample \cite{berger+2020}.
 If the first step is performed blindly, blended binaries in the sample cause an overestimation of the number of old stars.
@@
 \begin{enumerate}
-	\item blended the TRILEGAL stars with binary companions drawn from a flat mass-ratio distribution, using a known binary fraction \cite{m_raghavan+2010},
+	\item blended the TRILEGAL stars with binary companions drawn from a flat mass-ratio distribution, using a known binary fraction \cite{raghavan+2010},
 	\item recalculated the `observed' luminosities and magnitudes assuming that each binary pair was blended, and
-	\item shifted these stars' temperatures following a $g$-$K$ magnitude relation \cite{m_berger+2020}.
+	\item shifted these stars' temperatures following a $g$-$K$ magnitude relation \cite{berger+2020}.
 \end{enumerate}
@@
 Both the standard and WMB models contain stars with the same fundamental parameters (mass, radius, effective temperature, metallicity) but a different period based on the choice of rotational evolution prescription.
-Applying an asteroseismic selection function that depends on these fundamental parameters would have an identical effect on both models, therefore providing no net effect on our posterior distribution \cite{m_chaplin+2011}.
+Applying an asteroseismic selection function that depends on these fundamental parameters would have an identical effect on both models, therefore providing no net effect on our posterior distribution \cite{chaplin+2011}.
 Additionally, we expected any seismic selection function to be relatively flat (and therefore uninformative) on a star-by-star scale, on which we run our model analysis.
@@
 \subsection{Bayesian Mixture Model}
-In order to determine whether weakened magnetic braking occurs on the main sequence, we compared our sample of seismic age and rotation, along with temperature, metallicity and mass, to the two stellar population models of the \kepler field \cite{m_vansaders+2019}, discussed above.
+In order to determine whether weakened magnetic braking occurs on the main sequence, we compared our sample of seismic age and rotation, along with temperature, metallicity and mass, to the two stellar population models of the \kepler field \cite{vansaders+2019}, discussed above.
 Both stellar models were evaluated in a Bayesian framework, with the rationale of determining which of the two models (standard or WMB) is most likely to reproduce our observed data.
@@
 
-In order to draw probabilistic inference about the models, we built a five-dimensional Kernel Density Estimate (KDE) of both model populations using the \texttt{statsmodels} package \cite{m_seabold+perktold2010}.
+In order to draw probabilistic inference about the models, we built a five-dimensional Kernel Density Estimate (KDE) of both model populations using the \texttt{statsmodels} package \cite{seabold+perktold2010}.
 We used a band-width (setting the resolution of the KDE) of $0.02\, M_\odot$ in mass, $10\, \rm K$ in \teff, $0.01\, \rm{dex}$ in $\ln(t)$, $0.01\, \rm{dex}$ in $\rm{[Fe/H]}$ and $0.01\, \rm{dex}$ in $\ln(P)$.
@@
 
-We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{m_foreman-mackey+2013, m_foreman-mackey2016}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.
+We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{foreman-mackey+2013, m_foreman-mackey2016}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.
 
@@
 In this histogram, each bin approximated the value of the posterior function for $Q_{\rm WMB}$.
-The array of 100 bins for all stars were multiplied, resulting in an approximation of the joint posterior probability function for $Q_{\rm WMB}$ given all stars in the ensemble.
-
-\section{Verifying asteroseismic results}
-\subsection{Priors on rotational parameters}
-In our Bayesian analysis, we have placed weakly informative priors on our sampled rotational parameters, $\nu_{\rm s}\sin(i)$ and $\cos(i)$.
-The prior is especially important for the angle of inclination, which is hardest to infer from the data.
-We are able to validate the robustness of our asteroseismic results by confirming that their posterior distributions are data-dominated, and not prior-dominated.
-We can do so by comparing the $68\%$ credible regions of the posterior estimates of $\nu_{\rm s}\sin(i)$ and $i$ against the $68\%$ credible regions of their priors.
-
-A comparison between prior and posterior is shown for 94 stars in $\nu_{\rm s}\sin(i)$, $i$ and $P$ in \textbf{Extended Data} Figure \ref{fig:priors}, arranged by age.
-\rtwo{In the Figure, results with means (symbols) and $68\%$ credible regions (error bars) that are close to those same values for the prior distribution (where the horizontal line is the mean, and the shaded area is the credible region) can be interpreted as prior-dominated (i.e.
-poorly informed by the data).
-Cases where the means differ or the credible regions are smaller than the prior distribution are data-dominated.} The projected splitting, $\nu_{\rm s}\sin(i)$, is overall well constrained, with only one star \rtwo{being} prior dominated.
-This is expected, as the projected splitting is what we observe on the star before decoupling inclination and rotation.
-The angle of inclination $i$, sampled as $\cos(i)$, more closely follows the prior distribution in most cases.
-Combining the two, the rotation period $P$ has no stars directly corresponding to the effective prior on period, and globally follows a trend with increasing age.
-The three outliers with fast rotation at late ages (KICs 6603624, 8760414 and 8938364) are discussed in more detail in below.
-
-The rotation rates as presented in this work are a product of our Bayesian sampling of both projected splitting and angle of inclination.
-As seen in the Figure there are instances where $i$ or $\nu_{\rm s}\sin(i)$ closely resemble the prior (and are therefore prior-dominated).
-There are no cases of this when looking at the resulting period measurements, as they will have been informed by at least one strongly data-driven parameter (commonly $\nu_{\rm s}\sin(i)$).
-From this, we concluded that our ensemble of asteroseismic rotation is not strongly dominated by the priors imposed on projected splitting and inclination in our Bayesian analysis.
-
-\subsection{Comparisons to previous studies}\label{ssec:litcomp}
-In order to validate our results, we compared our rotational parameters to those obtained in the literature, as well as those resulting from the work presented in LEGACY and `Kages', which were unreported and received through private communication by the authors of the catalogue papers.
-
-Comparisons with LEGACY and `Kages' are shown in \textbf{Extended Data} Figure \ref{fig:legacykages} for projected splitting, inclination angle, and rotation period.
-In all three cases we show the fractional difference between the values obtained in this work and those from LEGACY and `Kages'.
-On the right of the Figure, we show the distribution of the fractional differences for the three parameters.
-The projected splitting is in good agreement with both studies, however LEGACY finds slightly lower $\nu_{\rm s}\sin(i)$ for the faster rotators, deviating from our work by over $1\sigma$.
-Neither LEGACY nor `Kages' used a spatially isotropic prior for the inclination angle in their analyses, instead opting for a uniform prior.
-As posterior estimates of inclination angle are only loosely data-driven, the introduction of an isotropic prior should result in our analysis reporting globally higher inclination angles.
-This effect is seen in the comparisons of both inclination angles and rotation rates for the LEGACY stars, where we find overall lower rotation rates compared to LEGACY for stars at very similar $\nu_{\rm s}\sin(i)$.
-
-A number of stars are excluded from \textbf{Extended Data} Figure \ref{fig:legacykages} and compared individually as extreme outliers: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have fast rotation rates ($<5\, \rm days$) in `Kages', but are found to have a broader spread of rotation rates in this work.
-At similar values for $\nu_{\rm s}\sin(i)$, `Kages' found much lower inclination angles with highly asymmetrical uncertainties.
-Based on a comparison between the summary statistics of these stars, we concluded that the results found in this work have better marginalised over inclination angle, improving our measure of rotation.
-
-Conversely, KICs 6603624, 8760414 and 8938364 have extremely slow rotation periods in LEGACY, but extremely \textit{fast} ($<3\, \rm {days}$) in this work.
-KICs 8760414 and 8938364 are excluded from the gyrochronology analysis below based on checks for $\hat{R}$ and the number of effective samples.
-Both stars have ages greater than $10\, \rm Gyr$, making their fast rotation rates highly unlikely under any model of rotational evolution.
-The posterior estimate of $P$ for KIC 6603624 is well-defined in our analysis, but with an age of $7.8\, \rm Gyr$, its measured rotation of $1.2\, \rm days$ is also highly unlikely under any model of rotational evolution.
-The LEGACY estimate of rotation is similarly extreme at $378\, \rm days$.
-These three stars have the lowest inclination angles in our sample ($< 10^\circ$), at which point the power in the split components of the seismic modes is so low that it becomes difficult to probe the measure of splitting.
-The split components for these stars will have a height roughly 3\% of the central mode.
-For comparison, for the next lowest inclined star at $17^\circ$, this rises to $10\%$.
-In cases such as these with lower signal-to-noise, spurious peaks may be interpreted as split components.\\
-
-We also compared our asteroseismic estimates of stellar rotation with similar studies in the literature, shown in \textbf{Extended Data} Figure \ref{fig:literaturecomp}.
-These included: a study of the binary solar analogues 16 Cyg A \& B \cite{m_davies+2015}, ; a study of surface and seismic rotation which our catalogue shares 5 stars with \cite{m_nielsen+2015}, ; and an asteroseismic study of differential rotation with which our catalogue shares 40 targets \cite{m_benomar+2018}.
-For the latter, we used their reported splitting value $a_1$, which is equivalent to $\nu_{\rm s}$.
-
-Overall,  \textbf{Extended Data} Figure \ref{fig:literaturecomp} shows no strong disagreements between our asteroseismic measurements for stellar rotation and those from the literature.
-The scatter of the fractional differences lies cleanly around the zero line, with a mean and spread of $0.0_{-15.6}^{+16.4}\, \%$.
-The increase in uncertainty with period is due to more slowly rotating stars being more difficult to constrain using asteroseismology.
-
-It is of note that 16 Cyg A was found to be rotating slightly faster in our analysis compared to the literature \cite{m_davies+2015} (deviating within $2\sigma$), despite the fit being performed on the same data.
-We found an inclination angle that is slightly lower for 16 Cyg A but at a similar projected splitting, which would explain finding a lower value of rotation.
-
-There are three outliers at low period in  \textbf{Extended Data} Figure \ref{fig:literaturecomp}: KICs 6603624, 8760414 and 8938364.
-These are the same targets found to be outliers in a comparison to the LEGACY and `Kages' measurements (see above), with anomalously fast rotation rates and low inclination angles.
-As these stars represent the lowest inclination angles in our sample, and were found to disagree with two independent studies, we opted to exclude them from the gyrochronology analysis, and to flag the rotation measurements for these three stars presented in this work.
-
-\subsection{\rtwo{Seismic vs Surface rotation}}
-As described in the main body of the paper, we compared a subsample of our asteroesismic rotation rates to surface rotation rates from spot rotation, where available.
-Both the surface ($P_{\rm surf}$) and seismic ($P_{\rm seis}$) rotation rates have associated uncertainties.
-Instead of fitting the slope between these two values directly, we instead fit the distribution
-
-\begin{equation}
-	p(\frac{P_{\rm seis}}{P_{\rm surf}}\, |\, m) = \mathcal{N}(m, \sigma_\frac{P_{\rm seis}}{P_{\rm surf}})\, ,
-\end{equation}
-
-\noindent where $m$ is the slope, and $\sigma_\frac{P_{\rm seis}}{P_{\rm surf}}$ is the uncertainty corresponding to $\frac{P_{\rm seis}}{P_{\rm surf}}$, following the propagation of the errors on both values.
-We used the larger of the asymmetrical uncertainties on asteroseismic rotation from our analysis.
-The model was fit using \texttt{PyMC3} for 2000 iterations each on 4 chains.
-Five stars for which both surface and seismic rotation were available, but which had a surface rotation above the 1.8:1 line, were excluded from this analysis.
-This was to exclude likely multiples of the true rotation rate skewing the fit, as measurements of double the true rotation may occur in spot rotation measurements.
-
-Our fit found a value of $m = 0.96 \pm 0.03$ using 48 stars.
-We reran this analysis using the 21 stars in this sample for which the median of their posterior probability for $Q_{\rm WMB}$ was greater than $0.5$ in our stellar model analysis, preferring the WMB model.
-A fit to these stars alone found a value of $m = 0.96 \pm 0.04$.
-
-\subsection{Seismic vs spectroscopic rotation}
-A distinct difference between rotation rates obtained through different techniques may hold information about differential rotation (both latitudinal and radial) of near-surface layers, such as those we observe in the Sun \cite{m_beck2000}.
-A previous comparison of spectroscopic and seismic rotation rates, performed on a sample of 22 stars, found no significant radial differential rotation \cite{m_benomar+2018}.
-In this work they not only considered rotation rates from spots, but also spectroscopic measures of the projected surface rotation $\textrm{v}\sin(i)$, which they found to be more reliable.
-
-With our expanded sample of asteroseismic rotation we can perform a similar analysis, to both validate our sample and probe radial differential rotation.
-\textbf{Extended Data} Figure \ref{fig:vsinilit} shows a comparison between spectroscopic $\textrm{v}\sin(i)$ measurements as listed in LEGACY and `Kages' (left) and Benomar et al.
-(2015) \cite{m_benomar+2015} (right).
-In these cases the asteroseismic $\textrm{v}\sin(i)$ has been calculated using our measure of asteroseismic $\nu_s\sin(i)$ and the known asteroseismic radii.
-Three stars (KICs 6603624, 8760414 and 8938364) have been excluded from this figure due to strong disagreements of measured rotation rates with the literature (see above).
-
-For the LEGACY and `Kages' sample, we find no strong deviation from the 1:1 line except at very low velocities, which is likely due to biases inherent to spectroscopic line broadening measurements \cite{m_doyle+2014, m_tayar+2015}.
-For the Benomar et al.
-(2015) sample stars lie a lot closer to the 1:1 line.
-
-Overall, there appears to be a global offset where spectroscopic measurements of projected rotation appear faster than asteroseismic measures.
-Based on the LEGACY and `Kages' $v\sin(i)$ values, this offset is roughly $18\%$ (i.e.
-spectroscopic projected rotation rates are faster than asteroseismic rates).
-This offset is much smaller ($\sim5\%$) for the \cite{m_benomar+2015} sample, albeit for far fewer stars.
-These offsets are within the typical disagreement between spectroscopic methods, based on comparisons of projected rotation measurements for red giant stars \cite[see Figure 2]{m_tayar+2015}, especially at $< 5\, \rm{km\,s^{-1}}$.
-
-It is worth addressing the impact this comparison would have on our conclusions for gyrochronology, were we to take the spectroscopic rotation rates as if they were the truth, even at velocities of $< 5\, \rm{km\,s^{-1}}$.
-For the majority of cases, the seismic velocities are slower than the spectroscopic velocities, which would bias our ensemble towards favouring a standard evolution over a weakened magnetic braking scenario (as stars would overall appear to be rotating slower at late ages).
-Based on the comparison to spot rotation presented in the main body of this paper, and given known issues comparing seismic and spectroscopic rotation at low velocities, we concluded that the divergence seen in  \textbf{Extended Data} Figure \ref{fig:vsinilit} does not undermine our results.
-
-\subsection{Asteroseismic detection biases}
-
-Stars that are rotating very slowly will show small rotational splittings, which may be indistinguishable from a non-rotating case, wheras stars that are spinning very fast may find that their splitting is so wide that they cross over with split modes at different radial orders ($n$).
-Asteroseismic selection techniques may also introduce additional biases on a population level.
-We consider the limitations this places on our asteroseismic method.
-
-\begin{itemize}
-	\item \textit{Fast rotating stars:} In prinicple, a star could rotate fast enough that the highest-frequency peak in a split dipole ($\ell = 2$) mode would overlap with the radial ($\ell = 0$) mode.
-This would occur if $2\nu_{\rm s} > \delta\nu_{02}$, the small separation.
-For the star in our sample with the smallest $\delta\nu_{02}$ (so the highest risk of this happening), this would occur at a rotation of 8.8 days or faster.
-For the star with the largest $\delta\nu_{02}$, this limit was roughly 2 days.
-
-	In practice, the model still properly fits a spectrum where this kind of mode-overlapping occurs, as the $\ell = 0$ modes don't split, meaning that there are no degenerate solutions in this regime, and further constraints can be obtained from the other modes and split components in the spectrum.
-A more serious issue may be when the $\ell = 1$ mode at lower frequencies overlaps with the $\ell = 2$ mode as well, which would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.
-
-	\item \textit{Slow rotating stars:} Except for the most rapidly rotating cases, asteroseismic mode splitting is detected by a change in the distribution of the power of mode frequencies as the split components begin to separate from the central mode.
-If there is to be hard limit at which this measurement is not possible, it should be in the case that $\nu_{\rm s} < 2/T$, where $T$ is the observation time, and $1/T$ is the frequency bin width.
-For the star in our sample with the shortest observing time, this limit would be $\sim 89$ days, which quickly rises for longer observing baselines.
-While this constitutes a hard limit, slower rotation rates will become harder and harder to constrain as the rate of splitting becomes smaller.
-A benefit of the Bayesian approach used in this paper is that it should accurately reflect the increased uncertainty associated with the small rotational splitting.
-\end{itemize}
-
-While these two limits cause concern when studying the most extreme rotators, the results presented in this work are driven by stars with rotation rates in the regime of 5 to 30 days.
-Above, we demonstrated that results on period for these stars were data-driven (i.e.
-do not reflect the priors), indicating that the splitting is well resolved in this regime, and so we do not expect these limits to bias our conclusions.
-
-Finally, we also consider bias in asteroseismic detections.
-The probability of an asteroseismic detection with \kepler scales with temperature and radius (i.e.
-scales inversely with \logg, and therefore main sequence age), \rtwo{and detections are unlikely below roughly $5200\, K$} \cite{m_chaplin+2011, m_schofield+2019}.
-\rtwo{Very young ($\lesssim 2\, \rm{Gyr}$), very magnetically active stars may also suppress their oscillation modes.
-\cite{m_mathur+2019}.
-Though these two effects impose a bias on asteroseismic populations, they do so outside the parameter range on which our comparison takes place.
-As it is older stars, undergoing magnetic braking, that are required to drive the distinction between stellar models, we conclude that our seismic sample can be assumed to be complete for the purposes of this work.}
-
-\section{Verifying consequences for gyrochronology}
-\subsection{Limits of our stellar models}\label{ssec:limits}
-The rotational stellar models used in this work \cite{m_vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$.
-Our sample of 91 stars contained 4 stars with metallicities below $-0.4\, \rm{dex}$, which are shown as shaded symbols in Figure \ref{fig:fullsample}.
-Of these, 3 were included in our final sample of 73 stars used to evaluate our stellar models: KICs 7970740, 8684723 and KIC 9965715.
-All three are classed as MS stars, with metallicities of $-0.54 \pm 0.10$, $-0.42 \pm 0.10$ and $-0.44 \pm 0.18\, \rm {dex}$ respectively, placing them within $3\sigma$ of the metallicity limits of our stellar models.
-KICs 8684723 and 9965715 strongly agree with the WMB model, whereas KIC 7970740 weakly prefers the standard model.
-Excluding these stars was not found to significantly alter the joint posterior distribution shown in Figure \ref{fig:gyroresults}.
-
-A recent study \cite{m_amard+matt2020} compared different rotational evolution models \cite[of which we use the former in this work]{m_vansaders+pinsonneault2013,m_matt+2015} while studying the effect metallicity has on rotation.
-They found that metal-rich stars spin down significantly more effectively than metal poor stars.
-The population of 73 stars used in our stellar model comparisons is roughly centered on a $\rm{[Fe/H]}$ of 0 $\rm dex$, with a spread of $~0.16\, \rm dex$, with no stars significantly above or below $\pm 0.4\, \rm dex$ (as discussed above).
-While differences in stellar rotational evolution as a function of metallicity in this region are still somewhat pronounced, they are much less so than for more metal-rich or poor stars \cite[see Figure 2]{m_amard+matt2020}.
-However, for stars with $\feh < 0$, the alternative model prescription \cite{m_matt+2015} sees stars spin down more slowly than the models used in this work (i.e.
-they will rotate faster at later ages).
-This work only explores the presence of weakened magnetic braking for a single braking law, and a comparison to alternative braking model will be explored in a future paper.
-
-When constructing KDEs from our stellar model samples (see Section \ref{s:gyro}), we selected fixed resolutions (or band-widths) for the KDEs.
-In mass, the band-width of $0.02\, M_\odot$, was larger than the uncertainties of 24 of 73 stars used to construct our joint posterior.
-For the stars with the smallest uncertainties, this significantly limits the size of the KDE being evaluated (as subsections of the full stellar models are used to evaluate individual stars, for computational efficiency).
-In order to confirm that these stars do not significantly affect the ensemble's preference towards the WMB model, we recalculated the joint posterior distribution for $Q_{\rm WMB}$, excluding stars with an uncertainty on mass smaller than the KDE band-width.
-While the 24 stars with small uncertainties do favour the WMB model, they do so very weakly, whereas the remaining 49 stars with larger uncertainties strongly favour the WMB model.
-Their removal from the total joint posterior probability does not significantly alter it from the distribution shown in Figure \ref{fig:gyroresults}.
-
-\subsection{Systematic uncertainties from asteroseismology}
-In our model analysis, we used asteroseismic mass and age obtained using \texttt{BASTA}, as reported in LEGACY and Kages.
-Asteroseismic properties obtained through stellar models can be subject to systematic errors arising from differences in input physics and choice of stellar models not included in the reported statistical uncertainties.
-A quantification of these different systematic effects can be found in the `Kages' catalogue paper \cite{m_silvaaguirre+2015}.
-Combining their reported median systematic uncertainties due to input physics results in median uncertainties of $20\%$ (up from $14\%)$ on age and $5\%$ (up from $3\%$) on mass for the `Kages' sample.
-For LEGACY, the median uncertainties are $18\%$ (up from $10\%)$ and $5.6\%$ (up from $4\%$) for age and mass respectively.
-
-We re-ran our model analysis after inflating uncertainties on mass and age.
-We increased uncertainties by the fractional difference between the \texttt{BASTA} statistical uncertainties and the median full statistical and systematic uncertainties described above.
-For example, a LEGACY star with a mass of $2.0 \pm 0.5\, M_\odot$ would have its uncertainty inflated by $1.6\%$ of its mass, to $0.53\, M_\odot$.
-
-To further test the limits of this analysis, we also reran our mixture model fit, this time only shifting the asteroseismic ages younger by the systematic uncertainty, and retaining the statistical uncertainty (i.e.
-the ages of LEGACY and `Kages' stars were reduced by $8\%$ and $6\%$ respectively).
-In this scenario where all asteroseismic ages are overestimated, `true' fast rotators at young ages would have been mistaken for fast rotators at old ages, suggesting the presence of weakened magnetic braking where none existed.
-
-The results of these tests are discussed further in the main body of the paper.
-
-\subsection{Binaries and Planet Hosts}
-For stars to be good probes of existing gyrochronology relations, their rotational evolution must occur in isolation.
-If a star interacts with a close binary companion (through tides, or a merger) the natural angular momentum loss can be disturbed, causing gyrochronology to mispredict ages \cite{m_leiner+2019, m_fleming+2019}.
-Between LEGACY and Kages, we have 8 known binaries.
-
-First, KIC 8379927, KIC 7510397, KIC 10454113 and KIC 9025370 are spectroscopic binaries.
-This does not affect the asteroseismic analysis, but may affect their rotational evolution.
-Of these, KICs 8379927, 7510397 and 9025370 were included in the gyrochronology analysis.
-None of them preferred one model strongly over the other, with all three finding flat posteriors for $Q_{\rm WMB}$.
-
-Second, the binary pairs of KIC 9139151 \& 9139163 and 16 Cyg A \& B are individually observed binary components with wide orbital separations, so we do not expect their binarity to have affected their rotational evolution \cite{m_halbwachs1986, m_white+2013}.
-
-While we chose not to account for star-planet tidal interactions in this work, we note that this may disturb the natural stellar rotational evolution when tidal forces are at play \cite{m_maxted+2015,m_gallet+delorme2019, m_benbakoura+2019}, although this has been disputed by observations of asteroseismic planet hosts \cite{m_ceillier+2016}.\\
+The array of 100 bins for all stars were multiplied, resulting in an approximation of the joint posterior probability function for $Q_{\rm WMB}$ given all stars in the ensemble.\\
 
@@
 
-This work made use of publicly available data described in the text, and reiterated here.
-\kepler power spectral density  were obtained from the \href{http://kasoc.phys.au.dk/}{KASOC} webpages for the majority of stars, and from the \href{https://archive.
+This work made use of publicly available data.
+\kepler power spectral densities were obtained from the \href{http://kasoc.phys.au.dk/}{KASOC} webpages for the majority of stars, and from the \href{https://archive.
 		stsci.edu/prepds/kepseismic/}{MAST} for 16 Cyg A and B.
@@
 (2016) and Lund et al.
-(2017) \cite{m_silvaaguirre+2015, m_silvaaguirre+2017,m_davies+2016, m_lund+2017}.
+(2017) \cite{silvaaguirre+2015, m_silvaaguirre+2017,m_davies+2016, m_lund+2017}.
 Parameter distributions of the \kepler field used to alter our stellar population models were taken from Berger et al.
-(2020) \cite{m_berger+2020}.\\
+(2020) \cite{berger+2020}.\\
 
@@
 \input{bblmethods.tex}
+%\bibliographystyle{naturemag}
+%\bibliography{library.bib} % if your bibtex file is called example.bib
 

### 2021-02-15 paper/natastron/Publication/paper.tex
tidying up for publication

@@
 
-\noindent Oliver J. Hall$^{1,2,3,}$\footnote[1]{Email: \texttt{oliver.hall@esa.int} | Twitter: \texttt{@asteronomer} | GitHub: \texttt{@ojhall94}},
+\noindent Oliver J. Hall$^{1,2,3,*}$,
 	Guy R. Davies$^{2,3}$, 
@@
 	\noindent $^{8}$ Hubble Fellow
+
+	\noindent $^{*}$ Email: \texttt{oliver.hall@esa.int} | Twitter: \texttt{@asteronomer} | GitHub: \texttt{@ojhall94}
 
@@
 	\includegraphics[width=0.6\textwidth]{data.pdf}
-	\caption{Our sample of 95 stars from the `Kages' and LEGACY catalogues coloured by asteroseismic age  \cite{silvaaguirre+2015, silvaaguirre+2017}.
+	\caption{\textbf{Our sample of 95 stars from the `Kages' and LEGACY catalogues.} Data are coloured by asteroseismic age  \cite{silvaaguirre+2015, silvaaguirre+2017}.
 The dashed lines indicate our classification boundaries: main sequence (circles, $\teff < 6250\, K$, $\logg < 4\, \rm{dex}$), potential sub-giants (squares, $\teff < 6250\, K$, $\logg > 4\, \rm{dex}$), and `hot' stars (triangles, $\teff > 6250\, K$).
@@
 For stars viewed near pole-on the split modes of oscillation have extremely low power, making them hard to detect reliably \cite{lund+2014}.
-We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we considered our asteroseismic rotation measurements to be robust (for a full justification, see \textbf{Methods}).\\
+We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we considered our asteroseismic rotation measurements to be robust (for a full justification, see \textbf{Supplementary Information}).\\
 
@@
 This is not the case for asteroseismic rotation, and so some stars may appear at the 2:1 and 1:2 lines in the figure.
-We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid likely multiples of the true rotation rate acting as outliers (transparent in the Figure, see \textbf{Methods}å for details).
+We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid likely multiples of the true rotation rate acting as outliers (transparent in the Figure, see \textbf{Methods} for details).
 Our fit found a value of $m = 0.96 \pm 0.03$, showing a close agreement ($<2\sigma$) between asteroseismic and surface rotation rates on a population level.
@@
 	\includegraphics[width=0.6\textwidth]{Images/surf-seis-comparison_update.pdf}
-	\caption{Comparisons between asteroseismic and photometric measures of stellar rotation, for 48 stars.
-Literature values were taken Garcia et al.
+	\caption{\textbf{Comparisons between asteroseismic and photometric measures of stellar rotation, for 48 stars.} Literature values were taken Garcia et al.
 (2014) \cite{garcia+2014} and Nielsen et al.
@@
 	\includegraphics[width=.9\textwidth]{fullsample.pdf}
-	\caption{Stars for which rotation was measured in this work, plotted over TRILEGAL \cite{girardi+2012} stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution.
+	\caption{\textbf{Stars for which rotation was measured in this work, plotted over stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution.} The model populations were generated using TRILEGAL (see text) \cite{girardi+2012}.
 \rtwo{The z-axis colour scale indicates the density of stars in $P$-\teff space for the models.} The 21 stars that were excluded from the gyrochronology analysis are marked with crosses and without uncertainties (see text).
@@
 	\includegraphics[width=\textwidth]{modelresults.pdf}
-	\caption{Posterior estimates of the mixture model parameter $Q_{\rm WMB}$, broken down by stellar classification.
-A value of $Q_{\rm WMB}$ close to 1 indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 0 indicates that the data are more consistent with a standard rotational evolution scenario.
+	\caption{\textbf{Posterior estimates of the mixture model parameter $Q_{\rm WMB}$, broken down by stellar classification.} A value of $Q_{\rm WMB}$ close to 1 indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 0 indicates that the data are more consistent with a standard rotational evolution scenario.
 \textit{Left:} \rtwo{the joint posterior probabilities} for 73 stars, or subsets thereof for different stellar classifications.
@@
 \textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful \rtwo{conclusion about} weakened magnetic braking, we ensured that the same results were obtained when using different subsets of the ensemble, and when exploring potential biases.
-We found that the joint posterior distribution did not change significantly when excluding stars with metallicities that fell only slightly outside the model range, or those with extremely small uncertainties on asteroseismic mass (see \textbf{Methods}).
+We found that the joint posterior distribution did not change significantly when excluding stars with metallicities that fell only slightly outside the model range, or those with extremely small uncertainties on asteroseismic mass.
 Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $Q_{\rm WMB}$.
@@
 From this, we can infer that our conclusions are robust against potential issues in seismic analyses.
-For a full discussion of these tests and other biases, see \textbf{Methods}.\\
+For a full discussion of these tests and other biases, see \textbf{Supplementary Information}.\\
 

### 2021-02-15 paper/natastron/Publication/si.tex
tidying up for publication

@@
 
+\subsection{Fitting procedure}
+Using our prior information and model described above, we fit Equation \ref{eq:model} to our data $\mathcal{P}$, using the likelihood function described in Section \ref{sec:like}.
+
+In order to speed up the fitting process, we only applied our model to the region of the power spectrum that contains visible modes of oscillation.
+We created this subset by removing all frequencies outside a range $0.25 \times \Delta\nu$ below and above the minimum and maximum mode frequencies reported in LEGACY and Kages.
+This region overlaps minimally with the data used to fit for our prior information of the convective background (see Section \ref{sec:background}), so that both model fits are independent.
+
+To improve computational efficiency, we reduced the number of oscillation modes being fit in five targets.
+For 16 Cyg A \& B, KIC 7970740 and KIC 8478994, we excluded any modes with a Bayes Factor ($\ln(K)$) of less than 6, as reported in LEGACY \cite{davies+2016,lund+2017,kass+raftery1995}.
+For KIC 8478994, which is reported without a value for $\ln(K)$ in Kages, we only included modes of an overtone number that contained a detection for all of $\ell = (0, 1, 2)$, retaining 5 sets of higher signal-to-noise overtones.
+We do not expect this reduced scope to bias our results, although they may reduce the precision on our measured rotation rates.
+
+We fit our model to our power spectrum data with \texttt{PyMC3}, using 2500 iterations each on 4 chains.
+An example of our model fit to an asteroseismic power spectrum of 16 Cyg A is shown in Supplementary Figure \ref{fig:modelfit}.
+
  \begin{figure*}
@@
 
-\subsection{Fitting procedure}
-Using our prior information and model described above, we fit Equation \ref{eq:model} to our data $\mathcal{P}$, using the likelihood function described in Section \ref{sec:like}.
+\section{Verifying asteroseismic results}
+\subsection{Priors on rotational parameters}
+In our Bayesian analysis, we have placed weakly informative priors on our sampled rotational parameters, $\nu_{\rm s}\sin(i)$ and $\cos(i)$.
+The prior is especially important for the angle of inclination, which is hardest to infer from the data.
+We are able to validate the robustness of our asteroseismic results by confirming that their posterior distributions are data-dominated, and not prior-dominated.
+We can do so by comparing the $68\%$ credible regions of the posterior estimates of $\nu_{\rm s}\sin(i)$ and $i$ against the $68\%$ credible regions of their priors.
 
-In order to speed up the fitting process, we only applied our model to the region of the power spectrum that contains visible modes of oscillation.
-We created this subset by removing all frequencies outside a range $0.25 \times \Delta\nu$ below and above the minimum and maximum mode frequencies reported in LEGACY and Kages.
-This region overlaps minimally with the data used to fit for our prior information of the convective background (see Section \ref{sec:background}), so that both model fits are independent.
+A comparison between prior and posterior is shown for 94 stars in $\nu_{\rm s}\sin(i)$, $i$ and $P$ in \textbf{Extended Data} Figure \ref{fig:priors}, arranged by age.
+In the Figure, results with means (symbols) and $68\%$ credible regions (error bars) that are close to those same values for the prior distribution (where the horizontal line is the mean, and the shaded area is the credible region) can be interpreted as prior-dominated (i.e.
+poorly informed by the data).
+Cases where the means differ or the credible regions are smaller than the prior distribution are data-dominated.
+The projected splitting, $\nu_{\rm s}\sin(i)$, is overall well constrained, with only one star being prior dominated.
+This is expected, as the projected splitting is what we observe on the star before decoupling inclination and rotation.
+The angle of inclination $i$, sampled as $\cos(i)$, more closely follows the prior distribution in most cases.
+Combining the two, the rotation period $P$ has no stars directly corresponding to the effective prior on period, and globally follows a trend with increasing age.
+The three outliers with fast rotation at late ages (KICs 6603624, 8760414 and 8938364) are discussed in more detail in below.
 
-To improve computational efficiency, we reduced the number of oscillation modes being fit in five targets.
-For 16 Cyg A \& B, KIC 7970740 and KIC 8478994, we excluded any modes with a Bayes Factor ($\ln(K)$) of less than 6, as reported in LEGACY \cite{davies+2016,lund+2017,kass+raftery1995}.
-For KIC 8478994, which is reported without a value for $\ln(K)$ in Kages, we only included modes of an overtone number that contained a detection for all of $\ell = (0, 1, 2)$, retaining 5 sets of higher signal-to-noise overtones.
-We do not expect this reduced scope to bias our results, although they may reduce the precision on our measured rotation rates.
+The rotation rates as presented in this work are a product of our Bayesian sampling of both projected splitting and angle of inclination.
+As seen in the Figure there are instances where $i$ or $\nu_{\rm s}\sin(i)$ closely resemble the prior (and are therefore prior-dominated).
+There are no cases of this when looking at the resulting period measurements, as they will have been informed by at least one strongly data-driven parameter (commonly $\nu_{\rm s}\sin(i)$).
+From this, we concluded that our ensemble of asteroseismic rotation is not strongly dominated by the priors imposed on projected splitting and inclination in our Bayesian analysis.
 
-We fit our model to our power spectrum data with \texttt{PyMC3}, using 2500 iterations each on 4 chains.
-An example of our model fit to an asteroseismic power spectrum of 16 Cyg A is shown in Supplementary Figure \ref{fig:modelfit}.
+\subsection{Comparisons to previous studies}\label{ssec:litcomp}
+In order to validate our results, we compared our rotational parameters to those obtained in the literature, as well as those resulting from the work presented in LEGACY and `Kages', which were unreported and received through private communication by the authors of the catalogue papers.
+
+Comparisons with LEGACY and `Kages' are shown in \textbf{Extended Data} Figure \ref{fig:legacykages} for projected splitting, inclination angle, and rotation period.
+In all three cases we show the fractional difference between the values obtained in this work and those from LEGACY and `Kages'.
+On the right of the Figure, we show the distribution of the fractional differences for the three parameters.
+The projected splitting is in good agreement with both studies, however LEGACY finds slightly lower $\nu_{\rm s}\sin(i)$ for the faster rotators, deviating from our work by over $1\sigma$.
+Neither LEGACY nor `Kages' used a spatially isotropic prior for the inclination angle in their analyses, instead opting for a uniform prior.
+As posterior estimates of inclination angle are only loosely data-driven, the introduction of an isotropic prior should result in our analysis reporting globally higher inclination angles.
+This effect is seen in the comparisons of both inclination angles and rotation rates for the LEGACY stars, where we find overall lower rotation rates compared to LEGACY for stars at very similar $\nu_{\rm s}\sin(i)$.
+
+A number of stars are excluded from \textbf{Extended Data} Figure \ref{fig:legacykages} and compared individually as extreme outliers: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have fast rotation rates ($<5\, \rm days$) in `Kages', but are found to have a broader spread of rotation rates in this work.
+At similar values for $\nu_{\rm s}\sin(i)$, `Kages' found much lower inclination angles with highly asymmetrical uncertainties.
+Based on a comparison between the summary statistics of these stars, we concluded that the results found in this work have better marginalised over inclination angle, improving our measure of rotation.
+
+Conversely, KICs 6603624, 8760414 and 8938364 have extremely slow rotation periods in LEGACY, but extremely \textit{fast} ($<3\, \rm {days}$) in this work.
+KICs 8760414 and 8938364 are excluded from the gyrochronology analysis below based on checks for $\hat{R}$ and the number of effective samples.
+Both stars have ages greater than $10\, \rm Gyr$, making their fast rotation rates highly unlikely under any model of rotational evolution.
+The posterior estimate of $P$ for KIC 6603624 is well-defined in our analysis, but with an age of $7.8\, \rm Gyr$, its measured rotation of $1.2\, \rm days$ is also highly unlikely under any model of rotational evolution.
+The LEGACY estimate of rotation is similarly extreme at $378\, \rm days$.
+These three stars have the lowest inclination angles in our sample ($< 10^\circ$), at which point the power in the split components of the seismic modes is so low that it becomes difficult to probe the measure of splitting.
+The split components for these stars will have a height roughly 3\% of the central mode.
+For comparison, for the next lowest inclined star at $17^\circ$, this rises to $10\%$.
+In cases such as these with lower signal-to-noise, spurious peaks may be interpreted as split components.\\
+
+We also compared our asteroseismic estimates of stellar rotation with similar studies in the literature, shown in \textbf{Extended Data} Figure \ref{fig:literaturecomp}.
+These included: a study of the binary solar analogues 16 Cyg A \& B \cite{m_davies+2015}, ; a study of surface and seismic rotation which our catalogue shares 5 stars with \cite{m_nielsen+2015}, ; and an asteroseismic study of differential rotation with which our catalogue shares 40 targets \cite{m_benomar+2018}.
+For the latter, we used their reported splitting value $a_1$, which is equivalent to $\nu_{\rm s}$.
+
+Overall,  \textbf{Extended Data} Figure \ref{fig:literaturecomp} shows no strong disagreements between our asteroseismic measurements for stellar rotation and those from the literature.
+The scatter of the fractional differences lies cleanly around the zero line, with a mean and spread of $0.0_{-15.6}^{+16.4}\, \%$.
+The increase in uncertainty with period is due to more slowly rotating stars being more difficult to constrain using asteroseismology.
+
+It is of note that 16 Cyg A was found to be rotating slightly faster in our analysis compared to the literature \cite{m_davies+2015} (deviating within $2\sigma$), despite the fit being performed on the same data.
+We found an inclination angle that is slightly lower for 16 Cyg A but at a similar projected splitting, which would explain finding a lower value of rotation.
+
+There are three outliers at low period in  \textbf{Extended Data} Figure \ref{fig:literaturecomp}: KICs 6603624, 8760414 and 8938364.
+These are the same targets found to be outliers in a comparison to the LEGACY and `Kages' measurements (see above), with anomalously fast rotation rates and low inclination angles.
+As these stars represent the lowest inclination angles in our sample, and were found to disagree with two independent studies, we opted to exclude them from the gyrochronology analysis, and to flag the rotation measurements for these three stars presented in this work.
+
+\subsection{Seismic vs spectroscopic rotation}
+A distinct difference between rotation rates obtained through different techniques may hold information about differential rotation (both latitudinal and radial) of near-surface layers, such as those we observe in the Sun \cite{m_beck2000}.
+A previous comparison of spectroscopic and seismic rotation rates, performed on a sample of 22 stars, found no significant radial differential rotation \cite{m_benomar+2018}.
+In this work they not only considered rotation rates from spots, but also spectroscopic measures of the projected surface rotation $\textrm{v}\sin(i)$, which they found to be more reliable.
+
+With our expanded sample of asteroseismic rotation we can perform a similar analysis, to both validate our sample and probe radial differential rotation.
+\textbf{Extended Data} Figure \ref{fig:vsinilit} shows a comparison between spectroscopic $\textrm{v}\sin(i)$ measurements as listed in LEGACY and `Kages' (left) and Benomar et al.
+(2015) \cite{m_benomar+2015} (right).
+In these cases the asteroseismic $\textrm{v}\sin(i)$ has been calculated using our measure of asteroseismic $\nu_s\sin(i)$ and the known asteroseismic radii.
+Three stars (KICs 6603624, 8760414 and 8938364) have been excluded from this figure due to strong disagreements of measured rotation rates with the literature (see above).
+
+For the LEGACY and `Kages' sample, we find no strong deviation from the 1:1 line except at very low velocities, which is likely due to biases inherent to spectroscopic line broadening measurements \cite{m_doyle+2014, m_tayar+2015}.
+For the Benomar et al.
+(2015) sample stars lie a lot closer to the 1:1 line.
+
+Overall, there appears to be a global offset where spectroscopic measurements of projected rotation appear faster than asteroseismic measures.
+Based on the LEGACY and `Kages' $v\sin(i)$ values, this offset is roughly $18\%$ (i.e.
+spectroscopic projected rotation rates are faster than asteroseismic rates).
+This offset is much smaller ($\sim5\%$) for the \cite{m_benomar+2015} sample, albeit for far fewer stars.
+These offsets are within the typical disagreement between spectroscopic methods, based on comparisons of projected rotation measurements for red giant stars \cite[see Figure 2]{m_tayar+2015}, especially at $< 5\, \rm{km\,s^{-1}}$.
+
+It is worth addressing the impact this comparison would have on our conclusions for gyrochronology, were we to take the spectroscopic rotation rates as if they were the truth, even at velocities of $< 5\, \rm{km\,s^{-1}}$.
+For the majority of cases, the seismic velocities are slower than the spectroscopic velocities, which would bias our ensemble towards favouring a standard evolution over a weakened magnetic braking scenario (as stars would overall appear to be rotating slower at late ages).
+Based on the comparison to spot rotation presented in the main body of this paper, and given known issues comparing seismic and spectroscopic rotation at low velocities, we concluded that the divergence seen in  \textbf{Extended Data} Figure \ref{fig:vsinilit} does not undermine our results.
+
+\subsection{Asteroseismic detection biases}
+
+Stars that are rotating very slowly will show small rotational splittings, which may be indistinguishable from a non-rotating case, wheras stars that are spinning very fast may find that their splitting is so wide that they cross over with split modes at different radial orders ($n$).
+Asteroseismic selection techniques may also introduce additional biases on a population level.
+We consider the limitations this places on our asteroseismic method.
+
+\begin{itemize}
+	\item \textit{Fast rotating stars:} In prinicple, a star could rotate fast enough that the highest-frequency peak in a split dipole ($\ell = 2$) mode would overlap with the radial ($\ell = 0$) mode.
+This would occur if $2\nu_{\rm s} > \delta\nu_{02}$, the small separation.
+For the star in our sample with the smallest $\delta\nu_{02}$ (so the highest risk of this happening), this would occur at a rotation of 8.8 days or faster.
+For the star with the largest $\delta\nu_{02}$, this limit was roughly 2 days.
+
+	In practice, the model still properly fits a spectrum where this kind of mode-overlapping occurs, as the $\ell = 0$ modes don't split, meaning that there are no degenerate solutions in this regime, and further constraints can be obtained from the other modes and split components in the spectrum.
+A more serious issue may be when the $\ell = 1$ mode at lower frequencies overlaps with the $\ell = 2$ mode as well, which would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.
+
+	\item \textit{Slow rotating stars:} Except for the most rapidly rotating cases, asteroseismic mode splitting is detected by a change in the distribution of the power of mode frequencies as the split components begin to separate from the central mode.
+If there is to be hard limit at which this measurement is not possible, it should be in the case that $\nu_{\rm s} < 2/T$, where $T$ is the observation time, and $1/T$ is the frequency bin width.
+For the star in our sample with the shortest observing time, this limit would be $\sim 89$ days, which quickly rises for longer observing baselines.
+While this constitutes a hard limit, slower rotation rates will become harder and harder to constrain as the rate of splitting becomes smaller.
+A benefit of the Bayesian approach used in this paper is that it should accurately reflect the increased uncertainty associated with the small rotational splitting.
+\end{itemize}
+
+While these two limits cause concern when studying the most extreme rotators, the results presented in this work are driven by stars with rotation rates in the regime of 5 to 30 days.
+Above, we demonstrated that results on period for these stars were data-driven (i.e.
+do not reflect the priors), indicating that the splitting is well resolved in this regime, and so we do not expect these limits to bias our conclusions.
+
+Finally, we also consider bias in asteroseismic detections.
+The probability of an asteroseismic detection with \kepler scales with temperature and radius (i.e.
+scales inversely with \logg, and therefore main sequence age), and detections are unlikely below roughly $5200\, K$ \cite{m_chaplin+2011, m_schofield+2019}.
+Very young ($\lesssim 2\, \rm{Gyr}$), very magnetically active stars may also suppress their oscillation modes.
+\cite{m_mathur+2019}.
+Though these two effects impose a bias on asteroseismic populations, they do so outside the parameter range on which our comparison takes place.
+As it is older stars, undergoing magnetic braking, that are required to drive the distinction between stellar models, we conclude that our seismic sample can be assumed to be complete for the purposes of this work.
+
+\section{Verifying consequences for gyrochronology}
+\subsection{Limits of our stellar models}\label{ssec:limits}
+The rotational stellar models used in this work \cite{m_vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$.
+Our sample of 91 stars contained 4 stars with metallicities below $-0.4\, \rm{dex}$, which are shown as shaded symbols in Figure \ref{fig:fullsample}.
+Of these, 3 were included in our final sample of 73 stars used to evaluate our stellar models: KICs 7970740, 8684723 and KIC 9965715.
+All three are classed as MS stars, with metallicities of $-0.54 \pm 0.10$, $-0.42 \pm 0.10$ and $-0.44 \pm 0.18\, \rm {dex}$ respectively, placing them within $3\sigma$ of the metallicity limits of our stellar models.
+KICs 8684723 and 9965715 strongly agree with the WMB model, whereas KIC 7970740 weakly prefers the standard model.
+Excluding these stars was not found to significantly alter the joint posterior distribution shown in Figure \ref{fig:gyroresults}.
+
+A recent study \cite{m_amard+matt2020} compared different rotational evolution models \cite[of which we use the former in this work]{m_vansaders+pinsonneault2013,m_matt+2015} while studying the effect metallicity has on rotation.
+They found that metal-rich stars spin down significantly more effectively than metal poor stars.
+The population of 73 stars used in our stellar model comparisons is roughly centered on a $\rm{[Fe/H]}$ of 0 $\rm dex$, with a spread of $~0.16\, \rm dex$, with no stars significantly above or below $\pm 0.4\, \rm dex$ (as discussed above).
+While differences in stellar rotational evolution as a function of metallicity in this region are still somewhat pronounced, they are much less so than for more metal-rich or poor stars \cite[see Figure 2]{m_amard+matt2020}.
+However, for stars with $\feh < 0$, the alternative model prescription \cite{m_matt+2015} sees stars spin down more slowly than the models used in this work (i.e.
+they will rotate faster at later ages).
+This work only explores the presence of weakened magnetic braking for a single braking law, and a comparison to alternative braking model will be explored in a future paper.
+
+When constructing KDEs from our stellar model samples (see Section \ref{s:gyro}), we selected fixed resolutions (or band-widths) for the KDEs.
+In mass, the band-width of $0.02\, M_\odot$, was larger than the uncertainties of 24 of 73 stars used to construct our joint posterior.
+For the stars with the smallest uncertainties, this significantly limits the size of the KDE being evaluated (as subsections of the full stellar models are used to evaluate individual stars, for computational efficiency).
+In order to confirm that these stars do not significantly affect the ensemble's preference towards the WMB model, we recalculated the joint posterior distribution for $Q_{\rm WMB}$, excluding stars with an uncertainty on mass smaller than the KDE band-width.
+While the 24 stars with small uncertainties do favour the WMB model, they do so very weakly, whereas the remaining 49 stars with larger uncertainties strongly favour the WMB model.
+Their removal from the total joint posterior probability does not significantly alter it from the distribution shown in Figure \ref{fig:gyroresults}.
+
+\subsection{Systematic uncertainties from asteroseismology}
+In our model analysis, we used asteroseismic mass and age obtained using \texttt{BASTA}, as reported in LEGACY and Kages.
+Asteroseismic properties obtained through stellar models can be subject to systematic errors arising from differences in input physics and choice of stellar models not included in the reported statistical uncertainties.
+A quantification of these different systematic effects can be found in the `Kages' catalogue paper \cite{m_silvaaguirre+2015}.
+Combining their reported median systematic uncertainties due to input physics results in median uncertainties of $20\%$ (up from $14\%)$ on age and $5\%$ (up from $3\%$) on mass for the `Kages' sample.
+For LEGACY, the median uncertainties are $18\%$ (up from $10\%)$ and $5.6\%$ (up from $4\%$) for age and mass respectively.
+
+We re-ran our model analysis after inflating uncertainties on mass and age.
+We increased uncertainties by the fractional difference between the \texttt{BASTA} statistical uncertainties and the median full statistical and systematic uncertainties described above.
+For example, a LEGACY star with a mass of $2.0 \pm 0.5\, M_\odot$ would have its uncertainty inflated by $1.6\%$ of its mass, to $0.53\, M_\odot$.
+
+To further test the limits of this analysis, we also reran our mixture model fit, this time only shifting the asteroseismic ages younger by the systematic uncertainty, and retaining the statistical uncertainty (i.e.
+the ages of LEGACY and `Kages' stars were reduced by $8\%$ and $6\%$ respectively).
+In this scenario where all asteroseismic ages are overestimated, `true' fast rotators at young ages would have been mistaken for fast rotators at old ages, suggesting the presence of weakened magnetic braking where none existed.
+
+The results of these tests are discussed further in the main body of the paper.
+
+\subsection{Binaries and Planet Hosts}
+For stars to be good probes of existing gyrochronology relations, their rotational evolution must occur in isolation.
+If a star interacts with a close binary companion (through tides, or a merger) the natural angular momentum loss can be disturbed, causing gyrochronology to mispredict ages \cite{m_leiner+2019, m_fleming+2019}.
+Between LEGACY and Kages, we have 8 known binaries.
+
+First, KIC 8379927, KIC 7510397, KIC 10454113 and KIC 9025370 are spectroscopic binaries.
+This does not affect the asteroseismic analysis, but may affect their rotational evolution.
+Of these, KICs 8379927, 7510397 and 9025370 were included in the gyrochronology analysis.
+None of them preferred one model strongly over the other, with all three finding flat posteriors for $Q_{\rm WMB}$.
+
+Second, the binary pairs of KIC 9139151 \& 9139163 and 16 Cyg A \& B are individually observed binary components with wide orbital separations, so we do not expect their binarity to have affected their rotational evolution \cite{m_halbwachs1986, m_white+2013}.
+
+While we chose not to account for star-planet tidal interactions in this work, we note that this may disturb the natural stellar rotational evolution when tidal forces are at play \cite{m_maxted+2015,m_gallet+delorme2019, m_benbakoura+2019}, although this has been disputed by observations of asteroseismic planet hosts \cite{m_ceillier+2016}.\\
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{Images/priors.jpg}
+	\caption{\textbf{Comparisons between posterior estimates of rotational parameters (data points and error bars) and the priors on these parameters (shaded regions).} The data are sorted from young stars (left) to old (right).
+Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$).
+Both the prior and values for $P$ are a transformation of the upper two parameters (see \textbf{Methods} and \textbf{Supplementary Information}).
+In all cases, the extent of the error bars and shaded regions indicate the 68\% credible interval of the posterior and prior distributions respectively.
+The solid lines indicate the median of the prior distributions.
+In this figure, results with means and errorbars that closely resemble the prior distribution can be interpreted as prior-dominated (i.e.
+poorly informed by the data).
+All stars are sorted and coloured and sorted by age.
+In the case of inclination angle $i$ and rotation period $P$, the displayed priors are transformed from the priors imposed on the sampled parameters from which their posteriors were derived.}
+	\label{fig:priors}
+\end{figure}
+
+\begin{figure*}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{Images/litcomp_alt2.jpg}
+	\caption{\textbf{Comparisons between posterior estimates of rotational parameters from this work and the literature}.
+Literature values are taken from LEGACY and `Kages' \cite[private communication]{m_davies+2016, m_lund+2017}.
+Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$).
+Fractional differences are plotted against stellar rotation obtained in this work.
+The $\Delta$ indicates the fractional difference between this work and the literature (i.e.
+stars above the zero-line have higher values in this work).
+The right hand panels the distribution of the fractional differences around the zero line.
+The colour legend is consistent throughout all panels.
+The x-axis units on the right hand panels are equivalent to the y-axis of the left hand panels.
+10 stars have been omitted from this plot and are discussed in more detail in \textbf{Methods}: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have extremely low rotation periods in Kages, with high uncertainties.
+Conversely, KICs 6603624, 8760414 and 8938364 have extremely high rotation periods in LEGACY with low uncertainties.
+Error bars represent the 68\% confidence intervals.
+In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
+	\label{fig:legacykages}
+\end{figure*}
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{Images/seis_comparison_rot_alt2.jpg}
+	\caption{\textbf{Fractional differences between posterior estimates of asteroseismic rotation period from this work.} Literature sources are: Davies et al.
+(2015) \cite{m_davies+2015} (16 Cyg A \& B), Nielsen et al.
+(2015) \cite{m_nielsen+2015} (5 stars) and Benomar et al.
+(2018) \cite{m_benomar+2018} (40 stars).
+We used the reported parameter $a_{1}$ from the latter, which represents the rotational splitting in the case of uniform latitudinal rotation in their model.
+The dashed line represents the median of the sample shown, with the dotted lines representing the $15.9^{\rm{th}}$ and $84.1^{\rm{st}}$ percentiles.
+Error bars represent the 68\% confidence intervals.
+In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
+	\label{fig:literaturecomp}
+\end{figure}
+
+\begin{figure*}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{Images/vsini_comparison_new.jpg}
+	\caption{\textbf{Comparisons between asteroseismic and spectroscopic measures of projected surface rotation, $\textrm{v}\sin(i)$.} All asteroseismic (x-axis) values are from this work, all spectroscopic (y-axis) values are from the literature.
+\textit{Left}: comparisons to 81 stars values reported in LEGACY and Kages.
+\textit{Right}: comparisons to 16 stars observed by Benomar et al.
+(2015) \cite{m_benomar+2015}.
+Asteroseismic values are transformed from projected splitting ($\nu_s\sin(i)$) using the asteroseismic radius measurements presented in LEGACY and `Kages'.
+Horizontal error bars represent the 68\% confidence intervals.
+Vertical error bars represent the formal uncertainty on the published spectroscopic values.
+The solid lines indicate the 1:1 line, while the dash-dotted lines represent the 2:1 and 1:2 lines.
+The dashed lines indicate the location of $\textrm{v}\sin(i) = 5\, \rm{kms^{-1}}$, the point at which surface and seismic measures of projected rotation begin to differ strongly \cite{m_tayar+2015}.}
+	\label{fig:vsinilit}
+\end{figure*}
 

### 2021-02-15 paper/natastron/Publication/aas_macros.tex
references done fucking finally

\let\jnl@style=\rm
\def\ref@jnl#1{{\jnl@style#1}}

\def\aj{\ref@jnl{AJ}}                   % Astronomical Journal
\def\actaa{\ref@jnl{Acta Astron.}}      % Acta Astronomica
\def\araa{\ref@jnl{ARA\&A}}             % Annual Review of Astron and Astrophys
\def\apj{\ref@jnl{ApJ}}                 % Astrophysical Journal
\def\apjl{\ref@jnl{ApJ}}                % Astrophysical Journal, Letters
\def\apjs{\ref@jnl{ApJS}}               % Astrophysical Journal, Supplement
\def\ao{\ref@jnl{Appl.~Opt.}}           % Applied Optics
\def\apss{\ref@jnl{Ap\&SS}}             % Astrophysics and Space Science
\def\aap{\ref@jnl{A\&A}}                % Astronomy and Astrophysics
\def\aapr{\ref@jnl{A\&A~Rev.}}          % Astronomy and Astrophysics Reviews
\def\aaps{\ref@jnl{A\&AS}}              % Astronomy and Astrophysics, Supplement
\def\azh{\ref@jnl{AZh}}                 % Astronomicheskii Zhurnal
\def\baas{\ref@jnl{BAAS}}               % Bulletin of the AAS
\def\bac{\ref@jnl{Bull. astr. Inst. Czechosl.}}
                % Bulletin of the Astronomical Institutes of Czechoslovakia 
\def\caa{\ref@jnl{Chinese Astron. Astrophys.}}
                % Chinese Astronomy and Astrophysics
\def\cjaa{\ref@jnl{Chinese J. Astron. Astrophys.}}
                % Chinese Journal of Astronomy and Astrophysics
\def\icarus{\ref@jnl{Icarus}}           % Icarus
\def\jcap{\ref@jnl{J. Cosmology Astropart. Phys.}}
                % Journal of Cosmology and Astroparticle Physics
\def\jrasc{\ref@jnl{JRASC}}             % Journal of the RAS of Canada
\def\memras{\ref@jnl{MmRAS}}            % Memoirs of the RAS
\def\mnras{\ref@jnl{MNRAS}}             % Monthly Notices of the RAS
\def\na{\ref@jnl{New A}}                % New Astronomy
\def\nar{\ref@jnl{New A Rev.}}          % New Astronomy Review
\def\pra{\ref@jnl{Phys.~Rev.~A}}        % Physical Review A: General Physics
\def\prb{\ref@jnl{Phys.~Rev.~B}}        % Physical Review B: Solid State
\def\prc{\ref@jnl{Phys.~Rev.~C}}        % Physical Review C
\def\prd{\ref@jnl{Phys.~Rev.~D}}        % Physical Review D
\def\pre{\ref@jnl{Phys.~Rev.~E}}        % Physical Review E
\def\prl{\ref@jnl{Phys.~Rev.~Lett.}}    % Physical Review Letters
\def\pasa{\ref@jnl{PASA}}               % Publications of the Astron. Soc. of Australia
\def\pasp{\ref@jnl{PASP}}               % Publications of the ASP
\def\pasj{\ref@jnl{PASJ}}               % Publications of the ASJ
\def\rmxaa{\ref@jnl{Rev. Mexicana Astron. Astrofis.}}%
                % Revista Mexicana de Astronomia y Astrofisica
\def\qjras{\ref@jnl{QJRAS}}             % Quarterly Journal of the RAS
\def\skytel{\ref@jnl{S\&T}}             % Sky and Telescope
\def\solphys{\ref@jnl{Sol.~Phys.}}      % Solar Physics
\def\sovast{\ref@jnl{Soviet~Ast.}}      % Soviet Astronomy
\def\ssr{\ref@jnl{Space~Sci.~Rev.}}     % Space Science Reviews
\def\zap{\ref@jnl{ZAp}}                 % Zeitschrift fuer Astrophysik
\def\nat{\ref@jnl{Nature}}              % Nature
\def\iaucirc{\ref@jnl{IAU~Circ.}}       % IAU Cirulars
\def\aplett{\ref@jnl{Astrophys.~Lett.}} % Astrophysics Letters
\def\apspr{\ref@jnl{Astrophys.~Space~Phys.~Res.}}
                % Astrophysics Space Physics Research
\def\bain{\ref@jnl{Bull.~Astron.~Inst.~Netherlands}} 
                % Bulletin Astronomical Institute of the Netherlands
\def\fcp{\ref@jnl{Fund.~Cosmic~Phys.}}  % Fundamental Cosmic Physics
\def\gca{\ref@jnl{Geochim.~Cosmochim.~Acta}}   % Geochimica Cosmochimica Acta
\def\grl{\ref@jnl{Geophys.~Res.~Lett.}} % Geophysics Research Letters
\def\jcp{\ref@jnl{J.~Chem.~Phys.}}      % Journal of Chemical Physics
\def\jgr{\ref@jnl{J.~Geophys.~Res.}}    % Journal of Geophysics Research
\def\jqsrt{\ref@jnl{J.~Quant.~Spec.~Radiat.~Transf.}}
                % Journal of Quantitiative Spectroscopy and Radiative Transfer
\def\memsai{\ref@jnl{Mem.~Soc.~Astron.~Italiana}}
                % Mem. Societa Astronomica Italiana
\def\nphysa{\ref@jnl{Nucl.~Phys.~A}}   % Nuclear Physics A
\def\physrep{\ref@jnl{Phys.~Rep.}}   % Physics Reports
\def\physscr{\ref@jnl{Phys.~Scr}}   % Physica Scripta
\def\planss{\ref@jnl{Planet.~Space~Sci.}}   % Planetary Space Science
\def\procspie{\ref@jnl{Proc.~SPIE}}   % Proceedings of the SPIE

\let\astap=\aap
\let\apjlett=\apjl
\let\apjsupp=\apjs
\let\applopt=\ao

### 2021-02-15 paper/natastron/Publication/bblmethods.tex
references done fucking finally

@@
-\begin{thebibliography}{10}
+\begin{thebibliography}{99}
+\makeatletter
+\addtocounter{\@listctr}{51}
+\makeatother
 \expandafter\ifx\csname url\endcsname\relax
@@
 	planet hosts for asteroseismic analysis}.
-\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-  Society}} \textbf{\bibinfo{volume}{445}}, \bibinfo{pages}{2698--2709}
+\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+\textbf{\bibinfo{volume}{445}}, \bibinfo{pages}{2698--2709}
 (\bibinfo{year}{2014}).
@@
 	asteroseismic analyses}.
-\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-  Society}} \textbf{\bibinfo{volume}{414}}, \bibinfo{pages}{L6--L10}
+\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+\textbf{\bibinfo{volume}{414}}, \bibinfo{pages}{L6--L10}
 (\bibinfo{year}{2011}).
+
+\bibitem{christensen-dalsgaard2008}
+\bibinfo{author}{{Christensen-Dalsgaard}, J.}
+\newblock \bibinfo{title}{{{ASTEC}}\textemdash the {{Aarhus STellar Evolution
+			Code}}}.
+\newblock \emph{\bibinfo{journal}{Astrophysics and Space Science}}
+\textbf{\bibinfo{volume}{316}}, \bibinfo{pages}{13} (\bibinfo{year}{2008}).
 
@@
 	{{Transiting Planets}}}.
-\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 \textbf{\bibinfo{volume}{808}}, \bibinfo{pages}{187} (\bibinfo{year}{2015}).
@@
 	astronomy}.
-\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
+\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
 \textbf{\bibinfo{volume}{558}}, \bibinfo{pages}{A33} (\bibinfo{year}{2013}).
+
+\bibitem{astropycollaboration+2018}
+\bibinfo{author}{{Astropy Collaboration}} \emph{et~al.}
+\newblock \bibinfo{title}{The {{Astropy Project}}: {{Building}} an
+	{{Open}}-science {{Project}} and {{Status}} of the v2.0 {{Core Package}}}.
+\newblock \emph{\bibinfo{journal}{Astron. J.}} \textbf{\bibinfo{volume}{156}},
+\bibinfo{pages}{123} (\bibinfo{year}{2018}).
+
+\bibitem{ginsburg+2019}
+\bibinfo{author}{Ginsburg, A.} \emph{et~al.}
+\newblock \bibinfo{title}{Astroquery: {{An Astronomical Web}}-querying
+	{{Package}} in {{Python}}}.
+\newblock \emph{\bibinfo{journal}{Astron. J.}} \textbf{\bibinfo{volume}{157}},
+\bibinfo{pages}{98} (\bibinfo{year}{2019}).
 
@@
 	pulsations}.
-\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
+\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
 \textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{469} (\bibinfo{year}{1980}).
 
+\bibitem{vrard+2016}
+\bibinfo{author}{Vrard, M.}, \bibinfo{author}{Mosser, B.} \&
+\bibinfo{author}{Samadi, R.}
+\newblock \bibinfo{title}{Period spacings in red giants. {{II}}. {{Automated}}
+	measurement}.
+\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+\textbf{\bibinfo{volume}{588}}, \bibinfo{pages}{A87} (\bibinfo{year}{2016}).
+
 \bibitem{hogg+2010}
-\bibinfo{author}{Hogg, D.~W.}, \bibinfo{author}{Bovy, J.} \&
-  \bibinfo{author}{Lang, D.}
-\newblock \bibinfo{title}{Data analysis recipes: {{Fitting}} a model to data}.
-\newblock \emph{\bibinfo{journal}{ArXiv e-prints}}
+\bibinfo{author}{{Hogg}, D.~W.}, \bibinfo{author}{{Bovy}, J.} \&
+\bibinfo{author}{{Lang}, D.}
+\newblock \bibinfo{title}{{Data analysis recipes: Fitting a model to data}}.
+\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
 \bibinfo{pages}{arXiv:1008.4686} (\bibinfo{year}{2010}).
+\newblock \eprint{1008.4686}.
+
+\bibitem{hall+2019}
+\bibinfo{author}{Hall, O.~J.} \emph{et~al.}
+\newblock \bibinfo{title}{Testing asteroseismology with {{Gaia DR2}}:
+	{{Hierarchical}} models of the {{Red Clump}}}.
+\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+\textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{3569--3585}
+(\bibinfo{year}{2019}).
+\newblock \eprint{1904.07919}.
 
@@
 	from oscillation frequencies observed by {{Kepler}}}.
-\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 \textbf{\bibinfo{volume}{782}}, \bibinfo{pages}{18} (\bibinfo{year}{2014}).
@@
 
+\bibitem{carpenter+2017}
+\bibinfo{author}{Carpenter, B.} \emph{et~al.}
+\newblock \bibinfo{title}{Stan: {{A Probabilistic Programming Language}}}.
+\newblock \emph{\bibinfo{journal}{Journal of Statistical Software}}
+\textbf{\bibinfo{volume}{76}}, \bibinfo{pages}{1--32} (\bibinfo{year}{2017}).
+
 \bibitem{vanderwalt+2011}
@@
 
+\bibitem{thetheanodevelopmentteam+2016}
+\bibinfo{author}{{The Theano Development Team}} \emph{et~al.}
+\newblock \bibinfo{title}{{Theano: A Python framework for fast computation of
+		mathematical expressions}}.
+\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
+\bibinfo{pages}{arXiv:1605.02688} (\bibinfo{year}{2016}).
+\newblock \eprint{1605.02688}.
+
 \bibitem{gaiacollaboration+2018}
 \bibinfo{author}{{Gaia Collaboration}} \emph{et~al.}
-\newblock \bibinfo{title}{Gaia {{Data Release}} 2. {{Summary}} of the contents
-  and survey properties}.
-\newblock \emph{\bibinfo{journal}{ArXiv e-prints}}
-  \bibinfo{pages}{arXiv:1804.09365} (\bibinfo{year}{2018}).
+\newblock \bibinfo{title}{{Gaia Data Release 2. Summary of the contents and
+		survey properties}}.
+\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+\textbf{\bibinfo{volume}{616}}, \bibinfo{pages}{A1} (\bibinfo{year}{2018}).
+\newblock \eprint{1804.09365}.
 
@@
 	{{Multiplicity}} of {{Solar}}-type {{Stars}}}.
-\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
+\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
 \textbf{\bibinfo{volume}{190}}, \bibinfo{pages}{1--42}
@@
 \bibinfo{author}{Seabold, S.} \& \bibinfo{author}{Perktold, J.}
-\newblock \bibinfo{title}{Statsmodels: {{Econometric}} and {{Statistical
-  Modeling}} with {{Python}}} \bibinfo{pages}{5} (\bibinfo{year}{2010}).
+\newblock \bibinfo{title}{{S}tatsmodels: {E}conometric and {S}tatistical
+	{M}odeling with {P}ython}.
+\newblock In \bibinfo{editor}{{S}t\'efan van~der {W}alt} \&
+\bibinfo{editor}{{J}arrod {M}illman} (eds.)
+\emph{\bibinfo{booktitle}{{P}roceedings of the 9th {P}ython in {S}cience
+		{C}onference}}, \bibinfo{pages}{92 -- 96} (\bibinfo{year}{2010}).
+
+\bibitem{betancourt+girolami2013}
+\bibinfo{author}{{Astrophys. J.}, M.~J.} \& \bibinfo{author}{{Girolami}, M.}
+\newblock \bibinfo{title}{{Hamiltonian Monte Carlo for Hierarchical Models}}.
+\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
+\bibinfo{pages}{arXiv:1312.0906} (\bibinfo{year}{2013}).
+\newblock \eprint{1312.0906}.
 
@@
 \newblock \bibinfo{title}{Emcee: {{The MCMC Hammer}}}.
-\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
-  the Pacific}} \textbf{\bibinfo{volume}{125}}, \bibinfo{pages}{306--312}
+\newblock \emph{\bibinfo{journal}{Publ. Astron. Soc. Pacific}}
+\textbf{\bibinfo{volume}{125}}, \bibinfo{pages}{306--312}
 (\bibinfo{year}{2013}).
@@
 
+\bibitem{foreman-mackey2016}
+\bibinfo{author}{{Foreman-Mackey}, D.}
+\newblock \bibinfo{title}{Corner.py: {{Scatterplot}} matrices in {{Python}}}.
+\newblock \emph{\bibinfo{journal}{The Journal of Open Source Software}}
+\textbf{\bibinfo{volume}{1}} (\bibinfo{year}{2016}).
+
 \end{thebibliography}

### 2021-02-15 paper/natastron/Publication/bblpaper.tex
tidying up for publication
references done fucking finally

--- 2020-10-09 paper/natastron/bblpaper.tex
@@
 
-	\bibitem{vansaders+pinsonneault2013}
-	\bibinfo{author}{{van Saders}, J.~L.} \& \bibinfo{author}{Pinsonneault, M.~H.}
-	\newblock \bibinfo{title}{Fast {{Star}}, {{Slow Star}}; {{Old Star}}, {{Young
-				Star}}: {{Subgiant Rotation}} as a {{Population}} and {{Stellar Physics
-				Diagnostic}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-	\textbf{\bibinfo{volume}{776}}, \bibinfo{pages}{67} (\bibinfo{year}{2013}).
-
-	\bibitem{vansaders+2016}
-	\bibinfo{author}{{van Saders}, J.~L.} \emph{et~al.}
-	\newblock \bibinfo{title}{Weakened magnetic braking as the origin of
-		anomalously rapid rotation in old field stars}.
-	\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{529}},
-	\bibinfo{pages}{181} (\bibinfo{year}{2016}).
-
 	\bibitem{barnes2007}
@@
 				Gyrochronology}}: {{Viability}}, {{Limitations}}, and {{Errors}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{669}}, \bibinfo{pages}{1167} (\bibinfo{year}{2007}).
@@
 				Periods}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{881}}, \bibinfo{pages}{47} (\bibinfo{year}{2019}).
@@
 	\bibitem{claytor+2019}
-	\bibinfo{author}{Claytor, Z.~R.} \emph{et~al.}
-	\newblock \bibinfo{title}{Chemical {{Evolution}} in the {{Milky Way}}:
-		{{Rotation}}-based ages for {{APOGEE}}-{{Kepler}} cool dwarf stars}.
-	\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
-	\bibinfo{pages}{arXiv:1911.04518} (\bibinfo{year}{2019}).
+	\bibinfo{author}{{Claytor}, Z.~R.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Chemical Evolution in the Milky Way: Rotation-based
+			Ages for APOGEE-Kepler Cool Dwarf Stars}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{888}}, \bibinfo{pages}{43} (\bibinfo{year}{2020}).
+	\newblock \eprint{1911.04518}.
 
@@
 		the {{Applicability}} of {{Gyrochronology}} to at least {{Solar Age}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{823}}, \bibinfo{pages}{16} (\bibinfo{year}{2016}).
@@
 		exoplanet host stars from asteroseismology}.
-	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-			Society}} \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2127}
-	(\bibinfo{year}{2015}).
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2127} (\bibinfo{year}{2015}).
 
@@
 		asteroseismic targets}.
-	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-			Society}} \textbf{\bibinfo{volume}{450}}, \bibinfo{pages}{1787}
-	(\bibinfo{year}{2015}).
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{450}}, \bibinfo{pages}{1787} (\bibinfo{year}{2015}).
 
@@
 		stars from asteroseismic and starspot rotation periods}.
-	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
+	\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
 	\textbf{\bibinfo{volume}{582}}, \bibinfo{pages}{A10} (\bibinfo{year}{2015}).
@@
 		and planetary system dynamics of 16 {{Cygni}}}.
-	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-			Society}} \textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959}
-	(\bibinfo{year}{2015}).
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959} (\bibinfo{year}{2015}).
+
+	\bibitem{vansaders+2016}
+	\bibinfo{author}{{van Saders}, J.~L.} \emph{et~al.}
+	\newblock \bibinfo{title}{Weakened magnetic braking as the origin of
+		anomalously rapid rotation in old field stars}.
+	\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{529}},
+	\bibinfo{pages}{181} (\bibinfo{year}{2016}).
 
 	\bibitem{reville+2015}
-	\bibinfo{author}{R{\'e}ville, V.}, \bibinfo{author}{Brun, A.~S.},
-	\bibinfo{author}{Matt, S.}, \bibinfo{author}{Strugarek, A.} \&
-	\bibinfo{author}{Pinto, R.}
-	\newblock \bibinfo{title}{The effect of magnetic topology on thermally-driven
-		winds: Towards a general formulation of the braking law}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\bibinfo{author}{{R{\'e}ville}, V.}, \bibinfo{author}{{Brun}, A.~S.},
+	\bibinfo{author}{{Matt}, S.~P.}, \bibinfo{author}{{Strugarek}, A.} \&
+	\bibinfo{author}{{Pinto}, R.~F.}
+	\newblock \bibinfo{title}{{The Effect of Magnetic Topology on Thermally Driven
+			Wind: Toward a General Formulation of the Braking Law}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{798}}, \bibinfo{pages}{116} (\bibinfo{year}{2015}).
@@
 		in {{Transition}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Letters}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J. Letters}}
 	\textbf{\bibinfo{volume}{826}}, \bibinfo{pages}{L2} (\bibinfo{year}{2016}).
@@
 	\bibitem{metcalfe+2019}
-	\bibinfo{author}{Metcalfe, T.~S.} \emph{et~al.}
-	\newblock \bibinfo{title}{{{LBT}}/{{PEPSI Spectropolarimetry}} of a {{Magnetic
-				Morphology Shift}} in {{Old Solar}}-type {{Stars}}}.
-	\newblock \emph{\bibinfo{journal}{arXiv:1912.01186 [astro-ph]}}
-	(\bibinfo{year}{2019}).
+	\bibinfo{author}{{Metcalfe}, T.~S.} \emph{et~al.}
+	\newblock \bibinfo{title}{{LBT/PEPSI Spectropolarimetry of a Magnetic
+			Morphology Shift in Old Solar-type Stars}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{887}}, \bibinfo{pages}{L38} (\bibinfo{year}{2019}).
 	\newblock \eprint{1912.01186}.
@@
 		{{Spin}}-down {{Torques}}?}
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{886}}, \bibinfo{pages}{120} (\bibinfo{year}{2019}).
@@
 				Main}}-{{Sequence Stars}}: {{The Full Autocorrelation Sample}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
 	\textbf{\bibinfo{volume}{211}}, \bibinfo{pages}{24} (\bibinfo{year}{2014}).
@@
 				Evolution}} in {{Sun}}-like {{Stars}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{799}}, \bibinfo{pages}{L23} (\bibinfo{year}{2015}).
@@
 				Stellar Populations}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{872}}, \bibinfo{pages}{128} (\bibinfo{year}{2019}).
@@
 		and the {{Problem}} of {{Beta Canis Majoris}}.}
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{114}}, \bibinfo{pages}{373} (\bibinfo{year}{1951}).
@@
 		planet-hosting stars using {{Bayesian}} techniques and machine learning}.
-	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-			Society}} \textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183}
-	(\bibinfo{year}{2016}).
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183} (\bibinfo{year}{2016}).
 
@@
 				Parameters}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{172} (\bibinfo{year}{2017}).
@@
 		{{Ages}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{173} (\bibinfo{year}{2017}).
@@
 		relations}.
-	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
+	\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
 	\textbf{\bibinfo{volume}{572}}, \bibinfo{pages}{A34} (\bibinfo{year}{2014}).
+
+	\bibitem{kraft1967}
+	\bibinfo{author}{Kraft, R.~P.}
+	\newblock \bibinfo{title}{Studies of {{Stellar Rotation}}. {{V}}. {{The
+				Dependence}} of {{Rotation}} on {{Age}} among {{Solar}}-{{Type Stars}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{150}}, \bibinfo{pages}{551} (\bibinfo{year}{1967}).
 
@@
 		{{Red Giants}}: {{First Results}} from {{Kepler}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Letters}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J. Letters}}
 	\textbf{\bibinfo{volume}{713}}, \bibinfo{pages}{L176--L181}
 	(\bibinfo{year}{2010}).
-
-	\bibitem{kraft1967}
-	\bibinfo{author}{Kraft, R.~P.}
-	\newblock \bibinfo{title}{Studies of {{Stellar Rotation}}. {{V}}. {{The
-				Dependence}} of {{Rotation}} on {{Age}} among {{Solar}}-{{Type Stars}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-	\textbf{\bibinfo{volume}{150}}, \bibinfo{pages}{551} (\bibinfo{year}{1967}).
 
@@
 		age}.
-	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
+	\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
 	\textbf{\bibinfo{volume}{580}}, \bibinfo{pages}{A130} (\bibinfo{year}{2015}).
@@
 	\bibitem{paxton+2017}
-	\bibinfo{author}{Paxton, B.} \emph{et~al.}
-	\newblock \bibinfo{title}{Modules for {{Experiments}} in {{Stellar
-				Astrophysics}} ({{MESA}}): {{Convective Boundaries}}, {{Element Diffusion}},
-		and {{Massive Star Explosions}}}.
-	\newblock \emph{\bibinfo{journal}{arXiv:1710.08424 [astro-ph]}}
-	(\bibinfo{year}{2017}).
+	\bibinfo{author}{{Paxton}, B.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Modules for Experiments in Stellar Astrophysics
+			(MESA): Convective Boundaries, Element Diffusion, and Massive Star
+			Explosions}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
+	\textbf{\bibinfo{volume}{234}}, \bibinfo{pages}{34} (\bibinfo{year}{2018}).
 	\newblock \eprint{1710.08424}.
@@
 		stars: {{Qualitative}} inference from asteroseismic data}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{790}}, \bibinfo{pages}{121} (\bibinfo{year}{2014}).
@@
 		spectroscopic measurements}.
-	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-			Society}} \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2654--2674}
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2654--2674}
 	(\bibinfo{year}{2015}).
@@
 		the {{Exoplanet Systems Kepler}}-50 and {{Kepler}}-65}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{766}}, \bibinfo{pages}{101} (\bibinfo{year}{2013}).
@@
 		observations}.
-	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
+	\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
 	\textbf{\bibinfo{volume}{557}}, \bibinfo{pages}{L10} (\bibinfo{year}{2013}).
@@
 	\bibitem{skumanich1972}
-	\bibinfo{author}{Skumanich, A.}
-	\newblock \bibinfo{title}{{{TIME SCALES FOR Ca}} n {{EMISSION DECAY}},
-		{{ROTATIONAL BRAKING}}, {{AND LITHIUM DEPLETION}}}.
-	\newblock \emph{\bibinfo{journal}{ApJ. . .}} \bibinfo{pages}{4}
-	(\bibinfo{year}{1972}).
+	\bibinfo{author}{{Skumanich}, A.}
+	\newblock \bibinfo{title}{{Time Scales for Ca II Emission Decay, Rotational
+			Braking, and Lithium Depletion}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{171}}, \bibinfo{pages}{565} (\bibinfo{year}{1972}).
 
@@
 	\newblock \bibinfo{title}{Angular momentum loss in low-mass stars}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{333}}, \bibinfo{pages}{236} (\bibinfo{year}{1988}).
@@
 	\bibitem{berger+2020}
-	\bibinfo{author}{Berger, T.~A.} \emph{et~al.}
-	\newblock \bibinfo{title}{The \${{Gaia}}\$-\${{Kepler}}\$ {{Stellar Properties
-				Catalog I}}: {{Homogeneous Fundamental Properties}} for 186,000
-		\${{Kepler}}\$ {{Stars}}}.
-	\newblock \emph{\bibinfo{journal}{arXiv:2001.07737 [astro-ph]}}
-	(\bibinfo{year}{2020}).
-	\newblock \eprint{2001.07737}.
+	\bibinfo{author}{{Berger}, T.~A.}, \bibinfo{author}{{Huber}, D.},
+	\bibinfo{author}{{Gaidos}, E.}, \bibinfo{author}{{van Saders}, J.~L.} \&
+	\bibinfo{author}{{Weiss}, L.~M.}
+	\newblock \bibinfo{title}{{The Gaia-Kepler Stellar Properties Catalog. II.
+			Planet Radius Demographics as a Function of Stellar Mass and Age}}.
+	\newblock \emph{\bibinfo{journal}{Astron. J.}} \textbf{\bibinfo{volume}{160}},
+	\bibinfo{pages}{108} (\bibinfo{year}{2020}).
+	\newblock \eprint{2005.14671}.
 
@@
 		{{Gyrochronology}} for {{Old Field Stars}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{871}}, \bibinfo{pages}{39} (\bibinfo{year}{2019}).
@@
 		solar twins}.
-	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-			Society}} \textbf{\bibinfo{volume}{485}}, \bibinfo{pages}{L68}
-	(\bibinfo{year}{2019}).
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{485}}, \bibinfo{pages}{L68} (\bibinfo{year}{2019}).
+
+	\bibitem{vansaders+pinsonneault2013}
+	\bibinfo{author}{{van Saders}, J.~L.} \& \bibinfo{author}{Pinsonneault, M.~H.}
+	\newblock \bibinfo{title}{Fast {{Star}}, {{Slow Star}}; {{Old Star}}, {{Young
+				Star}}: {{Subgiant Rotation}} as a {{Population}} and {{Stellar Physics
+				Diagnostic}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{776}}, \bibinfo{pages}{67} (\bibinfo{year}{2013}).
 
@@
 		for {{Gyrochronology}}, and {{Color}}-{{Period Diagrams}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	\textbf{\bibinfo{volume}{722}}, \bibinfo{pages}{222} (\bibinfo{year}{2010}).
@@
 		and {{Exploration}} ({{LEGUE}}) \textemdash{} {{The}} survey's science plan}.
-	\newblock \emph{\bibinfo{journal}{Research in Astronomy and Astrophysics}}
+	\newblock \emph{\bibinfo{journal}{Research in Astron. Astrophys.}}
 	\textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{735--754}
@@
 	\bibinfo{author}{{de Jong}, R.~S.} \emph{et~al.}
-	\newblock \bibinfo{title}{{{4MOST}}: 4-metre {{Multi}}-{{Object Spectroscopic
-				Telescope}}} \textbf{\bibinfo{volume}{9147}}, \bibinfo{pages}{91470M}
-	(\bibinfo{year}{2014}).
+	\newblock \bibinfo{title}{{4MOST: 4-metre Multi-Object Spectroscopic
+			Telescope}}.
+	\newblock In \bibinfo{editor}{{Ramsay}, S.~K.}, \bibinfo{editor}{{McLean},
+		I.~S.} \& \bibinfo{editor}{{Takami}, H.} (eds.)
+	\emph{\bibinfo{booktitle}{Ground-based and Airborne Instrumentation for
+			Astronomy V}}, vol. \bibinfo{volume}{9147} of \emph{\bibinfo{series}{Society
+			of Photo-Optical Instrumentation Engineers (SPIE) Conference Series}},
+	\bibinfo{pages}{91470M} (\bibinfo{year}{2014}).
 
 	\bibitem{dalton+2014}
-	\bibinfo{author}{Dalton, G.} \emph{et~al.}
-	\newblock \bibinfo{title}{Project overview and update on {{WEAVE}}: The next
-		generation wide-field spectroscopy facility for the {{William Herschel
-				Telescope}}} \textbf{\bibinfo{volume}{9147}}, \bibinfo{pages}{91470L}
-	(\bibinfo{year}{2014}).
+	\bibinfo{author}{{Dalton}, G.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Project overview and update on WEAVE: the next
+			generation wide-field spectroscopy facility for the William Herschel
+			Telescope}}.
+	\newblock In \bibinfo{editor}{{Ramsay}, S.~K.}, \bibinfo{editor}{{McLean},
+		I.~S.} \& \bibinfo{editor}{{Takami}, H.} (eds.)
+	\emph{\bibinfo{booktitle}{Ground-based and Airborne Instrumentation for
+			Astronomy V}}, vol. \bibinfo{volume}{9147} of \emph{\bibinfo{series}{Society
+			of Photo-Optical Instrumentation Engineers (SPIE) Conference Series}},
+	\bibinfo{pages}{91470L} (\bibinfo{year}{2014}).
+	\newblock \eprint{1412.0843}.
 
@@
 			Mid-Scale Program}}.
-	\newblock In \emph{\bibinfo{booktitle}{Bulletin of the American Astronomical
-			Society}}, vol.~\bibinfo{volume}{51}, \bibinfo{pages}{196}
-	(\bibinfo{year}{2019}).
+	\newblock In \emph{\bibinfo{booktitle}{Bull. Am. Astron. Soc.}},
+	vol.~\bibinfo{volume}{51}, \bibinfo{pages}{196} (\bibinfo{year}{2019}).
 
@@
 	\newblock \bibinfo{title}{{SDSS-V Pioneering Panoptic Spectroscopy}}.
-	\newblock In \emph{\bibinfo{booktitle}{Bulletin of the American Astronomical
-			Society}}, vol.~\bibinfo{volume}{51}, \bibinfo{pages}{274}
-	(\bibinfo{year}{2019}).
+	\newblock In \emph{\bibinfo{booktitle}{Bull. Am. Astron. Soc.}},
+	vol.~\bibinfo{volume}{51}, \bibinfo{pages}{274} (\bibinfo{year}{2019}).
 

### 2021-02-15 paper/natastron/Publication/methods.tex
references done fucking finally

@@
 
-For our asteroseismic ages, we used the ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{m_silvaaguirre+2015} in the `Kages' and LEGACY catalogues.
+For our asteroseismic ages, we used the ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{silvaaguirre+2015} in the `Kages' and LEGACY catalogues.
 These ages have been obtained by comparisons of measured oscillation properties to stellar models, accounting for an expanded range of metallicities.
 \texttt{BASTA} is thoroughly compared to four other seismic modelling techniques in \cite{silvaaguirre+2017}.
-While uncertainties found through \texttt{BASTA} are typically higher than for other techniques, only \texttt{BASTA} and \texttt{ASTFIT} \cite[Aarhus STellar Evolution Code]{m_christensen-dalsgaard2008} recover the radius, mass and age of the Sun, when applied to solar data.
+While uncertainties found through \texttt{BASTA} are typically higher than for other techniques, only \texttt{BASTA} and \texttt{ASTFIT} \cite[Aarhus STellar Evolution Code]{christensen-dalsgaard2008} recover the radius, mass and age of the Sun, when applied to solar data.
 Although the uncertainties on \texttt{ASTFIT} ages are overall lower, they are not published for the `Kages' sample.
@@
 As described in the catalogue papers, for `Kages' stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy \cite{huber+2013a}.
-For LEGACY stars, atmospheric properties were similarly taken from one study \cite{buchhave+latham2015} for most stars in the catalogue, and complemented by other values from the literature for the remaining stars \cite[see Table 3]{m_silvaaguirre+2017}.
+For LEGACY stars, atmospheric properties were similarly taken from one study \cite{buchhave+latham2015} for most stars in the catalogue, and complemented by other values from the literature for the remaining stars \cite[see Table 3]{silvaaguirre+2017}.
 
-Other asteroseismic properties used in this study, such as those used as first guesses on the free parameters in our asteroseismic model, were taken from the `Kages' and LEGACY catalogues \cite{astropycollaboration+2013, m_astropycollaboration+2018, m_ginsburg+2019}.
+Other asteroseismic properties used in this study, such as those used as first guesses on the free parameters in our asteroseismic model, were taken from the `Kages' and LEGACY catalogues \cite{astropycollaboration+2013, astropycollaboration+2018, ginsburg+2019}.
 In cases where both catalogues contained the same target, we used the stellar parameters reported in LEGACY \cite{mckinney2010}.
@@
 In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background, modes of oscillation, and white noise, while accounting for rotational splitting.
-The foundations of this approach follows best-practices in asteroseismology \cite{davies+2015}, fitting Harvey profiles for the background \cite{harvey1985} and expressing the frequencies of the modes using an asymptotic expression \cite{tassoul1980, m_vrard+2016}.
+The foundations of this approach follows best-practices in asteroseismology \cite{davies+2015}, fitting Harvey profiles for the background \cite{harvey1985} and expressing the frequencies of the modes using an asymptotic expression \cite{tassoul1980, vrard+2016}.
 
-The first core improvement in this work is the use of hierarchical latent variable models \cite{hogg+2010, m_hall+2019}, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{mazumdar+2014}).
+The first core improvement in this work is the use of hierarchical latent variable models \cite{hogg+2010, hall+2019}, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{mazumdar+2014}).
 By improving the inference of mode frequencies in this way, we also improve the ability to resolve the rotational splitting.
@@
 First, we fit a model for the convective background and white noise only, to the region of the power spectra that did not contain modes of oscillation.
-This was done using \texttt{PyStan} \cite{vanhoey+2013, m_carpenter+2017}, for 10,000 iterations on each star.
+This was done using \texttt{PyStan} \cite{vanhoey+2013, carpenter+2017}, for 10,000 iterations on each star.
 These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work.
@@
 The results of the first fit to the convective background were used as extremely informative priors on the background parameters in this second fit.
-This was done using \texttt{PyMC3} \cite{vanderwalt+2011,m_salvatier+2016, m_thetheanodevelopmentteam+2016} for 2500 iterations each on 4 chains.
+This was done using \texttt{PyMC3} \cite{vanderwalt+2011, salvatier+2016, thetheanodevelopmentteam+2016} for 2500 iterations each on 4 chains.
 
@@
 In the model, the Rossby number is defined as the rotation period divided by the convective turnover timescale, which in turn is defined as $\tau_{\rm cz} = H_p / v_{\rm conv}$, where $H_p$ is the pressure scale height at the base of the convection zone, and $v_{\rm conv}$ is the convetive velocity evaluated one pressure scale height above the base in a mixing length theory of convection.
-Solid body rotation is assumed \cite{nielsen+2015}.} For further details, see \cite{vansaders+pinsonneault2013} and \cite{vansaders+2016, m_vansaders+2019} for the standard and weakened magnetic braking cases respectively.
+Solid body rotation is assumed \cite{nielsen+2015}.} For further details, see \cite{vansaders+pinsonneault2013} and \cite{vansaders+2016, vansaders+2019} for the standard and weakened magnetic braking cases respectively.
 
@@
 Once drawn we dropped the binary companion and used the true TRILEGAL properties of those stars.
-For stars where the mass of the companion was $M < 0.4\, M_\odot$, binary contributions were ignored.
+For stars where the mass of the companion was $M < 0.4\, \odot$, binary contributions were ignored.
 Every binary was assumed to result in a blend, regardless of separation.
@@
 In order to draw probabilistic inference about the models, we built a five-dimensional Kernel Density Estimate (KDE) of both model populations using the \texttt{statsmodels} package \cite{seabold+perktold2010}.
-We used a band-width (setting the resolution of the KDE) of $0.02\, M_\odot$ in mass, $10\, \rm K$ in \teff, $0.01\, \rm{dex}$ in $\ln(t)$, $0.01\, \rm{dex}$ in $\rm{[Fe/H]}$ and $0.01\, \rm{dex}$ in $\ln(P)$.
+We used a band-width (setting the resolution of the KDE) of $0.02\, \odot$ in mass, $10\, \rm K$ in \teff, $0.01\, \rm{dex}$ in $\ln(t)$, $0.01\, \rm{dex}$ in $\rm{[Fe/H]}$ and $0.01\, \rm{dex}$ in $\ln(P)$.
 Note that age and rotation were treated in log space, where the posterior estimates from asteroseismology more closely resemble normal distributions.
@@
 At 95 stars, in 5 parameter spaces, this totals 476 free parameters to marginalise over.
-This is not an issue for Hamiltonian Monte Carlo \cite[HMC]{m_betancourt+girolami2013}, however the use of KDE functions, over which a probabilistic gradient can not be measured, reduces HMCs effectiveness.
-Alternative Markov Chain Monte Carlo techniques \cite[MCMC]{m_foreman-mackey+2013} can more efficiently sample the KDE functions, but can not treat the large number of hierarchical parameters.
+This is not an issue for Hamiltonian Monte Carlo \cite[HMC]{betancourt+girolami2013}, however the use of KDE functions, over which a probabilistic gradient can not be measured, reduces HMCs effectiveness.
+Alternative Markov Chain Monte Carlo techniques \cite[MCMC]{foreman-mackey+2013} can more efficiently sample the KDE functions, but can not treat the large number of hierarchical parameters.
 To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $Q_{\rm WMB}$, and multiplied these post hoc to obtain a combined posterior.
@@
 
-We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{foreman-mackey+2013, m_foreman-mackey2016}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.
+We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{foreman-mackey+2013, foreman-mackey2016}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.
 
@@
 (2016) and Lund et al.
-(2017) \cite{silvaaguirre+2015, m_silvaaguirre+2017,m_davies+2016, m_lund+2017}.
+(2017) \cite{silvaaguirre+2015, silvaaguirre+2017, davies+2016, lund+2017}.
 Parameter distributions of the \kepler field used to alter our stellar population models were taken from Berger et al.
@@
 %\bibliography{library.bib} % if your bibtex file is called example.bib
-
+%
 %\end{document}

### 2021-02-16 paper/natastron/Publication/bblmethods.tex
paper done

@@
 \bibitem{huber+2013a}
-\bibinfo{author}{Huber, D.} \emph{et~al.}
-\newblock \bibinfo{title}{Stellar {{Spin}}-{{Orbit Misalignment}} in a
-	{{Multiplanet System}}}.
-\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{342}},
-\bibinfo{pages}{331} (\bibinfo{year}{2013}).
+\bibinfo{author}{{Barnes}, S.~A.}
+\newblock \bibinfo{title}{{A Simple Nonlinear Model for the Rotation of
+  Main-sequence Cool Stars. I. Introduction, Implications for Gyrochronology,
+  and Color-Period Diagrams}}.
+\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+  \textbf{\bibinfo{volume}{722}}, \bibinfo{pages}{222--234}
+  (\bibinfo{year}{2010}).
 
@@
 \bibitem{tassoul1980}
-\bibinfo{author}{Tassoul, M.}
-\newblock \bibinfo{title}{Asymptotic approximations for stellar nonradial
-	pulsations}.
+\bibinfo{author}{{Tassoul}, M.}
+\newblock \bibinfo{title}{{Asymptotic approximations for stellar nonradial
+  pulsations.}}
 \newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
-\textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{469} (\bibinfo{year}{1980}).
+  \textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{469--490}
+  (\bibinfo{year}{1980}).
 
@@
 \bibitem{chaplin+2011}
-\bibinfo{author}{Chaplin, W.~J.} \emph{et~al.}
-\newblock \bibinfo{title}{Ensemble {{Asteroseismology}} of {{Solar}}-{{Type
-			Stars}} with the {{NASA Kepler Mission}}}.
+\bibinfo{author}{{Chaplin}, W.~J.} \emph{et~al.}
+\newblock \bibinfo{title}{{Ensemble Asteroseismology of Solar-Type Stars with
+  the NASA Kepler Mission}}.
 \newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{332}},
   \bibinfo{pages}{213} (\bibinfo{year}{2011}).
+\newblock \eprint{1109.4723}.
 
@@
   \textbf{\bibinfo{volume}{1}} (\bibinfo{year}{2016}).
-
 \end{thebibliography}

### 2021-02-16 paper/natastron/Publication/si.tex
Done with SI

@@
 \subsection{Likelihood Function for $M(\nu)$}\label{sec:like}
-If data have Gaussian noise in the time domain, they will appear in the frequency domain with noise following a $\chi^2$ distribution with two degrees of freedom \cite[$\chi^2_2$ hereafter]{woodard1984}.
+If data have Gaussian noise in the time domain, they will appear in the frequency domain with noise following a $\chi^2$ distribution with two degrees of freedom \cite[$\chi^2_2$ hereafter]{appourchaux+1998}.
 The noise properties of $\chi^2_2$ distributed data are multiplicative, and require a specific treatment when fitting a model.
@@
 
-A comparison between prior and posterior is shown for 94 stars in $\nu_{\rm s}\sin(i)$, $i$ and $P$ in \textbf{Extended Data} Figure \ref{fig:priors}, arranged by age.
+A comparison between prior and posterior is shown for 94 stars in $\nu_{\rm s}\sin(i)$, $i$ and $P$ in Supplementary Figure \ref{fig:priors}, arranged by age.
 In the Figure, results with means (symbols) and $68\%$ credible regions (error bars) that are close to those same values for the prior distribution (where the horizontal line is the mean, and the shaded area is the credible region) can be interpreted as prior-dominated (i.e.
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{Images/priors.pdf}
+	\caption{\textbf{Comparisons between posterior estimates of rotational parameters (data points and error bars) and the priors on these parameters (shaded regions).} The data are sorted from young stars (left) to old (right).
+Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$).
+Both the prior and values for $P$ are a transformation of the upper two parameters (see text).
+In all cases, the extent of the error bars and shaded regions indicate the 68\% credible interval of the posterior and prior distributions respectively.
+The solid lines indicate the median of the prior distributions.
+In this figure, results with means and errorbars that closely resemble the prior distribution can be interpreted as prior-dominated (i.e.
+poorly informed by the data).
+All stars are sorted and coloured and sorted by age.
+In the case of inclination angle $i$ and rotation period $P$, the displayed priors are transformed from the priors imposed on the sampled parameters from which their posteriors were derived.}
+	\label{fig:priors}
+\end{figure}
+
 \subsection{Comparisons to previous studies}\label{ssec:litcomp}
@@
 
-Comparisons with LEGACY and `Kages' are shown in \textbf{Extended Data} Figure \ref{fig:legacykages} for projected splitting, inclination angle, and rotation period.
+Comparisons with LEGACY and `Kages' are shown in Supplementary Figure \ref{fig:legacykages} for projected splitting, inclination angle, and rotation period.
 In all three cases we show the fractional difference between the values obtained in this work and those from LEGACY and `Kages'.
@@
 
-A number of stars are excluded from \textbf{Extended Data} Figure \ref{fig:legacykages} and compared individually as extreme outliers: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have fast rotation rates ($<5\, \rm days$) in `Kages', but are found to have a broader spread of rotation rates in this work.
+A number of stars are excluded from Supplementary Figure \ref{fig:legacykages} and compared individually as extreme outliers: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have fast rotation rates ($<5\, \rm days$) in `Kages', but are found to have a broader spread of rotation rates in this work.
 At similar values for $\nu_{\rm s}\sin(i)$, `Kages' found much lower inclination angles with highly asymmetrical uncertainties.
@@
 
-We also compared our asteroseismic estimates of stellar rotation with similar studies in the literature, shown in \textbf{Extended Data} Figure \ref{fig:literaturecomp}.
-These included: a study of the binary solar analogues 16 Cyg A \& B \cite{m_davies+2015}, ; a study of surface and seismic rotation which our catalogue shares 5 stars with \cite{m_nielsen+2015}, ; and an asteroseismic study of differential rotation with which our catalogue shares 40 targets \cite{m_benomar+2018}.
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{Images/litcomp_alt2.pdf}
+	\caption{\textbf{Comparisons between posterior estimates of rotational parameters from this work and the literature}.
+Literature values are taken from LEGACY and `Kages' \cite[private communication]{davies+2016, lund+2017}.
+Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$).
+Fractional differences are plotted against stellar rotation obtained in this work.
+The $\Delta$ indicates the fractional difference between this work and the literature (i.e.
+stars above the zero-line have higher values in this work).
+The right hand panels the distribution of the fractional differences around the zero line.
+The colour legend is consistent throughout all panels.
+The x-axis units on the right hand panels are equivalent to the y-axis of the left hand panels.
+10 stars have been omitted from this plot and are discussed in more detail in the text: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have extremely low rotation periods in Kages, with high uncertainties.
+Conversely, KICs 6603624, 8760414 and 8938364 have extremely high rotation periods in LEGACY with low uncertainties.
+Error bars represent the 68\% confidence intervals.
+In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
+	\label{fig:legacykages}
+\end{figure}
+
+We also compared our asteroseismic estimates of stellar rotation with similar studies in the literature, shown in Supplementary Figure \ref{fig:literaturecomp}.
+These included: a study of the binary solar analogues 16 Cyg A \& B \cite{davies+2015}, ; a study of surface and seismic rotation which our catalogue shares 5 stars with \cite{nielsen+2015}, ; and an asteroseismic study of differential rotation with which our catalogue shares 40 targets \cite{benomar+2018}.
 For the latter, we used their reported splitting value $a_1$, which is equivalent to $\nu_{\rm s}$.
 
-Overall,  \textbf{Extended Data} Figure \ref{fig:literaturecomp} shows no strong disagreements between our asteroseismic measurements for stellar rotation and those from the literature.
+Overall,  Supplementary Figure \ref{fig:literaturecomp} shows no strong disagreements between our asteroseismic measurements for stellar rotation and those from the literature.
 The scatter of the fractional differences lies cleanly around the zero line, with a mean and spread of $0.0_{-15.6}^{+16.4}\, \%$.
@@
 
-It is of note that 16 Cyg A was found to be rotating slightly faster in our analysis compared to the literature \cite{m_davies+2015} (deviating within $2\sigma$), despite the fit being performed on the same data.
+It is of note that 16 Cyg A was found to be rotating slightly faster in our analysis compared to the literature \cite{davies+2015} (deviating within $2\sigma$), despite the fit being performed on the same data.
 We found an inclination angle that is slightly lower for 16 Cyg A but at a similar projected splitting, which would explain finding a lower value of rotation.
 
-There are three outliers at low period in  \textbf{Extended Data} Figure \ref{fig:literaturecomp}: KICs 6603624, 8760414 and 8938364.
+There are three outliers at low period in  Supplementary Figure \ref{fig:literaturecomp}: KICs 6603624, 8760414 and 8938364.
 These are the same targets found to be outliers in a comparison to the LEGACY and `Kages' measurements (see above), with anomalously fast rotation rates and low inclination angles.
@@
 
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{Images/seis_comparison_rot_alt2.pdf}
+	\caption{\textbf{Fractional differences between posterior estimates of asteroseismic rotation period from this work.} Literature sources are: Davies et al.
+(2015) \cite{davies+2015} (16 Cyg A \& B), Nielsen et al.
+(2015) \cite{nielsen+2015} (5 stars) and Benomar et al.
+(2018) \cite{benomar+2018} (40 stars).
+We used the reported parameter $a_{1}$ from the latter, which represents the rotational splitting in the case of uniform latitudinal rotation in their model.
+The dashed line represents the median of the sample shown, with the dotted lines representing the $15.9^{\rm{th}}$ and $84.1^{\rm{st}}$ percentiles.
+Error bars represent the 68\% confidence intervals.
+In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
+	\label{fig:literaturecomp}
+\end{figure}
+
 \subsection{Seismic vs spectroscopic rotation}
-A distinct difference between rotation rates obtained through different techniques may hold information about differential rotation (both latitudinal and radial) of near-surface layers, such as those we observe in the Sun \cite{m_beck2000}.
-A previous comparison of spectroscopic and seismic rotation rates, performed on a sample of 22 stars, found no significant radial differential rotation \cite{m_benomar+2018}.
+A distinct difference between rotation rates obtained through different techniques may hold information about differential rotation (both latitudinal and radial) of near-surface layers, such as those we observe in the Sun \cite{beck2000}.
+A previous comparison of spectroscopic and seismic rotation rates, performed on a sample of 22 stars, found no significant radial differential rotation \cite{benomar+2018}.
 In this work they not only considered rotation rates from spots, but also spectroscopic measures of the projected surface rotation $\textrm{v}\sin(i)$, which they found to be more reliable.
@@
 With our expanded sample of asteroseismic rotation we can perform a similar analysis, to both validate our sample and probe radial differential rotation.
-\textbf{Extended Data} Figure \ref{fig:vsinilit} shows a comparison between spectroscopic $\textrm{v}\sin(i)$ measurements as listed in LEGACY and `Kages' (left) and Benomar et al.
-(2015) \cite{m_benomar+2015} (right).
+Supplementary Figure \ref{fig:vsinilit} shows a comparison between spectroscopic $\textrm{v}\sin(i)$ measurements as listed in LEGACY and `Kages' (left) and Benomar et al.
+(2015) \cite{benomar+2015} (right).
 In these cases the asteroseismic $\textrm{v}\sin(i)$ has been calculated using our measure of asteroseismic $\nu_s\sin(i)$ and the known asteroseismic radii.
@@
 
-For the LEGACY and `Kages' sample, we find no strong deviation from the 1:1 line except at very low velocities, which is likely due to biases inherent to spectroscopic line broadening measurements \cite{m_doyle+2014, m_tayar+2015}.
+For the LEGACY and `Kages' sample, we find no strong deviation from the 1:1 line except at very low velocities, which is likely due to biases inherent to spectroscopic line broadening measurements \cite{doyle+2014, tayar+2015}.
 For the Benomar et al.
@@
 spectroscopic projected rotation rates are faster than asteroseismic rates).
-This offset is much smaller ($\sim5\%$) for the \cite{m_benomar+2015} sample, albeit for far fewer stars.
-These offsets are within the typical disagreement between spectroscopic methods, based on comparisons of projected rotation measurements for red giant stars \cite[see Figure 2]{m_tayar+2015}, especially at $< 5\, \rm{km\,s^{-1}}$.
+This offset is much smaller ($\sim5\%$) for the \cite{benomar+2015} sample, albeit for far fewer stars.
+These offsets are within the typical disagreement between spectroscopic methods, based on comparisons of projected rotation measurements for red giant stars \cite[see Figure 2]{tayar+2015}, especially at $< 5\, \rm{km\,s^{-1}}$.
 
@@
 For the majority of cases, the seismic velocities are slower than the spectroscopic velocities, which would bias our ensemble towards favouring a standard evolution over a weakened magnetic braking scenario (as stars would overall appear to be rotating slower at late ages).
-Based on the comparison to spot rotation presented in the main body of this paper, and given known issues comparing seismic and spectroscopic rotation at low velocities, we concluded that the divergence seen in  \textbf{Extended Data} Figure \ref{fig:vsinilit} does not undermine our results.
+Based on the comparison to spot rotation presented in the main body of this paper, and given known issues comparing seismic and spectroscopic rotation at low velocities, we concluded that the divergence seen in  Supplementary Figure \ref{fig:vsinilit} does not undermine our results.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{Images/vsini_comparison_new.pdf}
+	\caption{\textbf{Comparisons between asteroseismic and spectroscopic measures of projected surface rotation, $\textrm{v}\sin(i)$.} All asteroseismic (x-axis) values are from this work, all spectroscopic (y-axis) values are from the literature.
+\textit{Left}: comparisons to 81 stars values reported in LEGACY and Kages.
+\textit{Right}: comparisons to 16 stars observed by Benomar et al.
+(2015) \cite{benomar+2015}.
+Asteroseismic values are transformed from projected splitting ($\nu_s\sin(i)$) using the asteroseismic radius measurements presented in LEGACY and `Kages'.
+Horizontal error bars represent the 68\% confidence intervals.
+Vertical error bars represent the formal uncertainty on the published spectroscopic values.
+The solid lines indicate the 1:1 line, while the dash-dotted lines represent the 2:1 and 1:2 lines.
+The dashed lines indicate the location of $\textrm{v}\sin(i) = 5\, \rm{kms^{-1}}$, the point at which surface and seismic measures of projected rotation begin to differ strongly \cite{tayar+2015}.}
+	\label{fig:vsinilit}
+\end{figure}
 
@@
 The probability of an asteroseismic detection with \kepler scales with temperature and radius (i.e.
-scales inversely with \logg, and therefore main sequence age), and detections are unlikely below roughly $5200\, K$ \cite{m_chaplin+2011, m_schofield+2019}.
+scales inversely with \logg, and therefore main sequence age), and detections are unlikely below roughly $5200\, K$ \cite{chaplin+2011, schofield+2019}.
 Very young ($\lesssim 2\, \rm{Gyr}$), very magnetically active stars may also suppress their oscillation modes.
-\cite{m_mathur+2019}.
+\cite{mathur+2019}.
 Though these two effects impose a bias on asteroseismic populations, they do so outside the parameter range on which our comparison takes place.
@@
 \subsection{Limits of our stellar models}\label{ssec:limits}
-The rotational stellar models used in this work \cite{m_vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$.
+The rotational stellar models used in this work \cite{vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$.
 Our sample of 91 stars contained 4 stars with metallicities below $-0.4\, \rm{dex}$, which are shown as shaded symbols in Figure \ref{fig:fullsample}.
@@
 KICs 8684723 and 9965715 strongly agree with the WMB model, whereas KIC 7970740 weakly prefers the standard model.
-Excluding these stars was not found to significantly alter the joint posterior distribution shown in Figure \ref{fig:gyroresults}.
+Excluding these stars was not found to significantly alter the joint posterior distribution shown in Figure 4 of the main paper.
 
-A recent study \cite{m_amard+matt2020} compared different rotational evolution models \cite[of which we use the former in this work]{m_vansaders+pinsonneault2013,m_matt+2015} while studying the effect metallicity has on rotation.
+A recent study \cite{amard+matt2020} compared different rotational evolution models \cite[of which we use the former in this work]{vansaders+pinsonneault2013, matt+2015} while studying the effect metallicity has on rotation.
 They found that metal-rich stars spin down significantly more effectively than metal poor stars.
 The population of 73 stars used in our stellar model comparisons is roughly centered on a $\rm{[Fe/H]}$ of 0 $\rm dex$, with a spread of $~0.16\, \rm dex$, with no stars significantly above or below $\pm 0.4\, \rm dex$ (as discussed above).
-While differences in stellar rotational evolution as a function of metallicity in this region are still somewhat pronounced, they are much less so than for more metal-rich or poor stars \cite[see Figure 2]{m_amard+matt2020}.
-However, for stars with $\feh < 0$, the alternative model prescription \cite{m_matt+2015} sees stars spin down more slowly than the models used in this work (i.e.
+While differences in stellar rotational evolution as a function of metallicity in this region are still somewhat pronounced, they are much less so than for more metal-rich or poor stars \cite[see Figure 2]{amard+matt2020}.
+However, for stars with $\feh < 0$, the alternative model prescription \cite{matt+2015} sees stars spin down more slowly than the models used in this work (i.e.
 they will rotate faster at later ages).
@@
 When constructing KDEs from our stellar model samples (see Section \ref{s:gyro}), we selected fixed resolutions (or band-widths) for the KDEs.
-In mass, the band-width of $0.02\, M_\odot$, was larger than the uncertainties of 24 of 73 stars used to construct our joint posterior.
+In mass, the band-width of $0.02\, \odot$, was larger than the uncertainties of 24 of 73 stars used to construct our joint posterior.
 For the stars with the smallest uncertainties, this significantly limits the size of the KDE being evaluated (as subsections of the full stellar models are used to evaluate individual stars, for computational efficiency).
@@
 While the 24 stars with small uncertainties do favour the WMB model, they do so very weakly, whereas the remaining 49 stars with larger uncertainties strongly favour the WMB model.
-Their removal from the total joint posterior probability does not significantly alter it from the distribution shown in Figure \ref{fig:gyroresults}.
+Their removal from the total joint posterior probability does not significantly alter it from the distribution shown in Figure 4 of the main paper.
 
@@
 Asteroseismic properties obtained through stellar models can be subject to systematic errors arising from differences in input physics and choice of stellar models not included in the reported statistical uncertainties.
-A quantification of these different systematic effects can be found in the `Kages' catalogue paper \cite{m_silvaaguirre+2015}.
+A quantification of these different systematic effects can be found in the `Kages' catalogue paper \cite{silvaaguirre+2015}.
 Combining their reported median systematic uncertainties due to input physics results in median uncertainties of $20\%$ (up from $14\%)$ on age and $5\%$ (up from $3\%$) on mass for the `Kages' sample.
@@
 For stars to be good probes of existing gyrochronology relations, their rotational evolution must occur in isolation.
-If a star interacts with a close binary companion (through tides, or a merger) the natural angular momentum loss can be disturbed, causing gyrochronology to mispredict ages \cite{m_leiner+2019, m_fleming+2019}.
+If a star interacts with a close binary companion (through tides, or a merger) the natural angular momentum loss can be disturbed, causing gyrochronology to mispredict ages \cite{leiner+2019, fleming+2019}.
 Between LEGACY and Kages, we have 8 known binaries.
@@
 
-Second, the binary pairs of KIC 9139151 \& 9139163 and 16 Cyg A \& B are individually observed binary components with wide orbital separations, so we do not expect their binarity to have affected their rotational evolution \cite{m_halbwachs1986, m_white+2013}.
+Second, the binary pairs of KIC 9139151 \& 9139163 and 16 Cyg A \& B are individually observed binary components with wide orbital separations, so we do not expect their binarity to have affected their rotational evolution \cite{halbwachs1986, white+2013}.
 
-While we chose not to account for star-planet tidal interactions in this work, we note that this may disturb the natural stellar rotational evolution when tidal forces are at play \cite{m_maxted+2015,m_gallet+delorme2019, m_benbakoura+2019}, although this has been disputed by observations of asteroseismic planet hosts \cite{m_ceillier+2016}.\\
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{Images/priors.jpg}
-	\caption{\textbf{Comparisons between posterior estimates of rotational parameters (data points and error bars) and the priors on these parameters (shaded regions).} The data are sorted from young stars (left) to old (right).
-Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$).
-Both the prior and values for $P$ are a transformation of the upper two parameters (see \textbf{Methods} and \textbf{Supplementary Information}).
-In all cases, the extent of the error bars and shaded regions indicate the 68\% credible interval of the posterior and prior distributions respectively.
-The solid lines indicate the median of the prior distributions.
-In this figure, results with means and errorbars that closely resemble the prior distribution can be interpreted as prior-dominated (i.e.
-poorly informed by the data).
-All stars are sorted and coloured and sorted by age.
-In the case of inclination angle $i$ and rotation period $P$, the displayed priors are transformed from the priors imposed on the sampled parameters from which their posteriors were derived.}
-	\label{fig:priors}
-\end{figure}
-
-\begin{figure*}[h!]
-	\centering
-	\includegraphics[width=\textwidth]{Images/litcomp_alt2.jpg}
-	\caption{\textbf{Comparisons between posterior estimates of rotational parameters from this work and the literature}.
-Literature values are taken from LEGACY and `Kages' \cite[private communication]{m_davies+2016, m_lund+2017}.
-Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$).
-Fractional differences are plotted against stellar rotation obtained in this work.
-The $\Delta$ indicates the fractional difference between this work and the literature (i.e.
-stars above the zero-line have higher values in this work).
-The right hand panels the distribution of the fractional differences around the zero line.
-The colour legend is consistent throughout all panels.
-The x-axis units on the right hand panels are equivalent to the y-axis of the left hand panels.
-10 stars have been omitted from this plot and are discussed in more detail in \textbf{Methods}: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have extremely low rotation periods in Kages, with high uncertainties.
-Conversely, KICs 6603624, 8760414 and 8938364 have extremely high rotation periods in LEGACY with low uncertainties.
-Error bars represent the 68\% confidence intervals.
-In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
-	\label{fig:legacykages}
-\end{figure*}
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=0.8\textwidth]{Images/seis_comparison_rot_alt2.jpg}
-	\caption{\textbf{Fractional differences between posterior estimates of asteroseismic rotation period from this work.} Literature sources are: Davies et al.
-(2015) \cite{m_davies+2015} (16 Cyg A \& B), Nielsen et al.
-(2015) \cite{m_nielsen+2015} (5 stars) and Benomar et al.
-(2018) \cite{m_benomar+2018} (40 stars).
-We used the reported parameter $a_{1}$ from the latter, which represents the rotational splitting in the case of uniform latitudinal rotation in their model.
-The dashed line represents the median of the sample shown, with the dotted lines representing the $15.9^{\rm{th}}$ and $84.1^{\rm{st}}$ percentiles.
-Error bars represent the 68\% confidence intervals.
-In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
-	\label{fig:literaturecomp}
-\end{figure}
-
-\begin{figure*}[h!]
-	\centering
-	\includegraphics[width=\textwidth]{Images/vsini_comparison_new.jpg}
-	\caption{\textbf{Comparisons between asteroseismic and spectroscopic measures of projected surface rotation, $\textrm{v}\sin(i)$.} All asteroseismic (x-axis) values are from this work, all spectroscopic (y-axis) values are from the literature.
-\textit{Left}: comparisons to 81 stars values reported in LEGACY and Kages.
-\textit{Right}: comparisons to 16 stars observed by Benomar et al.
-(2015) \cite{m_benomar+2015}.
-Asteroseismic values are transformed from projected splitting ($\nu_s\sin(i)$) using the asteroseismic radius measurements presented in LEGACY and `Kages'.
-Horizontal error bars represent the 68\% confidence intervals.
-Vertical error bars represent the formal uncertainty on the published spectroscopic values.
-The solid lines indicate the 1:1 line, while the dash-dotted lines represent the 2:1 and 1:2 lines.
-The dashed lines indicate the location of $\textrm{v}\sin(i) = 5\, \rm{kms^{-1}}$, the point at which surface and seismic measures of projected rotation begin to differ strongly \cite{m_tayar+2015}.}
-	\label{fig:vsinilit}
-\end{figure*}
+While we chose not to account for star-planet tidal interactions in this work, we note that this may disturb the natural stellar rotational evolution when tidal forces are at play \cite{maxted+2015, gallet+delorme2019, benbakoura+2019}, although this has been disputed by observations of asteroseismic planet hosts \cite{ceillier+2016}.\\
 
@@
 
-\begin{thebibliography}{10}
-	\expandafter\ifx\csname url\endcsname\relax
-	\def\url#1{\texttt{#1}}\fi
-	\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-	\providecommand{\bibinfo}[2]{#2}
-	\providecommand{\eprint}[2][]{\url{#2}}
-
-	\bibitem{davies+2015}
-	\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
-	\newblock \bibinfo{title}{Asteroseismic inference on rotation, gyrochronology
-		and planetary system dynamics of 16 {{Cygni}}}.
-	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-			Society}} \textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959}
-	(\bibinfo{year}{2015}).
-
-	\bibitem{chaplin+2011}
-	\bibinfo{author}{Chaplin, W.~J.} \emph{et~al.}
-	\newblock \bibinfo{title}{Ensemble {{Asteroseismology}} of {{Solar}}-{{Type
-				Stars}} with the {{NASA Kepler Mission}}}.
-	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{332}},
-	\bibinfo{pages}{213} (\bibinfo{year}{2011}).
-
-	\bibitem{harvey1985}
-	\bibinfo{author}{Harvey, J.}
-	\newblock \bibinfo{title}{High-{{Resolution Helioseismology}}}.
-	\newblock \emph{\bibinfo{journal}{Future Missions in Solar, Heliospheric \&
-			Space Plasma Physics}} \textbf{\bibinfo{volume}{235}}, \bibinfo{pages}{199}
-	(\bibinfo{year}{1985}).
-
-	\bibitem{chaplin+basu2017}
-	\bibinfo{author}{Chaplin, W.~J.} \& \bibinfo{author}{Basu}.
-	\newblock \emph{\bibinfo{title}{Asteroseismic {{Data Analysis}}:
-			{{Foundations}} and {{Techniques}}}} (\bibinfo{publisher}{{Princeton
-			University Press}}, \bibinfo{address}{{Princeton, New Jersey}},
-	\bibinfo{year}{2017}), \bibinfo{edition}{1st} edn.
-
-	\bibitem{davies+2016}
-	\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
-	\newblock \bibinfo{title}{Oscillation frequencies for 35 {{Kepler}} solar-type
-		planet-hosting stars using {{Bayesian}} techniques and machine learning}.
-	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-			Society}} \textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183}
-	(\bibinfo{year}{2016}).
-
-	\bibitem{lund+2017}
-	\bibinfo{author}{Lund, M.~N.} \emph{et~al.}
-	\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
-		{{Kepler Asteroseismic LEGACY Sample}}. {{I}}. {{Oscillation Mode
-				Parameters}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-	\textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{172} (\bibinfo{year}{2017}).
-
-	\bibitem{tassoul1980}
-	\bibinfo{author}{Tassoul, M.}
-	\newblock \bibinfo{title}{Asymptotic approximations for stellar nonradial
-		pulsations}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
-	\textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{469} (\bibinfo{year}{1980}).
-
-	\bibitem{vrard+2016}
-	\bibinfo{author}{Vrard, M.}, \bibinfo{author}{Mosser, B.} \&
-	\bibinfo{author}{Samadi, R.}
-	\newblock \bibinfo{title}{Period spacings in red giants. {{II}}. {{Automated}}
-		measurement}.
-	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
-	\textbf{\bibinfo{volume}{588}}, \bibinfo{pages}{A87} (\bibinfo{year}{2016}).
-
-	\bibitem{hogg2012}
-	\bibinfo{author}{Hogg, D.~W.}
-	\newblock \bibinfo{title}{Data analysis recipes: {{Probability}} calculus for
-		inference}.
-	\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
-	\bibinfo{pages}{arXiv:1205.4446} (\bibinfo{year}{2012}).
-
-	\bibitem{hall+2019}
-	\bibinfo{author}{Hall, O.~J.} \emph{et~al.}
-	\newblock \bibinfo{title}{Testing asteroseismology with {{Gaia DR2}}:
-		{{Hierarchical}} models of the {{Red Clump}}}.
-	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-			Society}} \textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{3569--3585}
-	(\bibinfo{year}{2019}).
-	\newblock \eprint{1904.07919}.
-
-	\bibitem{mazumdar+2014}
-	\bibinfo{author}{Mazumdar, A.} \emph{et~al.}
-	\newblock \bibinfo{title}{Measurement of acoustic glitches in solar-type stars
-		from oscillation frequencies observed by {{Kepler}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-	\textbf{\bibinfo{volume}{782}}, \bibinfo{pages}{18} (\bibinfo{year}{2014}).
-	\newblock \eprint{1312.4907}.
-
-	\bibitem{davies+2014}
-	\bibinfo{author}{Davies, G.~R.}, \bibinfo{author}{Chaplin, W.~J.},
-	\bibinfo{author}{Elsworth, Y.} \& \bibinfo{author}{Hale, S.~J.}
-	\newblock \bibinfo{title}{{{BiSON}} data preparation: A correction for
-		differential extinction and the weighted averaging of contemporaneous data}.
-	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-			Society}} \textbf{\bibinfo{volume}{441}}, \bibinfo{pages}{3009--3017}
-	(\bibinfo{year}{2014}).
-
-	\bibitem{appourchaux+2016}
-	\bibinfo{author}{Appourchaux, T.} \emph{et~al.}
-	\newblock \bibinfo{title}{Oscillation mode linewidths and heights of 23
-		main-sequence stars observed by {{{\emph{Kepler}}}}
-		{\emph{(}}{{{\emph{Corrigendum}}}}{\emph{)}}}.
-	\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
-	\textbf{\bibinfo{volume}{595}}, \bibinfo{pages}{C2} (\bibinfo{year}{2016}).
-
-	\bibitem{rasmussen+williams2006}
-	\bibinfo{author}{Rasmussen, C.~E.} \& \bibinfo{author}{Williams, C. K.~I.}
-	\newblock \emph{\bibinfo{title}{Gaussian Processes for Machine Learning}}.
-	\newblock Adaptive Computation and Machine Learning (\bibinfo{publisher}{{MIT
-			Press}}, \bibinfo{address}{{Cambridge, Mass}}, \bibinfo{year}{2006}).
-
-	\bibitem{toutain+appourchaux1994}
-	\bibinfo{author}{Toutain, T.} \& \bibinfo{author}{Appourchaux, T.}
-	\newblock \bibinfo{title}{Maximum likelihood estimators: {{An}} application to
-		the estimation of the precision of helioseismic measurements}.
-	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
-	\textbf{\bibinfo{volume}{289}}, \bibinfo{pages}{649--658}
-	(\bibinfo{year}{1994}).
-
-	\bibitem{gizon+solanki2003}
-	\bibinfo{author}{Gizon, L.} \& \bibinfo{author}{Solanki, S.~K.}
-	\newblock \bibinfo{title}{Determining the {{Inclination}} of the {{Rotation
-				Axis}} of a {{Sun}}-like {{Star}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-	\textbf{\bibinfo{volume}{589}}, \bibinfo{pages}{1009} (\bibinfo{year}{2003}).
-
-	\bibitem{handberg+campante2011}
-	\bibinfo{author}{Handberg, R.} \& \bibinfo{author}{Campante, T.~L.}
-	\newblock \bibinfo{title}{Bayesian peak-bagging of solar-like oscillators using
-		{{MCMC}}: A comprehensive guide}.
-	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
-	\textbf{\bibinfo{volume}{527}}, \bibinfo{pages}{A56} (\bibinfo{year}{2011}).
-
-	\bibitem{woodard1984}
-	\bibinfo{author}{Woodard, M.~F.}
-	\newblock \emph{\bibinfo{title}{Short-{{Period Oscillations}} in the {{Total
-					Solar Irradiance}}.}}
-	\newblock Ph.D. thesis (\bibinfo{year}{1984}).
-
-	\bibitem{anderson+1990}
-	\bibinfo{author}{Anderson, E.~R.}, \bibinfo{author}{Duvall, T.~L.} \&
-	\bibinfo{author}{Jefferies, S.~M.}
-	\newblock \bibinfo{title}{Modeling of {{Solar Oscillation Power Spectra}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-	\textbf{\bibinfo{volume}{364}}, \bibinfo{pages}{699} (\bibinfo{year}{1990}).
-
-	\bibitem{vanhoey+2013}
-	\bibinfo{author}{Van~Hoey, S.}, \bibinfo{author}{{van der Kwast}, J.},
-	\bibinfo{author}{Nopens, I.} \& \bibinfo{author}{Seuntjens, P.}
-	\newblock \bibinfo{title}{Python package for model {{STructure ANalysis}}
-		({{pySTAN}})}.
-	\newblock \emph{\bibinfo{journal}{EGU General Assembly Conference Abstracts}}
-	\textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{EGU2013--10059}
-	(\bibinfo{year}{2013}).
-
-	\bibitem{salvatier+2016}
-	\bibinfo{author}{Salvatier, J.}, \bibinfo{author}{Wiecki, T.~V.} \&
-	\bibinfo{author}{Fonnesbeck, C.}
-	\newblock \bibinfo{title}{Probabilistic programming in {{Python}} using
-		{{PyMC3}}}.
-	\newblock \emph{\bibinfo{journal}{PeerJ Computer Science}}
-	\textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{e55} (\bibinfo{year}{2016}).
-
-	\bibitem{gelman2006}
-	\bibinfo{author}{Gelman, A.}
-	\newblock \bibinfo{title}{Prior distributions for variance parameters in
-		hierarchical models (comment on article by {{Browne}} and {{Draper}})}.
-	\newblock \emph{\bibinfo{journal}{Bayesian Analysis}}
-	\textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{515--534}
-	(\bibinfo{year}{2006}).
-
-	\bibitem{ballot+2006}
-	\bibinfo{author}{Ballot, J.}, \bibinfo{author}{Garcia, R.~A.} \&
-	\bibinfo{author}{Lambert, P.}
-	\newblock \bibinfo{title}{Rotation speed and stellar axis inclination from p
-		modes: How {{CoRoT}} would see other suns}.
-	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-			Society}} \textbf{\bibinfo{volume}{369}}, \bibinfo{pages}{1281--1286}
-	(\bibinfo{year}{2006}).
-
-	\bibitem{ballot+2008a}
-	\bibinfo{author}{Ballot, J.}, \bibinfo{author}{Appourchaux, T.},
-	\bibinfo{author}{Toutain, T.} \& \bibinfo{author}{Guittet, M.}
-	\newblock \bibinfo{title}{On deriving p-mode parameters for inclined solar-like
-		stars}.
-	\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
-	\textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{867--875}
-	(\bibinfo{year}{2008}).
-	\newblock \eprint{0803.0885}.
-
-	\bibitem{kass+raftery1995}
-	\bibinfo{author}{Kass, R.~E.} \& \bibinfo{author}{Raftery, A.~E.}
-	\newblock \bibinfo{title}{Bayes {{Factors}}}.
-	\newblock \emph{\bibinfo{journal}{Journal of the American Statistical
-			Association}} \textbf{\bibinfo{volume}{90}}, \bibinfo{pages}{773--795}
-	(\bibinfo{year}{1995}).
-
-	\bibitem{silvaaguirre+2017}
-	\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
-	\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
-		{{Kepler Asteroseismic LEGACY Sample}}. {{II}}.{{Radii}}, {{Masses}}, and
-		{{Ages}}}.
-	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
-	\textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{173} (\bibinfo{year}{2017}).
-
-		\bibitem{silvaaguirre+2015}
-	\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
-	\newblock \bibinfo{title}{Ages and fundamental properties of {{Kepler}}
-		exoplanet host stars from asteroseismology}.
-	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
-			Society}} \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2127}
-	(\bibinfo{year}{2015}).
-
-\end{thebibliography}
+\bibliographystyle{naturemag}
+\bibliography{library.bib} % if your bibtex file is called example.bib
 

### 2021-02-16 paper/natastron/Publication/Send/bblpaper.tex
prepped upload

--- 2021-02-15 paper/natastron/Publication/bblpaper.tex
@@
 	\bibitem{barnes2007}
-	\bibinfo{author}{Barnes, S.~A.}
-	\newblock \bibinfo{title}{Ages for {{Illustrative Field Stars Using
-				Gyrochronology}}: {{Viability}}, {{Limitations}}, and {{Errors}}}.
+	\bibinfo{author}{{Barnes}, S.~A.}
+	\newblock \bibinfo{title}{{Ages for Illustrative Field Stars Using
+	  Gyrochronology: Viability, Limitations, and Errors}}.
 	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
-	\textbf{\bibinfo{volume}{669}}, \bibinfo{pages}{1167} (\bibinfo{year}{2007}).
+	  \textbf{\bibinfo{volume}{669}}, \bibinfo{pages}{1167--1189}
+	  (\bibinfo{year}{2007}).
+	\newblock \eprint{0704.3068}.
 
 	\bibitem{meibom+2015}
-	\bibinfo{author}{Meibom, S.} \emph{et~al.}
-	\newblock \bibinfo{title}{A spin-down clock for cool stars from observations of
-		a 2.5-billion-year-old cluster}.
+	\bibinfo{author}{{Meibom}, S.} \emph{et~al.}
+	\newblock \bibinfo{title}{{A spin-down clock for cool stars from observations
+	  of a 2.5-billion-year-old cluster}}.
 	\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{517}},
-	\bibinfo{pages}{589} (\bibinfo{year}{2015}).
+	  \bibinfo{pages}{589--591} (\bibinfo{year}{2015}).
+	\newblock \eprint{1501.05651}.
 
 	\bibitem{leiner+2019}
-	\bibinfo{author}{Leiner, E.}, \bibinfo{author}{Mathieu, R.~D.},
-	\bibinfo{author}{Vanderburg, A.}, \bibinfo{author}{Gosnell, N.~M.} \&
-	\bibinfo{author}{Smith, J.~C.}
-	\newblock \bibinfo{title}{Blue {{Lurkers}}: {{Hidden Blue Stragglers}} on the
-		{{M67 Main Sequence Identified}} from {{Their Kepler}}/{{K2 Rotation
-				Periods}}}.
+	\bibinfo{author}{{Leiner}, E.}, \bibinfo{author}{{Mathieu}, R.~D.},
+	  \bibinfo{author}{{Vanderburg}, A.}, \bibinfo{author}{{Gosnell}, N.~M.} \&
+	  \bibinfo{author}{{Smith}, J.~C.}
+	\newblock \bibinfo{title}{{Blue Lurkers: Hidden Blue Stragglers on the M67 Main
+	  Sequence Identified from Their Kepler/K2 Rotation Periods}}.
 	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
 	  \textbf{\bibinfo{volume}{881}}, \bibinfo{pages}{47} (\bibinfo{year}{2019}).
+	\newblock \eprint{1904.02169}.
 
@@
 	\bibitem{silvaaguirre+2015}
-	\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
-	\newblock \bibinfo{title}{Ages and fundamental properties of {{Kepler}}
-		exoplanet host stars from asteroseismology}.
+	\bibinfo{author}{{Silva Aguirre}, V.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Ages and fundamental properties of Kepler exoplanet
+	  host stars from asteroseismology}}.
 	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
-	\textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2127} (\bibinfo{year}{2015}).
+	  \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2127--2148}
+	  (\bibinfo{year}{2015}).
+	\newblock \eprint{1504.07992}.
 
 	\bibitem{angus+2015}
-	\bibinfo{author}{Angus, R.}, \bibinfo{author}{Aigrain, S.},
-	\bibinfo{author}{{Foreman-Mackey}, D.} \& \bibinfo{author}{McQuillan, A.}
-	\newblock \bibinfo{title}{Calibrating gyrochronology using {{Kepler}}
-		asteroseismic targets}.
+	\bibinfo{author}{{Angus}, R.}, \bibinfo{author}{{Aigrain}, S.},
+	  \bibinfo{author}{{Foreman-Mackey}, D.} \& \bibinfo{author}{{McQuillan}, A.}
+	\newblock \bibinfo{title}{{Calibrating gyrochronology using Kepler
+	  asteroseismic targets}}.
 	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
-	\textbf{\bibinfo{volume}{450}}, \bibinfo{pages}{1787} (\bibinfo{year}{2015}).
+	  \textbf{\bibinfo{volume}{450}}, \bibinfo{pages}{1787--1798}
+	  (\bibinfo{year}{2015}).
+	\newblock \eprint{1502.06965}.
 
@@
 	\bibitem{davies+2015}
-	\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
-	\newblock \bibinfo{title}{Asteroseismic inference on rotation, gyrochronology
-		and planetary system dynamics of 16 {{Cygni}}}.
+	\bibinfo{author}{{Davies}, G.~R.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Asteroseismic inference on rotation, gyrochronology
+	  and planetary system dynamics of 16 Cygni}}.
 	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
-	\textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959} (\bibinfo{year}{2015}).
+	  \textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959--2966}
+	  (\bibinfo{year}{2015}).
+	\newblock \eprint{1411.1359}.
 
@@
 	\bibinfo{author}{{van Saders}, J.~L.} \emph{et~al.}
-	\newblock \bibinfo{title}{Weakened magnetic braking as the origin of
-		anomalously rapid rotation in old field stars}.
+	\newblock \bibinfo{title}{{Weakened magnetic braking as the origin of
+	  anomalously rapid rotation in old field stars}}.
 	\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{529}},
-	\bibinfo{pages}{181} (\bibinfo{year}{2016}).
+	  \bibinfo{pages}{181--184} (\bibinfo{year}{2016}).
+	\newblock \eprint{1601.02631}.
 
@@
 	\bibitem{davies+2016}
-	\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
-	\newblock \bibinfo{title}{Oscillation frequencies for 35 {{Kepler}} solar-type
-		planet-hosting stars using {{Bayesian}} techniques and machine learning}.
+	\bibinfo{author}{{Davies}, G.~R.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Oscillation frequencies for 35 Kepler solar-type
+	  planet-hosting stars using Bayesian techniques and machine learning}}.
 	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
-	\textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183} (\bibinfo{year}{2016}).
+	  \textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183--2195}
+	  (\bibinfo{year}{2016}).
+	\newblock \eprint{1511.02105}.
 
@@
 	\bibitem{benomar+2018}
-	\bibinfo{author}{Benomar, O.} \emph{et~al.}
-	\newblock \bibinfo{title}{Asteroseismic detection of latitudinal differential
-		rotation in 13 {{Sun}}-like stars}.
+	\bibinfo{author}{{Benomar}, O.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Asteroseismic detection of latitudinal differential
+	  rotation in 13 Sun-like stars}}.
 	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{361}},
-	\bibinfo{pages}{1231} (\bibinfo{year}{2018}).
+	  \bibinfo{pages}{1231--1234} (\bibinfo{year}{2018}).
+	\newblock \eprint{1809.07938}.
 
@@
 	\bibinfo{author}{{Lorenzo-Oliveira}, D.} \emph{et~al.}
-	\newblock \bibinfo{title}{Constraining the evolution of stellar rotation using
-		solar twins}.
+	\newblock \bibinfo{title}{{Constraining the evolution of stellar rotation using
+	  solar twins}}.
 	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
-	\textbf{\bibinfo{volume}{485}}, \bibinfo{pages}{L68} (\bibinfo{year}{2019}).
+	  \textbf{\bibinfo{volume}{485}}, \bibinfo{pages}{L68--L72}
+	  (\bibinfo{year}{2019}).
+	\newblock \eprint{1903.02630}.
 
@@
 	\bibitem{barnes2010}
-	\bibinfo{author}{Barnes, S.~A.}
-	\newblock \bibinfo{title}{A {{Simple Nonlinear Model}} for the {{Rotation}} of
-		{{Main}}-sequence {{Cool Stars}}. {{I}}. {{Introduction}}, {{Implications}}
-		for {{Gyrochronology}}, and {{Color}}-{{Period Diagrams}}}.
+	\bibinfo{author}{{Barnes}, S.~A.}
+	\newblock \bibinfo{title}{{A Simple Nonlinear Model for the Rotation of
+	  Main-sequence Cool Stars. I. Introduction, Implications for Gyrochronology,
+	  and Color-Period Diagrams}}.
 	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
-	\textbf{\bibinfo{volume}{722}}, \bibinfo{pages}{222} (\bibinfo{year}{2010}).
+	  \textbf{\bibinfo{volume}{722}}, \bibinfo{pages}{222--234}
+	  (\bibinfo{year}{2010}).
 

### 2021-02-16 paper/natastron/Publication/coverletter.tex
done coverletter

--- 2020-10-09 paper/natastron/response/coverletter.tex
@@
 \usepackage[utf8]{inputenc}
-\usepackage{enumitem}
+%\usepackage{enumitem}
 \usepackage[left=1in, right=1in, bottom=0.5in, top=0.5in]{geometry}
@@
 
-We hope this letter finds you well.
-We have completed our response to the reviewer, which is attached below this cover letter (and uploaded separately with resubmission).
-Based on our discussion over email on the reformatting of the original draft, we have done our best to reshuffle the paper's contents.
-We think the updated draft best matches the Nature format while keeping it accessible to the reader.
-However the Methods is longer than conventional, so please let us know if you have any suggestions on what we should move to the Supplementary Information, if necessary.
+We have made the requested changes, including those discussed over email, to the best of my ability. Please don't hesitate to get in touch if anything is missing!
 
-We have also added data and code availability statements.
-At the moment, our main results table is in Extended Data, as we don't think it is necessary to include it in the main text.
-Ideally we would publish this table digitally along with the article (as well as host it on Vizier).
-If you have any input on whether this table should be (partially) included in the main text, we would be grateful also.
+For the purposes of advertising this work on Twitter, my handle is @asteronomer.
 
-The word count breakdown is as follows:
+Those of other authors involved (that have Twitter) are:
 \begin{itemize}
-	\item Abstract: 196
-	\item Introduction: 500
-	\item Main body (incl. Introduction): 2721
-	\item Methods: 5145
-	\item Supplementary Information: 2544
-	\item Extended Data: Figures and Table only.
+	\item Guy R. Davies: @CitationWarrior\\
+	\item Mikkel N. Lund: @miklnl41\\
+	\item Saniya Khan: @rilasani\\
+	\item Victor See: @AstroVictorSee\\
+	\item Jamie Tayar: @StellarTayar\\
 \end{itemize}
 
-\vspace{0.5cm}
+I'll leave it up to you whether you want to them. The institutional handles are, in order of appearance on the manuscript:
+
+\begin{itemize}
+	\item @ESAscience\\
+	\item @unibirmingham\\
+	\item @sacscience\\
+	\item @UHIfA\\
+	\item @CEAIrfu\\
+	\item @UniofExeter\\
+\end{itemize}
 

### 2021-02-17 paper/natastron/Publication/Send/paper.tex
prepped upload
resub

--- 2021-02-15 paper/natastron/Publication/paper.tex
@@
 \usepackage[ ]{hyperref}
-\graphicspath{{Images/}}
 %\usepackage[symbol]{footmisc}
@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{data.pdf}
+	\includegraphics[width=0.6\textwidth]{data_Fig1.pdf}
 	\caption{\textbf{Our sample of 95 stars from the `Kages' and LEGACY catalogues.} Data are coloured by asteroseismic age  \cite{silvaaguirre+2015, silvaaguirre+2017}.
@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{Images/surf-seis-comparison_update.pdf}
+	\includegraphics[width=0.6\textwidth]{surf-seis-comparison_update_FIg2.pdf}
 	\caption{\textbf{Comparisons between asteroseismic and photometric measures of stellar rotation, for 48 stars.} Literature values were taken Garcia et al.
@@
 	\centering
-	\includegraphics[width=.9\textwidth]{fullsample.pdf}
+	\includegraphics[width=.9\textwidth]{fullsample_Fig3.pdf}
 	\caption{\textbf{Stars for which rotation was measured in this work, plotted over stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution.} The model populations were generated using TRILEGAL (see text) \cite{girardi+2012}.
@@
 	\centering
-	\includegraphics[width=\textwidth]{modelresults.pdf}
+	\includegraphics[width=\textwidth]{modelresults_Fig4.pdf}
 	\caption{\textbf{Posterior estimates of the mixture model parameter $Q_{\rm WMB}$, broken down by stellar classification.} A value of $Q_{\rm WMB}$ close to 1 indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 0 indicates that the data are more consistent with a standard rotational evolution scenario.
@@
 
-\input{bblpaper.tex}
-%\bibliographystyle{naturemag}
-%\bibliography{library.bib} % if your bibtex file is called example.bib
+\begin{thebibliography}{10}
+	\expandafter\ifx\csname url\endcsname\relax
+	\def\url#1{\texttt{#1}}\fi
+	\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+	\providecommand{\bibinfo}[2]{#2}
+	\providecommand{\eprint}[2][]{\url{#2}}
 
-\newpage
+	\bibitem{barnes2007}
+	\bibinfo{author}{{Barnes}, S.~A.}
+	\newblock \bibinfo{title}{{Ages for Illustrative Field Stars Using
+			Gyrochronology: Viability, Limitations, and Errors}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{669}}, \bibinfo{pages}{1167--1189}
+	(\bibinfo{year}{2007}).
+	\newblock \eprint{0704.3068}.
+
+	\bibitem{meibom+2015}
+	\bibinfo{author}{{Meibom}, S.} \emph{et~al.}
+	\newblock \bibinfo{title}{{A spin-down clock for cool stars from observations
+			of a 2.5-billion-year-old cluster}}.
+	\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{517}},
+	\bibinfo{pages}{589--591} (\bibinfo{year}{2015}).
+	\newblock \eprint{1501.05651}.
+
+	\bibitem{leiner+2019}
+	\bibinfo{author}{{Leiner}, E.}, \bibinfo{author}{{Mathieu}, R.~D.},
+	\bibinfo{author}{{Vanderburg}, A.}, \bibinfo{author}{{Gosnell}, N.~M.} \&
+	\bibinfo{author}{{Smith}, J.~C.}
+	\newblock \bibinfo{title}{{Blue Lurkers: Hidden Blue Stragglers on the M67 Main
+			Sequence Identified from Their Kepler/K2 Rotation Periods}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{881}}, \bibinfo{pages}{47} (\bibinfo{year}{2019}).
+	\newblock \eprint{1904.02169}.
+
+	\bibitem{claytor+2019}
+	\bibinfo{author}{{Claytor}, Z.~R.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Chemical Evolution in the Milky Way: Rotation-based
+			Ages for APOGEE-Kepler Cool Dwarf Stars}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{888}}, \bibinfo{pages}{43} (\bibinfo{year}{2020}).
+	\newblock \eprint{1911.04518}.
+
+	\bibitem{barnes+2016}
+	\bibinfo{author}{Barnes, S.~A.}, \bibinfo{author}{Weingrill, J.},
+	\bibinfo{author}{Fritzewski, D.}, \bibinfo{author}{Strassmeier, K.~G.} \&
+	\bibinfo{author}{Platais, I.}
+	\newblock \bibinfo{title}{Rotation {{Periods}} for {{Cool Stars}} in the 4
+		{{Gyr}} old {{Open Cluster M67}}, {{The Solar}}-{{Stellar Connection}}, and
+		the {{Applicability}} of {{Gyrochronology}} to at least {{Solar Age}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{823}}, \bibinfo{pages}{16} (\bibinfo{year}{2016}).
+
+	\bibitem{borucki+2010}
+	\bibinfo{author}{Borucki, W.~J.}, \bibinfo{author}{Koch, D.} \&
+	\bibinfo{author}{Team, K.~S.}
+	\newblock \bibinfo{title}{Kepler {{Planet Detection Mission}}: {{Highlights}}
+		of the {{First Results}}}.
+	\newblock \emph{\bibinfo{journal}{AAS/Division for Planetary Sciences Meeting
+			Abstracts \#42}} \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{47.03}
+	(\bibinfo{year}{2010}).
+
+	\bibitem{silvaaguirre+2015}
+	\bibinfo{author}{{Silva Aguirre}, V.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Ages and fundamental properties of Kepler exoplanet
+			host stars from asteroseismology}}.
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2127--2148}
+	(\bibinfo{year}{2015}).
+	\newblock \eprint{1504.07992}.
+
+	\bibitem{angus+2015}
+	\bibinfo{author}{{Angus}, R.}, \bibinfo{author}{{Aigrain}, S.},
+	\bibinfo{author}{{Foreman-Mackey}, D.} \& \bibinfo{author}{{McQuillan}, A.}
+	\newblock \bibinfo{title}{{Calibrating gyrochronology using Kepler
+			asteroseismic targets}}.
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{450}}, \bibinfo{pages}{1787--1798}
+	(\bibinfo{year}{2015}).
+	\newblock \eprint{1502.06965}.
+
+	\bibitem{nielsen+2015}
+	\bibinfo{author}{Nielsen, M.~B.}, \bibinfo{author}{Schunker, H.},
+	\bibinfo{author}{Gizon, L.} \& \bibinfo{author}{Ball, W.~H.}
+	\newblock \bibinfo{title}{Constraining differential rotation of {{Sun}}-like
+		stars from asteroseismic and starspot rotation periods}.
+	\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+	\textbf{\bibinfo{volume}{582}}, \bibinfo{pages}{A10} (\bibinfo{year}{2015}).
+
+	\bibitem{davies+2015}
+	\bibinfo{author}{{Davies}, G.~R.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Asteroseismic inference on rotation, gyrochronology
+			and planetary system dynamics of 16 Cygni}}.
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959--2966}
+	(\bibinfo{year}{2015}).
+	\newblock \eprint{1411.1359}.
+
+	\bibitem{vansaders+2016}
+	\bibinfo{author}{{van Saders}, J.~L.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Weakened magnetic braking as the origin of
+			anomalously rapid rotation in old field stars}}.
+	\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{529}},
+	\bibinfo{pages}{181--184} (\bibinfo{year}{2016}).
+	\newblock \eprint{1601.02631}.
+
+	\bibitem{reville+2015}
+	\bibinfo{author}{{R{\'e}ville}, V.}, \bibinfo{author}{{Brun}, A.~S.},
+	\bibinfo{author}{{Matt}, S.~P.}, \bibinfo{author}{{Strugarek}, A.} \&
+	\bibinfo{author}{{Pinto}, R.~F.}
+	\newblock \bibinfo{title}{{The Effect of Magnetic Topology on Thermally Driven
+			Wind: Toward a General Formulation of the Braking Law}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{798}}, \bibinfo{pages}{116} (\bibinfo{year}{2015}).
+	\newblock \eprint{1410.8746}.
+
+	\bibitem{garraffo+2016}
+	\bibinfo{author}{Garraffo, C.}, \bibinfo{author}{Drake, J.~J.} \&
+	\bibinfo{author}{Cohen, O.}
+	\newblock \bibinfo{title}{The {{Missing Magnetic Morphology Term}} in {{Stellar
+				Rotation Evolution}}}.
+	\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
+	\textbf{\bibinfo{volume}{595}}, \bibinfo{pages}{A110} (\bibinfo{year}{2016}).
+	\newblock \eprint{1607.06096}.
+
+	\bibitem{metcalfe+2016}
+	\bibinfo{author}{Metcalfe, T.~S.}, \bibinfo{author}{Egeland, R.} \&
+	\bibinfo{author}{{van Saders}, J.}
+	\newblock \bibinfo{title}{Stellar {{Evidence That}} the {{Solar Dynamo May Be}}
+		in {{Transition}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J. Letters}}
+	\textbf{\bibinfo{volume}{826}}, \bibinfo{pages}{L2} (\bibinfo{year}{2016}).
+
+	\bibitem{metcalfe+2019}
+	\bibinfo{author}{{Metcalfe}, T.~S.} \emph{et~al.}
+	\newblock \bibinfo{title}{{LBT/PEPSI Spectropolarimetry of a Magnetic
+			Morphology Shift in Old Solar-type Stars}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{887}}, \bibinfo{pages}{L38} (\bibinfo{year}{2019}).
+	\newblock \eprint{1912.01186}.
+
+	\bibitem{see+2019}
+	\bibinfo{author}{See, V.} \emph{et~al.}
+	\newblock \bibinfo{title}{Do {{Non}}-dipolar {{Magnetic Fields Contribute}} to
+		{{Spin}}-down {{Torques}}?}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{886}}, \bibinfo{pages}{120} (\bibinfo{year}{2019}).
+
+	\bibitem{mcquillan+2014}
+	\bibinfo{author}{McQuillan, A.}, \bibinfo{author}{Mazeh, T.} \&
+	\bibinfo{author}{Aigrain, S.}
+	\newblock \bibinfo{title}{Rotation {{Periods}} of 34,030 {{Kepler
+				Main}}-{{Sequence Stars}}: {{The Full Autocorrelation Sample}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
+	\textbf{\bibinfo{volume}{211}}, \bibinfo{pages}{24} (\bibinfo{year}{2014}).
+	\newblock \eprint{1402.5694}.
+
+	\bibitem{matt+2015}
+	\bibinfo{author}{Matt, S.~P.}, \bibinfo{author}{Brun, A.~S.},
+	\bibinfo{author}{Baraffe, I.}, \bibinfo{author}{Bouvier, J.} \&
+	\bibinfo{author}{Chabrier, G.}
+	\newblock \bibinfo{title}{The {{Mass}}-dependence of {{Angular Momentum
+				Evolution}} in {{Sun}}-like {{Stars}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{799}}, \bibinfo{pages}{L23} (\bibinfo{year}{2015}).
+
+	\bibitem{reinhold+2020}
+	\bibinfo{author}{{Reinhold}, T.} \emph{et~al.}
+	\newblock \bibinfo{title}{{The Sun is less active than other solar-like
+			stars}}.
+	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{368}},
+	\bibinfo{pages}{518--521} (\bibinfo{year}{2020}).
+	\newblock \eprint{2005.01401}.
+
+	\bibitem{vansaders+2019}
+	\bibinfo{author}{{van Saders}, J.~L.}, \bibinfo{author}{Pinsonneault, M.~H.} \&
+	\bibinfo{author}{Barbieri, M.}
+	\newblock \bibinfo{title}{Forward {{Modeling}} of the {{Kepler Stellar Rotation
+				Period Distribution}}: {{Interpreting Periods}} from {{Mixed}} and {{Biased
+				Stellar Populations}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{872}}, \bibinfo{pages}{128} (\bibinfo{year}{2019}).
+
+	\bibitem{ledoux1951}
+	\bibinfo{author}{Ledoux, P.}
+	\newblock \bibinfo{title}{The {{Nonradial Oscillations}} of {{Gaseous Stars}}
+		and the {{Problem}} of {{Beta Canis Majoris}}.}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{114}}, \bibinfo{pages}{373} (\bibinfo{year}{1951}).
+
+	\bibitem{davies+2016}
+	\bibinfo{author}{{Davies}, G.~R.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Oscillation frequencies for 35 Kepler solar-type
+			planet-hosting stars using Bayesian techniques and machine learning}}.
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183--2195}
+	(\bibinfo{year}{2016}).
+	\newblock \eprint{1511.02105}.
+
+	\bibitem{lund+2017}
+	\bibinfo{author}{Lund, M.~N.} \emph{et~al.}
+	\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
+		{{Kepler Asteroseismic LEGACY Sample}}. {{I}}. {{Oscillation Mode
+				Parameters}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{172} (\bibinfo{year}{2017}).
+
+	\bibitem{silvaaguirre+2017}
+	\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
+	\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
+		{{Kepler Asteroseismic LEGACY Sample}}. {{II}}.{{Radii}}, {{Masses}}, and
+		{{Ages}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{173} (\bibinfo{year}{2017}).
+
+	\bibitem{garcia+2014}
+	\bibinfo{author}{Garc{\'i}a, R.~A.} \emph{et~al.}
+	\newblock \bibinfo{title}{Rotation and magnetism of {{Kepler}} pulsating
+		solar-like stars. {{Towards}} asteroseismically calibrated age-rotation
+		relations}.
+	\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+	\textbf{\bibinfo{volume}{572}}, \bibinfo{pages}{A34} (\bibinfo{year}{2014}).
+
+	\bibitem{kraft1967}
+	\bibinfo{author}{Kraft, R.~P.}
+	\newblock \bibinfo{title}{Studies of {{Stellar Rotation}}. {{V}}. {{The
+				Dependence}} of {{Rotation}} on {{Age}} among {{Solar}}-{{Type Stars}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{150}}, \bibinfo{pages}{551} (\bibinfo{year}{1967}).
+
+	\bibitem{bedding+2010}
+	\bibinfo{author}{Bedding, T.~R.} \emph{et~al.}
+	\newblock \bibinfo{title}{Solar-like {{Oscillations}} in {{Low}}-luminosity
+		{{Red Giants}}: {{First Results}} from {{Kepler}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J. Letters}}
+	\textbf{\bibinfo{volume}{713}}, \bibinfo{pages}{L176--L181}
+	(\bibinfo{year}{2010}).
+
+	\bibitem{bonanno+frohlich2015}
+	\bibinfo{author}{Bonanno, A.} \& \bibinfo{author}{Fr{\"o}hlich, H.-E.}
+	\newblock \bibinfo{title}{A {{Bayesian}} estimation of the helioseismic solar
+		age}.
+	\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+	\textbf{\bibinfo{volume}{580}}, \bibinfo{pages}{A130} (\bibinfo{year}{2015}).
+
+	\bibitem{paxton+2017}
+	\bibinfo{author}{{Paxton}, B.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Modules for Experiments in Stellar Astrophysics
+			(MESA): Convective Boundaries, Element Diffusion, and Massive Star
+			Explosions}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
+	\textbf{\bibinfo{volume}{234}}, \bibinfo{pages}{34} (\bibinfo{year}{2018}).
+	\newblock \eprint{1710.08424}.
+
+	\bibitem{hunter2007}
+	\bibinfo{author}{Hunter, J.~D.}
+	\newblock \bibinfo{title}{Matplotlib: {{A 2D Graphics Environment}}}.
+	\newblock \emph{\bibinfo{journal}{Computing in Science and Engineering}}
+	\textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{90--95} (\bibinfo{year}{2007}).
+
+	\bibitem{benomar+2018}
+	\bibinfo{author}{{Benomar}, O.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Asteroseismic detection of latitudinal differential
+			rotation in 13 Sun-like stars}}.
+	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{361}},
+	\bibinfo{pages}{1231--1234} (\bibinfo{year}{2018}).
+	\newblock \eprint{1809.07938}.
+
+	\bibitem{lund+2014}
+	\bibinfo{author}{Lund, M.~N.}, \bibinfo{author}{Miesch, M.~S.} \&
+	\bibinfo{author}{{Christensen-Dalsgaard}, J.}
+	\newblock \bibinfo{title}{Differential rotation in main-sequence solar-like
+		stars: {{Qualitative}} inference from asteroseismic data}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{790}}, \bibinfo{pages}{121} (\bibinfo{year}{2014}).
+	\newblock \eprint{1406.7873}.
+
+	\bibitem{benomar+2015}
+	\bibinfo{author}{Benomar, O.}, \bibinfo{author}{Takata, M.},
+	\bibinfo{author}{Shibahashi, H.}, \bibinfo{author}{Ceillier, T.} \&
+	\bibinfo{author}{Garc{\'i}a, R.~A.}
+	\newblock \bibinfo{title}{Nearly uniform internal rotation of solar-like
+		main-sequence stars revealed by space-based asteroseismology and
+		spectroscopic measurements}.
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2654--2674}
+	(\bibinfo{year}{2015}).
+
+	\bibitem{gizon+2013}
+	\bibinfo{author}{Gizon, L.} \emph{et~al.}
+	\newblock \bibinfo{title}{Seismic constraints on rotation of {{Sun}}-like star
+		and mass of exoplanet}.
+	\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
+			Science}} \textbf{\bibinfo{volume}{110}}, \bibinfo{pages}{13267}
+	(\bibinfo{year}{2013}).
+
+	\bibitem{chaplin+2013}
+	\bibinfo{author}{Chaplin, W.~J.} \emph{et~al.}
+	\newblock \bibinfo{title}{Asteroseismic {{Determination}} of {{Obliquities}} of
+		the {{Exoplanet Systems Kepler}}-50 and {{Kepler}}-65}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{766}}, \bibinfo{pages}{101} (\bibinfo{year}{2013}).
+
+	\bibitem{nielsen+2013}
+	\bibinfo{author}{Nielsen, M.~B.}, \bibinfo{author}{Gizon, L.},
+	\bibinfo{author}{Schunker, H.} \& \bibinfo{author}{Karoff, C.}
+	\newblock \bibinfo{title}{Rotation periods of 12 000 main-sequence {{Kepler}}
+		stars: {{Dependence}} on stellar spectral type and comparison with v sin i
+		observations}.
+	\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+	\textbf{\bibinfo{volume}{557}}, \bibinfo{pages}{L10} (\bibinfo{year}{2013}).
+
+	\bibitem{skumanich1972}
+	\bibinfo{author}{{Skumanich}, A.}
+	\newblock \bibinfo{title}{{Time Scales for Ca II Emission Decay, Rotational
+			Braking, and Lithium Depletion}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{171}}, \bibinfo{pages}{565} (\bibinfo{year}{1972}).
+
+	\bibitem{kawaler1988}
+	\bibinfo{author}{Kawaler, S.~D.}
+	\newblock \bibinfo{title}{Angular momentum loss in low-mass stars}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{333}}, \bibinfo{pages}{236} (\bibinfo{year}{1988}).
+
+	\bibitem{girardi+2012}
+	\bibinfo{author}{Girardi, L.} \emph{et~al.}
+	\newblock \bibinfo{title}{{{TRILEGAL}}, a {{TRIdimensional modeL}} of {{thE
+				GALaxy}}: {{Status}} and {{Future}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophysics and Space Science Proceedings}}
+	\textbf{\bibinfo{volume}{26}}, \bibinfo{pages}{165} (\bibinfo{year}{2012}).
+
+	\bibitem{berger+2020}
+	\bibinfo{author}{{Berger}, T.~A.}, \bibinfo{author}{{Huber}, D.},
+	\bibinfo{author}{{Gaidos}, E.}, \bibinfo{author}{{van Saders}, J.~L.} \&
+	\bibinfo{author}{{Weiss}, L.~M.}
+	\newblock \bibinfo{title}{{The Gaia-Kepler Stellar Properties Catalog. II.
+			Planet Radius Demographics as a Function of Stellar Mass and Age}}.
+	\newblock \emph{\bibinfo{journal}{Astron. J.}} \textbf{\bibinfo{volume}{160}},
+	\bibinfo{pages}{108} (\bibinfo{year}{2020}).
+	\newblock \eprint{2005.14671}.
+
+	\bibitem{gelman+rubin1992}
+	\bibinfo{author}{Gelman, A.} \& \bibinfo{author}{Rubin, D.~B.}
+	\newblock \bibinfo{title}{Inference from {{Iterative Simulation Using Multiple
+				Sequences}}}.
+	\newblock \emph{\bibinfo{journal}{Statistical Science}}
+	\textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{457--472}
+	(\bibinfo{year}{1992}).
+
+	\bibitem{salvatier+2016}
+	\bibinfo{author}{Salvatier, J.}, \bibinfo{author}{Wiecki, T.~V.} \&
+	\bibinfo{author}{Fonnesbeck, C.}
+	\newblock \bibinfo{title}{Probabilistic programming in {{Python}} using
+		{{PyMC3}}}.
+	\newblock \emph{\bibinfo{journal}{PeerJ Computer Science}}
+	\textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{e55} (\bibinfo{year}{2016}).
+
+	\bibitem{metcalfe+egeland2019}
+	\bibinfo{author}{Metcalfe, T.~S.} \& \bibinfo{author}{Egeland, R.}
+	\newblock \bibinfo{title}{Understanding the {{Limitations}} of
+		{{Gyrochronology}} for {{Old Field Stars}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{871}}, \bibinfo{pages}{39} (\bibinfo{year}{2019}).
+	\newblock \eprint{1811.11905}.
+
+	\bibitem{lorenzo-oliveira+2019}
+	\bibinfo{author}{{Lorenzo-Oliveira}, D.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Constraining the evolution of stellar rotation using
+			solar twins}}.
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{485}}, \bibinfo{pages}{L68--L72}
+	(\bibinfo{year}{2019}).
+	\newblock \eprint{1903.02630}.
+
+	\bibitem{vansaders+pinsonneault2013}
+	\bibinfo{author}{{van Saders}, J.~L.} \& \bibinfo{author}{Pinsonneault, M.~H.}
+	\newblock \bibinfo{title}{Fast {{Star}}, {{Slow Star}}; {{Old Star}}, {{Young
+				Star}}: {{Subgiant Rotation}} as a {{Population}} and {{Stellar Physics
+				Diagnostic}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{776}}, \bibinfo{pages}{67} (\bibinfo{year}{2013}).
+
+	\bibitem{barnes2010}
+	\bibinfo{author}{{Barnes}, S.~A.}
+	\newblock \bibinfo{title}{{A Simple Nonlinear Model for the Rotation of
+			Main-sequence Cool Stars. I. Introduction, Implications for Gyrochronology,
+			and Color-Period Diagrams}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{722}}, \bibinfo{pages}{222--234}
+	(\bibinfo{year}{2010}).
+
+	\bibitem{deng+2012}
+	\bibinfo{author}{Deng, L.-C.} \emph{et~al.}
+	\newblock \bibinfo{title}{{{LAMOST Experiment}} for {{Galactic Understanding}}
+		and {{Exploration}} ({{LEGUE}}) \textemdash{} {{The}} survey's science plan}.
+	\newblock \emph{\bibinfo{journal}{Research in Astron. Astrophys.}}
+	\textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{735--754}
+	(\bibinfo{year}{2012}).
+
+	\bibitem{dejong+2014}
+	\bibinfo{author}{{de Jong}, R.~S.} \emph{et~al.}
+	\newblock \bibinfo{title}{{4MOST: 4-metre Multi-Object Spectroscopic
+			Telescope}}.
+	\newblock In \bibinfo{editor}{{Ramsay}, S.~K.}, \bibinfo{editor}{{McLean},
+		I.~S.} \& \bibinfo{editor}{{Takami}, H.} (eds.)
+	\emph{\bibinfo{booktitle}{Ground-based and Airborne Instrumentation for
+			Astronomy V}}, vol. \bibinfo{volume}{9147} of \emph{\bibinfo{series}{Society
+			of Photo-Optical Instrumentation Engineers (SPIE) Conference Series}},
+	\bibinfo{pages}{91470M} (\bibinfo{year}{2014}).
+
+	\bibitem{dalton+2014}
+	\bibinfo{author}{{Dalton}, G.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Project overview and update on WEAVE: the next
+			generation wide-field spectroscopy facility for the William Herschel
+			Telescope}}.
+	\newblock In \bibinfo{editor}{{Ramsay}, S.~K.}, \bibinfo{editor}{{McLean},
+		I.~S.} \& \bibinfo{editor}{{Takami}, H.} (eds.)
+	\emph{\bibinfo{booktitle}{Ground-based and Airborne Instrumentation for
+			Astronomy V}}, vol. \bibinfo{volume}{9147} of \emph{\bibinfo{series}{Society
+			of Photo-Optical Instrumentation Engineers (SPIE) Conference Series}},
+	\bibinfo{pages}{91470L} (\bibinfo{year}{2014}).
+	\newblock \eprint{1412.0843}.
+
+	\bibitem{blanton+2019}
+	\bibinfo{author}{{Blanton}, M.} \emph{et~al.}
+	\newblock \bibinfo{title}{{The Sloan Digital Sky Survey as an Archetypal
+			Mid-Scale Program}}.
+	\newblock In \emph{\bibinfo{booktitle}{Bull. Am. Astron. Soc.}},
+	vol.~\bibinfo{volume}{51}, \bibinfo{pages}{196} (\bibinfo{year}{2019}).
+
+	\bibitem{kollmeier+2019}
+	\bibinfo{author}{{Kollmeier}, J.} \emph{et~al.}
+	\newblock \bibinfo{title}{{SDSS-V Pioneering Panoptic Spectroscopy}}.
+	\newblock In \emph{\bibinfo{booktitle}{Bull. Am. Astron. Soc.}},
+	vol.~\bibinfo{volume}{51}, \bibinfo{pages}{274} (\bibinfo{year}{2019}).
+
+\end{thebibliography}
+
+\vspace{5mm}
+
 \textbf{Acknowledgments}: The authors would like to thank the anonymous reviewers for their help improving this manuscript.
@@
 \clearpage
-\input{methods.tex}
+\section*{\underline{Methods}}
+\section{Asteroseismic Methods}
+\subsection{Asteroseismic Data}
+For our asteroseismic power spectrum data we used the unweighted power spectra from the KASOC pipeline \cite{handberg+lund2014}.
+We did not apply any additional treatment to these data.
+For 16 Cyg A \& B (KIC 12069424 and KIC 12069449) we used the KEPSEISMIC lightcurves \cite{garcia+2011}, which have significantly better signal-to-noise for these two stars.
 
-\clearpage
-\input{ed.tex}
+For our asteroseismic ages, we used the ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{silvaaguirre+2015} in the `Kages' and LEGACY catalogues.
+These ages have been obtained by comparisons of measured oscillation properties to stellar models, accounting for an expanded range of metallicities.
+\texttt{BASTA} is thoroughly compared to four other seismic modelling techniques in \cite{silvaaguirre+2017}.
+While uncertainties found through \texttt{BASTA} are typically higher than for other techniques, only \texttt{BASTA} and \texttt{ASTFIT} \cite[Aarhus STellar Evolution Code]{christensen-dalsgaard2008} recover the radius, mass and age of the Sun, when applied to solar data.
+Although the uncertainties on \texttt{ASTFIT} ages are overall lower, they are not published for the `Kages' sample.
+In order to maintain an internally consistent stellar age sample, we used age results from \texttt{BASTA} for both the `Kages' and LEGACY samples.
+
+For our stellar masses we used asteroseismic model masses obtained by \texttt{BASTA} reported in `Kages' and LEGACY, in order to maintain internal consistency with the age measurements.
+We note that age and mass posteriors from \texttt{BASTA} are correlated, but chose not to account for the unpublished correlations in this work.
+
+As described in the catalogue papers, for `Kages' stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy \cite{huber+2013a}.
+For LEGACY stars, atmospheric properties were similarly taken from one study \cite{buchhave+latham2015} for most stars in the catalogue, and complemented by other values from the literature for the remaining stars \cite[see Table 3]{silvaaguirre+2017}.
+
+Other asteroseismic properties used in this study, such as those used as first guesses on the free parameters in our asteroseismic model, were taken from the `Kages' and LEGACY catalogues \cite{astropycollaboration+2013, astropycollaboration+2018, ginsburg+2019}.
+In cases where both catalogues contained the same target, we used the stellar parameters reported in LEGACY \cite{mckinney2010}.
+This is also the case for the masses and ages described above.
+
+\subsection{Mode Frequency Fitting}
+
+In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background, modes of oscillation, and white noise, while accounting for rotational splitting.
+The foundations of this approach follows best-practices in asteroseismology \cite{davies+2015}, fitting Harvey profiles for the background \cite{harvey1985} and expressing the frequencies of the modes using an asymptotic expression \cite{tassoul1980, vrard+2016}.
+
+The first core improvement in this work is the use of hierarchical latent variable models \cite{hogg+2010, hall+2019}, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{mazumdar+2014}).
+By improving the inference of mode frequencies in this way, we also improve the ability to resolve the rotational splitting.
+The second improvement comes in the form of priors on our parameters, and in particular the rotational inclination, which more accurately reflects the true distribution of angles than previous techniques \cite{chaplin+basu2017}.
+A step-by-step breakdown of the model and all priors can be found in \textbf{Supplementary Information}.\\
+
+We separated our model fitting into two parts.
+First, we fit a model for the convective background and white noise only, to the region of the power spectra that did not contain modes of oscillation.
+This was done using \texttt{PyStan} \cite{vanhoey+2013, carpenter+2017}, for 10,000 iterations on each star.
+These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work.
+Second, we fit our full model (including the convective background) to the region containing the modes of oscillation.
+The results of the first fit to the convective background were used as extremely informative priors on the background parameters in this second fit.
+This was done using \texttt{PyMC3} \cite{vanderwalt+2011, salvatier+2016, thetheanodevelopmentteam+2016} for 2500 iterations each on 4 chains.
+
+From this asteroseismic analysis, we report inclination angle ($i$), rotational splitting ($\nu_{\rm s}$), and rotation period ($P$) in \textbf{Supplementary Information} Table 1.
+The summary statistics on these parameters were taken as the median of the posterior distribution, with uncertainties being the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles.
+For inclination angle ($i = \arccos(\cos(i))$) and rotation ($P = 1/\nu_{\rm s}$), the full posterior samples were transformed before taking the summary statistics, as our model sampled in $\cos(i)$ and $\nu_{\rm s}$.
+
+We flagged any sub-optimal conditions of the final fit.
+We flagged 5 for which the Gelman-Rubin convergence metric, $\hat{R}$, was greater than 1.01 and 2 stars for which it was greater than 1.1 on inclination angle or rotation, where a $\hat{R} = 1$ indicates a converged result \cite{gelman+rubin1992}.
+We also performed visual checks of the sampled chains on all hyperparameters and of the best-fit model compared to both the raw and smoothed asteroseismic data.
+We found no issues in the visual investigation of 94 stars.
+KIC 8478994 is not reported due to both a poor unconverged fit as well as high $\hat{R}$ on rotational parameters.
+KICs 6603624, 8760414 and 8938364 are reported in  \textbf{Supplementary Information} Table 1, but were excluded from the gyrochronology analysis due to strong disagreement with multiple studies in the literature (see main body of paper).
+Finally, we flagged any stars with fewer than 1000 effective samples ($n_{\rm eff}$) of $\nu_s$.
+
+\subsection{Seismic vs Surface rotation}
+As described in the main body of the paper, we compared a subsample of our asteroesismic rotation rates to surface rotation rates from spot rotation, where available.
+Both the surface ($P_{\rm surf}$) and seismic ($P_{\rm seis}$) rotation rates have associated uncertainties.
+Instead of fitting the slope between these two values directly, we instead fit the distribution
+
+\begin{equation}
+	p(\frac{P_{\rm seis}}{P_{\rm surf}}\, |\, m) = \mathcal{N}(m, \sigma_\frac{P_{\rm seis}}{P_{\rm surf}})\, ,
+\end{equation}
+
+\noindent where $m$ is the slope, and $\sigma_\frac{P_{\rm seis}}{P_{\rm surf}}$ is the uncertainty corresponding to $\frac{P_{\rm seis}}{P_{\rm surf}}$, following the propagation of the errors on both values.
+We used the larger of the asymmetrical uncertainties on asteroseismic rotation from our analysis.
+The model was fit using \texttt{PyMC3} for 2000 iterations each on 4 chains.
+Five stars for which both surface and seismic rotation were available, but which had a surface rotation above the 1.8:1 line, were excluded from this analysis.
+This was to exclude likely multiples of the true rotation rate skewing the fit, as measurements of double the true rotation may occur in spot rotation measurements.
+
+Our fit found a value of $m = 0.96 \pm 0.03$ using 48 stars.
+We reran this analysis using the 21 stars in this sample for which the median of their posterior probability for $Q_{\rm WMB}$ was greater than $0.5$ in our stellar model analysis, preferring the WMB model.
+A fit to these stars alone found a value of $m = 0.96 \pm 0.04$.
+
+\section{Gyrochronology Methods}\label{s:gyro}
+\subsection{Stellar Models}\label{ssec:models}
+The braking models used in this work have several parameters that inform the rotational evolution.
+These are: a normalization factor to reproduce the solar rotation ($f_k$); a disk locking timescale ($T_{\rm disk}$) and period ($P_{\rm disk}$) which together regulate the stellar angular velocity during the pre-main sequence; the critical angular velocity that marks the transition from saturated (rapidly rotating) to unsaturated (slowly rotating) regimes ($\omega_{\rm crit}$), and the critical Rossby number, above which stars conserve angular momentum ($Ro_{\rm crit}$), mentioned above.
+$T_{\rm disk}$, $P_{\rm disk}$ and $\omega_{\rm crit}$ are calibrated to match the behavior in young open clusters, but have little impact on the rotational evolution beyond $\approx 1\, \rm{Gyr}$ in solar-mass stars.
+Both $f_k$ and $Ro_{\rm crit}$ affect the late-time evolution.
+Both models adopt $\omega_{\rm crit} = 3.4  \times 10^{-5}\, \rm{s}^{-1}$, $P_{\rm disk} = 8.1$, $T_{\rm disk} = 0.28$ and $f_k = 6.6$.
+In the weakened magnetic braking model, $Ro_{\rm crit} = 1.97$.
+\rtwo{This Rossby number is based on model comparisons to catalogues of spot rotation rates \cite{vansaders+2019}.
+Its exact value is not critical in our analysis, as any similar value would create a model population significantly different from the standard case.
+In the model, the Rossby number is defined as the rotation period divided by the convective turnover timescale, which in turn is defined as $\tau_{\rm cz} = H_p / v_{\rm conv}$, where $H_p$ is the pressure scale height at the base of the convection zone, and $v_{\rm conv}$ is the convetive velocity evaluated one pressure scale height above the base in a mixing length theory of convection.
+Solid body rotation is assumed \cite{nielsen+2015}.} For further details, see \cite{vansaders+pinsonneault2013} and \cite{vansaders+2016, vansaders+2019} for the standard and weakened magnetic braking cases respectively.
+
+To construct a synthetic population of rotating stars, we expanded upon previous forward-models of the \textit{Kepler} field with the purpose of studying weakened magnetic braking \cite{vansaders+2019}, with some important improvements.
+We started with a TRILEGAL \cite{girardi+2012} Milky-Way simulation of the \kepler field, using the simulation's standard population values intended for this purpose.
+In order to replicate the \kepler selection effect, the TRILEGAL simulation was matched to the largest current catalogue of temperatures, luminosities and 2MASS $K$-band magnitudes of stars in the \kepler field \cite{berger+2020}.
+This was done using a nearest-neighbours approach, based on the density of stars on the HR diagram.
+This ensured that the TRILEGAL population matched the density of stars actually observed by \kepler, replicating its selection effects, and improved upon previous efforts \cite{vansaders+2019} by incorporating contemporary \textit{Gaia} mission data \cite{gaiacollaboration+2018}.
+
+We made further changes to account for possible binarity in the the matching sample \cite{berger+2020}.
+If the first step is performed blindly, blended binaries in the sample cause an overestimation of the number of old stars.
+In order to overcome this, we:
+
+\begin{enumerate}
+	\item blended the TRILEGAL stars with binary companions drawn from a flat mass-ratio distribution, using a known binary fraction \cite{raghavan+2010},
+	\item recalculated the `observed' luminosities and magnitudes assuming that each binary pair was blended, and
+	\item shifted these stars' temperatures following a $g$-$K$ magnitude relation \cite{berger+2020}.
+\end{enumerate}
+
+This new distribution was used for the nearest-neighbour matching.
+Once drawn we dropped the binary companion and used the true TRILEGAL properties of those stars.
+For stars where the mass of the companion was $M < 0.4\, \odot$, binary contributions were ignored.
+Every binary was assumed to result in a blend, regardless of separation.
+This results in slightly more young stars than reality, because young, blended binary systems contaminate regions of the HR diagram where one expects to find old stars, and the number of blends is overestimated by assuming every binary system is a blend.
+
+Our asteroseismic sample of stars with short cadence observations are subject to additional selection functions not included in the creation of the model populations above.
+We did \textit{not} explicitly account for these asteroseismic selection functions in our model, by design.
+Both the standard and WMB models contain stars with the same fundamental parameters (mass, radius, effective temperature, metallicity) but a different period based on the choice of rotational evolution prescription.
+Applying an asteroseismic selection function that depends on these fundamental parameters would have an identical effect on both models, therefore providing no net effect on our posterior distribution \cite{chaplin+2011}.
+Additionally, we expected any seismic selection function to be relatively flat (and therefore uninformative) on a star-by-star scale, on which we run our model analysis.
+
+\subsection{Bayesian Mixture Model}
+In order to determine whether weakened magnetic braking occurs on the main sequence, we compared our sample of seismic age and rotation, along with temperature, metallicity and mass, to the two stellar population models of the \kepler field \cite{vansaders+2019}, discussed above.
+Both stellar models were evaluated in a Bayesian framework, with the rationale of determining which of the two models (standard or WMB) is most likely to reproduce our observed data.
+Each model sample contained temperature (\teff), mass ($M$), age ($t$), metallicity ($\rm{[Fe/H]}$) and rotation ($P$) information.
+
+In order to draw probabilistic inference about the models, we built a five-dimensional Kernel Density Estimate (KDE) of both model populations using the \texttt{statsmodels} package \cite{seabold+perktold2010}.
+We used a band-width (setting the resolution of the KDE) of $0.02\, \odot$ in mass, $10\, \rm K$ in \teff, $0.01\, \rm{dex}$ in $\ln(t)$, $0.01\, \rm{dex}$ in $\rm{[Fe/H]}$ and $0.01\, \rm{dex}$ in $\ln(P)$.
+Note that age and rotation were treated in log space, where the posterior estimates from asteroseismology more closely resemble normal distributions.
+This approach translates the population models to a probability distribution we can use in a Bayesian framework.
+
+We evaluated our data against both models simultaneously by treating the data as being drawn from a mixture of both model KDEs.
+In this mixture model structure, the two KDEs were modulated by a weighting factor, $Q_{\rm WMB}$.
+In the limit $Q_{\rm WMB} \rightarrow 1$, the data are most likely drawn from the WMB model.
+In the limit $Q_{\rm WMB} \rightarrow 0$, the data are most likely drawn from the standard model.
+
+The posterior probability of obtaining $Q_{\rm WMB}$ and additional parameters $\theta$ given our data $\mathcal{D}$ is $p(Q_{\rm{WMB}}, \theta | \mathcal{D})$.
+Using Bayes equation, we can express this as:
+
+\begin{equation}\label{eq:modelll}
+	p(Q_{\rm{WMB}}, \theta | \mathcal{D}) \propto p(\mathcal{D} | \theta)\ p(\theta | Q_{\rm{WMB}}, \kappa_{\rm{s}}, \kappa_{\rm{WMB}})\ p(Q_{\rm{WMB}})\, ,
+\end{equation}
+
+\noindent where $\kappa_{\rm{s}}$ and $\kappa_{\rm{WMB}}$ are the KDE functions for the standard and WMB models respectively, and $\theta$ here are parameters, $\theta = \{M, \teff, \ln(t), \feh, \ln(P)\}$.
+The parameters $\theta$ may be referred to as latent parameters, as they form a step between the parameter we want to infer ($Q_{\rm{WMB}}$) and our data.
+Using this approach allowed our model to properly take into account the observational uncertainties on the data \rtwo{in five dimensions.}
+
+The second component on the right hand side of Equation \ref{eq:modelll} describes the probability of obtaining our latent parameters $\theta$ given our KDEs and the mixture model weighting parameter $Q_{\rm WMB}$, and is described by the mixture model
+
+\begin{equation}\label{eq:mixturell}
+	p(\theta | Q_{\rm{WMB}}, \kappa_{\rm{WMB}}, \kappa_{\rm{s}}) = Q_{\rm WMB} \times \kappa_{\rm WMB}(\theta) + (1 - Q_{\rm WMB}) \times \kappa_{\rm s}(\theta)\, ,
+\end{equation}
+
+\noindent where all parameters are as described above.
+This probability function describes a distribution that is a mixture of both KDEs.
+While the KDEs are constant, $Q_{\rm WMB}$ is a free parameter, and so the shape of this distribution can vary.
+The latent parameters $\theta$ are drawn from this distribution, and therefore from some combination of the two stellar models.
+
+The first component in Equation \ref{eq:modelll} describes the likelihood of obtaining the parameters $\theta$ given our data and their observational uncertainty. It takes the form
+
+\begin{equation}
+	p(\mathcal{D} | \theta) = \mathcal{N}(\mathcal{D} | \theta, \sigma_{\mathcal{D}})\, ,
+\end{equation}
+
+\noindent a normal distribution evaluating the latent parameters $\theta$ against the observations, with observational uncertainty $\sigma_{\mathcal{D}}$.
+This approach means that in each parameter space (such as age), the age drawn from the stellar model mixture is entered into the likelihood equation with our static observations.
+The value of this equation (and thus the likelihood) will increase if $\theta$ is closer to the observations, and the mixture model will be modulated in a manner that maximises this probability, inferring whether one stellar model is more likely to produce our data than the other.
+
+The final term, $p(Q_{\rm WMB})$, represents the prior on the mixture model weight, which is uniform between 0 and 1. A visual representation of our model is shown in \textbf{Extended Data} Figure 1.
+
+Typically, this model would evaluate all stars in our sample against the stellar models simultaneously for a single posterior estimate of $Q_{\rm WMB}$.
+At 95 stars, in 5 parameter spaces, this totals 476 free parameters to marginalise over.
+This is not an issue for Hamiltonian Monte Carlo \cite[HMC]{betancourt+girolami2013}, however the use of KDE functions, over which a probabilistic gradient can not be measured, reduces HMCs effectiveness.
+Alternative Markov Chain Monte Carlo techniques \cite[MCMC]{foreman-mackey+2013} can more efficiently sample the KDE functions, but can not treat the large number of hierarchical parameters.
+To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $Q_{\rm WMB}$, and multiplied these post hoc to obtain a combined posterior.
+This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications, at the expense of the ability to marginalise for a single value of $Q_{\rm WMB}$ directly.\\
+
+The parameter space of the stellar model populations were reduced before calculating the KDEs.
+These cuts were made in $M$, $\teff$, $\ln(t)$ and \feh, removing any stars in the models that fell more than $3 \times \sigma_{\mathcal{D}}$ outside the observations.
+Our observables $M$, $t$ and $P$ have asymmetric uncertainties from the Bayesian asteroseismic analysis.
+We used the larger of the reported uncertainties on each parameter as $\sigma_{\mathcal{D}}$ in each parameter space.
+
+KIC 6278762 was excluded from this stellar model analysis, because its age fell more than $3\sigma$ outside of the highest age in the stellar models (this is a metallicity issue, as the oldest stars have metallicities outside the range of the rotational model grids), and KICs 7106245 and 8760414 were excluded for the same reason due to low metallicities outside the functional range of the stellar models (-0.99 and -0.92 respectively).
+We also excluded any stars with $n_{\rm eff} < 1000$ for rotational splitting, and those with $\hat{R} > 1.1$.
+The remaining sample of 73 stars contained 4 sub-giants, 22 `hot' stars, and 47 main sequence stars.
+
+We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{foreman-mackey+2013, foreman-mackey2016}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.
+
+After fitting, we took a normalised histogram of the posterior estimate of $Q_{\rm WMB}$ for each star, using 100 bins.
+In this histogram, each bin approximated the value of the posterior function for $Q_{\rm WMB}$.
+The array of 100 bins for all stars were multiplied, resulting in an approximation of the joint posterior probability function for $Q_{\rm WMB}$ given all stars in the ensemble.\\
+
+\textbf{Data availability statement:} The core input data and results are summarised in  \textbf{Supplementary Information} Table 1, which is published with this article, and is also available on Vizier.
+Larger data files, such as stellar model populations and individual posterior distribution chains from the asteroseismic and gyrochronology model fitting are fully available on request.
+
+This work made use of publicly available data.
+\kepler power spectral densities were obtained from the \href{http://kasoc.phys.au.dk/}{KASOC} webpages for the majority of stars, and from the \href{https://archive.
+	stsci.edu/prepds/kepseismic/}{MAST} for 16 Cyg A and B.
+This work used asteroseismic data from Silva Aguirre et al.
+(2015, 2017), Davies et al.
+(2016) and Lund et al.
+(2017) \cite{silvaaguirre+2015, silvaaguirre+2017, davies+2016, lund+2017}.
+Parameter distributions of the \kepler field used to alter our stellar population models were taken from Berger et al.
+(2020) \cite{berger+2020}.\\
+
+\textbf{Code availability statement:} The code required to replicate our results has been placed in a curated online repository found here: \url{www.github.com/ojhall94/halletal2021}.
+
+All code written in the duration of this project, along with a full commit history, can be found in an un-curated online repository here: \url{www.github.com/ojhall94/malatium}.
+
+The code used to construct the stellar population models used in this work is available upon request.
+
+\begin{thebibliography}{99}
+	\makeatletter
+	\addtocounter{\@listctr}{51}
+	\makeatother
+	\expandafter\ifx\csname url\endcsname\relax
+	\def\url#1{\texttt{#1}}\fi
+	\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+	\providecommand{\bibinfo}[2]{#2}
+	\providecommand{\eprint}[2][]{\url{#2}}
+
+	\bibitem{handberg+lund2014}
+	\bibinfo{author}{Handberg, R.} \& \bibinfo{author}{Lund, M.~N.}
+	\newblock \bibinfo{title}{Automated preparation of {{Kepler}} time series of
+		planet hosts for asteroseismic analysis}.
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{445}}, \bibinfo{pages}{2698--2709}
+	(\bibinfo{year}{2014}).
+
+	\bibitem{garcia+2011}
+	\bibinfo{author}{Garc{\'i}a, R.~A.} \emph{et~al.}
+	\newblock \bibinfo{title}{Preparation of {{Kepler}} light curves for
+		asteroseismic analyses}.
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{414}}, \bibinfo{pages}{L6--L10}
+	(\bibinfo{year}{2011}).
+
+	\bibitem{christensen-dalsgaard2008}
+	\bibinfo{author}{{Christensen-Dalsgaard}, J.}
+	\newblock \bibinfo{title}{{{ASTEC}}\textemdash the {{Aarhus STellar Evolution
+				Code}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophysics and Space Science}}
+	\textbf{\bibinfo{volume}{316}}, \bibinfo{pages}{13} (\bibinfo{year}{2008}).
+
+	\bibitem{huber+2013a}
+	\bibinfo{author}{{Barnes}, S.~A.}
+	\newblock \bibinfo{title}{{A Simple Nonlinear Model for the Rotation of
+			Main-sequence Cool Stars. I. Introduction, Implications for Gyrochronology,
+			and Color-Period Diagrams}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{722}}, \bibinfo{pages}{222--234}
+	(\bibinfo{year}{2010}).
+
+	\bibitem{buchhave+latham2015}
+	\bibinfo{author}{Buchhave, L.~A.} \& \bibinfo{author}{Latham, D.~W.}
+	\newblock \bibinfo{title}{The {{Metallicities}} of {{Stars}} with and without
+		{{Transiting Planets}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{808}}, \bibinfo{pages}{187} (\bibinfo{year}{2015}).
+
+	\bibitem{astropycollaboration+2013}
+	\bibinfo{author}{{Astropy Collaboration}} \emph{et~al.}
+	\newblock \bibinfo{title}{Astropy: {{A}} community {{Python}} package for
+		astronomy}.
+	\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+	\textbf{\bibinfo{volume}{558}}, \bibinfo{pages}{A33} (\bibinfo{year}{2013}).
+
+	\bibitem{astropycollaboration+2018}
+	\bibinfo{author}{{Astropy Collaboration}} \emph{et~al.}
+	\newblock \bibinfo{title}{The {{Astropy Project}}: {{Building}} an
+		{{Open}}-science {{Project}} and {{Status}} of the v2.0 {{Core Package}}}.
+	\newblock \emph{\bibinfo{journal}{Astron. J.}} \textbf{\bibinfo{volume}{156}},
+	\bibinfo{pages}{123} (\bibinfo{year}{2018}).
+
+	\bibitem{ginsburg+2019}
+	\bibinfo{author}{Ginsburg, A.} \emph{et~al.}
+	\newblock \bibinfo{title}{Astroquery: {{An Astronomical Web}}-querying
+		{{Package}} in {{Python}}}.
+	\newblock \emph{\bibinfo{journal}{Astron. J.}} \textbf{\bibinfo{volume}{157}},
+	\bibinfo{pages}{98} (\bibinfo{year}{2019}).
+
+	\bibitem{mckinney2010}
+	\bibinfo{author}{McKinney, W.}
+	\newblock \bibinfo{title}{Data {{Structures}} for {{Statistical Computing}} in
+		{{Python}}}.
+	\newblock In \emph{\bibinfo{booktitle}{Proceedings of the 9th {{Python}} in
+			{{Science Conference}}}}, \bibinfo{pages}{51--56} (\bibinfo{year}{2010}).
+
+	\bibitem{harvey1985}
+	\bibinfo{author}{Harvey, J.}
+	\newblock \bibinfo{title}{High-{{Resolution Helioseismology}}}.
+	\newblock \emph{\bibinfo{journal}{Future Missions in Solar, Heliospheric \&
+			Space Plasma Physics}} \textbf{\bibinfo{volume}{235}}, \bibinfo{pages}{199}
+	(\bibinfo{year}{1985}).
+
+	\bibitem{tassoul1980}
+	\bibinfo{author}{{Tassoul}, M.}
+	\newblock \bibinfo{title}{{Asymptotic approximations for stellar nonradial
+			pulsations.}}
+	\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
+	\textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{469--490}
+	(\bibinfo{year}{1980}).
+
+	\bibitem{vrard+2016}
+	\bibinfo{author}{Vrard, M.}, \bibinfo{author}{Mosser, B.} \&
+	\bibinfo{author}{Samadi, R.}
+	\newblock \bibinfo{title}{Period spacings in red giants. {{II}}. {{Automated}}
+		measurement}.
+	\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+	\textbf{\bibinfo{volume}{588}}, \bibinfo{pages}{A87} (\bibinfo{year}{2016}).
+
+	\bibitem{hogg+2010}
+	\bibinfo{author}{{Hogg}, D.~W.}, \bibinfo{author}{{Bovy}, J.} \&
+	\bibinfo{author}{{Lang}, D.}
+	\newblock \bibinfo{title}{{Data analysis recipes: Fitting a model to data}}.
+	\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
+	\bibinfo{pages}{arXiv:1008.4686} (\bibinfo{year}{2010}).
+	\newblock \eprint{1008.4686}.
+
+	\bibitem{hall+2019}
+	\bibinfo{author}{Hall, O.~J.} \emph{et~al.}
+	\newblock \bibinfo{title}{Testing asteroseismology with {{Gaia DR2}}:
+		{{Hierarchical}} models of the {{Red Clump}}}.
+	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+	\textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{3569--3585}
+	(\bibinfo{year}{2019}).
+	\newblock \eprint{1904.07919}.
+
+	\bibitem{mazumdar+2014}
+	\bibinfo{author}{Mazumdar, A.} \emph{et~al.}
+	\newblock \bibinfo{title}{Measurement of acoustic glitches in solar-type stars
+		from oscillation frequencies observed by {{Kepler}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+	\textbf{\bibinfo{volume}{782}}, \bibinfo{pages}{18} (\bibinfo{year}{2014}).
+	\newblock \eprint{1312.4907}.
+
+	\bibitem{chaplin+basu2017}
+	\bibinfo{author}{Chaplin, W.~J.} \& \bibinfo{author}{Basu}.
+	\newblock \emph{\bibinfo{title}{Asteroseismic {{Data Analysis}}:
+			{{Foundations}} and {{Techniques}}}} (\bibinfo{publisher}{{Princeton
+			University Press}}, \bibinfo{address}{{Princeton, New Jersey}},
+	\bibinfo{year}{2017}), \bibinfo{edition}{1st} edn.
+
+	\bibitem{vanhoey+2013}
+	\bibinfo{author}{Van~Hoey, S.}, \bibinfo{author}{{van der Kwast}, J.},
+	\bibinfo{author}{Nopens, I.} \& \bibinfo{author}{Seuntjens, P.}
+	\newblock \bibinfo{title}{Python package for model {{STructure ANalysis}}
+		({{pySTAN}})}.
+	\newblock \emph{\bibinfo{journal}{EGU General Assembly Conference Abstracts}}
+	\textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{EGU2013--10059}
+	(\bibinfo{year}{2013}).
+
+	\bibitem{carpenter+2017}
+	\bibinfo{author}{Carpenter, B.} \emph{et~al.}
+	\newblock \bibinfo{title}{Stan: {{A Probabilistic Programming Language}}}.
+	\newblock \emph{\bibinfo{journal}{Journal of Statistical Software}}
+	\textbf{\bibinfo{volume}{76}}, \bibinfo{pages}{1--32} (\bibinfo{year}{2017}).
+
+	\bibitem{vanderwalt+2011}
+	\bibinfo{author}{{van der Walt}, S.}, \bibinfo{author}{Colbert, S.~C.} \&
+	\bibinfo{author}{Varoquaux, G.}
+	\newblock \bibinfo{title}{The {{NumPy Array}}: {{A Structure}} for {{Efficient
+				Numerical Computation}}}.
+	\newblock \emph{\bibinfo{journal}{Computing in Science and Engineering}}
+	\textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{22--30}
+	(\bibinfo{year}{2011}).
+
+	\bibitem{thetheanodevelopmentteam+2016}
+	\bibinfo{author}{{The Theano Development Team}} \emph{et~al.}
+	\newblock \bibinfo{title}{{Theano: A Python framework for fast computation of
+			mathematical expressions}}.
+	\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
+	\bibinfo{pages}{arXiv:1605.02688} (\bibinfo{year}{2016}).
+	\newblock \eprint{1605.02688}.
+
+	\bibitem{gaiacollaboration+2018}
+	\bibinfo{author}{{Gaia Collaboration}} \emph{et~al.}
+	\newblock \bibinfo{title}{{Gaia Data Release 2. Summary of the contents and
+			survey properties}}.
+	\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+	\textbf{\bibinfo{volume}{616}}, \bibinfo{pages}{A1} (\bibinfo{year}{2018}).
+	\newblock \eprint{1804.09365}.
+
+	\bibitem{raghavan+2010}
+	\bibinfo{author}{Raghavan, D.} \emph{et~al.}
+	\newblock \bibinfo{title}{A {{Survey}} of {{Stellar Families}}:
+		{{Multiplicity}} of {{Solar}}-type {{Stars}}}.
+	\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
+	\textbf{\bibinfo{volume}{190}}, \bibinfo{pages}{1--42}
+	(\bibinfo{year}{2010}).
+
+	\bibitem{chaplin+2011}
+	\bibinfo{author}{{Chaplin}, W.~J.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Ensemble Asteroseismology of Solar-Type Stars with
+			the NASA Kepler Mission}}.
+	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{332}},
+	\bibinfo{pages}{213} (\bibinfo{year}{2011}).
+	\newblock \eprint{1109.4723}.
+
+	\bibitem{seabold+perktold2010}
+	\bibinfo{author}{Seabold, S.} \& \bibinfo{author}{Perktold, J.}
+	\newblock \bibinfo{title}{{S}tatsmodels: {E}conometric and {S}tatistical
+		{M}odeling with {P}ython}.
+	\newblock In \bibinfo{editor}{{S}t\'efan van~der {W}alt} \&
+	\bibinfo{editor}{{J}arrod {M}illman} (eds.)
+	\emph{\bibinfo{booktitle}{{P}roceedings of the 9th {P}ython in {S}cience
+			{C}onference}}, \bibinfo{pages}{92 -- 96} (\bibinfo{year}{2010}).
+
+	\bibitem{betancourt+girolami2013}
+	\bibinfo{author}{{Astrophys. J.}, M.~J.} \& \bibinfo{author}{{Girolami}, M.}
+	\newblock \bibinfo{title}{{Hamiltonian Monte Carlo for Hierarchical Models}}.
+	\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
+	\bibinfo{pages}{arXiv:1312.0906} (\bibinfo{year}{2013}).
+	\newblock \eprint{1312.0906}.
+
+	\bibitem{foreman-mackey+2013}
+	\bibinfo{author}{{Foreman-Mackey}, D.}, \bibinfo{author}{Hogg, D.~W.},
+	\bibinfo{author}{Lang, D.} \& \bibinfo{author}{Goodman, J.}
+	\newblock \bibinfo{title}{Emcee: {{The MCMC Hammer}}}.
+	\newblock \emph{\bibinfo{journal}{Publ. Astron. Soc. Pacific}}
+	\textbf{\bibinfo{volume}{125}}, \bibinfo{pages}{306--312}
+	(\bibinfo{year}{2013}).
+	\newblock \eprint{1202.3665}.
+
+	\bibitem{foreman-mackey2016}
+	\bibinfo{author}{{Foreman-Mackey}, D.}
+	\newblock \bibinfo{title}{Corner.py: {{Scatterplot}} matrices in {{Python}}}.
+	\newblock \emph{\bibinfo{journal}{The Journal of Open Source Software}}
+	\textbf{\bibinfo{volume}{1}} (\bibinfo{year}{2016}).
+\end{thebibliography}
 

### 2021-02-22 paper/natastron/Publication/si.tex
fixed error

@@
 \usepackage{multirow}
-\usepackage[figurename={Supplementary Figure}]{caption}
+\usepackage[figurename={Supplementary Figure}, tablename={Supplementary Table}]{caption}
 \usepackage{booktabs}
@@
 The rotational stellar models used in this work \cite{vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$.
-Our sample of 91 stars contained 4 stars with metallicities below $-0.4\, \rm{dex}$, which are shown as shaded symbols in Figure \ref{fig:fullsample}.
+Our sample of 91 stars contained 4 stars with metallicities below $-0.4\, \rm{dex}$, which are shown as shaded symbols in Figure 3 in the main paper.
 Of these, 3 were included in our final sample of 73 stars used to evaluate our stellar models: KICs 7970740, 8684723 and KIC 9965715.
@@
 
-When constructing KDEs from our stellar model samples (see Section \ref{s:gyro}), we selected fixed resolutions (or band-widths) for the KDEs.
-In mass, the band-width of $0.02\, \odot$, was larger than the uncertainties of 24 of 73 stars used to construct our joint posterior.
+When constructing KDEs from our stellar model samples, we selected fixed resolutions (or band-widths) for the KDEs.
+In mass, the band-width of $0.02\, M_\odot$, was larger than the uncertainties of 24 of 73 stars used to construct our joint posterior.
 For the stars with the smallest uncertainties, this significantly limits the size of the KDE being evaluated (as subsections of the full stellar models are used to evaluate individual stars, for computational efficiency).

### 2021-04-08 paper/natastron/ArXiV/paper.tex
Added ArXiV stuff

--- 2021-02-17 paper/natastron/Publication/Send/paper.tex
@@
 \usepackage[ ]{hyperref}
+%\graphicspath{{Images/}}
 %\usepackage[symbol]{footmisc}
@@
 \begin{document}
-\noindent\textbf{\LARGE{New asteroseismic rotation rates of \emph{Kepler} dwarfs show strong \rtwo{preference for} weakened magnetic braking on the late-age main sequence}}\\
+\noindent\textbf{\LARGE{Weakened magnetic braking supported by asteroseismic rotation rates of \textit{Kepler} dwarfs}}\\
 
@@
 
+\setcounter{figure}{0}    
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.6 \textwidth]{Images/pgm_models.pdf}
+	\caption{\textbf{A probabilistic graphical model (PGM) represented algebraically in Equation \ref{eq:modelll}.} The shaded circle indicates observed data, and solid black points represent other fixed information, such as the KDEs and observational uncertainties.
+The remaining circles represent parameters.
+The underline indicates that the symbol represents a set of parameters or data.
+Here, $\kappa_{\rm{s}}$ and $\kappa_{\rm WMB}$ represent the KDEs of standard and WMB model populations respectively.
+$Q_{\rm{WMB}}$ is the mixture model weighting factor.
+The latent parameters $\theta$, our observations $\mathcal{D}$ and their uncertainties $\sigma_{\mathcal{D}}$ include temperature (\teff), mass ($M$), log-age ($\ln(t)$), metallicity (\feh) and log-rotation ($\ln(P)$).
+This model is \textit{hierarchical}, as all the latent parameters are drawn from the common probability distribution set by $Q_{\rm{WMB}}$ and described in Equation \ref{eq:mixturell}.}
+	\label{fig:pgm}
+\end{figure}
+
+\clearpage
+
+\input{si.tex}
+
 \end{document}

### 2021-04-12 paper/natastron/ArXiV/paper.tex
prepped the ArXiV submission

@@
 \usepackage[ ]{hyperref}
-%\graphicspath{{Images/}}
+\graphicspath{{Images/}}
 %\usepackage[symbol]{footmisc}
@@
 
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%%
  %500 words
@@
 
-In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting, excluding those with a number of effective samples $n_{\rm eff} < 1000$ and a Gelman-Rubin metric of $\hat{R}<1.1$ \cite{gelman+rubin1992,salvatier+2016} (see  \textbf{Supplementary Information} Table 1).
+In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting, excluding those with a number of effective samples $n_{\rm eff} < 1000$ and a Gelman-Rubin metric of $\hat{R}<1.1$ \cite{gelman+rubin1992,salvatier+2016} (see  \textbf{Supplementary Table 1}).
 Two stars with low metallicities ($< -0.8\, \rm {dex}$) that fell outside the boundaries of our stellar models were also excluded.
@@
 
-From this asteroseismic analysis, we report inclination angle ($i$), rotational splitting ($\nu_{\rm s}$), and rotation period ($P$) in \textbf{Supplementary Information} Table 1.
+From this asteroseismic analysis, we report inclination angle ($i$), rotational splitting ($\nu_{\rm s}$), and rotation period ($P$) in \textbf{Supplementary Table 1}.
 The summary statistics on these parameters were taken as the median of the posterior distribution, with uncertainties being the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles.
@@
 KIC 8478994 is not reported due to both a poor unconverged fit as well as high $\hat{R}$ on rotational parameters.
-KICs 6603624, 8760414 and 8938364 are reported in  \textbf{Supplementary Information} Table 1, but were excluded from the gyrochronology analysis due to strong disagreement with multiple studies in the literature (see main body of paper).
+KICs 6603624, 8760414 and 8938364 are reported in  \textbf{Supplementary Table 1}, but were excluded from the gyrochronology analysis due to strong disagreement with multiple studies in the literature (see main body of paper).
 Finally, we flagged any stars with fewer than 1000 effective samples ($n_{\rm eff}$) of $\nu_s$.
@@
 
-\textbf{Data availability statement:} The core input data and results are summarised in  \textbf{Supplementary Information} Table 1, which is published with this article, and is also available on Vizier.
+\textbf{Data availability statement:} The core input data and results are summarised in  \textbf{Supplementary Table 1}, which is published with this article, and is also available on Vizier.
 Larger data files, such as stellar model populations and individual posterior distribution chains from the asteroseismic and gyrochronology model fitting are fully available on request.
@@
 
+\renewcommand{\figurename}{Extended Data Figure}
+
 \setcounter{figure}{0}    
@@
 	\centering
-	\includegraphics[width=0.6 \textwidth]{Images/pgm_models.pdf}
+	\includegraphics[width=0.6 \textwidth]{pgm_models.pdf}
 	\caption{\textbf{A probabilistic graphical model (PGM) represented algebraically in Equation \ref{eq:modelll}.} The shaded circle indicates observed data, and solid black points represent other fixed information, such as the KDEs and observational uncertainties.

### 2021-04-12 paper/natastron/ArXiV/si.tex
Added ArXiV stuff
prepped the ArXiV submission

--- 2021-02-22 paper/natastron/Publication/si.tex
@@
-\documentclass[12pt]{article}
-\setlength{\textwidth}{167mm}
-\setlength{\headsep}{0mm}
-\setlength{\headheight}{0mm}
-\setlength{\textheight}{230mm}
-\setlength{\oddsidemargin}{1.6mm}
-\setlength{\evensidemargin}{1.6mm}
-\setlength{\topmargin}{4.6mm}
-
-\usepackage{chngcntr}
-\usepackage{xspace}
-\usepackage{color}
-\usepackage{graphicx}
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{lscape}
-\usepackage{longtable}
-\usepackage{threeparttable}
-\usepackage{multirow}
-\usepackage[figurename={Supplementary Figure}, tablename={Supplementary Table}]{caption}
-\usepackage{booktabs}
-\usepackage[ ]{hyperref}
-\graphicspath{{Images/}}
-%\usepackage[symbol]{footmisc}
-
-% Astronomical abbreviations (thanks to Dan Huber)
-\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
-\newcommand{\dnu}{\mbox{$\Delta \nu$}\xspace}
-\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
-\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
-\newcommand{\logg}{\mbox{$\log(g)$}\xspace}
-\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
-\newcommand{\msun}{\mbox{$\mathrm{M}_{\odot}$}\xspace}
-\newcommand{\lsun}{\mbox{$\mathrm{L}_{\odot}$}\xspace}
-\newcommand{\mearth}{\mbox{$\mathrm{M}_{\oplus}$}\xspace}
-\newcommand{\rsun}{\mbox{$\mathrm{R}_{\odot}$}\xspace}
-\newcommand{\kepler}{\emph{Kepler}\xspace}
-\newcommand{\tess}{\emph{TESS}\xspace}
-\newcommand{\ktwo}{K2\xspace}
-\newcommand{\gaia}{\emph{Gaia}\xspace}
-
-\begin{document}
+\renewcommand{\figurename}{Supplementary Figure}
 
@@
 
- \begin{figure*}
+ \begin{figure}
 	\centering
-	\includegraphics[width=.99\textwidth]{Images/modelfit.pdf}
+	\includegraphics[width=.99\textwidth]{modelfit.pdf}
 	\caption{A power spectrum constructed from four years of \kepler observations of 16 Cyg A (KIC 12069424).
@@
 	\label{fig:modelfit}
-\end{figure*}
+\end{figure}
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{Images/priors.pdf}
+	\includegraphics[width=\textwidth]{priors.pdf}
 	\caption{\textbf{Comparisons between posterior estimates of rotational parameters (data points and error bars) and the priors on these parameters (shaded regions).} The data are sorted from young stars (left) to old (right).
@@
 	\centering
-	\includegraphics[width=\textwidth]{Images/litcomp_alt2.pdf}
+	\includegraphics[width=\textwidth]{litcomp_alt2.pdf}
 	\caption{\textbf{Comparisons between posterior estimates of rotational parameters from this work and the literature}.
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{Images/seis_comparison_rot_alt2.pdf}
+	\includegraphics[width=0.8\textwidth]{seis_comparison_rot_alt2.pdf}
 	\caption{\textbf{Fractional differences between posterior estimates of asteroseismic rotation period from this work.} Literature sources are: Davies et al.
@@
 	\centering
-	\includegraphics[width=\textwidth]{Images/vsini_comparison_new.pdf}
+	\includegraphics[width=\textwidth]{vsini_comparison_new.pdf}
 	\caption{\textbf{Comparisons between asteroseismic and spectroscopic measures of projected surface rotation, $\textrm{v}\sin(i)$.} All asteroseismic (x-axis) values are from this work, all spectroscopic (y-axis) values are from the literature.
@@
 
-\section{Supplementary Table}
+%\bibliographystyle{naturemag}
+%\bibliography{library.bib} % if your bibtex file is called example.bib
+\addcontentsline{toc}{section}{References}
+\begin{thebibliography}{99}
+	\makeatletter
+	\addtocounter{\@listctr}{78}
+	\makeatother
+	\expandafter\ifx\csname url\endcsname\relax
+	\def\url#1{\texttt{#1}}\fi
+	\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+	\providecommand{\bibinfo}[2]{#2}
+	\providecommand{\eprint}[2][]{\url{#2}}
+
+\bibitem{hogg2012}
+\bibinfo{author}{Hogg, D.~W.}
+\newblock \bibinfo{title}{Data analysis recipes: {{Probability}} calculus for
+	inference}.
+\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
+\bibinfo{pages}{arXiv:1205.4446} (\bibinfo{year}{2012}).
+
+\bibitem{davies+2014}
+\bibinfo{author}{Davies, G.~R.}, \bibinfo{author}{Chaplin, W.~J.},
+\bibinfo{author}{Elsworth, Y.} \& \bibinfo{author}{Hale, S.~J.}
+\newblock \bibinfo{title}{{{BiSON}} data preparation: A correction for
+	differential extinction and the weighted averaging of contemporaneous data}.
+\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+\textbf{\bibinfo{volume}{441}}, \bibinfo{pages}{3009--3017}
+(\bibinfo{year}{2014}).
+
+\bibitem{appourchaux+2016}
+\bibinfo{author}{Appourchaux, T.} \emph{et~al.}
+\newblock \bibinfo{title}{Oscillation mode linewidths and heights of 23
+	main-sequence stars observed by {{{\emph{Kepler}}}}
+	{\emph{(}}{{{\emph{Corrigendum}}}}{\emph{)}}}.
+\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
+\textbf{\bibinfo{volume}{595}}, \bibinfo{pages}{C2} (\bibinfo{year}{2016}).
+
+\bibitem{rasmussen+williams2006}
+\bibinfo{author}{Rasmussen, C.~E.} \& \bibinfo{author}{Williams, C. K.~I.}
+\newblock \emph{\bibinfo{title}{Gaussian Processes for Machine Learning}}.
+\newblock Adaptive Computation and Machine Learning (\bibinfo{publisher}{{MIT
+		Press}}, \bibinfo{address}{{Cambridge, Mass}}, \bibinfo{year}{2006}).
+
+\bibitem{toutain+appourchaux1994}
+\bibinfo{author}{Toutain, T.} \& \bibinfo{author}{Appourchaux, T.}
+\newblock \bibinfo{title}{Maximum likelihood estimators: {{An}} application to
+	the estimation of the precision of helioseismic measurements}.
+\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+\textbf{\bibinfo{volume}{289}}, \bibinfo{pages}{649--658}
+(\bibinfo{year}{1994}).
+
+\bibitem{gizon+solanki2003}
+\bibinfo{author}{Gizon, L.} \& \bibinfo{author}{Solanki, S.~K.}
+\newblock \bibinfo{title}{Determining the {{Inclination}} of the {{Rotation
+			Axis}} of a {{Sun}}-like {{Star}}}.
+\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+\textbf{\bibinfo{volume}{589}}, \bibinfo{pages}{1009} (\bibinfo{year}{2003}).
+
+\bibitem{handberg+campante2011}
+\bibinfo{author}{Handberg, R.} \& \bibinfo{author}{Campante, T.~L.}
+\newblock \bibinfo{title}{Bayesian peak-bagging of solar-like oscillators using
+	{{MCMC}}: A comprehensive guide}.
+\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+\textbf{\bibinfo{volume}{527}}, \bibinfo{pages}{A56} (\bibinfo{year}{2011}).
+
+\bibitem{appourchaux+1998}
+\bibinfo{author}{Appourchaux, T.}, \bibinfo{author}{Gizon, L.} \&
+\bibinfo{author}{{Rabello-Soares}, M.-C.}
+\newblock \bibinfo{title}{The art of fitting p-mode spectra. {{I}}. {{Maximum}}
+	likelihood estimation}.
+\newblock \emph{\bibinfo{journal}{Astron. Astrophys. Supplement Series}}
+\textbf{\bibinfo{volume}{132}}, \bibinfo{pages}{107--119}
+(\bibinfo{year}{1998}).
+
+\bibitem{anderson+1990}
+\bibinfo{author}{{Anderson}, E.~R.}, \bibinfo{author}{{Duvall}, J., Thomas~L.}
+\& \bibinfo{author}{{Jefferies}, S.~M.}
+\newblock \bibinfo{title}{{Modeling of Solar Oscillation Power Spectra}}.
+\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+\textbf{\bibinfo{volume}{364}}, \bibinfo{pages}{699} (\bibinfo{year}{1990}).
+
+\bibitem{gelman2006}
+\bibinfo{author}{Gelman, A.}
+\newblock \bibinfo{title}{Prior distributions for variance parameters in
+	hierarchical models (comment on article by {{Browne}} and {{Draper}})}.
+\newblock \emph{\bibinfo{journal}{Bayesian Analysis}}
+\textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{515--534}
+(\bibinfo{year}{2006}).
+
+\bibitem{ballot+2006}
+\bibinfo{author}{Ballot, J.}, \bibinfo{author}{Garcia, R.~A.} \&
+\bibinfo{author}{Lambert, P.}
+\newblock \bibinfo{title}{Rotation speed and stellar axis inclination from p
+	modes: How {{CoRoT}} would see other suns}.
+\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+\textbf{\bibinfo{volume}{369}}, \bibinfo{pages}{1281--1286}
+(\bibinfo{year}{2006}).
+
+\bibitem{ballot+2008a}
+\bibinfo{author}{Ballot, J.}, \bibinfo{author}{Appourchaux, T.},
+\bibinfo{author}{Toutain, T.} \& \bibinfo{author}{Guittet, M.}
+\newblock \bibinfo{title}{On deriving p-mode parameters for inclined solar-like
+	stars}.
+\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
+\textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{867--875}
+(\bibinfo{year}{2008}).
+\newblock \eprint{0803.0885}.
+
+\bibitem{kass+raftery1995}
+\bibinfo{author}{Kass, R.~E.} \& \bibinfo{author}{Raftery, A.~E.}
+\newblock \bibinfo{title}{Bayes {{Factors}}}.
+\newblock \emph{\bibinfo{journal}{Journal of the American Statistical
+		Association}} \textbf{\bibinfo{volume}{90}}, \bibinfo{pages}{773--795}
+(\bibinfo{year}{1995}).
+
+\bibitem{beck2000}
+\bibinfo{author}{Beck, J.~G.}
+\newblock \bibinfo{title}{A comparison of differential rotation measurements -
+	({{Invited Review}})}.
+\newblock \emph{\bibinfo{journal}{Solar Physics}}
+\textbf{\bibinfo{volume}{191}}, \bibinfo{pages}{47--70}
+(\bibinfo{year}{2000}).
+
+\bibitem{doyle+2014}
+\bibinfo{author}{Doyle, A.~P.}, \bibinfo{author}{Davies, G.~R.},
+\bibinfo{author}{Smalley, B.}, \bibinfo{author}{Chaplin, W.~J.} \&
+\bibinfo{author}{Elsworth, Y.}
+\newblock \bibinfo{title}{Determining stellar macroturbulence using
+	asteroseismic rotational velocities from {{Kepler}}}.
+\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+\textbf{\bibinfo{volume}{444}}, \bibinfo{pages}{3592--3602}
+(\bibinfo{year}{2014}).
+
+\bibitem{tayar+2015}
+\bibinfo{author}{Tayar, J.} \emph{et~al.}
+\newblock \bibinfo{title}{Rapid {{Rotation}} of {{Low}}-mass {{Red Giants Using
+			APOKASC}}: {{A Measure}} of {{Interaction Rates}} on the
+	{{Post}}-main-sequence}.
+\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+\textbf{\bibinfo{volume}{807}}, \bibinfo{pages}{82} (\bibinfo{year}{2015}).
+
+\bibitem{schofield+2019}
+\bibinfo{author}{Schofield, M.} \emph{et~al.}
+\newblock \bibinfo{title}{The {{Asteroseismic Target List}} for {{Solar}}-like
+	{{Oscillators Observed}} in 2 minute {{Cadence}} with the {{Transiting
+			Exoplanet Survey Satellite}}}.
+\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
+\textbf{\bibinfo{volume}{241}}, \bibinfo{pages}{12} (\bibinfo{year}{2019}).
+
+\bibitem{mathur+2019}
+\bibinfo{author}{{Mathur}, S.} \emph{et~al.}
+\newblock \bibinfo{title}{{Revisiting the impact of stellar magnetic activity
+		on the detection of solar-like oscillations by Kepler}}.
+\newblock \emph{\bibinfo{journal}{Frontiers in Astronomy and Space Sciences}}
+\textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{46} (\bibinfo{year}{2019}).
+\newblock \eprint{1907.01415}.
+
+\bibitem{amard+matt2020}
+\bibinfo{author}{{Amard}, L.} \& \bibinfo{author}{{Matt}, S.~P.}
+\newblock \bibinfo{title}{{The Impact of Metallicity on the Evolution of the
+		Rotation and Magnetic Activity of Sun-like Stars}}.
+\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+\textbf{\bibinfo{volume}{889}}, \bibinfo{pages}{108} (\bibinfo{year}{2020}).
+\newblock \eprint{2001.10404}.
+
+\bibitem{fleming+2019}
+\bibinfo{author}{Fleming, D.~P.}, \bibinfo{author}{Barnes, R.},
+\bibinfo{author}{Davenport, J. R.~A.} \& \bibinfo{author}{Luger, R.}
+\newblock \bibinfo{title}{Rotation {{Period Evolution}} in {{Low}}-mass
+	{{Binary Stars}}: {{The Impact}} of {{Tidal Torques}} and {{Magnetic
+			Braking}}}.
+\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
+\textbf{\bibinfo{volume}{881}}, \bibinfo{pages}{88} (\bibinfo{year}{2019}).
+
+\bibitem{halbwachs1986}
+\bibinfo{author}{{Halbwachs}, J.~L.}
+\newblock \bibinfo{title}{{Common proper motion stars in the AGK 3.}}
+\newblock \emph{\bibinfo{journal}{Astron. Astrophys.s}}
+\textbf{\bibinfo{volume}{66}}, \bibinfo{pages}{131--148}
+(\bibinfo{year}{1986}).
+
+\bibitem{white+2013}
+\bibinfo{author}{{White}, T.~R.} \emph{et~al.}
+\newblock \bibinfo{title}{{Interferometric radii of bright Kepler stars with
+		the CHARA Array: {\ensuremath{\theta}} Cygni and 16 Cygni A and B}}.
+\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+\textbf{\bibinfo{volume}{433}}, \bibinfo{pages}{1262--1270}
+(\bibinfo{year}{2013}).
+\newblock \eprint{1305.1934}.
+
+\bibitem{maxted+2015}
+\bibinfo{author}{Maxted, P. F.~L.}, \bibinfo{author}{Serenelli, A.~M.} \&
+\bibinfo{author}{Southworth, J.}
+\newblock \bibinfo{title}{Comparison of gyrochronological and isochronal age
+	estimates for transiting exoplanet host stars}.
+\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+\textbf{\bibinfo{volume}{577}}, \bibinfo{pages}{A90} (\bibinfo{year}{2015}).
+
+\bibitem{gallet+delorme2019}
+\bibinfo{author}{{Gallet}, F.} \& \bibinfo{author}{{Delorme}, P.}
+\newblock \bibinfo{title}{{Star-planet tidal interaction and the limits of
+		gyrochronology}}.
+\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+\textbf{\bibinfo{volume}{626}}, \bibinfo{pages}{A120} (\bibinfo{year}{2019}).
+\newblock \eprint{1905.06070}.
+
+\bibitem{benbakoura+2019}
+\bibinfo{author}{Benbakoura, M.}, \bibinfo{author}{R{\'e}ville, V.},
+\bibinfo{author}{Brun, A.~S.}, \bibinfo{author}{{Le Poncin-Lafitte}, C.} \&
+\bibinfo{author}{Mathis, S.}
+\newblock \bibinfo{title}{Evolution of star-planet systems under magnetic
+	braking and tidal interaction}.
+\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
+\textbf{\bibinfo{volume}{621}}, \bibinfo{pages}{A124} (\bibinfo{year}{2019}).
+
+\bibitem{ceillier+2016}
+\bibinfo{author}{Ceillier, T.} \emph{et~al.}
+\newblock \bibinfo{title}{Rotation periods and seismic ages of {{KOIs}} -
+	comparison with stars without detected planets from {{Kepler}} observations}.
+\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
+\textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{119--125}
+(\bibinfo{year}{2016}).
+
+\end{thebibliography}
+
 \input{tabulate.tex}
 
-\bibliographystyle{naturemag}
-\bibliography{library.bib} % if your bibtex file is called example.bib
-
-\end{document}
+%\end{document}

### 2021-04-26 paper/natastron/ArXiV/paper.tex
updated arxiv

@@
 The weakened magnetic braking scenario was found to be $98.4\%$ more likely for our stellar ensemble, adding to the growing body of evidence for this stage of stellar rotational evolution.
-This work represents the largest catalogue of seismic rotation on the main sequence to date, opening up possibilities for more detailed ensemble analysis of rotational evolution with \textit{Kepler}.}
+This work represents a large catalogue of seismic rotation on the main sequence, opening up possibilities for more detailed ensemble analysis of rotational evolution with \textit{Kepler}.}
 
@@
 
-\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) p mode (\textit{Pressure} modes, the type of oscillation visible in main sequence stars) oscillations for each star, of which the latter have significantly lower signal-to noise.
+\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates for solar-like oscillators, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) p mode (\textit{Pressure} modes, the type of oscillation visible in main sequence stars) oscillations for each star, of which the latter have significantly lower signal-to noise.
 Radial oscillations ($\ell = 0$) are also visible, but do not split.
@@
 
-We compared our results with both published and unpublished asteroseismic rotation rates \cite{nielsen+2015,davies+2015,davies+2016, lund+2017, benomar+2018}, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with multiple other studies.
+We compared our results with both published and unpublished asteroseismic rotation rates for stars in our sample \cite{nielsen+2015,davies+2015,davies+2016, lund+2017, benomar+2018}, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with multiple other studies.
 For stars viewed near pole-on the split modes of oscillation have extremely low power, making them hard to detect reliably \cite{lund+2014}.
@@
 \textbf{Conclusions:} In this work, we obtained asteroseismic rotation rates for 91 stars using a hierarchical Bayesian model to fit for oscillation frequencies, convective background, and rotational splitting simultaneously.
-We validated these results against previously published and unpublished asteroseismic rotation measurements, making our new rotation catalogue the largest self-consistent sample of asteroseismic rotation in main sequence stars to date.
+We validated these results against previously published and unpublished asteroseismic rotation measurements, producing a catalogue with a large self-consistent sample of asteroseismic rotation in main sequence stars.
 We evaluated the stars in our sample against synthetic population \rtwo{distribution} models of the \textit{Kepler} field evolved under either a `standard' model of rotational evolution, or one where weakened magnetic braking takes place.
